### 2020-05-19 Manuscript/EPAWTFT.tex
init commit

\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}

\usepackage[normalem]{ulem}
\definecolor{darkgreen}{RGB}{0, 180, 0}
\newcommand{\titou}[1]{\textcolor{red}{#1}}
\newcommand{\hugh}[1]{\textcolor{orange}{#1}}
\newcommand{\trash}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\trashHB}[1]{\textcolor{orange}{\sout{#1}}}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\newcommand{\ctab}{\multicolumn{1}{c}{---}}
\newcommand{\mc}{\multicolumn}
\newcommand{\fnm}{\footnotemark}
\newcommand{\fnt}{\footnotetext}
\newcommand{\mcc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mr}{\multirow}
\newcommand{\SI}{\textcolor{blue}{supporting information}}

% operators
\newcommand{\bH}{\mathbf{H}}
\newcommand{\bh}{\mathbf{h}}
\newcommand{\bQ}{\mathbf{Q}}
\newcommand{\bSig}{\mathbf{\Sigma}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\PT}{\mathcal{PT}}

\newcommand{\EPT}{E_{\PT}}
\newcommand{\laPT}{\lambda_{\PT}}

\newcommand{\EEP}{E_\text{EP}}
\newcommand{\laEP}{\lambda_\text{EP}}

\newcommand{\Ne}{N}
\newcommand{\hH}{\Hat{H}}
\newcommand{\hT}{\Hat{T}}
\newcommand{\hW}{\Hat{W}}
\newcommand{\hV}{\Hat{V}}
\newcommand{\hc}[2]{\Hat{c}_{#1}^{#2}}
\newcommand{\hn}[1]{\Hat{n}_{#1}}
\newcommand{\n}[1]{n_{#1}}
\newcommand{\Dv}{\Delta v}
\newcommand{\up}{\uparrow}
\newcommand{\dw}{\downarrow}
\newcommand{\updw}{\up\dw}

\newcommand{\ra}{\rightarrow}

\newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France}
\newcommand{\UCAM}{Department of Chemistry, University of Cambridge, Lensfield Road, Cambridge, CB2 1EW, U.K.}

\begin{document}

\title{Exceptional points and where to find them}

\author{Antoine \surname{Marie}}
\email{antoine.marie@ens-lyon.fr}
\affiliation{\LCPQ}
%\author{Hugh G.~A.~\surname{Burton}}
%\email{hb407@cam.ac.uk}
%\affiliation{\UCAM}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
\thanks{Corresponding author}
\email{loos@irsamc.ups-tlse.fr}
\affiliation{\LCPQ}

\begin{abstract}
In this work, we explore the description of quantum chemistry in the complex plane. 
Using the Hubbard dimer as a simple model system, we investigate how various methods in electronic structure theory (including Hartree--Fock, \titou{density-functional theory}, perturbation theory and full configuration interaction) are formulated in the complex plane, and how this affects their behaviour in the real plane.
For example, we demonstrate how the position of exceptional points of the real axis controls the convergence of perturbation theory, and explore the inherent dependence on the set of orbital coefficients.
Moreover, we reveal how the avoided crossing of FCI states correspond to an exceptional point in the complex plane, which in turn demonstrates that multiple FCI solutions form a more general structure across the complex plane. 
Ultimately, by exposing these more profound topologies of electronic structure methods in the complex plane, we hope to pave the way for novel methodologies.
\end{abstract}

\maketitle

%============================================================%
\section{Introduction}
%============================================================%

The notion of quantised energy levels is a central feature of Hermitian quantum mechanics. 
In quantum chemistry, the ordering of the energy levels represents the different electronic states of a molecule, the lowest being the ground state while the higher ones are the so-called excited states.
Within this quantised paradigm, electronic states look completely disconnected from one another.
However, one can gain a different perspective on quantisation if one extends quantum chemistry into the complex domain.
In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.

Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), one can smoothly connect the ground and excited states of a molecule.
This connection is possible because, by extending real numbers to the complex domain, one loses the ordering property of real numbers.
Hence, one can interchange electronic states away from the real axis, as the concept of ground and excited states has been lost.
Amazingly, this smooth and continuous transition from one state to another has been recently realised experimentally in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics. \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}

Exceptional points (EPs) \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016} are non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996} where two states become exactly degenerate.
CIs are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to CIs in the decay of bound excited states.
Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
For example, by encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the starting wave function.
In contrast, encircling Hermitian degeneracies at CIs introduces only a geometric phase while leaving the states unchanged.
More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane. \cite{Olsen_1996, Olsen_2000}

%============================================================%
\section{Perturbation Theory}
%============================================================%

Within perturbation theory, the Schr\"odinger equation is usually rewritten as 
\begin{equation}
	\bH \Psi(\lambda) = (\bH^{(0)} + \lambda \bH^{(1)} ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
\end{equation}
with
\begin{equation}
	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}.
\end{equation}
However, it is not unusual that the series $E(\lambda)$ has a radius of convergence $\abs{\lambda_0} < 1$. 
This means that the series is divergent in the domain $\abs{\lambda} < \abs{\lambda_0}$, hence for the physical system at $\lambda = 1$.
As eluded above, $\abs{\lambda_0}$ is determined by the location of the singularity of $E(\lambda)$ closest to the origin.
These singularities are nothing but EPs at $\lambda_0$ and $\lambda_0^*$.
Here, we propose to thoroughly investigate the connection between Coulson-Fisher quasi-EPs and the radius of convergence of various flavours of perturbation theory.
For example, M{\o}ller-Plesset perturbation theory (MPPT) has the particularity of relying on a Hartree-Fock (HF) wave function as a zeroth-order wave function.
However, the flavour of HF one can select (restricted, unrestricted, generalised, holomorphic, \ldots) is up for grabs, and the convergence properties of the MPPT series will drastically change depending on this choice.
Indeed, the radius of convergence is intimately connected to the location of singularities in the complex plane; these singularities are, themselves, linked to the choice of $\bH^{(0)}$. 
Really, it depends on our ability of selecting a zeroth-order Hamiltonian such as $\bH$ does not have any EP inside the unit $\lambda$ circle.

For example, MPPT calculations based on UHF wave functions have shown to be slowly convergent due to spin contamination while RHF-based MPPT calculations can be divergent. \cite{Gill_1986, Gill_1988}
Although MPPT is widespread in the community, its convergence properties have not, to the very best of our knowledge, attracted much attention. \cite{Olsen_1996, Olsen_2000, Goodson_2012}
We believe that they deserve greater understanding, particularly in a non-Hermitian setting.

%============================================================%
\section{The asymmetric Hubbard dimer}
%============================================================%

The asymmetric Hubbard dimer is a model two-electron system whose Hamiltonian reads
\begin{equation}
	\hH = \hT + \hW + \hV,
\end{equation}
with
\begin{subequations}
\begin{align}
	\hT		& = - t \sum_{\sigma=\updw} (\hc{1\sigma}{\dag} \hc{2\sigma}{} + \hc{2\sigma}{\dag} \hc{1\sigma}{}),
	\\
	\hW	& =  U (\hn{1\up}\hn{1\dw} + \hn{2\up}\hn{2\dw}),
	\\
	\hV	& = \Dv (\hn{2} - \hn{1})/2,
\end{align}
\end{subequations}
where $\hn{i\sigma} = \hc{i\sigma}{\dag} \hc{i\sigma}{}$, $\hn{i} = \sum_{\sigma=\updw} \hn{i\sigma}$,  $U$ is the site energy, $t$ is hopping parameter, and $\Dv$ is the difference of on-site potential which controls the asymmetry of the model.
Note that $\n{1} + \n{2} = \Ne$, where $\Ne = 2$.

In the basis $\ket{1\up1\dw}$, $\ket{1\up2\dw}$, $\ket{2\up1\dw}$, $\ket{2\up2\dw}$, the Hamiltonian reads
\begin{equation}
	\hH = 
	\begin{pmatrix}
	- \Dv + U	&	-t	&	t	&	0		\\
	-t			&	0	&	0	&	-t		\\
	t			&	0	&	0	&	t		\\
	0			&	-t	&	t	&	\Dv + U	\\
	\end{pmatrix},
\end{equation}
which are composed by three singlet and one triplet states.
The ground-state singlet wave function can therefore be written as
\begin{equation}
	\ket*{^{1}\Psi} = \alpha \frac{\ket{1\up2\dw} + \ket{2\up1\dw}}{\sqrt{2}} + \beta \ket{1\up1\dw} + \gamma \ket{2\up2\dw}
\end{equation}
with $\alpha^2 + \beta^2 + \gamma^2 = 1$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Concluding remarks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\titou{What we have done is completely amazing.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%H.G.A.B.~thanks the Cambridge and Commonwealth Trust for a studentship. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{EPAWTFT}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2020-06-12 HalfInternshipSummary.tex
Add files via upload

\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage[top=3cm,bottom=5cm,left=3cm,right=3cm]{geometry}
\usepackage{caption}

\title{Summary sheet: half of the internship}
\author{Antoine Marie}

\begin{document}

\maketitle

\section{Generalities}

\subsection{Objectives}
Our goal is to understand the physics of exceptional points and perturbation series i.e. where are EP localize in the complex plane and how do they affect the convergence properties of the perturbation series. To do this we use the spherium model as a benchmark.

\subsection{Variables}

There are many variables that influence the physics of exceptional points and we need to rationalize how each variable affects the exceptional points.

\begin{itemize}
\item Partitioning of the Hamiltonian: Weak correlation reference (RHF or UHF, Möller-Plesset or Epstein-Nesbet), Strongly correlated reference
\item The basis set: minimal basis or infinite basis, localized or not basis functions
\item Radius of the spherium
\end{itemize}

\subsection{"Classification" of the bibliography}

We can categorize what have been done already in 3 groups:

\begin{itemize}
\item Gill, Handy, Nobes ... in the late 80's noticed that there are links between deceptive/erratic convergence of the Möller-Plesset pertubation series and spin contamination of the wavefunction.

\item Chaudhuri, Olsen ... in the late 90's highlighted links between singularities in the complex plane and convergence/divergence schemes of the MP series with a two-state model.

\item Sergeev, Goodson, Stillinger in the 00's studied this problem from a more mathematical point of view: $\alpha / \beta$ classification of the singularities, Pade approximant, critical point on the real axis ...
\end{itemize}

\section{Results}

\subsection{Spin contamination}
The UHF description of H\textsubscript{2} and spherium is analog. Gill's UHF description of H\textsubscript{2} in the minimal basis (1988) shows that the spin contamination of the doubly excited state RHF by triplet RHF wavefunctions are link to the poor convergence of the UMP series. 
For spherium in the minimal basis the RHF reference is bloc diagonal but the UHF reference have non zero matrix elements between triplet states and p\textsubscript{z}\textsuperscript{2} singlet. The matrix elements are

\begin{equation}
\lambda\frac{\sqrt[2]{-3+2R}(25+2R)\sqrt[2]{75+62R}}{280 R^{3}}
\end{equation}

The matrix elements are real for $R>\frac{3}{2}$ and $R<-\frac{75}{62}$. This is coherent with the Coulson-Fisher points of spherium (Burton 2019).

But Gill doesn't talk about the singularity structure of E(z) !

\subsection{Two state model}

Olsen et al. developped a two state model which allowed them to rationalize many schemes of convergence. Can we do this with our perturbation series ?

RHF: The schemes of convergence predicted by the two state model fit with our plots of the coefficients for both MP and EN partitioning.

UHF: The schemes predicted by the two state model are not correct.

In the UHF framework we need to consider more than two states because of the spin contamination -> this is expected that the two state model works for RHF and not for UHF.

\subsection{Singularity structure}

Sergeev 2005:
"Class $\alpha$ singularities are isolated complex conjugate pairs of square-root branch points, which correspond to the avoided crossings between the ground state and an excited state on a path along the real axis, while class $\beta$ singularities lie on or near the real axis and correspond to critical points at which one or more electrons dissociate from the nuclei."

\subsubsection{Class $\beta$}

According to this classification we could predict that there will be only class $\alpha$ singularities for the spherium because the electrons are restricted to the sphere.

But in the UHF framework we obtain class $\beta$ singularities, how is this possible ?

We can prove that there are a value of z at which the electrons form a cluster and dissociate from the nuclei (Stillinger 2000 and Sergeev 2005). By analogy with thermodynamics (Baker 1971) this value of z will be a critical point for $E(z)$. At this critical point the energy undergoes a phase transition from a discrete spectrum to a continuum of ionization states. So it's possible that class $\beta$ singularities are not just linked to ionization but more generally to phase transitions and symmetry breaking.

In our UHF framework we can see the apparition of those class $\beta$ singularities appear at the Coulson-Fischer points with the Möller-Plesset partitioning.

\subsubsection{Class $\alpha$}

We obtain as expected the class $\alpha$ singularities characteristic of an avoided crossing between the ground state and a doubly excited state. But they are sometimes in the positive half plane, sometimes in the negative half plane and they can also be on the pure imaginary axis.

Guess: this is due to the value/sign of E\textsubscript{1}. Can we prove this ?

\subsection{Strongly correlated}

We can use the "Laguerre" basis to define an adiabatic connection with a "localised" reference. We find that the radius of convergence is >1 for all R in the minimal and the n=3 basis.

\section{Open questions}

\begin{itemize}
\item Guess: adding diffuse functions as in the case of ionization $\beta$ singularities is not necessary because the symmetry breaking is already well described in the minimal basis. Can we prove this ?
\item Effect of an increase of the size of the basis set for the strongly correlated reference ?
\item Rationalize very precisely the singularity structure of the MP partitioning: avoided crossing (sharp or not) between which states, symmetry breaking, ...
\item Study the symmetry breaking in the Epstein-Nesbet partitioning
\item Why the radius of convergence for the strongly correlated partitioning is always greater than 1 ? Is there a feature of the basis functions that can make diverge a series ?

\end{itemize}

\end{document}

### 2020-06-12 MidTermSummary.tex
modifications in Part 1

--- 2020-06-12 HalfInternshipSummary.tex
@@
 
-\title{Summary sheet: half of the internship}
+\title{Internship Summary: Mid-Term Review}
+
 \author{Antoine Marie}
@@
 \subsection{Objectives}
-Our goal is to understand the physics of exceptional points and perturbation series i.e.
-where are EP localize in the complex plane and how do they affect the convergence properties of the perturbation series.
-To do this we use the spherium model as a benchmark.
+Our goal is to understand the physics of exceptional points (EPs) and perturbation series, i.e., where are EPs localize in the complex plane and how do they affect the convergence properties of the perturbation series.
+To do this we use the electronic ground-state of the spherium model (i.e., two opposite-spin electrons restricted to remain on a surface of a sphere of radius $R$) as a playground.
 
@@
 
-There are many variables that influence the physics of exceptional points and we need to rationalize how each variable affects the exceptional points.
-
+There are many variables that influence the physics of EPs and we must rationalize how each variable affects the location of these EPs.
 \begin{itemize}
-\item Partitioning of the Hamiltonian: Weak correlation reference (RHF or UHF, Möller-Plesset or Epstein-Nesbet), Strongly correlated reference
-\item The basis set: minimal basis or infinite basis, localized or not basis functions
-\item Radius of the spherium
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [restricted Hartree-Fock (RHF) or unrestricted Hartree-Fock (UHF) references, M{\o}ller-Plesset (MP) or Epstein-Nesbet (EN) partitioning], or strongly correlated reference.
+	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions
+	\item Radius of the spherium that ultimately dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
 \end{itemize}
 
-\subsection{"Classification" of the bibliography}
+\subsection{``Classification'' of the bibliography}
 
@@
 \begin{itemize}
-\item Gill, Handy, Nobes ... in the late 80's noticed that there are links between deceptive/erratic convergence of the Möller-Plesset pertubation series and spin contamination of the wavefunction.
+\item Gill, Handy, Nobes, \ldots in the late 80's noticed that there are links between deceptive/erratic convergence of the MP pertubation series and spin contamination of the wavefunction.
 
-\item Chaudhuri, Olsen ... in the late 90's highlighted links between singularities in the complex plane and convergence/divergence schemes of the MP series with a two-state model.
+\item Chaudhuri, Olsen, \ldots in the late 90's highlighted links between singularities in the complex plane and convergence/divergence schemes of the MP series with a two-state model.
 
-\item Sergeev, Goodson, Stillinger in the 00's studied this problem from a more mathematical point of view: $\alpha / \beta$ classification of the singularities, Pade approximant, critical point on the real axis ...
+\item Sergeev, Goodson, Stillinger in the 2000's studied this problem from a more mathematical point of view: $\alpha$/$\beta$ classification of the singularities, Pad\'e approximant, critical point on the real axis, etc.
 \end{itemize}

### 2020-06-12 MidTermSummary.tex
modifications in Part 2

@@
 \usepackage{caption}
+\usepackage[version=4]{mhchem}
 
@@
 \subsection{Spin contamination}
-The UHF description of H\textsubscript{2} and spherium is analog.
-Gill's UHF description of H\textsubscript{2} in the minimal basis (1988) shows that the spin contamination of the doubly excited state RHF by triplet RHF wavefunctions are link to the poor convergence of the UMP series.
-For spherium in the minimal basis the RHF reference is bloc diagonal but the UHF reference have non zero matrix elements between triplet states and p\textsubscript{z}\textsuperscript{2} singlet.
+The UHF description of \ce{H2} and spherium is analog. 
+Gill's UHF description of \ce{H2} in the minimal basis (1988) shows that the spin contamination of the doubly excited state RHF by triplet RHF wavefunctions are link to the poor convergence of the UMP series.
+For spherium in the minimal basis the RHF reference is bloc diagonal but the UHF reference has non-zero matrix elements between triplet states and $p_z^2$ singlet. 
 The matrix elements are
@@
 \begin{equation}
-\lambda\frac{\sqrt[2]{-3+2R}(25+2R)\sqrt[2]{75+62R}}{280 R^{3}}
+	\lambda\frac{\sqrt{-3+2R}(25+2R)\sqrt[2]{75+62R}}{280 R^{3}}
 \end{equation}
+% you should try to simplify this expression
 
-The matrix elements are real for $R>\frac{3}{2}$ and $R<-\frac{75}{62}$. This is coherent with the Coulson-Fisher points of spherium (Burton 2019).
-
-But Gill doesn't talk about the singularity structure of E(z) !
+The matrix elements are real for $R > 3/2$ and $R < -75/62$. 
+This is coherent with the Coulson-Fisher points of spherium (Burton 2019).
+However, Gill does not talk about the singularity structure of $E(z)$!
 
@@
 
-Olsen et al. developped a two state model which allowed them to rationalize many schemes of convergence. Can we do this with our perturbation series ?
+Olsen et al.~developped a two-state model which allowed them to rationalize many schemes of convergence. 
+Can we do this with our perturbation series?
 
-RHF: The schemes of convergence predicted by the two state model fit with our plots of the coefficients for both MP and EN partitioning.
-
-UHF: The schemes predicted by the two state model are not correct.
-
-In the UHF framework we need to consider more than two states because of the spin contamination -> this is expected that the two state model works for RHF and not for UHF.
+\begin{itemize}
+	\item RHF: The schemes of convergence predicted by the two-state model fit with our plots of the coefficients for both MP and EN partitioning.
+	\item UHF: The schemes predicted by the two-state model are not correct due to its intrinsic limitations. 
+\end{itemize}
+In the UHF framework we must consider more than two states because of the spin contamination $\rightarrow$ this is expected that the two state model works for RHF and not for UHF.
 
@@
 Sergeev 2005:
-"Class $\alpha$ singularities are isolated complex conjugate pairs of square-root branch points, which correspond to the avoided crossings between the ground state and an excited state on a path along the real axis, while class $\beta$ singularities lie on or near the real axis and correspond to critical points at which one or more electrons dissociate from the nuclei."
+\begin{quote}
+\textit{``Class $\alpha$ singularities are isolated complex conjugate pairs of square-root branch points, which correspond to the avoided crossings between the ground state and an excited state on a path along the real axis, while class $\beta$ singularities lie on or near the real axis and correspond to critical points at which one or more electrons dissociate from the nuclei.''}
+\end{quote}
 
@@
 
-According to this classification we could predict that there will be only class $\alpha$ singularities for the spherium because the electrons are restricted to the sphere.
+According to this classification we could predict that there will be only class $\alpha$ singularities for spherium because the electrons are restricted to the surface of the sphere.
+Nonetheless, in the UHF framework we obtain class $\beta$ singularities. 
+How is this possible?
 
-But in the UHF framework we obtain class $\beta$ singularities, how is this possible ?
-
-We can prove that there are a value of z at which the electrons form a cluster and dissociate from the nuclei (Stillinger 2000 and Sergeev 2005).
-By analogy with thermodynamics (Baker 1971) this value of z will be a critical point for $E(z)$.
+We can prove that there are a value of $z$ at which the electrons form a cluster and dissociate from the nuclei (Stillinger 2000 and Sergeev 2005). 
+By analogy with thermodynamics (Baker 1971) this value of $z$ is a critical point for $E(z)$. 
 At this critical point the energy undergoes a phase transition from a discrete spectrum to a continuum of ionization states. 
-So it's possible that class $\beta$ singularities are not just linked to ionization but more generally to phase transitions and symmetry breaking.
-
-In our UHF framework we can see the apparition of those class $\beta$ singularities appear at the Coulson-Fischer points with the Möller-Plesset partitioning.
+So it is possible that class $\beta$ singularities are not just linked to ionization but more generally to phase transitions and symmetry breaking.
+%T2: very true indeed.
+In our UHF framework we can see the apparition of those class $\beta$ singularities appear at the Coulson-Fischer points within the MP partitioning.
 
@@
 But they are sometimes in the positive half plane, sometimes in the negative half plane and they can also be on the pure imaginary axis.
-
-Guess: this is due to the value/sign of E\textsubscript{1}. Can we prove this ?
+Guess: this is due to the value/sign of $E_1$. 
+How can we prove this ?
 
@@
 
-We can use the "Laguerre" basis to define an adiabatic connection with a "localised" reference. We find that the radius of convergence is >1 for all R in the minimal and the n=3 basis.
+We can use the ``Laguerre'' basis to define an adiabatic connection with a ``localised'' reference. 
+We find that the radius of convergence is greater than unity for all $R$ in the minimal and the $n = 3$ basis.
 
@@
 	\item Guess: adding diffuse functions as in the case of ionization $\beta$ singularities is not necessary because the symmetry breaking is already well described in the minimal basis. 
-Can we prove this ?
-\item Effect of an increase of the size of the basis set for the strongly correlated reference ?
-\item Rationalize very precisely the singularity structure of the MP partitioning: avoided crossing (sharp or not) between which states, symmetry breaking, ...
-\item Study the symmetry breaking in the Epstein-Nesbet partitioning
-\item Why the radius of convergence for the strongly correlated partitioning is always greater than 1 ? Is there a feature of the basis functions that can make diverge a series ?
-
+	Can we prove this?
+	\item Effect of an increase of the size of the basis set for the strongly correlated reference?
+	\item Rationalize very precisely the singularity structure of the MP partitioning: avoided crossing (sharp or not) between which states, symmetry breaking, \ldots
+	\item Study the symmetry breaking in the EN partitioning
+	\item Why the radius of convergence for the strongly correlated partitioning is always greater than 1? 
+	Is there a feature of the basis functions that can make a series divergent?
 \end{itemize}

### 2020-06-28 SlideToulouse/main.tex
ajout des slides

\documentclass[xcolor=x11names,compress]{beamer}

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
\usepackage{mathpazo}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{multimedia}
\usepackage{subfigure}
\usepackage[absolute,overlay]{textpos}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Beamer Layout %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\useoutertheme[subsection=false,shadow]{miniframes}
\useinnertheme{default}

\setbeamerfont{title like}{shape=\scshape}
\setbeamerfont{frametitle}{shape=\scshape}
\setbeamerfont{framesubtitle}{size=\normalsize}
\setbeamerfont{caption}{size=\scriptsize}
\setbeamercolor*{lower separation line head}{bg=DeepSkyBlue4} 
\setbeamercolor*{normal text}{fg=black,bg=white} 
\setbeamercolor*{alerted text}{fg=red} 
\setbeamercolor*{example text}{fg=black} 
\setbeamercolor*{structure}{fg=black}

\setbeamercolor*{palette tertiary}{fg=black,bg=black!10} 
\setbeamercolor*{palette quaternary}{fg=black,bg=black!10} 
\setbeamercolor{caption name}{fg=DeepSkyBlue4}
\setbeamercolor{title}{fg=DeepSkyBlue4}
\setbeamercolor{itemize item}{fg=DeepSkyBlue4}
\setbeamercolor{frametitle}{fg=DeepSkyBlue4}
\renewcommand{\(}{\begin{columns}}
\renewcommand{\)}{\end{columns}}
\newcommand{\<}[1]{\begin{column}{#1}}
\renewcommand{\>}{\end{column}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamertemplate{navigation symbols}{} 
\setbeamertemplate{footline}[frame number]
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{section in toc}[ball]
\setbeamertemplate{itemize items}[circle]
\beamerboxesdeclarecolorscheme{clair}{Coral4}{Ivory2}
\beamerboxesdeclarecolorscheme{foncé}{DarkSeaGreen4}{Ivory2}

\title[Title]{Perturbation theories in the complex plane}
\author[]{Antoine \textsc{Marie}}
  \setbeamersize{text margin left=5mm}
  \setbeamersize{text margin right=5mm}
\institute{Supervised by Pierre-François \textsc{LOOS}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[plain]

\date{30th June 2020}
\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Why do we use perturbation theories in computational chemistry?}

\pause[1]

The Hartree-Fock theory is \textcolor{Green4}{computationally cheap} and can be applied even to \textcolor{Green4}{large systems}.

But this method is missing the \textcolor{red}{correlation energy}...

\vspace{0.5cm}

\pause[2]

$\rightarrow$ We need methods to get this correlation energy!

\vspace{0.5cm}

\pause[3]

\begin{beamerboxesrounded}[scheme=foncé]{\centering A general method}
In physics perturbation theory is often a good way to improve the obtained results with an approximated Hamiltonian.
\end{beamerboxesrounded}

\end{frame}

\section{\textsc{Strange behaviors of the MP series}}

\begin{frame}{The Møller-Plesset perturbation theory}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Partitioning of the Hamiltonian}

\begin{equation}
   H = H_0 + \lambda V
\end{equation}

\end{beamerboxesrounded}

\begin{itemize}
\centering
    \item $H_0$: Unperturbed Hamiltonian
    \item $V$: Perturbation operator
\end{itemize}

\pause[2]

\begin{beamerboxesrounded}[scheme=foncé]{\centering The Fock operator}

\begin{equation}
   F = T + J + K
\end{equation}

\end{beamerboxesrounded}

\begin{itemize}
\centering
    \item $T$: Kinetic energy operator
    \item $J$: Coulomb operator
    \item $K$: Exchange operator
\end{itemize}

\pause[3]

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering
Full Configuration Interaction gives us access to high order terms of the perturbation series !
\end{beamerboxesrounded}

\end{frame}

\begin{frame}{Deceptive or slow convergences}

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using minimal basis set MPn theory (n~=~1-20).\footnote{\cite{gill_deceptive_1986}}}
    \label{fig:my_label}
\end{figure}

\end{frame}

\begin{frame}{Multi-reference and spin contamination}
\begin{table}
    \centering
    \begin{tabular}{c c c c c c c}
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\end{tabular}
    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the minimal basis.}
    \label{tab:my_label}
\end{table}

\footnotetext{\tiny{Gill et al. Why does unrestricted Møller–Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}

\end{frame}

\begin{frame}{Divergent cases}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{The-energy-corrections-for-HF-at-stretched-geometry-in-the-cc-pVDZ-basis.png}
    \caption{The energy corrections for HF at stretched geometry in the cc-pVDZ basis.}
    \label{fig:my_label}
\end{figure}

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

\end{frame}

\section{The complex plane}

\begin{frame}{A simple example}

\begin{columns}

\column{0.48\textwidth}

\begin{beamerboxesrounded}[scheme=foncé]{An example function}

\begin{equation*}
   \frac{1}{1 + x^4}
\end{equation*}

\end{beamerboxesrounded}

\vspace{1cm}

\begin{itemize}
    \item Smooth for $x \in \mathbb{R}$

    \item Infinitely differentiable on $\mathbb{R}$
\end{itemize}

\column{0.48\textwidth}

    \begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{exemplesingu.pdf}
    \caption{Plot of $1/(1+x^4)$}
    \label{fig:my_label}
\end{figure}

\end{columns}

But the Taylor expansion of this function does not converge for $x\geq1$... 
\vspace{0.3cm}
\centering Why ?

\end{frame}

\begin{frame}{And if we look in the complex plane ?}

\begin{columns}

\column{0.48\textwidth}

\centering The function has 4 singularities in the complex plane !

\vspace{1cm}

$x = e^{i\pi/4}, e^{-i\pi/4}, e^{i3\pi/4}, e^{-i3\pi/4}$

\column{0.48\textwidth}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{possingu.pdf}
    \caption{\centering Singularities of the function $1/(1+x^4)$}
    \label{fig:my_label}
\end{figure}

\end{columns}

The \textcolor{red}{radius of convergence} of the Taylor expansion of a function is equal to the distance of the \textcolor{red}{closest singularity} to the origin in the \textcolor{red}{complex plane}.

\end{frame}

\begin{frame}{Extending chemistry in the complex plane}

\begin{beamerboxesrounded}[scheme=foncé]{\centering $\lambda$ a complex variable}

\begin{equation*}
   H(\lambda) = H_0 + \lambda V
\end{equation*}

\end{beamerboxesrounded}

\begin{columns}

\column{0.48\textwidth}

\begin{itemize}
    \item $n$ Riemann sheets
    \vspace{0.3cm}
    \item Exceptional points interconnecting the sheets
    \vspace{0.3cm}
    \item No ordering property in the complex plane
\end{itemize}

\column{0.48\textwidth}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{riemannsheet.png}
    \label{fig:my_label}
\end{figure}

\end{columns}

\end{frame}

\section{Classifying the singularity}

\begin{frame}{Which features of the system localize the singularities ?}

\begin{itemize}
    \item Partitioning of the Hamiltonian: Möller-Plesset, Epstein-Nesbet,...
    \item Zeroth order reference: weak correlation or strongly correlated electrons.
    \item Finite or complete basis set.
    \item Localized or delocalized basis functions.
\end{itemize}

\end{frame}

\begin{frame}{A two-state model}

\begin{columns}

\column{0.48\textwidth}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{avoidedcrossing.pdf}
    \caption{Example of an avoided crossing.}
    \label{fig:my_label}
\end{figure}

\column{0.48\textwidth}

\begin{beamerboxesrounded}[scheme=foncé]{A 2x2 matrix}
\centering \small{$\mqty(\alpha & \delta \\ \delta & \beta)  =$}

\vspace{0.15cm}

\small{$\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s ) + \mqty(- \alpha_s & \delta \\ \delta & - \beta_s)$}

\end{beamerboxesrounded}
\vspace{1cm}
\end{columns}

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

\end{frame}

\begin{frame}{Two-state model}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figure-fig14.png}
    \caption{\centering The energy corrections for HF at stretched geometry in the aug'-cc-pVDZ basis with the two-state model.\textsuperscript{a}}
    \label{fig:my_label}
\end{figure}

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

\end{frame}

\begin{frame}{Existence of a critical point}

For $\lambda<0$:

\begin{equation*}
    H(\lambda)=\sum\limits_{j=1}^{2n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{2n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
\end{equation*}

\footnote{stillinger, sergeev, baker}

\end{frame}

\begin{frame}{Critical point in a finite basis set}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Exact energy $E(z)$}
$E(z)$ has a critical point on the negative real axis and $E(z)$ is continue for real values below $z_{crit}$.
\end{beamerboxesrounded}

\vspace{0.5cm}

\pause[2]

\begin{beamerboxesrounded}[scheme=foncé]{\centering In a finite basis set}
The singularities occur in complex conjugate pairs with non-zero imaginary parts and the energies are discrete. 
\end{beamerboxesrounded}

\vspace{0.5cm}

\pause[3]

\centering \Large{How is this connected???}

\end{frame}

\begin{frame}{Singularities $\alpha$ and $\beta$}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Observation}
We can separate singularities in two parts. 
\end{beamerboxesrounded}

\pause[2]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
\begin{itemize}
    \item Large avoided crossing
    \item Non-zero imaginary part
    \item Interaction with a low lying doubly excited states
\end{itemize} 
\end{beamerboxesrounded}

\pause[3]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
\begin{itemize}
    \item Sharp avoided crossing
    \item Very small imaginary part
    \item Interaction with a diffuse function 
\end{itemize} 
\end{beamerboxesrounded}

\footnote{sergeev}

\end{frame}

\begin{frame}{Modeling the critical point}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Stillinger}
\begin{quote}
    \textit{"One might expect that $E_{FCI}(z) $ would try to model a continuum at $z_c$ with a grouping of discrete but closely spaced eigenstates that undergo sharp avoided crossing with the ground states."}
\end{quote}
\end{beamerboxesrounded}

\vspace{0.5cm}

\pause[2]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Sergeev et al.}
Proof of the existence of this group of sharp avoided crossings for Ne, He and HF when the basis set contains diffuse functions.
\end{beamerboxesrounded}

\end{frame}

\section{The spherium model}

\begin{frame}{Spherium: a theoretical playground}

\begin{beamerboxesrounded}[scheme=foncé]{\centering Two electrons on a sphere Hamiltonian}
\begin{equation*}
    H=-\frac{1}{2}(\grad_1^2 + \grad_2^2) + \frac{1}{r_{12}}
\end{equation*} 
\end{beamerboxesrounded}
\vspace{0.5cm}

\begin{columns}

\column{0.48\textwidth}

\centering{Small $R$}
\vspace{0.5cm}

\begin{itemize}
    \item $E_{kin} >> E_p$
    \item Uniform density of electrons
    \item \textcolor{red}{Weak correlation}
\end{itemize}

\vspace{0.5cm}

\column{0.48\textwidth}

\centering{Large $R$}
\vspace{0.5cm}

\begin{itemize}
    \item $E_{kin} << E_p$
    \item Electrons on the opposite sides of the sphere
    \item \textcolor{red}{Strong correlation}
    \end{itemize}

\end{columns}

\end{frame}

\begin{frame}{Apparition of a class $\beta$ singularity}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Expectation}
The electrons are restricted to the surface of the sphere so we should not observe singularities characteristic of ionization processes.
\end{beamerboxesrounded}

\vspace{0.5cm}

\pause[2]

\large But for some values of R... we actually observe some $\beta$ singularities!
\centering Why?

\vspace{0.5cm}

\pause[3]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Symmetry breaking}
The $\beta$ singularities observed are connected to the symmetry breaking of the wave function.
\end{beamerboxesrounded}

\end{frame}

\begin{frame}{Conclusion}

\pause[1]

\begin{beamerboxesrounded}[scheme=foncé]{\centering Møller-Plesset perturbation theory}
By understanding how the singularities are localized in the complex plane we hope that it will gives us a deep understanding of the strengths and weaknesses of the Møller-Plesset method to get the correlation energy.
\end{beamerboxesrounded}

\pause[2]

\vspace{0.5cm}

But there is an other secret application of exceptional points...

\pause[3]

\vspace{0.5cm}

\begin{beamerboxesrounded}[scheme=foncé]{\centering A new way to excited states energies}
The exceptionnal points connect ground and excited states in the complex plane. Using those properties one can smoothly morph a ground state in an excited state. 
\end{beamerboxesrounded}

\end{frame}

\end{document}

### 2020-06-28 SlideToulouse/main.tex
Add files via upload

@@
 \usepackage[utf8]{inputenc}
-\usepackage{xcolor}
 \usepackage{siunitx}
@@
 \usepackage{subfigure}
+\usepackage{xcolor}
 \usepackage[absolute,overlay]{textpos}
@@
 
+\renewcommand{\thefootnote}{\alph{footnote}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title[Title]{Perturbation theories in the complex plane}
+\title[Title]{Perturbative theories in the complex plane}
 \author[]{Antoine \textsc{Marie}}
+\date{30 Juin 2020}
   \setbeamersize{text margin left=5mm}
@@
 
-\date{30th June 2020}
+\date{24 Avril 2020}
 \titlepage
@@
 
-\begin{frame}{Why do we use perturbation theories in computational chemistry?}
-
-\pause[1]
-
-The Hartree-Fock theory is \textcolor{Green4}{computationally cheap} and can be applied even to \textcolor{Green4}{large systems}.
-
-But this method is missing the \textcolor{red}{correlation energy}...
-
-\vspace{0.5cm}
-
-\pause[2]
-
-$\rightarrow$ We need methods to get this correlation energy!
-
-\vspace{0.5cm}
-
-\pause[3]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering A general method}
-In physics perturbation theory is often a good way to improve the obtained results with an approximated Hamiltonian.
-\end{beamerboxesrounded}
-
-\end{frame}
-
 \section{\textsc{Strange behaviors of the MP series}}
 
-\begin{frame}{The Møller-Plesset perturbation theory}
-
-\pause[1]
+\begin{frame}{The Möller-Plesset theory}
 
@@
 \centering
-    \item $H_0$: Unperturbed Hamiltonian
-    \item $V$: Perturbation operator
+    \item $H_0$ : Unperturbed Hamiltonian
+    \item $V$ : Perturbation operator
 \end{itemize}
-
-\pause[2]
 
@@
 \end{equation}
-
 \end{beamerboxesrounded}
@@
 \centering
-    \item $T$: Kinetic energy operator
-    \item $J$: Coulomb operator
-    \item $K$: Exchange operator
+    \item $T$ : Kinetic energy operator
+    \item $J$ : Coulomb operator
+    \item $K$ : Exchange operator
 \end{itemize}
-
-\pause[3]
-
-\begin{beamerboxesrounded}[scheme=foncé]{}
-\centering
-Full Configuration Interaction gives us access to high order terms of the perturbation series !
-\end{beamerboxesrounded}
 
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using minimal basis set MPn theory (n~=~1-20).\footnote{\cite{gill_deceptive_1986}}}
+    \includegraphics[width=0.5\textwidth]{gill1986.png}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using minimal basis set MPn theory (n~=~1-20).}
     \label{fig:my_label}
 \end{figure}
+
+\footnotetext{\tiny{Gill et al.~Deceptive convergence in Møller-Plesset perturbation  energies, \textit{Chemical Physics Letter}, 1986}}
 
@@
 \hline
- $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
+ $r$ & UHF & UMP2 & UMP3 & UMP4 & $<S^2>$ \\
 \hline
@@
 \end{tabular}
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the minimal basis.}
+    \caption{\centering Percentage of electron correlation energy recovered and $<S^2>$ for the \ce{H2} molecule as a function of bond length (r,A) in the minimal basis.}
     \label{tab:my_label}
@@
 
-But the Taylor expansion of this function does not converge for $x\geq1$... 
+But the Taylor expansion of this function does not converge for $x\geq1$ ... 
 \vspace{0.3cm}
@@
 \begin{equation*}
-   H(\lambda) = H_0 + \lambda V
+   H = H_0 + \lambda V
 \end{equation*}
@@
 \begin{itemize}
-    \item Partitioning of the Hamiltonian: Möller-Plesset, Epstein-Nesbet,...
+    \item Partitioning of the Hamiltonian: Möller-Plesset, Epstein-Nesbet, ...
     \item Zeroth order reference: weak correlation or strongly correlated electrons.
@@
 
-\begin{beamerboxesrounded}[scheme=foncé]{A 2x2 matrix}
-\centering \small{$\mqty(\alpha & \delta \\ \delta & \beta)  =$}
+\begin{beamerboxesrounded}[scheme=foncé]{A 2x2 matrix\textsuperscript{a}}
 
-\vspace{0.15cm}
+$
 
-\small{$\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s ) + \mqty(- \alpha_s & \delta \\ \delta & - \beta_s)$}
+\small{\centering \begin{pmatrix}
+   \alpha & \delta \\
+   \delta & \beta 
+\end{pmatrix} =
+
+\vspace{0.3cm}
+
+\begin{pmatrix}
+
+   \alpha + \alpha_s & 0 \\
+   0 & \beta + \beta_s
+\end{pmatrix} +
+\begin{pmatrix}
+   - \alpha_s & \delta \\
+   \delta & - \beta_s
+\end{pmatrix}}
+$
 
@@
 
-\begin{frame}{Two-state model}
+\begin{frame}{Two state model}
 
@@
 
-For $\lambda<0$:
+For $\lambda<0$ :
 
 \begin{equation*}
-    H(\lambda)=\sum\limits_{j=1}^{2n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{2n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
+    H(\lambda)=\sum\limits_{j=1}^{2n}\left[ \underbrace{-\frac{1}{2}\nabla_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{2n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
 \end{equation*}
-
-\footnote{stillinger, sergeev, baker}
 
@@
 
-\pause[1]
-
 \begin{beamerboxesrounded}[scheme=foncé]{\centering Exact energy $E(z)$}
-$E(z)$ has a critical point on the negative real axis and $E(z)$ is continue for real values below $z_{crit}$.
+$E(z)$ has a critical point on the negative real axis and $E(z)$ is continue for real value below $z_{crit}$.
 \end{beamerboxesrounded}
@@
 \vspace{0.5cm}
-
-\pause[2]
 
@@
 
-\pause[3]
-
-\centering \Large{How is this connected???}
+\centering \Large{How is this connected ???}
 
@@
 
-\pause[1]
-
 \begin{beamerboxesrounded}[scheme=foncé]{\centering Observation}
@@
 
-\pause[2]
-
 \begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
@@
     \item Large avoided crossing
+    \item Interaction with a low lying doubly excited states
     \item Non-zero imaginary part
-    \item Interaction with a low lying doubly excited states
 \end{itemize} 
 \end{beamerboxesrounded}
-
-\pause[3]
 
@@
     \item Sharp avoided crossing
+    \item Interaction with a diffuse function 
     \item Very small imaginary part
-    \item Interaction with a diffuse function 
 \end{itemize} 
 \end{beamerboxesrounded}
-
-\footnote{sergeev}
 
@@
 \begin{frame}{Modeling the critical point}
-
-\pause[1]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Stillinger}
-\begin{quote}
-    \textit{"One might expect that $E_{FCI}(z) $ would try to model a continuum at $z_c$ with a grouping of discrete but closely spaced eigenstates that undergo sharp avoided crossing with the ground states."}
-\end{quote}
-\end{beamerboxesrounded}
-
-\vspace{0.5cm}
-
-\pause[2]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Sergeev et al.}
-Proof of the existence of this group of sharp avoided crossings for Ne, He and HF when the basis set contains diffuse functions.
-\end{beamerboxesrounded}
 
@@
 \begin{equation*}
-    H=-\frac{1}{2}(\grad_1^2 + \grad_2^2) + \frac{1}{r_{12}}
+    H=-\frac{1}{2}(\nabla_1^2 + \nabla_2^2) + \frac{1}{r_{12}}
 \end{equation*} 
@@
 
-\begin{frame}{Apparition of a class $\beta$ singularity}
-
-\pause[1]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Expectation}
-The electrons are restricted to the surface of the sphere so we should not observe singularities characteristic of ionization processes.
-\end{beamerboxesrounded}
-
-\vspace{0.5cm}
-
-\pause[2]
-
-\large But for some values of R... we actually observe some $\beta$ singularities!
-\centering Why?
-
-\vspace{0.5cm}
-
-\pause[3]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Symmetry breaking}
-The $\beta$ singularities observed are connected to the symmetry breaking of the wave function.
-\end{beamerboxesrounded}
+\begin{frame}{Why is there a class $\beta$ singularity ?}
 
@@
 
-\pause[1]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Møller-Plesset perturbation theory}
-By understanding how the singularities are localized in the complex plane we hope that it will gives us a deep understanding of the strengths and weaknesses of the Møller-Plesset method to get the correlation energy.
-\end{beamerboxesrounded}
-
-\pause[2]
-
-\vspace{0.5cm}
-
-But there is an other secret application of exceptional points...
-
-\pause[3]
-
-\vspace{0.5cm}
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering A new way to excited states energies}
-The exceptionnal points connect ground and excited states in the complex plane. Using those properties one can smoothly morph a ground state in an excited state. 
-\end{beamerboxesrounded}
-
 \end{frame}

### 2020-06-28 SlideToulouse/main.tex
Add files via upload

--- 2020-06-28 SlideToulouse/main.tex
@@
     \includegraphics[width=0.4\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using minimal basis set MPn theory (n~=~1-20).\footnote{\cite{gill_deceptive_1986}}}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using STO-3G basis set MPn theory (n~=~1-20).}
     \label{fig:my_label}
@@
 \end{tabular}
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the minimal basis.}
+    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set.}
     \label{tab:my_label}
@@
 \begin{itemize}
-    \item Partitioning of the Hamiltonian: Möller-Plesset, Epstein-Nesbet,...
+    \item Partitioning of the Hamiltonian: Møller-Plesset, Epstein-Nesbet,...
     \item Zeroth order reference: weak correlation or strongly correlated electrons.
@@
 
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\alpha$}
+\begin{beamerboxesrounded}[scheme=foncé]{\centering Singularity $\beta$}
 \begin{itemize}

### 2020-06-28 SlideToulouse/main.tex
minor corrections on slides

@@
 \centering
-Full Configuration Interaction gives us access to high order terms of the perturbation series !
+Full Configuration Interaction gives access to high-order terms of the perturbation series!
 \end{beamerboxesrounded}
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} using STO-3G basis set MPn theory (n~=~1-20).}
+    \includegraphics[width=0.5\textwidth]{gill1986.png}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
     \label{fig:my_label}
@@
 
-\footnotetext{\tiny{Gill et al. Why does unrestricted Møller–Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}
+\footnotetext{\tiny{Gill et al. Why does unrestricted M{\o}ller-Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}
 
@@
 
-    \item Infinitely differentiable on $\mathbb{R}$
+    \item Infinitely differentiable in $\mathbb{R}$
 \end{itemize}
@@
 
-\begin{frame}{And if we look in the complex plane ?}
+\begin{frame}{And if we look in the complex plane?}
 
@@
 
-\centering The function has 4 singularities in the complex plane !
+\centering The function has 4 singularities in the complex plane!
 
@@
 
-\begin{frame}{Which features of the system localize the singularities ?}
+\begin{frame}{Which features of the system localize the singularities?}
 
 \begin{itemize}
-    \item Partitioning of the Hamiltonian: Møller-Plesset, Epstein-Nesbet,...
-    \item Zeroth order reference: weak correlation or strongly correlated electrons.
+    \item Partitioning of the Hamiltonian: Møller-Plesset, Epstein-Nesbet, \ldots
+    \item Zeroth-order reference: weak or strong correlation.
     \item Finite or complete basis set.
@@
     \item Non-zero imaginary part
-    \item Interaction with a low lying doubly excited states
+    \item Interaction with a low-lying doubly excited states
 \end{itemize} 
@@
 \begin{itemize}
-    \item $E_{kin} >> E_p$
+    \item $E_\text{kin} \gg E_\text{pot}$
     \item Uniform density of electrons
@@
 \begin{itemize}
-    \item $E_{kin} << E_p$
+    \item $E_\text{kin} \ll E_\text{pot}$
     \item Electrons on the opposite sides of the sphere

### 2020-06-29 SlideToulouse/main.tex
Add files via upload

@@
 \usepackage{graphicx}
-\usepackage{tikz}
-\usetikzlibrary{decorations.fractals}
 \usepackage{mathpazo}
@@
 \usepackage{multimedia}
-\usepackage{subfigure}
 \usepackage[absolute,overlay]{textpos}
@@
 \usepackage[version=4]{mhchem}
+\usepackage[style=verbose,backend=bibtex]{biblatex}
+\bibliography{SlideToulouse}
 
@@
 \centering
+
 Full Configuration Interaction gives access to high-order terms of the perturbation series!
+
 \end{beamerboxesrounded}
@@
 
-\begin{frame}{Deceptive or slow convergences}
+\begin{frame}{Deceptive or slow convergences\footcite{gill_deceptive_1986}}
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{gill1986.png}
+
+    \includegraphics[width=0.45\textwidth]{gill1986.png}
+
     \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
@@
 
-\begin{frame}{Multi-reference and spin contamination}
+\begin{frame}{Multi-reference and spin contamination\footcite{gill_why_1988}}
 \begin{table}
@@
 
-\footnotetext{\tiny{Gill et al. Why does unrestricted M{\o}ller-Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}
-
 \end{frame}
@@
     \includegraphics[width=0.6\textwidth]{The-energy-corrections-for-HF-at-stretched-geometry-in-the-cc-pVDZ-basis.png}
-    \caption{The energy corrections for HF at stretched geometry in the cc-pVDZ basis.}
+    \caption{The energy corrections for HF at stretched geometry in the cc-pVDZ basis. \footcite{olsen_divergence_2000}}
     \label{fig:my_label}
 \end{figure}
-
-\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}
 
@@
 
-\begin{frame}{A two-state model}
+\begin{frame}{A two-state model\footcite{olsen_divergence_2000}}
 
@@
 
-\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}
-
 \end{frame}
 
-\begin{frame}{Two-state model}
+\begin{frame}{Two-state model\footcite{olsen_divergence_2000}}
 
@@
     \includegraphics[width=0.6\textwidth]{figure-fig14.png}
-    \caption{\centering The energy corrections for HF at stretched geometry in the aug'-cc-pVDZ basis with the two-state model.\textsuperscript{a}}
+    \caption{\centering The energy corrections for HF at stretched geometry in the aug'-cc-pVDZ basis with the two-state model.}
     \label{fig:my_label}
@@
 
-\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}
-
 \end{frame}
 
-\begin{frame}{Existence of a critical point}
+\begin{frame}{Existence of a critical point\footcite{stillinger_mollerplesset_2000}}
 
@@
 \end{equation*}
-
-\footnote{stillinger, sergeev, baker}
 
@@
 
-\begin{frame}{Singularities $\alpha$ and $\beta$}
+\begin{frame}{Singularities $\alpha$ and $\beta$ \footcite{sergeev_singularities_2006}}
 
@@
 
-\footnote{sergeev}
-
 \end{frame}
@@
 
-\begin{frame}{Spherium: a theoretical playground}
+\begin{frame}{Spherium: a theoretical playground\footcite{loos_ground_2009}}
 

### 2020-06-29 SlideToulouse/main.tex
Add files via upload

@@
 \begin{equation}
-   F = T + J + K
+   F = \sum\limits_{i=1}^{n} f(i) \hspace{0.3cm} ; \hspace{0.3cm} f(i) = h(i) + \sum\limits_{i=1}^{n/2} \left[2J_j(i) - K_j(i)\right]
 \end{equation}
@@
 \centering
-    \item $T$: Kinetic energy operator
-    \item $J$: Coulomb operator
-    \item $K$: Exchange operator
+    \item $f(i)$: Fock operator
+    \item $h(i)$: One electron Hamiltonian
+    \item $J_j(i)$: Coulomb operator
+    \item $K_j(i)$: Exchange operator
 \end{itemize}
@@
 \centering
-
-Full Configuration Interaction gives access to high-order terms of the perturbation series!
-
+Full Configuration Interaction gives access to high-order terms of the perturbation series !
 \end{beamerboxesrounded}
@@
     \centering
-
     \includegraphics[width=0.45\textwidth]{gill1986.png}
-
     \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
@@
 
+\begin{frame}{The Møller-Plesset Hamiltonian}
+
+\begin{equation}
+H(\lambda)=H_0 + \lambda (H_\text{phys} - H_0)    
+\end{equation}
+
+\begin{equation}
+    H_\text{phys}=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}\right]
+\end{equation}
+
+\begin{equation}
+    H_0=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+V_j^{(scf)}\right]
+\end{equation}
+
+\end{frame}
+
 \begin{frame}{Existence of a critical point\footcite{stillinger_mollerplesset_2000}}
@@
 \begin{equation*}
-    H(\lambda)=\sum\limits_{j=1}^{2n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{2n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
+    H(\lambda)=\sum\limits_{j=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
 \end{equation*}
@@
 
-\section{The spherium model}
-
-\begin{frame}{Spherium: a theoretical playground\footcite{loos_ground_2009}}
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Two electrons on a sphere Hamiltonian}
-\begin{equation*}
-    H=-\frac{1}{2}(\grad_1^2 + \grad_2^2) + \frac{1}{r_{12}}
-\end{equation*} 
-\end{beamerboxesrounded}
-\vspace{0.5cm}
-
-\begin{columns}
-
-\column{0.48\textwidth}
-
-\centering{Small $R$}
-\vspace{0.5cm}
-
-\begin{itemize}
-    \item $E_\text{kin} \gg E_\text{pot}$
-    \item Uniform density of electrons
-    \item \textcolor{red}{Weak correlation}
-\end{itemize}
-
-\vspace{0.5cm}
-
-\column{0.48\textwidth}
-
-\centering{Large $R$}
-\vspace{0.5cm}
-
-\begin{itemize}
-    \item $E_\text{kin} \ll E_\text{pot}$
-    \item Electrons on the opposite sides of the sphere
-    \item \textcolor{red}{Strong correlation}
-    \end{itemize}
-
-\end{columns}
-
-\end{frame}
-
-\begin{frame}{Apparition of a class $\beta$ singularity}
-
-\pause[1]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Expectation}
-The electrons are restricted to the surface of the sphere so we should not observe singularities characteristic of ionization processes.
-\end{beamerboxesrounded}
-
-\vspace{0.5cm}
-
-\pause[2]
-
-\large But for some values of R... we actually observe some $\beta$ singularities!
-\centering Why?
-
-\vspace{0.5cm}
-
-\pause[3]
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering Symmetry breaking}
-The $\beta$ singularities observed are connected to the symmetry breaking of the wave function.
-\end{beamerboxesrounded}
-
-\end{frame}
+\section{Conclusion}
 
@@
 
+\vspace{0.5cm}
+
 \pause[2]
 
-\vspace{0.5cm}
-
-But there is an other secret application of exceptional points...
-
-\pause[3]
-
-\vspace{0.5cm}
-
-\begin{beamerboxesrounded}[scheme=foncé]{\centering A new way to excited states energies}
-The exceptionnal points connect ground and excited states in the complex plane. Using those properties one can smoothly morph a ground state in an excited state. 
+\begin{beamerboxesrounded}[scheme=foncé]{\centering Spherium: a theoretical playground}
+We will use the spherium model (two opposite-spin electrons restricted to remain on a surface of a sphere of radius $R$) to investigate the effects of symmetry breaking on singularities.
 \end{beamerboxesrounded}

### 2020-07-07 RapportStage/Rapport.tex
Ajout repository RapportStage

\documentclass[11pt,a4paper]{article}

% définition des marges du document
\setlength{\topmargin}{0cm}
\setlength{\headheight}{0.4cm}
\setlength{\headsep}{0.8cm}
\setlength{\footskip}{1cm}
\setlength{\textwidth}{17cm}
\setlength{\textheight}{25cm}
\setlength{\voffset}{-1.5cm}
\setlength{\hoffset}{-0.5cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}

\usepackage{graphicx} % inclusion des figures
\usepackage{physics}

\usepackage{amsmath} % collection de symboles mathématiques
\usepackage{amssymb} % collection de symboles mathématiques
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc} % codage moderne des caractères sous Latex

\usepackage[english]{babel}
\usepackage{tabularx} % gestion avancée des tableaux

\usepackage{siunitx}
\usepackage[version=4]{mhchem}

\usepackage{color} % gestion de différentes couleurs

\definecolor{linkcolor}{rgb}{0,0,0.6} % définition de la couleur des liens pdf
\usepackage[ pdftex,colorlinks=true,
pdfstartview=FitV,
linkcolor= linkcolor,
citecolor= linkcolor,
urlcolor= linkcolor,
hyperindex=true,
hyperfigures=false]
{hyperref} % fichiers pdf 'intelligents', avec des liens entre les références, etc.
\usepackage{fancyhdr} % entêtes et pieds de pages personnalisés

% définition de l'entête et du pied de page
\pagestyle{fancy}
\fancyhead[L]{\scriptsize \textsc{Perturbation theory in the complex plane}}
\fancyhead[R]{\scriptsize \textsc{Antoine \textsc{MARIE}}}
\fancyfoot[C]{ \thepage}

% commande d'annulation du correcteur typographique du package [francais]{babel} qui force l'espace avant ':' (parfois utile pour la bibliographie)
\makeatletter
\@ifpackageloaded{babel}%
        {\newcommand{\nospace}[1]{{\NoAutoSpaceBeforeFDP{}#1}}}%  % !! double {{}} pour cantonner l'effet à l'argument #1 !!
        {\newcommand{\nospace}[1]{#1}}
\makeatother

% commande de déplacement d'un objet
\newcommand{\drawat}[3]{\makebox[0pt][l]{\raisebox{#2}{\hspace*{#1}#3}}}

\newcommand{\bH}{\mathbf{H}}
\newcommand{\bV}{\mathbf{V}}

\begin{document}

% Pour faciliter la mise en forme de la page du titre, on supprime l'indentation automatique en début de paragraphe
\setlength{\parindent}{0pt}

% Pas d'en-tête ni de pied pour la première page
\thispagestyle{empty}

\includegraphics[height=2cm]{logoens.eps} \hfill \includegraphics[height=2cm]{logoucbl.eps} \hfill \includegraphics[height=2cm]{logounivlyon.eps}
\vspace{0.5cm}

\begin{tabularx}{\textwidth}{@{} l X l @{} }
{\sc Licence / Master Science de la matière} & & Stage 2019-2020 \\
{\it École Normale Supérieure de Lyon} & & Antoine \textsc{MARIE} \\
{\it Université Claude Bernard Lyon I} & & M1 Chimie
\end{tabularx}

\begin{center}

\vspace{1.5cm}

\rule[11pt]{5cm}{0.5pt}

\textbf{\huge Pertubation theories in the complex plane}

\rule{5cm}{0.5pt}

\vspace{1.5cm}

\parbox{15cm}{\small
\textbf{Abstract} : \it Un résumé de 10 lignes environ du contenu du rapport, permettant de situer le sujet et les résultats principaux du stage
}

\parbox{15cm}{
\textbf{Keywords} : \it perturbation theory, Hartree-Fock, spherium, exceptional points
} %fin de la commande \parbox des mots clefs

\vspace{0.5cm}

\parbox{15cm}{
Internship supervisor:

{\bf Pierre-François \textsc{LOOS}}

\href{mailto:loos@irsamc.ups-tlse.fr}{\tt loos@irsamc.ups-tlse.fr} / tél. (+33) 5 61 55 73 39

Laboratoire de Chimie et Physique Quantiques

{\it 118, route de Narbonne

31062 Toulouse - France}

\url{https://www.irsamc.ups-tlse.fr/}
} %fin de la commande \parbox encadrant / laboratoire d'accueil

\vspace{0.5cm}
\includegraphics[height=2cm]{LCPQ_logo.pdf} \hfill \includegraphics[height=2cm]{LogoCNRS.eps} \hfill \includegraphics[height=2cm]{UPS_logo.jpg}

\end{center}

\vfill
\hfill \today

\newpage

\section*{Acknowledgments}

\tableofcontents

\newpage

%============================================================%
\section{Introduction}
%============================================================%

It has always been of great importance for theoretical chemists to better understand excited states and their properties because processes involving excited states are ubiquitous in nature (physics, chemistry and biology). One of the major challenges is to accurately compute excited states energies. Plenty of methods have been developed to this aim and each of them have its own qualities but also its own flaws. The fact that none of all those methods is succesfull for every molecule in every geometry encourage chemists to continue the development of new methodologies to get accurate energies and to try to understand deeply why each methods fails or not with each molecule. All those methods rely on the notion of quantised energy levels of Hermitian quantum mechanics. In quantum chemistry, the ordering of the energy levels represents the different electronic states of a molecule, the lowest being the ground state while the higher ones are the so-called excited states. And we need methods to get accurately how those states are ordered.

Within this quantised paradigm, electronic states look completely disconnected from one another.
However, one can gain a different perspective on quantisation if one extends quantum chemistry into the complex domain.
In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.

Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), one can smoothly connect the ground and excited states of a molecule.
This connection is possible because, by extending real numbers to the complex domain, one loses the ordering property of real numbers.
Hence, one can interchange electronic states away from the real axis, as the concept of ground and excited states has been lost.
Amazingly, this smooth and continuous transition from one state to another has been recently realized experimentally in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics. \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}

Exceptional points (EPs) \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016} are non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996} where two states become exactly degenerate.
CIs are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to CIs in the decay of bound excited states.
Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
For example, by encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the starting wave function.
In contrast, encircling Hermitian degeneracies at CIs introduces only a geometric phase while leaving the states unchanged.
More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane. \cite{Olsen_1996, Olsen_2000}

%============================================================%
\section{Perturbation theory}
%============================================================%

Within perturbation theory, the Schr\"odinger equation is usually rewritten as 
\begin{equation}
	\bH(\lambda) \Psi = (\bH^{(0)} + \lambda \bV ) \Psi(\lambda) = E(\lambda) \Psi,
\end{equation}
with
\begin{equation}
\bV=\bH - \bH^{(0)}
\end{equation}
The energy can then be written as a power series of $\lambda$
\begin{equation}
	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}
\end{equation}
where $\lambda$ is a coupling parameter set equal to 1 at the end of the calculation. However it is not guaranteed that the series $E(\lambda)$ has a radius of convergence $\abs{\lambda_0} < 1$. It means that the series is divergent for the physical system at $\lambda=1$. One can prove that $\abs{\lambda_0}$ can be obtained by extending $\lambda$ in the complex plane and looking for the singularities of $E(\lambda)$. The radius of convergence of the expansion of a function is equal to the distance of the closest singularities in the complex plane to the origin. These singularities are nothing but EPs at $\lambda_0$ and $\lambda_0^*$. Indeed, for a Hermitian Hamiltonian the singularities occur in complex conjugate pairs with non-zero imaginary parts.

 The discovery of a partitioning of the Hamiltonian that allowed chemists to get access to a part of the correlation energy using perturbation theory has been a major step in the development of post-Hartree-Fock methods. This case of the Rayleigh-Schrödinger perturbation theory is called the M{\o}ller-Plesset perturbation theory. In the MPPT the unperturbed Hamiltonian is the sum of the $n$ mono-electronic Fock operators which are the sum of the one-electron core Hamiltonian $h(i)$, the Coulomb $J_j(i)$ and Exchange $K_j(i)$ operators.

\begin{equation}
H_0= \sum\limits_{i=1}^{n} f(i)
\end{equation}

\begin{equation}
f(i) = h(i) + \sum\limits_{j=1,j \neq i}^{n} \left[J_j(i) - K_j(i)\right]
\end{equation}

In Hartree-Fock theory you approximate the exact wave function as a Slater-determinant (which is an anti-symmetric combination of mono-electronic orbitals) and those wave functions are eigenvectors of the Fock operators. In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1. We will refer to there energy up to the n-th order as the MPn energy. The MP1 energy is the Hartree-Fock energy and the correlation energy is getting recovered from the MP2 level.

\begin{equation}
E_{\text{MP\textsubscript{n}}}= \sum_{k=0}^n E^{(k)}
\end{equation}

But \textit{a priori} there is no reason that this power series is always convergent for $\lambda$=1 when n goes to infinity. In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results. A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable. By doing this the Hamiltonian and the energy become functions of this variable. So by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MPPT. Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction. The direct computation of the terms of the series is relatively easy up to the 4th order and the 5th and 6th order can be obtained at high cost. But to understand deeply the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series. For small systems we can have access to the whole series using Full Configuration Interaction. If you diagonalize the Hamiltonian $H(\lambda)$ in the FCI basis you get the exact energies (in this finite basis set) and expanding in $\lambda$ allow you to get the M{\o}ller-Plesset perturbation series at every order.

%============================================================%
\section{Historical overview}
%============================================================%

\subsection{Behavior of the M{\o}ller-Plesset series}

First the chemists hoped that each time you compute a term of higher order of the perturbation expansion the energy would be more accurate. If this was true it would give a direct method to the exact energy in a finite basis. But rapidly some strange behaviors of the series have been exhibited. In the late 80's Gill et al. have reported deceptive and slow convergences in stretch systems. In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are able to compute only few terms (for example here RMP5 is worse than RMP4).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

The unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but it is very slow so we can't use it for real systems where we can compute only the first terms. When a bond is stretched the exact function undergo a symmetry breaking becoming multi-reference during this process. A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same, which allow a better description of symmetry broken system the series doesn't give accurate results at low orders. In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which lead to spin contamination. Gill et al. highlighted that there is a link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as it's shown below.

\begin{table}[h!]
    \centering
    \begin{tabular}{c c c c c c c}
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\end{tabular}
    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set.}
    \label{tab:my_label}
\end{table}

This problem was preoccupying in order to develop a method that would allow to compute exact energies for all systems using perturbation theory. But in fact it could be expected as it was known that the perturbation theory was not working well if the wave functions eigenvectors of $H_0$ are bad approximations of the exact wave functions. But Olsen et al. have discovered even more preoccupying behavior of the MP series in the late 90's. They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF}.

\begin{figure}[h!]
    \includegraphics[height=5.5cm]{Nedivergence.png}
    \hfill
    \includegraphics[height=5.5cm]{HFdivergence.png}
    \hfill
    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets.}
    \label{fig:my_label}
\end{figure}

When the basis sets is augmented with diffuse functions the series are becoming divergent. This is a really worrying observation because chemists want to work in the largest basis set possible to model the complete basis set. They have shown that those divergences were due to a backdoor intruder state i.e. a pair of singularity in the negative half plane. Their method to investigate links between singularities and those behaviors of the series is to scan energies on the real axis to list the avoided crossings. An avoided crossing on the real axis is indicative of a pair of complex conjugate singularities, their real parts are equal to the value of $\lambda$ at the minimum difference of energy of the avoided crossing. Then modeling an avoided crossing with a two level model, they get an approximation of the pair of singularities by finding the EPs of the two-state model. When the basis set is augmented with diffuse functions the ground state undergoes a shark avoided crossing with a diffuse state on the negative real axis. When there are enough diffuse function in the basis set this pair of singularities is in the unit circle causing the divergence of the series. Olsen and his coworkers conclude that the divergence of the series in those case was due to the interaction of the ground state with a highly diffuse state. 
They also analyzed the convergence of the series for the \ce{CH_2} as an example molecule containing low-lying doubly excited states. In this molecule the doubly excited states are strongly interacting with the ground state because they have the same spatial and spin symmetry. Thus the single reference wave function is a poor approximation. They have shown that there is a singularity close to the unit circle resulting from an interaction with the lowest doubly excited states and that this singularity is causing the slow convergence for the series of \ce{CH_2}.

\subsection{The singularity structure}

In the 2000's Sergeev and Goodson analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and his co-workers were trying to find the singularity causing the divergence. They regroup singularities in two classes: the $\alpha$ singularities which have unit order imaginary parts and the $\beta$ singularities which have very small imaginary parts. The singularities $\alpha$ are related to large avoided crossing between the ground state and a low-lying excited states. Whereas the singularities $\beta$ come from a sharp avoided crossing between the ground state and a highly diffuse state. They used the work of Stillinger to explain the physical signification of those $\beta$ singularities. 
The M{\o}ller-Plesset Hamiltonian is defined as above and by reassembling the term we get the expression (10).

\begin{equation}
H(\lambda)=H_0 + \lambda (H_\text{phys} - H_0)    
\end{equation}

\begin{equation}
    H_\text{phys}=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}\right]
\end{equation}

\begin{equation}
    H_0=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+V_j^{(scf)}\right]
\end{equation}

\begin{equation}
    H(\lambda)=\sum\limits_{j=1}^{n}\left[-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|} + (1-\lambda)V_j^{(scf)}+\lambda\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|} \right]
\end{equation}

The first two terms, the kinetic energy and the electron-nucleus attraction, form the mono-electronic core Hamiltonian which is independant of $\lambda$. The third term is the mean field repulsion of the Hartree-Fock calculation done to get $H_0$ and the last term is the Coulomb repulsion. If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stay repulsive as it is proportional to $(1-\lambda)$. If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus can't bind anymore the electrons because the electron-nucleus attraction is not scaled with $\lambda$. But the repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nucleus. So there is a real negative value $\lambda_c$ where the electron form a bound cluster and goes to infinity. According to Baker this value is a critical point of the system and by analogy with thermodynamics the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$. Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.

This reasoning is done on the exact Hamiltonian and energy, this is the exact energy which exhibits this singularity on the negative real axis. But in finite basis set, one can prove that for a Hermitian Hamiltonian the singularities of $E(\lambda)$ occurs in complex conjugate pair with non-zero imaginary parts. Sergeev and Goodson proved that, as predicted by Stillinger, in a finite basis set the critical point on the real axis modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.

Finally, it has been shown that $\beta$ singularities are very sensitive to the basis sets but not to stretching of the system. On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult. To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function haven't been as well understood as the ionization effect and its link with diffuse function. In this work we try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.

%============================================================%
\section{The spherium model}
%============================================================%

\end{document}

### 2020-07-10 RapportStage/Rapport.tex
update

@@
 \parbox{15cm}{\small
-\textbf{Abstract} : \it Un résumé de 10 lignes environ du contenu du rapport, permettant de situer le sujet et les résultats principaux du stage
+\textbf{Abstract} : \it 
 }
@@
  The discovery of a partitioning of the Hamiltonian that allowed chemists to get access to a part of the correlation energy using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
-This case of the Rayleigh-Schrödinger perturbation theory is called the M{\o}ller-Plesset perturbation theory.
+This case of the Rayleigh-Schrödinger perturbation theory is called the M{\o}ller-Plesset perturbation theory \cite{Moller_1934}.
 In the MPPT the unperturbed Hamiltonian is the sum of the $n$ mono-electronic Fock operators which are the sum of the one-electron core Hamiltonian $h(i)$, the Coulomb $J_j(i)$ and Exchange $K_j(i)$ operators.
@@
 But \textit{a priori} there is no reason that this power series is always convergent for $\lambda$=1 when n goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1998, Handy_1985,Leininger_2000}.
 A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
@@
 In the late 80's Gill et al.
-have reported deceptive and slow convergences in stretch systems.
+have reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1998, Handy_1985,Leininger_2000}.
 In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are able to compute only few terms (for example here RMP5 is worse than RMP4).
@@
 The unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but it is very slow so we can't use it for real systems where we can compute only the first terms.
-When a bond is stretched the exact function undergo a symmetry breaking becoming multi-reference during this process.
-A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same, which allow a better description of symmetry broken system the series doesn't give accurate results at low orders.
+When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
+A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allow a better description of symmetry broken system the series doesn't give accurate results at low orders.
 In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which lead to spin contamination.
@@
 \end{table}
+
+Cremer and He performed the same analysis with 29 FCI systems and the regroup all the systems in two classes.
+The class A systems which have a monotonic convergence to the FCI value and the class B which converge erraticly after initial oscillations.
 
@@
 
+\subsection{The physics of quantum phase transition}
+
 %============================================================%
@@
 
+\newpage
+
+\bibliographystyle{unsrt}
+\bibliography{Rapport}
+
 \end{document}

### 2020-07-10 RapportStage/Rapport.tex
update friday

@@
 \usepackage{graphicx} % inclusion des figures
+\usepackage{tabularx} % gestion avancée des tableaux
+
 \usepackage{physics}
-
 \usepackage{amsmath} % collection de symboles mathématiques
 \usepackage{amssymb} % collection de symboles mathématiques
+
 \usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc} % codage moderne des caractères sous Latex
+\usepackage[T1]{fontenc}
+\DeclareUnicodeCharacter{2212}{-}
 
 \usepackage[english]{babel}
-\usepackage{tabularx} % gestion avancée des tableaux
 
@@
 
-\usepackage{color} % gestion de différentes couleurs
+\usepackage{xcolor} % gestion de différentes couleurs
 
@@
 \parbox{15cm}{\small
-\textbf{Abstract} : \it 
+\textbf{Abstract} : \it In this work, we explore the description of quantum chemistry in the complex plane.
+We see that the physic of the system can be connected to the position of the singularities of the energy in the complex plane.
+After briefly present the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we perform an historical review of the researches that have been done on the physic of singularities.
+Then we make links between all those points of view on this problem using the spherium model (i.e., two opposite-spin electrons restricted to remain on a surface of a sphere of radius $R$) as a theoretical playground.
+In particular, we explore the effects of symmetry breaking of the wave functions on the singularity structure.
 }
 
+\vspace{0.5cm}
+
 \parbox{15cm}{
-\textbf{Keywords} : \it perturbation theory, Hartree-Fock, spherium, exceptional points
+\textbf{Keywords} : \it Complex chemistry, Perturbation theory,  Spherium, Exceptional points, Symmetry breaking
 } %fin de la commande \parbox des mots clefs
@@
 It has always been of great importance for theoretical chemists to better understand excited states and their properties because processes involving excited states are ubiquitous in nature (physics, chemistry and biology).
-One of the major challenges is to accurately compute excited states energies.
+One of the major challenges is to accurately compute energies of a chemical system (atoms, molecules, ..).
 Plenty of methods have been developed to this aim and each of them have its own qualities but also its own flaws.
-The fact that none of all those methods is succesfull for every molecule in every geometry encourage chemists to continue the development of new methodologies to get accurate energies and to try to understand deeply why each methods fails or not with each molecule.
+The fact that none of all those methods is successful for every molecule in every geometry encourage chemists to continue the development of new methodologies to get accurate energies and to try to understand deeply why each methods fails or not in each situation.
 All those methods rely on the notion of quantised energy levels of Hermitian quantum mechanics.
@@
 But \textit{a priori} there is no reason that this power series is always convergent for $\lambda$=1 when n goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1998, Handy_1985,Leininger_2000}.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
 A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
@@
 
-First the chemists hoped that each time you compute a term of higher order of the perturbation expansion the energy would be more accurate.
-If this was true it would give a direct method to the exact energy in a finite basis.
-But rapidly some strange behaviors of the series have been exhibited.
+When you use M{\o}ller-Plesset perturbation theory it would be very convenient that each time you compute a term of higher order the result obtained is closer to exact energy.
+In other words that the M{\o]ller-Plesset series would be monotonically convergent.
+Assuming this the only limiting process to get the exact correlation energy in a finite basis is our ability to compute the terms of the perturbation series.
+Unfortunately this not true in generic cases and rapidly some strange behaviors of the series have been exhibited.
 In the late 80's Gill et al.
-have reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1998, Handy_1985,Leininger_2000}.
+have reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
 In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are able to compute only few terms (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we can't use it for systems where we can compute only the first terms.
 
@@
     \includegraphics[width=0.45\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$)\cite{Gill_1986}.}
     \label{fig:my_label}
@@
 
-The unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but it is very slow so we can't use it for real systems where we can compute only the first terms.
 When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
 A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allow a better description of symmetry broken system the series doesn't give accurate results at low orders.
+Even with this improvement of the zeroth order wave function the series doesn't have the smooth and rapidly converging behavior wanted.
+
 In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which lead to spin contamination.
 Gill et al.
-highlighted that there is a link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as it's shown below.
+highlighted that there is a link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as it's shown in the Table 1 within the example of \ce{H_2} in a minimal basis.
 
@@
 \end{tabular}
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set.}
+    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set \cite{Gill_1988}.}
     \label{tab:my_label}
@@
 
-Cremer and He performed the same analysis with 29 FCI systems and the regroup all the systems in two classes.
-The class A systems which have a monotonic convergence to the FCI value and the class B which converge erraticly after initial oscillations.
+Handy and co-workers.
+exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
+Cremer and He performed the same analysis with 29 FCI systems \cite{Cremer_1996} and regrouped all the systems in two classes.
+The class A systems which have a monotonic convergence to the FCI value and the class B which converge erratically after initial oscillations.
+The sample of systems contains stretched molecules and also some at equilibrium geometry, there are also some systems in various basis sets.
+They highlighted that systems with class A convergence have well-separated electrons pairs whereas class B systems present electrons clustering.
 
-This problem was preoccupying in order to develop a method that would allow to compute exact energies for all systems using perturbation theory.
-But in fact it could be expected as it was known that the perturbation theory was not working well if the wave functions eigenvectors of $H_0$ are bad approximations of the exact wave functions.
+This classification was encouraging in order to develop methods based on perturbation theory as it rationalize the two different convergence modes observed.
+If it is possible to predict if a system is class A or B, then one can use extrapolation method of the first terms adapted to the class of the systems \cite{Cremer_1996}.
+
+\subsection{Cases of divergence}
+
 But Olsen et al.
 have discovered even more preoccupying behavior of the MP series in the late 90's.
-They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF}.
+They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
+Cremer and He had already studied those two systems and classified them as class B systems.
+But Olsen and his co-workers have done the analysis in larger basis sets containing diffuse functions and in those basis sets the series become divergent at high order.
 
@@
 
-When the basis sets is augmented with diffuse functions the series are becoming divergent.
-This is a really worrying observation because chemists want to work in the largest basis set possible to model the complete basis set.
+The discovery of those divergent behavior was really worrying because to get more and more accurate results theoretical chemists need to work in large basis sets.
+So they investigated the causes of those divergences and in the same time the reasons of the different types of convergence.
+In order to do this they analyzed the relation between the dominant singularity (i.e.
+the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
+A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
+The method used is to do a scan of the real axis to identify the avoided crossing responsible for the pair of dominant singularity.
+Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the 2x2 Hamiltonian.
+The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbation part of the Hamiltonian.
+
+\begin{equation}
+\mqty(\alpha & \delta \\ \delta & \beta) = \mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s ) + \mqty(- \alpha_s & \delta \\ \delta & - \beta_s)
+\end{equation}
+
 They have shown that those divergences were due to a backdoor intruder state i.e.

### 2020-07-13 RapportStage/Rapport.tex
update

@@
 \parbox{15cm}{
-\textbf{Keywords} : \it Complex chemistry, Perturbation theory,  Spherium, Exceptional points, Symmetry breaking
+\textbf{Keywords} : \it Quantum chemistry, Perturbation theory,  Spherium, Exceptional points, Symmetry breaking
 } %fin de la commande \parbox des mots clefs
@@
 One can prove that $\abs{\lambda_0}$ can be obtained by extending $\lambda$ in the complex plane and looking for the singularities of $E(\lambda)$.
-The radius of convergence of the expansion of a function is equal to the distance of the closest singularities in the complex plane to the origin.
-These singularities are nothing but EPs at $\lambda_0$ and $\lambda_0^*$.
-Indeed, for a Hermitian Hamiltonian the singularities occur in complex conjugate pairs with non-zero imaginary parts.
+This is due to the following theorem \cite{Goodson_2011}: The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
+If the function has a singular point $z_s$ such that $\abs{z_s − z_0} < \abs{z_1 − z_0}$, then the series will diverge when evaluated at $z_1$.
+This theorem means that the radius of convergence of the perturbation series is equal to distance to the origin of the closest singularity of $E(\lambda)$.
 
- The discovery of a partitioning of the Hamiltonian that allowed chemists to get access to a part of the correlation energy using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
+The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a part of the correlation energy (i.e.
+the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
 This case of the Rayleigh-Schrödinger perturbation theory is called the M{\o}ller-Plesset perturbation theory \cite{Moller_1934}.
@@
 
-In Hartree-Fock theory you approximate the exact wave function as a Slater-determinant (which is an anti-symmetric combination of mono-electronic orbitals) and those wave functions are eigenvectors of the Fock operators.
+In Hartree-Fock theory the exact wave function is approximated as a Slater-determinant (which is an anti-symmetric combination of mono-electronic orbitals) and those wave functions are eigenvectors of the Fock operators.
 In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1.
 We will refer to there energy up to the n-th order as the MPn energy.
-The MP1 energy is the Hartree-Fock energy and the correlation energy is getting recovered from the MP2 level.
+The MP0 energy overestimate the energy by double counting the electron-electron interaction, the MP1 correct this effect and the MP1 energy is equal to the Hartree-Fock energy.
+The MP2 energy start to recover a part of the correlation energy.
 
@@
 
-But \textit{a priori} there is no reason that this power series is always convergent for $\lambda$=1 when n goes to infinity.
+But as mentioned before \textit{a priori} there are no reasons that this power series is always convergent for $\lambda$=1 when n goes to infinity.
 In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
@@
 By doing this the Hamiltonian and the energy become functions of this variable.
-So by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MPPT.
+By doing this the energy become a multivalued function on $n$ Riemann sheets.
+As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MPPT.
 Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
@@
 For small systems we can have access to the whole series using Full Configuration Interaction.
-If you diagonalize the Hamiltonian $H(\lambda)$ in the FCI basis you get the exact energies (in this finite basis set) and expanding in $\lambda$ allow you to get the M{\o}ller-Plesset perturbation series at every order.
+If you diagonalize the Hamiltonian $H(\lambda)$ in the FCI basis set you get the exact energies (in this finite basis set) and expanding in $\lambda$ allow you to get the M{\o}ller-Plesset perturbation series at every order.
 
@@
 
-The discovery of those divergent behavior was really worrying because to get more and more accurate results theoretical chemists need to work in large basis sets.
+The discovery of those divergent behavior was really worrying because in order to get more and more accurate results theoretical chemists need to work in large basis sets.
 So they investigated the causes of those divergences and in the same time the reasons of the different types of convergence.
@@
 the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
+Their analysis is based on Darboux's theorem: In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
+Following the result of this theorem, one can explain the convergence patterns of the MP series by looking at the dominant singularity
+
 A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
@@
 
-They have shown that those divergences were due to a backdoor intruder state i.e.
-a pair of singularity in the negative half plane.
-Their method to investigate links between singularities and those behaviors of the series is to scan energies on the real axis to list the avoided crossings.
-An avoided crossing on the real axis is indicative of a pair of complex conjugate singularities, their real parts are equal to the value of $\lambda$ at the minimum difference of energy of the avoided crossing.
-Then modeling an avoided crossing with a two level model, they get an approximation of the pair of singularities by finding the EPs of the two-state model.
-When the basis set is augmented with diffuse functions the ground state undergoes a shark avoided crossing with a diffuse state on the negative real axis.
-When there are enough diffuse function in the basis set this pair of singularities is in the unit circle causing the divergence of the series.
-Olsen and his coworkers conclude that the divergence of the series in those case was due to the interaction of the ground state with a highly diffuse state.
-They also analyzed the convergence of the series for the \ce{CH_2} as an example molecule containing low-lying doubly excited states.
-In this molecule the doubly excited states are strongly interacting with the ground state because they have the same spatial and spin symmetry.
-Thus the single reference wave function is a poor approximation.
-They have shown that there is a singularity close to the unit circle resulting from an interaction with the lowest doubly excited states and that this singularity is causing the slow convergence for the series of \ce{CH_2}.
+They first studied molecules with low-lying doubly excited states of the same spatial and spin symmetry because in those systems the HF wave function is a bad approximation.
+The exact wave function have non-negligible contribution from the doubly excited states so those low-lying excited states were good candidates for being intruder states.
+For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
+They have shown that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
+
+Then they have shown that the divergence for the \ce{Ne} is due to a back-door intruder state.
+When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back door intruder state.
+They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series.
+They conclude that the divergence of the series was due to the interaction with a highly diffuse excited states.
+
+Moreover they proved that the extrapolation formula of Cremer and He \cite{Cremer_1996} can't be used for all systems.
+Even more that those formula were not mathematically motivated when one look at the singularity causing the divergence.
+For example the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly excited states which result in alternated terms up to order 10 and then the series is monotonically convergent.
+This is due to the fact that two pairs of singularity are approximately at the same distance of the origin.
 
@@
 
-In the 2000's Sergeev and Goodson analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and his co-workers were trying to find the singularity causing the divergence.
+In the 2000's Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006}  analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and his co-workers were trying to find the dominant singularity causing the divergence.
 They regroup singularities in two classes: the $\alpha$ singularities which have unit order imaginary parts and the $\beta$ singularities which have very small imaginary parts.
@@
 Whereas the singularities $\beta$ come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They used the work of Stillinger to explain the physical signification of those $\beta$ singularities.
-The M{\o}ller-Plesset Hamiltonian is defined as above and by reassembling the term we get the expression (10).
+They succeed to explain the divergence of the series caused by $\beta$ singularities using a previous work of Stillinger \cite{Stillinger_2000}.
+
+The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression (10).
 
@@
 Sergeev and Goodson proved that, as predicted by Stillinger, in a finite basis set the critical point on the real axis modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+They explain that Olsen et al., because they used a 2x2 model, only observed the first singularity of this cluster of singularities causing the divergence.
 
@@
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult.
+According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult \cite{Goodson_2004}, this is conform with the observation of Olsen and co-workers on the \ce{HF} molecule at equilibrium geometry and stretched geometry \cite{Olsen_2000}.
 To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function haven't been as well understood as the ionization effect and its link with diffuse function.

### 2020-07-13 RapportStage/Rapport.tex
update

@@
 \textbf{Abstract} : \it In this work, we explore the description of quantum chemistry in the complex plane.
-We see that the physic of the system can be connected to the position of the singularities of the energy in the complex plane.
-After briefly present the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we perform an historical review of the researches that have been done on the physic of singularities.
-Then we make links between all those points of view on this problem using the spherium model (i.e., two opposite-spin electrons restricted to remain on a surface of a sphere of radius $R$) as a theoretical playground.
+We see that the physics of the system can be connected to the position of the energy singularities in the complex plane.
+After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we perform an historical review of the researches that have been done on the physic of singularities.
+Then we connect all those points of view on this problem using the spherium model (i.e., two opposite-spin electrons restricted to remain on the surface of a sphere of radius $R$) as a theoretical playground.
 In particular, we explore the effects of symmetry breaking of the wave functions on the singularity structure.
@@
 One of the major challenges is to accurately compute energies of a chemical system (atoms, molecules, ..).
-Plenty of methods have been developed to this aim and each of them have its own qualities but also its own flaws.
-The fact that none of all those methods is successful for every molecule in every geometry encourage chemists to continue the development of new methodologies to get accurate energies and to try to understand deeply why each methods fails or not in each situation.
+Plenty of methods have been developed to this end and each of them have its own advantages but also its own flaws.
+The fact that none of all those methods is successful for every molecule in every geometry encourages chemists to continue the development of new methodologies to get accurate energies and to try to deeply understand why each method fails or not in each situation.
 All those methods rely on the notion of quantised energy levels of Hermitian quantum mechanics.
 In quantum chemistry, the ordering of the energy levels represents the different electronic states of a molecule, the lowest being the ground state while the higher ones are the so-called excited states.
-And we need methods to get accurately how those states are ordered.
+We need methods to accurately get how those states are ordered.
 
 Within this quantised paradigm, electronic states look completely disconnected from one another.
-However, one can gain a different perspective on quantisation if one extends quantum chemistry into the complex domain.
+However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
 In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
@@
 
-Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), one can smoothly connect the ground and excited states of a molecule.
-This connection is possible because, by extending real numbers to the complex domain, one loses the ordering property of real numbers.
-Hence, one can interchange electronic states away from the real axis, as the concept of ground and excited states has been lost.
-Amazingly, this smooth and continuous transition from one state to another has been recently realized experimentally in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
+Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
+This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
+Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
+Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
 \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}
@@
 Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
-For example, by encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
-Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the starting wave function.
-In contrast, encircling Hermitian degeneracies at CIs introduces only a geometric phase while leaving the states unchanged.
+For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
+In contrast, encircling Hermitian degeneracies at CIs only introduces a geometric phase while leaving the states unchanged.
 More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
@@
 In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1.
-We will refer to there energy up to the n-th order as the MPn energy.
-The MP0 energy overestimate the energy by double counting the electron-electron interaction, the MP1 correct this effect and the MP1 energy is equal to the Hartree-Fock energy.
-The MP2 energy start to recover a part of the correlation energy.
+We will refer to the energy up to the n-th order as the MPn energy.
+The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the Hartree-Fock energy.
+The MP2 energy starts to recover a part of the correlation energy.
 
@@
 A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
-By doing this the Hamiltonian and the energy become functions of this variable.
-By doing this the energy become a multivalued function on $n$ Riemann sheets.
+By doing so the Hamiltonian and the energy become functions of this variable.
+The energy becomes a multivalued function on $n$ Riemann sheets.
 As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MPPT.
 Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
-The direct computation of the terms of the series is relatively easy up to the 4th order and the 5th and 6th order can be obtained at high cost.
-But to understand deeply the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
+The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost.
+But to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
 For small systems we can have access to the whole series using Full Configuration Interaction.
-If you diagonalize the Hamiltonian $H(\lambda)$ in the FCI basis set you get the exact energies (in this finite basis set) and expanding in $\lambda$ allow you to get the M{\o}ller-Plesset perturbation series at every order.
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and expanding in $\lambda$ allows to to get the M{\o}ller-Plesset perturbation series at every order.
 
@@
 
-When you use M{\o}ller-Plesset perturbation theory it would be very convenient that each time you compute a term of higher order the result obtained is closer to exact energy.
-In other words that the M{\o]ller-Plesset series would be monotonically convergent.
-Assuming this the only limiting process to get the exact correlation energy in a finite basis is our ability to compute the terms of the perturbation series.
-Unfortunately this not true in generic cases and rapidly some strange behaviors of the series have been exhibited.
+When we use M{\o}ller-Plesset perturbation theory it would be very convenient that each time a higher order term is computed the result obtained is closer to exact energy.
+In other words, that the M{\o]ller-Plesset series would be monotonically convergent.
+Assuming this, the only limiting process to get the exact correlation energy in a finite basis set is our ability to compute the terms of the perturbation series.
+Unfortunately this is not true in generic cases and rapidly some strange behaviors of the series were exhibited.
 In the late 80's Gill et al.
-have reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are able to compute only few terms (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we can't use it for systems where we can compute only the first terms.
+reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we can't use it for systems where we can only compute the first terms.
 
@@
 When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
-A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allow a better description of symmetry broken system the series doesn't give accurate results at low orders.
+A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allows a better description of broken symmetry system, the series doesn't give accurate results at low orders.
 Even with this improvement of the zeroth order wave function the series doesn't have the smooth and rapidly converging behavior wanted.
 
-In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which lead to spin contamination.
+In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which leads to spin contamination.
 Gill et al.
-highlighted that there is a link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as it's shown in the Table 1 within the example of \ce{H_2} in a minimal basis.
+highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the Table 1 in the example of \ce{H_2} in a minimal basis.
 
@@
 
-Handy and co-workers.
-exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
+Handy and co-workers exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
 Cremer and He performed the same analysis with 29 FCI systems \cite{Cremer_1996} and regrouped all the systems in two classes.
@@
 
-This classification was encouraging in order to develop methods based on perturbation theory as it rationalize the two different convergence modes observed.
+This classification was encouraging in order to develop methods based on perturbation theory as it rationalizes the two different observed convergence modes.
 If it is possible to predict if a system is class A or B, then one can use extrapolation method of the first terms adapted to the class of the systems \cite{Cremer_1996}.
@@
 
-But Olsen et al.
-have discovered even more preoccupying behavior of the MP series in the late 90's.
+However Olsen et al.
+have discovered an even more preoccupying behavior of the MP series in the late 90's.
 They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
@@
 
-The discovery of those divergent behavior was really worrying because in order to get more and more accurate results theoretical chemists need to work in large basis sets.
-So they investigated the causes of those divergences and in the same time the reasons of the different types of convergence.
-In order to do this they analyzed the relation between the dominant singularity (i.e.
+The discovery of this divergent behavior was really worrying because in order to get more and more accurate results theoretical chemists need to work in large basis sets.
+As a consequence they investigated the causes of those divergences and in the same time the reasons of the different types of convergence.
+To do this they analyzed the relation between the dominant singularity (i.e.
 the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
-Their analysis is based on Darboux's theorem: In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
-Following the result of this theorem, one can explain the convergence patterns of the MP series by looking at the dominant singularity
+Their analysis is based on Darboux's theorem: in the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
+Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.
 
@@
 The method used is to do a scan of the real axis to identify the avoided crossing responsible for the pair of dominant singularity.
-Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the 2x2 Hamiltonian.
-The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbation part of the Hamiltonian.
+Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $22\times$ Hamiltonian.
+The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbative part of the Hamiltonian.
 
@@
 They first studied molecules with low-lying doubly excited states of the same spatial and spin symmetry because in those systems the HF wave function is a bad approximation.
-The exact wave function have non-negligible contribution from the doubly excited states so those low-lying excited states were good candidates for being intruder states.
+The exact wave function has a non-negligible contribution from the doubly excited states, so those low-lying excited states were good candidates for being intruder states.
 For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
-They have shown that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
+They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
 
-Then they have shown that the divergence for the \ce{Ne} is due to a back-door intruder state.
+Then they demonstrated that the divergence for the \ce{Ne} is due to a back-door intruder state.
 When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back door intruder state.
 They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series.
-They conclude that the divergence of the series was due to the interaction with a highly diffuse excited states.
+They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state.
 
 Moreover they proved that the extrapolation formula of Cremer and He \cite{Cremer_1996} can't be used for all systems.
-Even more that those formula were not mathematically motivated when one look at the singularity causing the divergence.
-For example the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly excited states which result in alternated terms up to order 10 and then the series is monotonically convergent.
-This is due to the fact that two pairs of singularity are approximately at the same distance of the origin.
+Even more, that those formula were not mathematically motivated when looking at the singularity causing the divergence.
+For example the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly excited states which results in alternated terms up to order ten and then the series is monotonically convergent.
+This is due to the fact that two pairs of singularity are approximately at the same distance from the origin.
 
@@
 In the 2000's Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006}  analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and his co-workers were trying to find the dominant singularity causing the divergence.
-They regroup singularities in two classes: the $\alpha$ singularities which have unit order imaginary parts and the $\beta$ singularities which have very small imaginary parts.
+They regrouped singularities in two classes: the $\alpha$ singularities which have unit order imaginary parts and the $\beta$ singularities which have very small imaginary parts.
 The singularities $\alpha$ are related to large avoided crossing between the ground state and a low-lying excited states.
 Whereas the singularities $\beta$ come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They succeed to explain the divergence of the series caused by $\beta$ singularities using a previous work of Stillinger \cite{Stillinger_2000}.
+They succeeded to explain the divergence of the series caused by $\beta$ singularities using a previous work of Stillinger \cite{Stillinger_2000}.
 
-The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression (10).
+The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression (11).
 
@@
 The third term is the mean field repulsion of the Hartree-Fock calculation done to get $H_0$ and the last term is the Coulomb repulsion.
-If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stay repulsive as it is proportional to $(1-\lambda)$.
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus can't bind anymore the electrons because the electron-nucleus attraction is not scaled with $\lambda$.
-But the repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nucleus.
-So there is a real negative value $\lambda_c$ where the electron form a bound cluster and goes to infinity.
+If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stays repulsive as it is proportional to $(1-\lambda)$.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus can't bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
+The repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nucleus.
+There is a real negative value $\lambda_c$ where the electrons form a bound cluster and goes to infinity.
 According to Baker this value is a critical point of the system and by analogy with thermodynamics the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
@@
 But in finite basis set, one can prove that for a Hermitian Hamiltonian the singularities of $E(\lambda)$ occurs in complex conjugate pair with non-zero imaginary parts.
-Sergeev and Goodson proved that, as predicted by Stillinger, in a finite basis set the critical point on the real axis modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-They explain that Olsen et al., because they used a 2x2 model, only observed the first singularity of this cluster of singularities causing the divergence.
+Sergeev and Goodson proved, as predicted by Stillinger, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+They explain that Olsen et al., because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
 
-Finally, it has been shown that $\beta$ singularities are very sensitive to the basis sets but not to stretching of the system.
+Finally, it was shown that $\beta$ singularities are very sensitive to the basis sets but not to the stretching of the system.
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult \cite{Goodson_2004}, this is conform with the observation of Olsen and co-workers on the \ce{HF} molecule at equilibrium geometry and stretched geometry \cite{Olsen_2000}.
-To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function haven't been as well understood as the ionization effect and its link with diffuse function.
+According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult \cite{Goodson_2004}, this is consistent with the observation of Olsen and co-workers on the \ce{HF} molecule at equilibrium geometry and stretched geometry \cite{Olsen_2000}.
+To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function hasn't been as well understood as the ionization effect and its link with diffuse function.
 In this work we try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
@@
 
+At a sharp avoided crossings the two eigenstates undergo
+
 %============================================================%
@@
 %============================================================%
+
+Simple systems that are analytically solvable (or at least quasi-exactly solvable) are of great importance in theoretical chemistry.
+Those systems are very useful benchmarks to test new methods as they are mathematically easy but retain much of the key physics.
+To investigate the physics of EPs we use one such system named spherium model.
+It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential.
+The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
+We will use this model to try to rationalize the effects of the variables that may influence the physics of EPs:
+\begin{itemize}
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [restricted Hartree-Fock (RHF) or unrestricted Hartree-Fock (UHF) references, M{\o}ller-Plesset or Epstein-Nesbet (EN) partitioning], or strongly correlated reference.
+	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions
+	\item Radius of the spherium that ultimately dictates the correlation regime.
+\end{itemize}
+
+\subsection{Weak correlation regime}
+
+In the restricted Hartree-Fock formalism, the wave function can't model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
+Then a fortiori it can't represent two electrons on opposite side of the sphere.
+In the unrestricted formalism
+At a critical value of R, called the Coulson-Fischer point, a second unrestricted Hartree-Fock solution appear.
+This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
+By analogy with the case of \ce{H_2} \cite{SzaboBook}, the unrestricted Hartree-Fock wave function is defined as:
+
+Then the mono-electronic wave function are expand in the spatial basis set of the zonal spherical harmonics:
 

### 2020-07-13 RapportStage/Rapport.tex
update monday

@@
 There is a real negative value $\lambda_c$ where the electrons form a bound cluster and goes to infinity.
-According to Baker this value is a critical point of the system and by analogy with thermodynamics the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
+According to Baker this value is a critical point of the system and by analogy with thermodynamics the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$ \cite{Baker_1971}.
+At this point the system undergo a phase transition and a symmetry breaking.
 Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.
@@
 
-At a sharp avoided crossings the two eigenstates undergo
+In the previous section, we seen that a reasoning on the Hamiltonian allows us to predict the existence of a critical point.
+In a finite basis set this critical point is model by a cluster of singularity $\beta$.
+It is now well-known that this phenomenon is a specific case of a more general phenomenon.
+Indeed, theoretical physicist proved that EPs are connected to quantum phase transitions.
+In quantum mechanics, the Hamiltonian is almost always dependent of a parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
+Those quantum phase transitions exist both for ground and excited states.
+A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter.
+The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
+Otherwise, it is called continuous and of n-th order if the n-th derivative is discontinuous.
+A quantum phase transition can also be identify by the discontinuity of an appropriate order parameter (or one of its derivative).
+
+The presence of an EP close to the real axis is characteristic of a sharp avoided crossings.
+Yet at such an avoided crossings eigenstates change abruptly.
+Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarify.
+One of the major challenge in order to do this reside in our ability to compute the distribution of EPs.
+The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions.
+Cejnar et al.
+developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis.
+More recently Stransky and co-workers proved
+
+Ajouter la biblio
+Singularity $\beta$ and quantum phase transition ?
+Coulson-Fisher point second QPT
+Singularity $\beta$ + général
 

### 2020-07-14 RapportStage/Rapport.tex
update tuesday morning

@@
 
-In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which leads to spin contamination.
-Gill et al.
-highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the Table 1 in the example of \ce{H_2} in a minimal basis.
-
 \begin{table}[h!]
@@
 
+In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which leads to spin contamination.
+Gill et al.
+highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the Table 1 in the example of \ce{H_2} in a minimal basis.
 Handy and co-workers exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
-Cremer and He performed the same analysis with 29 FCI systems \cite{Cremer_1996} and regrouped all the systems in two classes.
+Lepetit et al.
+analyzed the difference between the M{\o}ller-Plesset and Epstein-Nesbet partitioning for the unrestricted Hartree-Fock reference \cite{Lepetit_1988}.
+They concluded that the slow convergence is due to the coupling of the single with the double excited configuration.
+Moreover the MP denominators tends towards a constant so each contribution become very small when the bond is stretched.
+
+Cremer and He analyzed 29 FCI systems \cite{Cremer_1996} and regrouped all the systems in two classes.
 The class A systems which have a monotonic convergence to the FCI value and the class B which converge erratically after initial oscillations.
@@
 They highlighted that systems with class A convergence have well-separated electrons pairs whereas class B systems present electrons clustering.
-
 This classification was encouraging in order to develop methods based on perturbation theory as it rationalizes the two different observed convergence modes.
@@
 
-In the previous section, we seen that a reasoning on the Hamiltonian allows us to predict the existence of a critical point.
+In the previous section, we saw that a reasoning on the Hamiltonian allows us to predict the existence of a critical point.
 In a finite basis set this critical point is model by a cluster of singularity $\beta$.
 It is now well-known that this phenomenon is a specific case of a more general phenomenon.
-Indeed, theoretical physicist proved that EPs are connected to quantum phase transitions.
+Indeed, theoretical physicists proved that EPs are connected to quantum phase transitions (citation du stransky 2018 sauf lee).
 In quantum mechanics, the Hamiltonian is almost always dependent of a parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
-Those quantum phase transitions exist both for ground and excited states.
-A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter.
+Those quantum phase transitions exist both for ground and excited states (stransky 2017, cejnar 2006 caprio 2008).
+A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter (cejnar 2009).
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
@@
 Cejnar et al.
-developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis.
-More recently Stransky and co-workers proved
+developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis (citation cejnar 2005 2007).
+More recently Stransky and co-workers proved that the distribution of EPs is not the same around a QPT of first or second order (cite stransky 2018).
+Moreover, that when the dimension of the system increases they tends towards the real axis in a different manner, meaning respectively exponentially and algebraically.
 
-Ajouter la biblio
-Singularity $\beta$ and quantum phase transition ?
-Coulson-Fisher point second QPT
-Singularity $\beta$ + général
+It seems like our understanding of the physics of spatial and/or spin symmetry breaking in the Hartree-Fock theory can be enlightened by quantum phase transition theory.
+Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which mean that the system undergo a second order quantum phase transition.
+The $\beta$ singularities introduced by Sergeev to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+
+Singularity $\alpha$ and quantum phase transition ?
 

### 2020-07-15 RapportStage/Rapport.tex
update wednesday

@@
 Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
-For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy (see Figure 1 for a graphical example).
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
@@
 \cite{Olsen_1996, Olsen_2000}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{TopologyEP.pdf}
+    \caption{\centering A generic EP with the square root branch point topology. A loop around the EP interconvert the states.}
+    \label{fig:my_label}
+\end{figure}
 
@@
 It is now well-known that this phenomenon is a specific case of a more general phenomenon.
-Indeed, theoretical physicists proved that EPs are connected to quantum phase transitions (citation du stransky 2018 sauf lee).
+Indeed, theoretical physicists proved that EPs are connected to quantum phase transitions \cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}.
 In quantum mechanics, the Hamiltonian is almost always dependent of a parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
-Those quantum phase transitions exist both for ground and excited states (stransky 2017, cejnar 2006 caprio 2008).
-A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter (cejnar 2009).
+Those quantum phase transitions exist both for ground and excited states \cite{Cejnar_2009, Sachdev_2011, Cejnar_2016, Cejnar_2006, Caprio_2008, Macek_2019}.
+A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
@@
 Cejnar et al.
-developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis (citation cejnar 2005 2007).
-More recently Stransky and co-workers proved that the distribution of EPs is not the same around a QPT of first or second order (cite stransky 2018).
+developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis \cite{Cejnar_2005, Cejnar_2007}.
+More recently Stransky and co-workers proved that the distribution of EPs is not the same around a QPT of first or second order \cite{Stransky_2018}.
 Moreover, that when the dimension of the system increases they tends towards the real axis in a different manner, meaning respectively exponentially and algebraically.
@@
 
+\section{To do list}
+
+\begin{itemize}
+\item Rajouter label pour les figures et équations cités
+\item Corriger les erreurs dans la biblio
+\item Finir le paragraphe QPT (singularité $\alpha$ ?)
+\end{itemize}
+
 \newpage

### 2020-07-15 RapportStage/Rapport.tex
little update

@@
 In quantum mechanics, the Hamiltonian is almost always dependent of a parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
-Those quantum phase transitions exist both for ground and excited states \cite{Cejnar_2009, Sachdev_2011, Cejnar_2016, Cejnar_2006, Caprio_2008, Macek_2019}.
+Those quantum phase transitions exist both for ground and excited states \cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019}.
 A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
@@
 \item Corriger les erreurs dans la biblio
+\item Changer de bibliographystyle
 \item Finir le paragraphe QPT (singularité $\alpha$ ?)

### 2020-07-15 RapportStage/Rapport.tex
update

@@
 \fancyfoot[C]{ \thepage}
-
-% commande d'annulation du correcteur typographique du package [francais]{babel} qui force l'espace avant ':' (parfois utile pour la bibliographie)
-\makeatletter
-\@ifpackageloaded{babel}%
-        {\newcommand{\nospace}[1]{{\NoAutoSpaceBeforeFDP{}#1}}}%  % !! double {{}} pour cantonner l'effet à l'argument #1 !!
-        {\newcommand{\nospace}[1]{#1}}
-\makeatother
-
-% commande de déplacement d'un objet
-\newcommand{\drawat}[3]{\makebox[0pt][l]{\raisebox{#2}{\hspace*{#1}#3}}}
 
@@
 
+\setlength{\parindent}{17pt}
+
 \section*{Acknowledgments}
@@
 Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
-For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy (see Figure 1 for a graphical example).
+For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy (see \autoref{fig:TopologyEP} for a graphical example).
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
@@
     \caption{\centering A generic EP with the square root branch point topology. A loop around the EP interconvert the states.}
-    \label{fig:my_label}
+    \label{fig:TopologyEP}
 \end{figure}
@@
 reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-In the figure below we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
+In the \autoref{fig:RUMP_Gill} we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
 On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we can't use it for systems where we can only compute the first terms.
@@
     \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$)\cite{Gill_1986}.}
-    \label{fig:my_label}
+    \label{fig:RUMP_Gill}
 \end{figure}
@@
 When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
-A restricted HF Slater determinant is a poor approximation of a broken symmetry wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allows a better description of broken symmetry system, the series doesn't give accurate results at low orders.
+A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series doesn't give accurate results at low orders.
 Even with this improvement of the zeroth order wave function the series doesn't have the smooth and rapidly converging behavior wanted.
@@
     \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set \cite{Gill_1988}.}
-    \label{tab:my_label}
+    \label{tab:SpinContamination}
 \end{table}
@@
 Gill et al.
-highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the Table 1 in the example of \ce{H_2} in a minimal basis.
+highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis.
 Handy and co-workers exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
@@
 The method used is to do a scan of the real axis to identify the avoided crossing responsible for the pair of dominant singularity.
-Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $22\times$ Hamiltonian.
+Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $2\times2$ Hamiltonian.
 The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbative part of the Hamiltonian.
@@
 
-The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression (11).
+The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression \eqref{eq:HamiltonianStillinger}.
 
@@
     H(\lambda)=\sum\limits_{j=1}^{n}\left[-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|} + (1-\lambda)V_j^{(scf)}+\lambda\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|} \right]
+\label{eq:HamiltonianStillinger}
 \end{equation}
@@
 It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential.
+Thus the Hamiltonian is:
+
+\begin{equation}
+\widehat{H} = \frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{\vb{r}_{12}}
+\end{equation}
+
+The laplacian operators are the kinetic operators for each electrons and $\vb{r}_{12}^{-1}$ is the Coulomb operator.
 The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
@@
 
+\subsubsection{Restricted and unrestricted equation for the  spherium model}
+
 In the restricted Hartree-Fock formalism, the wave function can't model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
 Then a fortiori it can't represent two electrons on opposite side of the sphere.
-In the unrestricted formalism
-At a critical value of R, called the Coulson-Fischer point, a second unrestricted Hartree-Fock solution appear.
+In the unrestricted formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second unrestricted Hartree-Fock solution appear.
 This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
@@
 
+\begin{equation}
+\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi(\theta_1)\phi(\pi-\theta_2)
+\end{equation}
+
 Then the mono-electronic wave function are expand in the spatial basis set of the zonal spherical harmonics:
+
+\begin{equation}
+\phi(\theta_1)=\sum\limits_{l=0}^{\infty}C_l\frac{Y_{l0}(\Omega_1)}{R}
+\end{equation}
+
+It is possible to obtain the formula for the ground state unrestricted Hartree-Fock energy in this basis set (see Appendix A for the development):
+
+\begin{equation}
+E_{\text{UHF}} = 2 \sum\limits_{L=0}^{\infty} C_L^2 \frac{L(L+1)}{R^2} + \sum\limits_{i,j,k,l=0}^{\infty}C_iC_jC_kC_l \frac{(-1)^{k+l}S_{i,j,k,l}}{R} \begin{pmatrix}
+ i & j & L \\
+ 0 & 0 & 0
+\end{pmatrix}^2 \begin{pmatrix}
+ k & l & L \\
+ 0 & 0 & 0
+\end{pmatrix}^2
+\label{eq:EUHF}
+\end{equation}
+
+\begin{equation*}
+S_{i,j,k,l}=\sqrt{(2i+1)(2j+1)(2k+1)(2l+1)}
+\end{equation*}
+
+We get an analog result using the same reasoning with the definition of the restricted wave function \eqref{eq: RHFWF}.
+
+\begin{equation}
+\Psi_{\text{RHF}}(\theta_1,\theta_2)=\phi(\theta_1)\phi(\theta_2)
+\label{eq: RHFWF}
+\end{equation}
+
+\begin{equation}
+E_{\text{RHF}} = 2 \sum\limits_{L=0}^{\infty} C_L^2 \frac{L(L+1)}{R^2} + \sum\limits_{i,j,k,l=0}^{\infty}C_iC_jC_kC_l\frac{S_{i,j,k,l}}{R} \begin{pmatrix}
+ i & j & L \\
+ 0 & 0 & 0
+\end{pmatrix}^2 \begin{pmatrix}
+ k & l & L \\
+ 0 & 0 & 0
+\end{pmatrix}^2
+\label{eq:ERHF}
+\end{equation}
+
+\subsubsection{The minimal basis example}
+
+We obtained the equations \eqref{eq:EUHF} and \eqref{eq:ERHF} for general forms of the wave functions, but to be associated with physical wave functions the energy need to be stationary.
+The general method is to use the Hartree-Fock self-consistent field method to get the coefficients of the wave functions corresponding to physical solutions.
+We will work in a minimal basis to illustrate the difference between the RHF and UHF solutions.
+In this basis there is a shortcut to find the stationary solutions.
+One can define the mono-electronic wave function $\phi(\theta_i)$ using a mixing angle between the two basis functions.
+Hence we just need to minimize the energy with respect to $\chi$.
+
+\begin{equation}
+\phi(\theta_1)= \cos(\chi)\frac{Y_{00}(\Omega_1)}{R} + \sin(\chi)\frac{Y_{10}(\Omega_1)}{R}
+\end{equation}
+
+Because the transformation between two basis sets needs to be unitary, we get the other physical solution at the same time:
+
+\begin{equation}
+\phi(\theta_1)= -\sin(\chi)\frac{Y_{00}(\Omega_1)}{R} + \cos(\chi)\frac{Y_{10}(\Omega_1)}{R}
+\end{equation}
+
+\subsubsection{Symmetry-broken solutions}
+
+\subsection{Strongly correlated regime}
+
+\section{Perturbation theory and exceptional points}
 
@@
 \begin{itemize}
-\item Rajouter label pour les figures et équations cités
 \item Corriger les erreurs dans la biblio
@@
 \end{itemize}
+
+\section{Conclusion}
 
@@
 
+\newpage
+\appendix
+
+\section{ERHF and EUHF}
+
 \end{document}

### 2020-07-16 RapportStage/Rapport.tex
update wednesday afternoon
update

@@
 One can prove that $\abs{\lambda_0}$ can be obtained by extending $\lambda$ in the complex plane and looking for the singularities of $E(\lambda)$.
-This is due to the following theorem \cite{Goodson_2011}: The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
+This is due to the following theorem \cite{Goodson_2012}: The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
 If the function has a singular point $z_s$ such that $\abs{z_s − z_0} < \abs{z_1 − z_0}$, then the series will diverge when evaluated at $z_1$.
@@
 
-The presence of an EP close to the real axis is characteristic of a sharp avoided crossings.
-Yet at such an avoided crossings eigenstates change abruptly.
+The presence of an EP close to the real axis is characteristic of a sharp avoided crossing.
+Yet at such an avoided crossing eigen states change abruptly.
 Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarify.
@@
 Cejnar et al.
-developped a method based on a Coulomb analogy giving access to the density of EP close to the real axis \cite{Cejnar_2005, Cejnar_2007}.
+developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis \cite{Cejnar_2005, Cejnar_2007}.
 More recently Stransky and co-workers proved that the distribution of EPs is not the same around a QPT of first or second order \cite{Stransky_2018}.
@@
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in the Hartree-Fock theory can be enlightened by quantum phase transition theory.
-Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which mean that the system undergo a second order quantum phase transition.
+Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which means that the system undergo a second order quantum phase transition.
 The $\beta$ singularities introduced by Sergeev to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
@@
 
+The minimization of the UHF and RHF ground state energies with respect to $\chi$ respectively yiels the following equations:
+
+\begin{equation}
+\frac{2(75+6R-56R\cos(2\chi))\sin(2\chi))}{75R^2}=0
+\label{eq:uhfstatio}
+\end{equation}
+
+\begin{equation}
+\frac{2(75+6R+44R\cos(2\chi))\sin(2\chi))}{75R^2}=0
+\label{eq:rhfstatio}
+\end{equation}
+
+It is evident that those equations are both verified for $\chi=\frac{n\pi}{2}$ with $n$ an integer. Those value of $\chi$ lead to the
+
 \subsubsection{Symmetry-broken solutions}
+
+Apparition of the sb-UHF solution
+Negative R possible, sb-UHF now a maximum
+Less know sb-RHF solution, maximum and minimum inversed
+Charge density wave vs Spin density wave
+
+NRJ graphics
 
@@
 
-\section{Perturbation theory and exceptional points}
+\section{Radius of convergence and exceptional points}
+
+\subsection{Evolution of the radius of convergence}
+
+Different partitioning
+
+$Y_{l0}$ vs $P_l(\cos(\theta))$
+
+Size of the basis set
+
+Strong coupling ???
+
+\subsection{Exceptional points}
+
+RHF vs UHF
+
+UHF spin contamination -> Riemann surfaces ??
+
+UHF: CF point = QPT, ESQPT ???
+
+PT broken symmetry sb UHF
 

### 2020-07-16 RapportStage/Rapport.tex
biber
update thursday

@@
 \setlength{\evensidemargin}{0cm}
+
+\usepackage[
+        backend=biber,
+        style=phys,  
+        mcite=true,
+        subentry,
+        hyperref=true,
+        ]{biblatex}
+\addbibresource{Rapport.bib}
 
@@
 \begin{equation}
-\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi(\theta_1)\phi(\pi-\theta_2)
+\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2)
 \end{equation}
@@
 \begin{equation}
-\phi(\theta_1)=\sum\limits_{l=0}^{\infty}C_l\frac{Y_{l0}(\Omega_1)}{R}
+\phi_\alpha(\theta_1)=\sum\limits_{l=0}^{\infty}C_{\alpha,l}\frac{Y_{l0}(\Omega_1)}{R}
 \end{equation}
@@
 \begin{equation}
-E_{\text{UHF}} = 2 \sum\limits_{L=0}^{\infty} C_L^2 \frac{L(L+1)}{R^2} + \sum\limits_{i,j,k,l=0}^{\infty}C_iC_jC_kC_l \frac{(-1)^{k+l}S_{i,j,k,l}}{R} \begin{pmatrix}
+E_{\text{UHF}} = E_{\text{c},\alpha} + E_{\text{c},\beta} + E_{\text{p}}
+\end{equation}
+
+\begin{equation}
+E_{\text{c},\alpha} = \sum\limits_{l=0}^{\infty} C_{\alpha,l}^2 \frac{l(l+1)}{R^2}
+\end{equation}
+
+\begin{equation}
+E_{\text{p}} = \sum\limits_{i,j,k,l=0}^{\infty}C_{\alpha,i}C_{\alpha,j}C_{\beta,k}C_{\beta,l} \frac{(-1)^{k+l}S_{i,j,k,l}}{R}\sum\limits_{L=0}^{\infty} \begin{pmatrix}
  i & j & L \\
@@
 
-We get an analog result using the same reasoning with the definition of the restricted wave function \eqref{eq: RHFWF}.
-
-\begin{equation}
-\Psi_{\text{RHF}}(\theta_1,\theta_2)=\phi(\theta_1)\phi(\theta_2)
-\label{eq: RHFWF}
-\end{equation}
-
-\begin{equation}
-E_{\text{RHF}} = 2 \sum\limits_{L=0}^{\infty} C_L^2 \frac{L(L+1)}{R^2} + \sum\limits_{i,j,k,l=0}^{\infty}C_iC_jC_kC_l\frac{S_{i,j,k,l}}{R} \begin{pmatrix}
- i & j & L \\
- 0 & 0 & 0
-\end{pmatrix}^2 \begin{pmatrix}
- k & l & L \\
- 0 & 0 & 0
-\end{pmatrix}^2
-\label{eq:ERHF}
-\end{equation}
-
 \subsubsection{The minimal basis example}
 
-We obtained the equations \eqref{eq:EUHF} and \eqref{eq:ERHF} for general forms of the wave functions, but to be associated with physical wave functions the energy need to be stationary.
+We obtained the equation \eqref{eq:EUHF} for the general form of the wave function, but to be associated with a physical wave function the energy need to be stationary with respect to the coefficient.
 The general method is to use the Hartree-Fock self-consistent field method to get the coefficients of the wave functions corresponding to physical solutions.
@@
 In this basis there is a shortcut to find the stationary solutions.
-One can define the mono-electronic wave function $\phi(\theta_i)$ using a mixing angle between the two basis functions.
-Hence we just need to minimize the energy with respect to $\chi$.
+One can define the mono-electronic wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
+Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
 
 \begin{equation}
-\phi(\theta_1)= \cos(\chi)\frac{Y_{00}(\Omega_1)}{R} + \sin(\chi)\frac{Y_{10}(\Omega_1)}{R}
+\phi_\alpha(\theta_1)= \cos(\chi_\alpha)\frac{Y_{00}(\Omega_1)}{R} + \sin(\chi_\alpha)\frac{Y_{10}(\Omega_1)}{R}
 \end{equation}
 
-Because the transformation between two basis sets needs to be unitary, we get the other physical solution at the same time:
+The minimization gives the 3 anticipated solutions (valid for all value of R):
+\begin{itemize}
+\item The two electrons are in the $Y_{00}$ orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
+\item The two electrons are in the $Y_{10}$ orbital which is a RHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$
+\item One electron is in the $Y_{00}$ orbital and the other is in the $Y_{10}$ orbital which is a UHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$
+\end{itemize}
 
-\begin{equation}
-\phi(\theta_1)= -\sin(\chi)\frac{Y_{00}(\Omega_1)}{R} + \cos(\chi)\frac{Y_{10}(\Omega_1)}{R}
-\end{equation}
-
-The minimization of the UHF and RHF ground state energies with respect to $\chi$ respectively yiels the following equations:
-
-\begin{equation}
-\frac{2(75+6R-56R\cos(2\chi))\sin(2\chi))}{75R^2}=0
-\label{eq:uhfstatio}
-\end{equation}
-
-\begin{equation}
-\frac{2(75+6R+44R\cos(2\chi))\sin(2\chi))}{75R^2}=0
-\label{eq:rhfstatio}
-\end{equation}
-
-It is evident that those equations are both verified for $\chi=\frac{n\pi}{2}$ with $n$ an integer. Those value of $\chi$ lead to the
+Vérifier minimum, maximum, point selle
 
@@
 
-Apparition of the sb-UHF solution
-Negative R possible, sb-UHF now a maximum
-Less know sb-RHF solution, maximum and minimum inversed
-Charge density wave vs Spin density wave
+In addition, there is also the well-known symmetry-broken UHF solution.
+For $R>3/2$ an other stationary UHF solution appear, this solution is a minimum.
+This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the other way round.
+The electrons can be on opposite sides of the sphere because the choice of $Y_{10}$ induced a privileged axis on the sphere for the electrons.
+The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
+However this solution gives more accurate results for the energy at large R as shown in Table x.
+In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy leading to this symmetry breaking.
+There is a competition between those two effects: keeping the symmetry of the exact wave function and minimize the energy.
+This type of symmetry breaking is called a spin density wave because the system oscillate between the two symmetry-broken configurations.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{c}
+a
+\end{tabular}
+    \caption{\centering .}
+\label{tab:ERHFvsEUHF}
+\end{table}
+
+There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum.
+This solution is associated with another type of symmetry breaking somewhat well-known.
+Indeed it corresponds to a configuration where both electrons are on the same side of the sphere, in the same orbital.
+This solution is called symmetry-broken RHF.
+At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the $Y_{10}$ orbitals.
+This symmetry breaking is associated with a charge density wave: the system oscillate between the situations with the electrons on each side.
+
+We can also consider negative value of R.
+This corresponds to the situation where one of the electrons is replaced by a positron.
+There are also a sb-RHF and a sb-UHF solution for some values of R but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
+Indeed, the sb-RHF state minimize the energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF state maximize the energy because the two particles are on opposite side of the sphere.
 
@@
 \item Finir le paragraphe QPT (singularité $\alpha$ ?)
+\item tableau nrj uhf, citation spin density wave et charge density wave
 \end{itemize}
@@
 
-\bibliographystyle{unsrt}
-\bibliography{Rapport}
+\printbibliography
 

### 2020-07-16 RapportStage/Rapport.tex
minor corrections

--- 2020-07-16 RapportStage/Rapport.tex
@@
 
-Within perturbation theory, the Schr\"odinger equation is usually rewritten as 
-\begin{equation}
-	\bH(\lambda) \Psi = (\bH^{(0)} + \lambda \bV ) \Psi(\lambda) = E(\lambda) \Psi,
+Within (time-independent) Rayleigh-Schr\"odinger perturbation theory, the Schr\"odinger equation 
+\begin{equation} \label{eq:SchrEq}
+	\bH \Psi = E \Psi
 \end{equation} 
-with
-\begin{equation}
-\bV=\bH - \bH^{(0)}
+is recast as 
+\begin{equation} \label{eq:SchrEq-PT}
+	\bH(\lambda) \Psi(\lambda) = (\bH^{(0)} + \lambda \bV ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
 \end{equation}
-The energy can then be written as a power series of $\lambda$
-\begin{equation}
+where $\bH^{(0)}$ is the zeroth-order Hamiltonian and $\bV = \bH - \bH^{(0)}$ is the so-called perturbation.
+The ``physical'' system of interest is recovered by setting the coupling parameter $\lambda$ to unity.
+This decomposition is obviously non-unique and motivated by several factors as discussed below.
+
+Accordingly to Eq.~\eqref{eq:SchrEq-PT}, the energy can then be written as a power series of $\lambda$
+\begin{equation} \label{eq:Elambda}
 	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}
 \end{equation}
-where $\lambda$ is a coupling parameter set equal to 1 at the end of the calculation.
-However it is not guaranteed that the series $E(\lambda)$ has a radius of convergence $\abs{\lambda_0} < 1$.
-It means that the series is divergent for the physical system at $\lambda=1$.
-One can prove that $\abs{\lambda_0}$ can be obtained by extending $\lambda$ in the complex plane and looking for the singularities of $E(\lambda)$.
-This is due to the following theorem \cite{Goodson_2012}: The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
-If the function has a singular point $z_s$ such that $\abs{z_s − z_0} < \abs{z_1 − z_0}$, then the series will diverge when evaluated at $z_1$.
-This theorem means that the radius of convergence of the perturbation series is equal to distance to the origin of the closest singularity of $E(\lambda)$.
+However it is not guaranteed that the series \eqref{eq:Elambda} has a radius of convergence $\abs{\lambda_0} < 1$. 
+In other words, the series might well be divergent for the physical system at $\lambda = 1$. 
+One can prove that the actual value of the radius of convergence $\abs{\lambda_0}$ can be obtained by looking for the singularities of $E(\lambda)$ in the complex $\lambda$ plane.
+This is due to the following theorem \cite{Goodson_2012}: 
+\begin{quote}
+	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
+If the function has a singular point $z_s$ such that $\abs{z_s − z_0} < \abs{z_1 − z_0}$, then the series will diverge when evaluated at $z_1$.''}
+\end{quote}
+This theorem means that the radius of convergence of the perturbation series is equal to the distance to the origin of the closest singularity of $E(\lambda)$.
 
@@
 In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1.
-We will refer to the energy up to the n-th order as the MPn energy.
+We will refer to the energy up to the $n$-th order as the MP$n$ energy.
 The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the Hartree-Fock energy.
@@
 \begin{equation}
-E_{\text{MP\textsubscript{n}}}= \sum_{k=0}^n E^{(k)}
+E_{\text{MP$_{n}$}}= \sum_{k=0}^n E^{(k)}
 \end{equation}
 
-But as mentioned before \textit{a priori} there are no reasons that this power series is always convergent for $\lambda$=1 when n goes to infinity.
+But as mentioned before \textit{a priori} there are no reasons that this power series is always convergent for $\lambda$=1 when $n$ goes to infinity.
 In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
@@
 \begin{equation}
-\widehat{H} = \frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{\vb{r}_{12}}
+\widehat{H} = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{\vb{r}_{12}}
 \end{equation}
@@
 
-\bibliographystyle{unsrt}
-\bibliography{Rapport}
+%\bibliographystyle{unsrt}
+%\bibliography{Rapport}
+\printbibliography
 

### 2020-07-17 RapportStage/Rapport.tex
modifications in intro

@@
 
-It has always been of great importance for theoretical chemists to better understand excited states and their properties because processes involving excited states are ubiquitous in nature (physics, chemistry and biology).
-One of the major challenges is to accurately compute energies of a chemical system (atoms, molecules, ..).
-Plenty of methods have been developed to this end and each of them have its own advantages but also its own flaws.
-The fact that none of all those methods is successful for every molecule in every geometry encourages chemists to continue the development of new methodologies to get accurate energies and to try to deeply understand why each method fails or not in each situation.
-All those methods rely on the notion of quantised energy levels of Hermitian quantum mechanics.
-In quantum chemistry, the ordering of the energy levels represents the different electronic states of a molecule, the lowest being the ground state while the higher ones are the so-called excited states.
-We need methods to accurately get how those states are ordered.
+Due to the ubiquitous influence of processes involving electronic excited states in physics, chemistry, and biology, their faithful description from first-principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
+Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community.
+An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws. 
+The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new excited-state methodologies, their main goal being to get the most accurate excitation energies (and properties) at the lowest computational cost, and in the most general context.
 
+One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
 Within this quantised paradigm, electronic states look completely disconnected from one another.
+Many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.
 However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
@@
 In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
+One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information.
 

### 2020-07-17 RapportStage/Rapport.tex
saving work in sec 3

@@
 Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
-Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
-\cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}
+Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}.
 
@@
 In contrast, encircling Hermitian degeneracies at CIs only introduces a geometric phase while leaving the states unchanged.
-More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
-More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
-\cite{Olsen_1996, Olsen_2000}
+More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state \cite{MoiseyevBook}.
+More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane \cite{Olsen_1996, Olsen_2000}.
 
@@
 But as mentioned before \textit{a priori} there are no reasons that this power series is always convergent for $\lambda$=1 when $n$ goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
 A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
@@
 When we use M{\o}ller-Plesset perturbation theory it would be very convenient that each time a higher order term is computed the result obtained is closer to exact energy.
-In other words, that the M{\o]ller-Plesset series would be monotonically convergent.
+In other words, that the M{\o}ller-Plesset series would be monotonically convergent.
 Assuming this, the only limiting process to get the exact correlation energy in a finite basis set is our ability to compute the terms of the perturbation series.
 Unfortunately this is not true in generic cases and rapidly some strange behaviors of the series were exhibited.
-In the late 80's Gill et al.
-reported deceptive and slow convergences in stretch systems\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-In the \autoref{fig:RUMP_Gill} we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we can't use it for systems where we can only compute the first terms.
+In the late 80's Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+In \autoref{fig:RUMP_Gill} we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we cannot use it for systems where we can only compute the first terms.
 
@@
     \includegraphics[width=0.45\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$)\cite{Gill_1986}.}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) \cite{Gill_1986}.}
     \label{fig:RUMP_Gill}
@@
 When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
-A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same\cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series doesn't give accurate results at low orders.
-Even with this improvement of the zeroth order wave function the series doesn't have the smooth and rapidly converging behavior wanted.
+A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series does not give accurate results at low orders.
+Even with this improvement of the zeroth order wave function the series does not have the smooth and rapidly converging behavior wanted.
 
@@
 In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which leads to spin contamination.
-Gill et al.
-highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis.
+Gill et al.~highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
 Handy and co-workers exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
-Lepetit et al.
-analyzed the difference between the M{\o}ller-Plesset and Epstein-Nesbet partitioning for the unrestricted Hartree-Fock reference \cite{Lepetit_1988}.
+Lepetit et al.~analyzed the difference between the M{\o}ller-Plesset and Epstein-Nesbet partitioning for the unrestricted Hartree-Fock reference \cite{Lepetit_1988}.
 They concluded that the slow convergence is due to the coupling of the single with the double excited configuration.
@@
 
-Moreover they proved that the extrapolation formula of Cremer and He \cite{Cremer_1996} can't be used for all systems.
+Moreover they proved that the extrapolation formula of Cremer and He \cite{Cremer_1996} cannot be used for all systems.
 Even more, that those formula were not mathematically motivated when looking at the singularity causing the divergence.
@@
 If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stays repulsive as it is proportional to $(1-\lambda)$.
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus can't bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus cannot bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
 The repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nucleus.
@@
 
-In the restricted Hartree-Fock formalism, the wave function can't model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
-Then a fortiori it can't represent two electrons on opposite side of the sphere.
+In the restricted Hartree-Fock formalism, the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
+Then a fortiori it cannot represent two electrons on opposite side of the sphere.
 In the unrestricted formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second unrestricted Hartree-Fock solution appear.

### 2020-07-17 RapportStage/Rapport.tex
update part 3.4 and 4.1

--- 2020-07-16 RapportStage/Rapport.tex
@@
 It is now well-known that this phenomenon is a specific case of a more general phenomenon.
-Indeed, theoretical physicists proved that EPs are connected to quantum phase transitions \cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}.
-In quantum mechanics, the Hamiltonian is almost always dependent of a parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
+Indeed, theoretical physicists proved that EPs close to the real axis are connected to quantum phase transitions \cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}.
+In quantum mechanics, the Hamiltonian is almost always dependent of at least one parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
 Those quantum phase transitions exist both for ground and excited states \cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019}.
@@
 The presence of an EP close to the real axis is characteristic of a sharp avoided crossing.
-Yet at such an avoided crossing eigen states change abruptly.
+Yet at such an avoided crossing eigenstates change abruptly.
 Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarify.
-One of the major challenge in order to do this reside in our ability to compute the distribution of EPs.
-The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions.
+One of the major challenge in order to do this resides in our ability to compute the distribution of EPs.
+The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions so methods are required to get information on the location of EPs.
 Cejnar et al.
@@
 Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which means that the system undergo a second order quantum phase transition.
-The $\beta$ singularities introduced by Sergeev to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
-
-Singularity $\alpha$ and quantum phase transition ?
+Moreover, the $\beta$ singularities introduced by Sergeev to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly.
+However the $\alpha$ singularities arise from large avoided crossings therefore they can not be connected to QPT.
+The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states.
+Those excited states have a non-negligible contribution to the exact FCI solution because they have the same spatial and spin symmetry as the ground state.
+We think that $\alpha$ singularities are connected to the multi-reference behavior of the wave function in the same way as $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function.
 
@@
 The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
-However this solution gives more accurate results for the energy at large R as shown in Table x.
+However this solution gives more accurate results for the energy at large R as shown in \autoref{tab:ERHFvsEUHF}.
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy leading to this symmetry breaking.
@@
 \centering
-\begin{tabular}{c}
-a
+\begin{tabular}{c c c c c c c c c}
+$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
+\hline
+RHF & 10 & 1 & 0.5 & 0.3333 & 0.2 & 0.1 & 0.01 & 0.001 \\
+\hline
+UHF & 10 & 1 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
+\hline
+Exact & 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
 \end{tabular}
-    \caption{\centering .}
+    \caption{\centering RHF and UHF energies in the minimal basis and exact energies for various R.}
 \label{tab:ERHFvsEUHF}
@@
 \item Corriger les erreurs dans la biblio
-\item Changer de bibliographystyle
-\item Finir le paragraphe QPT (singularité $\alpha$ ?)
 \item tableau nrj uhf, citation spin density wave et charge density wave

### 2020-07-17 RapportStage/Rapport.tex
modification part 2

@@
 \newpage
+\thispagestyle{empty}
 
@@
 \newpage
+\setcounter{page}{1}
 
@@
 %============================================================%
+
+\subsection{Background}
 
@@
 
+\subsection{An illustrative example}
+
 %============================================================%
@@
 %============================================================%
+
+\subsection{Rayleigh-Schr\"odinger perturbation theory}
 
@@
 This theorem means that the radius of convergence of the perturbation series is equal to the distance to the origin of the closest singularity of $E(\lambda)$.
+To illustrate this result we  consider the simple function \eqref{eq:DivExample}.
+This function is smooth for $x \in \mathbb{R}$ and infinitely differentiable in $\mathbb{R}$.
+One would expect that the Taylor series of such a function would be convergent for all $x \in \mathbb{R}$, however this series is divergent for $x\geq1$.
+This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}, e^{-i\pi/4}, e^{i3\pi/4}, e^{-i3\pi/4}$) with a modulus equal to 1.
+This simple example shows the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
 
+\begin{equation} \label{eq:DivExample}
+f(x)=\frac{1}{1+x^4}
+\end{equation}
+
+\subsection{The Hartree-Fock Hamiltonian}
+
+In the Born-Oppenheimer approximation, the equation \eqref{eq:ExactHamiltonian} gives the exact electronic Hamiltonian for a chemical system with $n$ electrons and $N$ nuclei.
+The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nuclei attraction and the electron-electron repulsion.
+
+\begin{equation}\label{eq:ExactHamiltonian}
+    \bH=\sum\limits_{i=1}^{n}\left[ -\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}+\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}\right]
+\end{equation}
+
+In the Hartree-Fock (HF) approximation the wave function is approximated as a single Slater determinant (which is an anti-symmetric combination of $n$ one electron spin-orbitals).
+Rather than solving the equation \eqref{eq:SchrEq}, the Hartree-Fock theory use the variational principle to find an approximation to $\Psi$.
+Hence the Slater determinants are not eigenfuctions of the exact Hamiltonian $\bH$.
+However they are eigenfunctions of an approximated Hamiltonian $\bH^{(0)}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
+
+\begin{equation}\label{eq:HFHamiltonian}
+\bH^{(0)}= \sum\limits_{i=1}^{n} f(i)
+\end{equation}
+
+The eigenfunctions of $f(i)$ are the one-electron spin-orbitals $\phi_a(i)$ used to create the $n$-electron Slater determinant.
+The equation \eqref{eq:FockOp} gives the eigenvalue equation for the one-electron Fock operator associated with the electron 1.
+The one-electron core Hamiltonian $h(i)$ are the sum of the kinetic energy of the electron $i$ and the attraction of the nuclei on this electron.
+The two other terms are the the Coulomb $J_a(i)$ and Exchange $K_a(i)$ operators.
+Their action on the spin-orbitals are given by the equation \eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
+The integration is over the spatial and spin coordinates.
+
+\begin{equation}\label{eq:FockOp}
+f(1)\phi_a(1) = \left[h(1) + \sum\limits_{b=1}^{n} J_b(1) - K_b(1)\right]\phi_a(1)=\epsilon_a\phi_a(1)
+\end{equation}
+
+\begin{equation}\label{eq:CoulOp}
+J_b(1)\phi_a(1)=\left[\int\dd\vb{x}_2\phi_b^*(2)\frac{1}{r_{12}}\phi_b(2) \right]\phi_a(1)
+\end{equation}
+
+\begin{equation}\label{eq:ExcOp}
+K_b(1)\phi_a(1)=\left[\int\dd\vb{x}_2\phi_b^*(2)\frac{1}{r_{12}}\phi_a(2) \right]\phi_b(1)
+\end{equation}
+
+\subsection{M{\o}ller-Plesset perturbation theory}
+
+The Hartree-Fock Hamiltonian \eqref{eq:HFHamiltonian} can be used as the zeroth-order Hamiltonian of the equation \eqref{eq:SchrEq-PT}.
+This partitioning of the Hamiltonian leads to the so-called M{\o}ller-Plesset (MP) perturbation theory \cite{Moller_1934}.
 The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a part of the correlation energy (i.e.
 the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
-This case of the Rayleigh-Schrödinger perturbation theory is called the M{\o}ller-Plesset perturbation theory \cite{Moller_1934}.
-In the MPPT the unperturbed Hamiltonian is the sum of the $n$ mono-electronic Fock operators which are the sum of the one-electron core Hamiltonian $h(i)$, the Coulomb $J_j(i)$ and Exchange $K_j(i)$ operators.
+This yields the Hamiltonian $\bH(\lambda)$ of the equation \eqref{eq:MPHamiltonian} where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{(scf)}$ for convenience.
 
-\begin{equation}
-H_0= \sum\limits_{i=1}^{n} f(i)
+\begin{equation}\label{eq:MPHamiltonian}
+    H(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{(scf)}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
 \end{equation}
 
-\begin{equation}
-f(i) = h(i) + \sum\limits_{j=1,j \neq i}^{n} \left[J_j(i) - K_j(i)\right]
-\end{equation}
-
-In Hartree-Fock theory the exact wave function is approximated as a Slater-determinant (which is an anti-symmetric combination of mono-electronic orbitals) and those wave functions are eigenvectors of the Fock operators.
 In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1.
@@
 \begin{equation}
-E_{\text{MP$_{n}$}}= \sum_{k=0}^n E^{(k)}
+E_{\text{MP}_{n}}= \sum_{k=0}^n E^{(k)}
 \end{equation}
 
-But as mentioned before \textit{a priori} there are no reasons that this power series is always convergent for $\lambda$=1 when $n$ goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
+But as mentioned before \textit{a priori} there are no reasons that $E_{\text{MP}_{n}}$ is always convergent when $n$ goes to infinity.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset method will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+A smart way to investigate the convergence properties of the M{\o}ller-Plesset series is to transform the coupling parameter $\lambda$ into a complex variable.
 By doing so the Hamiltonian and the energy become functions of this variable.
 The energy becomes a multivalued function on $n$ Riemann sheets.
-As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MPPT.
+As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the M{\o}ller-Plesset perturbation theory.
 Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
 The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost.
-But to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
-For small systems we can have access to the whole series using Full Configuration Interaction.
+But to deeply understand the behavior of the M{\o}ller-Plesset series and how it is connected to the singularities, we need to have access to high order terms of the series.
+For small systems we can have access to the whole series using Full Configuration Interaction (FCI).
 If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and expanding in $\lambda$ allows to to get the M{\o}ller-Plesset perturbation series at every order.
+
+\subsection{Alternative partitioning}
+
+The M{\o}ller-Plesset partitioning is not the only one possible in electronic structure theory.
 
@@
 The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression \eqref{eq:HamiltonianStillinger}.
-
-\begin{equation}
-H(\lambda)=H_0 + \lambda (H_\text{phys} - H_0)    
-\end{equation}
-
-\begin{equation}
-    H_\text{phys}=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}\right]
-\end{equation}
-
-\begin{equation}
-    H_0=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+V_j^{(scf)}\right]
-\end{equation}
-
-\begin{equation}
-    H(\lambda)=\sum\limits_{j=1}^{n}\left[-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|} + (1-\lambda)V_j^{(scf)}+\lambda\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|} \right]
-\label{eq:HamiltonianStillinger}
-\end{equation}
 

### 2020-07-17 RapportStage/Rapport.tex
add sec 1.2

@@
 \subsection{An illustrative example}
+In order to highlight the general properties of EPs mentioned above, we propose to consider the following $2 \times 2$ Hamiltonian commonly used in quantum chemistry
+
+\begin{equation}
+\label{eq:H_2x2}
+	\bH = 
+	\begin{pmatrix}
+		\epsilon_1	&	\lambda	\\
+		\lambda		&	\epsilon_2
+	\end{pmatrix},
+\end{equation}
+which represents two states of energies $\epsilon_1$ and $\epsilon_2$ coupled with a strength of magnitude $\lambda$.
+This Hamiltonian could represent, for example, a minimal-basis configuration interaction with doubles (CID) for the hydrogen molecule \cite{SzaboBook}.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=8cm]{2x2.pdf}
+    \includegraphics[width=8cm]{i2x2.pdf}
+    \caption{\centering Energies, as given by Eq.~\eqref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
+    \label{fig:2x2}
+\end{figure}
+
+For real $\lambda$, the Hamiltonian \eqref{eq:H_2x2} is clearly Hermitian, and it becomes non-Hermitian for any complex $\lambda$ value.
+Its eigenvalues are
+\begin{equation}
+\label{eq:E_2x2}
+	E_{\pm} = \frac{\epsilon_1 + \epsilon_2}{2} \pm \frac{1}{2} \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2},
+\end{equation}
+and they are represented as a function of $\lambda$ in Fig.~\ref{fig:2x2}.
+One notices that the two states become degenerate only for a pair of complex conjugate values of $\lambda$
+\begin{equation}
+\label{eq:lambda_EP}
+	\lambda_\text{EP} = \pm i\,\frac{\epsilon_1 - \epsilon_2}{2},
+	\quad
+	\text{with energy}	
+	\quad
+	E_\text{EP} = \frac{\epsilon_1 + \epsilon_2}{2},
+\end{equation}
+which correspond to square-root singularities in the complex-$\lambda$ plane (see Fig.~\ref{fig:2x2}).
+These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
+Starting from $\lambda_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
+In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
+The ``shape'' of the avoided crossing in linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
+
+Around $\lambda = \lambda_\text{EP}$, Eq.~\eqref{eq:E_2x2} behaves as \cite{MoiseyevBook}
+\begin{equation}
+        E_{\pm} = E_\text{EP} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}},
+\end{equation}
+and following a complex contour around the EP, i.e.~$\lambda = \lambda_\text{EP} + R \exp(i\theta)$, yields
+\begin{equation}
+        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2\lambda_\text{EP} R}  \exp(i\theta/2),
+\end{equation}
+and we have
+\begin{align}
+	E_{\pm}(2\pi) & = E_{\mp}(0),
+	&
+	E_{\pm}(4\pi) & = E_{\pm}(0).
+\end{align}
+This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
 
@@
 The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the Hartree-Fock energy.
-The MP2 energy starts to recover a part of the correlation energy.
+The MP2 energy starts to recover a part of the correlation energy \cite{SzaboBook}.
 
@@
 Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
-The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost.
+The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost \cite{JensenBook}.
 But to deeply understand the behavior of the M{\o}ller-Plesset series and how it is connected to the singularities, we need to have access to high order terms of the series.
@@
     \includegraphics[width=0.45\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) \cite{Gill_1986}.}
+    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from \cite{Gill_1986}).}
     \label{fig:RUMP_Gill}
@@
 \end{tabular}
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set \cite{Gill_1988}.}
+    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
     \label{tab:SpinContamination}
@@
 
-Cremer and He analyzed 29 FCI systems \cite{Cremer_1996} and regrouped all the systems in two classes.
+Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all the systems in two classes.
 The class A systems which have a monotonic convergence to the FCI value and the class B which converge erratically after initial oscillations.
@@
     \hfill
-    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets.}
+    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from \cite{Olsen_1996}).}
     \label{fig:my_label}
@@
 \begin{equation}
-\widehat{H} = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{\vb{r}_{12}}
+\widehat{H} = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}}
 \end{equation}

### 2020-07-18 RapportStage/Rapport.tex
minor corrections

@@
 \definecolor{linkcolor}{rgb}{0,0,0.6} % définition de la couleur des liens pdf
+\newcommand{\titou}[1]{\textcolor{red}{#1}}
 \usepackage[ pdftex,colorlinks=true,
@@
 
-Due to the ubiquitous influence of processes involving electronic excited states in physics, chemistry, and biology, their faithful description from first-principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
+Due to the ubiquitous influence of processes involving electronic excited states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
 Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community.
 An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws. 
-The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new excited-state methodologies, their main goal being to get the most accurate excitation energies (and properties) at the lowest computational cost, and in the most general context.
+The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new excited-state methodologies, their main goal being to get the most accurate excitation energies (and properties) at the lowest possible computational cost in the most general context.
 
@@
 
-Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
+By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
 This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
@@
     \centering
-    \includegraphics[width=8cm]{2x2.pdf}
-    \includegraphics[width=8cm]{i2x2.pdf}
+    \includegraphics[width=0.45\textwidth]{2x2.pdf}
+    \includegraphics[width=0.45\textwidth]{i2x2.pdf}
     \caption{\centering Energies, as given by Eq.~\eqref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
@@
 This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+\titou{Maybe you should add a few equations here to highlight the self-orthogonality process. 
+What do you think?
+You could also show that the behaviour of the wave function when one follows the complex contour around the EP.}
 
@@
 \begin{figure}[h!]
-    \includegraphics[height=5.5cm]{Nedivergence.png}
-    \hfill
-    \includegraphics[height=5.5cm]{HFdivergence.png}
-    \hfill
+    \centering
+    \includegraphics[width=0.45\textwidth]{Nedivergence.png}
+    \includegraphics[width=0.45\textwidth]{HFdivergence.png}
     \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from \cite{Olsen_1996}).}
@@
 the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
-Their analysis is based on Darboux's theorem: in the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
-Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.
+Their analysis is based on Darboux's theorem:
+\begin{quote}
+	\textit{``In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
+Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.''}
+\end{quote}
 
@@
 
-The laplacian operators are the kinetic operators for each electrons and $\vb{r}_{12}^{-1}$ is the Coulomb operator.
+The laplacian operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}$ is the Coulomb operator.
 The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.

### 2020-07-19 RapportStage/Rapport.tex
few changes

--- 2020-07-17 RapportStage/Rapport.tex
@@
 the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
-This yields the Hamiltonian $\bH(\lambda)$ of the equation \eqref{eq:MPHamiltonian} where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{(scf)}$ for convenience.
+This yields the Hamiltonian $\bH(\lambda)$ of the equation \eqref{eq:MPHamiltonian} where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{HF}$ for convenience.
 
 \begin{equation}\label{eq:MPHamiltonian}
-    H(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{(scf)}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
+    H(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{HF}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
 \end{equation}
@@
 The M{\o}ller-Plesset partitioning is not the only one possible in electronic structure theory.
+An other possibility, even more natural than the M{\o}ller-Plesset one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
+Hence, the off-diagonal elements of $\bH(\lambda)$ are the perturbation operator.
+
+The electronic Hamiltonian can be separated in the kinetic part and the potential part. We can use this to consider to other partitioning
 
@@
 
-When a bond is stretched the exact function can undergo a symmetry breaking becoming multi-reference during this process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
+When a bond is stretched the exact wave function becomes more and more multi-reference.
+Yet the Hartree-Fock wave function is restricted to be single reference so it can not model properly stretched system.
+Nevertheless the Hartree-Fock wave function can undergo a symmetry breaking to minimize its energy losing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
 A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series does not give accurate results at low orders.
@@
 
-In the unrestricted framework the ground state singlet wave function is allowed to mix with triplet states which leads to spin contamination.
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function which leads to spin contamination.
 Gill et al.~highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
@@
 Lepetit et al.~analyzed the difference between the M{\o}ller-Plesset and Epstein-Nesbet partitioning for the unrestricted Hartree-Fock reference \cite{Lepetit_1988}.
-They concluded that the slow convergence is due to the coupling of the single with the double excited configuration.
+They concluded that the slow convergence is due to the coupling of the singly with the doubly excited configuration.
 Moreover the MP denominators tends towards a constant so each contribution become very small when the bond is stretched.
@@
 The sample of systems contains stretched molecules and also some at equilibrium geometry, there are also some systems in various basis sets.
-They highlighted that systems with class A convergence have well-separated electrons pairs whereas class B systems present electrons clustering.
-This classification was encouraging in order to develop methods based on perturbation theory as it rationalizes the two different observed convergence modes.
-If it is possible to predict if a system is class A or B, then one can use extrapolation method of the first terms adapted to the class of the systems \cite{Cremer_1996}.
+They highlighted that \cite{Cremer_1996}\begin{quote}
+\textit{Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.}
+\end{quote}
+They proved that using different extrapolation formulas of the first terms of the M{\o}ller-Plesset of the series for class A and class B systems improve the precision of those formulas.
+The mean deviation from FCI correlation energies is 0.3 mhartrees whereas with the formula that do not distinguish the system it is 12 mhartrees.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the M{\o]ller-Plesset perturbation theory and to more accurate correlation energies.
 
@@
 \begin{equation}
-\mqty(\alpha & \delta \\ \delta & \beta) = \mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s ) + \mqty(- \alpha_s & \delta \\ \delta & - \beta_s)
+\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\bH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\bV}
 \end{equation}
@@
 Then they demonstrated that the divergence for the \ce{Ne} is due to a back-door intruder state.
-When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back door intruder state.
+When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back-door intruder state.
 They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series.
@@
 
-Moreover they proved that the extrapolation formula of Cremer and He \cite{Cremer_1996} cannot be used for all systems.
+Moreover they proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} cannot be used for all systems.
 Even more, that those formula were not mathematically motivated when looking at the singularity causing the divergence.

### 2020-07-20 RapportStage/Rapport.tex
update

@@
 In the Hartree-Fock (HF) approximation the wave function is approximated as a single Slater determinant (which is an anti-symmetric combination of $n$ one electron spin-orbitals).
-Rather than solving the equation \eqref{eq:SchrEq}, the Hartree-Fock theory use the variational principle to find an approximation to $\Psi$.
+Rather than solving the equation \eqref{eq:SchrEq}, the Hartree-Fock theory uses the variational principle to find an approximation to $\Psi$.
 Hence the Slater determinants are not eigenfuctions of the exact Hamiltonian $\bH$.
-However they are eigenfunctions of an approximated Hamiltonian $\bH^{(0)}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
+However, they are eigenfunctions of an approximated Hamiltonian $\bH^{(0)}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
 
@@
 \begin{equation}\label{eq:MPHamiltonian}
-    H(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{HF}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
+    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{\text{HF}}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
 \end{equation}
@@
 The mean deviation from FCI correlation energies is 0.3 mhartrees whereas with the formula that do not distinguish the system it is 12 mhartrees.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the M{\o]ller-Plesset perturbation theory and to more accurate correlation energies.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the M{\o}ller-Plesset perturbation theory and to more accurate correlation energies.
 
@@
 
-The M{\o}ller-Plesset Hamiltonian is defined as below and by reassembling the term we get the expression \eqref{eq:HamiltonianStillinger}.
+To understand the convergence properties at $\lambda=1$ of the perturbation series one need to look at the whole complex plane.
+In particular for real negative value of $\lambda$.
+If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stays repulsive as it is proportional to $(1-\lambda)$.
 
-The first two terms, the kinetic energy and the electron-nucleus attraction, form the mono-electronic core Hamiltonian which is independant of $\lambda$.
-The third term is the mean field repulsion of the Hartree-Fock calculation done to get $H_0$ and the last term is the Coulomb repulsion.
-If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stays repulsive as it is proportional to $(1-\lambda)$.
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nucleus cannot bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
-The repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nucleus.
+\begin{equation}\label{eq:HamiltonianStillinger}
+    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of }\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{Attractive}}  \right]
+\end{equation}
+
+The major difference between those two terms is that the repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nuclei.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nuclei can not bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
 There is a real negative value $\lambda_c$ where the electrons form a bound cluster and goes to infinity.
@@
 This reasoning is done on the exact Hamiltonian and energy, this is the exact energy which exhibits this singularity on the negative real axis.
-But in finite basis set, one can prove that for a Hermitian Hamiltonian the singularities of $E(\lambda)$ occurs in complex conjugate pair with non-zero imaginary parts.
-Sergeev and Goodson proved, as predicted by Stillinger, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+But in a finite basis set, one can prove that for a Hermitian Hamiltonian the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
 They explain that Olsen et al., because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
 
-Finally, it was shown that $\beta$ singularities are very sensitive to the basis sets but not to the stretching of the system.
+Finally, it was shown that $\beta$ singularities are very sensitive to changes of the basis set but not to the stretching of the system.
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
@@
 Yet at such an avoided crossing eigenstates change abruptly.
-Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarify.
-One of the major challenge in order to do this resides in our ability to compute the distribution of EPs.
+Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarified.
+One of the major challenges in order to do this resides in our ability to compute the distribution of EPs.
 The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions so methods are required to get information on the location of EPs.
@@
 \end{itemize}
-
-\subsection{Weak correlation regime}
-
-\subsubsection{Restricted and unrestricted equation for the  spherium model}
 
@@
 
-\subsubsection{The minimal basis example}
-
 We obtained the equation \eqref{eq:EUHF} for the general form of the wave function, but to be associated with a physical wave function the energy need to be stationary with respect to the coefficient.
@@
 
-\subsubsection{Symmetry-broken solutions}
+In addition, there is also the well-known symmetry-broken UHF solution.
+For $R>3/2$ an other stationary UHF solution appear, this solution is a minimum of the Hartree-Fock equations.
+This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the other way round.
+The electrons can be on opposite sides of the sphere because the choice of $Y_{10}$ as a basis function induced a privileged axis on the sphere for the electrons.
+This solution have the energy \eqref{eq:EUHF} for $R>3/2$.
 
-In addition, there is also the well-known symmetry-broken UHF solution.
-For $R>3/2$ an other stationary UHF solution appear, this solution is a minimum.
-This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the other way round.
-The electrons can be on opposite sides of the sphere because the choice of $Y_{10}$ induced a privileged axis on the sphere for the electrons.
+\begin{equation}
+E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}
+\end{equation}
+
 The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
@@
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy leading to this symmetry breaking.
-There is a competition between those two effects: keeping the symmetry of the exact wave function and minimize the energy.
 This type of symmetry breaking is called a spin density wave because the system oscillate between the two symmetry-broken configurations.
@@
 
-There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum.
-This solution is associated with another type of symmetry breaking somewhat well-known.
-Indeed it corresponds to a configuration where both electrons are on the same side of the sphere, in the same orbital.
+There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the .
+This solution is associated with another type of symmetry breaking somewhat less known.
+It corresponds to a configuration where both electrons are on the same side of the sphere, in the same orbital.
 This solution is called symmetry-broken RHF.
@@
 
+\begin{equation}
+E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}
+\end{equation}
+
 We can also consider negative value of R.
 This corresponds to the situation where one of the electrons is replaced by a positron.
-There are also a sb-RHF and a sb-UHF solution for some values of R but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
-Indeed, the sb-RHF state minimize the energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF state maximize the energy because the two particles are on opposite side of the sphere.
+There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of R (see Fig.\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
+Indeed, the sb-RHF state minimizes the energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF state maximizes the energy because the two particles are on opposite sides of the sphere.
 
-NRJ graphics
+In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer by analytically continuing the respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
+All those energies are plot in \autoref{fig:SpheriumNrj}.
+The dotted curves corresponds to the holomorphic domain of the energies.
 
-\subsection{Strongly correlated regime}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.9\textwidth]{EsbHF.pdf}
+    \caption{\centering Energies of the 5 solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+    \label{fig:SpheriumNrj}
+\end{figure}
 
@@
 
-\subsection{Exceptional points}
+\subsection{Exceptional points in the UHF formalism}
 

### 2020-07-20 RapportStage/Rapport.tex
update sec 5.1

@@
 
-Different partitioning
+In this part, we will try to investigate how some parameters of $\bH(\lambda)$ influence the radius of convergence of the perturbation series.
+The radius of convergence is equal to the closest singularity to the origin of $E(\lambda)$.
+The exceptional points are simultaneous solution of \eqref{eq:PolChar} and \eqref{eq:DPolChar} so we solve this system to find their position.
 
-$Y_{l0}$ vs $P_l(\cos(\theta))$
+\begin{equation}\label{eq:PolChar}
+\text{det}[E-\bH(\lambda)]=0
+\end{equation}
 
-Size of the basis set
+\begin{equation}\label{eq:DPolChar}
+\pdv{E}\text{det}[E-\bH(\lambda)]=0
+\end{equation}
 
-Strong coupling ???
+We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis. \\
+
+Puis on rajoute les 3 autres partitionnements \\
+
+Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). Parler de la possibilité de la base strong coupling. \\
+
+Différence RHF/UHF, Hamiltonien non-bloc diagonal, coefficients complexe pour R<3/2 \\
+
+Influence de la taille de la base en RHF et UHF \\
 
@@
 \item Corriger les erreurs dans la biblio
-\item tableau nrj uhf, citation spin density wave et charge density wave
+\item citation spin density wave et charge density wave
 \end{itemize}

### 2020-07-20 RapportStage/Rapport.tex
add some graph

@@
 
-Puis on rajoute les 3 autres partitionnements \\
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
+    \caption{\centering }
+    \label{fig:RHFMiniBasRCV}
+\end{figure}
 
-Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). Parler de la possibilité de la base strong coupling. \\
+Then we will compare the different partitioning using the same basis set.
+The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the weak correlation and the strong coupling partitioning.
+We can see that
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{PartitioningRCV.pdf}
+    \caption{\centering }
+    \label{fig:RadiusPartitioning}
+\end{figure}
+
+Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). + petit Parler de la possibilité de la base strong coupling avec la citation paola et les polynomes . \\
 

### 2020-07-20 RapportStage/Rapport.tex
update monday
corrections biblio

@@
 
-\subsection{Alternative partitioning}
+\subsection{Alternative partitioning}\label{sec:AlterPart}
 
@@
 
-We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis. \\
+We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis.
+The electron 1 have a spin $\alpha$ and the electron 2 a spin $\beta$.
+Hence we can forget the spin part of the spin-orbitals and from now we will work with spatial orbitals.
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set is: $\psi_1=Y_0(\theta_1)Y_0(\theta_2)$; $\psi_2=Y_0(\theta_1)Y_1(\theta_2)$; $\psi_3=Y_1(\theta_1)Y_0(\theta_2)$; $\psi_4=Y_1(\theta_1)Y_1(\theta_2)$.
+
+The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set.
+$\psi_1$ have the same symmetry as $\psi_4$ and there is an avoided crossing between these two states as we can see in \autoref{fig:RHFMiniBasRCV}.
 
@@
     \centering
+    \includegraphics[width=0.45\textwidth]{EMP_RHF_R10.pdf}
     \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
@@
 
-Then we will compare the different partitioning using the same basis set.
-The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the weak correlation and the strong coupling partitioning.
+Then we can compare the different partitioning of \autoref{sec:AlterPart} using the same basis set.
+The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning.
 We can see that
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{PartitioningRCV.pdf}
+    \includegraphics[width=0.7\textwidth]{PartitioningRCV.pdf}
     \caption{\centering }
@@
 Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). + petit Parler de la possibilité de la base strong coupling avec la citation paola et les polynomes . \\
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{CSF_RCV.pdf}
+    \caption{\centering }
+    \label{fig:RadiusCSF}
+\end{figure}
 
@@
 
-\section{To do list}
-
-\begin{itemize}
-\item Corriger les erreurs dans la biblio
-\item citation spin density wave et charge density wave
-\end{itemize}
-
 \section{Conclusion}

### 2020-07-21 RapportStage/Rapport.tex
update skype

@@
 \newcommand{\titou}[1]{\textcolor{red}{#1}}
+\newcommand{\antoine}[1]{\textcolor{orange}{#1}}
 \usepackage[ pdftex,colorlinks=true,
@@
 Moreover the MP denominators tends towards a constant so each contribution become very small when the bond is stretched.
+\antoine{Rephrase this sentence}
 
@@
 This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
-By analogy with the case of \ce{H_2} \cite{SzaboBook}, the unrestricted Hartree-Fock wave function is defined as:
+The unrestricted Hartree-Fock wave function is defined as:
 
-\begin{equation}
+\begin{equation}\label{eq:UHF_WF}
 \Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2)
@@
 
-We obtained the equation \eqref{eq:EUHF} for the general form of the wave function, but to be associated with a physical wave function the energy need to be stationary with respect to the coefficient.
-The general method is to use the Hartree-Fock self-consistent field method to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis to illustrate the difference between the RHF and UHF solutions.
+We obtained the equation \eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients.
+The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
+We will work in a minimal basis ($Y_{00}$ and $Y_{10}$) to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions.
-One can define the mono-electronic wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
+One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
 Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
@@
 \begin{equation}
-\phi_\alpha(\theta_1)= \cos(\chi_\alpha)\frac{Y_{00}(\Omega_1)}{R} + \sin(\chi_\alpha)\frac{Y_{10}(\Omega_1)}{R}
+\phi_\alpha(\theta_1)= \cos(\chi_\alpha)\frac{Y_{00}(\theta_1)}{R} + \sin(\chi_\alpha)\frac{Y_{10}(\theta_1)}{R}
 \end{equation}
 
-The minimization gives the 3 anticipated solutions (valid for all value of R):
+The minimization gives the three following solutions valid for all value of R:
 \begin{itemize}
@@
 
-Vérifier minimum, maximum, point selle
+Those solutions are respectively a minimum, a maximum and a saddle point of the HF equations.\\
 
@@
 For $R>3/2$ an other stationary UHF solution appear, this solution is a minimum of the Hartree-Fock equations.
-This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the other way round.
+This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the configuration the other way round.
 The electrons can be on opposite sides of the sphere because the choice of $Y_{10}$ as a basis function induced a privileged axis on the sphere for the electrons.
-This solution have the energy \eqref{eq:EUHF} for $R>3/2$.
+This solution have the energy \eqref{eq:EsbUHF} for $R>3/2$.
 
-\begin{equation}
+\begin{equation}\label{eq:EsbUHF}
 E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}
@@
 
-The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
+The exact solution for the ground state is a singlet so this wave function does not have the true symmetry\antoine{add an equation that shows this}.
 However this solution gives more accurate results for the energy at large R as shown in \autoref{tab:ERHFvsEUHF}.
-In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy leading to this symmetry breaking.
-This type of symmetry breaking is called a spin density wave because the system oscillate between the two symmetry-broken configurations.
+In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
+Thus the wave function break the spin symmetry because it allows a more efficient minimization of the Coulomb repulsion.
+This type of symmetry breaking is called a spin density wave because the system oscillates between the two symmetry-broken configurations \cite{GiulianiBook}.
 
@@
 
-There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the .
+There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
 This solution is associated with another type of symmetry breaking somewhat less known.
-It corresponds to a configuration where both electrons are on the same side of the sphere, in the same orbital.
+It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
 This solution is called symmetry-broken RHF.
 At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the $Y_{10}$ orbitals.
-This symmetry breaking is associated with a charge density wave: the system oscillate between the situations with the electrons on each side.
+This symmetry breaking is associated with a charge density wave: the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
 
@@
 There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of R (see Fig.\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
-Indeed, the sb-RHF state minimizes the energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF state maximizes the energy because the two particles are on opposite sides of the sphere.
+Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF states maximize the energy because the two particles are on opposite sides of the sphere.
 
-In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer by analytically continuing the respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
-All those energies are plot in \autoref{fig:SpheriumNrj}.
+In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
+All those energies are plotted in \autoref{fig:SpheriumNrj}.
 The dotted curves corresponds to the holomorphic domain of the energies.
@@
     \includegraphics[width=0.9\textwidth]{EsbHF.pdf}
-    \caption{\centering Energies of the 5 solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+    \caption{\centering Energies of the 5 solutions of the HF equations (multiplied by $R^2$).
+The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.
+\antoine{Change legend}}
     \label{fig:SpheriumNrj}
@@
 Hence we can forget the spin part of the spin-orbitals and from now we will work with spatial orbitals.
-In the restricted formalism the spatial orbitals are the same so the two-electron basis set is: $\psi_1=Y_0(\theta_1)Y_0(\theta_2)$; $\psi_2=Y_0(\theta_1)Y_1(\theta_2)$; $\psi_3=Y_1(\theta_1)Y_0(\theta_2)$; $\psi_4=Y_1(\theta_1)Y_1(\theta_2)$.
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set is: $\psi_1=Y_{00}(\theta_1)Y_{00}(\theta_2)$; $\psi_2=Y_{00}(\theta_1)Y_{10}(\theta_2)$; $\psi_3=Y_{10}(\theta_1)Y_{00}(\theta_2)$; $\psi_4=Y_{10}(\theta_1)Y_{10}(\theta_2)$.
 
@@
     \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
-    \caption{\centering }
+    \caption{\centering (left): \antoine{Change legend, change colour} (right): }
     \label{fig:RHFMiniBasRCV}
@@
     \includegraphics[width=0.7\textwidth]{PartitioningRCV.pdf}
-    \caption{\centering }
+    \caption{\centering \antoine{Swap curves to make colors consistent}}
     \label{fig:RadiusPartitioning}
@@
 
-Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF). + petit Parler de la possibilité de la base strong coupling avec la citation paola et les polynomes . \\
+Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF)+ tableau d'énergie ?
++ petit paragraphe: parler de la possibilité de la base strong coupling avec la citation paola et les polynomes laguerre.
+\\
 

### 2020-07-21 RapportStage/Rapport.tex
update

@@
 In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
-The ``shape'' of the avoided crossing in linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
+The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
 
@@
 This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+
+The eigenvectors associated to the energies \eqref{eq:E_2x2} are
+\begin{equation}
+\phi_{\pm}=\begin{pmatrix}
+\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
+\end{pmatrix},
+\end{equation}
+and for $\lambda=\lambda_\text{EP}$ they become
+\begin{equation}
+\phi_{\pm}=\begin{pmatrix}
+\mp i \\ 1
+\end{pmatrix},
+\end{equation}
+which are clearly self-orthogonal. The equation (7) can be rewrite as
+\begin{equation}
+\phi_{\pm}=\begin{pmatrix}
+\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\
+\end{pmatrix},
+\end{equation}
+we can see that if we normalise them they will behave as
+$(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
+\begin{align}
+	\phi_{\pm}(2\pi) & = \phi_{\mp}(0),
+	&
+	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0) \\
+	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
+	&
+	\phi_{\pm}(8\pi) & = \phi_{\pm}(0),
+\end{align}
+showing that 4 loops around the EP are necessary to recover the initial state. We can also that looping around the other way round leads to a different pattern.
 \titou{Maybe you should add a few equations here to highlight the self-orthogonality process. 
@@
 Hence, the off-diagonal elements of $\bH(\lambda)$ are the perturbation operator.
+This partitioning leads to the Epstein-Nesbet (EN) perturbation theory.
+The zeroth-order eigenstates for this partitioning are Slater determinants as for the M{\o}ller-Plesset partitioning.
+The expression of the second order correction to the energy is given for both M{\o}ller-Plesset and Epstein-Nesbet.
+The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies.
+The i,j indices represent the occupied orbitals and r,s the virtual orbitals of the basis sets.
 
-The electronic Hamiltonian can be separated in the kinetic part and the potential part. We can use this to consider to other partitioning
+\begin{equation}\label{eq:EMP2}
+E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\bra{ij}\hspace{1pt}\ket{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s}
+\end{equation}
+\begin{equation}\label{eq:EEN2}
+E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\bra{ij}\hspace{1pt}\ket{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s - (J_{ij} + J_{rs} - J_{ir} - J_{is} - J_{jr} + J_{js})}
+\end{equation}
+where $J_{ij}$ is the matrix element of the Coulomb operator \eqref{eq:CoulOp} and with
+\begin{equation}
+\bra{ij}\hspace{1pt}\ket{rs}=\bra{ij}\ket{rs} - \bra{ij}\ket{sr}
+\end{equation}
+where $\bra{ij}\ket{rs}$ is the two-electron integral
+\begin{equation}
+\bra{ij}\ket{rs}=\int \dd\vb{x}_1\dd\vb{x}_2\chi_i^*(\vb{x}_1)\chi_j^*(\vb{x}_2)r_{12}^{-1}\chi_r(\vb{x}_1)\chi_s(\vb{x}_2)
+\end{equation}
+
+Additionally, we will consider two other partitioning.
+The electronic Hamiltonian can be separated in a one-electron part and in a two-electron part as seen previously.
+We can use this separation to create two other partitioning:
+
+\begin{itemize}
+\item The Weak Correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
+\item The Strong Coupling partitioning where the two operators are inverted compared to the weak correlation partitioning.
+\end{itemize}
 
@@
 They concluded that the slow convergence is due to the coupling of the singly with the doubly excited configuration.
-Moreover the MP denominators tends towards a constant so each contribution become very small when the bond is stretched.
-\antoine{Rephrase this sentence}
-
+Moreover the MP and EN numerators in Eq.
+\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
+Yet the MP denominators tends towards a constant when $r\rightarrow\infty$ so the terms vanish.
+Where as the EN denominators tends to 0 which improve the convergence but can also make diverge the series.
 Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all the systems in two classes.
@@
 
-The exact solution for the ground state is a singlet so this wave function does not have the true symmetry\antoine{add an equation that shows this}.
+The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
+Indeed, the spherical harmonics are eigenvectors of $S^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $S^2$.
 However this solution gives more accurate results for the energy at large R as shown in \autoref{tab:ERHFvsEUHF}.

### 2020-07-21 RapportStage/Rapport.tex
update tuesday

@@
 \phi_{\pm}=\begin{pmatrix}
-\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\
+\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\ 1
 \end{pmatrix},
@@
 The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis ($Y_{00}$ and $Y_{10}$) to illustrate the difference between the RHF and UHF solutions.
+We will work in a minimal basis, composed  of a $Y_{00}$ and a $Y_{10}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions.

### 2020-07-22 RapportStage/Rapport.tex
update

@@
 \begin{itemize}
-\item The two electrons are in the $Y_{00}$ orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
-\item The two electrons are in the $Y_{10}$ orbital which is a RHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$
-\item One electron is in the $Y_{00}$ orbital and the other is in the $Y_{10}$ orbital which is a UHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$
+\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$
 \end{itemize}
@@
 This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the configuration the other way round.
-The electrons can be on opposite sides of the sphere because the choice of $Y_{10}$ as a basis function induced a privileged axis on the sphere for the electrons.
+The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
 This solution have the energy \eqref{eq:EsbUHF} for $R>3/2$.
@@
 This solution is called symmetry-broken RHF.
-At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the $Y_{10}$ orbitals.
+At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
 This symmetry breaking is associated with a charge density wave: the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
@@
     \includegraphics[width=0.9\textwidth]{EsbHF.pdf}
-    \caption{\centering Energies of the 5 solutions of the HF equations (multiplied by $R^2$).
-The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.
-\antoine{Change legend}}
+    \caption{\centering Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
     \label{fig:SpheriumNrj}
@@
 In this part, we will try to investigate how some parameters of $\bH(\lambda)$ influence the radius of convergence of the perturbation series.
-The radius of convergence is equal to the closest singularity to the origin of $E(\lambda)$.
-The exceptional points are simultaneous solution of \eqref{eq:PolChar} and \eqref{eq:DPolChar} so we solve this system to find their position.
+The radius of convergence is equal to the closest singularity to the origin of $E(\lambda)$ so we need to determine the locations of the exceptional points.
+To find them we solve simultaneously the equations \eqref{eq:PolChar} and \eqref{eq:DPolChar}.
+The equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system, if an energy is also solution of \eqref{eq:DPolChar} then this energy is degenerate.
+In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate i.e.
+the exceptional points.
 
@@
 
-We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis.
 The electron 1 have a spin $\alpha$ and the electron 2 a spin $\beta$.
-Hence we can forget the spin part of the spin-orbitals and from now we will work with spatial orbitals.
-In the restricted formalism the spatial orbitals are the same so the two-electron basis set is: $\psi_1=Y_{00}(\theta_1)Y_{00}(\theta_2)$; $\psi_2=Y_{00}(\theta_1)Y_{10}(\theta_2)$; $\psi_3=Y_{10}(\theta_1)Y_{00}(\theta_2)$; $\psi_4=Y_{10}(\theta_1)Y_{10}(\theta_2)$.
+Hence we can forget the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set is:
 
-The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set.
-$\psi_1$ have the same symmetry as $\psi_4$ and there is an avoided crossing between these two states as we can see in \autoref{fig:RHFMiniBasRCV}.
+\begin{align}\label{eq:basis}
+ \psi_1 & =Y_{00}(\theta_1)Y_{00}(\theta_2),
+ & 
+ \psi_2 & =Y_{00}(\theta_1)Y_{10}(\theta_2),\\
+ \psi_3 & =Y_{10}(\theta_1)Y_{00}(\theta_2),
+ & 
+ \psi_4 & =Y_{10}(\theta_1)Y_{10}(\theta_2).
+\end{align}
+
+The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set ($\psi_1$ interacts with $\psi_4$ and $\psi_2$ with $\psi_3$).
+The two singly excited states yields a singlet and a triplet sp\textsubscript{z} but they don't have the same symmetry so these states can't form exceptional points with the ground state.
+However there is an avoided crossing (see Fig.
+\ref{fig:RHFMiniBas}) between the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} which is connected to two exceptional points in the complex plane.
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{EMP_RHF_R10.pdf}
-    \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
-    \caption{\centering (left): \antoine{Change legend, change colour} (right): }
-    \label{fig:RHFMiniBasRCV}
+    \includegraphics[width=0.7\textwidth]{EMP_RHF_R10.pdf}
+    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:basis} with $R=10$.}
+    \label{fig:RHFMiniBas}
 \end{figure}
 
-Then we can compare the different partitioning of \autoref{sec:AlterPart} using the same basis set.
-The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning.
-We can see that
+To simplify the problem, it is convenient to only consider basis function with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
+In this case the ground state is a totally symmetric singlet.
+According to the angular-momentum theory we expand the exact wave function in the following two-electron basis:
+\begin{equation}
+\Phi_l(\theta)=\frac{\sqrt{2l+1}}{4\pi R^2}P_l(\cos\theta)
+\end{equation}
+where $P_l$ are the Legendre polynomial and $\theta$ is the interelectronic angle.
+
+Then using this basis set we can compare the different partitioning of \autoref{sec:AlterPart}.
+The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
+$P_0$ and $P_1$.
+We see that
 
@@
     \includegraphics[width=0.7\textwidth]{PartitioningRCV.pdf}
-    \caption{\centering \antoine{Swap curves to make colors consistent}}
+    \caption{\centering Radius of convergence in the minimal basis for different partitioning of the Hamiltonian$\bH(\lambda)$.}
     \label{fig:RadiusPartitioning}
@@
 
-Puis différence entre $Y_{l0}$ et $P_l(\cos(\theta))$ (CSF)+ tableau d'énergie ?
-+ petit paragraphe: parler de la possibilité de la base strong coupling avec la citation paola et les polynomes laguerre.
-\\
+Commenter figure 8 (singularité alpha pas très sensible à basis set)
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{CSF_RCV.pdf}
-    \caption{\centering }
-    \label{fig:RadiusCSF}
+    \includegraphics[width=0.45\textwidth]{MPlargebasis.pdf}
+    \includegraphics[width=0.45\textwidth]{WCElargebasis.pdf}
+    \caption{\centering Radius of convergence in the CSF basis with $n$ basis function for the MP partitioning (left) and the WC partitioning (right).}
+    \label{fig:RadiusPartitioning}
 \end{figure}
@@
 
-Influence de la taille de la base en RHF et UHF \\
+ + petit paragraphe: parler de la possibilité de la base strong coupling avec la citation paola et les polynomes laguerre. \\
 

### 2020-07-23 RapportStage/Rapport.tex
update sec 5.1

@@
     \centering
+    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
     \begin{tabular}{c c c c c c c}
@@
 \end{tabular}
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
     \label{tab:SpinContamination}
@@
 %============================================================%
-\section{The spherium model}
+\section{The spherium model}\label{sec:spherium}
 %============================================================%
@@
 \centering
+\caption{\centering RHF and UHF energies in the minimal basis and exact energies for various R.}
 \begin{tabular}{c c c c c c c c c}
@@
 \end{tabular}
-    \caption{\centering RHF and UHF energies in the minimal basis and exact energies for various R.}
 \label{tab:ERHFvsEUHF}
@@
 
-The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set ($\psi_1$ interacts with $\psi_4$ and $\psi_2$ with $\psi_3$).
-The two singly excited states yields a singlet and a triplet sp\textsubscript{z} but they don't have the same symmetry so these states can't form exceptional points with the ground state.
+The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set ($\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$).
+The two singly excited states yields a singlet and a triplet sp\textsubscript{z} but they don't have the appropriate symmetry so these states can't form exceptional points with the ground state.
 However there is an avoided crossing (see Fig.
@@
 The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
-$P_0$ and $P_1$.
-We see that
+$P_0$ and $P_1$ and in the three function basis.
+We see that the radius of convergence of the strong coupling partitioning is growing with R whereas it is decreasing for the three other partitioning.
+This result was expected because the three decreasing partitioning use a weakly correlated reference so $\bH^{(0)}$ is a good approximation for small $R$.
+On the contrary the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated i.e.
+when $R$ is large for the spherium model.
+The M{\o}ller-Plesset partitioning is always better than the weak correlation in \autoref{fig:RadiusPartitioning}.
+In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
+Whereas the M{\o}ller-Plesset reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
+Moreover it can be proved that the n-th order energy of the weak correlation series can be obtained as a limited development of MP$n$ respective to $R$.
+It seems that the Epstein-Nesbet partitioning is better than the M{\o}ller-Plesset one for very small R in the minimal basis.
+In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2
+$ (and in larger basis set) the M{\o}ller-Plesset series converge faster for all value of $R$.
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{PartitioningRCV.pdf}
-    \caption{\centering Radius of convergence in the minimal basis for different partitioning of the Hamiltonian$\bH(\lambda)$.}
+    \includegraphics[width=0.45\textwidth]{PartitioningRCV2.pdf}
+    \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
+    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian$\bH(\lambda)$.}
     \label{fig:RadiusPartitioning}
@@
 
-Commenter figure 8 (singularité alpha pas très sensible à basis set)
+The \autoref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
+The CSF basis function have all the same spin and spatial symmetry so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
+The \autoref{tab:SingAlpha} proves that the singularities considered in this case are $\alpha$ singularities.
+This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities.
+The discontinuities observed in \autoref{fig:RadiusBasis} with the M{\o}ller-Plesset partitioning are due to a change of the dominant singularity.
+\\
 
@@
     \caption{\centering Radius of convergence in the CSF basis with $n$ basis function for the MP partitioning (left) and the WC partitioning (right).}
-    \label{fig:RadiusPartitioning}
+    \label{fig:RadiusBasis}
 \end{figure}
 
-Différence RHF/UHF, Hamiltonien non-bloc diagonal, coefficients complexe pour R<3/2 \\
+\begin{table}[h!]
+\centering
+\caption{\centering }
+\begin{tabular}{c}
+a
+\end{tabular}
+\label{tab:SingAlpha}
+\end{table}
+
+Now we will investigate the differences in the singularity structure between the RHF and UHF formalism.
+To do this we use the symmetry-broken orbitals obtained in \autoref{sec:spherium}.
+Thus the UHF two-electron basis is:
 

### 2020-07-23 RapportStage/Rapport.tex
fin partie 5.1 (pas encore relu)

@@
 
-\begin{align}\label{eq:basis}
+\begin{align}\label{eq:rhfbasis}
  \psi_1 & =Y_{00}(\theta_1)Y_{00}(\theta_2),
@@
     \includegraphics[width=0.7\textwidth]{EMP_RHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:basis} with $R=10$.}
+    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:rhfbasis} with $R=10$.}
     \label{fig:RHFMiniBas}
@@
 Thus the UHF two-electron basis is:
+\begin{align}\label{eq:uhfbasis}
+ \psi_1 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,1}(\theta_2),
+ & 
+ \psi_2 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,2}(\theta_2),\\
+ \psi_3 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,1}(\theta_2),
+ & 
+ \psi_4 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,2}(\theta_2).
+\end{align}
+with the symmetry-broken orbitals
+\begin{align*}\label{eq:uhforbitals}
+ \phi_{\alpha,1}(\theta) & =\frac{\sqrt{75+62R}Y_{00}(\theta)+5\sqrt{-3+2R}Y_{10}(\theta)}{4\sqrt{7R}},
+ & 
+ \phi_{\beta,1}(\theta) & =\frac{\sqrt{75+62R}Y_{00}(\theta)-5\sqrt{-3+2R}Y_{10}(\theta)}{4\sqrt{7R}},\\
+ \phi_{\alpha,2}(\theta) & =\frac{-5\sqrt{-3+2R}Y_{00}(\theta)+\sqrt{75+62R}Y_{10}(\theta)}{4\sqrt{7R}},
+ & 
+ \phi_{\beta,2}(\theta) & =\frac{5\sqrt{-3+2R}Y_{00}(\theta)+\sqrt{75+62R}Y_{10}(\theta)}{4\sqrt{7R}}.
+\end{align*}
+In the UHF formalism the Hamiltonian $\bH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
+The matrix element for this  interaction is proportional to $\sqrt{-3+2R}$.
+For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix element become real.
+This interaction corresponds to the spin contamination of the wave function.
+For $R<3/2$ the matrix element is complex, this corresponds to the holomorphic solution of \autoref{fig:SpheriumNrj}, the singularities in this case will be treated in \autoref{sec:uhfSing}.
 
- + petit paragraphe: parler de la possibilité de la base strong coupling avec la citation paola et les polynomes laguerre. \\
+The singularity structure in this case is more complex because of this spin contamination because we can't use configuration state function.
+So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some corresponds to EPs and some to conical intersections.
+The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
+The \autoref{fig:UHFMiniBas} is the analog of \autoref{fig:RHFMiniBas} in the UHF formalism.
+We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
+Those avoided crossings are due to the spin contamination of the wave function.
+The exceptional points resulting from those avoided crossings will be discussed in \autoref{sec:uhfSing}.
+\\
 
-\subsection{Exceptional points in the UHF formalism}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{EMP_UHF_R10.pdf}
+    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:rhfbasis} with $R=10$.}
+    \label{fig:UHFMiniBas}
+\end{figure}
+
+In this study we have used spherical harmonics (or combination of spherical harmonics) as basis function which are diffuse wave functions.
+It would also be interesting to investigate the use of localized basis function \cite{Seidl_2018} (for example gaussians) because those functions would be more adapted to describe the correlated regime.
+\\
+
+\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
 

### 2020-07-23 RapportStage/Rapport.tex
modifications 1st page

@@
 
-\textbf{\huge Pertubation theories in the complex plane}
+\textbf{\huge Pertubation theory in the complex plane}
 
@@
 \parbox{15cm}{\small
-\textbf{Abstract} : \it In this work, we explore the description of quantum chemistry in the complex plane.
-We see that the physics of the system can be connected to the position of the energy singularities in the complex plane.
-After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we perform an historical review of the researches that have been done on the physic of singularities.
-Then we connect all those points of view on this problem using the spherium model (i.e., two opposite-spin electrons restricted to remain on the surface of a sphere of radius $R$) as a theoretical playground.
-In particular, we explore the effects of symmetry breaking of the wave functions on the singularity structure.
+\textbf{Abstract} : \it In this work, we explore the extension of quantum chemistry in the complex plane.
+We observe that the physics of a quantum system is intimately connected to the position of the energy singularities in the complex plane.
+After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
+Then we connect and further discuss these different aspects using the spherium model (i.e., two opposite-spin electrons restricted to remain on the surface of a sphere) as a theoretical playground.
+In particular, we explore various perturbative partitioning strategies and the effects of symmetry breaking on the singularity structure of the electronic energy.
+This provides fundamental insights on the location of these singularities in the complex plane (that one calls exceptional points) and, specifically, on the magnitude of the radius of convergence associated with the perturbative treatment.
 }
@@
 \parbox{15cm}{
-\textbf{Keywords} : \it Quantum chemistry, Perturbation theory,  Spherium, Exceptional points, Symmetry breaking
+\textbf{Keywords} : \it quantum chemistry, perturbation theory, complex plane, spherium, exceptional points, radius of convergence, symmetry breaking
 } %fin de la commande \parbox des mots clefs

### 2020-07-23 RapportStage/Rapport.tex
sec 1.2

@@
 
-\url{https://www.irsamc.ups-tlse.fr/}
+\url{https://www.irsamc.ups-tlse.fr/loos}
 } %fin de la commande \parbox encadrant / laboratoire d'accueil
@@
 Around $\lambda = \lambda_\text{EP}$, Eq.~\eqref{eq:E_2x2} behaves as \cite{MoiseyevBook}
-\begin{equation}
+\begin{equation} \label{eq:E_EP}
         E_{\pm} = E_\text{EP} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}},
@@
 
-The eigenvectors associated to the energies \eqref{eq:E_2x2} are
-\begin{equation}
-\phi_{\pm}=\begin{pmatrix}
-\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
+The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
+\begin{equation} \label{eq:phi_2x2}
+\phi_{\pm}=
+	\begin{pmatrix}
+		E_{\pm}/\lambda
+		\\ 
+		1
 	\end{pmatrix},
 \end{equation}
-and for $\lambda=\lambda_\text{EP}$ they become
+and, for $\lambda=\lambda_\text{EP}$, they become
 \begin{equation}
@@
 \end{equation}
-which are clearly self-orthogonal. The equation (7) can be rewrite as
+which are clearly self-orthogonal. 
+\titou{what do you mean by self-orthogonal?}
+Using Eq.~\eqref{eq:E_EP}, Eq.~\eqref{eq:phi_2x2} can be recast as
 \begin{equation}
-\phi_{\pm}=\begin{pmatrix}
-\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\ 1
+\phi_{\pm}=
+	\begin{pmatrix}
+		E_\text{EP}/\lambda \pm \sqrt{2\lambda_\text{EP}/\lambda} \sqrt{1 - \lambda_\text{EP}/\lambda} 
+		\\ 
+		1
 	\end{pmatrix},
 \end{equation}
-we can see that if we normalise them they will behave as
-$(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
+where one clearly see that, if normalised, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
 \begin{align}
@@
 \end{align}
-showing that 4 loops around the EP are necessary to recover the initial state. We can also that looping around the other way round leads to a different pattern.
-\titou{Maybe you should add a few equations here to highlight the self-orthogonality process. 
-What do you think?
-You could also show that the behaviour of the wave function when one follows the complex contour around the EP.}
+\titou{I don't think it is too obvious that the eigenvectors behave as $(\lambda - \lambda_\text{EP})^{-1/4}$.}
+In plain words, four loops around the EP are necessary to recover the initial state. 
+We can also see that looping the other way around leads to a different pattern.
 

### 2020-07-23 RapportStage/Rapport.tex
Sec 3.4

@@
 
-In the previous section, we saw that a reasoning on the Hamiltonian allows us to predict the existence of a critical point.
-In a finite basis set this critical point is model by a cluster of singularity $\beta$.
-It is now well-known that this phenomenon is a specific case of a more general phenomenon.
-Indeed, theoretical physicists proved that EPs close to the real axis are connected to quantum phase transitions \cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}.
-In quantum mechanics, the Hamiltonian is almost always dependent of at least one parameter, in some cases the variation of a parameter can lead to abrupt changes at a critical point.
-Those quantum phase transitions exist both for ground and excited states \cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019}.
-A ground-state quantum phase transition is characterized by the successive derivative of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
+In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point.
+In a finite basis set this critical point is model by a cluster of $\beta$ singularities.
+It is now well known that this phenomenon is a special case of a more general phenomenon.
+Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs) \cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}.
+In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter.
+In some cases the variation of a parameter can lead to abrupt changes at a critical point.
+These QPTs exist both for ground and excited states as shown by Cejnar and coworkers \cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019}.
+A ground-state QPT is characterized by the \titou{successive?} derivative of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
-Otherwise, it is called continuous and of n-th order if the n-th derivative is discontinuous.
-A quantum phase transition can also be identify by the discontinuity of an appropriate order parameter (or one of its derivative).
+Otherwise, it is called continuous and of $n$-th order if the $n$-th derivative is discontinuous.
+A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
 
 The presence of an EP close to the real axis is characteristic of a sharp avoided crossing.
-Yet at such an avoided crossing eigenstates change abruptly.
-Although it is now well understood that EPs are closely related to quantum phase transitions, the link between the type of QPT (ground state or excited state, first or superior order) and EPs still need to be clarified.
-One of the major challenges in order to do this resides in our ability to compute the distribution of EPs.
-The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions so methods are required to get information on the location of EPs.
-Cejnar et al.
-developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis \cite{Cejnar_2005, Cejnar_2007}.
-More recently Stransky and co-workers proved that the distribution of EPs is not the same around a QPT of first or second order \cite{Stransky_2018}.
-Moreover, that when the dimension of the system increases they tends towards the real axis in a different manner, meaning respectively exponentially and algebraically.
+Yet, at such an avoided crossing, eigenstates change abruptly.
+Although it is now well understood that EPs are closely related to QPTs, the link between the type of QPT (ground state or excited state, first or higher order) and EPs still need to be clarified.
+One of the major obstacles that one faces in order to achieve this resides in the ability to compute the distribution of EPs.
+The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions.
+Hence, the design of specific methods are required to get information on the location of EPs.
+Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis \cite{Cejnar_2005, Cejnar_2007}.
+More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT \cite{Stransky_2018}.
+In particular, they showed that when the dimensionality of the system increases, first- and second-order QTP behave differently, and converge towards the real axis at different rates (exponentially and algebraically for the first and second order, respectively).
 
-It seems like our understanding of the physics of spatial and/or spin symmetry breaking in the Hartree-Fock theory can be enlightened by quantum phase transition theory.
-Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which means that the system undergo a second order quantum phase transition.
-Moreover, the $\beta$ singularities introduced by Sergeev to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+It seems like our understanding of the physics of spatial and/or spin symmetry breaking in the Hartree-Fock theory can be enlightened by QPT theory.
+Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which means that the system undergo a second-order QPT.
+Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
 The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly.
-However the $\alpha$ singularities arise from large avoided crossings therefore they can not be connected to QPT.
+However, the $\alpha$ singularities arise from large avoided crossings.
+Thus, they can not be connected to QPT.
 The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states.
@@
 We think that $\alpha$ singularities are connected to the multi-reference behavior of the wave function in the same way as $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function.
+\titou{I am not sure I agree with your last comment. Maybe, we can talk about it tomorrow.}
 

### 2020-07-23 RapportStage/Rapport.tex
Sec 3.3

@@
 
-In the 2000's Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006}  analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and his co-workers were trying to find the dominant singularity causing the divergence.
-They regrouped singularities in two classes: the $\alpha$ singularities which have unit order imaginary parts and the $\beta$ singularities which have very small imaginary parts.
-The singularities $\alpha$ are related to large avoided crossing between the ground state and a low-lying excited states.
-Whereas the singularities $\beta$ come from a sharp avoided crossing between the ground state and a highly diffuse state.
+In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+They regrouped singularities in two classes: i) $\alpha$ singularities which have ``large'' imaginary parts, and ii) $\beta$ singularities which have very small imaginary parts.
+Singularities of type $\alpha$ are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
 They succeeded to explain the divergence of the series caused by $\beta$ singularities using a previous work of Stillinger \cite{Stillinger_2000}.
 
-To understand the convergence properties at $\lambda=1$ of the perturbation series one need to look at the whole complex plane.
-In particular for real negative value of $\lambda$.
-If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field stays repulsive as it is proportional to $(1-\lambda)$.
+To understand the convergence properties of the perturbation series at $\lambda=1$, one must look at the whole complex plane, in particular, for negative (i.e., real) values of $\lambda$.
+If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field (which has been computed at $\lambda = 1$) remains repulsive as it is proportional to $(1-\lambda)$:
 
 \begin{equation}\label{eq:HamiltonianStillinger}
-    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of }\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{Attractive}}  \right]
+    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of $\lambda$}} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
 \end{equation}
 
-The major difference between those two terms is that the repulsive mean field is localized around nucleus whereas the electrons interactions persist away from nuclei.
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so the nuclei can not bind the electrons anymore because the electron-nucleus attraction is not scaled with $\lambda$.
-There is a real negative value $\lambda_c$ where the electrons form a bound cluster and goes to infinity.
-According to Baker this value is a critical point of the system and by analogy with thermodynamics the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$ \cite{Baker_1971}.
-At this point the system undergo a phase transition and a symmetry breaking.
-Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.
+The major difference between those two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
+For $\lambda = \lambda_c$, the electrons form a bound cluster that dissociates from the nuclei \titou{by going towards $\lambda = -\infty$.} According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
+At this point the system undergo a phase transition \titou{and a symmetry breaking}.
+\titou{Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.}
 
 This reasoning is done on the exact Hamiltonian and energy, this is the exact energy which exhibits this singularity on the negative real axis. 
-But in a finite basis set, one can prove that for a Hermitian Hamiltonian the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-They explain that Olsen et al., because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
+\titou{The Hamiltonian can be exact in a finite basis. I wonder if it would not be more judicious to talk about complete/infinite Hilbert space and finite Hilbert space.}
+However, in a finite basis set, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger, \cite{} that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+They explain that Olsen et al., \cite{} because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
 
@@
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-According to Goodson the singularity structure from molecules stretched from the equilibrium geometry is difficult \cite{Goodson_2004}, this is consistent with the observation of Olsen and co-workers on the \ce{HF} molecule at equilibrium geometry and stretched geometry \cite{Olsen_2000}.
-To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function hasn't been as well understood as the ionization effect and its link with diffuse function.
-In this work we try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
+According to Goodson, \cite{Goodson_2004} the singularity structure from molecules stretched from the equilibrium geometry is difficult, this is consistent with the observation of Olsen and co-workers  \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.
+To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization effect and its link with diffuse function.
+In this work we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
 

### 2020-07-23 RapportStage/Rapport.tex
update

--- 2020-07-23 RapportStage/Rapport.tex
@@
 \newcommand{\bV}{\mathbf{V}}
+\newcommand{\pt}{$\mathcal{PT}$}
 
@@
 
-\textbf{\huge Pertubation theory in the complex plane}
+\textbf{\huge Pertubation theories in the complex plane}
 
@@
 \parbox{15cm}{\small
-\textbf{Abstract} : \it In this work, we explore the extension of quantum chemistry in the complex plane.
-We observe that the physics of a quantum system is intimately connected to the position of the energy singularities in the complex plane.
-After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
-Then we connect and further discuss these different aspects using the spherium model (i.e., two opposite-spin electrons restricted to remain on the surface of a sphere) as a theoretical playground.
-In particular, we explore various perturbative partitioning strategies and the effects of symmetry breaking on the singularity structure of the electronic energy.
-This provides fundamental insights on the location of these singularities in the complex plane (that one calls exceptional points) and, specifically, on the magnitude of the radius of convergence associated with the perturbative treatment.
+\textbf{Abstract} : \it In this work, we explore the description of quantum chemistry in the complex plane.
+We see that the physics of the system can be connected to the position of the energy singularities in the complex plane.
+After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we perform an historical review of the researches that have been done on the physic of singularities.
+Then we connect all those points of view on this problem using the spherium model (i.e., two opposite-spin electrons restricted to remain on the surface of a sphere of radius $R$) as a theoretical playground.
+In particular, we explore the effects of symmetry breaking of the wave functions on the singularity structure.
 }
@@
 \parbox{15cm}{
-\textbf{Keywords} : \it quantum chemistry, perturbation theory, complex plane, spherium, exceptional points, radius of convergence, symmetry breaking
+\textbf{Keywords} : \it Quantum chemistry, Perturbation theory,  Spherium, Exceptional points, Symmetry breaking
 } %fin de la commande \parbox des mots clefs
@@
 
-\url{https://www.irsamc.ups-tlse.fr/loos}
+\url{https://www.irsamc.ups-tlse.fr/}
 } %fin de la commande \parbox encadrant / laboratoire d'accueil
@@
 Around $\lambda = \lambda_\text{EP}$, Eq.~\eqref{eq:E_2x2} behaves as \cite{MoiseyevBook}
-\begin{equation} \label{eq:E_EP}
+\begin{equation}
         E_{\pm} = E_\text{EP} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}},
@@
 
-The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
-\begin{equation} \label{eq:phi_2x2}
-\phi_{\pm}=
-	\begin{pmatrix}
-		E_{\pm}/\lambda
-		\\ 
-		1
+The eigenvectors associated to the energies \eqref{eq:E_2x2} are
+\begin{equation}\label{ev2x2}
+\phi_{\pm}=\begin{pmatrix}
+\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
 \end{pmatrix},
 \end{equation}
-and, for $\lambda=\lambda_\text{EP}$, they become
+and for $\lambda=\lambda_\text{EP}$ they become
 \begin{equation}
@@
 \end{equation}
-which are clearly self-orthogonal. 
-\titou{what do you mean by self-orthogonal?}
-Using Eq.~\eqref{eq:E_EP}, Eq.~\eqref{eq:phi_2x2} can be recast as
+which are clearly self-orthogonal. The equation (7) can be rewrite as
 \begin{equation}
-\phi_{\pm}=
-	\begin{pmatrix}
-		E_\text{EP}/\lambda \pm \sqrt{2\lambda_\text{EP}/\lambda} \sqrt{1 - \lambda_\text{EP}/\lambda} 
-		\\ 
-		1
+\phi_{\pm}=\begin{pmatrix}
+\frac{1}{\lambda}(\frac{\epsilon_1 - \epsilon_2}{2} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}) \\ 1
 \end{pmatrix},
 \end{equation}
-where one clearly see that, if normalised, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
+we can see that if we normalise them they will behave as
+$(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
 \begin{align}
@@
 \end{align}
-\titou{I don't think it is too obvious that the eigenvectors behave as $(\lambda - \lambda_\text{EP})^{-1/4}$.}
-In plain words, four loops around the EP are necessary to recover the initial state. 
-We can also see that looping the other way around leads to a different pattern.
+showing that 4 loops around the EP are necessary to recover the initial state. We can also see that looping the other way round leads to a different pattern.
 
@@
 In this part, we will try to investigate how some parameters of $\bH(\lambda)$ influence the radius of convergence of the perturbation series.
-The radius of convergence is equal to the closest singularity to the origin of $E(\lambda)$ so we need to determine the locations of the exceptional points.
+The radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
+Hence we need to determine the locations of the exceptional points to obtain information on the convergence properties.
 To find them we solve simultaneously the equations \eqref{eq:PolChar} and \eqref{eq:DPolChar}.
@@
 Hence we can forget the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
-In the restricted formalism the spatial orbitals are the same so the two-electron basis set is:
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set is defined as:
 
@@
 
-The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set ($\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$).
-The two singly excited states yields a singlet and a triplet sp\textsubscript{z} but they don't have the appropriate symmetry so these states can't form exceptional points with the ground state.
-However there is an avoided crossing (see Fig.
-\ref{fig:RHFMiniBas}) between the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} which is connected to two exceptional points in the complex plane.
+The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set i.e.
+$\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
+The two singly excited states give a singlet sp\textsubscript{z} and a triplet sp\textsubscript{z} state but their symmetry is not the same as the ground state.
+Thus these states can not be involved in an avoided crossing with the ground state as it can be seen in \autoref{fig:RHFMiniBas} and a fortiori can not be involved in an exceptional point with the ground state.
+However there is an avoided crossing between the s\textsuperscript{2} state and the p\textsubscript{z}\textsuperscript{2} one which gives two exceptional points in the complex plane.
 
@@
 
-To simplify the problem, it is convenient to only consider basis function with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
+To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
+It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties i.e.
+the exceptional points between states with the same symmetry.
 In this case the ground state is a totally symmetric singlet.
-According to the angular-momentum theory we expand the exact wave function in the following two-electron basis:
+According to the angular-momentum theory \cite{AngularBook, SlaterBook, Loos_2009} we expand the exact wave function in the following two-electron basis:
 \begin{equation}
@@
 The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
-$P_0$ and $P_1$ and in the three function basis.
-We see that the radius of convergence of the strong coupling partitioning is growing with R whereas it is decreasing for the three other partitioning.
+$P_0$ and $P_1$ and in the same basis augmented with $P_2$.
+We see that the radius of convergence of the strong coupling partitioning is growing with R whereas it is decreasing for the three others partitioning.
 This result was expected because the three decreasing partitioning use a weakly correlated reference so $\bH^{(0)}$ is a good approximation for small $R$.
-On the contrary the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated i.e.
+On the contrary, the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated i.e.
 when $R$ is large for the spherium model.
@@
 In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
-Whereas the M{\o}ller-Plesset reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
-Moreover it can be proved that the n-th order energy of the weak correlation series can be obtained as a limited development of MP$n$ respective to $R$.
+Whereas the M{\o}ller-Plesset reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the M{\o}ller-Plesset series is not well-defined in terms of powers of $R$.
+Moreover it can be proved that the $n$-th order energy of the weak correlation series can be obtained as a  Taylor approximation of MP$n$ respective to $R$.
 It seems that the Epstein-Nesbet partitioning is better than the M{\o}ller-Plesset one for very small R in the minimal basis.
 In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2
-$ (and in larger basis set) the M{\o}ller-Plesset series converge faster for all value of $R$.
+$ (and in larger basis set) the M{\o}ller-Plesset series has a greater radius of convergence for all value of $R$.
 
@@
 In the UHF formalism the Hamiltonian $\bH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix element for this  interaction is proportional to $\sqrt{-3+2R}$.
-For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix element become real.
+The matrix element for this  interaction is given in \eqref{eq:MatrixElem}.
+For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix element becomes real.
 This interaction corresponds to the spin contamination of the wave function.
 For $R<3/2$ the matrix element is complex, this corresponds to the holomorphic solution of \autoref{fig:SpheriumNrj}, the singularities in this case will be treated in \autoref{sec:uhfSing}.
+This matrix element becomes real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in \autoref{sec:spherium}.
+We will refer to the domain where the matrix element becomes complex as the holomorphic domain.
 
-The singularity structure in this case is more complex because of this spin contamination because we can't use configuration state function.
-So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some corresponds to EPs and some to conical intersections.
+\begin{equation}\label{eq:MatrixElem}
+\sqrt{-3+2R}\sqrt{75+62R}\frac{25+2R}{280R^3}
+\end{equation}
+
+The singularity structure in this case is more complex because of the spin contamination of the wave function.
+We can not use configuration state function in this case.
+So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
 The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
@@
     \includegraphics[width=0.7\textwidth]{EMP_UHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:rhfbasis} with $R=10$.}
+    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:uhfbasis} with $R=10$.}
     \label{fig:UHFMiniBas}
@@
 
-RHF vs UHF
+In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in \autoref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are connected to $\beta$ singularities.
+For example.
+However in the spherium the electrons can't be ionized so those singularities are not the $\beta$ singularities highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
+\antoine{Changer ce passage} We can see in \autoref{fig:UHFEP} that the sharp avoided crossing between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet appears for $R>3/2$.
+As presented before $\beta$ singularities are linked to quantum phase transition so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
+The fact that a similar pair of $\beta$ singularities appear for $R<-75/62$ confirms this assumption.
+A second pair of $\beta$ singularities appear for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
 
-UHF spin contamination -> Riemann surfaces ??
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
+    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
+    \caption{\centering .}
+    \label{fig:UHFEP}
+\end{figure}
 
-UHF: CF point = QPT, ESQPT ???
+As shown before, some matrix elements of the Hamiltonian become complex for $R<3/2$ so this Hamiltonian becomes non-Hermitian for those value of $R$.
+In \cite{Burton_2019a} Burton et al.
+proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
+An analog reasoning can be done with the spherium model to prove the same result.
+The \pt -symmetry (invariance with respect to combined space reflection $\mathcal{P}$ and time reversal $\mathcal{T}$) is a property which ensures that a non-Hermitian Hamiltonian has a real energy spectrum.
+Thus \pt -symmetric Hamiltonian can be seen as an intermediate between Hermitian and non-Hermitian.
+In our case we can see in Figure x that a part of the energy spectrum becomes complex when R is in the holomorphic domain.
+This part of the spectrum where the energy becomes complex is called the broken \pt symmetry  region.
+This is consistent with the fact that in the holomorphic domain the Hamiltonian break the \pt -symmetry.
 
-PT broken symmetry sb UHF
+For a non-Hermitian Hamiltonian the exceptional points can lie on the real axis.
+In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate so it is an exceptional.
+We can see this phenomenon on Figure x, the points of PT transition are indicate by .
 

### 2020-07-23 RapportStage/Rapport.tex
update thursday

--- 2020-07-23 RapportStage/Rapport.tex
@@
 
+The eigenvectors associated to the energies \eqref{eq:E_2x2} are
+\begin{equation}\label{ev2x2}
+\phi_{\pm}=\begin{pmatrix}
+\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
+\end{pmatrix},
+\end{equation}
 The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
@@
 	\begin{pmatrix}
-		E_{\pm}/\lambda
+		(E_{\pm}-2\epsilon_2)/\lambda
 		\\ 
@@
 	\begin{pmatrix}
-		E_\text{EP}/\lambda \pm \sqrt{2\lambda_\text{EP}/\lambda} \sqrt{1 - \lambda_\text{EP}/\lambda} 
+		(\epsilon_1-\epsilon_2)/\lambda \pm \sqrt{2\lambda_\text{EP}/\lambda} \sqrt{1 - \lambda_\text{EP}/\lambda} 
 		\\ 
@@
 	&
-	\phi_{\pm}(8\pi) & = \phi_{\pm}(0),
+	\phi_{\pm}(8\pi) & = \phi_{\pm}(0).
 \end{align}
-\titou{I don't think it is too obvious that the eigenvectors behave as $(\lambda - \lambda_\text{EP})^{-1/4}$.}
 In plain words, four loops around the EP are necessary to recover the initial state. 
 We can also see that looping the other way around leads to a different pattern.
+\titou{I don't think it is too obvious that the eigenvectors behave as $(\lambda - \lambda_\text{EP})^{-1/4}$.}
 
@@
 However, in a finite basis set, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger, \cite{} that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-They explain that Olsen et al., \cite{} because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
+Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger \cite{Stillinger_2000}, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+They explain that Olsen et al., because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
 
@@
 In the UHF formalism the Hamiltonian $\bH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix element for this  interaction is proportional to $\sqrt{-3+2R}$.
-For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix element become real.
+The matrix elements $H_{ij}$ for this interaction are given in \eqref{eq:MatrixElem}.
+For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$ the matrix element is complex, this corresponds to the holomorphic solution of \autoref{fig:SpheriumNrj}, the singularities in this case will be treated in \autoref{sec:uhfSing}.
+For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of \autoref{fig:SpheriumNrj}, the singularities in this case will be treated in \autoref{sec:uhfSing}.
+The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in \autoref{sec:spherium}.
+We will refer to the domain where the matrix element are complex as the holomorphic domain.
 
-The singularity structure in this case is more complex because of this spin contamination because we can't use configuration state function.
-So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some corresponds to EPs and some to conical intersections.
+\begin{equation}\label{eq:MatrixElem}
+H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{-3+2R}\sqrt{75+62R}\frac{25+2R}{280R^3}
+\end{equation}
+
+The singularity structure in this case is more complex because of the spin contamination of the wave function.
+We can not use configuration state function in this case.
+So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
 The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.

### 2020-07-23 RapportStage/Rapport.tex
some modifications in 3.1

@@
 But as mentioned before \textit{a priori} there are no reasons that $E_{\text{MP}_{n}}$ is always convergent when $n$ goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the M{\o}ller-Plesset method will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-A smart way to investigate the convergence properties of the M{\o}ller-Plesset series is to transform the coupling parameter $\lambda$ into a complex variable.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the MP method will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
 By doing so the Hamiltonian and the energy become functions of this variable.
 The energy becomes a multivalued function on $n$ Riemann sheets.
-As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the M{\o}ller-Plesset perturbation theory.
+As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MP perturbation theory.
 Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
 The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost \cite{JensenBook}.
-But to deeply understand the behavior of the M{\o}ller-Plesset series and how it is connected to the singularities, we need to have access to high order terms of the series.
+But to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
 For small systems we can have access to the whole series using Full Configuration Interaction (FCI).
-If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and expanding in $\lambda$ allows to to get the M{\o}ller-Plesset perturbation series at every order.
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and expanding in $\lambda$ allows to to get the MP perturbation series at every order.
 
@@
 
-The M{\o}ller-Plesset partitioning is not the only one possible in electronic structure theory.
-An other possibility, even more natural than the M{\o}ller-Plesset one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
+The MP partitioning is not the only one possible in electronic structure theory.
+An other possibility, even more natural than the MP one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
 Hence, the off-diagonal elements of $\bH(\lambda)$ are the perturbation operator.
 This partitioning leads to the Epstein-Nesbet (EN) perturbation theory.
-The zeroth-order eigenstates for this partitioning are Slater determinants as for the M{\o}ller-Plesset partitioning.
-The expression of the second order correction to the energy is given for both M{\o}ller-Plesset and Epstein-Nesbet.
+The zeroth-order eigenstates for this partitioning are Slater determinants as for the MP partitioning.
+The expression of the second order correction to the energy is given for both MP and EN.
 The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies.
@@
 
-When we use M{\o}ller-Plesset perturbation theory it would be very convenient that each time a higher order term is computed the result obtained is closer to exact energy.
-In other words, that the M{\o}ller-Plesset series would be monotonically convergent.
-Assuming this, the only limiting process to get the exact correlation energy in a finite basis set is our ability to compute the terms of the perturbation series.
-Unfortunately this is not true in generic cases and rapidly some strange behaviors of the series were exhibited.
-In the late 80's Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-In \autoref{fig:RUMP_Gill} we can see that the restricted M{\o}ller-Plesset series is convergent but oscillating which is not convenient if you are only able to compute few terms (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted M{\o}ller-Plesset series is monotonically converging (except for the first few orders) but very slowly so we cannot use it for systems where we can only compute the first terms.
+When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, i.e., one would expect that the more terms of the perturbative series one has, the closer the result from the exact energy.
+%In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
+In other words, one would like a monotonic convergence of the MP series.
+Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
+Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
+In \autoref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
 
@@
 
-When a bond is stretched the exact wave function becomes more and more multi-reference.
-Yet the Hartree-Fock wave function is restricted to be single reference so it can not model properly stretched system.
-Nevertheless the Hartree-Fock wave function can undergo a symmetry breaking to minimize its energy losing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in \cite{SzaboBook}).
-A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series does not give accurate results at low orders.
-Even with this improvement of the zeroth order wave function the series does not have the smooth and rapidly converging behavior wanted.
+When a bond is stretched the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be single Slater determinant.
+Thus, it is inappropriate to model (even qualitatively) stretched system.
+Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in Ref.~\cite{SzaboBook}).
+\titou{A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series does not give accurate results at low orders.} Even with this improvement of the zeroth-order wave function the series does not have the smooth and rapidly converging behavior wanted.
 
@@
     \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
-    \begin{tabular}{c c c c c c c}
+    \begin{tabular}{ccccccc}
+\hline
 \hline
@@
 \hline
+\hline
 \end{tabular}
@@
 In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function which leads to spin contamination.
-Gill et al.~highlighted the link between the slow convergence of the unrestricted MP series and the spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
-Handy and co-workers exhibited the same behaviors of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
-Lepetit et al.~analyzed the difference between the M{\o}ller-Plesset and Epstein-Nesbet partitioning for the unrestricted Hartree-Fock reference \cite{Lepetit_1988}.
-They concluded that the slow convergence is due to the coupling of the singly with the doubly excited configuration.
-Moreover the MP and EN numerators in Eq.
-\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
-Yet the MP denominators tends towards a constant when $r\rightarrow\infty$ so the terms vanish.
-Where as the EN denominators tends to 0 which improve the convergence but can also make diverge the series.
-Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all the systems in two classes.
-The class A systems which have a monotonic convergence to the FCI value and the class B which converge erratically after initial oscillations.
-The sample of systems contains stretched molecules and also some at equilibrium geometry, there are also some systems in various basis sets.
-They highlighted that \cite{Cremer_1996}\begin{quote}
-\textit{Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.}
+Gill \textit{et al.}~highlighted the link between slow convergence of the unrestricted MP series and spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
+Handy and coworkers exhibited the same behavior of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
+Lepetit et al.~analyzed the difference between the MP and EN partitioning for the unrestricted HF reference \cite{Lepetit_1988}.
+They concluded that the slow convergence is due to the coupling of the singly and doubly excited configurations.
+Moreover, the MP and EN numerators in Eqs.~\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
+Yet the MP denominators tends towards a constant when $r \to \infty$ so the terms vanish, whereas the EN denominators tends to zero which improves the convergence but can also make the series diverge.
+Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all of these systems in two classes.
+The class A systems where one observes a monotonic convergence to the FCI energy and the class B for which convergence is erratic after initial oscillations.
+The sample of systems contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
+They highlighted that \cite{Cremer_1996}
+\begin{quote}
+	\textit{``Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
 \end{quote}
-They proved that using different extrapolation formulas of the first terms of the M{\o}ller-Plesset of the series for class A and class B systems improve the precision of those formulas.
-The mean deviation from FCI correlation energies is 0.3 mhartrees whereas with the formula that do not distinguish the system it is 12 mhartrees.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the M{\o}ller-Plesset perturbation theory and to more accurate correlation energies.
+They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.
+The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
 
@@
 
-However Olsen et al.
-have discovered an even more preoccupying behavior of the MP series in the late 90's.
+However Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series in the late 90's.
 They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
@@
 \begin{itemize}
-	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [restricted Hartree-Fock (RHF) or unrestricted Hartree-Fock (UHF) references, M{\o}ller-Plesset or Epstein-Nesbet (EN) partitioning], or strongly correlated reference.
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [restricted Hartree-Fock (RHF) or unrestricted Hartree-Fock (UHF) references, MP or EN partitioning], or strongly correlated reference.
 	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions
@@
 \caption{\centering RHF and UHF energies in the minimal basis and exact energies for various R.}
-\begin{tabular}{c c c c c c c c c}
+\begin{tabular}{ccccccccc}
+\hline
+\hline
 $R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
 \hline
-RHF & 10 & 1 & 0.5 & 0.3333 & 0.2 & 0.1 & 0.01 & 0.001 \\
+RHF 	& 10.00000 & 1.000000 & 0.500000 & 0.333333 & 0.200000 & 0.100000 & 0.010000 & 0.001000 \\
+UHF 	& 10.00000 & 1.000000 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
+Exact 	& 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
 \hline
-UHF & 10 & 1 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
 \hline
-Exact & 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
 \end{tabular}
@@
 Then using this basis set we can compare the different partitioning of \autoref{sec:AlterPart}.
-The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
+The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
 $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
@@
 when $R$ is large for the spherium model.
-The M{\o}ller-Plesset partitioning is always better than the weak correlation in \autoref{fig:RadiusPartitioning}.
+The MP partitioning is always better than the weak correlation in \autoref{fig:RadiusPartitioning}.
 In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
-Whereas the M{\o}ller-Plesset reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the M{\o}ller-Plesset series is not well-defined in terms of powers of $R$.
+Whereas the MP reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
 Moreover it can be proved that the $n$-th order energy of the weak correlation series can be obtained as a  Taylor approximation of MP$n$ respective to $R$.
-It seems that the Epstein-Nesbet partitioning is better than the M{\o}ller-Plesset one for very small R in the minimal basis.
+It seems that the EN partitioning is better than the MP one for very small R in the minimal basis.
 In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2
-$ (and in larger basis set) the M{\o}ller-Plesset series has a greater radius of convergence for all value of $R$.
+$ (and in larger basis set) the MP series has a greater radius of convergence for all value of $R$.
 
@@
 This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities.
-The discontinuities observed in \autoref{fig:RadiusBasis} with the M{\o}ller-Plesset partitioning are due to a change of the dominant singularity.
+The discontinuities observed in \autoref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
 \\

### 2020-07-24 RapportStage/Rapport.tex
saving work in 3.2

@@
 
-However Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series in the late 90's.
-They have shown that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
-Cremer and He had already studied those two systems and classified them as class B systems.
-But Olsen and his co-workers have done the analysis in larger basis sets containing diffuse functions and in those basis sets the series become divergent at high order.
+In the late 90's, Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series \cite{}.
+They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
+Cremer and He had already studied these two systems and classified them as ``class B'' systems.
+However, the analysis of Olsen and coworkers was performed in larger basis sets containing diffuse functions.
+In these basis sets, they found that the series become divergent at (very) high order.
 
@@
 
-The discovery of this divergent behavior was really worrying because in order to get more and more accurate results theoretical chemists need to work in large basis sets.
-As a consequence they investigated the causes of those divergences and in the same time the reasons of the different types of convergence.
-To do this they analyzed the relation between the dominant singularity (i.e.
-the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
+The discovery of this divergent behavior is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
+Including diffuse functions is particularly important for the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
+As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence.
+To do so, they analyzed the relation between the dominant singularity (i.e., the closest singularity to the origin) and the convergence behavior of the series \cite{Olsen_2000}.
 Their analysis is based on Darboux's theorem:
@@
 A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
-The method used is to do a scan of the real axis to identify the avoided crossing responsible for the pair of dominant singularity.
-Then by modeling this avoided crossing by a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $2\times2$ Hamiltonian.
+Theie method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularity.
+Then by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $2\times2$ Hamiltonian.
 The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbative part of the Hamiltonian.

### 2020-07-24 RapportStage/Rapport.tex
update skype

--- 2020-07-23 RapportStage/Rapport.tex
@@
     \includegraphics[width=0.7\textwidth]{EMP_RHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:rhfbasis} with $R=10$.}
+    \caption{\centering Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
     \label{fig:RHFMiniBas}
@@
     \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
-    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian$\bH(\lambda)$.}
+    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian $\bH(\lambda)$.}
     \label{fig:RadiusPartitioning}
@@
 The discontinuities observed in \autoref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
-\\
+We can observe this change in \autoref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative plane.
 
@@
 \centering
-\caption{\centering }
-\begin{tabular}{c}
-a
+\caption{\centering Dominant singularity in the CSF basis set ($n=8$) for various value of R. The first line is the value for the MP partitioning and the second for the WC one.}
+\begin{tabular}{cccccccc}
+\hline
+\hline
+$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
+\hline
+MP & 14.1-10.9i & 2.38-1.47i & -0.67-1.30i & -0.49-0.89i & -0.33-0.55i & -0.22-0.31i & 0.03-0.05i \\
+WC & -9.6-10.7i & -0.96-1.07i & -0.48-0.53i & -0.32-0.36 & -0.19-0.21i & -0.10-0.11i & -0.01-0.01i \\
+\hline
+\hline
 \end{tabular}
@@
     \includegraphics[width=0.7\textwidth]{EMP_UHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the basis set \eqref{eq:uhfbasis} with $R=10$.}
+    \caption{\centering Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
     \label{fig:UHFMiniBas}
@@
 In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in \autoref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are connected to $\beta$ singularities.
-For example.
+For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014i$.
+And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023i$.
 However in the spherium the electrons can't be ionized so those singularities are not the $\beta$ singularities highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
-\antoine{Changer ce passage} We can see in \autoref{fig:UHFEP} that the sharp avoided crossing between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet appears for $R>3/2$.
+We can see in \autoref{fig:UHFEP} that the degeneracy between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet at $R=3/2$.
+For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are moved in the complex plane.
+The wave function is spin contaminated for $R>3/2$ this why the s\textsuperscript{2} singlet energy can not cross the sp\textsubscript{z} triplet curves anymore.
+When $R$ increases this avoided crossing becomes sharper.
 As presented before $\beta$ singularities are linked to quantum phase transition so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
-The fact that a similar pair of $\beta$ singularities appear for $R<-75/62$ confirms this assumption.
+The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
 A second pair of $\beta$ singularities appear for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
@@
     \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
-    \caption{\centering .}
+    \caption{\centering Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
     \label{fig:UHFEP}
@@
 
-As shown before, some matrix elements of the Hamiltonian become complex for $R<3/2$ so this Hamiltonian becomes non-Hermitian for those value of $R$.
+As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
+Therefore the Hamiltonian becomes non-Hermitian for those value of $R$.
 In \cite{Burton_2019a} Burton et al.
@@
 Thus \pt -symmetric Hamiltonian can be seen as an intermediate between Hermitian and non-Hermitian.
+
  In our case we can see in Figure x that a part of the energy spectrum becomes complex when R is in the holomorphic domain.

### 2020-07-24 RapportStage/Rapport.tex
braket

@@
 \end{equation}
-which correspond to square-root singularities in the complex-$\lambda$ plane (see Fig.~\ref{fig:2x2}).
+which correspond to square-root singularities in the complex-$\lambda$ plane (see \autoref{fig:2x2}).
 These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
@@
 \begin{equation}\label{eq:EMP2}
-E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\bra{ij}\hspace{1pt}\ket{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s}
+E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\mel{ij}{}{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s}
 \end{equation}
 \begin{equation}\label{eq:EEN2}
-E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\bra{ij}\hspace{1pt}\ket{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s - (J_{ij} + J_{rs} - J_{ir} - J_{is} - J_{jr} + J_{js})}
+E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\mel{ij}{}{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s - (J_{ij} + J_{rs} - J_{ir} - J_{is} - J_{jr} + J_{js})}
 \end{equation}
@@
 \begin{equation}
-\bra{ij}\hspace{1pt}\ket{rs}=\bra{ij}\ket{rs} - \bra{ij}\ket{sr}
+	\mel{ij}{}{rs}=\braket{ij}{rs} - \braket{ij}{sr}
 \end{equation}
-where $\bra{ij}\ket{rs}$ is the two-electron integral
+where $\braket{ij}{rs}$ is the two-electron integral
 \begin{equation}
-\bra{ij}\ket{rs}=\int \dd\vb{x}_1\dd\vb{x}_2\chi_i^*(\vb{x}_1)\chi_j^*(\vb{x}_2)r_{12}^{-1}\chi_r(\vb{x}_1)\chi_s(\vb{x}_2)
+\braket{ij}{rs}=\int \dd\vb{x}_1\dd\vb{x}_2\chi_i^*(\vb{x}_1)\chi_j^*(\vb{x}_2)r_{12}^{-1}\chi_r(\vb{x}_1)\chi_s(\vb{x}_2)
 \end{equation}

### 2020-07-24 RapportStage/Rapport.tex
corrections skype

@@
 
-The eigenvectors associated to the energies \eqref{eq:E_2x2} are
-\begin{equation}\label{ev2x2}
+The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
+\begin{equation}\label{eq:phi_2x2}
 \phi_{\pm}=\begin{pmatrix}
-\frac{1}{2\lambda}(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}) \\ 1
-\end{pmatrix},
-\end{equation}
-The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
-\begin{equation} \label{eq:phi_2x2}
-\phi_{\pm}=
-	\begin{pmatrix}
-		(E_{\pm}-2\epsilon_2)/\lambda
-		\\ 
-		1
+(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2})/2\lambda \\ 1
 \end{pmatrix},
@@
 and, for $\lambda=\lambda_\text{EP}$, they become
-\begin{equation}
-\phi_{\pm}=\begin{pmatrix}
-\mp i \\ 1
-\end{pmatrix},
-\end{equation}
-which are clearly self-orthogonal. 
-\titou{what do you mean by self-orthogonal?}
+\begin{align}
+	\phi_{\pm}(i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} -i \\ 1\end{pmatrix},
+	&
+	\phi_{\pm}(-i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} i \\ 1\end{pmatrix}.
+\end{align}
+which are self-orthogonal i.e. their norm is equal to zero. 
 Using Eq.~\eqref{eq:E_EP}, Eq.~\eqref{eq:phi_2x2} can be recast as
-\begin{equation}
+\begin{equation}\label{eq:phi_EP}
 \phi_{\pm}=
 	\begin{pmatrix}
-		(\epsilon_1-\epsilon_2)/\lambda \pm \sqrt{2\lambda_\text{EP}/\lambda} \sqrt{1 - \lambda_\text{EP}/\lambda} 
+		(\epsilon_1-\epsilon_2)/2\lambda \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}/\lambda 
 		\\ 
 		1
-	\end{pmatrix},
+	\end{pmatrix}.
 \end{equation}
-where one clearly see that, if normalised, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$ resulting in the following pattern when looping around one EP:
+We have seen that the EP inherits its topology from the double valued function $\sqrt{\lambda - \lambda_\text{EP}}$.
+Then if the eigenvectors are normalised they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$ which gives the following pattern when looping around one EP:
 \begin{align}
@@
 We can also see that looping the other way around leads to a different pattern.
-\titou{I don't think it is too obvious that the eigenvectors behave as $(\lambda - \lambda_\text{EP})^{-1/4}$.}
+\antoine{Is this a bit better like this ?}
 
@@
 \begin{equation}\label{eq:EMP2}
-E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\mel{ij}{}{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s}
+E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b}
 \end{equation}
@@
 \begin{equation}
-	\mel{ij}{}{rs}=\braket{ij}{rs} - \braket{ij}{sr}
+	\mel{ij}{}{ab}=\braket{ij}{ab} - \braket{ij}{ba}
 \end{equation}
-where $\braket{ij}{rs}$ is the two-electron integral
+where $\braket{ij}{ab}$ is the two-electron integral
 \begin{equation}
-\braket{ij}{rs}=\int \dd\vb{x}_1\dd\vb{x}_2\chi_i^*(\vb{x}_1)\chi_j^*(\vb{x}_2)r_{12}^{-1}\chi_r(\vb{x}_1)\chi_s(\vb{x}_2)
+\braket{ij}{ab}=\int \dd\vb{x}_1\dd\vb{x}_2\phi_i^*(\vb{x}_1)\phi_j^*(\vb{x}_2)r_{12}^{-1}\phi_a(\vb{x}_1)\phi_b(\vb{x}_2)
 \end{equation}
@@
 Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in Ref.~\cite{SzaboBook}).
-\titou{A restricted HF Slater determinant is a poor approximation of a symmetry-broken wave function but even in the unrestricted formalism, where the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}, which allows a better description of symmetry-broken system, the series does not give accurate results at low orders.} Even with this improvement of the zeroth-order wave function the series does not have the smooth and rapidly converging behavior wanted.
+\antoine{It could be expected that  the restricted MP series has inappropriate convergence properties as a restricted HF Slater determinant is a poor approximation of the exact wave function for stretched system.
+However even in the unrestricted formalism the series does not give accurate results at low orders.
+Whereas the unrestricted formalism allows a better description of a stretched system because the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}.} Even with this improvement of the zeroth-order wave function the series does not have the smooth and rapidly converging behavior wanted.
 
@@
 \begin{equation}\label{eq:HamiltonianStillinger}
-    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of $\lambda$}} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
+    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of}~\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
 \end{equation}
@@
 If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
-For $\lambda = \lambda_c$, the electrons form a bound cluster that dissociates from the nuclei \titou{by going towards $\lambda = -\infty$.} According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
+\antoine{For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei}.
+According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
 At this point the system undergo a phase transition \titou{and a symmetry breaking}.
@@
 
-This reasoning is done on the exact Hamiltonian and energy, this is the exact energy which exhibits this singularity on the negative real axis. 
-\titou{The Hamiltonian can be exact in a finite basis. I wonder if it would not be more judicious to talk about complete/infinite Hilbert space and finite Hilbert space.}
-However, in a finite basis set, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+\antoine{This reasoning is done on the exact Hamiltonian and energy i.e.
+the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis}.
+\antoine{However, in a finite basis set which does not span the complete Hilbert space}, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
 Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger \cite{Stillinger_2000}, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
@@
 These QPTs exist both for ground and excited states as shown by Cejnar and coworkers \cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019}.
-A ground-state QPT is characterized by the \titou{successive?} derivative of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
+A ground-state QPT is characterized by the derivatives of the ground-state energy with respect to a non-thermal control parameter \cite{Cejnar_2009, Sachdev_2011}.
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
@@
 Those excited states have a non-negligible contribution to the exact FCI solution because they have the same spatial and spin symmetry as the ground state.
-We think that $\alpha$ singularities are connected to the multi-reference behavior of the wave function in the same way as $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function.
-\titou{I am not sure I agree with your last comment. Maybe, we can talk about it tomorrow.}
+\antoine{We think that $\alpha$ singularities are connected the states with non-negligible contribution in the configuration interaction expansion thus to the dynamical part of the correlation energy.
+Whereas the $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function i.e.
+the multi-reference aspect of the wave function thus to the static part of the correlation energy.}
 
@@
 
- In our case we can see in Figure x that a part of the energy spectrum becomes complex when R is in the holomorphic domain.
+ In our case we can see in \autoref{fig:UHFPT} that a part of the energy spectrum becomes complex when R is in the holomorphic domain.
 This part of the spectrum where the energy becomes complex is called the broken \pt symmetry  region.
 This is consistent with the fact that in the holomorphic domain the Hamiltonian break the \pt -symmetry.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
+    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
+    \caption{\centering Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
+    \label{fig:UHFPT}
+\end{figure}
 

### 2020-07-24 RapportStage/Rapport.tex
few modifications

@@
 The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies.
-The i,j indices represent the occupied orbitals and r,s the virtual orbitals of the basis sets.
+The i,j indices represent the occupied orbitals and a,b the virtual orbitals of the basis sets.
 
@@
 \begin{equation}\label{eq:EEN2}
-E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ r<s}}^{n}\frac{\abs{\mel{ij}{}{rs}}^2}{\epsilon_i + \epsilon_j - \epsilon_r - \epsilon_s - (J_{ij} + J_{rs} - J_{ir} - J_{is} - J_{jr} + J_{js})}
+E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{}
 \end{equation}
@@
 In the late 90's, Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series \cite{}.
-They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} \cite{Olsen_1996, Christiansen_1996}.
+They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} (see \autoref{fig:NeHFDiv}) \cite{Olsen_1996, Christiansen_1996}.
 Cremer and He had already studied these two systems and classified them as ``class B'' systems.
@@
     \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from \cite{Olsen_1996}).}
-    \label{fig:my_label}
+    \label{fig:NeHFDiv}
 \end{figure}
@@
 Then using this basis set we can compare the different partitioning of \autoref{sec:AlterPart}.
-The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
+\autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
 $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
@@
 
-The \autoref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
+\autoref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
 The CSF basis function have all the same spin and spatial symmetry so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
@@
     \includegraphics[width=0.45\textwidth]{WCElargebasis.pdf}
-    \caption{\centering Radius of convergence in the CSF basis with $n$ basis function for the MP partitioning (left) and the WC partitioning (right).}
+    \caption{\centering Radius of convergence in the CSF basis with $K$ basis function for the MP partitioning (left) and the WC partitioning (right).}
     \label{fig:RadiusBasis}
@@
 \end{align*}
+
 In the UHF formalism the Hamiltonian $\bH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
@@
 The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
-The \autoref{fig:UHFMiniBas} is the analog of \autoref{fig:RHFMiniBas} in the UHF formalism.
+\autoref{fig:UHFMiniBas} is the analog of \autoref{fig:RHFMiniBas} in the UHF formalism.
 We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
@@
 
- In our case we can see in \autoref{fig:UHFPT} that a part of the energy spectrum becomes complex when R is in the holomorphic domain.
-This part of the spectrum where the energy becomes complex is called the broken \pt symmetry  region.
+\autoref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when R is in the holomorphic domain.
+The parameter domain of value where the energy becomes complex is called the broken \pt symmetry  region.
 This is consistent with the fact that in the holomorphic domain the Hamiltonian break the \pt -symmetry.
@@
 For a non-Hermitian Hamiltonian the exceptional points can lie on the real axis.
-In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate so it is an exceptional.
-We can see this phenomenon on Figure x, the points of PT transition are indicate by .
+In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate resulting in such an exceptional point on the real axis.
+This degeneracy can be seen in \autoref{fig:UHFPT}.
 
@@
 \newpage
-
 \printbibliography

### 2020-07-27 RapportStage/Rapport.tex
few corrections sec 4

@@
 This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}, e^{-i\pi/4}, e^{i3\pi/4}, e^{-i3\pi/4}$) with a modulus equal to 1.
-This simple example shows the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
+This simple example emphasizes the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
 
@@
 
-In the Born-Oppenheimer approximation, the equation \eqref{eq:ExactHamiltonian} gives the exact electronic Hamiltonian for a chemical system with $n$ electrons and $N$ nuclei.
+In the Born-Oppenheimer approximation, the equation \eqref{eq:ExactHamiltonian} gives the exact electronic Hamiltonian for a chemical system with $n$ electrons and $N$ nuclei with respective charge $Z_k$.
 The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nuclei attraction and the electron-electron repulsion.
@@
 Hence the Slater determinants are not eigenfuctions of the exact Hamiltonian $\bH$.
-However, they are eigenfunctions of an approximated Hamiltonian $\bH^{(0)}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
+However, they are eigenfunctions of an approximated Hamiltonian $\bH^{\text{HF}}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
 
 \begin{equation}\label{eq:HFHamiltonian}
-\bH^{(0)}= \sum\limits_{i=1}^{n} f(i)
+\bH^{\text{HF}}= \sum\limits_{i=1}^{n} f(i)
 \end{equation}
@@
 The two other terms are the the Coulomb $J_a(i)$ and Exchange $K_a(i)$ operators.
-Their action on the spin-orbitals are given by the equation \eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
+Their action on spin-orbital (occupied or virtual) are given by the equation \eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
 The integration is over the spatial and spin coordinates.
@@
 \begin{equation}\label{eq:FockOp}
-f(1)\phi_a(1) = \left[h(1) + \sum\limits_{b=1}^{n} J_b(1) - K_b(1)\right]\phi_a(1)=\epsilon_a\phi_a(1)
+f(1)\phi_i(1) = \left[h(1) + \sum\limits_{j=1}^{n} J_j(1) - K_j(1)\right]\phi_i(1)=\epsilon_i\phi_i(1)
 \end{equation}
@@
 \begin{equation}\label{eq:CoulOp}
-J_b(1)\phi_a(1)=\left[\int\dd\vb{x}_2\phi_b^*(2)\frac{1}{r_{12}}\phi_b(2) \right]\phi_a(1)
+J_j(1)\phi_i(1)=\left[\int\dd\vb{x}_2\phi_j^*(2)\frac{1}{r_{12}}\phi_j(2) \right]\phi_i(1)
 \end{equation}
@@
 \begin{equation}\label{eq:ExcOp}
-K_b(1)\phi_a(1)=\left[\int\dd\vb{x}_2\phi_b^*(2)\frac{1}{r_{12}}\phi_a(2) \right]\phi_b(1)
+K_j(1)\phi_i(1)=\left[\int\dd\vb{x}_2\phi_j^*(2)\frac{1}{r_{12}}\phi_j(2) \right]\phi_i(1)
 \end{equation}
@@
 The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost \cite{JensenBook}.
-But to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
+In order to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
 For small systems we can have access to the whole series using Full Configuration Interaction (FCI).
-If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and expanding in $\lambda$ allows to to get the MP perturbation series at every order.
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and the Taylor expansion respective to $\lambda$ allows to get the MP perturbation series at every order.
 
@@
 An other possibility, even more natural than the MP one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
-Hence, the off-diagonal elements of $\bH(\lambda)$ are the perturbation operator.
+Hence, the off-diagonal elements of $\bH$ are the perturbation operator.
 This partitioning leads to the Epstein-Nesbet (EN) perturbation theory.
@@
 The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
-We will use this model to try to rationalize the effects of the variables that may influence the physics of EPs:
+We will use this model to try to rationalize the effects of the parameters that may influence the physics of EPs:
 \begin{itemize}
@@
 
-In the restricted Hartree-Fock formalism, the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
-Then a fortiori it cannot represent two electrons on opposite side of the sphere.
-In the unrestricted formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second unrestricted Hartree-Fock solution appear.
+In the restricted Hartree-Fock formalism (RHF), the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
+If the spatial orbitals are the  same a fortiori it cannot represent two electrons on opposite side of the sphere.
+In the unrestricted Hartree-Fock (UHF) formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second UHF solution appears.
 This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
-The unrestricted Hartree-Fock wave function is defined as:
+The UHF wave function is defined as:
 
@@
 
-It is possible to obtain the formula for the ground state unrestricted Hartree-Fock energy in this basis set (see Appendix A for the development):
+It is possible to obtain the formula for the ground state UHF energy in this basis set (see \autoref{sec:UHF_NRJ} for the development):
 
@@
 
-In addition, there is also the well-known symmetry-broken UHF solution.
-For $R>3/2$ an other stationary UHF solution appear, this solution is a minimum of the Hartree-Fock equations.
+In addition, there is also the well-known symmetry-broken UHF (sb-UHF) solution.
+For $R>3/2$ an other stationary UHF solution appears, this solution is a minimum of the HF equations.
 This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the configuration the other way round.
@@
 It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
-This solution is called symmetry-broken RHF.
+This solution is called symmetry-broken RHF (sb-RHF).
 At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
-This symmetry breaking is associated with a charge density wave: the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
+This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
 
@@
 
-We can also consider negative value of R.
+We can also consider negative values of R.
 This corresponds to the situation where one of the electrons is replaced by a positron.
@@
 Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF states maximize the energy because the two particles are on opposite sides of the sphere.
+And the sb-UHF states maximize the energy because the two attracting particles are on opposite sides of the sphere.
 
@@
 
-\section{ERHF and EUHF}
+\section{The unrestricted energy}\label{sec:UHF_NRJ}
 

### 2020-07-27 RapportStage/Rapport.tex
modifications sec 5

@@
 \begin{itemize}
-\item The Weak Correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
-\item The Strong Coupling partitioning where the two operators are inverted compared to the weak correlation partitioning.
+\item The Weak Correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
+\item The Strong Coupling (SC) partitioning where the two operators are inverted compared to the weak correlation partitioning.
 \end{itemize}
@@
 
-In the restricted Hartree-Fock formalism (RHF), the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
+In the RHF formalism, the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
 If the spatial orbitals are the  same a fortiori it cannot represent two electrons on opposite side of the sphere.
-In the unrestricted Hartree-Fock (UHF) formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second UHF solution appears.
+In the UHF formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second UHF solution appears.
 This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
@@
 The equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system, if an energy is also solution of \eqref{eq:DPolChar} then this energy is degenerate.
-In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate i.e.
-the exceptional points.
+In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
+These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ or exceptional points between two states with the same symmetry for complex value of $\lambda$.
 
@@
 Then using this basis set we can compare the different partitioning of \autoref{sec:AlterPart}.
-\autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the Weak Correlation and the Strong Coupling partitioning in a minimal basis i.e.
+\autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis i.e.
 $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
-We see that the radius of convergence of the strong coupling partitioning is growing with R whereas it is decreasing for the three others partitioning.
+We see that the radius of convergence of the SC partitioning is growing with R whereas it is decreasing for the three others partitioning.
 This result was expected because the three decreasing partitioning use a weakly correlated reference so $\bH^{(0)}$ is a good approximation for small $R$.
@@
 \centering
-\caption{\centering Dominant singularity in the CSF basis set ($n=8$) for various value of R. The first line is the value for the MP partitioning and the second for the WC one.}
+\caption{\centering Dominant singularity in the CSF basis set ($K=8$) for various value of R. The first line is the value for the MP partitioning and the second for the WC one.}
 \begin{tabular}{cccccccc}
@@
 
-In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in \autoref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are connected to $\beta$ singularities.
+In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in \autoref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
 For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014i$.

### 2020-07-28 RapportStage/Rapport.tex
remove autref

@@
 
-One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
-Within this quantised paradigm, electronic states look completely disconnected from one another.
+One common feature of all these methods is that they rely on the notion of quantized energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
+Within this quantized paradigm, electronic states look completely disconnected from one another.
 Many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.
-However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
+However, one can gain a different perspective on quantization extending quantum chemistry into the complex domain.
 In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
-In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
-The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
+In other words, our view of the quantized nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+The realization that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
 One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information.
@@
 
-Exceptional points (EPs) \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016} are non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996} where two states become exactly degenerate.
+Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016}. 
+They are the non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996}.
 CIs are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
@@
 Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
-For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy (see \autoref{fig:TopologyEP} for a graphical example).
+For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy (see Fig.~\ref{fig:TopologyEP} for a graphical example).
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
@@
     \includegraphics[width=0.45\textwidth]{i2x2.pdf}
-    \caption{\centering Energies, as given by Eq.~\eqref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
+    \caption{\centering Energies, as given by Eq.~\ref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
     \label{fig:2x2}
@@
 \end{equation}
-which correspond to square-root singularities in the complex-$\lambda$ plane (see \autoref{fig:2x2}).
+which correspond to square-root singularities in the complex-$\lambda$ plane (see Fig.~\eqref{fig:2x2}).
 These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
@@
 For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
-In \autoref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
 On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
@@
 In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function which leads to spin contamination.
-Gill \textit{et al.}~highlighted the link between slow convergence of the unrestricted MP series and spin contamination of the wave function as shown in the \autoref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
+Gill \textit{et al.}~highlighted the link between slow convergence of the unrestricted MP series and spin contamination of the wave function as shown in Table \ref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
 Handy and coworkers exhibited the same behavior of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
@@
 In the late 90's, Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series \cite{}.
-They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} (see \autoref{fig:NeHFDiv}) \cite{Olsen_1996, Christiansen_1996}.
+They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} (see Fig.~\ref{fig:NeHFDiv}) \cite{Olsen_1996, Christiansen_1996}.
 Cremer and He had already studied these two systems and classified them as ``class B'' systems.
@@
 
-It is possible to obtain the formula for the ground state UHF energy in this basis set (see \autoref{sec:UHF_NRJ} for the development):
+It is possible to obtain the formula for the ground state UHF energy in this basis set (see Sec.~\ref{sec:UHF_NRJ} for the development):
 
@@
 Indeed, the spherical harmonics are eigenvectors of $S^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $S^2$.
-However this solution gives more accurate results for the energy at large R as shown in \autoref{tab:ERHFvsEUHF}.
+However this solution gives more accurate results for the energy at large R as shown in Table \ref{tab:ERHFvsEUHF}.
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
@@
 In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
-All those energies are plotted in \autoref{fig:SpheriumNrj}.
+All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
 The dotted curves corresponds to the holomorphic domain of the energies.
@@
 The two singly excited states give a singlet sp\textsubscript{z} and a triplet sp\textsubscript{z} state but their symmetry is not the same as the ground state.
-Thus these states can not be involved in an avoided crossing with the ground state as it can be seen in \autoref{fig:RHFMiniBas} and a fortiori can not be involved in an exceptional point with the ground state.
+Thus these states can not be involved in an avoided crossing with the ground state as it can be seen in Fig.~\ref{fig:RHFMiniBas} and a fortiori can not be involved in an exceptional point with the ground state.
 However there is an avoided crossing between the s\textsuperscript{2} state and the p\textsubscript{z}\textsuperscript{2} one which gives two exceptional points in the complex plane.
@@
 
-Then using this basis set we can compare the different partitioning of \autoref{sec:AlterPart}.
-\autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis i.e.
+Then using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
+Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis i.e.
 $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
@@
 when $R$ is large for the spherium model.
-The MP partitioning is always better than the weak correlation in \autoref{fig:RadiusPartitioning}.
+The MP partitioning is always better than the weak correlation in Fig.~\ref{fig:RadiusPartitioning}.
 In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
@@
 
-\autoref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
+Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
 The CSF basis function have all the same spin and spatial symmetry so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
-The \autoref{tab:SingAlpha} proves that the singularities considered in this case are $\alpha$ singularities.
+Table \ref{tab:SingAlpha} proves that the singularities considered in this case are $\alpha$ singularities.
 This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities.
-The discontinuities observed in \autoref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
-We can observe this change in \autoref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative plane.
+The discontinuities observed in Fig.~\ref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
+We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative plane.
 
@@
 Now we will investigate the differences in the singularity structure between the RHF and UHF formalism.
-To do this we use the symmetry-broken orbitals obtained in \autoref{sec:spherium}.
+To do this we use the symmetry-broken orbitals obtained in Sec.~\ref{sec:spherium}.
 Thus the UHF two-electron basis is:
@@
 This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of \autoref{fig:SpheriumNrj}, the singularities in this case will be treated in \autoref{sec:uhfSing}.
-The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in \autoref{sec:spherium}.
+For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated in Sec.~\ref{sec:uhfSing}.
+The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
 We will refer to the domain where the matrix element are complex as the holomorphic domain.
@@
 The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
-\autoref{fig:UHFMiniBas} is the analog of \autoref{fig:RHFMiniBas} in the UHF formalism.
+Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
 We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
 Those avoided crossings are due to the spin contamination of the wave function.
-The exceptional points resulting from those avoided crossings will be discussed in \autoref{sec:uhfSing}.
+The exceptional points resulting from those avoided crossings will be discussed in Sec.~\ref{sec:uhfSing}.
 \\
@@
 
-In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in \autoref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
+In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
 For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014i$.
@@
 However in the spherium the electrons can't be ionized so those singularities are not the $\beta$ singularities highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
-We can see in \autoref{fig:UHFEP} that the degeneracy between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet at $R=3/2$.
+We can see in Fig.~\ref{fig:UHFEP} that the degeneracy between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet at $R=3/2$.
 For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are moved in the complex plane.
@@
 
-\autoref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when R is in the holomorphic domain.
+Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when R is in the holomorphic domain.
 The parameter domain of value where the energy becomes complex is called the broken \pt symmetry  region.
@@
 In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate resulting in such an exceptional point on the real axis.
-This degeneracy can be seen in \autoref{fig:UHFPT}.
+This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
 

### 2020-07-28 RapportStage/Rapport.tex
modifications in Sec. 1

@@
 \usepackage{physics}
+\usepackage{wrapfig}
 \usepackage{amsmath} % collection de symboles mathématiques
@@
 
+\begin{wrapfigure}{r}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{TopologyEP.pdf}
+    \caption{A generic EP with the square root branch point topology. A loop around the EP interconvert the states.}
+    \label{fig:TopologyEP}
+\end{wrapfigure}
 By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
@@
 More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane \cite{Olsen_1996, Olsen_2000}.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{TopologyEP.pdf}
-    \caption{\centering A generic EP with the square root branch point topology. A loop around the EP interconvert the states.}
-    \label{fig:TopologyEP}
-\end{figure}
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{2x2.pdf}
-    \includegraphics[width=0.45\textwidth]{i2x2.pdf}
-    \caption{\centering Energies, as given by Eq.~\ref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
+    \includegraphics[width=0.3\textwidth]{2x2.pdf}
+    \hspace{0.2\textwidth}
+    \includegraphics[width=0.3\textwidth]{i2x2.pdf}
+    \caption{Energies, as given by Eq.~\ref{eq:E_2x2}, of the Hamiltonian \eqref{eq:H_2x2} as a function of $\lambda$ with $\epsilon_1 = -1/2$ and $\epsilon_2 = +1/2$.}
     \label{fig:2x2}
@@
 \end{equation}
-and following a complex contour around the EP, i.e.~$\lambda = \lambda_\text{EP} + R \exp(i\theta)$, yields
+and following a complex contour around the EP, i.e., $\lambda = \lambda_\text{EP} + R \exp(i\theta)$, yields
 \begin{equation}
@@
 \begin{equation}\label{eq:phi_2x2}
-\phi_{\pm}=\begin{pmatrix}
-(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2})/2\lambda \\ 1
-\end{pmatrix},
-\end{equation}
-and, for $\lambda=\lambda_\text{EP}$, they become
-\begin{align}
-	\phi_{\pm}(i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} -i \\ 1\end{pmatrix},
-	&
-	\phi_{\pm}(-i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} i \\ 1\end{pmatrix}.
-\end{align}
-which are self-orthogonal i.e. their norm is equal to zero. 
-Using Eq.~\eqref{eq:E_EP}, Eq.~\eqref{eq:phi_2x2} can be recast as
-\begin{equation}\label{eq:phi_EP}
-\phi_{\pm}=
+\begin{split}
+	\phi_{\pm}(\lambda)
+	& = 
+	\begin{pmatrix}
+		(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2})/2\lambda 
+		\\ 
+		1
+	\end{pmatrix}
+	\\
+	& =
 	\begin{pmatrix}
@@
 		1
-	\end{pmatrix}.
+	\end{pmatrix},
+\end{split}
 \end{equation}
-We have seen that the EP inherits its topology from the double valued function $\sqrt{\lambda - \lambda_\text{EP}}$.
-Then if the eigenvectors are normalised they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$ which gives the following pattern when looping around one EP:
+and, for $\lambda=\lambda_\text{EP}$, they become
+\begin{align}
+	\phi_{\pm}\qty(i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} -i \\ 1\end{pmatrix},
+	&
+	\phi_{\pm}\qty(-i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} i \\ 1\end{pmatrix}.
+\end{align}
+which are clearly self-orthogonal, i.e., their norm is equal to zero. 
+%Using Eq.~\eqref{eq:E_EP}, Eq.~\eqref{eq:phi_2x2} can be recast as
+%\begin{equation}\label{eq:phi_EP}
+%\phi_{\pm}=
+%\end{equation}
+As branch point (square-root) singularities, EPs inherit their topology from the multi-valued function $\sqrt{\lambda - \lambda_\text{EP}}$. 
+Then, if the eigenvectors are properly normalized, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$, which gives the following pattern when looping around one EP:
 \begin{align}
@@
 	&
-	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0) \\
+	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0), 
+	\\
 	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
@@
 We can also see that looping the other way around leads to a different pattern.
-\antoine{Is this a bit better like this ?}
 
@@
 This partitioning of the Hamiltonian leads to the so-called M{\o}ller-Plesset (MP) perturbation theory \cite{Moller_1934}.
-The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a part of the correlation energy (i.e.
-the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
+The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a part of the correlation energy (i.e., the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
 This yields the Hamiltonian $\bH(\lambda)$ of the equation \eqref{eq:MPHamiltonian} where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{HF}$ for convenience.
@@
 
-\antoine{This reasoning is done on the exact Hamiltonian and energy i.e.
-the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis}.
+\antoine{This reasoning is done on the exact Hamiltonian and energy, i.e., the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis}.
 \antoine{However, in a finite basis set which does not span the complete Hilbert space}, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
@@
 \antoine{We think that $\alpha$ singularities are connected the states with non-negligible contribution in the configuration interaction expansion thus to the dynamical part of the correlation energy.
-Whereas the $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function i.e.
-the multi-reference aspect of the wave function thus to the static part of the correlation energy.}
+Whereas the $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function, i.e., the multi-reference aspect of the wave function thus to the static part of the correlation energy.}
 
@@
 
-The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set i.e.
-$\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
+The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
 The two singly excited states give a singlet sp\textsubscript{z} and a triplet sp\textsubscript{z} state but their symmetry is not the same as the ground state.
@@
 To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
-It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties i.e.
-the exceptional points between states with the same symmetry.
+It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties, i.e., the exceptional points between states with the same symmetry.
 In this case the ground state is a totally symmetric singlet.
@@
 Then using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
-Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis i.e.
-$P_0$ and $P_1$ and in the same basis augmented with $P_2$.
+Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis, i.e., $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
 We see that the radius of convergence of the SC partitioning is growing with R whereas it is decreasing for the three others partitioning.
 This result was expected because the three decreasing partitioning use a weakly correlated reference so $\bH^{(0)}$ is a good approximation for small $R$.
-On the contrary, the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated i.e.
-when $R$ is large for the spherium model.
+On the contrary, the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated, i.e., when $R$ is large for the spherium model.
 The MP partitioning is always better than the weak correlation in Fig.~\ref{fig:RadiusPartitioning}.

### 2020-07-28 RapportStage/Rapport.tex
modifications in Sec. 1
saving work

@@
     \includegraphics[width=\linewidth]{TopologyEP.pdf}
-    \caption{A generic EP with the square root branch point topology. A loop around the EP interconvert the states.}
+    \caption{A generic EP with the square-root branch point topology. A loop around the EP interconvert the states.}
     \label{fig:TopologyEP}
@@
 \begin{equation} \label{eq:Elambda}
-	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}
+	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}.
 \end{equation}
-However it is not guaranteed that the series \eqref{eq:Elambda} has a radius of convergence $\abs{\lambda_0} < 1$. 
+However, it is not guaranteed that the series \eqref{eq:Elambda} has a radius of convergence $\abs{\lambda_0} < 1$. 
 In other words, the series might well be divergent for the physical system at $\lambda = 1$. 
@@
 \begin{quote}
-	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1 − z_0}$.
-If the function has a singular point $z_s$ such that $\abs{z_s − z_0} < \abs{z_1 − z_0}$, then the series will diverge when evaluated at $z_1$.''}
+	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1-z_0}$.
+If the function has a singular point $z_s$ such that $\abs{z_s-z_0} < \abs{z_1-z_0}$, then the series will diverge when evaluated at $z_1$.''}
 \end{quote}
 This theorem means that the radius of convergence of the perturbation series is equal to the distance to the origin of the closest singularity of $E(\lambda)$.
-To illustrate this result we  consider the simple function \eqref{eq:DivExample}.
-This function is smooth for $x \in \mathbb{R}$ and infinitely differentiable in $\mathbb{R}$.
-One would expect that the Taylor series of such a function would be convergent for all $x \in \mathbb{R}$, however this series is divergent for $x\geq1$.
-This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}, e^{-i\pi/4}, e^{i3\pi/4}, e^{-i3\pi/4}$) with a modulus equal to 1.
-This simple example emphasizes the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
-
+To illustrate this result we  consider the simple function \cite{BenderBook}
 \begin{equation} \label{eq:DivExample}
@@
 \end{equation}
+This function is smooth for $x \in \mathbb{R}$ and infinitely differentiable in $\mathbb{R}$.
+One would expect that the Taylor series of such a function would be convergent $\forall x \in \mathbb{R}$.
+However this series is divergent for $x \ge 1$.
+This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}$, $e^{-i\pi/4}$, $e^{i3\pi/4}$, and $e^{-i3\pi/4}$) with a modulus equal to $1$.
+This simple example emphasizes the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
 
@@
 
-In the Born-Oppenheimer approximation, the equation \eqref{eq:ExactHamiltonian} gives the exact electronic Hamiltonian for a chemical system with $n$ electrons and $N$ nuclei with respective charge $Z_k$.
-The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nuclei attraction and the electron-electron repulsion.
+Within the Born-Oppenheimer approximation, 
+\begin{equation}\label{eq:ExactHamiltonian}
+    \bH = - \sum_{i}^{n} \frac{1}{2}\grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{|\vb{r}_i-\vb{R}_A|} + \sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}
+\end{equation}
+is the exact electronic Hamiltonian for a chemical system with $n$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $N$ nuclei (where $\vb{R}_A$ is the position of the $A$th nucleus and $Z_A$ its charge).
+The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
+Note that we use atomic units throughout unless otherwise stated.
 
-\begin{equation}\label{eq:ExactHamiltonian}
-    \bH=\sum\limits_{i=1}^{n}\left[ -\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}+\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}\right]
+In the Hartree-Fock (HF) approximation the wave function is approximated as a single Slater determinant (which is an anti-symmetric combination of $n$ one-electron spin-orbitals).
+Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
+Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\bH$.
+However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian, which is the sum of the one-electron Fock operators:
+\begin{equation}\label{eq:HFHamiltonian}
+	\bH^{\text{HF}}= \sum\limits_{i=1}^{n} f(\vb{r}_i)
 \end{equation}
+% Note that the eigenvalue of this Hamiltonian is not the HF energy but the sum of the eigenvalues
 
-In the Hartree-Fock (HF) approximation the wave function is approximated as a single Slater determinant (which is an anti-symmetric combination of $n$ one electron spin-orbitals).
-Rather than solving the equation \eqref{eq:SchrEq}, the Hartree-Fock theory uses the variational principle to find an approximation to $\Psi$.
-Hence the Slater determinants are not eigenfuctions of the exact Hamiltonian $\bH$.
-However, they are eigenfunctions of an approximated Hamiltonian $\bH^{\text{HF}}$, called the Hartree-Fock Hamiltonian, which is the sum of the one-electron Fock operators.
+\titou{I STOPPED HERE.}
 
-\begin{equation}\label{eq:HFHamiltonian}
-\bH^{\text{HF}}= \sum\limits_{i=1}^{n} f(i)
-\end{equation}
-
-The eigenfunctions of $f(i)$ are the one-electron spin-orbitals $\phi_a(i)$ used to create the $n$-electron Slater determinant.
-The equation \eqref{eq:FockOp} gives the eigenvalue equation for the one-electron Fock operator associated with the electron 1.
-The one-electron core Hamiltonian $h(i)$ are the sum of the kinetic energy of the electron $i$ and the attraction of the nuclei on this electron.
-The two other terms are the the Coulomb $J_a(i)$ and Exchange $K_a(i)$ operators.
-Their action on spin-orbital (occupied or virtual) are given by the equation \eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
+The eigenfunctions of $f(\vb{r}_i)$ are the one-electron spin-orbitals $\phi_p(i)$ used to create the $n$-electron Slater determinant.
+Equation \eqref{eq:FockOp} gives the eigenvalue equation for the one-electron Fock operator associated with the electron $i$.
+The one-electron core Hamiltonian $h(\vb{r}_i)$ are the sum of the kinetic energy of the electron $i$ and the attraction of the nuclei on this electron.
+The two other terms are the the Coulomb $J_a(\vb{r}_i)$ and Exchange $K_a(\vb{r}_i)$ operators.
+Their action on spin-orbital (occupied or virtual) are given by Eqs.~\eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
 The integration is over the spatial and spin coordinates.

### 2020-07-28 RapportStage/Rapport.tex
major modifs in Sec 2

@@
 
+Within the Born-Oppenheimer approximation, 
+\begin{equation}\label{eq:ExactHamiltonian}
+    \bH = - \frac{1}{2} \sum_{i}^{n} \grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} + \sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}
+\end{equation}
+is the exact electronic Hamiltonian for a chemical system with $n$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $N$ (fixed) nuclei (where $\vb{R}_A$ and $Z_A$ are the position and the charge of the $A$th nucleus respectively).
+The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
+Note that we use atomic units throughout unless otherwise stated.
+
 Within (time-independent) Rayleigh-Schr\"odinger perturbation theory, the Schr\"odinger equation 
@@
 
-Within the Born-Oppenheimer approximation, 
-\begin{equation}\label{eq:ExactHamiltonian}
-    \bH = - \sum_{i}^{n} \frac{1}{2}\grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{|\vb{r}_i-\vb{R}_A|} + \sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+\begin{equation}\label{eq:FockOp}
+	f(\vb{x}) \phi_p(\vb{x}) = [ h(\vb{x}) + v^\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
 \end{equation}
-is the exact electronic Hamiltonian for a chemical system with $n$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $N$ nuclei (where $\vb{R}_A$ is the position of the $A$th nucleus and $Z_A$ its charge).
-The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
-Note that we use atomic units throughout unless otherwise stated.
+where 
+\begin{equation}
+	h(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
+\end{equation}
+is the core Hamiltonian and 
+\begin{equation}
+	v^\text{HF}(\vb{x}) = \sum_i \qty[ J_i(\vb{x}) - K_i(\vb{x}) ]
+\end{equation}
+is the HF mean-field potential with 
+\begin{gather}
+	\label{eq:CoulOp}
+	J_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') ] \phi_p(\vb{x})
+	\\
+	\label{eq:ExcOp}
+	K_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_p(\vb{x}') ] \phi_i(\vb{x})
+\end{gather}
+being the Coulomb and exchange operators (respectively) in the spin-orbital basis.
 
-In the Hartree-Fock (HF) approximation the wave function is approximated as a single Slater determinant (which is an anti-symmetric combination of $n$ one-electron spin-orbitals).
 Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
 Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\bH$.
-However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian, which is the sum of the one-electron Fock operators:
+However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian defined as the sum of the one-electron Fock operators
 \begin{equation}\label{eq:HFHamiltonian}
-	\bH^{\text{HF}}= \sum\limits_{i=1}^{n} f(\vb{r}_i)
+	\bH^{\text{HF}} = \sum_{i}^{n} f(\vb{x}_i).
 \end{equation}
-% Note that the eigenvalue of this Hamiltonian is not the HF energy but the sum of the eigenvalues
+Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues.
 
-\titou{I STOPPED HERE.}
-
-The eigenfunctions of $f(\vb{r}_i)$ are the one-electron spin-orbitals $\phi_p(i)$ used to create the $n$-electron Slater determinant.
+%The eigenfunctions of $f(\vb{r}_i)$ are the one-electron spin-orbitals $\phi_p(i)$ used to create the $n$-electron Slater determinant.
 Equation \eqref{eq:FockOp} gives the eigenvalue equation for the one-electron Fock operator associated with the electron $i$.
-The one-electron core Hamiltonian $h(\vb{r}_i)$ are the sum of the kinetic energy of the electron $i$ and the attraction of the nuclei on this electron.
-The two other terms are the the Coulomb $J_a(\vb{r}_i)$ and Exchange $K_a(\vb{r}_i)$ operators.
+The one-electron core Hamiltonian $h(\vb{r}_i)$ are  The two other terms are the the Coulomb $J_a(\vb{r}_i)$ and Exchange $K_a(\vb{r}_i)$ operators.
 Their action on spin-orbital (occupied or virtual) are given by Eqs.~\eqref{eq:CoulOp} and \eqref{eq:ExcOp}.
@@
 
-\begin{equation}\label{eq:FockOp}
-f(1)\phi_i(1) = \left[h(1) + \sum\limits_{j=1}^{n} J_j(1) - K_j(1)\right]\phi_i(1)=\epsilon_i\phi_i(1)
-\end{equation}
-
-\begin{equation}\label{eq:CoulOp}
-J_j(1)\phi_i(1)=\left[\int\dd\vb{x}_2\phi_j^*(2)\frac{1}{r_{12}}\phi_j(2) \right]\phi_i(1)
-\end{equation}
-
-\begin{equation}\label{eq:ExcOp}
-K_j(1)\phi_i(1)=\left[\int\dd\vb{x}_2\phi_j^*(2)\frac{1}{r_{12}}\phi_j(2) \right]\phi_i(1)
-\end{equation}
-
 \subsection{M{\o}ller-Plesset perturbation theory}
 
-The Hartree-Fock Hamiltonian \eqref{eq:HFHamiltonian} can be used as the zeroth-order Hamiltonian of the equation \eqref{eq:SchrEq-PT}.
+The HF Hamiltonian \eqref{eq:HFHamiltonian} can be used as the zeroth-order Hamiltonian of Eq.~\eqref{eq:SchrEq-PT}.
 This partitioning of the Hamiltonian leads to the so-called M{\o}ller-Plesset (MP) perturbation theory \cite{Moller_1934}.
-The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a part of the correlation energy (i.e., the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-Hartree-Fock methods.
-This yields the Hamiltonian $\bH(\lambda)$ of the equation \eqref{eq:MPHamiltonian} where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{HF}$ for convenience.
+The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a large chunck of the correlation energy (i.e., the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-HF methods.
+This yields
+% the Hamiltonian $\bH(\lambda)$ of Eq.~\eqref{eq:MPHamiltonian}.
+% where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{HF}$ for convenience.
 
 \begin{equation}\label{eq:MPHamiltonian}
-    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|} + (1-\lambda)V_i^{\text{HF}}+\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|} \right]
+    \bH(\lambda) = 
+    \sum_{i}^{n} \qty[ 
+    -\frac{\grad_i^2}{2} 
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+    + (1-\lambda) v^{\text{HF}}(\vb{x}_i) 
+    + \lambda\sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
+    ].
 \end{equation}
-
-In the perturbation theory the energy is a power series of $\lambda$ and the physical energy is obtained by taking $\lambda$ equal to 1.
+As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
+\titou{STOPPED HERE.}
 We will refer to the energy up to the $n$-th order as the MP$n$ energy. 
-The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the Hartree-Fock energy.
+The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the HF energy. 
 The MP2 energy starts to recover a part of the correlation energy \cite{SzaboBook}.
@@
 \begin{equation}
-E_{\text{MP}_{n}}= \sum_{k=0}^n E^{(k)}
+E_{\text{MP}{n}}= \sum_{k=0}^n E^{(k)}
 \end{equation}
@@
 \begin{equation}\label{eq:EMP2}
-E_{\text{MP2}}=\sum\limits_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b}
+E_{\text{MP2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b}
 \end{equation}
 \begin{equation}\label{eq:EEN2}
-E_{\text{EN2}}=\sum\limits_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{}
+E_{\text{EN2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{}
 \end{equation}
@@
 \begin{equation}\label{eq:HamiltonianStillinger}
-    \bH(\lambda)=\sum\limits_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of}~\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum\limits_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
+    \bH(\lambda)=\sum_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of}~\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
 \end{equation}
@@
 \begin{equation}
-\phi_\alpha(\theta_1)=\sum\limits_{l=0}^{\infty}C_{\alpha,l}\frac{Y_{l0}(\Omega_1)}{R}
+\phi_\alpha(\theta_1)=\sum_{l=0}^{\infty}C_{\alpha,l}\frac{Y_{l0}(\Omega_1)}{R}
 \end{equation}
@@
 \begin{equation}
-E_{\text{c},\alpha} = \sum\limits_{l=0}^{\infty} C_{\alpha,l}^2 \frac{l(l+1)}{R^2}
+E_{\text{c},\alpha} = \sum_{l=0}^{\infty} C_{\alpha,l}^2 \frac{l(l+1)}{R^2}
 \end{equation}
@@
 \begin{equation}
-E_{\text{p}} = \sum\limits_{i,j,k,l=0}^{\infty}C_{\alpha,i}C_{\alpha,j}C_{\beta,k}C_{\beta,l} \frac{(-1)^{k+l}S_{i,j,k,l}}{R}\sum\limits_{L=0}^{\infty} \begin{pmatrix}
+E_{\text{p}} = \sum_{i,j,k,l=0}^{\infty}C_{\alpha,i}C_{\alpha,j}C_{\beta,k}C_{\beta,l} \frac{(-1)^{k+l}S_{i,j,k,l}}{R}\sum_{L=0}^{\infty} \begin{pmatrix}
  i & j & L \\

### 2020-07-28 RapportStage/Rapport.tex
major modifs in Sec 2

@@
 \titou{STOPPED HERE.}
-We will refer to the energy up to the $n$-th order as the MP$n$ energy. 
-The MP0 energy overestimates the energy by double counting the electron-electron interaction, the MP1 corrects this effect and the MP1 energy is equal to the HF energy. 
-The MP2 energy starts to recover a part of the correlation energy \cite{SzaboBook}.
-
-\begin{equation}
-E_{\text{MP}{n}}= \sum_{k=0}^n E^{(k)}
-\end{equation}
+The MP$n$ energy is defined as 
+\begin{equation}
+	E_{\text{MP}{n}}= \sum_{k=0}^n E^{(k)},
+\end{equation}
+where $E^{(k)}$ is the $k$th-order correction.
+The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies. 
+The MP1 corrects this and is then equal to the HF energy. 
+MP2 starts recovering correlation energy and the MP2 energy is then lower than the HF energy \cite{SzaboBook}.
 
@@
 
+\begin{wrapfigure}{r}{0.4\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{gill1986.png}
+    \caption{Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from \cite{Gill_1986}).}
+    \label{fig:RUMP_Gill}
+\end{wrapfigure}
 When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, i.e., one would expect that the more terms of the perturbative series one has, the closer the result from the exact energy.
@@
 On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{gill1986.png}
-    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from \cite{Gill_1986}).}
-    \label{fig:RUMP_Gill}
-\end{figure}
 
@@
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
-Otherwise, it is called continuous and of $n$-th order if the $n$-th derivative is discontinuous.
+Otherwise, it is called continuous and of $n$th order if the $n$th derivative is discontinuous.
 A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
@@
 Whereas the MP reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
-Moreover it can be proved that the $n$-th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$n$ respective to $R$.
+Moreover it can be proved that the $n$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$n$ respective to $R$.
 It seems that the EN partitioning is better than the MP one for very small R in the minimal basis.

### 2020-07-28 RapportStage/Rapport.tex
done with section 2

@@
 
-In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
 \begin{equation}\label{eq:FockOp}
@@
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis.
-
+From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
 Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
@@
 \end{equation}
-Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues.
+Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues (see below).
 
@@
 As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
-\titou{STOPPED HERE.}
 The MP$n$ energy is defined as 
 \begin{equation}
-	E_{\text{MP}{n}}= \sum_{k=0}^n E^{(k)},
+	E_{\text{MP}n}= \sum_{k=0}^n E^{(k)},
 \end{equation}
 where $E^{(k)}$ is the $k$th-order correction.
-The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies. 
-The MP1 corrects this and is then equal to the HF energy. 
-MP2 starts recovering correlation energy and the MP2 energy is then lower than the HF energy \cite{SzaboBook}.
-
-But as mentioned before \textit{a priori} there are no reasons that $E_{\text{MP}_{n}}$ is always convergent when $n$ goes to infinity.
-In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the MP method will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
-By doing so the Hamiltonian and the energy become functions of this variable.
-The energy becomes a multivalued function on $n$ Riemann sheets.
-As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MP perturbation theory.
-Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
-The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost \cite{JensenBook}.
-In order to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
-For small systems we can have access to the whole series using Full Configuration Interaction (FCI).
-If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and the Taylor expansion respective to $\lambda$ allows to get the MP perturbation series at every order.
+The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies, i.e.,
+\begin{equation}
+	E_{\text{MP0}} = \sum_i^n \epsilon_i.
+\end{equation}
+The MP1 corrects this and is then equal to the HF energy, i.e.,
+\begin{equation}
+	E_{\text{MP1}} = E_\text{HF} = \sum_i^n \epsilon_i - \frac{1}{2} \sum_{ij}^n \mel{ij}{}{ij},
+\end{equation}
+with $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$, and where  
+\begin{equation}
+	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\frac{1}{\abs{\vb{r}_1 - \vb{r}_2}}\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)
+\end{equation}
+is a two-electron integral in the spin-orbital basis.
+MP2 starts recovering correlation energy and the MP2 energy, which reads
+\begin{equation}\label{eq:EMP2}
+	E_{\text{MP2}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
+\end{equation}
+is then lower than the HF energy \cite{SzaboBook}.
+
+As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$n$ series converges to the exact energy when $n$ goes to infinity. 
+In fact, it is known that when the HF wave function is a bad approximation to the exact wave function, for example in multi-reference systems, the MP method yields bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
+By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function \titou{on $n$ Riemann sheets}. 
+As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
+These singularities of the energy function are exactly the exceptional points connecting the electronic states as mentioned in the introduction. 
+The direct computation of the terms of the series is quite manageable up to 4th order in perturbation, while the 5th and 6th order in perturbation can still be obtained but at a rather high cost \cite{JensenBook}.
+In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
+For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
+\titou{If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.}
 
@@
 
-The MP partitioning is not the only one possible in electronic structure theory.
-An other possibility, even more natural than the MP one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
-Hence, the off-diagonal elements of $\bH$ are the perturbation operator.
-This partitioning leads to the Epstein-Nesbet (EN) perturbation theory.
-The zeroth-order eigenstates for this partitioning are Slater determinants as for the MP partitioning.
-The expression of the second order correction to the energy is given for both MP and EN.
-The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies.
-The i,j indices represent the occupied orbitals and a,b the virtual orbitals of the basis sets.
-
-\begin{equation}\label{eq:EMP2}
-	E_{\text{MP2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b}
-\end{equation}
-\begin{equation}\label{eq:EEN2}
-	E_{\text{EN2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{}
-\end{equation}
-where $J_{ij}$ is the matrix element of the Coulomb operator \eqref{eq:CoulOp} and with
-\begin{equation}
-	\mel{ij}{}{ab}=\braket{ij}{ab} - \braket{ij}{ba}
-\end{equation}
-where $\braket{ij}{ab}$ is the two-electron integral
-\begin{equation}
-\braket{ij}{ab}=\int \dd\vb{x}_1\dd\vb{x}_2\phi_i^*(\vb{x}_1)\phi_j^*(\vb{x}_2)r_{12}^{-1}\phi_a(\vb{x}_1)\phi_b(\vb{x}_2)
-\end{equation}
-
-Additionally, we will consider two other partitioning.
-The electronic Hamiltonian can be separated in a one-electron part and in a two-electron part as seen previously.
-We can use this separation to create two other partitioning:
-
+Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility. 
+Here, we will consider three alternative partitioning schemes
 \begin{itemize}
-\item The Weak Correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
-\item The Strong Coupling (SC) partitioning where the two operators are inverted compared to the weak correlation partitioning.
+	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\bH$ as the zeroth-order Hamiltonian. 
+	Hence, the off-diagonal elements of $\bH$ are the perturbation operator. .
+	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
+	\item The strong coupling (SC) partitioning where the two operators are inverted as compared to the WC partitioning.
 \end{itemize}
+%An alternative partitioning scheme, maybe even more natural than the MP one, 
+%This partitioning leads to Epstein-Nesbet (EN) perturbation theory. 
+%The zeroth-order eigenstates for this partitioning are Slater determinants as for the MP partitioning. 
+%The expression of the second-order EN correction to the energy is 
+%\begin{equation}\label{eq:EEN2}
+%	E_{\text{EN2}} = \frac{1}{4} \sum_{ij}  \sum_{ab} ??
+%\end{equation}
+%The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies. 
+%Additionally, we will consider two other partitioning. 
+%The electronic Hamiltonian can be separated in a one-electron part and in a two-electron part as seen previously. 
+%We can use this separation to create two other partitioning:
 

### 2020-07-28 RapportStage/Rapport.tex
operator and matrices

@@
 
+\newcommand{\hH}{\Hat{H}}
+\newcommand{\hV}{\Hat{V}}
 \newcommand{\bH}{\mathbf{H}}
@@
 \begin{equation}\label{eq:ExactHamiltonian}
-    \bH = - \frac{1}{2} \sum_{i}^{n} \grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} + \sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}
+    \hH = - \frac{1}{2} \sum_{i}^{n} \grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} + \sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}
 \end{equation}
@@
 \begin{equation} \label{eq:SchrEq}
-	\bH \Psi = E \Psi
+	\hH \Psi = E \Psi
 \end{equation} 
@@
 \begin{equation} \label{eq:SchrEq-PT}
-	\bH(\lambda) \Psi(\lambda) = (\bH^{(0)} + \lambda \bV ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
-\end{equation}
-where $\bH^{(0)}$ is the zeroth-order Hamiltonian and $\bV = \bH - \bH^{(0)}$ is the so-called perturbation.
+	\hH(\lambda) \Psi(\lambda) = (\hH^{(0)} + \lambda \hV ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
+\end{equation}
+where $\hH^{(0)}$ is the zeroth-order Hamiltonian and $\hV = \hH - \hH^{(0)}$ is the so-called perturbation.
 The ``physical'' system of interest is recovered by setting the coupling parameter $\lambda$ to unity.
@@
 Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
-Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\bH$.
+Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\hH$.
 However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian defined as the sum of the one-electron Fock operators
 \begin{equation}\label{eq:HFHamiltonian}
-	\bH^{\text{HF}} = \sum_{i}^{n} f(\vb{x}_i).
+	\hH^{\text{HF}} = \sum_{i}^{n} f(\vb{x}_i).
 \end{equation}
@@
 \begin{equation}\label{eq:MPHamiltonian}
-    \bH(\lambda) = 
+    \hH(\lambda) = 
     \sum_{i}^{n} \qty[ 
@@
 \begin{itemize}
-	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\bH$ as the zeroth-order Hamiltonian. 
-	Hence, the off-diagonal elements of $\bH$ are the perturbation operator. .
-	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
+	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. 
+	Hence, the off-diagonal elements of $\hH$ are the perturbation operator. .
+	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$.
 	\item The strong coupling (SC) partitioning where the two operators are inverted as compared to the WC partitioning.
@@
     \includegraphics[width=\linewidth]{gill1986.png}
-    \caption{Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from \cite{Gill_1986}).}
+    \caption{Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from Ref.~\cite{Gill_1986}).}
     \label{fig:RUMP_Gill}
 \end{wrapfigure}
-When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, i.e., one would expect that the more terms of the perturbative series one has, the closer the result from the exact energy.
+When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, i.e., one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
 %In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
@@
 On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
-
-When a bond is stretched the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be single Slater determinant.
+\titou{There is a problem here as one has not introduce restricted and unrestricted formalisms.}
+
+When a bond is stretched, in most cases the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be single Slater determinant.
 Thus, it is inappropriate to model (even qualitatively) stretched system.

### 2020-07-28 RapportStage/Rapport.tex
fix issue with phi

@@
 \begin{split}
-	\phi_{\pm}(\lambda)
+	\phi_{\pm}
 	& = 
@@
 \begin{align}
-	\phi_{\pm}\qty(i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} -i \\ 1\end{pmatrix},
+	\phi_{\pm} & = \begin{pmatrix} -i \\ 1\end{pmatrix},
 	&
-	\phi_{\pm}\qty(-i\,\frac{\epsilon_1 - \epsilon_2}{2}) & = \begin{pmatrix} i \\ 1\end{pmatrix}.
+	\phi_{\pm} & = \begin{pmatrix} i \\ 1\end{pmatrix},
 \end{align}
@@
 	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0), 
-	\\
+	&
 	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
@@
 is the HF mean-field potential with 
+\begin{subequations}
 \begin{gather}
@@
 \end{gather}
+\end{subequations}
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis.
@@
 where $E^{(k)}$ is the $k$th-order correction.
+\titou{$n$ is the number of electrons and here you use it as something else...}
 The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies, i.e.,

### 2020-07-28 RapportStage/Rapport.tex
Conclusion

--- 2020-07-28 RapportStage/Rapport.tex
@@
 
-In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
 \begin{equation}\label{eq:FockOp}
@@
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis.
-From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
+
 Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
@@
 \end{equation}
-Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues (see below).
+Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues.
 
@@
 As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
+\titou{STOPPED HERE.}
 The MP$n$ energy is defined as 
 \begin{equation}
-	E_{\text{MP}n}= \sum_{k=0}^n E^{(k)},
+	E_{\text{MP}{n}}= \sum_{k=0}^n E^{(k)},
 \end{equation}
 where $E^{(k)}$ is the $k$th-order correction.
-The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies, i.e.,
-\begin{equation}
-	E_{\text{MP0}} = \sum_i^n \epsilon_i.
-\end{equation}
-The MP1 corrects this and is then equal to the HF energy, i.e.,
-\begin{equation}
-	E_{\text{MP1}} = E_\text{HF} = \sum_i^n \epsilon_i - \frac{1}{2} \sum_{ij}^n \mel{ij}{}{ij},
-\end{equation}
-with $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$, and where  
-\begin{equation}
-	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\frac{1}{\abs{\vb{r}_1 - \vb{r}_2}}\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)
-\end{equation}
-is a two-electron integral in the spin-orbital basis.
-MP2 starts recovering correlation energy and the MP2 energy, which reads
+The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies. 
+The MP1 corrects this and is then equal to the HF energy. 
+MP2 starts recovering correlation energy and the MP2 energy is then lower than the HF energy \cite{SzaboBook}.
+
+But as mentioned before \textit{a priori} there are no reasons that $E_{\text{MP}_{n}}$ is always convergent when $n$ goes to infinity.
+In fact, it is known that when the Hartree-Fock wave function is a bad approximation of the exact wave function, for example for multi-reference states, the MP method will give bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
+A smart way to investigate the convergence properties of the MP series is to transform the coupling parameter $\lambda$ into a complex variable.
+By doing so the Hamiltonian and the energy become functions of this variable.
+The energy becomes a multivalued function on $n$ Riemann sheets.
+As mentioned above by searching the singularities of the function $E(\lambda)$ we can get information on the convergence properties of the MP perturbation theory.
+Those singularities of the energy are exactly the exceptional points connecting the electronic states mentioned in the introduction.
+The direct computation of the terms of the series is quite easy up to the 4th order and the 5th and 6th order can be obtained at high cost \cite{JensenBook}.
+In order to deeply understand the behavior of the MP series and how it is connected to the singularities, we need to have access to high order terms of the series.
+For small systems we can have access to the whole series using Full Configuration Interaction (FCI).
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI basis set we get the exact energies (in this finite basis set) and the Taylor expansion respective to $\lambda$ allows to get the MP perturbation series at every order.
+
+\subsection{Alternative partitioning}\label{sec:AlterPart}
+
+The MP partitioning is not the only one possible in electronic structure theory.
+An other possibility, even more natural than the MP one, is to take the diagonal elements of $\bH$ as the zeroth-order Hamiltonian.
+Hence, the off-diagonal elements of $\bH$ are the perturbation operator.
+This partitioning leads to the Epstein-Nesbet (EN) perturbation theory.
+The zeroth-order eigenstates for this partitioning are Slater determinants as for the MP partitioning.
+The expression of the second order correction to the energy is given for both MP and EN.
+The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies.
+The i,j indices represent the occupied orbitals and a,b the virtual orbitals of the basis sets.
+
 \begin{equation}\label{eq:EMP2}
-	E_{\text{MP2}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
-\end{equation}
-is then lower than the HF energy \cite{SzaboBook}.
-
-As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$n$ series converges to the exact energy when $n$ goes to infinity. 
-In fact, it is known that when the HF wave function is a bad approximation to the exact wave function, for example in multi-reference systems, the MP method yields bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
-A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
-By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function \titou{on $n$ Riemann sheets}. 
-As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
-These singularities of the energy function are exactly the exceptional points connecting the electronic states as mentioned in the introduction. 
-The direct computation of the terms of the series is quite manageable up to 4th order in perturbation, while the 5th and 6th order in perturbation can still be obtained but at a rather high cost \cite{JensenBook}.
-In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
-For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
-\titou{If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.}
-
-\subsection{Alternative partitioning}\label{sec:AlterPart}
-
-Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility. 
-Here, we will consider three alternative partitioning schemes
+	E_{\text{MP2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b}
+\end{equation}
+\begin{equation}\label{eq:EEN2}
+	E_{\text{EN2}}=\sum_{\substack{i<j \\ a<b}}^{n}\frac{\abs{\mel{ij}{}{ab}}^2}{}
+\end{equation}
+where $J_{ij}$ is the matrix element of the Coulomb operator \eqref{eq:CoulOp} and with
+\begin{equation}
+	\mel{ij}{}{ab}=\braket{ij}{ab} - \braket{ij}{ba}
+\end{equation}
+where $\braket{ij}{ab}$ is the two-electron integral
+\begin{equation}
+\braket{ij}{ab}=\int \dd\vb{x}_1\dd\vb{x}_2\phi_i^*(\vb{x}_1)\phi_j^*(\vb{x}_2)r_{12}^{-1}\phi_a(\vb{x}_1)\phi_b(\vb{x}_2)
+\end{equation}
+
+Additionally, we will consider two other partitioning.
+The electronic Hamiltonian can be separated in a one-electron part and in a two-electron part as seen previously.
+We can use this separation to create two other partitioning:
+
 \begin{itemize}
-	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\bH$ as the zeroth-order Hamiltonian. 
-	Hence, the off-diagonal elements of $\bH$ are the perturbation operator. .
-	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
-	\item The strong coupling (SC) partitioning where the two operators are inverted as compared to the WC partitioning.
+\item The Weak Correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\bH^{(0)}$ and the two-electron part is the perturbation operator $\bV$.
+\item The Strong Coupling (SC) partitioning where the two operators are inverted compared to the weak correlation partitioning.
 \end{itemize}
-%An alternative partitioning scheme, maybe even more natural than the MP one, 
-%This partitioning leads to Epstein-Nesbet (EN) perturbation theory. 
-%The zeroth-order eigenstates for this partitioning are Slater determinants as for the MP partitioning. 
-%The expression of the second-order EN correction to the energy is 
-%\begin{equation}\label{eq:EEN2}
-%	E_{\text{EN2}} = \frac{1}{4} \sum_{ij}  \sum_{ab} ??
-%\end{equation}
-%The energies at the MP denominator are the orbitals energies whereas in the EN case it is the excitation energies. 
-%Additionally, we will consider two other partitioning. 
-%The electronic Hamiltonian can be separated in a one-electron part and in a two-electron part as seen previously. 
-%We can use this separation to create two other partitioning:
 
@@
 
-It is possible to obtain the formula for the ground state UHF energy in this basis set (see Sec.~\ref{sec:UHF_NRJ} for the development):
+It is possible to obtain the formula for the ground state UHF energy in this basis set \cite{Loos_2009}:
 
@@
 
+We have seen that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
+Indeed, those singularities close to the real axis are connected to quantum phase transition.
+In this work we have shown that $\beta$ singularities are also involved in the spin symmetry breaking of the unrestricted Hartree-Fock wave function.
+It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure.
+Moreover the singularity structure in the non-Hermitian case still need to be investigated.
+In the holomorphic domain some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
+To conclude this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of exceptional points in electronic structure theory.
+
 \newpage
@@
 
-\newpage
-\appendix
-
-\section{The unrestricted energy}\label{sec:UHF_NRJ}
-
 \end{document}

### 2020-07-29 RapportStage/Rapport.tex
conclusion + modifications

@@
 \newcommand{\hV}{\Hat{V}}
+\newcommand{\hI}{\Hat{I}}
 \newcommand{\bH}{\mathbf{H}}
@@
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis.
+\antoine{If the spatial parts of the spin-orbital basis are restricted to be the same for electrons $\alpha$ and $\beta$, we will talk about restricted HF (RHF) theory leading to the restricted MP (RMP) series.
+Whereas if the spatial part can be different it leads to the so-called unrestricted HF (UHF) theory and to the unrestricted MP (UMP) series.}
 From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
@@
 As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
-The MP$n$ energy is defined as 
-\begin{equation}
-	E_{\text{MP}n}= \sum_{k=0}^n E^{(k)},
+The MP$l$ energy is defined as 
+\begin{equation}
+	E_{\text{MP}l}= \sum_{k=0}^l E^{(k)},
 \end{equation}
 where $E^{(k)}$ is the $k$th-order correction.
-\titou{$n$ is the number of electrons and here you use it as something else...}
 The MP0 energy overestimates the energy by double counting the electron-electron interaction and is equal to the sum of the occupied orbital energies, i.e.,
@@
 
-As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$n$ series converges to the exact energy when $n$ goes to infinity. 
+As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$l$ series converges to the exact energy when $l$ goes to infinity. 
 In fact, it is known that when the HF wave function is a bad approximation to the exact wave function, for example in multi-reference systems, the MP method yields bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
 A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
-By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function \titou{on $n$ Riemann sheets}. 
+By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function on \antoine{$K$ Riemann sheets where $K$ is the number of function in the basis set}.
 As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
@@
 On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
-\titou{There is a problem here as one has not introduce restricted and unrestricted formalisms.}
 
@@
 They concluded that the slow convergence is due to the coupling of the singly and doubly excited configurations.
-Moreover, the MP and EN numerators in Eqs.~\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
-Yet the MP denominators tends towards a constant when $r \to \infty$ so the terms vanish, whereas the EN denominators tends to zero which improves the convergence but can also make the series diverge.
+Moreover, the MP denominators in \eqref{eq:EMP2} tends towards a constant when $r \to \infty$  whereas the numerators tends to zero so the terms vanish when the bond is stretched.
 Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all of these systems in two classes.
@@
 \begin{equation}
-\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\bH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\bV}
+\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\hH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\hH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\hV}
 \end{equation}
@@
 \begin{equation}\label{eq:HamiltonianStillinger}
-    \bH(\lambda)=\sum_{i=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_i^2 - \sum_{k=1}^{N} \frac{Z_k}{|\vb{r}_i-\vb{R}_k|}}_{\text{Independent of}~\lambda} + \overbrace{(1-\lambda)V_i^{\text{HF}}}^{\textcolor{red}{\text{Repulsive}}}+\underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}}  \right]
+    \hH(\lambda) = 
+    \sum_{i}^{n} \qty[ 
+    \underbrace{-\frac{1}{2}\grad_i^2 
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}_{\text{Independent of}~\lambda}
+    \overbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}^{\textcolor{red}{\text{Repulsive}}}
+    \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}} 
+    ].
 \end{equation}
@@
 \begin{equation}
-\phi_\alpha(\theta_1)=\sum_{l=0}^{\infty}C_{\alpha,l}\frac{Y_{l0}(\Omega_1)}{R}
+\phi_\alpha(\theta_1)=\sum_{k=0}^{\infty}C_{\alpha,k}\frac{Y_{k0}(\theta_1)}{R}
 \end{equation}
@@
 \begin{equation}
-E_{\text{c},\alpha} = \sum_{l=0}^{\infty} C_{\alpha,l}^2 \frac{l(l+1)}{R^2}
+E_{\text{c},\alpha} = \sum_{k=0}^{\infty} C_{\alpha,k}^2 \frac{k(k+1)}{R^2}
 \end{equation}
@@
 
-In this part, we will try to investigate how some parameters of $\bH(\lambda)$ influence the radius of convergence of the perturbation series.
+In this part, we will try to investigate how some parameters of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
 The radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
@@
 To find them we solve simultaneously the equations \eqref{eq:PolChar} and \eqref{eq:DPolChar}.
-The equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system, if an energy is also solution of \eqref{eq:DPolChar} then this energy is degenerate.
+The equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system where $\hI$ is the identity operator.
+If an energy is also solution of \eqref{eq:DPolChar} then this energy is degenerate.
 In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
@@
 \begin{equation}\label{eq:PolChar}
-\text{det}[E-\bH(\lambda)]=0
+\text{det}[E\hI-\hH(\lambda)]=0
 \end{equation}
@@
 \begin{equation}\label{eq:DPolChar}
-\pdv{E}\text{det}[E-\bH(\lambda)]=0
+\pdv{E}\text{det}[E\hI-\hH(\lambda)]=0
 \end{equation}
@@
 
-The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
+The Hamiltonian $\hH(\lambda)$ is block diagonal because of the symmetry of the basis set, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
 The two singly excited states give a singlet sp\textsubscript{z} and a triplet sp\textsubscript{z} state but their symmetry is not the same as the ground state.
@@
 We see that the radius of convergence of the SC partitioning is growing with R whereas it is decreasing for the three others partitioning.
-This result was expected because the three decreasing partitioning use a weakly correlated reference so $\bH^{(0)}$ is a good approximation for small $R$.
+This result was expected because the three decreasing partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
 On the contrary, the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated, i.e., when $R$ is large for the spherium model.
@@
 
-In the UHF formalism the Hamiltonian $\bH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
+In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
 The matrix elements $H_{ij}$ for this interaction are given in \eqref{eq:MatrixElem}.
@@
 
+In order to model properly chemical systems, one need to know which computational method is adapted to each system.
+That means that we need to understand why each method fails in some cases but also why they work with other systems.
+We have seen that for methods relying on perturbation theory the successes and failures of those methods is connected to the position of EPs in the complex plane.
+Much work have been done on the failures of the MP perturbation theory.
+First, it has been understood that for chemical systems for which the Hartree-Fock method yields a poor approximation of the exact wave function, the MP perturbation theory will fail too.
+Such systems can be for example systems where the exact wave function is dominated by more than one configuration i.e.
+multi-reference systems.
+More preoccupying cases were reported rapidly during the development of the MP method.
+It has been proved that systems considered as well-understood, for example \ce{Ne}, can exhibit divergent behavior when the basis set is augmented with diffuse functions.
+
+Afterwards, those behaviors of the perturbation theory have been investigated in terms of avoided crossings and singularities in the complex plane.
+It has been shown that the singularities can be sorted in two parts.
+The first ones are the $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly excited states.
+The $\beta$ ones are consequences in a finite Hilbert space of a ionization phenomenon occurring in the complete Hilbert space.
+Those singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state.
 We have seen that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
-Indeed, those singularities close to the real axis are connected to quantum phase transition.
-In this work we have shown that $\beta$ singularities are also involved in the spin symmetry breaking of the unrestricted Hartree-Fock wave function.
+Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking.
+Some work in theoretical physics have shown that the behavior of the EPs depends of the type of transition from which the EPs result (first or superior order, ground state or excited state transition).
+
+In this work we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the unrestricted Hartree-Fock wave function.
+This confirms that $\beta$ singularities can occur for other type of transition and symmetry breaking than just the formation of the bound cluster of electrons.
 It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure.

### 2020-07-29 RapportStage/Rapport.tex
saving work

--- 2020-07-28 RapportStage/Rapport.tex
@@
 For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
-In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
+In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP \titou{(RMP)} series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted MP series \titou{(UMP)} is monotonically convergent (except for the first few orders) but very slowly. 
+Thus, one cannot practically use it for systems where only the first terms can be computed.
 \titou{There is a problem here as one has not introduce restricted and unrestricted formalisms.}
@@
 Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in Ref.~\cite{SzaboBook}).
-\antoine{It could be expected that  the restricted MP series has inappropriate convergence properties as a restricted HF Slater determinant is a poor approximation of the exact wave function for stretched system.
-However even in the unrestricted formalism the series does not give accurate results at low orders.
-Whereas the unrestricted formalism allows a better description of a stretched system because the spatial orbitals of electrons $\alpha$ and $\beta$ are not restricted to be the same \cite{Fukutome_1981}.} Even with this improvement of the zeroth-order wave function the series does not have the smooth and rapidly converging behavior wanted.
+One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
+However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly converging behavior that one would wish for.
 
@@
     \centering
-    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
+    \caption{Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
     \begin{tabular}{ccccccc}
@@
 
-In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function which leads to spin contamination.
-Gill \textit{et al.}~highlighted the link between slow convergence of the unrestricted MP series and spin contamination of the wave function as shown in Table \ref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
-Handy and coworkers exhibited the same behavior of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
-Lepetit et al.~analyzed the difference between the MP and EN partitioning for the unrestricted HF reference \cite{Lepetit_1988}.
-They concluded that the slow convergence is due to the coupling of the singly and doubly excited configurations.
-Moreover, the MP and EN numerators in Eqs.~\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function, leading to the so-called spin contamination issue.
+Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination, as shown in Table \ref{tab:SpinContamination} for the example of \ce{H2} in a minimal basis \cite{Gill_1988}.
+Handy and coworkers reported the same behavior of the series (oscillating and \titou{slowly monotonically convergent}) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
+Lepetit et al.~analyzed the difference between the MP and EN partitioning for the UHF reference \cite{Lepetit_1988}.
+They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations.
+%Moreover, the MP and EN numerators in Eqs.~\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
 Yet the MP denominators tends towards a constant when $r \to \infty$ so the terms vanish, whereas the EN denominators tends to zero which improves the convergence but can also make the series diverge.
-Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all of these systems in two classes.
-The class A systems where one observes a monotonic convergence to the FCI energy and the class B for which convergence is erratic after initial oscillations.
+Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the class A systems where one observes a monotonic convergence to the FCI energy, and ii) the class B for which convergence is erratic after initial oscillations.
 The sample of systems contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
@@
 \end{quote}
-They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.
-The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
+\titou{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.} The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
 Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
@@
 \begin{equation}
-\widehat{H} = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}}
+	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}}
 \end{equation}

### 2020-07-29 RapportStage/Rapport.tex

--- 2020-07-29 RapportStage/Rapport.tex
@@
 For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
-In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted MP series is monotonically convergent (except for the first few orders) but very slowly so one cannot use it in practice for systems where one can only compute the first terms.
+In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP \titou{(RMP)} series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+On the other hand, the unrestricted MP series \titou{(UMP)} is monotonically convergent (except for the first few orders) but very slowly. 
+Thus, one cannot practically use it for systems where only the first terms can be computed.
+\titou{There is a problem here as one has not introduce restricted and unrestricted formalisms.}
 
@@
 
-In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function which leads to spin contamination.
-Gill \textit{et al.}~highlighted the link between slow convergence of the unrestricted MP series and spin contamination of the wave function as shown in Table \ref{tab:SpinContamination} in the example of \ce{H_2} in a minimal basis \cite{Gill_1988}.
-Handy and coworkers exhibited the same behavior of the series (oscillating and monotonically slowly) in stretched \ce{H_2O} and \ce{NH_2} systems \cite{Handy_1985}.
-Lepetit et al.~analyzed the difference between the MP and EN partitioning for the unrestricted HF reference \cite{Lepetit_1988}.
-They concluded that the slow convergence is due to the coupling of the singly and doubly excited configurations.
-Moreover, the MP denominators in \eqref{eq:EMP2} tends towards a constant when $r \to \infty$  whereas the numerators tends to zero so the terms vanish when the bond is stretched.
-Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and regrouped all of these systems in two classes.
-The class A systems where one observes a monotonic convergence to the FCI energy and the class B for which convergence is erratic after initial oscillations.
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function, leading to the so-called spin contamination issue.
+Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination, as shown in Table \ref{tab:SpinContamination} for the example of \ce{H2} in a minimal basis \cite{Gill_1988}.
+Handy and coworkers reported the same behavior of the series (oscillating and \titou{slowly monotonically convergent}) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
+Lepetit et al.~analyzed the difference between the MP and EN partitioning for the UHF reference \cite{Lepetit_1988}.
+They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations.
+%Moreover, the MP and EN numerators in Eqs.~\eqref{eq:EMP2} and \eqref{eq:EEN2} are the same and they vanish when the bond length $r$ goes to infinity.
+Yet the MP denominators tends towards a constant when $r \to \infty$ so the terms vanish, whereas the EN denominators tends to zero which improves the convergence but can also make the series diverge.
+Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the class A systems where one observes a monotonic convergence to the FCI energy, and ii) the class B for which convergence is erratic after initial oscillations.
 The sample of systems contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.

### 2020-07-29 RapportStage/Rapport.tex
T2 OK up to end of Sec II

@@
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis. 
-\antoine{If the spatial parts of the spin-orbital basis are restricted to be the same for electrons $\alpha$ and $\beta$, we will talk about restricted HF (RHF) theory leading to the restricted MP (RMP) series.
-Whereas if the spatial part can be different it leads to the so-called unrestricted HF (UHF) theory and to the unrestricted MP (UMP) series.}
+If the spatial part of the spin-orbitals are restricted to be the same for spin-up and spin-down electrons, one talks about restricted HF (RHF) theory, whereas if one does not enforce this constrain it leads to the so-called unrestricted HF (UHF) theory.
 From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
+
 Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
@@
 \begin{equation}\label{eq:HFHamiltonian}
-	\hH^{\text{HF}} = \sum_{i}^{n} f(\vb{x}_i).
+	\hH^{\text{HF}} = \sum_{i} f(\vb{x}_i).
 \end{equation}
@@
 % where the two-electron part of the Fock operator $f(i)$ has been written $V_i^{HF}$ for convenience.
-
 \begin{equation}\label{eq:MPHamiltonian}
@@
 \end{equation}
+If one considers a RHF or UHF reference wave functions, it leads to the RMP or UMP series, respectively.
+
 As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
-The MP$l$ energy is defined as 
-\begin{equation}
-	E_{\text{MP}l}= \sum_{k=0}^l E^{(k)},
+The MP$m$ energy is defined as 
+\begin{equation}
+	E_{\text{MP}m}= \sum_{k=0}^m E^{(k)},
 \end{equation}
@@
 \begin{equation}
-	E_{\text{MP0}} = \sum_i^n \epsilon_i.
+	E_{\text{MP0}} = \sum_i \epsilon_i.
 \end{equation}
@@
 \begin{equation}
-	E_{\text{MP1}} = E_\text{HF} = \sum_i^n \epsilon_i - \frac{1}{2} \sum_{ij}^n \mel{ij}{}{ij},
+	E_{\text{MP1}} = E_\text{HF} = \sum_i \epsilon_i - \frac{1}{2} \sum_{ij} \mel{ij}{}{ij},
 \end{equation}
@@
 
-As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$l$ series converges to the exact energy when $l$ goes to infinity. 
+As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$m$ series converges to the exact energy when $m$ goes to infinity. 
 In fact, it is known that when the HF wave function is a bad approximation to the exact wave function, for example in multi-reference systems, the MP method yields bad results \cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}.
 A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
-By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function on \antoine{$K$ Riemann sheets where $K$ is the number of function in the basis set}.
+By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
 As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
@@
 For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
-\titou{If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.}
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
 
@@
 For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
-In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the restricted MP \titou{(RMP)} series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
-On the other hand, the unrestricted MP series \titou{(UMP)} is monotonically convergent (except for the first few orders) but very slowly. 
+In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the RMP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
 Thus, one cannot practically use it for systems where only the first terms can be computed.
-\titou{There is a problem here as one has not introduce restricted and unrestricted formalisms.}
 
@@
     \underbrace{-\frac{1}{2}\grad_i^2 
-    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}_{\text{Independent of}~\lambda}
-    \overbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}^{\textcolor{red}{\text{Repulsive}}}
-    \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive}}} 
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}_{\text{Independent of $\lambda$}}
+    + \overbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}^{\textcolor{red}{\text{Repulsive for $\lambda < 1$}}}
+    + \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\textcolor{blue}{\text{Attractive for $\lambda < 0$}}} 
     ].
@@
 If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
-\antoine{For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei}.
-According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_c$.
+For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei.
+According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_\text{c}$.
 At this point the system undergo a phase transition \titou{and a symmetry breaking}.
@@
 
-\antoine{This reasoning is done on the exact Hamiltonian and energy, i.e., the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis}.
-\antoine{However, in a finite basis set which does not span the complete Hilbert space}, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+This reasoning is done on the exact Hamiltonian and energy, i.e., the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis.
+However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
 Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger \cite{Stillinger_2000}, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
@@
 Those excited states have a non-negligible contribution to the exact FCI solution because they have the same spatial and spin symmetry as the ground state.
-\antoine{We think that $\alpha$ singularities are connected the states with non-negligible contribution in the configuration interaction expansion thus to the dynamical part of the correlation energy.
-Whereas the $\beta$ singularities are linked to symmetry breaking and phase transition of the wave function, i.e., the multi-reference aspect of the wave function thus to the static part of the correlation energy.}
+We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the configuration interaction expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, i.e., to the multi-reference nature of the wave function thus to the static part of the correlation energy.
 
@@
 
-In order to model properly chemical systems, one need to know which computational method is adapted to each system.
-That means that we need to understand why each method fails in some cases but also why they work with other systems.
-We have seen that for methods relying on perturbation theory the successes and failures of those methods is connected to the position of EPs in the complex plane.
-Much work have been done on the failures of the MP perturbation theory.
-First, it has been understood that for chemical systems for which the Hartree-Fock method yields a poor approximation of the exact wave function, the MP perturbation theory will fail too.
-Such systems can be for example systems where the exact wave function is dominated by more than one configuration i.e.
-multi-reference systems.
-More preoccupying cases were reported rapidly during the development of the MP method.
-It has been proved that systems considered as well-understood, for example \ce{Ne}, can exhibit divergent behavior when the basis set is augmented with diffuse functions.
-
-Afterwards, those behaviors of the perturbation theory have been investigated in terms of avoided crossings and singularities in the complex plane.
-It has been shown that the singularities can be sorted in two parts.
-The first ones are the $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly excited states.
-The $\beta$ ones are consequences in a finite Hilbert space of a ionization phenomenon occurring in the complete Hilbert space.
-Those singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state.
+In order to model accurately chemical systems, one must choose, in a ever larger zoo of methods, which computational protocol is adapted to the system of interest.
+This choice can be, moreover, motivated by the type of properties that one is interested in.
+That means that one must understand the strengths and weaknesses of each method, i.e., why one method might fail in some cases and work beautifully in others. 
+We have seen that for methods relying on perturbation theory the successes and failures are directly connected to the position of EPs in the complex plane. 
+Exhaustive studies have been performed on the causes of failure of MP perturbation theory. 
+First, it has been understood that, for chemical systems for which the HF method is a poor approximation to the exact wave function, MP perturbation theory will fail too.
+Such systems can be, for example, systems where the exact wave function is dominated by more than one configuration, i.e., multi-reference systems.
+More preoccupying cases were reported. 
+For instance, it has been shown that systems considered as well-understood (e.g., \ce{Ne}) can exhibit divergent behavior when the basis set is augmented with diffuse functions. 
+Later, these behaviors of the perturbation series have been investigated and rationalized in terms of avoided crossings and singularities in the complex plane.
+It has been shown that the singularities can be classified in two families.
+The first family includes $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly-excited states. 
+The $\beta$ singularities, which constitutes the second family, are artifacts generated by the incompleteness of the Hilbert space, and they are directly connected to an ionization phenomenon occurring in the complete Hilbert space.
+These singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state. 
 We have seen that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
-Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking.
-Some work in theoretical physics have shown that the behavior of the EPs depends of the type of transition from which the EPs result (first or superior order, ground state or excited state transition).
-
-In this work we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the unrestricted Hartree-Fock wave function.
-This confirms that $\beta$ singularities can occur for other type of transition and symmetry breaking than just the formation of the bound cluster of electrons.
+Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking, and theoretical physics have demonstrated that the behavior of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).
+
+In this work, we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the UHF wave function. 
+This confirms that $\beta$ singularities can occur for other types of transition and symmetry breaking than just the formation of a bound cluster of electrons. 
 It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure. 
 Moreover the singularity structure in the non-Hermitian case still need to be investigated. 
-In the holomorphic domain some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
-To conclude this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of exceptional points in electronic structure theory.
+In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
+To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
 

### 2020-07-29 RapportStage/Rapport.tex
minor corrections

@@
 \end{quote}
-\titou{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.} The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+\titou{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.} \antoine{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the system it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
 
@@
 \begin{itemize}
-	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [restricted Hartree-Fock (RHF) or unrestricted Hartree-Fock (UHF) references, MP or EN partitioning], or strongly correlated reference.
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [RHF or UHF references, MP or EN partitioning], or strongly correlated reference.
 	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions
@@
     \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
-    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian $\bH(\lambda)$.}
+    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian $\hH(\lambda)$.}
     \label{fig:RadiusPartitioning}

### 2020-07-29 RapportStage/Rapport.tex
OK up to sec 4

--- 2020-07-29 RapportStage/Rapport.tex
@@
 \section{Introduction}
+\label{sec:intro}
 %============================================================%
@@
 As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
-These singularities of the energy function are exactly the exceptional points connecting the electronic states as mentioned in the introduction. 
+These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
 The direct computation of the terms of the series is quite manageable up to 4th order in perturbation, while the 5th and 6th order in perturbation can still be obtained but at a rather high cost \cite{JensenBook}.
@@
 Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility. 
-Here, we will consider three alternative partitioning schemes
+Here, we will consider three alternative partitioning schemes:
 \begin{itemize}
 	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. 
-	Hence, the off-diagonal elements of $\hH$ are the perturbation operator. .
+	Hence, the off-diagonal elements of $\hH$ are the perturbation operator.
 	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$.
-	\item The strong coupling (SC) partitioning where the two operators are inverted as compared to the WC partitioning.
+	\item The strong coupling (SC) partitioning where the two operators are inverted compared to the WC partitioning.
 \end{itemize}
@@
 Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
-For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretch systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
-In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the RMP series is convergent, yet oscillating which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\cite{Handy_1985, Lepetit_1988}).
+In Fig.~\ref{fig:RUMP_Gill}, which has been extracted from Ref.~\cite{Gill_1986}, one can see that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
 On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
@@
 
-When a bond is stretched, in most cases the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be single Slater determinant.
-Thus, it is inappropriate to model (even qualitatively) stretched system.
+When a bond is stretched, in most cases the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be a single Slater determinant.
+Thus, it is inappropriate to model (even qualitatively) stretched systems.
 Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H_2} in Ref.~\cite{SzaboBook}).
@@
     \centering
-    \caption{Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from \cite{Gill_1988}).}
+    \caption{Percentage of electron correlation energy recovered and $\expval*{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set (taken from Ref.~\cite{Gill_1988}).}
     \begin{tabular}{ccccccc}
@@
 \hline
- $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
+ $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval*{S^2}$ \\
 \hline
@@
 
-In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave function, leading to the so-called spin contamination issue.
-Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination, as shown in Table \ref{tab:SpinContamination} for the example of \ce{H2} in a minimal basis \cite{Gill_1988}.
-Handy and coworkers reported the same behavior of the series (oscillating and \titou{slowly monotonically convergent}) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
-Lepetit et al.~analyzed the difference between the MP and EN partitioning for the UHF reference \cite{Lepetit_1988}.
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
+Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination, as shown in Table \ref{tab:SpinContamination} for \ce{H2} in a minimal basis \cite{Gill_1988}.
+Handy and coworkers reported the same behavior of the series (oscillatory and \titou{slowly monotonically convergent}) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
+Lepetit \textit{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference \cite{Lepetit_1988}.
 They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations.
@@
 Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the class A systems where one observes a monotonic convergence to the FCI energy, and ii) the class B for which convergence is erratic after initial oscillations.
-The sample of systems contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
+Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
 They highlighted that \cite{Cremer_1996}
@@
 \end{quote}
-\titou{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems, this improves the precision of those formulas.} The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+\titou{They proved that using specific extrapolation formulas involving the first terms of the MP series for class A and class B systems improves the precision of those formulas.} The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different convergence modes would lead to a more rationalized use of MP perturbation theory and to more accurate correlation energies.
 
@@
 
-In the late 90's, Olsen \textit{et al.}~have discovered an even more preoccupying behavior of the MP series \cite{}.
+In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behavior of the MP series \cite{Olsen_1996}.
 They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF} (see Fig.~\ref{fig:NeHFDiv}) \cite{Olsen_1996, Christiansen_1996}.
@@
     \includegraphics[width=0.45\textwidth]{HFdivergence.png}
-    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from \cite{Olsen_1996}).}
+    \caption{\centering Correlation contributions for \ce{Ne} and \ce{HF} in the cc-pVTZ-(f/d) $\circ$ and aug-cc-pVDZ $\bullet$ basis sets (taken from Ref.~\cite{Olsen_1996}).}
     \label{fig:NeHFDiv}
@@
 The discovery of this divergent behavior is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
-Including diffuse functions is particularly important for the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
+Including diffuse functions is particularly important in the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
 As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence.
@@
 A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
-Theie method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularity.
-Then by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularity by finding the EPs of the $2\times2$ Hamiltonian.
-The diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbative part of the Hamiltonian.
-
-\begin{equation}
-\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\hH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\hH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\hV}
-\end{equation}
-
-They first studied molecules with low-lying doubly excited states of the same spatial and spin symmetry because in those systems the HF wave function is a bad approximation.
-The exact wave function has a non-negligible contribution from the doubly excited states, so those low-lying excited states were good candidates for being intruder states.
+Their method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities.
+Then by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ Hamiltonian
+\begin{equation}
+\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\hH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\hH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\hV},
+\end{equation}
+where the diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbation.
+
+They first studied molecules with low-lying doubly-excited states of the same spatial and spin symmetry.
+% \titou{because in those systems the HF wave function is a bad approximation.} 
+The exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states were good candidates for being intruder states.
 For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
@@
 
-Then they demonstrated that the divergence for the \ce{Ne} is due to a back-door intruder state.
+Then they demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state.
 When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back-door intruder state.
 They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series.
-They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state.
-
-Moreover they proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} cannot be used for all systems.
-Even more, that those formula were not mathematically motivated when looking at the singularity causing the divergence.
-For example the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly excited states which results in alternated terms up to order ten and then the series is monotonically convergent.
-This is due to the fact that two pairs of singularity are approximately at the same distance from the origin.
+%They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state.
+
+Moreover they proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} cannot be used for all systems, and that these formulas were not mathematically motivated when looking at the singularity causing the divergence.
+For example, the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly-excited states which results in alternated terms up to 10th order.
+For higher orders, the series is monotonically convergent.
+This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
 
@@
 Singularities of type $\alpha$ are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They succeeded to explain the divergence of the series caused by $\beta$ singularities using a previous work of Stillinger \cite{Stillinger_2000}.
+They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work of Stillinger \cite{Stillinger_2000}.
 
@@
 Sergeev and Goodson proved \cite{Sergeev_2005}, as predicted by Stillinger \cite{Stillinger_2000}, that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-They explain that Olsen et al., because they used a $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
-
-Finally, it was shown that $\beta$ singularities are very sensitive to changes of the basis set but not to the stretching of the system.
+This explains that Olsen \textit{et al.}, because they used a simple $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
+
+Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the stretching of the system.
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-According to Goodson, \cite{Goodson_2004} the singularity structure from molecules stretched from the equilibrium geometry is difficult, this is consistent with the observation of Olsen and co-workers  \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.
-To our knowledge the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization effect and its link with diffuse function.
-In this work we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
+\titou{According to Goodson \cite{Goodson_2004}, the singularity structure from molecules stretched from the equilibrium geometry is difficult, this is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.} To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
 
@@
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
-Otherwise, it is called continuous and of $n$th order if the $n$th derivative is discontinuous.
+Otherwise, it is called continuous and of $m$th order if the $m$th derivative is discontinuous.
 A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
@@
 More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT \cite{Stransky_2018}.
-In particular, they showed that when the dimensionality of the system increases, first- and second-order QTP behave differently, and converge towards the real axis at different rates (exponentially and algebraically for the first and second order, respectively).
-
-It seems like our understanding of the physics of spatial and/or spin symmetry breaking in the Hartree-Fock theory can be enlightened by QPT theory.
-Indeed, the second derivative of the energy is discontinuous at the Coulson-Fischer point which means that the system undergo a second-order QPT.
+\titou{In particular, they showed that when the dimensionality of the system increases, first- and second-order QTP behave differently, and the position of these singularities converge towards the real axis at different rates (exponentially and algebraically for the first and second order, respectively).}
+
+It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.
+Indeed, the second derivative of the energy is discontinuous at the \titou{Coulson-Fischer point (not defined)} which means that the system undergo a second-order QPT.
 Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
@@
 However, the $\alpha$ singularities arise from large avoided crossings.
-Thus, they can not be connected to QPT.
+Thus, they cannot be connected to QPT.
 The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states.
 Those excited states have a non-negligible contribution to the exact FCI solution because they have the same spatial and spin symmetry as the ground state.
-We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the configuration interaction expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, i.e., to the multi-reference nature of the wave function thus to the static part of the correlation energy.
+We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, i.e., to the multi-reference nature of the wave function thus to the static part of the correlation energy.
 
@@
 
-The laplacian operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}$ is the Coulomb operator.
+The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}$ is the Coulomb operator.
 The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
@@
 Therefore the Hamiltonian becomes non-Hermitian for those value of $R$.
-In \cite{Burton_2019a} Burton et al.
-proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
+In \cite{Burton_2019a} Burton \textit{et al.}~proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
 An analog reasoning can be done with the spherium model to prove the same result.
@@
 
-In order to model accurately chemical systems, one must choose, in a ever larger zoo of methods, which computational protocol is adapted to the system of interest.
+In order to model accurately chemical systems, one must choose, in a ever growing zoo of methods, which computational protocol is adapted to the system of interest.
 This choice can be, moreover, motivated by the type of properties that one is interested in.

### 2020-07-29 RapportStage/Rapport.tex

@@
 \end{quote}
-\titou{They proved that using specific extrapolation formulas involving the first terms of the MP series for class A and class B systems improves the precision of those formulas.} The mean deviation from FCI correlation energies is $0.3$ millihartree whereas with the formula that do not distinguish the system it is 12 millihartree.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different convergence modes would lead to a more rationalized use of MP perturbation theory and to more accurate correlation energies.
+\antoine{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the system it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+%>>>>>>> 4aba1a6e837a50f3a21d610948564733096cf38e
 

### 2020-07-29 RapportStage/Rapport.tex
OK up to sec 4 and ccl

@@
 That means that one must understand the strengths and weaknesses of each method, i.e., why one method might fail in some cases and work beautifully in others. 
-We have seen that for methods relying on perturbation theory the successes and failures are directly connected to the position of EPs in the complex plane. 
+We have seen that for methods relying on perturbation theory, their successes and failures are directly connected to the position of EPs in the complex plane. 
 Exhaustive studies have been performed on the causes of failure of MP perturbation theory. 
-First, it has been understood that, for chemical systems for which the HF method is a poor approximation to the exact wave function, MP perturbation theory will fail too.
-Such systems can be, for example, systems where the exact wave function is dominated by more than one configuration, i.e., multi-reference systems.
-More preoccupying cases were reported. 
+First, it was understood that, for chemical systems for which the HF Slater determinant is a poor approximation to the exact wave function, MP perturbation theory fails too.
+Such systems can be, for example, molecules where the exact ground-state wave function is dominated by more than one configuration, i.e., multi-reference systems.
+More preoccupying cases were also reported. 
 For instance, it has been shown that systems considered as well-understood (e.g., \ce{Ne}) can exhibit divergent behavior when the basis set is augmented with diffuse functions. 
-Later, these behaviors of the perturbation series have been investigated and rationalized in terms of avoided crossings and singularities in the complex plane.
-It has been shown that the singularities can be classified in two families.
+Later, these erratic behaviors of the perturbation series were investigated and rationalized in terms of avoided crossings and singularities in the complex plane.
+It was shown that the singularities can be classified in two families.
 The first family includes $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly-excited states. 
@@
 These singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state. 
-We have seen that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
+We have found that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
 Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking, and theoretical physics have demonstrated that the behavior of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).

### 2020-07-30 RapportStage/Rapport.tex
saving work in sec 4

@@
 
-Simple systems that are analytically solvable (or at least quasi-exactly solvable) are of great importance in theoretical chemistry.
-Those systems are very useful benchmarks to test new methods as they are mathematically easy but retain much of the key physics.
-To investigate the physics of EPs we use one such system named spherium model.
+Simple systems that are analytically solvable (or at least quasi-exactly solvable \titou{(please define)}) are of great importance in theoretical chemistry. 
+These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
+To investigate the physics of EPs we consider one such system named \textit{spherium}. 
 It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. 
-Thus the Hamiltonian is:
-
+Thus, the Hamiltonian is
 \begin{equation}
@@
 \end{equation}
-
-The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}$ is the Coulomb operator.
-The radius R of the sphere dictates the correlation regime, i.e., weak correlation regime at small $R$ where the kinetic energy dominates, or strong correlation regime where the electron repulsion term drives the physics.
-We will use this model to try to rationalize the effects of the parameters that may influence the physics of EPs:
+\titou{T2: I would write the Hamiltonian as a function of the interelectronic angle $\omega$ to highlight the different scaling of the kinetic and potential terms.
+This would help following the discussion below which I think is a bit too fast.}
+
+The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
+Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
+The radius of the sphere $R$ dictates the correlation regime. 
+In the weak correlation regime (i.e., small $R$), the kinetic energy dominates and the electrons are delocalized over the sphere.
+For large $R$ (or strong correlation regime), the electron repulsion term drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion. 
+This phenomenon is sometimes referred as a Wigner crystalization.
+\titou{T2: Missing references in this part.}
+
+We will use this model in order to rationalize the effects of the parameters that may influence the physics of EPs:
 \begin{itemize}
-	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference [RHF or UHF references, MP or EN partitioning], or strongly correlated reference.
-	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions
-	\item Radius of the spherium that ultimately dictates the correlation regime.
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
+	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions.
+	\item Radius of the sphere that ultimately dictates the correlation regime.
 \end{itemize}
 
-In the RHF formalism, the wave function cannot model properly the physics of the system at large R because the spatial orbitals are restricted to be the same.
+In the RHF formalism, the wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same. 
 If the spatial orbitals are the  same a fortiori it cannot represent two electrons on opposite side of the sphere. 
-In the UHF formalism there is a critical value of R, called the Coulson-Fischer point \cite{Coulson_1949}, at which a second UHF solution appears.
-This solution is symmetry-broken as the two electrons tends to localize on opposite side of the sphere.
-The UHF wave function is defined as:
-
+In the UHF formalism there is a critical value of $R$, called the Coulson-Fischer point \cite{Coulson_1949}, at which a UHF solution appears. 
+This solution has broken symmetry as the two electrons tends to localize on opposite side of the sphere. 
+\titou{T2: This paragraph could be improved.}
+
+The UHF wave function is defined as
 \begin{equation}\label{eq:UHF_WF}
@@
 \end{equation}
-
-Then the mono-electronic wave function are expand in the spatial basis set of the zonal spherical harmonics:
+\titou{T2: Please define the RHF wave function first. The angles are not defined.}
+
+Then the one-electron orbitals are expanded in the spatial basis set of the zonal spherical harmonics $Y_{k}(\theta)$:
 

### 2020-07-30 RapportStage/Rapport.tex
saving work in sec 4

@@
 \begin{equation}
-	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}}
-\end{equation}
-\titou{T2: I would write the Hamiltonian as a function of the interelectronic angle $\omega$ to highlight the different scaling of the kinetic and potential terms.
-This would help following the discussion below which I think is a bit too fast.}
-
+	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}},
+\end{equation}
+or
+\begin{equation}
+	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
+\end{equation}
+where $\omega$ is the interelectronic angle.
 The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
@@
 The radius of the sphere $R$ dictates the correlation regime. 
-In the weak correlation regime (i.e., small $R$), the kinetic energy dominates and the electrons are delocalized over the sphere.
-For large $R$ (or strong correlation regime), the electron repulsion term drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion. 
-This phenomenon is sometimes referred as a Wigner crystalization.
+In the weak correlation regime (i.e., small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
+For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
+This phenomenon is sometimes referred to as a Wigner crystallization.
 \titou{T2: Missing references in this part.}
@@
 
-In the RHF formalism, the wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same. 
-If the spatial orbitals are the  same a fortiori it cannot represent two electrons on opposite side of the sphere. 
-In the UHF formalism there is a critical value of $R$, called the Coulson-Fischer point \cite{Coulson_1949}, at which a UHF solution appears. 
-This solution has broken symmetry as the two electrons tends to localize on opposite side of the sphere. 
-\titou{T2: This paragraph could be improved.}
-
-The UHF wave function is defined as
+In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
+The spatial part of the RHF wave function is then
+\begin{equation}\label{eq:RHF_WF}
+	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2)
+\end{equation}
+where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic.
+
+The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
+In the UHF formalism there is a critical value of $R$, called Coulson-Fischer point \cite{Coulson_1949}, at which a UHF solution appears and is lower in energy than the RHF one.
+The UHF solution has broken symmetry as the two electrons tends to localize on opposite sides of the sphere. 
+The spatial part of the UHF wave function is defined as
 \begin{equation}\label{eq:UHF_WF}
@@
 \end{equation}
-\titou{T2: Please define the RHF wave function first. The angles are not defined.}
-
-Then the one-electron orbitals are expanded in the spatial basis set of the zonal spherical harmonics $Y_{k}(\theta)$:
-
-\begin{equation}
-\phi_\alpha(\theta_1)=\sum_{k=0}^{\infty}C_{\alpha,k}\frac{Y_{k0}(\theta_1)}{R}
-\end{equation}
-
+where $\phi_\sigma(\theta)$ is the spatial orbital associated with the spin-$\sigma$ electrons ($\sigma = \alpha$ for spin-up electrons and $\sigma = \beta$ for spin-down electrons).
+These one-electron orbitals are expanded in the basis of zonal spherical harmonics
+\begin{equation}
+	\phi_\sigma(\theta)=\sum_{\ell=0}^{\infty}C_{\sigma,\ell}Y_{\ell}(\theta)
+\end{equation}
 It is possible to obtain the formula for the ground state UHF energy in this basis set \cite{Loos_2009}:
@@
 \centering
-\caption{\centering RHF and UHF energies in the minimal basis and exact energies for various R.}
+\caption{\centering RHF and UHF energies in the minimal basis and exact energies for various $R$.}
 \begin{tabular}{ccccccccc}
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.9\textwidth]{EsbHF.pdf}
-    \caption{\centering Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+\begin{wrapfigure}{r}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EsbHF.pdf}
+    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
     \label{fig:SpheriumNrj}
-\end{figure}
+\end{wrapfigure}
 
@@
 Hence we need to determine the locations of the exceptional points to obtain information on the convergence properties.
-To find them we solve simultaneously the equations \eqref{eq:PolChar} and \eqref{eq:DPolChar}.
-The equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system where $\hI$ is the identity operator.
-If an energy is also solution of \eqref{eq:DPolChar} then this energy is degenerate.
+To find them we solve simultaneously Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar}.
+Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system where $\hI$ is the identity operator.
+If an energy is also solution of Eq.~\eqref{eq:DPolChar} then this energy is degenerate.
 In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
@@
 
-\begin{equation}\label{eq:PolChar}
-\text{det}[E\hI-\hH(\lambda)]=0
-\end{equation}
-
-\begin{equation}\label{eq:DPolChar}
-\pdv{E}\text{det}[E\hI-\hH(\lambda)]=0
-\end{equation}
+\begin{subequations}
+\begin{align}
+	\label{eq:PolChar}
+	\text{det}[E\hI-\hH(\lambda)] & = 0,
+	\\ 
+	\label{eq:DPolChar}
+	\pdv{E}\text{det}[E\hI-\hH(\lambda)] & = 0.
+\end{align}
+\end{subequations}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{EMP_RHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
+\begin{wrapfigure}{c}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
+    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
     \label{fig:RHFMiniBas}
-\end{figure}
+\end{wrapfigure}
 
@@
 We can not use configuration state function in this case.
-So when we compute all the degeneracies using \eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
+So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
 The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{EMP_UHF_R10.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
+\begin{wrapfigure}{c}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
+    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
     \label{fig:UHFMiniBas}
-\end{figure}
+\end{wrapfigure}
 

### 2020-07-30 RapportStage/Rapport.tex
saving work in sec 4

@@
 \begin{equation}
-E_{\text{UHF}} = E_{\text{c},\alpha} + E_{\text{c},\beta} + E_{\text{p}}
-\end{equation}
-
-\begin{equation}
-E_{\text{c},\alpha} = \sum_{k=0}^{\infty} C_{\alpha,k}^2 \frac{k(k+1)}{R^2}
-\end{equation}
-
-\begin{equation}
-E_{\text{p}} = \sum_{i,j,k,l=0}^{\infty}C_{\alpha,i}C_{\alpha,j}C_{\beta,k}C_{\beta,l} \frac{(-1)^{k+l}S_{i,j,k,l}}{R}\sum_{L=0}^{\infty} \begin{pmatrix}
- i & j & L \\
- 0 & 0 & 0
-\end{pmatrix}^2 \begin{pmatrix}
- k & l & L \\
+E_{\text{UHF}} = T_{\alpha} + T_{\beta} + V
+\label{eq:EUHF}
+\end{equation}
+with
+\begin{gather}
+	T_{\sigma} = \frac{1}{R^2} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1)
+	\\
+	V = \frac{1}{R} \sum_{\ell_1,\ell_2,\ell_3,\ell_4=0}^{\infty} \sum_{L=0}^{\infty} 
+	(-1)^{\ell_3+\ell_4} v^\alpha_{\ell_1,\ell_2,L} v^\beta_{\ell_3,\ell_4,L} 
+\end{gather}
+and
+\begin{equation}
+	v^\sigma_{\ell_1,\ell_2,L} 
+	= \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
+	\begin{pmatrix}
+		\ell_1 & \ell_2 & L 
+		\\
 		0 & 0 & 0
 	\end{pmatrix}^2 
-\label{eq:EUHF}
-\end{equation}
-
-\begin{equation*}
-S_{i,j,k,l}=\sqrt{(2i+1)(2j+1)(2k+1)(2l+1)}
-\end{equation*}
-
-We obtained the equation \eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients.
+\end{equation}
+\titou{T2: please define Wigner 3j symbols.}
+
+We obtained Eq.~\eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients.
 The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.

### 2020-07-30 RapportStage/Rapport.tex
saving work in sec 4

@@
 \titou{T2: please define Wigner 3j symbols.}
-
-We obtained Eq.~\eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients.
-The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis, composed  of a $Y_{00}$ and a $Y_{10}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
+\titou{STOPPED HERE.}
+
+Equation \eqref{eq:EUHF} is obtained from the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy has to be stationary with respect to the coefficients.
+The general method is to use a self-consistent field procedure \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
+We will work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbitals, to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions.
@@
 \begin{equation}
-\phi_\alpha(\theta_1)= \cos(\chi_\alpha)\frac{Y_{00}(\theta_1)}{R} + \sin(\chi_\alpha)\frac{Y_{10}(\theta_1)}{R}
-\end{equation}
-
-The minimization gives the three following solutions valid for all value of R:
+	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta)
+\end{equation}
+
+The minimization gives the three following solutions valid for all value of $R$:
 \begin{itemize}
-\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$
+\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R^{2}$.
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $1/R^{2} + 1/R$
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$
 \end{itemize}
@@
 The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
-This solution have the energy \eqref{eq:EsbUHF} for $R>3/2$.
+This solution has the energy \eqref{eq:EsbUHF} for $R>3/2$.
 
@@
 Indeed, the spherical harmonics are eigenvectors of $S^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $S^2$.
-However this solution gives more accurate results for the energy at large R as shown in Table \ref{tab:ERHFvsEUHF}.
+However this solution gives more accurate results for the energy at large $R$ as shown in Table \ref{tab:ERHFvsEUHF}.
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
@@
 \end{table}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EsbHF.pdf}
+    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+    \label{fig:SpheriumNrj}
+\end{wrapfigure}
 
@@
 This solution is called symmetry-broken RHF (sb-RHF).
-At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
+At the critical value of $R$, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
 This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
@@
 
-We can also consider negative values of R.
+We can also consider negative values of $R$.
 This corresponds to the situation where one of the electrons is replaced by a positron.
-There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of R (see Fig.\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
+There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
 Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{EsbHF.pdf}
-    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
-    \label{fig:SpheriumNrj}
-\end{wrapfigure}
-
 \section{Radius of convergence and exceptional points}
@@
 The radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
-Hence we need to determine the locations of the exceptional points to obtain information on the convergence properties.
+Hence, we have to determine the locations of the exceptional points to obtain information on the convergence properties.
 To find them we solve simultaneously Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar}.

### 2020-07-30 RapportStage/Rapport.tex
corrections

--- 2020-07-30 RapportStage/Rapport.tex
@@
 Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination, as shown in Table \ref{tab:SpinContamination} for \ce{H2} in a minimal basis \cite{Gill_1988}.
-Handy and coworkers reported the same behavior of the series (oscillatory and \titou{slowly monotonically convergent}) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
+Handy and coworkers reported the same behavior of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2} systems \cite{Handy_1985}.
 Lepetit \textit{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference \cite{Lepetit_1988}.
@@
 \end{quote}
-\antoine{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
-The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the system it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
-%>>>>>>> 4aba1a6e837a50f3a21d610948564733096cf38e
+\antoine{As one can only compute the first terms of the MP$l$ series, a smart way to get more accurate results is to use extrapolation formula of this series.
+They proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
 
@@
 According to Baker \cite{Baker_1971}, this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_\text{c}$.
-At this point the system undergo a phase transition \titou{and a symmetry breaking}.
-\titou{Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.}
+At this point the system undergo a phase transition and a symmetry breaking.
+Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.
 
@@
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-\titou{According to Goodson \cite{Goodson_2004}, the singularity structure from molecules stretched from the equilibrium geometry is difficult, this is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.} To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+\antoine{According to Goodson \cite{Goodson_2004}, the singularity structure from molecules stretched from the equilibrium geometry is difficult because there is more than one significant singularity.
+This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.} To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
 In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
@@
 More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT \cite{Stransky_2018}.
-\titou{In particular, they showed that when the dimensionality of the system increases, first- and second-order QTP behave differently, and the position of these singularities converge towards the real axis at different rates (exponentially and algebraically for the first and second order, respectively).}
+\antoine{In the thermodynamic limit some of the EPs converge towards a critical point $\lambda$\textsuperscript{c} on the real axis.
+They showed that within the LMG model \cite{Lipkin_1965} (which can be for example interacting fermions on two-energy levels or two interacting bosonic species) EPs associated to first- and second-order QPT behave differently when the number of particles increases.
+The position of these singularities converge towards the critical point and the real axis at different rates (exponentially and algebraically for the first and second order, respectively).}
 
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.
-Indeed, the second derivative of the energy is discontinuous at the \titou{Coulson-Fischer point (not defined)} which means that the system undergo a second-order QPT.
-Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+\antoine{Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.} Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
 The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly.
@@
 
-Simple systems that are analytically solvable (or at least quasi-exactly solvable \titou{(please define)}) are of great importance in theoretical chemistry. 
+Simple systems that are analytically solvable (or at least quasi-exactly solvable \antoine{i.e.
+model for which it is possible to obtain a finite portion of the exact solutions of the Schrödinger equation \eqref{eq:SchrEq} \cite{Ushveridze_1994}}) are of great importance in theoretical chemistry.
 These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
 To investigate the physics of EPs we consider one such system named \textit{spherium}. 
-It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. 
+It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential \cite{Thompson_2005, Seidl_2007, Loos_2009b}. 
 Thus, the Hamiltonian is
@@
 Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
-The radius of the sphere $R$ dictates the correlation regime. 
+The radius of the sphere $R$ dictates the correlation regime \cite{Loos_2009}. 
 In the weak correlation regime (i.e., small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
 For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
-This phenomenon is sometimes referred to as a Wigner crystallization.
+This phenomenon is sometimes referred to as a Wigner crystallization \cite{Wigner_1934}.
 \titou{T2: Missing references in this part.}
@@
 \end{gather}
-and
+\antoine{and $v^\sigma_{\ell_1,\ell_2,L}$ is expressed in terms of the Wigner 3j-symbols \cite{AngularBook}}
 \begin{equation}
@@
 \end{equation}
-\titou{T2: please define Wigner 3j symbols.}
+\titou{STOPPED HERE.}
 
@@
 The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis, composed  of a $Y_{00}$ and a $Y_{10}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
+We will work in a minimal basis, composed  of a $Y_{0}$ and a $Y_{1}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions.
@@
 \begin{equation}
-\phi_\alpha(\theta_1)= \cos(\chi_\alpha)\frac{Y_{00}(\theta_1)}{R} + \sin(\chi_\alpha)\frac{Y_{10}(\theta_1)}{R}
+\phi_\sigma(\theta_i)= \cos(\chi_\sigma)\frac{Y_{0}(\theta_i)}{R} + \sin(\chi_\sigma)\frac{Y_{1}(\theta_i)}{R}
 \end{equation}

### 2020-07-30 RapportStage/Rapport.tex
minor corrections

@@
 In this basis there is a shortcut to find the stationary solutions.
-One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
+One can define the one-electron wave functions $\phi_\sigma(\theta_i)$ using a mixing angle between the two basis functions.
 Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
@@
 \begin{equation}
-\phi_\sigma(\theta_i)= \cos(\chi_\sigma)\frac{Y_{0}(\theta_i)}{R} + \sin(\chi_\sigma)\frac{Y_{1}(\theta_i)}{R}
+\phi_\sigma(\theta_i)= \cos(\chi_\sigma)Y_{0}(\theta_i) + \sin(\chi_\sigma)Y_{1}(\theta_i)
 \end{equation}
@@
 \item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$.
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$.
 \end{itemize}
@@
 \begin{align}\label{eq:rhfbasis}
- \psi_1 & =Y_{00}(\theta_1)Y_{00}(\theta_2),
+ \psi_1 & =Y_{0}(\theta_1)Y_{0}(\theta_2),
  & 
- \psi_2 & =Y_{00}(\theta_1)Y_{10}(\theta_2),\\
- \psi_3 & =Y_{10}(\theta_1)Y_{00}(\theta_2),
+ \psi_2 & =Y_{0}(\theta_1)Y_{1}(\theta_2),\\
+ \psi_3 & =Y_{1}(\theta_1)Y_{0}(\theta_2),
  & 
- \psi_4 & =Y_{10}(\theta_1)Y_{10}(\theta_2).
+ \psi_4 & =Y_{1}(\theta_1)Y_{1}(\theta_2).
 \end{align}
@@
 \begin{equation}
-\Phi_l(\theta)=\frac{\sqrt{2l+1}}{4\pi R^2}P_l(\cos\theta)
-\end{equation}
-where $P_l$ are the Legendre polynomial and $\theta$ is the interelectronic angle.
+\Phi_l(\omega)=\frac{\sqrt{2l+1}}{4\pi R^2}P_l(\cos\omega)
+\end{equation}
+where $P_l$ are the Legendre polynomial and $\omega$ is the interelectronic angle.
 
@@
 Whereas the MP reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
-Moreover it can be proved that the $n$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$n$ respective to $R$.
+Moreover it can be proved that the $l$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$l$ respective to $R$.
 It seems that the EN partitioning is better than the MP one for very small R in the minimal basis.
-In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2
-$ (and in larger basis set) the MP series has a greater radius of convergence for all value of $R$.
+In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2$ (and in larger basis set) the MP series has a greater radius of convergence for all value of $R$.
 
@@
 \hline
-MP & 14.1-10.9i & 2.38-1.47i & -0.67-1.30i & -0.49-0.89i & -0.33-0.55i & -0.22-0.31i & 0.03-0.05i \\
-WC & -9.6-10.7i & -0.96-1.07i & -0.48-0.53i & -0.32-0.36 & -0.19-0.21i & -0.10-0.11i & -0.01-0.01i \\
+MP & 14.1-10.9\,i & 2.38-1.47\,i & -0.67-1.30\,i & -0.49-0.89\,i & -0.33-0.55\,i & -0.22-0.31\,i & 0.03-0.05\,i \\
+WC & -9.6-10.7\,i & -0.96-1.07\,i & -0.48-0.53\,i & -0.32-0.36\,i & -0.19-0.21\,i & -0.10-0.11\,i & -0.01-0.01\,i \\
 \hline
@@
 In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
-For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014i$.
-And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023i$.
+For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
+And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
 However in the spherium the electrons can't be ionized so those singularities are not the $\beta$ singularities highlighted by Sergeev and Goodson \cite{Sergeev_2005}.

### 2020-07-30 RapportStage/Rapport.tex

--- 2020-07-30 RapportStage/Rapport.tex
@@
 \end{quote}
-\antoine{They proved that using different extrapolation formulas of the first terms of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
-The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the system it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
-%>>>>>>> 4aba1a6e837a50f3a21d610948564733096cf38e
+As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, i.e., estimating the limit of the series with only few terms. 
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
 
@@
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-\titou{According to Goodson \cite{Goodson_2004}, the singularity structure from molecules stretched from the equilibrium geometry is difficult, this is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.} To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+According to Goodson \cite{Goodson_2004}, the singularity structure of stretched molecules is difficult because there is more than one significant singularity.
+This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.
+To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
 In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
@@
 More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT \cite{Stransky_2018}.
-\titou{In particular, they showed that when the dimensionality of the system increases, first- and second-order QTP behave differently, and the position of these singularities converge towards the real axis at different rates (exponentially and algebraically for the first and second order, respectively).}
+In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda^\text{c}$ on the real axis.
+They showed that, within the interaction boson model \cite{Lipkin_1965}, EPs associated to first- and second-order QPT behave differently when the number of particles increases.
+The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second order, respectively) with respect to the number of particles.
 
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.
-Indeed, the second derivative of the energy is discontinuous at the \titou{Coulson-Fischer point (not defined)} which means that the system undergo a second-order QPT.
+Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.
 Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
@@
 
-Simple systems that are analytically solvable (or at least quasi-exactly solvable \titou{(please define)}) are of great importance in theoretical chemistry. 
+Simple systems that are analytically solvable (or at least quasi-exactly solvable, i.e., models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
 These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
 To investigate the physics of EPs we consider one such system named \textit{spherium}. 
-It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. 
+It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential \cite{Thompson_2005, Seidl_2007, Loos_2009b}. 
 Thus, the Hamiltonian is
@@
 Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
-The radius of the sphere $R$ dictates the correlation regime. 
+The radius of the sphere $R$ dictates the correlation regime \cite{Loos_2009}. 
 In the weak correlation regime (i.e., small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
 For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
-This phenomenon is sometimes referred to as a Wigner crystallization.
-\titou{T2: Missing references in this part.}
+This phenomenon is sometimes referred to as a Wigner crystallization \cite{Wigner_1934}.
 
@@
 \end{equation}
-\titou{T2: please define Wigner 3j symbols.}
+is expressed in terms of the Wigner 3j-symbols \cite{AngularBook}.
 \titou{STOPPED HERE.}

### 2020-07-30 RapportStage/Rapport.tex
HF part for spherium

@@
 \end{equation}
-It is possible to obtain the formula for the ground state UHF energy in this basis set \cite{Loos_2009}:
-
-\begin{equation}
-E_{\text{UHF}} = T_{\alpha} + T_{\beta} + V
-\label{eq:EUHF}
-\end{equation}
-with
-\begin{gather}
-	T_{\sigma} = \frac{1}{R^2} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1)
-	\\
-	V = \frac{1}{R} \sum_{\ell_1,\ell_2,\ell_3,\ell_4=0}^{\infty} \sum_{L=0}^{\infty} 
-	(-1)^{\ell_3+\ell_4} v^\alpha_{\ell_1,\ell_2,L} v^\beta_{\ell_3,\ell_4,L} 
-\end{gather}
+It is possible to obtain the formula for the HF energy in this basis set \cite{Loos_2009}:
+\begin{equation}
+	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}}
+\label{eq:EHF}
+\end{equation}
+where the kinetic and potential energies are
+\begin{align}
+	T_{\text{HF}} & = \sum_{\sigma=\alpha,\beta} \frac{1}{R^2} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1)
+	&
+	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty} 
+	v^\alpha_{L} v^\beta_{L} 
+\end{align}
 and
 \begin{equation}
-	v^\sigma_{\ell_1,\ell_2,L} 
-	= \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
+	v^\sigma_{L} 
+	=  \sum_{\ell_1,\ell_2} \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
 	\begin{pmatrix}
@@
 is expressed in terms of the Wigner 3j-symbols \cite{AngularBook}.
+
+The general method is to use a self-consistent field procedure as described in Ref.~\cite{SzaboBook} to get the coefficients of the wave functions corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, i.e.,
+\begin{equation}
+	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
+\end{equation}. 
+Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
+In this basis there is a shortcut to find the stationary solutions.
+One can define the one-electron wave functions
+\begin{equation}
+	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta)
+\end{equation}
+using a mixing angle between the two basis functions for each spin manifold. 
+Hence we just minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
 \titou{STOPPED HERE.}
-
-Equation \eqref{eq:EUHF} is obtained from the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy has to be stationary with respect to the coefficients.
-The general method is to use a self-consistent field procedure \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbitals, to illustrate the difference between the RHF and UHF solutions.
-In this basis there is a shortcut to find the stationary solutions.
-One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
-Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
-
-\begin{equation}
-	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta)
-\end{equation}
 

### 2020-07-30 RapportStage/Rapport.tex
HF part for spherium

@@
 Hence we just minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
-\titou{STOPPED HERE.}
-
-The minimization gives the three following solutions valid for all value of $R$:
+
+This process provides the three following solutions valid for all value of $R$, which are respectively a minimum, a maximum and a saddle point of the HF equations:
 \begin{itemize}
 \item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R^{2}$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $1/R^{2} + 1/R$
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
 \end{itemize}
-
-Those solutions are respectively a minimum, a maximum and a saddle point of the HF equations.\\
+\titou{STOPPED HERE.}
 

### 2020-07-30 RapportStage/Rapport.tex
minor corrections

--- 2020-07-30 RapportStage/Rapport.tex
@@
 \newcommand{\hI}{\Hat{I}}
+\newcommand{\hS}{\Hat{S}}
 \newcommand{\bH}{\mathbf{H}}
@@
 \end{quote}
-As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, i.e., estimating the limit of the series with only few terms. 
-Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
-The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+\antoine{As one can only compute the first terms of the MP$l$ series, a smart way to get more accurate results is to use extrapolation formula of this series.
+They proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.} Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
 
@@
 On the contrary $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
-According to Goodson \cite{Goodson_2004}, the singularity structure of stretched molecules is difficult because there is more than one significant singularity.
-This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.
-To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+\antoine{According to Goodson \cite{Goodson_2004}, the singularity structure from molecules stretched from the equilibrium geometry is difficult because there is more than one significant singularity.
+This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.} To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
 In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
@@
 More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT \cite{Stransky_2018}.
-In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda^\text{c}$ on the real axis.
-They showed that, within the interaction boson model \cite{Lipkin_1965}, EPs associated to first- and second-order QPT behave differently when the number of particles increases.
-The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second order, respectively) with respect to the number of particles.
+\antoine{In the thermodynamic limit some of the EPs converge towards a critical point $\lambda$\textsuperscript{c} on the real axis.
+They showed that within the LMG model \cite{Lipkin_1965} (which can be for example interacting fermions on two-energy levels or two interacting bosonic species) EPs associated to first- and second-order QPT behave differently when the number of particles increases.
+The position of these singularities converge towards the critical point and the real axis at different rates (exponentially and algebraically for the first and second order, respectively).}
 
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.
-Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.
-Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+\antoine{Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.} Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
 The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly.
@@
 
-Simple systems that are analytically solvable (or at least quasi-exactly solvable, i.e., models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
+Simple systems that are analytically solvable (or at least quasi-exactly solvable \antoine{i.e.
+model for which it is possible to obtain a finite portion of the exact solutions of the Schrödinger equation \eqref{eq:SchrEq} \cite{Ushveridze_1994}}) are of great importance in theoretical chemistry.
 These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
@@
 This phenomenon is sometimes referred to as a Wigner crystallization \cite{Wigner_1934}.
+\titou{T2: Missing references in this part.}
 
@@
 	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
-	\item Basis set: minimal basis or infinite (i.e., complete) basis made of localized or delocalized basis functions.
+	\item Basis set: minimal basis or infinite (i.e., complete) basis.
 	\item Radius of the sphere that ultimately dictates the correlation regime.
@@
 \end{equation}
-is expressed in terms of the Wigner 3j-symbols \cite{AngularBook}.
 \titou{STOPPED HERE.}
 
-Equation \eqref{eq:EUHF} is obtained from the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy has to be stationary with respect to the coefficients.
-The general method is to use a self-consistent field procedure \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
-We will work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbitals, to illustrate the difference between the RHF and UHF solutions.
+We obtained Eq.~\eqref{eq:EUHF} for the general form of the wave function \eqref{eq:UHF_WF}, but to be associated with a physical wave function the energy needs to be stationary with respect to the coefficients.
+The general method is to use the Hartree-Fock self-consistent field method \cite{SzaboBook} to get the coefficients of the wave functions corresponding to physical solutions.
+We will work in a minimal basis, composed  of a $Y_{0}$ and a $Y_{1}$ spherical harmonic, or equivalently a s and a p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions.
-One can define the one-electron wave functions $\phi(\theta)$ using a mixing angle between the two basis functions.
+One can define the one-electron wave functions $\phi_\sigma(\theta_i)$ using a mixing angle between the two basis functions.
 Hence we just need to minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
@@
 \begin{equation}
-	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta)
-\end{equation}
-
-The minimization gives the three following solutions valid for all value of $R$:
+\phi_\sigma(\theta_i)= \cos(\chi_\sigma)Y_{0}(\theta_i) + \sin(\chi_\sigma)Y_{1}(\theta_i)
+\end{equation}
+
+The minimization gives the three following solutions valid for all value of R:
 \begin{itemize}
-\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R^{2}$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $1/R^{2} + 1/R$
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$
+\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $R^{-2}$.
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2R^{-2}+\frac{29}{25}R^{-1}$.
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $R^{-2} + R^{-1}$.
 \end{itemize}
@@
 The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
-This solution has the energy \eqref{eq:EsbUHF} for $R>3/2$.
+This solution have the energy \eqref{eq:EsbUHF} for $R>3/2$.
 
@@
 The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
-Indeed, the spherical harmonics are eigenvectors of $S^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $S^2$.
-However this solution gives more accurate results for the energy at large $R$ as shown in Table \ref{tab:ERHFvsEUHF}.
+Indeed, the spherical harmonics are eigenvectors of $\hS^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $\hS^2$.
+However this solution gives more accurate results for the energy at large R as shown in Table \ref{tab:ERHFvsEUHF}.
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
@@
 \end{table}
+
+There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
+This solution is associated with another type of symmetry breaking somewhat less known.
+It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
+This solution is called symmetry-broken RHF (sb-RHF).
+At the critical value of R, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
+This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
+
+\begin{equation}
+E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}
+\end{equation}
+
+We can also consider negative values of R.
+This corresponds to the situation where one of the electrons is replaced by a positron.
+There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of R (see Fig.\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
+Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF states maximize the energy because the two attracting particles are on opposite sides of the sphere.
+
+In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
+All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
+The dotted curves corresponds to the holomorphic domain of the energies.
 
@@
 
-There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
-This solution is associated with another type of symmetry breaking somewhat less known.
-It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
-This solution is called symmetry-broken RHF (sb-RHF).
-At the critical value of $R$, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
-This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
-
-\begin{equation}
-E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}
-\end{equation}
-
-We can also consider negative values of $R$.
-This corresponds to the situation where one of the electrons is replaced by a positron.
-There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
-Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF states maximize the energy because the two attracting particles are on opposite sides of the sphere.
-
-In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions \cite{Hiscock_2014, Burton_2019, Burton_2019a}.
-All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
-The dotted curves corresponds to the holomorphic domain of the energies.
-
 \section{Radius of convergence and exceptional points}
@@
 The radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
-Hence, we have to determine the locations of the exceptional points to obtain information on the convergence properties.
+Hence we need to determine the locations of the exceptional points to obtain information on the convergence properties.
 To find them we solve simultaneously Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar}.
@@
 In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix elements $H_{ij}$ for this interaction are given in \eqref{eq:MatrixElem}.
+The matrix elements of the Hamiltonian $H_{ij}$ corresponding to this interaction are given in \eqref{eq:MatrixElem}.
 For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix elements become real.

### 2020-07-30 RapportStage/Rapport.tex

--- 2020-07-30 RapportStage/Rapport.tex
@@
 \item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R^{2}$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
 \end{itemize}
@@
 
-In addition, there is also the well-known symmetry-broken UHF (sb-UHF) solution.
-For $R>3/2$ an other stationary UHF solution appears, this solution is a minimum of the HF equations.
+In addition, the minimization process gives also the well-known symmetry-broken UHF (sb-UHF) solution.
+In this case the Coulson-Fischer point associated to this solution is $R=3/2$.
+For $R>3/2$ the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
 This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the configuration the other way round.
@@
 
-The exact solution for the ground state is a singlet so this wave function does not have the true symmetry.
-Indeed, the spherical harmonics are eigenvectors of $S^2$ but the symmetry-broken solution is a linear combination of the two eigenvectors and is not an eigenvector of $S^2$.
-However this solution gives more accurate results for the energy at large $R$ as shown in Table \ref{tab:ERHFvsEUHF}.
+The exact solution for the ground state is a singlet.
+The spherical harmonics are eigenvectors of $\hS^2$ and they are associated to differents eigenvalue.
+Yet, the symmetry-broken orbitals are linear combination of $Y_0$ and $Y_1$.
+Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$.
+However this solution gives more accurate results for the energy at large R than the RHF one as shown in Table \ref{tab:ERHFvsEUHF} even if it does not have the exact spin symmetry.
 In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
@@
 At the critical value of $R$, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
-This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the electrons on each side \cite{GiulianiBook}.
+This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side \cite{GiulianiBook}.
 
@@
 This corresponds to the situation where one of the electrons is replaced by a positron.
-There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj} but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
-Indeed, the sb-RHF states minimize the energy by placing the electron and the positron on the same side of the sphere.
+There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
+Indeed, the sb-RHF states minimize the attraction energy by placing the electron and the positron on the same side of the sphere.
 And the sb-UHF states maximize the energy because the two attracting particles are on opposite sides of the sphere.
@@
 To find them we solve simultaneously Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar}.
-Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system where $\hI$ is the identity operator.
+Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system.
 If an energy is also solution of Eq.~\eqref{eq:DPolChar} then this energy is degenerate.
 In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
-These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ or exceptional points between two states with the same symmetry for complex value of $\lambda$.
+These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or exceptional points between two states with the same symmetry for complex value of $\lambda$.
 
@@
 \end{subequations}
+with $\hI$ the identity operator.
 
@@
 The Hamiltonian $\hH(\lambda)$ is block diagonal because of the symmetry of the basis set, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
-The two singly excited states give a singlet sp\textsubscript{z} and a triplet sp\textsubscript{z} state but their symmetry is not the same as the ground state.
+The two singly excited states yields after diagonalization a spatially anti-symmetric singlet sp\textsubscript{z} and a spatially symmetric triplet sp\textsubscript{z} state.
+Hence those states do not have the same symmetry as the spatially symmetric singlet ground state.
 Thus these states can not be involved in an avoided crossing with the ground state as it can be seen in Fig.~\ref{fig:RHFMiniBas} and a fortiori can not be involved in an exceptional point with the ground state.
@@
 To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
-It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties, i.e., the exceptional points between states with the same symmetry.
+It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties, i.e., the exceptional points between states with the same symmetry as the ground state.
 In this case the ground state is a totally symmetric singlet.
@@
 Table \ref{tab:SingAlpha} proves that the singularities considered in this case are $\alpha$ singularities.
-This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities.
+This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities which said that $\alpha$ singularities are relatively insensitive to change of the basis set.
 The discontinuities observed in Fig.~\ref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
@@
 Now we will investigate the differences in the singularity structure between the RHF and UHF formalism.
-To do this we use the symmetry-broken orbitals obtained in Sec.~\ref{sec:spherium}.
+To do this we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
 Thus the UHF two-electron basis is:
@@
 In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix elements $H_{ij}$ for this interaction are given in \eqref{eq:MatrixElem}.
-For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for R>3/2 the matrix elements become real.
+The matrix elements $H_{ij}$ of the Hamiltonian corresponding to this interaction are given in \eqref{eq:MatrixElem}.
+For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
@@
 The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We can not use configuration state function in this case.
+We can not use configuration state functions in this case.
 So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
@@
 And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
-However in the spherium the electrons can't be ionized so those singularities are not the $\beta$ singularities highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
-We can see in Fig.~\ref{fig:UHFEP} that the degeneracy between the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet at $R=3/2$.
-For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are moved in the complex plane.
-The wave function is spin contaminated for $R>3/2$ this why the s\textsuperscript{2} singlet energy can not cross the sp\textsubscript{z} triplet curves anymore.
+However, in the spherium the electrons can't be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
+We can see in Fig.~\ref{fig:UHFEP} that the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet states are degenerated for $R=3/2$.
+For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are $moved$ in the complex plane.
+The wave function is spin contaminated by $Y_1$ for $R>3/2$ this why the s\textsuperscript{2} singlet energy can not cross the sp\textsubscript{z} triplet curves anymore.
 When $R$ increases this avoided crossing becomes sharper.
@@
 The parameter domain of value where the energy becomes complex is called the broken \pt symmetry  region.
-This is consistent with the fact that in the holomorphic domain the Hamiltonian break the \pt -symmetry.
+This is consistent with the fact that in the holomorphic domain the Hamiltonian is no more \pt -symmetric.
 

### 2020-07-30 RapportStage/Rapport.tex
minor corrections

@@
 For $R>3/2$ the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
-This solution corresponds to the configuration with the electron $\alpha$ on one side of the sphere and the electron $\beta$ on the opposite side and the configuration the other way round.
+This solution corresponds to the configuration with the electron $\alpha$ in an orbital on one side of the sphere and the electron $\beta$ in a symmetric orbital on the opposite side and the configuration the other way round.
 The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
@@
 This solution is called symmetry-broken RHF (sb-RHF).
-At the critical value of $R$, the repulsion of the two electrons on the same side of the sphere maximizes more the energy than the kinetic energy of the p\textsubscript{z} orbitals.
-This symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side \cite{GiulianiBook}.
+At the critical value of $R$, the repulsion of the two electrons being in the same orbital on the same side of the sphere maximizes more the energy than the kinetic energy of the two electrons in the p\textsubscript{z} orbital.
+This configuration break the spatial symmetry of charge.
+Hence this symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side \cite{GiulianiBook}.
 
@@
 We can also consider negative values of $R$.
-This corresponds to the situation where one of the electrons is replaced by a positron.
-There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum.
-Indeed, the sb-RHF states minimize the attraction energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF states maximize the energy because the two attracting particles are on opposite sides of the sphere.
+This corresponds to the situation where one of the electrons is replaced by a positron (the anti-particle of the electron).
+There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
+Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF state maximizes the energy because the two attracting particles are on opposite sides of the sphere.
 

### 2020-07-31 RapportStage/Rapport.tex
done with Sec 4

@@
 or
-\begin{equation}
+\begin{equation} \label{eq:H-sph-omega}
 	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
@@
 \begin{equation}\label{eq:RHF_WF}
-	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2)
+	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
 \end{equation}
 where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
+Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
 
 The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
-In the UHF formalism there is a critical value of $R$, called Coulson-Fischer point \cite{Coulson_1949}, at which a UHF solution appears and is lower in energy than the RHF one.
-The UHF solution has broken symmetry as the two electrons tends to localize on opposite sides of the sphere. 
+Within the UHF formalism, there is a critical value of $R$, called Coulson-Fischer point \cite{Coulson_1949}, at which a UHF solution appears and is lower in energy than the RHF one.
+The UHF solution has broken symmetry because the two electrons tends to localize on opposite sides of the sphere. 
 The spatial part of the UHF wave function is defined as
 \begin{equation}\label{eq:UHF_WF}
-	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2)
+	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2),
 \end{equation}
@@
 \begin{equation}
-	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}}
+	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}},
 \label{eq:EHF}
 \end{equation}
-where the kinetic and potential energies are
+where the kinetic and potential energies are, respectively,
 \begin{align}
-	T_{\text{HF}} & = \sum_{\sigma=\alpha,\beta} \frac{1}{R^2} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1)
+	T_{\text{HF}} & = \frac{1}{R^2} \sum_{\sigma=\alpha,\beta} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1),
 	&
 	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty}
-	v^\alpha_{L} v^\beta_{L} 
+	v^\alpha_{L} v^\beta_{L},
 \end{align}
@@
 
-The general method is to use a self-consistent field procedure as described in Ref.~\cite{SzaboBook} to get the coefficients of the wave functions corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, i.e.,
+The general method is to use a self-consistent field procedure as described in Ref.~\cite{SzaboBook} to get the coefficients of the HF wave function corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, i.e.,
 \begin{equation}
 	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
-\end{equation}. 
+\end{equation}
 Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
-In this basis there is a shortcut to find the stationary solutions.
-One can define the one-electron wave functions
-\begin{equation}
-	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta)
+In this basis there is a shortcut to find the stationary solutions and ensure normalization of the orbitals.
+One can define the one-electron orbitals as
+\begin{equation}
+	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta),
 \end{equation}
 using a mixing angle between the two basis functions for each spin manifold. 
-Hence we just minimize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
+Hence, one has just to minimize/maximize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
 
@@
 \begin{itemize}
-\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R^{2}$.
+\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R$.
 \item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
@@
 \end{itemize}
-\titou{STOPPED HERE.}
 
@@
 For $R>3/2$ the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
-This solution corresponds to the configuration with the electron $\alpha$ in an orbital on one side of the sphere and the electron $\beta$ in a symmetric orbital on the opposite side and the configuration the other way round.
+This solution corresponds to the configuration with the spin-up electron in an orbital on one side of the sphere and the spin-down electron in a miror-image orbital on the opposite side and the configuration the other way round.
 The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
-This solution has the energy \eqref{eq:EsbUHF} for $R>3/2$.
-
+For $R>3/2$, this solution has the energy
 \begin{equation}\label{eq:EsbUHF}
-	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}
+	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}.
 \end{equation}
@@
 The exact solution for the ground state is a singlet.
-The spherical harmonics are eigenvectors of $\hS^2$ and they are associated to differents eigenvalue.
-Yet, the symmetry-broken orbitals are linear combination of $Y_0$ and $Y_1$.
+The spherical harmonics are eigenvectors of $\hS^2$ (the spin operator) and they are associated to different eigenvalues.
+Yet, the symmetry-broken orbitals are linear combinations of $Y_0$ and $Y_1$.
 Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$.
-However this solution gives more accurate results for the energy at large R than the RHF one as shown in Table \ref{tab:ERHFvsEUHF} even if it does not have the exact spin symmetry.
-In fact at the Coulson-Fischer point, it becomes more efficient to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
-Thus the wave function break the spin symmetry because it allows a more efficient minimization of the Coulomb repulsion.
+However, this solution gives lower energies than the RHF one at large $R$ as shown in Table \ref{tab:ERHFvsEUHF} even if it does not have the exact spin symmetry.
+In fact, at the Coulson-Fischer point, it becomes more effective to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
+Thus, within the HF approximation, the variational principle is allowed to break the spin symmetry because it yields a more effective minimization of the Coulomb repulsion.
 This type of symmetry breaking is called a spin density wave because the system oscillates between the two symmetry-broken configurations \cite{GiulianiBook}.
@@
 \centering
-\caption{\centering RHF and UHF energies in the minimal basis and exact energies for various $R$.}
+\caption{RHF and sb-UHF energies in the minimal basis and exact energies (in the complete basis) for various $R$.}
 \begin{tabular}{ccccccccc}
@@
 This solution is called symmetry-broken RHF (sb-RHF).
-At the critical value of $R$, the repulsion of the two electrons being in the same orbital on the same side of the sphere maximizes more the energy than the kinetic energy of the two electrons in the p\textsubscript{z} orbital.
-This configuration break the spatial symmetry of charge.
+\titou{At a critical value of $R$, placing two electrons in the same orbital on the same side of the sphere increases the repulsion energy more than the kinetic energy of the two electrons in the p\textsubscript{z} orbital.} This configuration breaks the spatial symmetry of charge.
 Hence this symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side \cite{GiulianiBook}.
-
-\begin{equation}
-E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}
-\end{equation}
-
-We can also consider negative values of $R$.
-This corresponds to the situation where one of the electrons is replaced by a positron (the anti-particle of the electron).
-There are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
+The energy associated with this sb-RHF solution reads
+\begin{equation}
+E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}.
+\end{equation}
+
+We can also consider negative values of $R$, which corresponds to the situation where one of the electrons is replaced by a positron (the anti-particle of the electron) as readily seen in Eq.~\eqref{eq:H-sph-omega}.
+For negative $R$ values, there are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
 Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere.

### 2020-07-31 RapportStage/Rapport.tex
modification sec 4

@@
 This solution is called symmetry-broken RHF (sb-RHF).
-\titou{At a critical value of $R$, placing two electrons in the same orbital on the same side of the sphere increases the repulsion energy more than the kinetic energy of the two electrons in the p\textsubscript{z} orbital.} This configuration breaks the spatial symmetry of charge.
+\antoine{The reasoning is counter-intuitive because the electrons tends to maximize their energy.
+If the orbitals are symmetric, the maximum is when the two electrons are in the p\textsubscript{z} orbital because it maximizes the kinetic energy.
+At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital i.e., on the same side of the sphere gives a superior energy than the p\textsubscript{z}\textsuperscript{2} state.
+This is because it becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$.}
+This configuration breaks the spatial symmetry of charge.
 Hence this symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side \cite{GiulianiBook}.

### 2020-07-31 RapportStage/Rapport.tex
5.1 done

--- 2020-07-31 RapportStage/Rapport.tex
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}{R}{0.5\textwidth}
     \centering
@@
 Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016}. 
-They are the non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996}.
-CIs are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
-In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to CIs in the decay of bound excited states.
+They are the non-Hermitian analogs of conical intersections \cite{Yarkony_1996}.
+Conical intersections are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
+In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states.
 Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
@@
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
-In contrast, encircling Hermitian degeneracies at CIs only introduces a geometric phase while leaving the states unchanged.
-More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state \cite{MoiseyevBook}.
+In contrast, encircling Hermitian degeneracies at conical intersections only introduces a geometric phase while leaving the states unchanged.
+More dramatically, whilst eigenvectors remain orthogonal at conical intersections, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state \cite{MoiseyevBook}.
 More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane \cite{Olsen_1996, Olsen_2000}.
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{wrapfigure}{R}{0.4\textwidth}
     \centering
@@
 
-In this part, we will try to investigate how some parameters of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
-The radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
-Hence, we have to determine the locations of the exceptional points to obtain information on the convergence properties.
-To find them we solve simultaneously Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar}.
+In this subsection, we investigate how \titou{parameters} of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
+Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
+Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
+To find them we solve simultaneously the following equations:
+\begin{subequations}
+\begin{align}
+	\label{eq:PolChar}
+	\det[E\hI-\hH(\lambda)] & = 0,
+	\\ 
+	\label{eq:DPolChar}
+	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
+\end{align}
+\end{subequations}
+where $\hI$ is the identity operator.
 Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system.
@@
 In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
-These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or exceptional points between two states with the same symmetry for complex value of $\lambda$.
-
-\begin{subequations}
-\begin{align}
-	\label{eq:PolChar}
-	\text{det}[E\hI-\hH(\lambda)] & = 0,
-	\\ 
-	\label{eq:DPolChar}
-	\pdv{E}\text{det}[E\hI-\hH(\lambda)] & = 0.
-\end{align}
-\end{subequations}
-with $\hI$ the identity operator.
-
-The electron 1 have a spin $\alpha$ and the electron 2 a spin $\beta$.
-Hence we can forget the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
-In the restricted formalism the spatial orbitals are the same so the two-electron basis set is defined as:
+These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
+
+Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
+Hence, we can forget the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set can be defined as
 
@@
 \end{align}
-
-The Hamiltonian $\hH(\lambda)$ is block diagonal because of the symmetry of the basis set, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
-The two singly excited states yields after diagonalization a spatially anti-symmetric singlet sp\textsubscript{z} and a spatially symmetric triplet sp\textsubscript{z} state.
+The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
+The two singly-excited states yield after diagonalization a spatially anti-symmetric singlet sp\textsubscript{z} and a spatially symmetric triplet sp\textsubscript{z} state.
 Hence those states do not have the same symmetry as the spatially symmetric singlet ground state.
-Thus these states can not be involved in an avoided crossing with the ground state as it can be seen in Fig.~\ref{fig:RHFMiniBas} and a fortiori can not be involved in an exceptional point with the ground state.
-However there is an avoided crossing between the s\textsuperscript{2} state and the p\textsubscript{z}\textsuperscript{2} one which gives two exceptional points in the complex plane.
-
-\begin{wrapfigure}{c}{0.5\textwidth}
+Thus these states can not be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
+However there is an avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states which gives two EPs in the complex plane.
+
+\begin{wrapfigure}{R}{0.5\textwidth}
     \centering
@@
 
-To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called Configuration State Function (CSF).
-It simplifies the problem because with such a basis set we only get the degeneracies of interest for the convergence properties, i.e., the exceptional points between states with the same symmetry as the ground state.
+To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called configuration state functions (CSFs).
+It simplifies the problem because with such a basis set, one only gets the degeneracies of interest for the convergence properties, i.e., the EPs between states with the same symmetry as the ground state.
 In this case the ground state is a totally symmetric singlet.
-According to the angular-momentum theory \cite{AngularBook, SlaterBook, Loos_2009} we expand the exact wave function in the following two-electron basis:
-\begin{equation}
-\Phi_l(\omega)=\frac{\sqrt{2l+1}}{4\pi R^2}P_l(\cos\omega)
-\end{equation}
-where $P_l$ are the Legendre polynomial and $\omega$ is the interelectronic angle.
-
-Then using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
-Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ in function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis, i.e., $P_0$ and $P_1$ and in the same basis augmented with $P_2$.
-We see that the radius of convergence of the SC partitioning is growing with R whereas it is decreasing for the three others partitioning.
+According to the angular momentum theory \cite{AngularBook, SlaterBook, Loos_2009}, we expand the exact wave function in the following two-electron basis:
+\begin{equation}
+\Phi_\ell(\omega)=\frac{\sqrt{2\ell+1}}{4\pi R^2}P_\ell(\cos\omega),
+\end{equation}
+where $P_\ell$ are the Legendre polynomial and $\omega$ is the interelectronic angle.
+
+Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
+Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (i.e., $P_0$ and $P_1$) and in the same basis augmented with $P_2$.
+We see that $R_{\text{CV}}$ for the SC partitioning increases with $R$ whereas it is decreasing for the three others partitioning.
 This result was expected because the three decreasing partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
-On the contrary, the strong coupling one uses a strongly correlated reference so this series converge better when the electron are strongly correlated, i.e., when $R$ is large for the spherium model.
-The MP partitioning is always better than the weak correlation in Fig.~\ref{fig:RadiusPartitioning}.
+On the contrary, the strong coupling one uses a strongly correlated reference so the SC series converges better when the electron are strongly correlated, i.e., when $R$ is large in the spherium model.
+The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
 In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
-Whereas the MP reference is proportionnal to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
-Moreover it can be proved that the $l$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$l$ respective to $R$.
-It seems that the EN partitioning is better than the MP one for very small R in the minimal basis.
-In fact, it is just an artifact of the minimal basis because in the minimal basis augmented with $P_2$ (and in larger basis set) the MP series has a greater radius of convergence for all value of $R$.
+Whereas the MP reference is proportional to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
+Moreover it can be proved that the $m$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$m$ respective to $R$.
+It seems that the EN partitioning is better than the MP one for very small $R$ in the minimal basis.
+In fact, it is just an artefact of the minimal basis because in the minimal basis augmented with $P_2$ (and in larger basis set) the MP series has a greater radius of convergence for all values of $R$.
 
@@
     \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
-    \caption{\centering Radius of convergence in the minimal basis (left) and in the minimal basis augmented with $P_2$ (right) for different partitioning of the Hamiltonian $\hH(\lambda)$.}
+    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
     \label{fig:RadiusPartitioning}
@@
 
-Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the expansion of the basis set.
-The CSF basis function have all the same spin and spatial symmetry so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
-Table \ref{tab:SingAlpha} proves that the singularities considered in this case are $\alpha$ singularities.
-This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} on $\alpha$ singularities which said that $\alpha$ singularities are relatively insensitive to change of the basis set.
-The discontinuities observed in Fig.~\ref{fig:RadiusBasis} with the MP partitioning are due to a change of the dominant singularity.
+Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the size of the basis set.
+The CSFs have all the same spin and spatial symmetries so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
+Table \ref{tab:SingAlpha} shows that the singularities considered in this case are indeed $\alpha$ singularities.
+This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} who stated that $\alpha$ singularities are relatively insensitive to the basis set size.
+The discontinuities observed in Fig.~\ref{fig:RadiusBasis} for the MP partitioning are due to changes in dominant singularity.
 We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative plane.
@@
     \includegraphics[width=0.45\textwidth]{WCElargebasis.pdf}
-    \caption{\centering Radius of convergence in the CSF basis with $K$ basis function for the MP partitioning (left) and the WC partitioning (right).}
+    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
     \label{fig:RadiusBasis}
@@
 \centering
-\caption{\centering Dominant singularity in the CSF basis set ($K=8$) for various value of R. The first line is the value for the MP partitioning and the second for the WC one.}
+\footnotesize
+\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
 \begin{tabular}{cccccccc}
@@
 \hline
-MP & 14.1-10.9\,i & 2.38-1.47\,i & -0.67-1.30\,i & -0.49-0.89\,i & -0.33-0.55\,i & -0.22-0.31\,i & 0.03-0.05\,i \\
-WC & -9.6-10.7\,i & -0.96-1.07\,i & -0.48-0.53\,i & -0.32-0.36\,i & -0.19-0.21\,i & -0.10-0.11\,i & -0.01-0.01\,i \\
+MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
+WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
 \hline
@@
 
-Now we will investigate the differences in the singularity structure between the RHF and UHF formalism.
-To do this we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
-Thus the UHF two-electron basis is:
+Now, we investigate the differences in the singularity structure between the RHF and UHF formalism.
+To do so, we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
+Thus, the UHF two-electron basis is
 \begin{align}\label{eq:uhfbasis}
@@
 with the symmetry-broken orbitals
-\begin{align*}\label{eq:uhforbitals}
- \phi_{\alpha,1}(\theta) & =\frac{\sqrt{75+62R}Y_{00}(\theta)+5\sqrt{-3+2R}Y_{10}(\theta)}{4\sqrt{7R}},
- & 
- \phi_{\beta,1}(\theta) & =\frac{\sqrt{75+62R}Y_{00}(\theta)-5\sqrt{-3+2R}Y_{10}(\theta)}{4\sqrt{7R}},\\
- \phi_{\alpha,2}(\theta) & =\frac{-5\sqrt{-3+2R}Y_{00}(\theta)+\sqrt{75+62R}Y_{10}(\theta)}{4\sqrt{7R}},
- & 
- \phi_{\beta,2}(\theta) & =\frac{5\sqrt{-3+2R}Y_{00}(\theta)+\sqrt{75+62R}Y_{10}(\theta)}{4\sqrt{7R}}.
-\end{align*}
+\begin{subequations}
+\begin{align}\label{eq:uhforbitals}
+ \phi_{\alpha,1}(\theta) & =\frac{\sqrt{75+62R}Y_{0}(\theta)+5\sqrt{-3+2R}Y_{1}(\theta)}{4\sqrt{7R}},
+ \\ 
+ \phi_{\beta,1}(\theta) & =\frac{\sqrt{75+62R}Y_{0}(\theta)-5\sqrt{-3+2R}Y_{1}(\theta)}{4\sqrt{7R}},
+ \\
+ \phi_{\alpha,2}(\theta) & =\frac{-5\sqrt{-3+2R}Y_{0}(\theta)+\sqrt{75+62R}Y_{1}(\theta)}{4\sqrt{7R}},
+ \\
+ \phi_{\beta,2}(\theta) & =\frac{5\sqrt{-3+2R}Y_{0}(\theta)+\sqrt{75+62R}Y_{1}(\theta)}{4\sqrt{7R}}.
+\end{align}
+\end{subequations}
 
 In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix elements $H_{ij}$ of the Hamiltonian corresponding to this interaction are given in \eqref{eq:MatrixElem}.
-For $R=3/2$ the Hamitonian is block diagonal and this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
+The matrix elements of the Hamiltonian corresponding to this interaction are
+\begin{equation}\label{eq:MatrixElem}
+H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{-3+2R}\sqrt{75+62R}\frac{25+2R}{280R^3}
+\end{equation}
+For $R=3/2$ the Hamiltonian is block diagonal and this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
@@
 The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
-We will refer to the domain where the matrix element are complex as the holomorphic domain.
-
-\begin{equation}\label{eq:MatrixElem}
-H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{-3+2R}\sqrt{75+62R}\frac{25+2R}{280R^3}
-\end{equation}
+We will refer to the domain where the matrix elements are complex as the holomorphic domain.
+
+\begin{wrapfigure}{R}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
+    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
+    \label{fig:UHFMiniBas}
+\end{wrapfigure}
 
 The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We can not use configuration state functions in this case.
+We can not use CSFs in this case.
 So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
@@
 Those avoided crossings are due to the spin contamination of the wave function.
-The exceptional points resulting from those avoided crossings will be discussed in Sec.~\ref{sec:uhfSing}.
-\\
-
-\begin{wrapfigure}{c}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
-    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
-    \label{fig:UHFMiniBas}
-\end{wrapfigure}
-
-In this study we have used spherical harmonics (or combination of spherical harmonics) as basis function which are diffuse wave functions.
-It would also be interesting to investigate the use of localized basis function \cite{Seidl_2018} (for example gaussians) because those functions would be more adapted to describe the correlated regime.
-\\
+The EPs resulting from those avoided crossings will be discussed in Sec.~\ref{sec:uhfSing}.
+
+In this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
 
@@
     \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
-    \caption{\centering Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
+    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
     \label{fig:UHFEP}
@@
 
-For a non-Hermitian Hamiltonian the exceptional points can lie on the real axis.
-In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate resulting in such an exceptional point on the real axis.
+For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
+In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
 This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.

### 2020-07-31 RapportStage/Rapport.tex
get rid of wrapfig

@@
 
-\begin{wrapfigure}{R}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{TopologyEP.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{TopologyEP.pdf}
     \caption{A generic EP with the square-root branch point topology. A loop around the EP interconvert the states.}
     \label{fig:TopologyEP}
-\end{wrapfigure}
+\end{figure}
 By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
@@
 
-\begin{figure}[h!]
+\begin{figure}
     \centering
@@
 
-\begin{table}[h!]
+\begin{table}
     \centering
@@
 
-\begin{table}[h!]
+\begin{table}
 \centering
@@
 
-\begin{wrapfigure}{R}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{EsbHF.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{EsbHF.pdf}
     \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
     \label{fig:SpheriumNrj}
-\end{wrapfigure}
+\end{figure}
 
@@
 
-In this subsection, we investigate how \titou{parameters} of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
+In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
 Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
@@
 
-\begin{wrapfigure}{R}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{EMP_RHF_R10.pdf}
     \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
     \label{fig:RHFMiniBas}
-\end{wrapfigure}
+\end{figure}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{PartitioningRCV2.pdf}
-    \includegraphics[width=0.45\textwidth]{PartitioningRCV3.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
     \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{MPlargebasis.pdf}
-    \includegraphics[width=0.45\textwidth]{WCElargebasis.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
+    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
     \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
@@
 
-\begin{wrapfigure}{R}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{EMP_UHF_R10.pdf}
     \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
     \label{fig:UHFMiniBas}
-\end{wrapfigure}
+\end{figure}
 

### 2020-07-31 RapportStage/Rapport.tex
done with 1st iteration

@@
 
-In this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
-It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
+\titou{In this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.}
+\titou{T2: Please move to concluding section.}
 
@@
 
-In the RHF case there are only $\alpha$ singularities and large avoided crossings but we can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
+\titou{T2: please modify structure of this section.}
+Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
 For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
 And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
-However, in the spherium the electrons can't be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
+However, in spherium, the electrons cannot be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson \cite{Sergeev_2005}.
 We can see in Fig.~\ref{fig:UHFEP} that the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet states are degenerated for $R=3/2$.
 For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are $moved$ in the complex plane.
-The wave function is spin contaminated by $Y_1$ for $R>3/2$ this why the s\textsuperscript{2} singlet energy can not cross the sp\textsubscript{z} triplet curves anymore.
+The wave function is spin contaminated by $Y_1$ for $R>3/2$ this is why the s\textsuperscript{2} singlet energy cannot cross the sp\textsubscript{z} triplet curves anymore.
 When $R$ increases this avoided crossing becomes sharper.
@@
 As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
-Therefore the Hamiltonian becomes non-Hermitian for those value of $R$.
-In \cite{Burton_2019a} Burton \textit{et al.}~proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
+Therefore the Hamiltonian becomes non-Hermitian for these values of $R$.
+In Ref.~\cite{Burton_2019a}, Burton \textit{et al.}~proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
 An analog reasoning can be done with the spherium model to prove the same result.
-The \pt -symmetry (invariance with respect to combined space reflection $\mathcal{P}$ and time reversal $\mathcal{T}$) is a property which ensures that a non-Hermitian Hamiltonian has a real energy spectrum.
-Thus \pt -symmetric Hamiltonian can be seen as an intermediate between Hermitian and non-Hermitian.
-
-Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when R is in the holomorphic domain.
-The parameter domain of value where the energy becomes complex is called the broken \pt symmetry  region.
+The \pt -symmetry (invariance with respect to combined space reflection $\mathcal{P}$ and time reversal $\mathcal{T}$) is a property which ensures that a non-Hermitian Hamiltonian has a real energy spectrum \cite{BenderBook}.
+Thus \pt -symmetric Hamiltonians can be seen as an intermediate class between Hermitian and non-Hermitian Hamiltonians.
+
+Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when $R$ is in the holomorphic domain.
+The domain of values where the energy becomes complex is called the broken \pt-symmetry region.
 This is consistent with the fact that in the holomorphic domain the Hamiltonian is no more \pt -symmetric.
@@
 For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
-In particular, at the point of PT transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
+In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
 This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.

### 2020-07-31 RapportStage/Rapport.tex
more corrections in 5.1

@@
 Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
-To find them we solve simultaneously the following equations:
+To find them we solve simultaneously the following equations \titou{REFS}:
 \begin{subequations}
@@
 where $\hI$ is the identity operator.
-Equation \eqref{eq:PolChar} is the well-known secular equation giving the energies of the system.
-If an energy is also solution of Eq.~\eqref{eq:DPolChar} then this energy is degenerate.
-In this case the energies obtained are dependent of $\lambda$ so solving those equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
-These degeneracies can be conical intersections between two states with different symmetry for real value of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
+Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system.
+If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy is, at least two-fold degenerate.
+In this case the energies obtained are dependent of $\lambda$.
+Thus, solving these equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
+These degeneracies can be conical intersections between two states with different symmetry for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
 
 Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
-Hence, we can forget the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
+Hence, we can forget about the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
 In the restricted formalism the spatial orbitals are the same so the two-electron basis set can be defined as
@@
 \end{align}
-The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, i.e., $\psi_1$ only interacts with $\psi_4$ and $\psi_2$ with $\psi_3$.
-The two singly-excited states yield after diagonalization a spatially anti-symmetric singlet sp\textsubscript{z} and a spatially symmetric triplet sp\textsubscript{z} state.
+The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, i.e., $\psi_1$ only interacts with $\psi_4$, and $\psi_2$ with $\psi_3$.
+The two singly-excited states yield, after diagonalization, a spatially anti-symmetric singlet sp\textsubscript{z} and a spatially symmetric triplet sp\textsubscript{z} state.
 Hence those states do not have the same symmetry as the spatially symmetric singlet ground state.
-Thus these states can not be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
+Thus, these states cannot be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
 However there is an avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states which gives two EPs in the complex plane.
@@
     \includegraphics[width=0.5\linewidth]{EMP_RHF_R10.pdf}
-    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.}
+    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
+    One can clearly see the avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states around $\lambda = 1$.}
     \label{fig:RHFMiniBas}
@@
 
-To simplify the problem, it is convenient to only consider basis functions with the symmetry of the exact wave function, such basis functions are called configuration state functions (CSFs).
-It simplifies the problem because with such a basis set, one only gets the degeneracies of interest for the convergence properties, i.e., the EPs between states with the same symmetry as the ground state.
-In this case the ground state is a totally symmetric singlet.
-According to the angular momentum theory \cite{AngularBook, SlaterBook, Loos_2009}, we expand the exact wave function in the following two-electron basis:
+To simplify the problem, it is convenient to only consider basis functions of a given symmetry.
+Such basis functions are called configuration state functions (CSFs).
+It simplifies greatly the problem because, with such a basis set, one only gets the degeneracies of interest associated with the convergence properties, i.e., the EPs between states with the same symmetry as the ground state.
+In the present context, the ground state is a totally symmetric singlet.
+According to angular momentum theory \cite{AngularBook, SlaterBook, Loos_2009}, we expand the exact wave function in the following two-electron basis:
 \begin{equation}
@@
 \end{equation}
-where $P_\ell$ are the Legendre polynomial and $\omega$ is the interelectronic angle.
+where $P_\ell$ are Legendre polynomials.
 
 Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
-Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (i.e., $P_0$ and $P_1$) and in the same basis augmented with $P_2$.
-We see that $R_{\text{CV}}$ for the SC partitioning increases with $R$ whereas it is decreasing for the three others partitioning.
-This result was expected because the three decreasing partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
-On the contrary, the strong coupling one uses a strongly correlated reference so the SC series converges better when the electron are strongly correlated, i.e., when $R$ is large in the spherium model.
+Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (i.e., consisting of $P_0$ and $P_1$) of size $K = 2$, and in the same basis augmented with $P_2$ ($K = 3$).
+We see that, for the SC partitioning, $R_{\text{CV}}$ increases with $R$ whereas it is decreasing for the three others partitioning.
+This result is expected because the MP, EN, and WC partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
+On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, i.e., when $R$ is large in the spherium model.
+Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a great range of radii for $K = 2$ than $K = 3$.
+\titou{T2: what happens in complete basis?}
 The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
-In the weak correlation partitioning the powers of $R$ are well-separated so each term of the series is a different power of $R$.
-Whereas the MP reference is proportional to $R^{-1}$ and $R^{-2}$ so the MP series is not well-defined in terms of powers of $R$.
-Moreover it can be proved that the $m$th order energy of the weak correlation series can be obtained as a Taylor approximation of MP$m$ respective to $R$.
-It seems that the EN partitioning is better than the MP one for very small $R$ in the minimal basis.
-In fact, it is just an artefact of the minimal basis because in the minimal basis augmented with $P_2$ (and in larger basis set) the MP series has a greater radius of convergence for all values of $R$.
+In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
+This is not the case for the MP series.
+Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
+It seems that the EN is better than MP for very small $R$ in the minimal basis.
+In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
 
@@
 The discontinuities observed in Fig.~\ref{fig:RadiusBasis} for the MP partitioning are due to changes in dominant singularity.
-We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative plane.
+We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative planes.
 
@@
 \begin{align}\label{eq:uhforbitals}
- \phi_{\alpha,1}(\theta) & =\frac{\sqrt{75+62R}Y_{0}(\theta)+5\sqrt{-3+2R}Y_{1}(\theta)}{4\sqrt{7R}},
+ 	\phi_{\alpha,1}(\theta) 
+ 		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+ 		+ \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
  \\ 
- \phi_{\beta,1}(\theta) & =\frac{\sqrt{75+62R}Y_{0}(\theta)-5\sqrt{-3+2R}Y_{1}(\theta)}{4\sqrt{7R}},
+ 	\phi_{\beta,1}(\theta) 
+		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+		- \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
  \\
- \phi_{\alpha,2}(\theta) & =\frac{-5\sqrt{-3+2R}Y_{0}(\theta)+\sqrt{75+62R}Y_{1}(\theta)}{4\sqrt{7R}},
+	 \phi_{\alpha,2}(\theta) 
+	 & = - \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+	  + \frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta),
  \\
- \phi_{\beta,2}(\theta) & =\frac{5\sqrt{-3+2R}Y_{0}(\theta)+\sqrt{75+62R}Y_{1}(\theta)}{4\sqrt{7R}}.
+	 \phi_{\beta,2}(\theta) 
+	 & =\frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+	 +\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta).
 \end{align}
@@
 \begin{equation}\label{eq:MatrixElem}
-H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{-3+2R}\sqrt{75+62R}\frac{25+2R}{280R^3}
-\end{equation}
-For $R=3/2$ the Hamiltonian is block diagonal and this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
+	H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{R-\frac{3}{2}}\sqrt{R+\frac{75}{62}}\qty(R+\frac{25}{2})\frac{\sqrt{31}}{70R^3}
+\end{equation}
+For $R=3/2$, the Hamiltonian is block diagonal and this is equivalent to the RHF case.
+For $R>3/2$, the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated in Sec.~\ref{sec:uhfSing}.
+For $R<3/2$, the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated in Sec.~\ref{sec:uhfSing}.
 The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
@@
 The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We can not use CSFs in this case.
+We cannot use CSFs in this case.
 So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.

### 2020-07-31 RapportStage/Rapport.tex
more modifs in 5.2

@@
 \titou{T2: please modify structure of this section.}
-Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
-For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
+Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that, in the UHF case, there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
+For example, at $R=10$, the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
 And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
@@
 When $R$ increases this avoided crossing becomes sharper.
-As presented before $\beta$ singularities are linked to quantum phase transition so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
+As presented before $\beta$ singularities are linked to QTPs so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
 The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
-A second pair of $\beta$ singularities appear for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
+A second pair of $\beta$ singularities appear for $R\gtrsim 2.5$, this is probably due to an excited-state QTP but this has to be investigated further.
 

### 2020-07-31 RapportStage/Rapport.tex
modifications sec 5 and figures

--- 2020-07-31 RapportStage/Rapport.tex
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{TopologyEP.pdf}
+\begin{wrapfigure}{R}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{TopologyEP.pdf}
     \caption{A generic EP with the square-root branch point topology. A loop around the EP interconvert the states.}
     \label{fig:TopologyEP}
-\end{figure}
+\end{wrapfigure}
 By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
@@
 
-\begin{figure}
+For real $\lambda$, the Hamiltonian \eqref{eq:H_2x2} is clearly Hermitian, and it becomes non-Hermitian for any complex $\lambda$ value.
+Its eigenvalues are
+\begin{equation}
+\label{eq:E_2x2}
+	E_{\pm} = \frac{\epsilon_1 + \epsilon_2}{2} \pm \frac{1}{2} \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2},
+\end{equation}
+and they are represented as a function of $\lambda$ in Fig.~\ref{fig:2x2}.
+One notices that the two states become degenerate only for a pair of complex conjugate values of $\lambda$
+\begin{equation}
+\label{eq:lambda_EP}
+	\lambda_\text{EP} = \pm i\,\frac{\epsilon_1 - \epsilon_2}{2},
+	\quad
+	\text{with energy}	
+	\quad
+	E_\text{EP} = \frac{\epsilon_1 + \epsilon_2}{2},
+\end{equation}
+which correspond to square-root singularities in the complex-$\lambda$ plane (see Fig.~\eqref{fig:2x2}).
+These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
+Starting from $\lambda_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
+In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
+The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
+
+\begin{figure}[h!]
     \centering
@@
 \end{figure}
-
-For real $\lambda$, the Hamiltonian \eqref{eq:H_2x2} is clearly Hermitian, and it becomes non-Hermitian for any complex $\lambda$ value.
-Its eigenvalues are
-\begin{equation}
-\label{eq:E_2x2}
-	E_{\pm} = \frac{\epsilon_1 + \epsilon_2}{2} \pm \frac{1}{2} \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2},
-\end{equation}
-and they are represented as a function of $\lambda$ in Fig.~\ref{fig:2x2}.
-One notices that the two states become degenerate only for a pair of complex conjugate values of $\lambda$
-\begin{equation}
-\label{eq:lambda_EP}
-	\lambda_\text{EP} = \pm i\,\frac{\epsilon_1 - \epsilon_2}{2},
-	\quad
-	\text{with energy}	
-	\quad
-	E_\text{EP} = \frac{\epsilon_1 + \epsilon_2}{2},
-\end{equation}
-which correspond to square-root singularities in the complex-$\lambda$ plane (see Fig.~\eqref{fig:2x2}).
-These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
-Starting from $\lambda_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
-In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
-The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{EsbHF.pdf}
-    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
-    \label{fig:SpheriumNrj}
-\end{figure}
-
 There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
@@
 \end{equation}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{EsbHF.pdf}
+    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+    \label{fig:SpheriumNrj}
+\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
     \centering
@@
 \end{table}
+
+\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
 
@@
 \end{equation}
-For $R=3/2$ the Hamiltonian is block diagonal and this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
+For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated in Sec.~\ref{sec:uhfSing}.
+For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated later.
 The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
@@
 
-\begin{figure}
+The singularity structure in this case is more complex because of the spin contamination of the wave function.
+We can not use CSFs in this case.
+So when one compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
+The numerical distinction of those singularities is very difficult.
+We will first look at the energies $E(\lambda)$ obtained with this basis set to attribute a physical signification to the singularities obtained numerically.
+Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
+We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
+Those avoided crossings are due to the spin contamination of the wave function.
+
+\begin{figure}[h!]
     \centering
@@
 
-The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We can not use CSFs in this case.
-So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
-The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
-Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
-We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
-Those avoided crossings are due to the spin contamination of the wave function.
-The EPs resulting from those avoided crossings will be discussed in Sec.~\ref{sec:uhfSing}.
-
-\titou{In this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
-It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.}
-\titou{T2: Please move to concluding section.}
-
-\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
-
-\titou{T2: please modify structure of this section.}
 Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
@@
 The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
-A second pair of $\beta$ singularities appear for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
+The sharp avoided crossing between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is not present on Fig.
+\ref{fig:UHFEP}.
+The second pair of $\beta$ singularities resulting from this avoided crossing appears for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
 
@@
 
+For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
+In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
+This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
+
 \begin{figure}
@@
 \end{figure}
-
-For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
-In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
-This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
 
@@
 In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
+\antoine{Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
+More generally, to investigate the effect of the type of basis on the physics of EPs.}
 To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.

### 2020-07-31 RapportStage/Rapport.tex

--- 2020-07-31 RapportStage/Rapport.tex
@@
 \end{equation}
-For $R=3/2$, the Hamiltonian is block diagonal and this is equivalent to the RHF case.
-For $R>3/2$, the matrix elements become real.
+
+For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$, the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated in Sec.~\ref{sec:uhfSing}.
+For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated later.
 The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
@@
 
-The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We cannot use CSFs in this case.
-So when we compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
-The numerical distinction of those singularities is very difficult so we will first look at the energies $E(\lambda)$ obtained with this basis set.
-Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
-We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
-Those avoided crossings are due to the spin contamination of the wave function.
-The EPs resulting from those avoided crossings will be discussed in Sec.~\ref{sec:uhfSing}.
-
-\titou{In this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
-It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.}
-\titou{T2: Please move to concluding section.}
-
-\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
-
-\titou{T2: please modify structure of this section.}
 Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.

### 2020-07-31 RapportStage/Rapport.tex
corrections

@@
 Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
-To find them we solve simultaneously the following equations \titou{REFS}:
+To find them we solve simultaneously the following equations \antoine{\cite{Cejnar_2007}}:
 \begin{subequations}
@@
 On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, i.e., when $R$ is large in the spherium model.
-Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a great range of radii for $K = 2$ than $K = 3$.
-\titou{T2: what happens in complete basis?}
+Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$.
+\antoine{In the complete basis the basis the radius of convergence of the SC partitioning is greater than one only for very large value of R.}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
+    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
+    \label{fig:RadiusPartitioning}
+\end{figure}
 The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
@@
 It seems that the EN is better than MP for very small $R$ in the minimal basis.
-In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
-    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
-    \label{fig:RadiusPartitioning}
-\end{figure}
+In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$ \antoine{and this is still true for $K>3$.}
 

### 2020-07-31 RapportStage/Rapport.tex
validation Antoine comments

@@
 Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
-To find them we solve simultaneously the following equations \antoine{\cite{Cejnar_2007}}:
+To find them we solve simultaneously the following equations \cite{Cejnar_2007}:
 \begin{subequations}
@@
 Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$. 
-\antoine{In the complete basis the basis the radius of convergence of the SC partitioning is greater than one only for very large value of R.}
+In the complete basis limit, the radius of convergence of the SC partitioning is greater than unity only for very large value of $R$.
+
 \begin{figure}
@@
 It seems that the EN is better than MP for very small $R$ in the minimal basis.
-In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$ \antoine{and this is still true for $K>3$.}
+In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
+It holds true for $K>3$.
 
@@
 In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
-\antoine{Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
 It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
-More generally, to investigate the effect of the type of basis on the physics of EPs.}
+%More generally, to investigate the effect of the type of basis on the physics of EPs.
 To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.

### 2020-07-31 RapportStage/Rapport.tex
figures

--- 2020-07-31 RapportStage/Rapport.tex
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{EMP_RHF_R10.pdf}
+\begin{wrapfigure}{R}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
     \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
@@
     \label{fig:RHFMiniBas}
-\end{figure}
+\end{wrapfigure}
 
@@
 \antoine{In the complete basis the basis the radius of convergence of the SC partitioning is greater than one only for very large value of R.}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
-    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
-    \label{fig:RadiusPartitioning}
-\end{figure}
 The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
@@
 In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$ \antoine{and this is still true for $K>3$.}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
+    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
+    \label{fig:RadiusPartitioning}
+\end{figure}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.5\linewidth]{EMP_UHF_R10.pdf}
+\begin{wrapfigure}{R}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
     \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
     \label{fig:UHFMiniBas}
-\end{figure}
+\end{wrapfigure}
 

### 2020-07-31 RapportStage/Rapport.tex

--- 2020-07-31 RapportStage/Rapport.tex
@@
 On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, i.e., when $R$ is large in the spherium model.
+
 Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$. 
 In the complete basis limit, the radius of convergence of the SC partitioning is greater than unity only for very large value of $R$.
+The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
+In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
+This is not the case for the MP series.
+Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
+It seems that the EN is better than MP for very small $R$ in the minimal basis.
+In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$ \antoine{and this is still true for $K>3$.}
 
@@
 \end{figure}
+
 The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.

### 2020-07-31 RapportStage/Rapport.tex
minor correction
final version

@@
 \section*{Acknowledgments}
+
+I would like to sincerely thanks Pierre-François \textsc{LOOS} for supervising my internship.
+This first experience of academic research in theoretical chemistry confirmed my interest for this domain and taught me many things about theoretical chemistry but also about the job of researcher.
+I hope that I will have the chance to work in this group agian (and not in the context of a global pandemic if possible).
+I also thanks my three confined flatmates Tristan, Sylvio and especially Julie for bearing with me during those 3(+2) months.
 
@@
 This solution is called symmetry-broken RHF (sb-RHF).
-\antoine{The reasoning is counter-intuitive because the electrons tends to maximize their energy.
+The reasoning is counter-intuitive because the electrons tends to maximize their energy.
+The p\textsubscript{z} orbital is symmetric with respect to the center of the sphere.
 If the orbitals are symmetric, the maximum is when the two electrons are in the p\textsubscript{z} orbital because it maximizes the kinetic energy.
 At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital i.e., on the same side of the sphere gives a superior energy than the p\textsubscript{z}\textsuperscript{2} state.
-This is because it becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$.}
+Adding a s orbital on one side of the p\textsubscript{z} orbital to form a symmetry-broken orbital reduce the kinetic energy but increase the repulsion energy as the two electrons are more localized on one side of the sphere.
+It becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$.
 This configuration breaks the spatial symmetry of charge.
@@
 \end{equation}
-
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=0.8\linewidth]{EsbHF.pdf}
+    \includegraphics[width=0.77\linewidth]{EsbHF.pdf}
     \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
@@
 Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$.
-In the complete basis limit, the radius of convergence of the SC partitioning is greater than unity only for very large value of $R$.
-The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
-In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
-This is not the case for the MP series.
-Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
-It seems that the EN is better than MP for very small $R$ in the minimal basis.
-In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$ \antoine{and this is still true for $K>3$.}
 

### 2020-07-31 RapportStage/Rapport.tex
coquille remerciement

@@
 This first experience of academic research in theoretical chemistry confirmed my interest for this domain and taught me many things about theoretical chemistry but also about the job of researcher.
-I hope that I will have the chance to work in this group agian (and not in the context of a global pandemic if possible).
-I also thanks my three confined flatmates Tristan, Sylvio and especially Julie for bearing with me during those 3(+2) months.
+I hope that I will have the chance to work in this group again (and not in the context of a global pandemic if possible).
+I also thank my three confined flatmates Tristan, Sylvio and especially Julie for bearing with me during those 3(+2) months.
 

### 2020-08-24 Manuscript/EPAWTFT.tex
update
saving work

@@
 \documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,wrapfig,txfonts}
+\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,txfonts,mhchem}
 
@@
 \newcommand{\ctab}{\multicolumn{1}{c}{---}}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\eg}{\textit{e.g.}}
 \newcommand{\mc}{\multicolumn}
@@
 \newcommand{\Ne}{N}
+\newcommand{\hI}{\Hat{I}}
 \newcommand{\hH}{\Hat{H}}
+\newcommand{\hS}{\Hat{S}}
 \newcommand{\hT}{\Hat{T}}
@@
 \newcommand{\ra}{\rightarrow}
+\newcommand{\pt}{$\mathcal{PT}$}
 
-\newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France}
+\newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France.}
 \newcommand{\UCAM}{Department of Chemistry, University of Cambridge, Lensfield Road, Cambridge, CB2 1EW, U.K.}
-
+\newcommand{\VU}{Department of Theoretical Chemistry and Amsterdam Center for Multiscale Modeling, FEW, Vrije Universiteit, De Boelelaan 1083, 1081HV Amsterdam, The Netherlands.}
 \begin{document}
 
-\title{Exceptional points and where to find them}
+\title{Perturbation theory in the complex plane}
+%\title{Exceptional points and where to find them}
 
 \author{Antoine \surname{Marie}}
-\email{antoine.marie@ens-lyon.fr}
 \affiliation{\LCPQ}
-%\author{Hugh G.~A.~\surname{Burton}}
-%\email{hb407@cam.ac.uk}
-%\affiliation{\UCAM}
+\author{Hugh G.~A.~\surname{Burton}}
+\affiliation{\UCAM}
+\author{Paola \surname{Gori-Giorgi}}
+\affiliation{\VU}
 \author{Pierre-Fran\c{c}ois \surname{Loos}}
-\thanks{Corresponding author}
 \email{loos@irsamc.ups-tlse.fr}
@@
 \begin{abstract}
-In this work, we explore the description of quantum chemistry in the complex plane. 
-Using the Hubbard dimer as a simple model system, we investigate how various methods in electronic structure theory (including Hartree--Fock, \titou{density-functional theory}, perturbation theory and full configuration interaction) are formulated in the complex plane, and how this affects their behaviour in the real plane.
-For example, we demonstrate how the position of exceptional points of the real axis controls the convergence of perturbation theory, and explore the inherent dependence on the set of orbital coefficients.
-Moreover, we reveal how the avoided crossing of FCI states correspond to an exceptional point in the complex plane, which in turn demonstrates that multiple FCI solutions form a more general structure across the complex plane.
-Ultimately, by exposing these more profound topologies of electronic structure methods in the complex plane, we hope to pave the way for novel methodologies.
+In this work, we explore the extension of quantum chemistry in the complex plane.
+We observe that the physics of a quantum system is intimately connected to the position of the energy singularities in the complex plane.
+After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
+Then we connect and further discuss these different aspects using the spherium model (\ie, two opposite-spin electrons restricted to remain on the surface of a sphere) as a theoretical playground.
+In particular, we explore various perturbative partitioning strategies and the effects of symmetry breaking on the singularity structure of the electronic energy.
+This provides fundamental insights on the location of these singularities in the complex plane (that one calls exceptional points) and, specifically, on the magnitude of the radius of convergence associated with the perturbative treatment.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:intro}
 %============================================================%
 
-The notion of quantised energy levels is a central feature of Hermitian quantum mechanics. 
-In quantum chemistry, the ordering of the energy levels represents the different electronic states of a molecule, the lowest being the ground state while the higher ones are the so-called excited states.
-Within this quantised paradigm, electronic states look completely disconnected from one another.
-However, one can gain a different perspective on quantisation if one extends quantum chemistry into the complex domain.
+\subsection{Background}
+
+Due to the ubiquitous influence of processes involving electronic excited states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
+Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community.
+An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws. 
+The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new excited-state methodologies, their main goal being to get the most accurate excitation energies (and properties) at the lowest possible computational cost in the most general context.
+
+One common feature of all these methods is that they rely on the notion of quantized energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
+Within this quantized paradigm, electronic states look completely disconnected from one another.
+Many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.
+However, one can gain a different perspective on quantization extending quantum chemistry into the complex domain.
 In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
-In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+In other words, our view of the quantized nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+\cite{MoiseyevBook,BenderPTBook}
+The realization that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
+One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019}
 
-Therefore, by analytically continuing the energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), one can smoothly connect the ground and excited states of a molecule.
-This connection is possible because, by extending real numbers to the complex domain, one loses the ordering property of real numbers.
-Hence, one can interchange electronic states away from the real axis, as the concept of ground and excited states has been lost.
-Amazingly, this smooth and continuous transition from one state to another has been recently realised experimentally in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
+By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
+This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
+Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
+Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
 \cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}
 
-Exceptional points (EPs) \cite{Heiss_1990, Heiss_1999, Heiss_2012, Heiss_2016} are non-Hermitian analogs of conical intersections (CIs) \cite{Yarkony_1996} where two states become exactly degenerate.
-CIs are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
-In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to CIs in the decay of bound excited states.
-Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
-For example, by encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate. \cite{Heiss_1990,Heiss_1999,Heiss_2012,Heiss_2016}
+They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
+In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
+Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
+For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
+In contrast, encircling Hermitian degeneracies at conical intersections only introduces a geometric phase while leaving the states unchanged.
+More dramatically, whilst eigenvectors remain orthogonal at conical intersections, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state.
+\cite{MoiseyevBook}
+More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
+\cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019}
+
+\subsection{An illustrative example}
+In order to highlight the general properties of EPs mentioned above, we propose to consider the following $2 \times 2$ Hamiltonian commonly used in quantum chemistry
+
+\begin{equation}
+\label{eq:H_2x2}
+	\bH = 
+	\begin{pmatrix}
+		\epsilon_1	&	\lambda	\\
+		\lambda		&	\epsilon_2
+	\end{pmatrix},
+\end{equation}
+which represents two states of energies $\epsilon_1$ and $\epsilon_2$ coupled with a strength of magnitude $\lambda$.
+This Hamiltonian could represent, for example, a minimal-basis configuration interaction with doubles (CID) for the hydrogen molecule. \cite{SzaboBook}
+
+For real $\lambda$, the Hamiltonian \eqref{eq:H_2x2} is clearly Hermitian, and it becomes non-Hermitian for any complex $\lambda$ value.
+Its eigenvalues are
+\begin{equation}
+\label{eq:E_2x2}
+	E_{\pm} = \frac{\epsilon_1 + \epsilon_2}{2} \pm \frac{1}{2} \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}.
+\end{equation}
+%and they are represented as a function of $\lambda$ in Fig.~\ref{fig:2x2}.
+One notices that the two states become degenerate only for a pair of complex conjugate values of $\lambda$
+\begin{equation}
+\label{eq:lambda_EP}
+	\lambda_\text{EP} = \pm i\,\frac{\epsilon_1 - \epsilon_2}{2},
+\end{equation}
+with energy
+\begin{equation}
+\label{eq:E_EP}
+	E_\text{EP} = \frac{\epsilon_1 + \epsilon_2}{2},
+\end{equation}
+which correspond to square-root singularities in the complex-$\lambda$ plane. % (see Fig.~\eqref{fig:2x2}).
+These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
+Starting from $\lambda_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
+In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
+The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
+
+Around $\lambda = \lambda_\text{EP}$, Eq.~\eqref{eq:E_2x2} behaves as \cite{MoiseyevBook}
+\begin{equation} %\label{eq:E_EP}
+        E_{\pm} = E_\text{EP} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}},
+\end{equation}
+and following a complex contour around the EP, \ie, $\lambda = \lambda_\text{EP} + R \exp(i\theta)$, yields
+\begin{equation}
+        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2\lambda_\text{EP} R}  \exp(i\theta/2),
+\end{equation}
+and we have
+\begin{align}
+	E_{\pm}(2\pi) & = E_{\mp}(0),
+	&
+	E_{\pm}(4\pi) & = E_{\pm}(0). \notag
+\end{align}
+This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the starting wave function.
-In contrast, encircling Hermitian degeneracies at CIs introduces only a geometric phase while leaving the states unchanged.
-More dramatically, whilst eigenvectors remain orthogonal at CIs, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
-More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
-\cite{Olsen_1996, Olsen_2000}
+\cite{MoiseyevBook}
+
+%The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
+%\begin{equation}\label{eq:phi_2x2}
+%\begin{split}
+%	\phi_{\pm}
+%	& = 
+%	\begin{pmatrix}
+%		(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2})/2\lambda 
+%		\\ 
+%		1
+%	\end{pmatrix}
+%	\\
+%	=
+%	\begin{pmatrix}
+%		(\epsilon_1-\epsilon_2)/2\lambda \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}/\lambda 
+%		\\ 
+%		1
+%	\end{pmatrix},
+%\end{split}
+%\end{equation}
+%and, for $\lambda=\lambda_\text{EP}$, they become
+%\begin{equation}
+%	\phi_{\pm} = \begin{pmatrix} \mp i \\ 1\end{pmatrix},
+%\end{equation}
+%which are clearly self-orthogonal, \ie, their norm is equal to zero. 
+%
+%As branch point (square-root) singularities, EPs inherit their topology from the multi-valued function $\sqrt{\lambda - \lambda_\text{EP}}$. 
+%Then, if the eigenvectors are properly normalized, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$, which gives the following pattern when looping around one EP:
+%\begin{align}
+%	\phi_{\pm}(2\pi) & = \phi_{\mp}(0), 
+%	&
+%	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0), \notag
+%	\\
+%	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
+%	&
+%	\phi_{\pm}(8\pi) & = \phi_{\pm}(0).\notag
+%\end{align}
+%In plain words, four loops around the EP are necessary to recover the initial state. 
+%We can also see that looping the other way around leads to a different pattern.
 
 %============================================================%
-\section{Perturbation Theory}
+\section{Perturbation theory}
 %============================================================%
 
-Within perturbation theory, the Schr\"odinger equation is usually rewritten as 
-\begin{equation}
-	\bH \Psi(\lambda) = (\bH^{(0)} + \lambda \bH^{(1)} ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
+\subsection{Rayleigh-Schr\"odinger perturbation theory}
+
+Within the Born-Oppenheimer approximation, 
+\begin{equation}\label{eq:ExactHamiltonian}
+    \hH = - \frac{1}{2} \sum_{i}^{n} \grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} + \sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}
 \end{equation}
-with
-\begin{equation}
+is the exact electronic Hamiltonian for a chemical system with $n$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $N$ (fixed) nuclei (where $\vb{R}_A$ and $Z_A$ are the position and the charge of the $A$th nucleus respectively).
+The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
+Note that we use atomic units throughout unless otherwise stated.
+
+Within (time-independent) Rayleigh-Schr\"odinger perturbation theory, the Schr\"odinger equation 
+\begin{equation} \label{eq:SchrEq}
+	\hH \Psi = E \Psi
+\end{equation} 
+is recast as 
+\begin{equation} \label{eq:SchrEq-PT}
+	\hH(\lambda) \Psi(\lambda) = (\hH^{(0)} + \lambda \hV ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
+\end{equation}
+where $\hH^{(0)}$ is the zeroth-order Hamiltonian and $\hV = \hH - \hH^{(0)}$ is the so-called perturbation.
+The ``physical'' system of interest is recovered by setting the coupling parameter $\lambda$ to unity.
+This decomposition is obviously non-unique and motivated by several factors as discussed below.
+
+Accordingly to Eq.~\eqref{eq:SchrEq-PT}, the energy can then be written as a power series of $\lambda$
+\begin{equation} \label{eq:Elambda}
 	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}.
 \end{equation}
-However, it is not unusual that the series $E(\lambda)$ has a radius of convergence $\abs{\lambda_0} < 1$. 
-This means that the series is divergent in the domain $\abs{\lambda} < \abs{\lambda_0}$, hence for the physical system at $\lambda = 1$.
-As eluded above, $\abs{\lambda_0}$ is determined by the location of the singularity of $E(\lambda)$ closest to the origin.
-These singularities are nothing but EPs at $\lambda_0$ and $\lambda_0^*$.
-Here, we propose to thoroughly investigate the connection between Coulson-Fisher quasi-EPs and the radius of convergence of various flavours of perturbation theory.
-For example, M{\o}ller-Plesset perturbation theory (MPPT) has the particularity of relying on a Hartree-Fock (HF) wave function as a zeroth-order wave function.
-However, the flavour of HF one can select (restricted, unrestricted, generalised, holomorphic, \ldots) is up for grabs, and the convergence properties of the MPPT series will drastically change depending on this choice.
-Indeed, the radius of convergence is intimately connected to the location of singularities in the complex plane; these singularities are, themselves, linked to the choice of $\bH^{(0)}$. 
-Really, it depends on our ability of selecting a zeroth-order Hamiltonian such as $\bH$ does not have any EP inside the unit $\lambda$ circle.
+However, it is not guaranteed that the series \eqref{eq:Elambda} has a radius of convergence $\abs{\lambda_0} < 1$. 
+In other words, the series might well be divergent for the physical system at $\lambda = 1$. 
+One can prove that the actual value of the radius of convergence $\abs{\lambda_0}$ can be obtained by looking for the singularities of $E(\lambda)$ in the complex $\lambda$ plane.
+This is due to the following theorem: \cite{Goodson_2012}
+\begin{quote}
+	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1-z_0}$.
+If the function has a singular point $z_s$ such that $\abs{z_s-z_0} < \abs{z_1-z_0}$, then the series will diverge when evaluated at $z_1$.''}
+\end{quote}
+This theorem means that the radius of convergence of the perturbation series is equal to the distance to the origin of the closest singularity of $E(\lambda)$.
+To illustrate this result we consider the simple function \cite{BenderBook}
+\begin{equation} \label{eq:DivExample}
+	f(x)=\frac{1}{1+x^4}.
+\end{equation}
+This function is smooth for $x \in \mathbb{R}$ and infinitely differentiable in $\mathbb{R}$.
+One would expect that the Taylor series of such a function would be convergent $\forall x \in \mathbb{R}$.
+However this series is divergent for $x \ge 1$.
+This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}$, $e^{-i\pi/4}$, $e^{i3\pi/4}$, and $e^{-i3\pi/4}$) with a modulus equal to $1$.
+This simple yet powerful example emphasizes the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
 
-For example, MPPT calculations based on UHF wave functions have shown to be slowly convergent due to spin contamination while RHF-based MPPT calculations can be divergent. \cite{Gill_1986, Gill_1988}
-Although MPPT is widespread in the community, its convergence properties have not, to the very best of our knowledge, attracted much attention. \cite{Olsen_1996, Olsen_2000, Goodson_2012}
-We believe that they deserve greater understanding, particularly in a non-Hermitian setting.
+\subsection{The Hartree-Fock Hamiltonian}
+
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+\begin{equation}\label{eq:FockOp}
+	f(\vb{x}) \phi_p(\vb{x}) = [ h(\vb{x}) + v^\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
+\end{equation}
+where 
+\begin{equation}
+	h(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
+\end{equation}
+is the core Hamiltonian and 
+\begin{equation}
+	v^\text{HF}(\vb{x}) = \sum_i \qty[ J_i(\vb{x}) - K_i(\vb{x}) ]
+\end{equation}
+is the HF mean-field potential with 
+\begin{subequations}
+\begin{gather}
+	\label{eq:CoulOp}
+	J_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') ] \phi_p(\vb{x})
+	\\
+	\label{eq:ExcOp}
+	K_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_p(\vb{x}') ] \phi_i(\vb{x})
+\end{gather}
+\end{subequations}
+being the Coulomb and exchange operators (respectively) in the spin-orbital basis. \cite{SzaboBook}
+If the spatial part of the spin-orbitals are restricted to be the same for spin-up and spin-down electrons, one talks about restricted HF (RHF) theory, whereas if one does not enforce this constrain it leads to the so-called unrestricted HF (UHF) theory.
+From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
+
+Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
+Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\hH$.
+However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian defined as the sum of the one-electron Fock operators
+\begin{equation}\label{eq:HFHamiltonian}
+	\hH^{\text{HF}} = \sum_{i} f(\vb{x}_i).
+\end{equation}
+%Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues (see below).
+
+\subsection{M{\o}ller-Plesset perturbation theory}
+
+The HF Hamiltonian \eqref{eq:HFHamiltonian} can be used as the zeroth-order Hamiltonian of Eq.~\eqref{eq:SchrEq-PT}.
+This partitioning of the Hamiltonian leads to the so-called M{\o}ller-Plesset (MP) perturbation theory.
+\cite{Moller_1934}
+The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a large chunck of the correlation energy (\ie, the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-HF methods.
+This yields
+\begin{multline}\label{eq:MPHamiltonian}
+    \hH(\lambda) = 
+    \sum_{i}^{n} \Bigg[ 
+    -\frac{\grad_i^2}{2} 
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+    \\
+    + (1-\lambda) v^{\text{HF}}(\vb{x}_i) 
+    + \lambda\sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
+    \Bigg].
+\end{multline}
+If one considers a RHF or UHF reference wave functions, it leads to the RMP or UMP series, respectively.
+
+As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
+The MP$m$ energy is defined as 
+\begin{equation}
+	E_{\text{MP}m}= \sum_{k=0}^m E^{(k)},
+\end{equation}
+where $E^{(k)}$ is the $k$th-order MP correction, and it is well known that $E_{\text{MP1}} =  E^{(0)} + E^{(1)} = E_\text{HF}$. \cite{SzaboBook}
+The MP2 energy reads
+\begin{equation}\label{eq:EMP2}
+	E_{\text{MP2}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
+\end{equation}
+with $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$, and where  
+\begin{equation}
+	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\frac{1}{\abs{\vb{r}_1 - \vb{r}_2}}\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)
+\end{equation}
+is a two-electron integral in the spin-orbital basis.
+
+As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$m$ series converges to the exact energy when $m \to \infty$. 
+In fact, it is known that when the HF wave function is a poor approximation to the exact wave function, for example in multi-reference systems, the MP method yields deceptive results.
+\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}
+A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
+By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
+As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
+These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
+The direct computation of the terms of the series is quite manageable up to fourth order in perturbation, while the fifth and sixth order in perturbation can still be obtained but at a rather high cost.
+\cite{JensenBook}
+In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
+For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
+If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
+
+\subsection{Alternative partitioning}\label{sec:AlterPart}
+
+Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility. 
+Here, we will consider three alternative partitioning schemes:
+\begin{itemize}
+	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. 
+	Hence, the off-diagonal elements of $\hH$ are the perturbation operator.
+	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$.
+	\item The strong coupling (SC) partitioning where the two operators are inverted compared to the WC partitioning. \cite{Seidl_2018}
+\end{itemize}
 
 %============================================================%
-\section{The asymmetric Hubbard dimer}
+\section{Historical overview}
 %============================================================%
 
-The asymmetric Hubbard dimer is a model two-electron system whose Hamiltonian reads
+\subsection{Behavior of the M{\o}ller-Plesset series}
+
+When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
+%In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
+In other words, one would like a monotonic convergence of the MP series.
+Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
+Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
+In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
+Thus, one cannot practically use it for systems where only the first terms can be computed.
+
+When a bond is stretched, in most cases the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be a single Slater determinant.
+Thus, it is inappropriate to model (even qualitatively) stretched systems.
+Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
+One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
+However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly converging behavior that one would wish for.
+
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
+Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination for \ce{H2} in a minimal basis.
+\cite{Gill_1988}
+Handy and coworkers reported the same behavior of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2} systems.
+\cite{Handy_1985} Lepetit \textit`{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference.
+\cite{Lepetit_1988}
+They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations. 
+Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
+They highlighted that \cite{Cremer_1996}
+\begin{quote}
+	\textit{``Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+\end{quote}
+As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
+The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.
+Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+
+\subsection{Cases of divergence}
+
+In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behavior of the MP series.
+\cite{Olsen_1996} They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF}.
+\cite{Olsen_1996, Christiansen_1996} Cremer and He had already studied these two systems and classified them as \textit{class B} systems.
+However, the analysis of Olsen and coworkers was performed in larger basis sets containing diffuse functions.
+In these basis sets, they found that the series become divergent at (very) high order.
+
+The discovery of this divergent behavior is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
+Including diffuse functions is particularly important in the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
+As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence.
+To do so, they analyzed the relation between the dominant singularity (\ie, the closest singularity to the origin) and the convergence behavior of the series.
+\cite{Olsen_2000} Their analysis is based on Darboux's theorem:
+\begin{quote}
+	\textit{``In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
+Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.''}
+\end{quote}
+
+A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
+Their method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities.
+Then, by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ Hamiltonian
 \begin{equation}
-	\hH = \hT + \hW + \hV,
+\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\hH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\hH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\hV},
 \end{equation}
-with
+where the diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbation.
+See also Ref.~\onlinecite{Olsen_2019} where the present model is generalized to a non-symmetric (i.e, non-Hermitian) Hamiltonian.
+
+They first studied molecules with low-lying doubly-excited states of the same spatial and spin symmetry.
+% \titou{because in those systems the HF wave function is a bad approximation.} 
+The exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states were good candidates for being intruder states.
+For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
+They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
+
+Then they demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state.
+When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back-door intruder state.
+They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series.
+%They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state.
+
+Moreover they proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} cannot be used for all systems, and that these formulas were not mathematically motivated when looking at the singularity causing the divergence.
+For example, the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly-excited states which results in alternated terms up to 10th order.
+For higher orders, the series is monotonically convergent.
+This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
+
+\subsection{The singularity structure}
+
+In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+They regrouped singularities in two classes: i) $\alpha$ singularities which have ``large'' imaginary parts, and ii) $\beta$ singularities which have very small imaginary parts.
+Singularities of type $\alpha$ are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
+They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work of Stillinger.
+\cite{Stillinger_2000}
+
+To understand the convergence properties of the perturbation series at $\lambda=1$, one must look at the whole complex plane, in particular, for negative (\ie, real) values of $\lambda$.
+If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field (which has been computed at $\lambda = 1$) remains repulsive as it is proportional to $(1-\lambda)$:
+
+\begin{multline}
+\label{eq:HamiltonianStillinger}
+    \hH(\lambda) = 
+    \sum_{i}^{n} \Bigg[ 
+    \overbrace{-\frac{1}{2}\grad_i^2 
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}^{\text{Independent of $\lambda$}}
+    \\
+    + \underbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}_{\text{Repulsive for $\lambda < 1$}}
+    + \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{Attractive for $\lambda < 0$}}
+    \Bigg].
+\end{multline}
+
+The major difference between those two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
+For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei.
+According to Baker, \cite{Baker_1971} this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_\text{c}$.
+At this point the system undergo a phase transition and a symmetry breaking.
+Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.
+
+This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis.
+However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+This explains that Olsen \textit{et al.}, because they used a simple $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
+\cite{Olsen_2000}
+
+Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the stretching of the system.
+On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching.
+According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity.
+This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry.
+To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
+
+\subsection{The physics of quantum phase transition}
+
+In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point.
+In a finite basis set this critical point is model by a cluster of $\beta$ singularities.
+It is now well known that this phenomenon is a special case of a more general phenomenon.
+Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
+\cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017} In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter.
+In some cases the variation of a parameter can lead to abrupt changes at a critical point.
+These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
+\cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019} A ground-state QPT is characterized by the derivatives of the ground-state energy with respect to a non-thermal control parameter.
+\cite{Cejnar_2009, Sachdev_2011} The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
+Otherwise, it is called continuous and of $m$th order if the $m$th derivative is discontinuous.
+A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
+
+The presence of an EP close to the real axis is characteristic of a sharp avoided crossing.
+Yet, at such an avoided crossing, eigenstates change abruptly.
+Although it is now well understood that EPs are closely related to QPTs, the link between the type of QPT (ground state or excited state, first or higher order) and EPs still need to be clarified.
+One of the major obstacles that one faces in order to achieve this resides in the ability to compute the distribution of EPs.
+The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions.
+Hence, the design of specific methods are required to get information on the location of EPs.
+Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis.
+\cite{Cejnar_2005, Cejnar_2007} More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT.
+\cite{Stransky_2018} In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis.
+They showed that, within the interaction boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases.
+The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second orders, respectively) with respect to the number of particles.
+
+It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.
+Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.
+Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly.
+However, the $\alpha$ singularities arise from large avoided crossings.
+Thus, they cannot be connected to QPT.
+The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states.
+Those excited states have a non-negligible contribution to the exact FCI solution because they have (usually) the same spatial and spin symmetry as the ground state.
+We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, \ie, to the multi-reference nature of the wave function thus to the static part of the correlation energy.
+
+%============================================================%
+\section{The spherium model}\label{sec:spherium}
+%============================================================%
+
+Simple systems that are analytically solvable (or at least quasi-exactly solvable, \ie, models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
+These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
+To investigate the physics of EPs we consider one such system named \textit{spherium}. 
+It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. \cite{Thompson_2005, Seidl_2007, Loos_2009b} 
+Thus, the Hamiltonian is
+\begin{equation}
+	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}},
+\end{equation}
+or
+\begin{equation} \label{eq:H-sph-omega}
+	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
+\end{equation}
+where $\omega$ is the interelectronic angle.
+The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
+Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
+The radius of the sphere $R$ dictates the correlation regime. \cite{Loos_2009}
+In the weak correlation regime (\ie, small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
+For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
+This phenomenon is sometimes referred to as a Wigner crystallization. \cite{Wigner_1934}
+
+We will use this model in order to rationalize the effects of the parameters that may influence the physics of EPs:
+\begin{itemize}
+	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
+	\item Basis set: minimal basis or infinite (\ie, complete) basis.
+	\item Radius of the sphere that ultimately dictates the correlation regime.
+\end{itemize}
+
+In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
+The spatial part of the RHF wave function is then
+\begin{equation}\label{eq:RHF_WF}
+	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
+\end{equation}
+where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
+Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
+
+The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
+Within the UHF formalism, there is a critical value of $R$, called Coulson-Fischer point, \cite{Coulson_1949} at which a UHF solution appears and is lower in energy than the RHF one.
+The UHF solution has broken symmetry because the two electrons tends to localize on opposite sides of the sphere. 
+The spatial part of the UHF wave function is defined as
+\begin{equation}\label{eq:UHF_WF}
+	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2),
+\end{equation}
+where $\phi_\sigma(\theta)$ is the spatial orbital associated with the spin-$\sigma$ electrons ($\sigma = \alpha$ for spin-up electrons and $\sigma = \beta$ for spin-down electrons).
+These one-electron orbitals are expanded in the basis of zonal spherical harmonics
+\begin{equation}
+	\phi_\sigma(\theta)=\sum_{\ell=0}^{\infty}C_{\sigma,\ell}Y_{\ell}(\theta)
+\end{equation}
+It is possible to obtain the formula for the HF energy in this basis set: \cite{Loos_2009}
+\begin{equation}
+	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}},
+\label{eq:EHF}
+\end{equation}
+where the kinetic and potential energies are, respectively,
+\begin{align}
+	T_{\text{HF}} & = \frac{1}{R^2} \sum_{\sigma=\alpha,\beta} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1),
+	&
+	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty}
+	v^\alpha_{L} v^\beta_{L},
+\end{align}
+and
+\begin{equation}
+	v^\sigma_{L} 
+	=  \sum_{\ell_1,\ell_2} \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
+	\begin{pmatrix}
+		\ell_1 & \ell_2 & L 
+		\\
+		0 & 0 & 0
+	\end{pmatrix}^2 
+\end{equation}
+is expressed in terms of the Wigner 3j-symbols. \cite{AngularBook}
+
+The general method is to use a self-consistent field procedure as described in Ref.~\onlinecite{SzaboBook} to get the coefficients of the HF wave function corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, \ie,
+\begin{equation}
+	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
+\end{equation}
+Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
+In this basis there is a shortcut to find the stationary solutions and ensure normalization of the orbitals.
+One can define the one-electron orbitals as
+\begin{equation}
+	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta),
+\end{equation}
+using a mixing angle between the two basis functions for each spin manifold. 
+Hence, one has just to minimize/maximize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
+
+This process provides the three following solutions valid for all value of $R$, which are respectively a minimum, a maximum and a saddle point of the HF equations:
+\begin{itemize}
+\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R$.
+\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
+\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
+\end{itemize}
+
+In addition, the minimization process gives also the well-known symmetry-broken UHF (sb-UHF) solution.
+In this case the Coulson-Fischer point associated to this solution is $R=3/2$.
+For $R>3/2$ the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
+This solution corresponds to the configuration with the spin-up electron in an orbital on one side of the sphere and the spin-down electron in a miror-image orbital on the opposite side and the configuration the other way round.
+The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
+For $R>3/2$, this solution has the energy
+\begin{equation}\label{eq:EsbUHF}
+	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}.
+\end{equation}
+
+The exact solution for the ground state is a singlet.
+The spherical harmonics are eigenvectors of $\hS^2$ (the spin operator) and they are associated to different eigenvalues.
+Yet, the symmetry-broken orbitals are linear combinations of $Y_0$ and $Y_1$.
+Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$.
+However, this solution gives lower energies than the RHF one at large $R$ as shown in Table \ref{tab:ERHFvsEUHF} even if it does not have the exact spin symmetry.
+In fact, at the Coulson-Fischer point, it becomes more effective to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
+Thus, within the HF approximation, the variational principle is allowed to break the spin symmetry because it yields a more effective minimization of the Coulomb repulsion.
+This type of symmetry breaking is called a spin density wave because the system oscillates between the two symmetry-broken configurations.
+\cite{GiulianiBook}
+
+\begin{table*}
+\caption{RHF and sb-UHF energies in the minimal basis and exact energies (in the complete basis) for various $R$.
+\label{tab:ERHFvsEUHF}}
+\begin{ruledtabular}
+\begin{tabular}{ccccccccc}
+$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
+\hline
+RHF 	& 10.00000 & 1.000000 & 0.500000 & 0.333333 & 0.200000 & 0.100000 & 0.010000 & 0.001000 \\
+UHF 	& 10.00000 & 1.000000 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
+Exact 	& 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
+\end{tabular}
+\end{ruledtabular}
+\end{table*}
+
+There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
+This solution is associated with another type of symmetry breaking somewhat less known.
+It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
+This solution is called symmetry-broken RHF (sb-RHF).
+The reasoning is counter-intuitive because the electrons tends to maximize their energy.
+The p\textsubscript{z} orbital is symmetric with respect to the center of the sphere.
+If the orbitals are symmetric, the maximum is when the two electrons are in the p\textsubscript{z} orbital because it maximizes the kinetic energy.
+At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital \ie, on the same side of the sphere gives a superior energy than the p\textsubscript{z}\textsuperscript{2} state.
+Adding a s orbital on one side of the p\textsubscript{z} orbital to form a symmetry-broken orbital reduce the kinetic energy but increase the repulsion energy as the two electrons are more localized on one side of the sphere.
+It becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$.
+This configuration breaks the spatial symmetry of charge.
+Hence this symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side.
+\cite{GiulianiBook}
+The energy associated with this sb-RHF solution reads
+\begin{equation}
+E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}.
+\end{equation}
+\begin{figure}
+    \includegraphics[width=\linewidth]{EsbHF.pdf}
+    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+    \label{fig:SpheriumNrj}
+\end{figure}
+
+We can also consider negative values of $R$, which corresponds to the situation where one of the electrons is replaced by a positron (the anti-particle of the electron) as readily seen in Eq.~\eqref{eq:H-sph-omega}.
+For negative $R$ values, there are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
+Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere.
+And the sb-UHF state maximizes the energy because the two attracting particles are on opposite sides of the sphere.
+
+In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions.
+\cite{Hiscock_2014, Burton_2019, Burton_2019a} All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
+The dotted curves corresponds to the holomorphic domain of the energies.
+
+\section{Radius of convergence and exceptional points}
+
+\subsection{Evolution of the radius of convergence}
+
+In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
+Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
+Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
+To find them we solve simultaneously the following equations: \cite{Cejnar_2007}
 \begin{subequations}
 \begin{align}
-	\hT		& = - t \sum_{\sigma=\updw} (\hc{1\sigma}{\dag} \hc{2\sigma}{} + \hc{2\sigma}{\dag} \hc{1\sigma}{}),
+	\label{eq:PolChar}
+	\det[E\hI-\hH(\lambda)] & = 0,
 	\\ 
-	\hW	& =  U (\hn{1\up}\hn{1\dw} + \hn{2\up}\hn{2\dw}),
-	\\
-	\hV	& = \Dv (\hn{2} - \hn{1})/2,
+	\label{eq:DPolChar}
+	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
 \end{align}
 \end{subequations}
-where $\hn{i\sigma} = \hc{i\sigma}{\dag} \hc{i\sigma}{}$, $\hn{i} = \sum_{\sigma=\updw} \hn{i\sigma}$,  $U$ is the site energy, $t$ is hopping parameter, and $\Dv$ is the difference of on-site potential which controls the asymmetry of the model.
-Note that $\n{1} + \n{2} = \Ne$, where $\Ne = 2$.
+where $\hI$ is the identity operator.
+Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system.
+If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy is, at least two-fold degenerate.
+In this case the energies obtained are dependent of $\lambda$.
+Thus, solving these equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
+These degeneracies can be conical intersections between two states with different symmetry for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
 
-In the basis $\ket{1\up1\dw}$, $\ket{1\up2\dw}$, $\ket{2\up1\dw}$, $\ket{2\up2\dw}$, the Hamiltonian reads
+Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
+Hence, we can forget about the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
+In the restricted formalism the spatial orbitals are the same so the two-electron basis set can be defined as
+
+\begin{align}\label{eq:rhfbasis}
+ \psi_1 & =Y_{0}(\theta_1)Y_{0}(\theta_2),
+ & 
+ \psi_2 & =Y_{0}(\theta_1)Y_{1}(\theta_2),\\
+ \psi_3 & =Y_{1}(\theta_1)Y_{0}(\theta_2),
+ & 
+ \psi_4 & =Y_{1}(\theta_1)Y_{1}(\theta_2).
+\end{align}
+The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, \ie, $\psi_1$ only interacts with $\psi_4$, and $\psi_2$ with $\psi_3$.
+The two singly-excited states yield, after diagonalization, a spatially anti-symmetric singlet $sp_z$ and a spatially symmetric triplet sp\textsubscript{z} state.
+Hence those states do not have the same symmetry as the spatially symmetric singlet ground state.
+Thus, these states cannot be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
+However there is an avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states which gives two EPs in the complex plane.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
+    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
+    One can clearly see the avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states around $\lambda = 1$.}
+    \label{fig:RHFMiniBas}
+\end{figure}
+
+To simplify the problem, it is convenient to only consider basis functions of a given symmetry.
+Such basis functions are called configuration state functions (CSFs).
+It simplifies greatly the problem because, with such a basis set, one only gets the degeneracies of interest associated with the convergence properties, \ie, the EPs between states with the same symmetry as the ground state.
+In the present context, the ground state is a totally symmetric singlet.
+According to angular momentum theory, \cite{AngularBook, SlaterBook, Loos_2009} we expand the exact wave function in the following two-electron basis:
 \begin{equation}
-	\hH = 
-	\begin{pmatrix}
-	- \Dv + U	&	-t	&	t	&	0		\\
-	-t			&	0	&	0	&	-t		\\
-	t			&	0	&	0	&	t		\\
-	0			&	-t	&	t	&	\Dv + U	\\
-	\end{pmatrix},
+\Phi_\ell(\omega)=\frac{\sqrt{2\ell+1}}{4\pi R^2}P_\ell(\cos\omega),
 \end{equation}
-which are composed by three singlet and one triplet states.
-The ground-state singlet wave function can therefore be written as
-\begin{equation}
-	\ket*{^{1}\Psi} = \alpha \frac{\ket{1\up2\dw} + \ket{2\up1\dw}}{\sqrt{2}} + \beta \ket{1\up1\dw} + \gamma \ket{2\up2\dw}
+where $P_\ell$ are Legendre polynomials.
+
+Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
+Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (\ie, consisting of $P_0$ and $P_1$) of size $K = 2$, and in the same basis augmented with $P_2$ ($K = 3$).
+We see that, for the SC partitioning, $R_{\text{CV}}$ increases with $R$ whereas it is decreasing for the three others partitioning.
+This result is expected because the MP, EN, and WC partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
+On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, \ie, when $R$ is large in the spherium model.
+
+Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$.
+
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
+    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
+    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
+    \label{fig:RadiusPartitioning}
+\end{figure}
+
+The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
+In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
+This is not the case for the MP series.
+Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
+It seems that the EN is better than MP for very small $R$ in the minimal basis.
+In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
+It holds true for $K>3$.
+
+Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the size of the basis set.
+The CSFs have all the same spin and spatial symmetries so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
+Table \ref{tab:SingAlpha} shows that the singularities considered in this case are indeed $\alpha$ singularities.
+This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} who stated that $\alpha$ singularities are relatively insensitive to the basis set size.
+The discontinuities observed in Fig.~\ref{fig:RadiusBasis} for the MP partitioning are due to changes in dominant singularity.
+We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative planes.
+
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
+    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
+    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
+    \label{fig:RadiusBasis}
+\end{figure}
+
+\begin{table}
+\footnotesize
+\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
+\begin{tabular}{cccccccc}
+\hline
+\hline
+$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
+\hline
+MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
+WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
+\hline
+\hline
+\end{tabular}
+\label{tab:SingAlpha}
+\end{table}
+
+\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
+
+Now, we investigate the differences in the singularity structure between the RHF and UHF formalism.
+To do so, we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
+Thus, the UHF two-electron basis is
+\begin{align}\label{eq:uhfbasis}
+ \psi_1 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,1}(\theta_2),
+ & 
+ \psi_2 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,2}(\theta_2),\\
+ \psi_3 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,1}(\theta_2),
+ & 
+ \psi_4 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,2}(\theta_2).
+\end{align}
+with the symmetry-broken orbitals
+\begin{subequations}
+\begin{align}\label{eq:uhforbitals}
+ 	\phi_{\alpha,1}(\theta) 
+ 		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+ 		+ \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
+ \\ 
+ 	\phi_{\beta,1}(\theta) 
+		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+		- \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
+ \\
+	 \phi_{\alpha,2}(\theta) 
+	 & = - \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+	  + \frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta),
+ \\
+	 \phi_{\beta,2}(\theta) 
+	 & =\frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+	 +\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta).
+\end{align}
+\end{subequations}
+
+In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
+The matrix elements of the Hamiltonian corresponding to this interaction are
+\begin{equation}\label{eq:MatrixElem}
+	H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{R-\frac{3}{2}}\sqrt{R+\frac{75}{62}}\qty(R+\frac{25}{2})\frac{\sqrt{31}}{70R^3}
 \end{equation}
-with $\alpha^2 + \beta^2 + \gamma^2 = 1$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Concluding remarks}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\titou{What we have done is completely amazing.}
+For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
+This interaction corresponds to the spin contamination of the wave function.
+For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated later.
+The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
+We will refer to the domain where the matrix elements are complex as the holomorphic domain.
+
+The singularity structure in this case is more complex because of the spin contamination of the wave function.
+We can not use CSFs in this case.
+So when one compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
+The numerical distinction of those singularities is very difficult.
+We will first look at the energies $E(\lambda)$ obtained with this basis set to attribute a physical signification to the singularities obtained numerically.
+Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
+We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
+Those avoided crossings are due to the spin contamination of the wave function.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
+    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
+    \label{fig:UHFMiniBas}
+\end{figure}
+
+Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
+For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
+And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
+However, in spherium, the electrons cannot be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson.
+\cite{Sergeev_2005} We can see in Fig.~\ref{fig:UHFEP} that the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet states are degenerated for $R=3/2$.
+For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are $moved$ in the complex plane.
+The wave function is spin contaminated by $Y_1$ for $R>3/2$ this is why the s\textsuperscript{2} singlet energy cannot cross the sp\textsubscript{z} triplet curves anymore.
+When $R$ increases this avoided crossing becomes sharper.
+As presented before $\beta$ singularities are linked to quantum phase transition so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
+The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
+The sharp avoided crossing between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is not present on Fig.
+\ref{fig:UHFEP}.
+The second pair of $\beta$ singularities resulting from this avoided crossing appears for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
+    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
+    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
+    \label{fig:UHFEP}
+\end{figure}
+
+As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
+Therefore the Hamiltonian becomes non-Hermitian for these values of $R$.
+In Ref.~\onlinecite{Burton_2019a}, Burton \textit{et al.}~proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
+An analog reasoning can be done with the spherium model to prove the same result.
+The \pt -symmetry (invariance with respect to combined space reflection $\mathcal{P}$ and time reversal $\mathcal{T}$) is a property which ensures that a non-Hermitian Hamiltonian has a real energy spectrum.
+\cite{BenderPTBook} Thus \pt -symmetric Hamiltonians can be seen as an intermediate class between Hermitian and non-Hermitian Hamiltonians.
+
+Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when $R$ is in the holomorphic domain.
+The domain of values where the energy becomes complex is called the broken \pt-symmetry region.
+This is consistent with the fact that in the holomorphic domain the Hamiltonian is no more \pt -symmetric.
+
+For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
+In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
+This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
+
+\begin{figure}[h!]
+    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
+    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
+    \caption{Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
+    \label{fig:UHFPT}
+\end{figure}
+
+\section{Conclusion}
+
+In order to model accurately chemical systems, one must choose, in a ever growing zoo of methods, which computational protocol is adapted to the system of interest.
+This choice can be, moreover, motivated by the type of properties that one is interested in.
+That means that one must understand the strengths and weaknesses of each method, \ie, why one method might fail in some cases and work beautifully in others. 
+We have seen that for methods relying on perturbation theory, their successes and failures are directly connected to the position of EPs in the complex plane. 
+Exhaustive studies have been performed on the causes of failure of MP perturbation theory. 
+First, it was understood that, for chemical systems for which the HF Slater determinant is a poor approximation to the exact wave function, MP perturbation theory fails too.
+Such systems can be, for example, molecules where the exact ground-state wave function is dominated by more than one configuration, \ie, multi-reference systems.
+More preoccupying cases were also reported. 
+For instance, it has been shown that systems considered as well-understood (\eg, \ce{Ne}) can exhibit divergent behavior when the basis set is augmented with diffuse functions. 
+Later, these erratic behaviors of the perturbation series were investigated and rationalized in terms of avoided crossings and singularities in the complex plane.
+It was shown that the singularities can be classified in two families.
+The first family includes $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly-excited states. 
+The $\beta$ singularities, which constitutes the second family, are artifacts generated by the incompleteness of the Hilbert space, and they are directly connected to an ionization phenomenon occurring in the complete Hilbert space.
+These singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state. 
+We have found that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
+Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking, and theoretical physics have demonstrated that the behavior of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).
+
+In this work, we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the UHF wave function. 
+This confirms that $\beta$ singularities can occur for other types of transition and symmetry breaking than just the formation of a bound cluster of electrons. 
+It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure. 
+Moreover the singularity structure in the non-Hermitian case still need to be investigated. 
+In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
+Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
+%More generally, to investigate the effect of the type of basis on the physics of EPs.
+To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%H.G.A.B.~thanks the Cambridge and Commonwealth Trust for a studentship. 
+This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-12 Manuscript/EPAWTFT.tex
update review

@@
 \newcommand{\bH}{\mathbf{H}}
+\newcommand{\bV}{\mathbf{V}}
 \newcommand{\bh}{\mathbf{h}}
@@
 
-\title{Perturbation theory in the complex plane}
-%\title{Exceptional points and where to find them}
+\title{Perturbation theory in the complex plane: Exceptional points and where to find them}
 
@@
 \affiliation{\UCAM}
-\author{Paola \surname{Gori-Giorgi}}
-\affiliation{\VU}
+%\author{Paola \surname{Gori-Giorgi}}
+%\affiliation{\VU}
 \author{Pierre-Fran\c{c}ois \surname{Loos}}
@@
 \begin{abstract}
-In this work, we explore the extension of quantum chemistry in the complex plane.
+In this review, we explore the extension of quantum chemistry in the complex plane. 
 We observe that the physics of a quantum system is intimately connected to the position of the energy singularities in the complex plane. 
-After a brief presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
-Then we connect and further discuss these different aspects using the spherium model (\ie, two opposite-spin electrons restricted to remain on the surface of a sphere) as a theoretical playground.
-In particular, we explore various perturbative partitioning strategies and the effects of symmetry breaking on the singularity structure of the electronic energy.
-This provides fundamental insights on the location of these singularities in the complex plane (that one calls exceptional points) and, specifically, on the magnitude of the radius of convergence associated with the perturbative treatment.
+After a presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
 \end{abstract}
@@
 
-%============================================================%
+%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 \label{sec:intro}
-%============================================================%
+%%%%%%%%%%%%%%%%%%%%%%%
 
+%======================%
 \subsection{Background}
+%=======================%
 
@@
 The realization that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
-One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019}
+One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019,Burton_2019a}
 
@@
 Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
-\cite{Bittner_2012, Chong_2011, Chtchelkatchev_2012, Doppler_2016, Guo_2009, Hang_2013, Liertzer_2012, Longhi_2010, Peng_2014, Peng_2014a, Regensburger_2012, Ruter_2010, Schindler_2011, Szameit_2011, Zhao_2010, Zheng_2013, Choi_2018, El-Ganainy_2018}
+\cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
 
-Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate. \cite{Heiss_1990,Heiss_1999,Heiss_2012,Heiss_2016}
+Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate.
+\cite{MoiseyevBook,Heiss_1988,Heiss_1990,Heiss_1999,Berry_2011,Heiss_2012,Heiss_2016,Benda_2018}
 They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
@@
 For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+\cite{MoiseyevBook,Heiss_2016,Benda_2018}
 Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
@@
 More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
-\cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019}
+\cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019,Mihalka_2017a,Mihalka_2017b,Mihalka_2019}
 
+%===================================%
 \subsection{An illustrative example}
+%===================================%
 In order to highlight the general properties of EPs mentioned above, we propose to consider the following $2 \times 2$ Hamiltonian commonly used in quantum chemistry
@@
 This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
-Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the starting wave function.
+Additionally, the wave function picks up a geometric phase and four loops are required to recover the starting wave function.
 \cite{MoiseyevBook}
 
-%The eigenvectors associated to the eigenenergies \eqref{eq:E_2x2} are
-%\begin{equation}\label{eq:phi_2x2}
-%\begin{split}
-%	\phi_{\pm}
-%	& = 
-%	\begin{pmatrix}
-%		(\epsilon_1 - \epsilon_2 \pm \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2})/2\lambda 
-%		\\ 
-%		1
-%	\end{pmatrix}
-%	\\
-%	=
-%	\begin{pmatrix}
-%		(\epsilon_1-\epsilon_2)/2\lambda \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}}/\lambda 
-%		\\ 
-%		1
-%	\end{pmatrix},
-%\end{split}
-%\end{equation}
-%and, for $\lambda=\lambda_\text{EP}$, they become
-%\begin{equation}
-%	\phi_{\pm} = \begin{pmatrix} \mp i \\ 1\end{pmatrix},
-%\end{equation}
-%which are clearly self-orthogonal, \ie, their norm is equal to zero. 
-%
-%As branch point (square-root) singularities, EPs inherit their topology from the multi-valued function $\sqrt{\lambda - \lambda_\text{EP}}$. 
-%Then, if the eigenvectors are properly normalized, they behave as $(\lambda - \lambda_\text{EP})^{-1/4}$, which gives the following pattern when looping around one EP:
-%\begin{align}
-%	\phi_{\pm}(2\pi) & = \phi_{\mp}(0), 
-%	&
-%	\phi_{\pm}(4\pi) & = -\phi_{\pm}(0), \notag
-%	\\
-%	\phi_{\pm}(6\pi) & = -\phi_{\mp}(0),
-%	&
-%	\phi_{\pm}(8\pi) & = \phi_{\pm}(0).\notag
-%\end{align}
-%In plain words, four loops around the EP are necessary to recover the initial state. 
-%We can also see that looping the other way around leads to a different pattern.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Perturbation theory}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %============================================================%
-\section{Perturbation theory}
+\subsection{Rayleigh-Schr\"odinger perturbation theory}
 %============================================================%
-
-\subsection{Rayleigh-Schr\"odinger perturbation theory}
 
@@
 The ``physical'' system of interest is recovered by setting the coupling parameter $\lambda$ to unity.
-This decomposition is obviously non-unique and motivated by several factors as discussed below.
+This decomposition is obviously non-unique and motivated by several factors as discussed below. \cite{Mihalka_2017b}
 
@@
 
+%============================================================%
 \subsection{The Hartree-Fock Hamiltonian}
+%============================================================%
 
@@
 \end{equation}
-%Note that the lowest eigenvalue of the Hamiltonian \eqref{eq:HFHamiltonian} is not the HF energy but the sum of the eigenvalues associated with the occupied eigenvalues (see below).
 
@@
 \begin{equation}
-	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\frac{1}{\abs{\vb{r}_1 - \vb{r}_2}}\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)
+	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\frac{\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)}{\abs{\vb{r}_1 - \vb{r}_2}}
 \end{equation}
-is a two-electron integral in the spin-orbital basis.
+are two-electron integral in the spin-orbital basis. \cite{Gill_1994}
 
@@
 
-\subsection{Alternative partitioning}\label{sec:AlterPart}
+Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
+i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
+Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
+ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
+iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
 
-Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility. 
-Here, we will consider three alternative partitioning schemes:
-\begin{itemize}
-	\item The Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. 
-	Hence, the off-diagonal elements of $\hH$ are the perturbation operator.
-	\item The weak correlation (WC) partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$.
-	\item The strong coupling (SC) partitioning where the two operators are inverted compared to the WC partitioning. \cite{Seidl_2018}
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Historical overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%============================================================%
-\section{Historical overview}
-%============================================================%
-
+%=====================================================%
 \subsection{Behavior of the M{\o}ller-Plesset series}
+%=====================================================%
 
@@
 
-When a bond is stretched, in most cases the exact wave function becomes more and more multi-reference. Yet the HF wave function is restricted to be a single Slater determinant.
-Thus, it is inappropriate to model (even qualitatively) stretched systems.
-Nevertheless, the HF wave function can undergo a symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function during the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
+When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
+Yet the HF wave function is restricted to be a single Slater determinant.
+It is then inappropriate to model (even qualitatively) stretched systems.
+Nevertheless, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
 One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
-However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly converging behavior that one would wish for.
+However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behavior that one would wish for.
 
@@
 \cite{Gill_1988}
-Handy and coworkers reported the same behavior of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2} systems.
-\cite{Handy_1985} Lepetit \textit`{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference.
+Handy and coworkers reported the same behavior of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
+\cite{Handy_1985} Lepetit \textit{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference.
 \cite{Lepetit_1988}
@@
 They highlighted that \cite{Cremer_1996}
-\begin{quote}
 \textit{``Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-\end{quote}
 As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without classes.
-The mean deviation from FCI correlation energies is $0.3$ millihartree with the adapted formula whereas with the formula that do not distinguish the systems it is 12 millihartree.
-Even if there were still shaded areas and that this classification was incomplete, this work showed that understanding the origin of the different modes of convergence would lead to a more rationalized use of the MP perturbation theory and to more accurate correlation energies.
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalized use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 
+%===============================%
 \subsection{Cases of divergence}
+%===============================%
 
@@
 Their method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities.
-Then, by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ Hamiltonian
+Then, by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ matrix
 \begin{equation}
-\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\hH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\hH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\hV},
+\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\bH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\bV},
 \end{equation}
-where the diagonal matrix is the unperturbed Hamiltonian and the other matrix is the perturbation.
+where the diagonal matrix is the unperturbed Hamiltonian matrix $\bH^{(0)}$ and the second matrix in the right-hand-side $\bV$ is the perturbation.
 See also Ref.~\onlinecite{Olsen_2019} where the present model is generalized to a non-symmetric (i.e, non-Hermitian) Hamiltonian.
@@
 They first studied molecules with low-lying doubly-excited states of the same spatial and spin symmetry.
-% \titou{because in those systems the HF wave function is a bad approximation.} 
 The exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states were good candidates for being intruder states.
-For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
-They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
+\titou{For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
+They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.}
 
@@
 
+%=======================================
 \subsection{The singularity structure}
-
+%=======================================
 In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
@@
     \overbrace{-\frac{1}{2}\grad_i^2 
-    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}^{\text{Independent of $\lambda$}}
+    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}^{\text{independent of $\lambda$}}
     \\
-    + \underbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}_{\text{Repulsive for $\lambda < 1$}}
-    + \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{Attractive for $\lambda < 0$}}
+    + \underbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}_{\text{repulsive for $\lambda < 1$}}
+    + \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{attractive for $\lambda < 0$}}
     \Bigg].
@@
 
-The major difference between those two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
+The major difference between these two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
 If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
@@
 At this point the system undergo a phase transition and a symmetry breaking.
-Beyond $\lambda_c$ there is a continuum of eigenstates with electrons dissociated from the nucleus.
+Beyond $\lambda_c$ there is a continuum of eigenstates thanks to which the electrons dissociated from the nuclei.
 
@@
 This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry. 
-To the best our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
-In this work, we shall try to improve our understanding of the effect of symmetry breaking on the singularities of $E(\lambda)$ and we hope that it will lead to a deeper understanding of perturbation theory.
+To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
 
-\subsection{The physics of quantum phase transition}
+%====================================================
+\subsection{The physics of quantum phase transitions}
+%====================================================
 
@@
 Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
-\cite{Heiss_1988, Heiss_2002, Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017} In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter.
+\cite{Heiss_1988,Heiss_2002,Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017} In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter.
 In some cases the variation of a parameter can lead to abrupt changes at a critical point.
@@
 
-%============================================================%
-\section{The spherium model}\label{sec:spherium}
-%============================================================%
-
-Simple systems that are analytically solvable (or at least quasi-exactly solvable, \ie, models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
-These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
-To investigate the physics of EPs we consider one such system named \textit{spherium}. 
-It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. \cite{Thompson_2005, Seidl_2007, Loos_2009b} 
-Thus, the Hamiltonian is
-\begin{equation}
-	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}},
-\end{equation}
-or
-\begin{equation} \label{eq:H-sph-omega}
-	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
-\end{equation}
-where $\omega$ is the interelectronic angle.
-The Laplace operators are the kinetic operators for each electrons and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
-Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
-The radius of the sphere $R$ dictates the correlation regime. \cite{Loos_2009}
-In the weak correlation regime (\ie, small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
-For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
-This phenomenon is sometimes referred to as a Wigner crystallization. \cite{Wigner_1934}
-
-We will use this model in order to rationalize the effects of the parameters that may influence the physics of EPs:
-\begin{itemize}
-	\item Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
-	\item Basis set: minimal basis or infinite (\ie, complete) basis.
-	\item Radius of the sphere that ultimately dictates the correlation regime.
-\end{itemize}
-
-In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
-The spatial part of the RHF wave function is then
-\begin{equation}\label{eq:RHF_WF}
-	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
-\end{equation}
-where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
-Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
-
-The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
-Within the UHF formalism, there is a critical value of $R$, called Coulson-Fischer point, \cite{Coulson_1949} at which a UHF solution appears and is lower in energy than the RHF one.
-The UHF solution has broken symmetry because the two electrons tends to localize on opposite sides of the sphere. 
-The spatial part of the UHF wave function is defined as
-\begin{equation}\label{eq:UHF_WF}
-	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2),
-\end{equation}
-where $\phi_\sigma(\theta)$ is the spatial orbital associated with the spin-$\sigma$ electrons ($\sigma = \alpha$ for spin-up electrons and $\sigma = \beta$ for spin-down electrons).
-These one-electron orbitals are expanded in the basis of zonal spherical harmonics
-\begin{equation}
-	\phi_\sigma(\theta)=\sum_{\ell=0}^{\infty}C_{\sigma,\ell}Y_{\ell}(\theta)
-\end{equation}
-It is possible to obtain the formula for the HF energy in this basis set: \cite{Loos_2009}
-\begin{equation}
-	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}},
-\label{eq:EHF}
-\end{equation}
-where the kinetic and potential energies are, respectively,
-\begin{align}
-	T_{\text{HF}} & = \frac{1}{R^2} \sum_{\sigma=\alpha,\beta} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1),
-	&
-	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty}
-	v^\alpha_{L} v^\beta_{L},
-\end{align}
-and
-\begin{equation}
-	v^\sigma_{L} 
-	=  \sum_{\ell_1,\ell_2} \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
-	\begin{pmatrix}
-		\ell_1 & \ell_2 & L 
-		\\
-		0 & 0 & 0
-	\end{pmatrix}^2 
-\end{equation}
-is expressed in terms of the Wigner 3j-symbols. \cite{AngularBook}
-
-The general method is to use a self-consistent field procedure as described in Ref.~\onlinecite{SzaboBook} to get the coefficients of the HF wave function corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, \ie,
-\begin{equation}
-	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
-\end{equation}
-Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a s and p\textsubscript{z} orbital, to illustrate the difference between the RHF and UHF solutions.
+%%============================================================%
+%\section{The spherium model}
+%\label{sec:spherium}
+%%============================================================%
+%
+%Simple systems that are analytically solvable (or at least quasi-exactly solvable, \ie, models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
+%These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
+%To investigate the physics of EPs we consider one such system named \textit{spherium}. 
+%It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. \cite{Thompson_2005, Seidl_2007, Loos_2009b} 
+%Thus, the Hamiltonian is
+%\begin{equation}
+%	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}},
+%\end{equation}
+%or
+%\begin{equation} \label{eq:H-sph-omega}
+%	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
+%\end{equation}
+%in term of the interelectronic angle $\omega$.
+%The Laplace operators are the kinetic operators for each electron and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
+%Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
+%The radius of the sphere $R$ dictates the correlation regime. \cite{Loos_2009}
+%In the weak correlation regime (\ie, small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
+%For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
+%This phenomenon is sometimes referred to as a Wigner crystallization. \cite{Wigner_1934}
+%
+%We will use this model in order to rationalize the effects of the parameters that may influence the physics of EPs:
+%i) Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
+%ii) Basis set: minimal basis or infinite (\ie, complete) basis.
+%iii) Radius of the sphere that ultimately dictates the correlation regime.
+%
+%In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
+%The spatial part of the RHF wave function is then
+%\begin{equation}\label{eq:RHF_WF}
+%	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
+%\end{equation}
+%where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
+%Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
+%
+%The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
+%Within the UHF formalism, there is a critical value of $R$, called Coulson-Fischer point, \cite{Coulson_1949} at which a UHF solution appears and is lower in energy than the RHF one.
+%The UHF solution has broken symmetry because the two electrons tends to localize on opposite sides of the sphere. 
+%The spatial part of the UHF wave function is defined as
+%\begin{equation}\label{eq:UHF_WF}
+%	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2),
+%\end{equation}
+%where $\phi_\sigma(\theta)$ is the spatial orbital associated with the spin-$\sigma$ electrons ($\sigma = \alpha$ for spin-up electrons and $\sigma = \beta$ for spin-down electrons).
+%These one-electron orbitals are expanded in the basis of zonal spherical harmonics
+%\begin{equation}
+%	\phi_\sigma(\theta)=\sum_{\ell=0}^{\infty}C_{\sigma,\ell}Y_{\ell}(\theta).
+%\end{equation}
+%It is possible to obtain the formula for the HF energy in this basis set: \cite{Loos_2009}
+%\begin{equation}
+%	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}},
+%\label{eq:EHF}
+%\end{equation}
+%where the kinetic and potential energies are, respectively,
+%\begin{align}
+%	T_{\text{HF}} & = \frac{1}{R^2} \sum_{\sigma=\alpha,\beta} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1),
+%	&
+%	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty}
+%	v^\alpha_{L} v^\beta_{L},
+%\end{align}
+%and
+%\begin{equation}
+%	v^\sigma_{L} 
+%	=  \sum_{\ell_1,\ell_2} \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
+%	\begin{pmatrix}
+%		\ell_1 & L & \ell_2 
+%		\\
+%		0 & 0 & 0
+%	\end{pmatrix}^2 
+%\end{equation}
+%is expressed in terms of the Wigner 3j-symbols. \cite{AngularBook}
+%
+%The general method is to use a self-consistent field procedure as described in Ref.~\onlinecite{SzaboBook} to get the coefficients of the HF wave function corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, \ie,
+%\begin{equation}
+%	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
+%\end{equation}
+%Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a $s$ and $p_{z}$ orbital, to illustrate the difference between the RHF and UHF solutions.
 In this basis there is a shortcut to find the stationary solutions and ensure normalization of the orbitals.
 One can define the one-electron orbitals as
-\begin{equation}
-	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta),
-\end{equation}
-using a mixing angle between the two basis functions for each spin manifold. 
-Hence, one has just to minimize/maximize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
-
-This process provides the three following solutions valid for all value of $R$, which are respectively a minimum, a maximum and a saddle point of the HF equations:
-\begin{itemize}
-\item The two electrons are in the s orbital which is a RHF solution. This solution is associated with the energy $1/R$.
-\item The two electrons are in the p\textsubscript{z} orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$.
-\item One electron is in the s orbital and the other is in the p\textsubscript{z} orbital which is a UHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
-\end{itemize}
-
-In addition, the minimization process gives also the well-known symmetry-broken UHF (sb-UHF) solution.
-In this case the Coulson-Fischer point associated to this solution is $R=3/2$.
-For $R>3/2$ the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
+%\begin{equation}
+%	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta),
+%\end{equation}
+%using a mixing angle $\chi_\sigma$ between the two basis functions for each spin manifold. 
+%Hence, one has just to minimize/maximize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
+% 
+%This process provides the three following solutions valid for all value of $R$, which are respectively a minimum, a maximum and a saddle point of the HF equations:
+%i) the two electrons are in the $s$ orbital which is a RHF solution. This solution is associated with the energy $1/R$;
+%ii) the two electrons are in the $p_{z}$ orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$;
+%iii) one electron is in the $s$ orbital and the other is in the $p_{z}$ orbital which is a UHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
+%
+%In addition, the minimization process gives also the well-known symmetry-broken UHF (sb-UHF) solution. In this case the Coulson-Fischer point associated to this solution is $R=3/2$. 
+%For $R>3/2$, the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
 This solution corresponds to the configuration with the spin-up electron in an orbital on one side of the sphere and the spin-down electron in a miror-image orbital on the opposite side and the configuration the other way round.
-The electrons can be on opposite sides of the sphere because the choice of p\textsubscript{z} as a basis function induced a privileged axis on the sphere for the electrons.
+The electrons can be on opposite sides of the sphere because the choice of $p_{z}$ as a basis function induced a privileged axis on the sphere for the electrons.
 For $R>3/2$, this solution has the energy
-\begin{equation}\label{eq:EsbUHF}
-	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}.
-\end{equation}
-
-The exact solution for the ground state is a singlet.
-The spherical harmonics are eigenvectors of $\hS^2$ (the spin operator) and they are associated to different eigenvalues.
-Yet, the symmetry-broken orbitals are linear combinations of $Y_0$ and $Y_1$.
-Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$.
-However, this solution gives lower energies than the RHF one at large $R$ as shown in Table \ref{tab:ERHFvsEUHF} even if it does not have the exact spin symmetry.
-In fact, at the Coulson-Fischer point, it becomes more effective to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy.
-Thus, within the HF approximation, the variational principle is allowed to break the spin symmetry because it yields a more effective minimization of the Coulomb repulsion.
-This type of symmetry breaking is called a spin density wave because the system oscillates between the two symmetry-broken configurations.
-\cite{GiulianiBook}
-
-\begin{table*}
-\caption{RHF and sb-UHF energies in the minimal basis and exact energies (in the complete basis) for various $R$.
-\label{tab:ERHFvsEUHF}}
-\begin{ruledtabular}
-\begin{tabular}{ccccccccc}
-$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 & 1000 \\
-\hline
-RHF 	& 10.00000 & 1.000000 & 0.500000 & 0.333333 & 0.200000 & 0.100000 & 0.010000 & 0.001000 \\
-UHF 	& 10.00000 & 1.000000 & 0.490699 & 0.308532 & 0.170833 & 0.078497 & 0.007112 & 0.000703 \\
-Exact 	& 9.783874 & 0.852781 & 0.391959 & 0.247898 & 0.139471 & 0.064525 & 0.005487 & 0.000515 \\
-\end{tabular}
-\end{ruledtabular}
-\end{table*}
-
-There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations.
-This solution is associated with another type of symmetry breaking somewhat less known.
-It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital.
-This solution is called symmetry-broken RHF (sb-RHF).
-The reasoning is counter-intuitive because the electrons tends to maximize their energy.
-The p\textsubscript{z} orbital is symmetric with respect to the center of the sphere.
-If the orbitals are symmetric, the maximum is when the two electrons are in the p\textsubscript{z} orbital because it maximizes the kinetic energy.
-At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital \ie, on the same side of the sphere gives a superior energy than the p\textsubscript{z}\textsuperscript{2} state.
-Adding a s orbital on one side of the p\textsubscript{z} orbital to form a symmetry-broken orbital reduce the kinetic energy but increase the repulsion energy as the two electrons are more localized on one side of the sphere.
-It becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$.
-This configuration breaks the spatial symmetry of charge.
-Hence this symmetry breaking is associated with a charge density wave, the system oscillates between the situations with the two electrons on each side.
-\cite{GiulianiBook}
-The energy associated with this sb-RHF solution reads
-\begin{equation}
-E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}.
-\end{equation}
-\begin{figure}
-    \includegraphics[width=\linewidth]{EsbHF.pdf}
-    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
-    \label{fig:SpheriumNrj}
-\end{figure}
-
-We can also consider negative values of $R$, which corresponds to the situation where one of the electrons is replaced by a positron (the anti-particle of the electron) as readily seen in Eq.~\eqref{eq:H-sph-omega}.
-For negative $R$ values, there are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
-Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere.
-And the sb-UHF state maximizes the energy because the two attracting particles are on opposite sides of the sphere.
-
-In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions.
+%\begin{equation}\label{eq:EsbUHF}
+%	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}.
+%\end{equation}
+%
+%The exact solution for the ground state is a singlet. The spherical harmonics are eigenvectors of $\hS^2$ (the spin operator) and they are associated to different eigenvalues. 
+%Yet, the symmetry-broken orbitals are linear combinations of $Y_0$ and $Y_1$. 
+%Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$. 
+%However, this solution gives lower energies than the RHF one at large $R$, even if it does not have the exact spin symmetry. 
+%In fact, at the Coulson-Fischer point, it becomes more effective to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy. 
+%Thus, within the HF approximation, the variational principle is allowed to break the spin symmetry because it yields a more effective minimization of the Coulomb repulsion. 
+%This type of symmetry breaking is also called a spin-density wave in the physics community as the system ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
+%
+%There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations. 
+%This solution is associated with another type of symmetry breaking somewhat less known. 
+%It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital. 
+%This solution is called symmetry-broken RHF (sb-RHF). The reasoning is counter-intuitive because the electrons tends to maximize their energy. 
+%The $sp_{z}$ orbital is symmetric with respect to the center of the sphere. 
+%If the orbitals are symmetric, the maximum is when the two electrons are in the $p_{z}$ orbital because it maximizes the kinetic energy. 
+%At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital \ie, on the same side of the sphere gives a superior energy than the $p_{z}^2$ state.
+Adding a s orbital on one side of the $p_{z}$ orbital to form a symmetry-broken orbital reduce the kinetic energy but increase the repulsion energy as the two electrons are more localized on one side of the sphere.
+%It becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$. 
+%This configuration breaks the spatial symmetry of charge. 
+%Hence this symmetry breaking is associated with a charge-density wave as the system oscillates between the situations where the two electrons are one side or the other. \cite{GiulianiBook}
+%The energy associated with this sb-RHF solution reads
+%\begin{equation}
+%E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}.
+%\end{equation}
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{EsbHF.pdf}
+%    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
+%    \label{fig:SpheriumNrj}
+%\end{figure}
+%
+%We can also consider negative values of $R$, which corresponds to the situation where one of the electrons is replaced by a positron as readily seen in Eq.~\eqref{eq:H-sph-omega}. 
+%For negative $R$ values, there are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
+%Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere. 
+%And the sb-UHF state maximizes the energy because the two attracting particles are on opposite sides of the sphere.
+%
+%In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions.
 \cite{Hiscock_2014, Burton_2019, Burton_2019a} All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
 The dotted curves corresponds to the holomorphic domain of the energies.
-
-\section{Radius of convergence and exceptional points}
-
-\subsection{Evolution of the radius of convergence}
-
-In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
+%
+%
+%\section{Radius of convergence and exceptional points}
+%
+%\subsection{Evolution of the radius of convergence}
+%
+%In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
 Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
@@
 To find them we solve simultaneously the following equations: \cite{Cejnar_2007}
-\begin{subequations}
-\begin{align}
-	\label{eq:PolChar}
-	\det[E\hI-\hH(\lambda)] & = 0,
-	\\ 
-	\label{eq:DPolChar}
-	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
-\end{align}
-\end{subequations}
-where $\hI$ is the identity operator.
-Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system.
-If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy is, at least two-fold degenerate.
-In this case the energies obtained are dependent of $\lambda$.
-Thus, solving these equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate.
-These degeneracies can be conical intersections between two states with different symmetry for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
-
-Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
-Hence, we can forget about the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
+%\begin{subequations}
+%\begin{align}
+%	\label{eq:PolChar}
+%	\det[E\hI-\hH(\lambda)] & = 0,
+%	\\ 
+%	\label{eq:DPolChar}
+%	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
+%\end{align}
+%\end{subequations}
+%where $\hI$ is the identity operator.
+%Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system.
+If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy is, at least, two-fold degenerate.
+In this case the energies obtained are  $\lambda$-dependent.
+%Thus, solving these equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate. 
+%These degeneracies can be conical intersections between two states with different symmetries for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
+%
+%Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
+%Hence, we can forget about the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
 In the restricted formalism the spatial orbitals are the same so the two-electron basis set can be defined as
-
-\begin{align}\label{eq:rhfbasis}
- \psi_1 & =Y_{0}(\theta_1)Y_{0}(\theta_2),
- & 
- \psi_2 & =Y_{0}(\theta_1)Y_{1}(\theta_2),\\
- \psi_3 & =Y_{1}(\theta_1)Y_{0}(\theta_2),
- & 
- \psi_4 & =Y_{1}(\theta_1)Y_{1}(\theta_2).
-\end{align}
-The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, \ie, $\psi_1$ only interacts with $\psi_4$, and $\psi_2$ with $\psi_3$.
-The two singly-excited states yield, after diagonalization, a spatially anti-symmetric singlet $sp_z$ and a spatially symmetric triplet sp\textsubscript{z} state.
-Hence those states do not have the same symmetry as the spatially symmetric singlet ground state.
-Thus, these states cannot be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
-However there is an avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states which gives two EPs in the complex plane.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
-    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
-    One can clearly see the avoided crossing between the s\textsuperscript{2} and p\textsubscript{z}\textsuperscript{2} states around $\lambda = 1$.}
-    \label{fig:RHFMiniBas}
-\end{figure}
-
-To simplify the problem, it is convenient to only consider basis functions of a given symmetry.
+%
+%\begin{align}\label{eq:rhfbasis}
+% \psi_1 & =Y_{0}(\theta_1)Y_{0}(\theta_2),
+% & 
+% \psi_2 & =Y_{0}(\theta_1)Y_{1}(\theta_2),\\
+% \psi_3 & =Y_{1}(\theta_1)Y_{0}(\theta_2),
+% & 
+% \psi_4 & =Y_{1}(\theta_1)Y_{1}(\theta_2).
+%\end{align}
+%The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, \ie, $\psi_1$ only interacts with $\psi_4$, and $\psi_2$ with $\psi_3$.
+The two singly-excited states yield, after diagonalization, a spatially anti-symmetric singlet $sp_z$ and a spatially symmetric triplet $sp_{z}$ state.
+%Hence those states do not have the same symmetry as the spatially symmetric singlet ground state. 
+%Thus, these states cannot be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
+%However there is an avoided crossing between the $s^{2}$ and $p_{z}^{2}$ states which gives two EPs in the complex plane. 
+%
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
+%    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
+%    One can clearly see the avoided crossing between the $s^{2}$ and $p_{z}^{2}$ states around $\lambda = 1$.}
+%    \label{fig:RHFMiniBas}
+%\end{figure}
+%
+%To simplify the problem, it is convenient to only consider basis functions of a given symmetry.
 Such basis functions are called configuration state functions (CSFs).
@@
 According to angular momentum theory, \cite{AngularBook, SlaterBook, Loos_2009} we expand the exact wave function in the following two-electron basis:
-\begin{equation}
-\Phi_\ell(\omega)=\frac{\sqrt{2\ell+1}}{4\pi R^2}P_\ell(\cos\omega),
-\end{equation}
-where $P_\ell$ are Legendre polynomials.
-
-Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
+%\begin{equation}
+%\Phi_\ell(\omega)=\frac{\sqrt{2\ell+1}}{4\pi R^2}P_\ell(\cos\omega),
+%\end{equation}
+%where $P_\ell$ are Legendre polynomials.
+%
+%Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
 Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (\ie, consisting of $P_0$ and $P_1$) of size $K = 2$, and in the same basis augmented with $P_2$ ($K = 3$).
@@
 On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, \ie, when $R$ is large in the spherium model.
-
-Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$.
-
-\begin{figure}
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
-    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
-    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
-    \label{fig:RadiusPartitioning}
-\end{figure}
-
-The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
+%
+%Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$. 
+%
+%\begin{figure}
+%    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
+%    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
+%    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
+%    \label{fig:RadiusPartitioning}
+%\end{figure}
+%
+%The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
 In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
 This is not the case for the MP series.
-Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
-It seems that the EN is better than MP for very small $R$ in the minimal basis.
+%Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
+%It seems that the EN is better than MP for very small $R$ in the minimal basis.
 In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
 It holds true for $K>3$.
-
-Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the size of the basis set.
+%
+%
+%Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the size of the basis set.
 The CSFs have all the same spin and spatial symmetries so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
@@
 We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative planes.
-
-\begin{figure}
-    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
-    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
-    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
-    \label{fig:RadiusBasis}
-\end{figure}
-
-\begin{table}
-\footnotesize
-\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
-\begin{tabular}{cccccccc}
-\hline
-\hline
-$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
-\hline
-MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
-WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
-\hline
-\hline
-\end{tabular}
-\label{tab:SingAlpha}
-\end{table}
-
-\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
-
-Now, we investigate the differences in the singularity structure between the RHF and UHF formalism.
+%
+%\begin{figure}
+%    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
+%    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
+%    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
+%    \label{fig:RadiusBasis}
+%\end{figure}
+%
+%\begin{table*}
+%\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
+%\begin{ruledtabular}
+%\begin{tabular}{cccccccc}
+%$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
+%\hline
+%MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
+%WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
+%\end{tabular}
+%\end{ruledtabular}
+%\label{tab:SingAlpha}
+%\end{table*}
+%
+%\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
+%
+%Now, we investigate the differences in the singularity structure between the RHF and UHF formalism.
 To do so, we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
 Thus, the UHF two-electron basis is
-\begin{align}\label{eq:uhfbasis}
- \psi_1 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,1}(\theta_2),
- & 
- \psi_2 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,2}(\theta_2),\\
- \psi_3 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,1}(\theta_2),
- & 
- \psi_4 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,2}(\theta_2).
-\end{align}
-with the symmetry-broken orbitals
-\begin{subequations}
-\begin{align}\label{eq:uhforbitals}
- 	\phi_{\alpha,1}(\theta) 
- 		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
- 		+ \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
- \\ 
- 	\phi_{\beta,1}(\theta) 
-		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
-		- \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
- \\
-	 \phi_{\alpha,2}(\theta) 
-	 & = - \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
-	  + \frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta),
- \\
-	 \phi_{\beta,2}(\theta) 
-	 & =\frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
-	 +\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta).
-\end{align}
-\end{subequations}
-
-In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
+%\begin{align}\label{eq:uhfbasis}
+% \psi_1 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,1}(\theta_2),
+% & 
+% \psi_2 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,2}(\theta_2),\\
+% \psi_3 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,1}(\theta_2),
+% & 
+% \psi_4 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,2}(\theta_2).
+%\end{align}
+%with the symmetry-broken orbitals
+%\begin{subequations}
+%\begin{align}\label{eq:uhforbitals}
+% 	\phi_{\alpha,1}(\theta) 
+% 		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+% 		+ \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
+% \\ 
+% 	\phi_{\beta,1}(\theta) 
+%		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
+%		- \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
+% \\
+%	 \phi_{\alpha,2}(\theta) 
+%	 & = - \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+%	  + \frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta),
+% \\
+%	 \phi_{\beta,2}(\theta) 
+%	 & =\frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
+%	 +\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta).
+%\end{align}
+%\end{subequations}
+%
+%In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
 The matrix elements of the Hamiltonian corresponding to this interaction are
-\begin{equation}\label{eq:MatrixElem}
-	H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{R-\frac{3}{2}}\sqrt{R+\frac{75}{62}}\qty(R+\frac{25}{2})\frac{\sqrt{31}}{70R^3}
-\end{equation}
-
-For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
+%\begin{equation}\label{eq:MatrixElem}
+%	H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{R-\frac{3}{2}}\sqrt{R+\frac{75}{62}}\qty(R+\frac{25}{2})\frac{\sqrt{31}}{70R^3}
+%\end{equation}
+%
+%For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
 This interaction corresponds to the spin contamination of the wave function.
@@
 We will refer to the domain where the matrix elements are complex as the holomorphic domain.
-
-The singularity structure in this case is more complex because of the spin contamination of the wave function.
+%
+%The singularity structure in this case is more complex because of the spin contamination of the wave function.
 We can not use CSFs in this case.
@@
 We will first look at the energies $E(\lambda)$ obtained with this basis set to attribute a physical signification to the singularities obtained numerically.
-Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
-We see that in this case the sp\textsubscript{z} triplet interacts with the s\textsuperscript{2} and the p\textsubscript{z}\textsuperscript{2} singlets.
+%Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
+We see that in this case the $sp_{z}$ triplet interacts with the $s^{2}$ and the $p_{z}^{2}$ singlets.
 Those avoided crossings are due to the spin contamination of the wave function.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
-    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
-    \label{fig:UHFMiniBas}
-\end{figure}
-
-Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
-For example at $R=10$ the pair of singularities connected to the avoided crossing between s\textsuperscript{2} and sp\textsubscript{z} $^{3}P$ is $0.999\pm0.014\,i$.
-And the one between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is connected with the singularities $2.207\pm0.023\,i$.
+%
+%\begin{figure}
+%    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
+%    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
+%    \label{fig:UHFMiniBas}
+%\end{figure}
+%
+%Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
+For example at $R=10$ the pair of singularities connected to the avoided crossing between $s^{2}$ and $sp_{z}$ $^{3}P$ is $0.999\pm0.014\,i$.
+And the one between $sp_{z}$ $^{3}P$ and $p_{z}^{2}$ is connected with the singularities $2.207\pm0.023\,i$.
 However, in spherium, the electrons cannot be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson.
-\cite{Sergeev_2005} We can see in Fig.~\ref{fig:UHFEP} that the s\textsuperscript{2} singlet and the sp\textsubscript{z} triplet states are degenerated for $R=3/2$.
+\cite{Sergeev_2005} We can see in Fig.~\ref{fig:UHFEP} that the $s^{2}$ singlet and the $sp_{z}$ triplet states are degenerated for $R=3/2$.
 For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are $moved$ in the complex plane.
-The wave function is spin contaminated by $Y_1$ for $R>3/2$ this is why the s\textsuperscript{2} singlet energy cannot cross the sp\textsubscript{z} triplet curves anymore.
+The wave function is spin contaminated by $Y_1$ for $R>3/2$ this is why the $s^{2}$ singlet energy cannot cross the $sp_{z}$ triplet curves anymore.
 When $R$ increases this avoided crossing becomes sharper.
@@
 The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
-The sharp avoided crossing between sp\textsubscript{z} $^{3}P$ and p\textsubscript{z}\textsuperscript{2} is not present on Fig.
+The sharp avoided crossing between $sp_{z}$ $^{3}P$ and $p_{z}^{2}$ is not present on Fig.
 \ref{fig:UHFEP}.
 The second pair of $\beta$ singularities resulting from this avoided crossing appears for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
-
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
-    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
-    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
-    \label{fig:UHFEP}
-\end{figure}
-
-As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
+%
+%\begin{figure}
+%    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
+%    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
+%    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
+%    \label{fig:UHFEP}
+%\end{figure}
+%
+%As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
 Therefore the Hamiltonian becomes non-Hermitian for these values of $R$.
@@
 \cite{BenderPTBook} Thus \pt -symmetric Hamiltonians can be seen as an intermediate class between Hermitian and non-Hermitian Hamiltonians.
-
-Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when $R$ is in the holomorphic domain.
+%
+%Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when $R$ is in the holomorphic domain.
 The domain of values where the energy becomes complex is called the broken \pt-symmetry region.
 This is consistent with the fact that in the holomorphic domain the Hamiltonian is no more \pt -symmetric.
-
-For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
+%
+%For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
 In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
 This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
-
-\begin{figure}[h!]
-    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
-    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
-    \caption{Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
-    \label{fig:UHFPT}
-\end{figure}
+%
+%\begin{figure}[h!]
+%    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
+%    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
+%    \caption{Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
+%    \label{fig:UHFPT}
+%\end{figure}
 
@@
 
-In this work, we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the UHF wave function. 
-This confirms that $\beta$ singularities can occur for other types of transition and symmetry breaking than just the formation of a bound cluster of electrons. 
-It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure. 
-Moreover the singularity structure in the non-Hermitian case still need to be investigated. 
-In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
-Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
+%In this work, we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the UHF wave function. 
+%This confirms that $\beta$ singularities can occur for other types of transition and symmetry breaking than just the formation of a bound cluster of electrons. 
+%It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure. 
+%Moreover the singularity structure in the non-Hermitian case still need to be investigated. 
+%In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
+%Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
 It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
 %More generally, to investigate the effect of the type of basis on the physics of EPs.
-To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
+%To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
 

### 2020-11-12 Manuscript/EPAWTFT.tex
Changed HGAB affiliation!
little paragraph on Olsen 2019

@@
 \newcommand{\UCAM}{Department of Chemistry, University of Cambridge, Lensfield Road, Cambridge, CB2 1EW, U.K.}
+\newcommand{\UOX}{Physical and Theoretical Chemical Laboratory, Department of Chemistry, University of Oxford, Oxford, OX1 3QZ, U.K.}
 \newcommand{\VU}{Department of Theoretical Chemistry and Amsterdam Center for Multiscale Modeling, FEW, Vrije Universiteit, De Boelelaan 1083, 1081HV Amsterdam, The Netherlands.}
@@
 \author{Hugh G.~A.~\surname{Burton}}
-\affiliation{\UCAM}
+%\affiliation{\UCAM}
+\affiliation{\UOX}
 %\author{Paola \surname{Gori-Giorgi}}
@@
 where the diagonal matrix is the unperturbed Hamiltonian matrix $\bH^{(0)}$ and the second matrix in the right-hand-side $\bV$ is the perturbation.
-See also Ref.~\onlinecite{Olsen_2019} where the present model is generalized to a non-symmetric (i.e, non-Hermitian) Hamiltonian.
+
+In Ref.~\onlinecite{Olsen_2019}, the simple $2 \times 2$ model proposed by Olsen \textit{et al.} is generalized to a non-symmetric (i.e, non-Hermitian) Hamiltonian and various choice of perturbation (not only the MP partioning).
+Interestingly, they showed that the convergence pattern of a given perturbation method can be characterized by its archetype which defines the overall ``shape'' of the energy convergence and can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
+Other features characterizing the convergence behavior of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
 
@@
 For example, the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly-excited states which results in alternated terms up to 10th order. 
-For higher orders, the series is monotonically convergent.
-This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
+For higher orders, the series is monotonically convergent. This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
 

### 2020-11-12 Manuscript/EPAWTFT.tex
little paragraph on Olsen 2019

@@
 \documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,longtable,txfonts,mhchem}
-
+\usepackage{graphicx,tabularx,array,booktabs,longtable,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\mr}{\multirow}
-\newcommand{\SI}{\textcolor{blue}{supporting information}}
 
@@
 \end{equation}
-are two-electron integral in the spin-orbital basis. \cite{Gill_1994}
+are two-electron integrals in the spin-orbital basis. \cite{Gill_1994}
 
@@
 In fact, it is known that when the HF wave function is a poor approximation to the exact wave function, for example in multi-reference systems, the MP method yields deceptive results.
-\cite{Gill_1986, Gill_1988, Handy_1985, Lepetit_1988}
+\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000}
 A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
@@
 \begin{equation}
-\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha + \alpha_s & 0 \\ 0 & \beta + \beta_s )}_{\bH^{(0)}} + \underbrace{\mqty(- \alpha_s & \delta \\ \delta & - \beta_s)}_{\bV},
+	\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta \\ \delta & - \gamma)}_{\bV},
 \end{equation}
@@
 
-In Ref.~\onlinecite{Olsen_2019}, the simple $2 \times 2$ model proposed by Olsen \textit{et al.} is generalized to a non-symmetric (i.e, non-Hermitian) Hamiltonian and various choice of perturbation (not only the MP partioning).
+In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalized to a non-symmetric Hamiltonian 
+\begin{equation}
+	\underbrace{\mqty(\alpha & \delta_1 \\ \delta_2 & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta_2 \\ \delta_1 & - \gamma)}_{\bV}.
+\end{equation}
+allowing an analysis of various choice of perturbation (not only the MP partioning) such as coupled cluster perturbation expansions and other non-Hermitian perturbation methods.
+It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
 Interestingly, they showed that the convergence pattern of a given perturbation method can be characterized by its archetype which defines the overall ``shape'' of the energy convergence and can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.

### 2020-11-12 Manuscript/EPAWTFT.tex
little paragraph on Olsen 2019

@@
 
-In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalized to a non-symmetric Hamiltonian 
-\begin{equation}
-	\underbrace{\mqty(\alpha & \delta_1 \\ \delta_2 & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta_2 \\ \delta_1 & - \gamma)}_{\bV}.
-\end{equation}
-allowing an analysis of various choice of perturbation (not only the MP partioning) such as coupled cluster perturbation expansions and other non-Hermitian perturbation methods.
-It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
-Interestingly, they showed that the convergence pattern of a given perturbation method can be characterized by its archetype which defines the overall ``shape'' of the energy convergence and can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
-Other features characterizing the convergence behavior of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
-
 They first studied molecules with low-lying doubly-excited states of the same spatial and spin symmetry.
@@
 For higher orders, the series is monotonically convergent. This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
+
+In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalized to a non-symmetric Hamiltonian 
+\begin{equation}
+	\underbrace{\mqty(\alpha & \delta_1 \\ \delta_2 & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta_2 \\ \delta_1 & - \gamma)}_{\bV}.
+\end{equation}
+allowing an analysis of various choice of perturbation (not only the MP partioning) such as coupled cluster perturbation expansions \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} and other non-Hermitian perturbation methods.
+It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
+Interestingly, they showed that the convergence pattern of a given perturbation method can be characterized by its archetype which defines the overall ``shape'' of the energy convergence.
+These so-called archetypes can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
+Importantly, they observed that the the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
+Other features characterizing the convergence behavior of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern;
+the three remaining archetypes seem to be rarely observed in MP perturbation theory.
+However, in the non-Hermitian setting of coupled cluster perturbation theory, \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} on can encounter interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric archetypes.
+One of main take-home messages of Olsen's study is that the primary critical point defines the high-order convergence, irrespective of whether this point is inside or outside the complex unit circle.
+\cite{Handy_1985,Olsen_2000}
 

### 2020-11-13 Manuscript/EPAWTFT.tex

@@
 
-%===============================%
-\subsection{Cases of divergence}
-%===============================%
+Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning.
+\cite{Mihalka_2017a}
+Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of the convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
+In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent series taking again as an example the water molecule in a stretched geometry.
+In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent, and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
+However, the choice of the functional form of the fit remains a subtle task.
+This technique was first generalized by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula
+\begin{equation}
+	\frac{1}{2\pi i} \oint \frac{E(z)}{z - a} = E(a)
+\end{equation}
+instead of the solution of the Laplace equation. \cite{Mihalka_2019}
+
+%==========================================%
+\subsection{Insights from a two-state model}
+%==========================================%
 

### 2020-11-13 Manuscript/EPAWTFT.tex
Added HGAB acknowledgement

@@
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481)
+HGAB gratefully acknowledges New College, Oxford for funding through the Astor Junior Research Fellowship.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-14 Manuscript/EPAWTFT.tex
saving work on Hubbard

@@
 \newcommand{\Dv}{\Delta v}
+
+\newcommand{\ra}{\rightarrow}
 \newcommand{\up}{\uparrow}
 \newcommand{\dw}{\downarrow}
-\newcommand{\updw}{\up\dw}
 
-\newcommand{\ra}{\rightarrow}
-\newcommand{\pt}{$\mathcal{PT}$}
+\newcommand{\updot}{%
+  \mathrel{\ooalign{\hfil$\vcenter{
+    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\uparrow$\cr}
+  }%
+}
+\newcommand{\dwdot}{%
+  \mathrel{\ooalign{\hfil$\vcenter{
+    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\downarrow$\cr}
+  }%
+}
+\newcommand{\vac}{%
+  \mathrel{\ooalign{\hfil$\vcenter{
+    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$ $\cr}
+  }%
+}
+
+\newcommand{\uddot}{%
+  \mathrel{\ooalign{\hfil$\vcenter{
+    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\uparrow\downarrow$\cr}
+  }%
+}
 
@@
 %===================================%
-In order to highlight the general properties of EPs mentioned above, we propose to consider the following $2 \times 2$ Hamiltonian commonly used in quantum chemistry
-
+In order to highlight the general properties of EPs mentioned above, we propose to consider the ubiquitous symmetric Hubbard dimer at half filling (\ie, with two opposite-spin fermions) whose Hamiltonian reads in the singlet configuration state function basis
+%\begin{align}
+%		\ket{1\up1\dw}		&	\ket{1\up2\dw}		&	\ket{1\dw2\up}		&	\ket{2\up2\dw}	\\
+%		\uddot \quad \vac	&	\updot \quad \dwdot	&	\dwdot \quad \updot	&	\vac \quad \uddot	 \\
+%\end{align}
 \begin{equation}
-\label{eq:H_2x2}
+\label{eq:H_FCI}
 	\bH = 
 	\begin{pmatrix}
-		\epsilon_1	&	\lambda	\\
-		\lambda		&	\epsilon_2
+		-2t	+ U &	0 & U/2	\\
+		0		&	U 	&	0	\\
+		U/2 &	0 & -2t	+ U	\\
 	\end{pmatrix},
 \end{equation}
-which represents two states of energies $\epsilon_1$ and $\epsilon_2$ coupled with a strength of magnitude $\lambda$.
-This Hamiltonian could represent, for example, a minimal-basis configuration interaction with doubles (CID) for the hydrogen molecule. \cite{SzaboBook}
+where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.
+We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
+We will consistently use this system to illustrate the different concepts discussed in the present review article.
 
-For real $\lambda$, the Hamiltonian \eqref{eq:H_2x2} is clearly Hermitian, and it becomes non-Hermitian for any complex $\lambda$ value.
-Its eigenvalues are
+For real $U$, the Hamiltonian \eqref{eq:H_FCI} is clearly Hermitian, and it becomes non-Hermitian for any complex $U$ value.
+The eigenvalues associated with its singlet ground state and singlet doubly-excited state are
 \begin{equation}
-\label{eq:E_2x2}
-	E_{\pm} = \frac{\epsilon_1 + \epsilon_2}{2} \pm \frac{1}{2} \sqrt{(\epsilon_1 - \epsilon_2)^2 + 4\lambda^2}.
+\label{eq:E_FCI}
+	E_{\pm} = \frac{1}{2} \qty( U \pm \sqrt{(4t^2) + U^2} ).
 \end{equation}
-%and they are represented as a function of $\lambda$ in Fig.~\ref{fig:2x2}.
-One notices that the two states become degenerate only for a pair of complex conjugate values of $\lambda$
+and they are represented as a function of $U$ in Fig.~\ref{fig:FCI} together with the energy of the singlet open-shell configuration of energy $U$.
+
+%%% FIG 1 %%%
+\begin{figure*}
+	\includegraphics[height=0.3\textwidth]{fig1a}
+	\hspace{0.1\textwidth}
+	\includegraphics[height=0.3\textwidth]{fig1b}	
+	\caption{
+	Exact energies for the Hubbard dimer as functions of $U/t$.
+	\label{fig:FCI}}
+\end{figure*}
+
+One notices that these two states become degenerate only for a pair of complex conjugate values of $U$
 \begin{equation}
 \label{eq:lambda_EP}
-	\lambda_\text{EP} = \pm i\,\frac{\epsilon_1 - \epsilon_2}{2},
+	U_\text{EP} = \pm 4 i t,
 \end{equation}
@@
 \label{eq:E_EP}
-	E_\text{EP} = \frac{\epsilon_1 + \epsilon_2}{2},
+	E_\text{EP} = \pm 2 i t,
 \end{equation}
-which correspond to square-root singularities in the complex-$\lambda$ plane. % (see Fig.~\eqref{fig:2x2}).
-These two $\lambda$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
-Starting from $\lambda_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
-In the real $\lambda$ axis, the point for which the states are the closest ($\lambda = 0$) is called an avoided crossing and this occurs at $\lambda = \Re(\lambda_\text{EP})$.
-The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(\lambda_\text{EP})$: the smaller $\Im(\lambda_\text{EP})$, the sharper the avoided crossing is.
+which correspond to square-root singularities in the complex-$U$ plane [see Fig.~\eqref{fig:FCI}].
+These two $U$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
+Starting from $U_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
+In the real $U$ axis, the point for which the states are the closest ($U = 0$) is called an avoided crossing and this occurs at $U = \Re(U_\text{EP})$.
+The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(U_\text{EP})$: the smaller $\Im(U_\text{EP})$, the sharper the avoided crossing is.
 
-Around $\lambda = \lambda_\text{EP}$, Eq.~\eqref{eq:E_2x2} behaves as \cite{MoiseyevBook}
+Around $U = U_\text{EP}$, Eq.~\eqref{eq:E_FCI} behaves as \cite{MoiseyevBook}
 \begin{equation} %\label{eq:E_EP}
-        E_{\pm} = E_\text{EP} \pm \sqrt{2\lambda_\text{EP}} \sqrt{\lambda - \lambda_\text{EP}},
+        E_{\pm} = E_\text{EP} \pm \sqrt{2U_\text{EP}} \sqrt{U - U_\text{EP}},
 \end{equation}
-and following a complex contour around the EP, \ie, $\lambda = \lambda_\text{EP} + R \exp(i\theta)$, yields
+and following a complex contour around the EP, \ie, $U = U_\text{EP} + R \exp(i\theta)$, yields
 \begin{equation}
-        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2\lambda_\text{EP} R}  \exp(i\theta/2),
+        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2U_\text{EP} R}  \exp(i\theta/2),
 \end{equation}
@@
 
+Coming back to the Hubbard dimer, the HF energy is
+\begin{equation}
+	E_\text{HF} = -t \qty[ \sin \theta_\alpha  + \sin \theta_\beta ] + \frac{U}{2} \qty[ 1 + \cos \theta_\alpha \cos \theta_\beta ]
+\end{equation}
+where 
+\begin{align}
+	\psi_{1\sigma} & = \cos(\frac{\theta_\sigma}{2}) s_1 - \sin(\frac{\theta_\sigma}{2})s_2
+	\\
+	\psi_{2\sigma} & = \sin(\frac{\theta_\sigma}{2}) s_1 + \cos(\frac{\theta_\sigma}{2})s_2 
+\end{align}
+
+\begin{align}
+	\theta_\alpha & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+	\\
+	\theta_\beta & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+\end{align}
+
+%=====================================================%
 \subsection{M{\o}ller-Plesset perturbation theory}
+%=====================================================%
 

### 2020-11-14 RapportStage/Rapport.tex
added UMP data to notebook

@@
 
-\begin{wrapfigure}{R}{0.4\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{gill1986.png}
-    \caption{Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from Ref.~\cite{Gill_1986}).}
-    \label{fig:RUMP_Gill}
-\end{wrapfigure}
+%\begin{wrapfigure}{R}{0.4\textwidth}
+%    \centering
+%    \includegraphics[width=\linewidth]{gill1986.png}
+%    \caption{Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$) (taken from Ref.~\cite{Gill_1986}).}
+ %   \label{fig:RUMP_Gill}
+%\end{wrapfigure}
 When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, i.e., one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.

### 2020-11-15 Manuscript/EPAWTFT.tex
Cremer and He's part update

@@
 \textit{``Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+Moreover, they analyzed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation.
+On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
+This observation on the contribution to the MPn energy corroborates the electronic structure discussed above.
 As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
@@
 These so-called archetypes can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
-Importantly, they observed that the the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
+Importantly, they observed that the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
 Other features characterizing the convergence behavior of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern;
@@
 The major difference between these two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the the electron-nucleus attraction.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the electron-nucleus attraction.
 For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei.
@@
 \cite{Stransky_2018} In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis.
-They showed that, within the interaction boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases.
+They showed that, within the interacting boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases.
 The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second orders, respectively) with respect to the number of particles.

### 2020-11-15 Manuscript/EPAWTFT.tex
Update QPT

@@
 
+Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the IBM model from the QPT's point of view \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}.
+The phase of the ensemble of $s$ and $d$ bosons is characterized by a dynamical symmetry.
+When a parameter is continously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase.
+They showed that at this critical value of the parameter, the system undergoes a QPT.
+For example, without interaction the ground state is the spherical phase (a condensate of s bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of s and d bosons states.
+In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wavefunction of the hydrogen molecule when the bond is stretched \cite{SzaboBook}.
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory.

### 2020-11-15 Manuscript/EPAWTFT.tex
saving work: more Surjan and starting Hubbard MP

@@
 Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of the convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
-In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent series taking again as an example the water molecule in a stretched geometry.
+In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series taking again as an example the water molecule in a stretched geometry.
 In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent, and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
 However, the choice of the functional form of the fit remains a subtle task.
-This technique was first generalized by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula
-\begin{equation}
-	\frac{1}{2\pi i} \oint \frac{E(z)}{z - a} = E(a)
-\end{equation}
-instead of the solution of the Laplace equation. \cite{Mihalka_2019}
+This technique was first generalized by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
+\begin{equation}
+	\label{eq:Cauchy}
+	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(z)}{z - a} = E(a).
+\end{equation}
+Their method consists in refining self-consistently the values of $E(z)$ computed on a contour going through the physical point at $z = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
+The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(z)$ is analytic.
+When the values of $E(z)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(z=1)$ which corresponds to the final estimate of the FCI energy.
+The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
+
+%%% FIG 2 %%%
+\begin{figure*}
+	\includegraphics[height=0.25\textwidth]{fig2a}	
+	\hspace{0.05\textwidth}
+	\includegraphics[height=0.25\textwidth]{fig2b}
+	\hspace{0.05\textwidth}
+	\includegraphics[height=0.25\textwidth]{fig2c}	
+	\caption{
+	Convergence of the RMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3.5$ (before the radius of convergence) and $4.5$ (after the radius of convergence).
+	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
+	\label{fig:RMP}}
+\end{figure*}
+
+Let us illustrate the behavior of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
+Within the RMP parition thecnique, we have 
+\begin{equation}
+\label{eq:H_RMP}
+	\bH^\text{RMP} = 
+	\begin{pmatrix}
+		-2t + U - \lambda U/2	&	0					&	0					&	\lambda U/2	\\
+		0						&	U - \lambda U/2 	&	\lambda U/2			&	0	\\
+		0						&	\lambda U/2			&	U - \lambda U/2 	&	0	\\
+		\lambda U/2 			&	0 					&	0					&	2t + U - \lambda U/2	\\
+	\end{pmatrix},
+\end{equation}
+which yields the ground-state energy 
+\begin{equation}
+	\label{eq:E0MP}
+	E_0(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}
+\end{equation}
+From this expression, it is easy to identify that the radius of convergence is defined by the exceptional points at $\lambda = \pm i 4t / U$ (which is similar to the FCI exceptional point).
+Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction
+\begin{equation}
+	E_0^{(n)} = U \delta_{0,n} - \frac{1}{2} \frac{U^n}{(4t)^{n-1}} \mqty( n/2 \\ 1/2)
+\end{equation}
+with 
+\begin{equation}
+	E_0(\lambda) = \sum_{n=0}^\infty E_0^{(n)} \lambda^n
+\end{equation}
+We illustrate this by plotting the energy expansions at orders of $\lambda$ just below and above the radius of convergence in Fig.~\ref{fig:RMP}.
+\titou{T2 is going to add a discussion about this figure.}
+
+At the UMP level now, we have
+\begin{widetext}
+\begin{equation}
+\label{eq:H_UMP}
+	\bH^\text{UMP} = 
+	\begin{pmatrix}
+		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
+		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
+	\end{pmatrix},
+\end{equation}
+\end{widetext}
+A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting its expression.
+
+%%% FIG 3 %%%
+\begin{figure*}
+	\includegraphics[height=0.25\textwidth]{fig3a}	
+	\hspace{0.05\textwidth}
+	\includegraphics[height=0.25\textwidth]{fig3b}
+	\hspace{0.05\textwidth}
+	\includegraphics[height=0.25\textwidth]{fig3c}	
+	\caption{
+	Convergence of the URMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3$ and $7$.
+	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
+	\label{fig:UMP}}
+\end{figure*}
 

### 2020-11-16 Manuscript/EPAWTFT.tex
Added meshes and cylinders to figures, and sorted UMP axis labels

@@
 %\affiliation{\UCAM}
+\email{hugh.burton@chem.ox.ac.uk}
 \affiliation{\UOX}
@@
 \begin{figure*}
-	\includegraphics[height=0.25\textwidth]{fig3a}	
+    \centering
+	\includegraphics[height=0.23\textwidth]{fig3a}	
 	\hspace{0.05\textwidth}
-	\includegraphics[height=0.25\textwidth]{fig3b}
+	\includegraphics[height=0.23\textwidth]{fig3b}
 	\hspace{0.05\textwidth}
-	\includegraphics[height=0.25\textwidth]{fig3c}	
+	\includegraphics[height=0.23\textwidth]{fig3c}	
 	\caption{
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481)
+This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
 HGAB gratefully acknowledges New College, Oxford for funding through the Astor Junior Research Fellowship.

### 2020-11-17 Manuscript/EPAWTFT.tex
Modified exact example to Wannier basis.

@@
 \documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,tabularx,array,booktabs,longtable,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
+\usepackage{subcaption}
+\usepackage{graphicx,tabularx,array,booktabs,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[normalem]{ulem}
-\definecolor{darkgreen}{RGB}{0, 180, 0}
+\definecolor{hughgreen}{RGB}{0, 128, 0}
 \newcommand{\titou}[1]{\textcolor{red}{#1}}
-\newcommand{\hugh}[1]{\textcolor{orange}{#1}}
+\newcommand{\hugh}[1]{\textcolor{hughgreen}{#1}}
 \newcommand{\trash}[1]{\textcolor{red}{\sout{#1}}}
@@
     citecolor=blue,
+    linkcolor=blue,
+    filecolor=blue,      
+    urlcolor=blue,	
     breaklinks=true
@@
 \newcommand{\ctab}{\multicolumn{1}{c}{---}}
-\newcommand{\ie}{\textit{i.e.}}
-\newcommand{\eg}{\textit{e.g.}}
+\newcommand{\latin}[1]{#1}
+%\newcommand{\latin}[1]{\textit{#1}}
+\newcommand{\ie}{\latin{i.e.}}
+\newcommand{\eg}{\latin{e.g.}}
 \newcommand{\mc}{\multicolumn}
@@
 
+% Center tabularx columns
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
+
+% Imaginary constant
+\renewcommand{\i}{\mathrm{i}}
+% Blackboard bold
+\newcommand{\bbR}{\mathbb{R}}
+\newcommand{\bbC}{\mathbb{C}}
+
+\newcommand{\Lup}{\text{L}^{\uparrow}}
+\newcommand{\Ldown}{\text{L}^{\downarrow}}
+\newcommand{\Rup}{\text{R}^{\uparrow}}
+\newcommand{\Rdown}{\text{R}^{\downarrow}}
+
 \newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France.}
@@
 %===================================%
-\subsection{An illustrative example}
+\subsection{\hugh{Exact Exceptional Points}}
 %===================================%
-In order to highlight the general properties of EPs mentioned above, we propose to consider the ubiquitous symmetric Hubbard dimer at half filling (\ie, with two opposite-spin fermions) whose Hamiltonian reads in the singlet configuration state function basis
-%\begin{align}
-%		\ket{1\up1\dw}		&	\ket{1\up2\dw}		&	\ket{1\dw2\up}		&	\ket{2\up2\dw}	\\
-%		\uddot \quad \vac	&	\updot \quad \dwdot	&	\dwdot \quad \updot	&	\vac \quad \uddot	 \\
-%\end{align}
+
+%%% FIG 1 %%%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{fig1a}
+	\subcaption{\label{subfig:FCI_real}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{fig1b}
+	\subcaption{\label{subfig:FCI_cplx}}
+    \end{subfigure}
+	\caption{%
+	\hugh{Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
+    Only the interacting closed-shell singlets are plotted in the complex plane, becoming degenerate at the EP (black dot).}
+	\label{fig:FCI}}
+\end{figure*}
+
+\hugh{To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
+Using the localised Wannier basis, the Hilbert space for this system comprises the four configurations
+\begin{equation}
+\ket{\Lup \Ldown} \qquad \ket{\Lup\Rdown} \qquad \ket{\Rup\Ldown} \qquad \ket{\Rup\Rdown}
+\end{equation}
+%\begin{tabularx}{\linewidth}{YYYY}
+%$\ket{\Lup \Ldown}$ & $\ket{\Lup\Rdown}$ & $\ket{\Rup\Ldown}$ &	$\ket{\Rup\Rdown}$
+%\\
+%$\uddot \quad \vac$ & $\updot \quad \dwdot$ & $\dwdot \quad \updot$ & $\vac \quad \uddot$
+%\end{tabularx}
+where $\text{L}^{\sigma}$ ($\text{R}^{\sigma}$) denotes an electron with spin $\sigma$ on the left (right) site.
+The exact Hamiltonian is then 
 \begin{equation}
@@
 	\begin{pmatrix}
-		-2t	+ U &	0 & U/2	\\
-		0		&	U 	&	0	\\
-		U/2 &	0 & -2t	+ U	\\
+		U &	- t & -  t & 0	\\
+	   -  t &  0 &  0 & -  t \\
+       -  t &  0 &  0 & -  t \\
+        0 & -  t & -  t & U \\
 	\end{pmatrix},
 \end{equation}
-where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.
+where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.}
 We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
-We will consistently use this system to illustrate the different concepts discussed in the present review article.
-
-For real $U$, the Hamiltonian \eqref{eq:H_FCI} is clearly Hermitian, and it becomes non-Hermitian for any complex $U$ value.
-The eigenvalues associated with its singlet ground state and singlet doubly-excited state are
-\begin{equation}
-\label{eq:E_FCI}
-	E_{\pm} = \frac{1}{2} \qty( U \pm \sqrt{(4t^2) + U^2} ).
-\end{equation}
-and they are represented as a function of $U$ in Fig.~\ref{fig:FCI} together with the energy of the singlet open-shell configuration of energy $U$.
-
-%%% FIG 1 %%%
-\begin{figure*}
-	\includegraphics[height=0.3\textwidth]{fig1a}
-	\hspace{0.1\textwidth}
-	\includegraphics[height=0.3\textwidth]{fig1b}	
-	\caption{
-	Exact energies for the Hubbard dimer as functions of $U/t$.
-	\label{fig:FCI}}
-\end{figure*}
-
-One notices that these two states become degenerate only for a pair of complex conjugate values of $U$
-\begin{equation}
-\label{eq:lambda_EP}
-	U_\text{EP} = \pm 4 i t,
+
+\hugh{%
+To illustrate the formation of an exceptional points, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$.
+When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) eigenvalues
+\begin{subequations}
+\begin{align}
+E_{\mp} &= \frac{1}{2} \qty(U \mp \sqrt{ (4 \lambda t)^2 + U^2 } ),
+\label{eq:singletE}
+\\
+E_{\text{T}} &= 0,
+\\
+E_{\text{S}} &= U.
+\end{align}
+\end{subequations}
+While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Figure~\ref{subfig:FCI_real}).
+At non-zero values of $U$ and $t$, these closed-shell singlets can only become degenerate at a pair of complex conjugate points in the complex $\lambda$ plane 
+\begin{equation}
+\lambda_{\text{EP}} = \pm \frac{U}{4t} \i,
 \end{equation}
@@
 \label{eq:E_EP}
-	E_\text{EP} = \pm 2 i t,
-\end{equation}
-which correspond to square-root singularities in the complex-$U$ plane [see Fig.~\eqref{fig:FCI}].
-These two $U$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
-Starting from $U_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
-In the real $U$ axis, the point for which the states are the closest ($U = 0$) is called an avoided crossing and this occurs at $U = \Re(U_\text{EP})$.
-The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(U_\text{EP})$: the smaller $\Im(U_\text{EP})$, the sharper the avoided crossing is.
-
-Around $U = U_\text{EP}$, Eq.~\eqref{eq:E_FCI} behaves as \cite{MoiseyevBook}
-\begin{equation} %\label{eq:E_EP}
-        E_{\pm} = E_\text{EP} \pm \sqrt{2U_\text{EP}} \sqrt{U - U_\text{EP}},
-\end{equation}
-and following a complex contour around the EP, \ie, $U = U_\text{EP} + R \exp(i\theta)$, yields
-\begin{equation}
-        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2U_\text{EP} R}  \exp(i\theta/2),
-\end{equation}
-and we have
+	E_\text{EP} = \frac{U}{2}.
+\end{equation}
+These $\lambda$ values correspond to so-called EPs and connect the ground and excited state in the complex plane.
+Crucially, the energy surface becomes non-analytic at $\lambda_{\text{EP}}$ and a square-root singularity forms with two branch cuts running along the imaginary axis from $\lambda_{\text{EP}}$  to $\pm \i \infty$ (see Fig.~\ref{subfig:FCI_cplx}).
+On the real $\lambda$ axis, these EPs lead to the singlet avoided crossing at $\lambda = \Re(\lambda_{\text{EP}})$.
+The ``shape'' of this avoided crossing is related to the magnitude of $\Im(\lambda_{\text{EP}})$, with smaller values giving a ``sharper'' interaction.
+}
+
+\hugh{
+Remarkably, the existence of these square-root singularities means that following a complex contour around an EP in the complex $\lambda$ plane will interconvert the closed-shell ground and excited states.
+This behaviour can be seen by expanding the radicand in Eq.~\eqref{eq:singletE} as a Taylor series around $\lambda_{\text{EP}}$ to give
+\begin{equation}
+E_{\pm} \approx E_{\text{EP}} \pm \sqrt{32t^2 \lambda_{\text{EP}}} \sqrt{\lambda - \lambda_{\text{EP}}}.
+\end{equation}
+Parametrising the complex contour as $\lambda(\theta) = \lambda_{\text{EP}} + R \exp(\i \theta)$ gives the continuous energy pathways 
+\begin{equation}
+E_{\pm} \qty(\theta) \approx E_{\text{EP}} \pm \sqrt{32t^2 \lambda_{\text{EP}} R}\, \exp(\i \theta/2)
+\end{equation}
+such that}
 \begin{align}
@@
 \end{align}
-This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
-Additionally, the wave function picks up a geometric phase and four loops are required to recover the starting wave function.
-\cite{MoiseyevBook}
+As a result, completely encircling an EP leads to the interconversion of the two interacting states, while a second complete rotation returns the two states to their original energies.
+Additionally, the wave functions pick up a geometric phase in the process, and four complete loops are required to recover their starting forms.\cite{MoiseyevBook}
+
+%In order to highlight the general properties of EPs mentioned above, we propose to consider the ubiquitous symmetric Hubbard dimer at half filling (\ie, with two opposite-spin fermions) whose Hamiltonian reads in the singlet configuration state function basis
+%\begin{align}
+%		\ket{1\up1\dw}		&	\ket{1\up2\dw}		&	\ket{1\dw2\up}		&	\ket{2\up2\dw}	\\
+%		\uddot \quad \vac	&	\updot \quad \dwdot	&	\dwdot \quad \updot	&	\vac \quad \uddot	 \\
+%\end{align}
+%\begin{equation}
+%\label{eq:H_FCI}
+%	\bH = 
+%	\begin{pmatrix}
+%		-2t	+ U &	0 & U/2	\\
+%		0		&	U 	&	0	\\
+%		U/2 &	0 & -2t	+ U	\\
+%	\end{pmatrix},
+%\end{equation}
+%where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.
+%We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
+%We will consistently use this system to illustrate the different concepts discussed in the present review article.
+
+%For real $U$, the Hamiltonian \eqref{eq:H_FCI} is clearly Hermitian, and it becomes non-Hermitian %for any complex $U$ value.
+%The eigenvalues associated with its singlet ground state and singlet doubly-excited state are
+%\begin{equation}
+%\label{eq:E_FCI}
+%	E_{\pm} = \frac{1}{2} \qty( U \pm \sqrt{(4t^2) + U^2} ).
+%\end{equation}
+%and they are represented as a function of $U$ in Fig.~\ref{fig:FCI} together with the energy of the %singlet open-shell configuration of energy $U$.
+
+%One notices that these two states become degenerate only for a pair of complex conjugate values of $U$
+%\begin{equation}
+%\label{eq:lambda_EP}
+%	U_\text{EP} = \pm 4 i t,
+%\end{equation}
+%with energy
+%\begin{equation}
+%\label{eq:E_EP}
+%	E_\text{EP} = \pm 2 i t,
+%\end{equation}
+%which correspond to square-root singularities in the complex-$U$ plane [see Fig.~\eqref{fig:FCI}].
+%These two $U$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
+%Starting from $U_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
+%In the real $U$ axis, the point for which the states are the closest ($U = 0$) is called an avoided crossing and this occurs at $U = \Re(U_\text{EP})$.
+%The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(U_\text{EP})$: the smaller $\Im(U_\text{EP})$, the sharper the avoided crossing is.
+
+%Around $U = U_\text{EP}$, Eq.~\eqref{eq:E_FCI} behaves as \cite{MoiseyevBook}
+%\begin{equation} %\label{eq:E_EP}
+%        E_{\pm} = E_\text{EP} \pm \sqrt{2U_\text{EP}} \sqrt{U - U_\text{EP}},
+%\end{equation}
+%and following a complex contour around the EP, \ie, $U = U_\text{EP} + R \exp(i\theta)$, yields
+%\begin{equation}
+%        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2U_\text{EP} R}  \exp(i\theta/2),
+%\end{equation}
+%and we have
+%\begin{align}
+%	E_{\pm}(2\pi) & = E_{\mp}(0),
+%	&
+%	E_{\pm}(4\pi) & = E_{\pm}(0). \notag
+%\end{align}
+%This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+%Additionally, the wave function picks up a geometric phase and four loops are required to recover the starting wave function.
+%\cite{MoiseyevBook}
 

### 2020-11-17 Manuscript/EPAWTFT.tex
restoed 'Illustrative Example' title
corrected lambda axis labels in fig1
goign through Hugh stuff and starting working on HF

@@
 \usepackage{subcaption}
-\usepackage{graphicx,tabularx,array,booktabs,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
+\usepackage{bm,graphicx,tabularx,array,booktabs,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
 \usepackage[utf8]{inputenc}
@@
 
-\newcommand{\Lup}{\text{L}^{\uparrow}}
-\newcommand{\Ldown}{\text{L}^{\downarrow}}
-\newcommand{\Rup}{\text{R}^{\uparrow}}
-\newcommand{\Rdown}{\text{R}^{\downarrow}}
+\newcommand{\Lup}{\mathcal{L}^{\uparrow}}
+\newcommand{\Ldown}{\mathcal{L}^{\downarrow}}
+\newcommand{\Lsi}{\mathcal{L}^{\sigma}}
+\newcommand{\Rup}{\mathcal{R}^{\uparrow}}
+\newcommand{\Rdown}{\mathcal{R}^{\downarrow}}
+\newcommand{\Rsi}{\mathcal{R}^{\sigma}}
 
@@
 %===================================%
-\subsection{\hugh{Exact Exceptional Points}}
+\subsection{Illustrative Example}
 %===================================%
@@
 	\caption{%
-	\hugh{Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
-    Only the interacting closed-shell singlets are plotted in the complex plane, becoming degenerate at the EP (black dot).}
+	Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
+    Only the interacting closed-shell singlets are plotted in the complex plane, becoming degenerate at the EP (black dot).
 	\label{fig:FCI}}
@@
 
-\hugh{To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
-Using the localised Wannier basis, the Hilbert space for this system comprises the four configurations
-\begin{equation}
-\ket{\Lup \Ldown} \qquad \ket{\Lup\Rdown} \qquad \ket{\Rup\Ldown} \qquad \ket{\Rup\Rdown}
-\end{equation}
-%\begin{tabularx}{\linewidth}{YYYY}
-%$\ket{\Lup \Ldown}$ & $\ket{\Lup\Rdown}$ & $\ket{\Rup\Ldown}$ &	$\ket{\Rup\Rdown}$
-%\\
-%$\uddot \quad \vac$ & $\updot \quad \dwdot$ & $\dwdot \quad \updot$ & $\vac \quad \uddot$
-%\end{tabularx}
-where $\text{L}^{\sigma}$ ($\text{R}^{\sigma}$) denotes an electron with spin $\sigma$ on the left (right) site.
+To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
+Using the localised site basis, the Hilbert space for this system comprises the four configurations
+\begin{align}
+& \ket{\Lup \Ldown} &  & \ket{\Lup\Rdown} &  & \ket{\Rup\Ldown} &  & \ket{\Rup\Rdown}
+\end{align}
+where $\Lsi$ ($\Rsi$) denotes an electron with spin $\sigma$ on the left (right) site.
 The exact Hamiltonian is then 
@@
 	\begin{pmatrix}
-		U &	- t & -  t & 0	\\
+		U &	- t & +  t & 0	\\
 	   -  t &  0 &  0 & -  t \\
-       -  t &  0 &  0 & -  t \\
-        0 & -  t & -  t & U \\
+       +  t &  0 &  0 & +  t \\
+        0 & -  t & +  t & U \\
 	\end{pmatrix},
 \end{equation}
-where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.}
+where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.
 We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
 
-\hugh{%
 To illustrate the formation of an exceptional points, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$.
@@
 \end{subequations}
-While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Figure~\ref{subfig:FCI_real}).
+While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Fig.~\ref{subfig:FCI_real}).
 At non-zero values of $U$ and $t$, these closed-shell singlets can only become degenerate at a pair of complex conjugate points in the complex $\lambda$ plane 
 \begin{equation}
-\lambda_{\text{EP}} = \pm \frac{U}{4t} \i,
+\lambda_{\text{EP}} = \pm  \i \frac{U}{4t},
 \end{equation}
@@
 The ``shape'' of this avoided crossing is related to the magnitude of $\Im(\lambda_{\text{EP}})$, with smaller values giving a ``sharper'' interaction.
-}
-
-\hugh{
+
 Remarkably, the existence of these square-root singularities means that following a complex contour around an EP in the complex $\lambda$ plane will interconvert the closed-shell ground and excited states.
@@
 \end{equation}
-such that}
+such that
 \begin{align}
@@
 	\label{eq:CoulOp}
-	J_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') ] \phi_p(\vb{x})
+	J_i(\vb{x})\phi_p(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_p(\vb{x})
 	\\
 	\label{eq:ExcOp}
-	K_i(\vb{x})\phi_p(\vb{x})=\qty[\int\dd\vb{x}'\phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_p(\vb{x}') ] \phi_i(\vb{x})
+	K_i(\vb{x})\phi_p(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_p(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x})
 \end{gather}
@@
 being the Coulomb and exchange operators (respectively) in the spin-orbital basis. \cite{SzaboBook}
+The HF energy is then defined as 
+\begin{equation}
+\label{eq:E_HF}
+	E_\text{HF} = \sum_i h_i + \frac{1}{2} \sum_{ij} \qty( J_{ij} - K_{ij} )
+\end{equation}
+with 
+\begin{subequations}
+\begin{gather}
+	h_i = \int \phi_i(\vb{x}) h(\vb{x})  \phi_i(\vb{x}) \dd\vb{x}
+	\\
+	J_{ij} = \int \phi_i(\vb{x})  J_j(\vb{x}) \phi_i(\vb{x}) \dd\vb{x}
+	\\
+	K_{ij} = \int \phi_i(\vb{x})  K_j(\vb{x}) \phi_i(\vb{x}) \dd\vb{x}
+\end{gather}
+\end{subequations}
 If the spatial part of the spin-orbitals are restricted to be the same for spin-up and spin-down electrons, one talks about restricted HF (RHF) theory, whereas if one does not enforce this constrain it leads to the so-called unrestricted HF (UHF) theory.
@@
 
-Coming back to the Hubbard dimer, the HF energy is
+Coming back to the Hubbard dimer, the HF energy is [see Eq.~\eqref{eq:E_HF}]
 \begin{equation}
@@
 \begin{align}
-	\psi_{1\sigma} & = \cos(\frac{\theta_\sigma}{2}) s_1 - \sin(\frac{\theta_\sigma}{2})s_2
+	\psi_{1\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi - \sin(\frac{\theta_\sigma}{2}) \Rsi
 	\\
-	\psi_{2\sigma} & = \sin(\frac{\theta_\sigma}{2}) s_1 + \cos(\frac{\theta_\sigma}{2})s_2 
+	\psi_{2\sigma} & = \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
 \end{align}
-
+are the one-electron molecule orbitals for the spin-$\sigma$ electrons and the angles which makes the energy stationnary, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$ are given by
 \begin{align}

### 2020-11-17 Manuscript/EPAWTFT.tex
first draft for HF

@@
 \newcommand{\UOX}{Physical and Theoretical Chemical Laboratory, Department of Chemistry, University of Oxford, Oxford, OX1 3QZ, U.K.}
-\newcommand{\VU}{Department of Theoretical Chemistry and Amsterdam Center for Multiscale Modeling, FEW, Vrije Universiteit, De Boelelaan 1083, 1081HV Amsterdam, The Netherlands.}
 \begin{document}
@@
 \author{Hugh G.~A.~\surname{Burton}}
-%\affiliation{\UCAM}
 \email{hugh.burton@chem.ox.ac.uk}
 \affiliation{\UOX}
-%\author{Paola \surname{Gori-Giorgi}}
-%\affiliation{\VU}
 \author{Pierre-Fran\c{c}ois \surname{Loos}}
@@
 
-One common feature of all these methods is that they rely on the notion of quantized energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
-Within this quantized paradigm, electronic states look completely disconnected from one another.
+One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
+Within this quantised paradigm, electronic states look completely disconnected from one another.
 Many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.
-However, one can gain a different perspective on quantization extending quantum chemistry into the complex domain.
+However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
 In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
-In other words, our view of the quantized nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
 \cite{MoiseyevBook,BenderPTBook}
-The realization that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
+The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
 One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019,Burton_2019a}
@@
 They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
-In the case of auto-ionizing resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
-Although Hermitian and non-Hermitian Hamiltonians are closely related, the behavior of their eigenvalues near degeneracies is starkly different.
+In the case of auto-ionising resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
+Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
 For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
@@
 To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
-Using the localised site basis, the Hilbert space for this system comprises the four configurations
+Simple systems that are analytically solvable are of great importance in theoretical chemistry and physics as they can be employed to illustrate concepts and test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but they retain much of the key physics.
+
+Using the (localised) site basis, the (singlet) Hilbert space of the Hubbard dimer comprises the four configurations
 \begin{align}
@@
 We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
+The parameter $U$ dictates the correlation regime. 
+In the weak correlation regime (\ie, small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
+For large $U$ (or strong correlation regime), the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
+This phenomenon is sometimes referred to as a Wigner crystallisation. \cite{Wigner_1934}
 
@@
 
-%In order to highlight the general properties of EPs mentioned above, we propose to consider the ubiquitous symmetric Hubbard dimer at half filling (\ie, with two opposite-spin fermions) whose Hamiltonian reads in the singlet configuration state function basis
-%\begin{align}
-%		\ket{1\up1\dw}		&	\ket{1\up2\dw}		&	\ket{1\dw2\up}		&	\ket{2\up2\dw}	\\
-%		\uddot \quad \vac	&	\updot \quad \dwdot	&	\dwdot \quad \updot	&	\vac \quad \uddot	 \\
-%\end{align}
-%\begin{equation}
-%\label{eq:H_FCI}
-%	\bH = 
-%	\begin{pmatrix}
-%		-2t	+ U &	0 & U/2	\\
-%		0		&	U 	&	0	\\
-%		U/2 &	0 & -2t	+ U	\\
-%	\end{pmatrix},
-%\end{equation}
-%where $t$ is the hopping parameter and $U$ is the on-site Coulomb repulsion.
-%We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
-%We will consistently use this system to illustrate the different concepts discussed in the present review article.
-
-%For real $U$, the Hamiltonian \eqref{eq:H_FCI} is clearly Hermitian, and it becomes non-Hermitian %for any complex $U$ value.
-%The eigenvalues associated with its singlet ground state and singlet doubly-excited state are
-%\begin{equation}
-%\label{eq:E_FCI}
-%	E_{\pm} = \frac{1}{2} \qty( U \pm \sqrt{(4t^2) + U^2} ).
-%\end{equation}
-%and they are represented as a function of $U$ in Fig.~\ref{fig:FCI} together with the energy of the %singlet open-shell configuration of energy $U$.
-
-%One notices that these two states become degenerate only for a pair of complex conjugate values of $U$
-%\begin{equation}
-%\label{eq:lambda_EP}
-%	U_\text{EP} = \pm 4 i t,
-%\end{equation}
-%with energy
-%\begin{equation}
-%\label{eq:E_EP}
-%	E_\text{EP} = \pm 2 i t,
-%\end{equation}
-%which correspond to square-root singularities in the complex-$U$ plane [see Fig.~\eqref{fig:FCI}].
-%These two $U$ values, given by Eq.~\eqref{eq:lambda_EP}, are the so-called EPs and one can clearly see that they connect the ground and excited states.
-%Starting from $U_\text{EP}$, two square-root branch cuts run on the imaginary axis towards $\pm i \infty$.
-%In the real $U$ axis, the point for which the states are the closest ($U = 0$) is called an avoided crossing and this occurs at $U = \Re(U_\text{EP})$.
-%The ``shape'' of the avoided crossing is linked to the magnitude of $\Im(U_\text{EP})$: the smaller $\Im(U_\text{EP})$, the sharper the avoided crossing is.
-
-%Around $U = U_\text{EP}$, Eq.~\eqref{eq:E_FCI} behaves as \cite{MoiseyevBook}
-%\begin{equation} %\label{eq:E_EP}
-%        E_{\pm} = E_\text{EP} \pm \sqrt{2U_\text{EP}} \sqrt{U - U_\text{EP}},
-%\end{equation}
-%and following a complex contour around the EP, \ie, $U = U_\text{EP} + R \exp(i\theta)$, yields
-%\begin{equation}
-%        E_{\pm}(\theta) = E_\text{EP} \pm \sqrt{2U_\text{EP} R}  \exp(i\theta/2),
-%\end{equation}
-%and we have
-%\begin{align}
-%	E_{\pm}(2\pi) & = E_{\mp}(0),
-%	&
-%	E_{\pm}(4\pi) & = E_{\pm}(0). \notag
-%\end{align}
-%This evidences that encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
-%Additionally, the wave function picks up a geometric phase and four loops are required to recover the starting wave function.
-%\cite{MoiseyevBook}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-is the exact electronic Hamiltonian for a chemical system with $n$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $N$ (fixed) nuclei (where $\vb{R}_A$ and $Z_A$ are the position and the charge of the $A$th nucleus respectively).
+is the exact electronic Hamiltonian for a chemical system with $N$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $M$ (fixed) nuclei (where $\vb{R}_A$ and $Z_A$ are the position and the charge of the $A$th nucleus respectively).
 The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
@@
 \begin{quote}
-	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centered at $z_0$ with radius $\abs{z_1-z_0}$.
+	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centred at $z_0$ with radius $\abs{z_1-z_0}$.
 If the function has a singular point $z_s$ such that $\abs{z_s-z_0} < \abs{z_1-z_0}$, then the series will diverge when evaluated at $z_1$.''}
@@
 
-In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_n)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $n$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $N$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
 \begin{equation}\label{eq:FockOp}
-	f(\vb{x}) \phi_p(\vb{x}) = [ h(\vb{x}) + v^\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
+	\Hat{f}(\vb{x}) \phi_p(\vb{x}) = [ \Hat{h}(\vb{x}) + \Hat{v}^\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
 \end{equation}
@@
 \begin{equation}
-	h(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
+	\Hat{h}(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
 \end{equation}
@@
 \begin{equation}
-	v^\text{HF}(\vb{x}) = \sum_i \qty[ J_i(\vb{x}) - K_i(\vb{x}) ]
+	\Hat{v}^\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
 \end{equation}
@@
 	\label{eq:CoulOp}
-	J_i(\vb{x})\phi_p(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_p(\vb{x})
+	\Hat{J}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_j(\vb{x})
 	\\
 	\label{eq:ExcOp}
-	K_i(\vb{x})\phi_p(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_p(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x})
+	\Hat{K}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_j(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x})
 \end{gather}
@@
 \label{eq:E_HF}
-	E_\text{HF} = \sum_i h_i + \frac{1}{2} \sum_{ij} \qty( J_{ij} - K_{ij} )
+	E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} )
 \end{equation}
 with
-\begin{subequations}
-\begin{gather}
-	h_i = \int \phi_i(\vb{x}) h(\vb{x})  \phi_i(\vb{x}) \dd\vb{x}
-	\\
-	J_{ij} = \int \phi_i(\vb{x})  J_j(\vb{x}) \phi_i(\vb{x}) \dd\vb{x}
-	\\
-	K_{ij} = \int \phi_i(\vb{x})  K_j(\vb{x}) \phi_i(\vb{x}) \dd\vb{x}
-\end{gather}
-\end{subequations}
+\begin{align}
+	h_i & = \mel{\phi_i}{h}{\phi_i}
+	&
+	J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i}
+	&
+	K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}
+\end{align}
 If the spatial part of the spin-orbitals are restricted to be the same for spin-up and spin-down electrons, one talks about restricted HF (RHF) theory, whereas if one does not enforce this constrain it leads to the so-called unrestricted HF (UHF) theory.
@@
 
+%
+%The spatial part of the RHF wave function is then
+%\begin{equation}\label{eq:RHF_WF}
+%	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
+%\end{equation}
+%where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
+%Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
+%
+
 Coming back to the Hubbard dimer, the HF energy is [see Eq.~\eqref{eq:E_HF}]
@@
 \begin{align}
-	\psi_{1\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi - \sin(\frac{\theta_\sigma}{2}) \Rsi
+	\mathcal{B}^{\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi - \sin(\frac{\theta_\sigma}{2}) \Rsi
 	\\
-	\psi_{2\sigma} & = \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
+	\mathcal{A}^{\sigma} & = \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
 \end{align}
-are the one-electron molecule orbitals for the spin-$\sigma$ electrons and the angles which makes the energy stationnary, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$ are given by
+are the bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for the spin-$\sigma$ electrons and the angles which minimises the HF energy, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are
+\begin{equation}
+	\theta_\text{RHF}^\alpha = \theta_\text{RHF}^\beta = \pi/4 
+\end{equation}
+for $0 \le U \le 4t$, and
 \begin{align}
-	\theta_\alpha & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+	\theta_\text{UHF}^\alpha & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
 	\\
-	\theta_\beta & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+	\theta_\text{UHF}^\beta & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
 \end{align}
+otherwise.
+In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
+The RHF ground-state energy is then
+\begin{equation}
+	E_\text{RHF} =  -2t + \frac{U}{2}
+\end{equation}
+
+The RHF wave function cannot model properly the physics of the system at large $U$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite sites.
+Within the HF approximation, at the critical value of $U = 4t$, famously known as the Coulson-Fischer point, \cite{Coulson_1949} a symmetry-broken UHF solution appears with lower in energy than the RHF one.
+The UHF ground-state energy is
+\begin{equation}
+	E_\text{UHF} = - \frac{2t^2}{U}
+\end{equation}
+for $U \ge 4t$.
 
@@
     \hH(\lambda) = 
-    \sum_{i}^{n} \Bigg[ 
+    \sum_{i}^{N} \Bigg[ 
     -\frac{\grad_i^2}{2} 
-    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+    - \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
     \\
     + (1-\lambda) v^{\text{HF}}(\vb{x}_i) 
-    + \lambda\sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
+    + \lambda\sum_{i<j}^{N}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
     \Bigg].
@@
 As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
-The MP$m$ energy is defined as 
-\begin{equation}
-	E_{\text{MP}m}= \sum_{k=0}^m E^{(k)},
+The MP$n$ energy is defined as 
+\begin{equation}
+	E_{\text{MP}n}= \sum_{k=0}^n E^{(k)},
 \end{equation}

### 2020-11-17 Manuscript/EPAWTFT.tex
almost done with HF part

@@
     Only the interacting closed-shell singlets are plotted in the complex plane, becoming degenerate at the EP (black dot).
+    The contour followed around the EP in order to interchange states is also represented.
 	\label{fig:FCI}}
@@
 	\begin{pmatrix}
-		U &	- t & +  t & 0	\\
+		U &	- t & -  t & 0	\\
 	   -  t &  0 &  0 & -  t \\
-       +  t &  0 &  0 & +  t \\
-        0 & -  t & +  t & U \\
+       -  t &  0 &  0 & -  t \\
+        0 & -  t & -  t & U \\
 	\end{pmatrix},
@@
 In the weak correlation regime (\ie, small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
-For large $U$ (or strong correlation regime), the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
+In the large-$U$ (or strong correlation) regime, the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
 This phenomenon is sometimes referred to as a Wigner crystallisation. \cite{Wigner_1934}
 
-To illustrate the formation of an exceptional points, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$.
-When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) eigenvalues
+To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$.
+When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) (eigen)energies
 \begin{subequations}
@@
 \end{equation}
-These $\lambda$ values correspond to so-called EPs and connect the ground and excited state in the complex plane.
+These $\lambda$ values correspond to so-called EPs and connect the ground and excited states in the complex plane.
 Crucially, the energy surface becomes non-analytic at $\lambda_{\text{EP}}$ and a square-root singularity forms with two branch cuts running along the imaginary axis from $\lambda_{\text{EP}}$  to $\pm \i \infty$ (see Fig.~\ref{subfig:FCI_cplx}).
@@
 
-Remarkably, the existence of these square-root singularities means that following a complex contour around an EP in the complex $\lambda$ plane will interconvert the closed-shell ground and excited states.
+Remarkably, the existence of these square-root singularities means that following a complex contour around an EP in the complex $\lambda$ plane will interconvert the closed-shell ground and excited states (see Fig.~\ref{subfig:FCI_cplx}).
 This behaviour can be seen by expanding the radicand in Eq.~\eqref{eq:singletE} as a Taylor series around $\lambda_{\text{EP}}$ to give
@@
 	\label{eq:CoulOp}
-	\Hat{J}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_j(\vb{x})
+	\Hat{J}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_j(\vb{x}),
 	\\
 	\label{eq:ExcOp}
-	\Hat{K}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_j(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x})
+	\Hat{K}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_j(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x}),
 \end{gather}
@@
 \label{eq:E_HF}
-	E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} )
+	E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} ),
 \end{equation}
@@
 \begin{align}
-	h_i & = \mel{\phi_i}{h}{\phi_i}
+	h_i & = \mel{\phi_i}{\Hat{h}}{\phi_i},
 	&
-	J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i}
+	J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
 	&
-	K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}
+	K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}.
 \end{align}
@@
 \begin{equation}
-	E_\text{HF} = -t \qty[ \sin \theta_\alpha  + \sin \theta_\beta ] + \frac{U}{2} \qty[ 1 + \cos \theta_\alpha \cos \theta_\beta ]
+	E_\text{HF} = -t \qty[ \sin \theta_\alpha  + \sin \theta_\beta ] + \frac{U}{2} \qty[ 1 + \cos \theta_\alpha \cos \theta_\beta ],
 \end{equation}
@@
 \begin{align}
-	\mathcal{B}^{\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi - \sin(\frac{\theta_\sigma}{2}) \Rsi
+	\mathcal{B}^{\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi + \sin(\frac{\theta_\sigma}{2}) \Rsi,
 	\\
-	\mathcal{A}^{\sigma} & = \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
+	\mathcal{A}^{\sigma} & = - \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
 \end{align}
-are the bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for the spin-$\sigma$ electrons and the angles which minimises the HF energy, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are
-\begin{equation}
-	\theta_\text{RHF}^\alpha = \theta_\text{RHF}^\beta = \pi/4 
-\end{equation}
-for $0 \le U \le 4t$, and
+are the bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for the spin-$\sigma$ electrons. 
+The angles which minimises the HF energy, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are 
+\begin{equation}
+	\theta_\text{RHF}^\alpha = \theta_\text{RHF}^\beta = \pi/4,
+\end{equation}
+for $0 \le U \le 4t$, yielding
 \begin{align}
-	\theta_\text{UHF}^\alpha & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+	\mathcal{B}_\text{RHF}^{\sigma} & = \frac{\Lsi + \Rsi}{\sqrt{2}},
+	&
+	\mathcal{A}_\text{RHF}^{\sigma} & = \frac{\Lsi - \Rsi}{\sqrt{2}},
+\end{align}
+and the following RHF ground-state energy:
+\begin{equation}
+	E_\text{RHF} =  -2t + \frac{U}{2}
+\end{equation}
+In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
+The RHF wave function cannot model properly the physics of the system at large $U$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite sites.
+
+Within the HF approximation, at the critical value of $U = 4t$, famously known as the Coulson-Fischer point, \cite{Coulson_1949} a symmetry-broken UHF solution appears with a lower energy than the RHF one.
+Indeed, for $U \ge 4t$, we have
+\begin{align}
+	\theta_\text{UHF}^\alpha & = \titou{\arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U})},
 	\\
-	\theta_\text{UHF}^\beta & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}) 
+	\theta_\text{UHF}^\beta & = \titou{\arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U})},
 \end{align}
-otherwise.
-In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
-The RHF ground-state energy is then
-\begin{equation}
-	E_\text{RHF} =  -2t + \frac{U}{2}
-\end{equation}
-
-The RHF wave function cannot model properly the physics of the system at large $U$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite sites.
-Within the HF approximation, at the critical value of $U = 4t$, famously known as the Coulson-Fischer point, \cite{Coulson_1949} a symmetry-broken UHF solution appears with lower in energy than the RHF one.
-The UHF ground-state energy is
-\begin{equation}
-	E_\text{UHF} = - \frac{2t^2}{U}
-\end{equation}
-for $U \ge 4t$.
+and the corresponding UHF ground-state energy is
+\begin{equation}
+	E_\text{UHF} = - \frac{2t^2}{U}.
+\end{equation}
+Note that, for $U \ge 4t$, the RHF wave function remains a genuine solution of the HF equations but corresponds to a saddle point, not a minimum.
 
@@
 \end{multline}
-If one considers a RHF or UHF reference wave functions, it leads to the RMP or UMP series, respectively.
+The nature of the HF wave function is up for grabs, and if one considers a RHF or UHF reference wave functions, it leads to the RMP or UMP series, respectively.
 
@@
 \begin{equation}
-	E_{\text{MP}n}= \sum_{k=0}^n E^{(k)},
-\end{equation}
-where $E^{(k)}$ is the $k$th-order MP correction, and it is well known that $E_{\text{MP1}} =  E^{(0)} + E^{(1)} = E_\text{HF}$. \cite{SzaboBook}
+	E_{\text{MP}n}= \sum_{k=0}^n E_{\text{MP}}^{(k)},
+\end{equation}
+where $E_{\text{MP}}^{(k)}$ is the $k$th-order MP correction, and it is well known that $E_{\text{MP1}} =  E_{\text{MP}}^{(0)} + E_{\text{MP}}^{(1)} = E_\text{HF}$. \cite{SzaboBook}
 The MP2 energy reads
@@
 
-As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$m$ series converges to the exact energy when $m \to \infty$. 
+As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$n$ series converges to the exact energy as $n \to \infty$. 
 In fact, it is known that when the HF wave function is a poor approximation to the exact wave function, for example in multi-reference systems, the MP method yields deceptive results.

### 2020-11-17 Manuscript/EPAWTFT.tex
starting MP

@@
 \subsection{Illustrative Example}
+\label{sec:example}
 %===================================%
@@
 where $\Lsi$ ($\Rsi$) denotes an electron with spin $\sigma$ on the left (right) site.
-The exact Hamiltonian is then 
+The exact [or full configuration interaction (FCI)] Hamiltonian is then 
 \begin{equation}
@@
 \begin{equation}\label{eq:FockOp}
-	\Hat{f}(\vb{x}) \phi_p(\vb{x}) = [ \Hat{h}(\vb{x}) + \Hat{v}^\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
+	\Hat{f}(\vb{x}) \phi_p(\vb{x}) = [ \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
 \end{equation}
@@
 \begin{equation}
-	\Hat{v}^\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
+	\Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
 \end{equation}
@@
 \begin{equation}\label{eq:HFHamiltonian}
-	\hH^{\text{HF}} = \sum_{i} f(\vb{x}_i).
+	\hH_{\text{HF}} = \sum_{i} f(\vb{x}_i).
 \end{equation}
@@
 	\label{eq:Cauchy}
-	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(z)}{z - a} = E(a).
-\end{equation}
+	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(z)}{z - a} = E(a),
+\end{equation}
+which states that the value of the energy can be computed at $z=a$ inside the contour $\gamma$ only by the knowledge of its values on the same contour.
 Their method consists in refining self-consistently the values of $E(z)$ computed on a contour going through the physical point at $z = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
@@
 
-Let us illustrate the behavior of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
-Within the RMP parition thecnique, we have 
+Let us illustrate the behaviour of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
+Within the RMP partition technique, we have 
 \begin{equation}
 \label{eq:H_RMP}
-	\bH^\text{RMP} = 
+	\bH_\text{RMP} = 
 	\begin{pmatrix}
@@
 	\label{eq:E0MP}
-	E_0(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}
-\end{equation}
-From this expression, it is easy to identify that the radius of convergence is defined by the exceptional points at $\lambda = \pm i 4t / U$ (which is similar to the FCI exceptional point).
+	E_{-}(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}.
+\end{equation}
+From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
 Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction
 \begin{equation}
-	E_0^{(n)} = U \delta_{0,n} - \frac{1}{2} \frac{U^n}{(4t)^{n-1}} \mqty( n/2 \\ 1/2)
+	E_\text{MP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2),
 \end{equation}
@@
 \begin{equation}
-	E_0(\lambda) = \sum_{n=0}^\infty E_0^{(n)} \lambda^n
+	E_{-}(\lambda) = \sum_{k=0}^\infty E_\text{MP}^{(k)} \lambda^k.
 \end{equation}
 We illustrate this by plotting the energy expansions at orders of $\lambda$ just below and above the radius of convergence in Fig.~\ref{fig:RMP}.
-\titou{T2 is going to add a discussion about this figure.}
 
@@
 \label{eq:H_UMP}
-	\bH^\text{UMP} = 
+	\bH_\text{UMP} = 
 	\begin{pmatrix}
@@
 A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting its expression.
+The convergence of the UMP as a function of the ratio $U/t$ is depicted in Fig.~\ref{fig:UMP}.
 

### 2020-11-18 Manuscript/EPAWTFT.tex

@@
 
-\newcommand{\Ne}{N}
+\newcommand{\Ne}{N} % Number of electrons
+\newcommand{\Nn}{M} % Number of nuclei
 \newcommand{\hI}{\Hat{I}}
@@
 
-% Imaginary constant
-\renewcommand{\i}{\mathrm{i}}
+% HF rotation angles
+\newcommand{\ta}{\theta_{\alpha}}
+\newcommand{\tb}{\theta_{\beta}}
+
+% Some constants
+\renewcommand{\i}{\mathrm{i}} % Imaginary unit
+\newcommand{\e}{\mathrm{e}} % Euler number
+\newcommand{\rc}{r_{\text{c}}}
+
 % Blackboard bold
@@
 To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
-Simple systems that are analytically solvable are of great importance in theoretical chemistry and physics as they can be employed to illustrate concepts and test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but they retain much of the key physics.
-
-Using the (localised) site basis, the (singlet) Hilbert space of the Hubbard dimer comprises the four configurations
+Analytically solvable model systems are essential in theoretical chemistry and physics as the simplicity of the
+mathematics compared to realistic systems (e.g.\ atoms and molecules) readily allows concepts to be illustrated and new methods to be tested wile retaining much 
+of the key physics.
+
+Using the (localised) site basis, the Hilbert space of the Hubbard dimer comprises the four configurations
 \begin{align}
@@
 where $\Lsi$ ($\Rsi$) denotes an electron with spin $\sigma$ on the left (right) site.
-The exact [or full configuration interaction (FCI)] Hamiltonian is then 
+The exact, or full configuration interaction (FCI), Hamiltonian is then 
 \begin{equation}
@@
 We refer the interested reader to Refs.~\onlinecite{Carrascal_2015,Carrascal_2018} for more details about this system.
-The parameter $U$ dictates the correlation regime. 
-In the weak correlation regime (\ie, small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
+The parameter $U$ controls the strength of the electron correlation.
+In the weak correlation regime (small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
 In the large-$U$ (or strong correlation) regime, the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
-This phenomenon is sometimes referred to as a Wigner crystallisation. \cite{Wigner_1934}
+This phenomenon is often referred to as a Wigner crystallisation. \cite{Wigner_1934}
 
@@
 
-Within the Born-Oppenheimer approximation, 
+Within the Born-Oppenheimer approximation, the exact molecular Hamiltonian with $\Ne$ electrons and 
+$\Nn$ (clamped) nuclei is defined as
 \begin{equation}\label{eq:ExactHamiltonian}
-    \hH = - \frac{1}{2} \sum_{i}^{n} \grad_i^2 - \sum_{i}^{n} \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} + \sum_{i<j}^{n}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}
-\end{equation}
-is the exact electronic Hamiltonian for a chemical system with $N$ electrons (where $\vb{r}_i$ is the position of the $i$th electron) and $M$ (fixed) nuclei (where $\vb{R}_A$ and $Z_A$ are the position and the charge of the $A$th nucleus respectively).
-The first term is the kinetic energy of the electrons, the two following terms account respectively for the electron-nucleus attraction and the electron-electron repulsion.
-Note that we use atomic units throughout unless otherwise stated.
-
-Within (time-independent) Rayleigh-Schr\"odinger perturbation theory, the Schr\"odinger equation 
-\begin{equation} \label{eq:SchrEq}
-	\hH \Psi = E \Psi
-\end{equation} 
+    \hH = 
+    - \frac{1}{2} \sum_{i}^{\Ne} \grad_i^2 
+    - \sum_{i}^{\Ne} \sum_{A}^{\Nn} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+    + \sum_{i<j}^{\Ne}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}},
+\end{equation}
+where $\vb{r}_i$ defines the position of the $i$-th electron, and $\vb{R}_{A}$ and $Z_{A}$ are the position
+and charge of the $A$-th nucleus respectively.
+The first term represents the kinetic energy of the electrons, while 
+the two following terms account for the electron-nucleus attraction and the electron-electron repulsion.
+Atomic units are used unless otherwise stated.
+
+% EXACT SCHRODINGER EQUATION
+The exact many-electron wave function $\Psi$ corresponds to the solution of the (time-independent)
+Schr\"{o}dinger equation
+\begin{equation} 
+	\hH\Psi = E \Psi,
+    \label{eq:SchrEq}
+\end{equation} 
+with the eigenvalue $E$ providing the exact energy.
+Exact solutions to Eq.~\eqref{eq:SchrEq} are only possible in the simplest of systems, such as 
+the one-electron hydrogen atom. 
+In practice, one of the most common approximations involves
+a perturbative expansion of the energy.
+% SUMMARY OF RS-PT
+Within Rayleigh-Schr\"odinger perturbation theory, the time-independent Schr\"odinger equation 
 is recast as 
-\begin{equation} \label{eq:SchrEq-PT}
-	\hH(\lambda) \Psi(\lambda) = (\hH^{(0)} + \lambda \hV ) \Psi(\lambda) = E(\lambda) \Psi(\lambda),
-\end{equation}
-where $\hH^{(0)}$ is the zeroth-order Hamiltonian and $\hV = \hH - \hH^{(0)}$ is the so-called perturbation.
-The ``physical'' system of interest is recovered by setting the coupling parameter $\lambda$ to unity.
-This decomposition is obviously non-unique and motivated by several factors as discussed below. \cite{Mihalka_2017b}
-
-Accordingly to Eq.~\eqref{eq:SchrEq-PT}, the energy can then be written as a power series of $\lambda$
-\begin{equation} \label{eq:Elambda}
-	E(\lambda) = \sum_{k=0}^\infty \lambda^k E^{(k)}.
-\end{equation}
-However, it is not guaranteed that the series \eqref{eq:Elambda} has a radius of convergence $\abs{\lambda_0} < 1$. 
-In other words, the series might well be divergent for the physical system at $\lambda = 1$. 
-One can prove that the actual value of the radius of convergence $\abs{\lambda_0}$ can be obtained by looking for the singularities of $E(\lambda)$ in the complex $\lambda$ plane.
-This is due to the following theorem: \cite{Goodson_2012}
+\begin{equation} 
+	\hH(\lambda) \Psi(\lambda) 
+    = \qty(\hH^{(0)} + \lambda \hV ) \Psi(\lambda) 
+    = E(\lambda) \Psi(\lambda),
+    \label{eq:SchrEq-PT}
+\end{equation}
+where $\hH^{(0)}$ is a zeroth-order Hamiltonian and $\hV = \hH - \hH^{(0)}$ represents the perturbation operator.
+Expanding the wave function and energy as power series in $\lambda$ as 
+\begin{subequations}
+\begin{align}
+    \Psi(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,\Psi^{(k)} 
+    \label{eq:psi_expansion}
+    \\
+    E(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,E^{(k)}
+    \label{eq:E_expansion}
+\end{align}
+\end{subequations}
+and solving the corresponding perturbation equations up to a given order $k$ then 
+yields approximate solutions to Eq.~\eqref{eq:SchrEq}.
+
+% MATHEMATICAL REPRESENTATION
+Mathematically, Eq.~\eqref{eq:E_expansion} corresponds to a Taylor series expansion of the exact energy
+around the reference system $\lambda = 0$.
+The energy of the target ``physical'' system is then recovered at the point $\lambda = 1$.
+However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
+When $\rc < 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
+for the physical system.
+The value of $\rc$ can vary significantly between different systems and strongly depends on the particular decomposition
+of the reference and perturbation Hamiltonians in Eq.~\eqref{eq:SchrEq-PT}.\cite{Mihalka_2017b}
+
+% LAMBDA IN THE COMPLEX PLANE
+From complex-analysis, the radius of convergence for the energy can be obtained by looking for the 
+singularities of $E(\lambda)$ in the complex $\lambda$ plane.
+This property arises from the following theorem: \cite{Goodson_2012}
 \begin{quote}
-	\textit{``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ if the function is non-singular at all values of $z$ in the circular region centred at $z_0$ with radius $\abs{z_1-z_0}$.
-If the function has a singular point $z_s$ such that $\abs{z_s-z_0} < \abs{z_1-z_0}$, then the series will diverge when evaluated at $z_1$.''}
+\it
+``The Taylor series about a point $z_0$ of a function over the complex $z$ plane will converge at a value $z_1$ 
+if the function is non-singular at all values of $z$ in the circular region centred at $z_0$ with radius $\abs{z_1-z_0}$. 
+If the function has a singular point $z_s$ such that $\abs{z_s-z_0} < \abs{z_1-z_0}$, 
+then the series will diverge when evaluated at $z_1$.''
 \end{quote}
-This theorem means that the radius of convergence of the perturbation series is equal to the distance to the origin of the closest singularity of $E(\lambda)$.
-To illustrate this result we consider the simple function \cite{BenderBook}
+As a result, the radius of convergence for a function is equal to the distance from the origin of the closest singularity
+in the complex plane.
+For example, the simple function \cite{BenderBook}
 \begin{equation} \label{eq:DivExample}
@@
 \end{equation}
-This function is smooth for $x \in \mathbb{R}$ and infinitely differentiable in $\mathbb{R}$.
-One would expect that the Taylor series of such a function would be convergent $\forall x \in \mathbb{R}$.
-However this series is divergent for $x \ge 1$.
-This is because the function has four singularities in the complex plane ($x = e^{i\pi/4}$, $e^{-i\pi/4}$, $e^{i3\pi/4}$, and $e^{-i3\pi/4}$) with a modulus equal to $1$.
-This simple yet powerful example emphasizes the importance of the singularities in the complex plane to understand the convergence properties on the real axis.
+is smooth and infinitely differentiable for $x \in \mathbb{R}$, and one might expect that its Taylor series expansion would 
+converge in this domain.
+However, this series diverges $x \ge 1$.
+This divergence occurs because $f(x)$ has four singularities in the complex 
+($\e^{\i\pi/4}$, $\e^{-\i\pi/4}$, $\e^{\i3\pi/4}$, and $\e^{-\i3\pi/4}$) with a modulus equal to $1$, demonstrating
+that complex singularities are essential to fully understand the series convergence on the real axis.
+
+The radius of convergence of the perturbation series is therefore dictated by the magnitude $|\lambda_0|$ of the
+singularity in $E(\lambda)$ that is closest to the origin.
+\hugh{Like the exact system in Section~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
+a ``one-to-many'' function with the output elements representing an approximation to both the ground and excited states.
+The most common singularities on $E(\lambda)$ therefore correspond to non-analytic EPs in the complex 
+$\lambda$ plane where two states become degenerate.
+We will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
+ultimately determines the convergence properties of the perturbation series.
+}
 
@@
 
-In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$ [where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates] defined as an antisymmetric combination of $N$ (real-valued) one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
+% SUMMARY OF HF
+In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
+This Slater determinant is defined as an antisymmetric combination of $\Ne$ (real-valued) occupied one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
 \begin{equation}\label{eq:FockOp}
-	\Hat{f}(\vb{x}) \phi_p(\vb{x}) = [ \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}),
-\end{equation}
-where 
+    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty( \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ) \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
+\end{equation}
+Here the core Hamiltonian is
 \begin{equation}
@@
 \end{equation}
-is the core Hamiltonian and 
-\begin{equation}
-	\Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
-\end{equation}
-is the HF mean-field potential with 
+and
+\begin{equation}
+    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty( \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) )
+\end{equation}
+is the HF mean-field electron-electron potential with 
 \begin{subequations}
@@
 	\label{eq:CoulOp}
-	\Hat{J}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ] \phi_j(\vb{x}),
+    \Hat{J}_i(\vb{x})\phi_j(\vb{x})=\qty(\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_i(\vb{x}') \dd\vb{x}' ) \phi_j(\vb{x}),
 	\\
 	\label{eq:ExcOp}
-	\Hat{K}_i(\vb{x})\phi_j(\vb{x})=\qty[\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_j(\vb{x}') \dd\vb{x}'] \phi_i(\vb{x}),
+\Hat{K}_i(\vb{x})\phi_j(\vb{x})=\qty(\int \phi_i(\vb{x}')\frac{1}{\abs{\vb{r} - \vb{r}'}}\phi_j(\vb{x}') \dd\vb{x}')\phi_i(\vb{x}),
 \end{gather}
 \end{subequations}
-being the Coulomb and exchange operators (respectively) in the spin-orbital basis. \cite{SzaboBook}
+defining the Coulomb and exchange operators (respectively) in the spin-orbital basis.\cite{SzaboBook}
 The HF energy is then defined as 
@@
 \end{equation}
-with
+with the corresponding matrix elements
 \begin{align}
@@
 \end{align}
-If the spatial part of the spin-orbitals are restricted to be the same for spin-up and spin-down electrons, one talks about restricted HF (RHF) theory, whereas if one does not enforce this constrain it leads to the so-called unrestricted HF (UHF) theory.
-From hereon, $i$ and $j$ are occupied orbitals, $a$ and $b$ are unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ indicate arbitrary orbitals.
-
-Rather than solving Eq.~\eqref{eq:SchrEq}, HF theory uses the variational principle to find an approximation of $\Psi$ as a single Slater determinant.
-Hence a Slater determinant is not an eigenfunction of the exact Hamiltonian $\hH$.
-However, it is, by definition, an eigenfunction of the so-called (approximated) HF many-electron Hamiltonian defined as the sum of the one-electron Fock operators
+The optimal HF wave function is identified by using the variational principle to minimise the HF energy.
+For any system with more than one electron, the resulting Slater determinant is not an eigenfunction of the exact Hamiltonian $\hH$. 
+However, it is by definition an eigenfunction of the approximate many-electron HF Hamiltonian constructed 
+from the one-electron Fock operators as
 \begin{equation}\label{eq:HFHamiltonian}
@@
 \end{equation}
+From hereon, $i$ and $j$ denote occupied orbitals, $a$ and $b$ denote unoccupied (or virtual) orbitals, while $p$, $q$, $r$, and $s$ denote arbitrary orbitals.
+
+% BRIEF FLAVOURS OF HF
+\hugh{In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
+and contain a mixture of spin-up and spin-down components.
+However, the application of HF with some level of constraint on the orbital structure is far more common.
+Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, while allowing different for different spins leads to the so-called unrestricted HF (UHF) approach.
+The advantage of the UHF approximation is its ability to correctly describe strongly correlated systems, 
+such as the dissociation of the hydrogen dimer.\cite{Coulson_1949}
+However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
+the total spin $\hat{\mathcal{S}}^2$ operator, leading to so-called ``spin-contamination'' in the wave function.}
 
@@
 
-Coming back to the Hubbard dimer, the HF energy is [see Eq.~\eqref{eq:E_HF}]
-\begin{equation}
-	E_\text{HF} = -t \qty[ \sin \theta_\alpha  + \sin \theta_\beta ] + \frac{U}{2} \qty[ 1 + \cos \theta_\alpha \cos \theta_\beta ],
-\end{equation}
-where 
+Returning to the Hubbard dimer, the UHF energy can be parametrised in terms of two rotation angles $\ta$ and $\tb$ as
+\begin{equation}
+E_\text{HF}(\ta, \tb) = -t \qty( \sin \ta + \sin \tb ) + \frac{U}{2} \qty( 1 + \cos \ta \cos \tb ),
+\end{equation}
+where we have introduced bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for 
+the spin-$\sigma$ electrons as
 \begin{align}
-	\mathcal{B}^{\sigma} & = \cos(\frac{\theta_\sigma}{2}) \Lsi + \sin(\frac{\theta_\sigma}{2}) \Rsi,
+    \mathcal{B}^{\sigma} & = \hphantom{-} \cos(\frac{\theta_\sigma}{2}) \Lsi + \sin(\frac{\theta_\sigma}{2}) \Rsi,
 	\\
@@
 \end{align}
-are the bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for the spin-$\sigma$ electrons. 
-The angles which minimises the HF energy, \ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are 
-\begin{equation}
-	\theta_\text{RHF}^\alpha = \theta_\text{RHF}^\beta = \pi/4,
-\end{equation}
-for $0 \le U \le 4t$, yielding
+In the weak correlation regime $0 \le U \le 2t$, the angles which minimise the HF energy, 
+\ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are 
+\begin{equation}
+	\ta^\text{RHF} = \tb^\text{RHF} = \pi/4,
+\end{equation}
+giving the symmetry-pure molecular orbitals
 \begin{align}
@@
 \end{align}
-and the following RHF ground-state energy:
+and the ground-state RHF energy
 \begin{equation}
@@
 \end{equation}
-In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
-The RHF wave function cannot model properly the physics of the system at large $U$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite sites.
-
-Within the HF approximation, at the critical value of $U = 4t$, famously known as the Coulson-Fischer point, \cite{Coulson_1949} a symmetry-broken UHF solution appears with a lower energy than the RHF one.
-Indeed, for $U \ge 4t$, we have
+However, in the strongly correlated regime (large $U$), the closed-shell restriction on the orbitals prevents RHF from 
+correctly modelling the physics of the system with the two electrons on opposing sites.
+
+As the on-site repulsion is increased from 0, the HF approximation reaches a critical value at $U=2t$ where a symmetry-broken 
+UHF solution appears with a lower energy than the RHF one.
+This critical point is analogous to the infamous Coulson--Fischer point identified in the hydrogen dimer.\cite{Coulson_1949}
+For $U \ge 2t$, the optimal orbital rotation angles for the UHF orbitals become
 \begin{align}
-	\theta_\text{UHF}^\alpha & = \titou{\arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U})},
+	\ta^\text{UHF} & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}),
+    \label{eq:ta_uhf}
 	\\
-	\theta_\text{UHF}^\beta & = \titou{\arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U})},
+	\tb^\text{UHF} & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}),
+    \label{eq:tb_uhf}
 \end{align}
-and the corresponding UHF ground-state energy is
+with the corresponding UHF ground-state energy
 \begin{equation}
@@
 \end{equation}
-Note that, for $U \ge 4t$, the RHF wave function remains a genuine solution of the HF equations but corresponds to a saddle point, not a minimum.
+Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped pair, obtained 
+by swapping $\ta^{\text{UHF}}$ and $\tb^{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
+Note that the RHF wave function remains a genuine solution of the HF equations for $U \ge 2t$, but corresponds to a saddle point 
+of the HF energy rather than a minimum.
 

### 2020-11-18 Manuscript/EPAWTFT.tex
add sec eq and iAC paragraphs

@@
 While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Fig.~\ref{subfig:FCI_real}).
+
 At non-zero values of $U$ and $t$, these closed-shell singlets can only become degenerate at a pair of complex conjugate points in the complex $\lambda$ plane 
@@
 \end{subequations}
-and solving the corresponding perturbation equations up to a given order $k$ then 
-yields approximate solutions to Eq.~\eqref{eq:SchrEq}.
+and solving the corresponding perturbation equations up to a given order $k$, then 
+yields approximate solutions to Eq.~\eqref{eq:SchrEq} \titou{by setting $\lambda = 1$}.
 
@@
 However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
-When $\rc < 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
+When $\rc \titou{\le} 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
 for the physical system.
@@
 
-The radius of convergence of the perturbation series is therefore dictated by the magnitude $|\lambda_0|$ of the
+The radius of convergence of the perturbation series is therefore dictated by the magnitude $\abs{\lambda_0}$ of the
 singularity in $E(\lambda)$ that is closest to the origin.
-\hugh{Like the exact system in Section~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
+Like the exact system in Section~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
 a ``one-to-many'' function with the output elements representing an approximation to both the ground and excited states.
@@
 ultimately determines the convergence properties of the perturbation series.
-}
+
+\titou{Practically, to locate EPs in a more complicated systems, one must solve simultaneously the following equations: \cite{Cejnar_2007}
+\begin{subequations}
+\begin{align}
+	\label{eq:PolChar}
+	\det[E\hI-\hH(\lambda)] & = 0,
+	\\ 
+	\label{eq:DPolChar}
+	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
+\end{align}
+\end{subequations}
+where $\hI$ is the identity operator.
+Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system. 
+If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is, at least, two-fold degenerate. 
+These degeneracies can be conical intersections between two states with different symmetries for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.}
 
@@
 % BRIEF FLAVOURS OF HF
-\hugh{In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
+In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
 and contain a mixture of spin-up and spin-down components.
@@
 However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
-the total spin $\hat{\mathcal{S}}^2$ operator, leading to so-called ``spin-contamination'' in the wave function.}
+the total spin $\hat{\mathcal{S}}^2$ operator, leading to so-called ``spin-contamination'' in the wave function.
 
@@
 \begin{equation}
-	E_\text{RHF} =  -2t + \frac{U}{2}
+	E_\text{RHF} \equiv E_\text{HF}(\ta^\text{RHF}, \tb^\text{RHF}) = -2t + \frac{U}{2}
 \end{equation}
@@
 \begin{equation}
-	E_\text{UHF} = - \frac{2t^2}{U}.
+	E_\text{UHF} \equiv E_\text{HF}(\ta^\text{UHF}, \tb^\text{UHF}) = - \frac{2t^2}{U}.
 \end{equation}
@@
 of the HF energy rather than a minimum.
+
+\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
+In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
+\cite{Seidl_2018}
+In such a way, we could obtain a doubly-excited state wave function starting from the ground state wave function, a process which is not as easy as one might think.
+\cite{Gilbert_2008,Thom_2008,Shea_2018}
+One of the fundamental discovery we made was that Coulson-Fisher points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
+The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
+It perfectly illustrates the deeper topology of electronic states revealed using a complex-scaled electron-electron interaction.
+Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{iAC}
+	\caption{
+	\label{fig:iAC}
+	An example of complex adiabatic connection. \cite{Burton_2019}}
+\end{figure}
 

### 2020-11-18 Manuscript/EPAWTFT.tex
moving Hubbard MP section
saving work in MP section

@@
 
+%============================================================%
+\subsection{Complex adiabatic connection}
+%============================================================%
+
 \titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
@@
 iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
+
+Let us illustrate the behaviour of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
+Within the RMP partition technique, we have 
+\begin{equation}
+\label{eq:H_RMP}
+	\bH_\text{RMP} = 
+	\begin{pmatrix}
+		-2t + U - \lambda U/2	&	0					&	0					&	\lambda U/2	\\
+		0						&	U - \lambda U/2 	&	\lambda U/2			&	0	\\
+		0						&	\lambda U/2			&	U - \lambda U/2 	&	0	\\
+		\lambda U/2 			&	0 					&	0					&	2t + U - \lambda U/2	\\
+	\end{pmatrix},
+\end{equation}
+which yields the ground-state energy 
+\begin{equation}
+	\label{eq:E0MP}
+	E_{-}(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}.
+\end{equation}
+From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
+Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction
+\begin{equation}
+	E_\text{MP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2),
+\end{equation}
+with 
+\begin{equation}
+	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
+\end{equation}
+The convergence of the RMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3.5$ (where $r_c > 1$) and $4.5$ (where $r_c < 1$) is illustrated in Fig.~\ref{subfig:RMP_cvg}.
+The Riemann surfaces associated with the exact energy of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$ (see Figs.~\ref{subfig:RMP_3.5} and \ref{subfig:RMP_4.5}).
+From these, one \titou{clearly?} sees that the EP is outside (inside) the (pink) cylinder of unit radius for $U/t = 3.5$ ($4.5$),
+and the centre graph of Fig.~\ref{fig:RMP} evidences the convergent (divergent) nature of the RMP series.
+Interestingly, one can show that the convergent and divergent series start to differ at fourth order.
+
+%%% FIG 2 %%%
+\begin{figure*}
+	\begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig2a}	
+		\subcaption{\label{subfig:RMP_3.5} $U/t = 3.5$}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig2b}
+		\subcaption{\label{subfig:RMP_cvg}}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig2c}	
+		\subcaption{\label{subfig:RMP_4.5} $U/t = 4.5$}
+    \end{subfigure}
+	\caption{
+	Convergence of the RMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3.5$ (where $r_c > 1$) and $4.5$ (where $r_c < 1$).
+	The Riemann surfaces associated with the exact energy of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$. 
+	\label{fig:RMP}}
+\end{figure*}
+
+The behaviour of the UMP series is more subtle as the spin-contamination comes into play and introduces additional coupling between electronic states.
+The UMP partitioning yield the following $\lambda$-dependent Hamiltonian:
+\begin{widetext}
+\begin{equation}
+\label{eq:H_UMP}
+	\bH_\text{UMP} = 
+	\begin{pmatrix}
+		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
+		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
+	\end{pmatrix},
+\end{equation}
+\end{widetext}
+A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting its expression.
+The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{eq:UMP_rc}.
+Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
+This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
+
+The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{fig:UMP} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
+
+For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is a pretty good estimate. 
+Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
+
+For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
+We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
+An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually!
+
+On the other hand, there is an exceptional point on the excited energy surface that is well within the radius of convergence.
+We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
+at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
+In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
+the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
+
+%%% FIG 3 %%%
+\begin{figure*}
+	\begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig3c}	
+		\subcaption{\label{subfig:UMP_3} $U/t = 3$}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig3b}
+		\subcaption{\label{subfig:UMP_cvg}}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{fig3a}	
+		\subcaption{\label{subfig:UMP_7} $U/t = 7$}
+    \end{subfigure}	\caption{
+	Convergence of the UMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3$ and $7$.
+	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
+	\label{fig:UMP}}
+\end{figure*}
 
@@
 The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
-
-%%% FIG 2 %%%
-\begin{figure*}
-	\includegraphics[height=0.25\textwidth]{fig2a}	
-	\hspace{0.05\textwidth}
-	\includegraphics[height=0.25\textwidth]{fig2b}
-	\hspace{0.05\textwidth}
-	\includegraphics[height=0.25\textwidth]{fig2c}	
-	\caption{
-	Convergence of the RMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3.5$ (before the radius of convergence) and $4.5$ (after the radius of convergence).
-	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
-	\label{fig:RMP}}
-\end{figure*}
-
-Let us illustrate the behaviour of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
-Within the RMP partition technique, we have 
-\begin{equation}
-\label{eq:H_RMP}
-	\bH_\text{RMP} = 
-	\begin{pmatrix}
-		-2t + U - \lambda U/2	&	0					&	0					&	\lambda U/2	\\
-		0						&	U - \lambda U/2 	&	\lambda U/2			&	0	\\
-		0						&	\lambda U/2			&	U - \lambda U/2 	&	0	\\
-		\lambda U/2 			&	0 					&	0					&	2t + U - \lambda U/2	\\
-	\end{pmatrix},
-\end{equation}
-which yields the ground-state energy 
-\begin{equation}
-	\label{eq:E0MP}
-	E_{-}(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}.
-\end{equation}
-From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
-Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction
-\begin{equation}
-	E_\text{MP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2),
-\end{equation}
-with 
-\begin{equation}
-	E_{-}(\lambda) = \sum_{k=0}^\infty E_\text{MP}^{(k)} \lambda^k.
-\end{equation}
-We illustrate this by plotting the energy expansions at orders of $\lambda$ just below and above the radius of convergence in Fig.~\ref{fig:RMP}.
-
-At the UMP level now, we have
-\begin{widetext}
-\begin{equation}
-\label{eq:H_UMP}
-	\bH_\text{UMP} = 
-	\begin{pmatrix}
-		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
-		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
-	\end{pmatrix},
-\end{equation}
-\end{widetext}
-A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting its expression.
-The convergence of the UMP as a function of the ratio $U/t$ is depicted in Fig.~\ref{fig:UMP}.
-
-%%% FIG 3 %%%
-\begin{figure*}
-    \centering
-	\includegraphics[height=0.23\textwidth]{fig3a}	
-	\hspace{0.05\textwidth}
-	\includegraphics[height=0.23\textwidth]{fig3b}
-	\hspace{0.05\textwidth}
-	\includegraphics[height=0.23\textwidth]{fig3c}	
-	\caption{
-	Convergence of the URMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3$ and $7$.
-	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
-	\label{fig:UMP}}
-\end{figure*}
 

### 2020-11-18 Manuscript/EPAWTFT.tex
Added Mayer GHF reference

@@
 
-\titou{Practically, to locate EPs in a more complicated systems, one must solve simultaneously the following equations: \cite{Cejnar_2007}
+\titou{Practically, to locate EPs in a more complicated systems, one must solve simultaneously the following equations:\cite{Cejnar_2007}
 \begin{subequations}
@@
 In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
-and contain a mixture of spin-up and spin-down components.
+and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993}
 However, the application of HF with some level of constraint on the orbital structure is far more common.

### 2020-11-19 Manuscript/EPAWTFT.tex
update MP

@@
 % BRIEF FLAVOURS OF HF
-In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
+In the most flexible variant of real HF theory (generalised HF \cite{Mayer_1993}) the one-electron orbitals can be complex-valued
 and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993}
@@
 	Convergence of the RMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3.5$ (where $r_c > 1$) and $4.5$ (where $r_c < 1$).
-	The Riemann surfaces associated with the exact energy of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$. 
+	The Riemann surfaces associated with the exact energies of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$ as functions of $\lambda$. 
 	\label{fig:RMP}}
@@
 \end{widetext}
-A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting its expression.
-The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{eq:UMP_rc}.
+A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
+The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in \titou{Fig.~\ref{eq:UMP_rc}}.
+
+The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
 Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
 This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
-
-The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{fig:UMP} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
-
-For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is a pretty good estimate. 
+For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
 Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
-
 For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
 We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
-An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually!
-
-On the other hand, there is an exceptional point on the excited energy surface that is well within the radius of convergence.
-We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
-at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
-In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
-the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
+An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
+%On the other hand, there is an EP on the excited energy surface that is well within the radius of convergence.
+%We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
+%at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
+%In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
+%the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
 
@@
 	\begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig3c}	
+	\includegraphics[height=0.75\textwidth]{fig3a}	
 		\subcaption{\label{subfig:UMP_3} $U/t = 3$}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig3a}	
+	\includegraphics[height=0.75\textwidth]{fig3c}	
 		\subcaption{\label{subfig:UMP_7} $U/t = 7$}
@@
 	Convergence of the UMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3$ and $7$.
-	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
+	The Riemann surfaces associated with the exact energies of the UMP Hamiltonian \eqref{eq:H_UMP} are also represented for these two values of $U/t$ as functions of $\lambda$.
 	\label{fig:UMP}}

### 2020-11-19 Manuscript/EPAWTFT.tex
Modifications to HF section

@@
 
+\begin{figure}
+\includegraphics[width=\linewidth]{HF_real.pdf}
+\caption{\label{fig:HF_real}
+\hugh{RHF and UHF energies as a function of the correlation strength $U/t$. 
+The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot).}}
+\end{figure}
+
 Returning to the Hubbard dimer, the UHF energy can be parametrised in terms of two rotation angles $\ta$ and $\tb$ as
@@
 \end{align}
-and the ground-state RHF energy
+and the ground-state RHF energy (Fig.~\ref{fig:HF_real})
 \begin{equation}
@@
 \end{align}
-with the corresponding UHF ground-state energy
+with the corresponding UHF ground-state energy (Fig.~\ref{fig:HF_real})
 \begin{equation}
@@
 %============================================================%
+
+%%% FIG 1 %%%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+    \includegraphics[height=0.65\textwidth,trim={0pt 0pt 0pt -30pt},clip]{HF_cplx_angle}
+	\subcaption{\label{subfig:UHF_cplx_angle}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{HF_cplx_energy}
+	\subcaption{\label{subfig:UHF_cplx_energy}}
+    \end{subfigure}
+	\caption{%
+    Analytic continuation of HF into the complex $\lambda$ plane.
+	\label{fig:HF_cplx}}
+\end{figure*}
 
@@
 Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{iAC}
-	\caption{
-	\label{fig:iAC}
-	An example of complex adiabatic connection. \cite{Burton_2019}}
-\end{figure}
 

### 2020-11-19 Manuscript/EPAWTFT.tex
local changes

--- 2020-11-18 Manuscript/EPAWTFT.tex
@@
 \begin{align}
-	\ta^\text{UHF} & = \arctan (-\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}),
+    \ta^\text{UHF} & = \arctan (-\frac{2t}{\sqrt{U^2 - 4t^2}}),
     \label{eq:ta_uhf}
 	\\
-	\tb^\text{UHF} & = \arctan (+\frac{\sqrt{U^2 - 4t^2}}{U},\frac{2t}{U}),
+    \tb^\text{UHF} & = \arctan (+\frac{2t}{\sqrt{U^2 - 4t^2}}),
     \label{eq:tb_uhf}
@@
 %============================================================%
+
+Self-consistency in HF approximations leads to the inherently non-linear Fock eigenvalue
+problem that is normally solved using an iterative approach.
+Alternatively, the non-linear terms arising from the Coulomb and exchange can be considered
+as a perturbation from the reference core Hamiltonian problem by introducing the parameterised Fock operator
+\begin{equation}
+    \Hat{f}_{\lambda}(\vb{x}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+\end{equation}
+The orbitals in the reference problem correspond to the symmetry-pure eigenfunctions of the one-electron core
+Hamiltonian, while self-consistent solutions at $\lambda = 1$ represent the orbitals of the exact HF solution.
 

### 2020-11-19 Manuscript/EPAWTFT.tex

--- 2020-11-19 Manuscript/EPAWTFT.tex
@@
 %============================================================%
+Self-consistency in HF approximations leads to the inherently non-linear Fock eigenvalue
+problem that is normally solved using an iterative approach.
+Alternatively, the non-linear terms arising from the Coulomb and exchange can be considered
+as a perturbation from the reference core Hamiltonian problem by introducing the parameterised Fock operator
+\begin{equation}
+    \Hat{f}_{\lambda}(\vb{x}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+\end{equation}
+The orbitals in the reference problem correspond to the symmetry-pure eigenfunctions of the one-electron core
+Hamiltonian, while self-consistent solutions at $\lambda = 1$ represent the orbitals of the exact HF solution.
 

### 2020-11-19 Manuscript/EPAWTFT.tex
Added discussion on self-consistency as a perturbation

--- 2020-11-19 Manuscript/EPAWTFT.tex
@@
 %============================================================%
-\subsection{Complex adiabatic connection}
+\subsection{Self-consistency as a perturbation} %OR {Complex adiabatic connection}
 %============================================================%
 
-%%% FIG 1 %%%
+%%% FIG 3 (?) %%%
+% Analytic Continuation of HF
+%%%%%%%%%%%%%%%%%
 \begin{figure*}[t]
@@
 \end{figure*}
-
+%%%%%%%%%%%%%%%%%
+
+% INTRODUCE PARAMETRISED FOCK HAMILTONIAN
+\hugh{The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
+in the HF approximation, and is usually solved through an iterative approach.\cite{SzaboBook}
+Alternatively, the non-linear terms arising from the Coulomb and exchange operators can 
+be considered as a perturbation from the core Hamiltonian by introducing the
+transformation $U \rightarrow \lambda\, U$, giving the parametrised Fock operator 
+\begin{equation}
+    \Hat{f}_{\lambda}(\vb{x}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+\end{equation}
+The orbitals in the reference problem $\lambda=0$ correspond to the symmetry-pure eigenfunctions of the one-electron core
+Hamiltonian, while self-consistent solutions at $\lambda = 1$ represent the orbitals of the true HF solution.}
+
+% INTRODUCE COMPLEX ANALYTIC-CONTINUATION
+\hugh{For real $\lambda$, the self-consistent HF energies at give (real) $U$ and $t$ values
+in the Hubbard dimer directly mirror the energies shown in Fig.~\ref{fig:HF_real}, 
+with coalesence points at 
+\begin{equation}
+    \lambda_{\text{c}} = \pm \frac{2t}{U}.
+\end{equation}
+In contrast, when $\lambda$ becomes complex, the HF equations become non-Hermitian and 
+each HF solutions can be analytically continued for all $\lambda$ values using
+the holomorphic HF approach.\cite{Hiscock_2014,Burton_2016,Burton_2018}
+Remarkably, the coalescence point in this analytic continuation emerges as a 
+\textit{quasi}-EP on the real $\lambda$ axis (Fig.~\ref{fig:HF_cplx}), where
+the different HF solutions become equivalent but not self-orthogonal.\cite{Burton_2019}
+By analogy with perturbation theory, the regime where this quasi-EP occurs 
+within $\lambda_{\text{c}} \le 1$ can be interpreted as an indication that 
+the symmetry-pure reference orbitals no longer provide a qualitatively 
+accurate representation for the true HF ground state at $\lambda = 1$.
+For example, in the Hubbard dimer with $U > 2t$, one finds $\lambda_{\text{c}} < 1$ and the symmetry-pure orbitals
+do not provide a good representation of the HF ground state.
+In contrast, $U < 2t$ yields $\lambda_{\text{c}} > 1$ and corresponds to
+the regime where the HF ground state is correctly represented by symmetry-pure orbitals.}
+
+% COMPLEX ADIABATIC CONNECTION
 \titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).

### 2020-11-19 Manuscript/EPAWTFT.tex
minor edit
comment on complex adiabatic connection, added figure legend

@@
 \begin{equation}
-	\ta^\text{RHF} = \tb^\text{RHF} = \pi/4,
+	\ta^\text{RHF} = \tb^\text{RHF} = \pi/2,
 \end{equation}
@@
 correctly modelling the physics of the system with the two electrons on opposing sites.
+
+%%% FIG 3 (?) %%%
+% Analytic Continuation of HF
+%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+    \includegraphics[height=0.65\textwidth,trim={0pt 0pt 0pt -35pt},clip]{HF_cplx_angle}
+	\subcaption{\label{subfig:UHF_cplx_angle}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{HF_cplx_energy}
+	\subcaption{\label{subfig:UHF_cplx_energy}}
+    \end{subfigure}
+	\caption{%
+    \hugh{(\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
+    Symmetry-broken solutions correspond to an individual sheets and become equivalent at the quasi-EP (black dot).
+    The RHF solution is independent of $\lambda$, giving constant plane at $\pi/2$.
+    (\subref{subfig:UHF_cplx_energy}) The corresponding HF energy surfaces show a non-analytic 
+    point at the quasi-exceptional point.}
+	\label{fig:HF_cplx}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%
 
@@
 
-%%% FIG 3 (?) %%%
-% Analytic Continuation of HF
-%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-	\begin{subfigure}{0.49\textwidth}
-    \includegraphics[height=0.65\textwidth,trim={0pt 0pt 0pt -30pt},clip]{HF_cplx_angle}
-	\subcaption{\label{subfig:UHF_cplx_angle}}
-    \end{subfigure}
-	\begin{subfigure}{0.49\textwidth}
-	\includegraphics[height=0.65\textwidth]{HF_cplx_energy}
-	\subcaption{\label{subfig:UHF_cplx_energy}}
-    \end{subfigure}
-	\caption{%
-    Analytic continuation of HF into the complex $\lambda$ plane.
-	\label{fig:HF_cplx}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%
-
 % INTRODUCE PARAMETRISED FOCK HAMILTONIAN
@@
     \lambda_{\text{c}} = \pm \frac{2t}{U}.
+    \label{eq:scaled_fock}
 \end{equation}
@@
 In contrast, $U < 2t$ yields $\lambda_{\text{c}} > 1$ and corresponds to
-the regime where the HF ground state is correctly represented by symmetry-pure orbitals.}
+the regime where the HF ground state is correctly represented by symmetry-pure orbitals.
+}
 
 % COMPLEX ADIABATIC CONNECTION
-\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
-In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
+\hugh{We have recently shown that the complex scaled Fock operator Eq.~\eqref{eq:scaled_fock}
+also allows states of different symmetries to be interconverted by following a well-defined
+contour in the complex $\lambda$-plane.\cite{Burton_2019}
+In particular, by slowly varying $\lambda$ in a similar (yet different) manner
+to an adiabatic connection in density-functional theory,\cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} 
+a ground-state wave function can be ``morphed'' into an excited-state wave function 
+via a stationary path of HF solutions.
+This novel approach to identifying excited-state wave functions demonstrates the fundamental 
+role of quasi-EPs in determining the behaviour of the HF approximation.}
+
+%\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
+%In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
 \cite{Seidl_2018}
-In such a way, we could obtain a doubly-excited state wave function starting from the ground state wave function, a process which is not as easy as one might think.
+%In such a way, we could obtain a doubly-excited state wave function starting from the ground state wave function, a process which is not as easy as one might think.
 \cite{Gilbert_2008,Thom_2008,Shea_2018}
-One of the fundamental discovery we made was that Coulson-Fisher points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
-The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
-It perfectly illustrates the deeper topology of electronic states revealed using a complex-scaled electron-electron interaction.
-Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
+%One of the fundamental discovery we made was that Coulson-Fisher points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
+%The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
+%It perfectly illustrates the deeper topology of electronic states revealed using a complex-scaled electron-electron interaction.
+%Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
 

### 2020-11-19 Manuscript/EPAWTFT.tex
typo fix

@@
 % INTRODUCE COMPLEX ANALYTIC-CONTINUATION
-\hugh{For real $\lambda$, the self-consistent HF energies at give (real) $U$ and $t$ values
+\hugh{For real $\lambda$, the self-consistent HF energies at given (real) $U$ and $t$ values
 in the Hubbard dimer directly mirror the energies shown in Fig.~\ref{fig:HF_real}, 

### 2020-11-19 Manuscript/EPAWTFT.tex
accepted \titou changes

@@
 and solving the corresponding perturbation equations up to a given order $k$, then 
-yields approximate solutions to Eq.~\eqref{eq:SchrEq} \titou{by setting $\lambda = 1$}.
+yields approximate solutions to Eq.~\eqref{eq:SchrEq} by setting $\lambda = 1$.
 
@@
 However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
-When $\rc \titou{\le} 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
+When $\rc \le 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
 for the physical system.
@@
 
-\titou{Practically, to locate EPs in a more complicated systems, one must solve simultaneously the following equations:\cite{Cejnar_2007}
+Practically, to locate EPs in a more complicated systems, one must simultaneously solve\cite{Cejnar_2007}
 \begin{subequations}
@@
 where $\hI$ is the identity operator.
-Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system. 
-If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is, at least, two-fold degenerate. 
-These degeneracies can be conical intersections between two states with different symmetries for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.}
+Equation \eqref{eq:PolChar} is the well-known secular equation providing the (eigen)energies of the system. 
+If the energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is at least two-fold degenerate. 
+These degeneracies can be conical intersections between two states with different symmetries 
+for real values of $\lambda$\cite{Yarkony_1996} or EPs between two states with the 
+same symmetry for complex values of $\lambda$.
 

### 2020-11-19 Manuscript/EPAWTFT.tex
more tweaks
more and more tweaks... now lunch

@@
 
+%%% FIG 2 (?) %%%
+% HF energies as a function of U/t
+%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%
 
@@
     \hugh{(\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
-    Symmetry-broken solutions correspond to an individual sheets and become equivalent at the quasi-EP (black dot).
+    Symmetry-broken solutions correspond to individual sheets and become equivalent at 
+    the \textit{quasi}-EP $\lambda_{\text{c}}$ (black dot).
     The RHF solution is independent of $\lambda$, giving constant plane at $\pi/2$.
     (\subref{subfig:UHF_cplx_energy}) The corresponding HF energy surfaces show a non-analytic 
-    point at the quasi-exceptional point.}
+    point at the \textit{quasi}-EP.}
 	\label{fig:HF_cplx}}
@@
 the different HF solutions become equivalent but not self-orthogonal.\cite{Burton_2019}
-By analogy with perturbation theory, the regime where this quasi-EP occurs 
+By analogy with perturbation theory, the regime where this \textit{quasi}-EP occurs 
 within $\lambda_{\text{c}} \le 1$ can be interpreted as an indication that 
@@
 This novel approach to identifying excited-state wave functions demonstrates the fundamental 
-role of quasi-EPs in determining the behaviour of the HF approximation.}
+role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.}
 

### 2020-11-19 Manuscript/EPAWTFT.tex
degreenified Hugh stuff

@@
     \caption{\label{fig:HF_real}
-    \hugh{RHF and UHF energies as a function of the correlation strength $U/t$. 
-    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot).}}
+    RHF and UHF energies as a function of the correlation strength $U/t$. 
+    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot) known as the Coulson-Fischer point.}
 \end{figure}
@@
 	\caption{%
-    \hugh{(\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
+    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
     Symmetry-broken solutions correspond to individual sheets and become equivalent at 
@@
     (\subref{subfig:UHF_cplx_energy}) The corresponding HF energy surfaces show a non-analytic 
-    point at the \textit{quasi}-EP.}
+    point at the \textit{quasi}-EP.
 	\label{fig:HF_cplx}}
@@
 % INTRODUCE PARAMETRISED FOCK HAMILTONIAN
-\hugh{The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
+The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
 in the HF approximation, and is usually solved through an iterative approach.\cite{SzaboBook}
@@
 The orbitals in the reference problem $\lambda=0$ correspond to the symmetry-pure eigenfunctions of the one-electron core
-Hamiltonian, while self-consistent solutions at $\lambda = 1$ represent the orbitals of the true HF solution.}
+Hamiltonian, while self-consistent solutions at $\lambda = 1$ represent the orbitals of the true HF solution.
 
 % INTRODUCE COMPLEX ANALYTIC-CONTINUATION
-\hugh{For real $\lambda$, the self-consistent HF energies at given (real) $U$ and $t$ values
+For real $\lambda$, the self-consistent HF energies at given (real) $U$ and $t$ values
 in the Hubbard dimer directly mirror the energies shown in Fig.~\ref{fig:HF_real}, 
@@
 the regime where the HF ground state is correctly represented by symmetry-pure orbitals.
-}
 
 % COMPLEX ADIABATIC CONNECTION
-\hugh{We have recently shown that the complex scaled Fock operator Eq.~\eqref{eq:scaled_fock}
+We have recently shown that the complex scaled Fock operator Eq.~\eqref{eq:scaled_fock}
 also allows states of different symmetries to be interconverted by following a well-defined
@@
 This novel approach to identifying excited-state wave functions demonstrates the fundamental 
-role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.}
+role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.
 
@@
 \cite{Gilbert_2008,Thom_2008,Shea_2018}
-%One of the fundamental discovery we made was that Coulson-Fisher points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
+%One of the fundamental discovery we made was that Coulson-Fischer points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
 %The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
@@
 Within the RMP partition technique, we have 
+\begin{widetext}
 \begin{equation}
@@
 \end{equation}
+\end{widetext}
 which yields the ground-state energy 
@@
 \end{equation}
-From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
+From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda_c = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
 Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction

### 2020-11-19 Manuscript/EPAWTFT.tex
edits to the HF section

--- 2020-11-19 Manuscript/EPAWTFT.tex
@@
-\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
+\documentclass[aps,prb,reprint,noshowkeys,linenumbers,superscriptaddress]{revtex4-1}
 \usepackage{subcaption}
@@
 In the large-$U$ (or strong correlation) regime, the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
-This phenomenon is often referred to as a Wigner crystallisation. \cite{Wigner_1934}
+This phenomenon is often referred to as Wigner crystallisation. \cite{Wigner_1934}
 
@@
 \end{equation}
-such that
-\begin{align}
-	E_{\pm}(2\pi) & = E_{\mp}(0),
-	&
-	E_{\pm}(4\pi) & = E_{\pm}(0). \notag
-\end{align}
+such that $E_{\pm}(2\pi)  = E_{\mp}(0)$ and $E_{\pm}(4\pi)  = E_{\pm}(0)$.
 As a result, completely encircling an EP leads to the interconversion of the two interacting states, while a second complete rotation returns the two states to their original energies.
@@
     \\
-    E(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,E^{(k)}
+    E(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,E^{(k)},
     \label{eq:E_expansion}
@@
 \end{subequations}
-and solving the corresponding perturbation equations up to a given order $k$, then 
-yields approximate solutions to Eq.~\eqref{eq:SchrEq} by setting $\lambda = 1$.
+solving the corresponding perturbation equations up to a given order $k$, and
+setting $\lambda = 1$ then yields approximate solutions to Eq.~\eqref{eq:SchrEq}.
 
@@
 around the reference system $\lambda = 0$.
-The energy of the target ``physical'' system is then recovered at the point $\lambda = 1$.
+The energy of the target ``physical'' system is recovered at the point $\lambda = 1$.
 However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
@@
 in the complex plane.
-For example, the simple function \cite{BenderBook}
+For example, the simple function
 \begin{equation} \label{eq:DivExample}
@@
 ($\e^{\i\pi/4}$, $\e^{-\i\pi/4}$, $\e^{\i3\pi/4}$, and $\e^{-\i3\pi/4}$) with a modulus equal to $1$, demonstrating
-that complex singularities are essential to fully understand the series convergence on the real axis.
-
-The radius of convergence of the perturbation series is therefore dictated by the magnitude $\abs{\lambda_0}$ of the
+that complex singularities are essential to fully understand the series convergence on the real axis.\cite{BenderBook}
+
+The radius of convergence for the perturbation series is therefore dictated by the magnitude $\abs{\lambda_0}$ of the
 singularity in $E(\lambda)$ that is closest to the origin.
@@
 $\lambda$ plane where two states become degenerate.
-We will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
+Later we will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
 ultimately determines the convergence properties of the perturbation series.
 
-Practically, to locate EPs in a more complicated systems, one must simultaneously solve\cite{Cejnar_2007}
+Practically, to locate EPs in a more complicated systems, one must simultaneously solve
 \begin{subequations}
@@
 \end{subequations}
-where $\hI$ is the identity operator.
+where $\hI$ is the identity operator.\cite{Cejnar_2007}
 Equation \eqref{eq:PolChar} is the well-known secular equation providing the (eigen)energies of the system. 
@@
 These degeneracies can be conical intersections between two states with different symmetries 
-for real values of $\lambda$\cite{Yarkony_1996} or EPs between two states with the 
+for real values of $\lambda$,\cite{Yarkony_1996} or EPs between two states with the 
 same symmetry for complex values of $\lambda$.
@@
     \label{eq:E_HF}
-	E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} ),
+    E_\text{HF} = \hugh{\frac{1}{2} \sum_i^{N} \Big( h_i + f_i \Big)},
+	%E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} ),
 \end{equation}
@@
 \begin{align}
-	h_i & = \mel{\phi_i}{\Hat{h}}{\phi_i},
-	&
-	J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
-	&
-	K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}.
+	h_i = \mel{\phi_i}{\Hat{h}}{\phi_i}
+    \quad \text{and} \quad
+    \hugh{f_i = \mel{\phi_i}{\Hat{f}}{\phi_i}.}
+	%J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
+	%&
+	%K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}.
 \end{align}
@@
 % BRIEF FLAVOURS OF HF
-In the most flexible variant of real HF theory (generalised HF \cite{Mayer_1993}) the one-electron orbitals can be complex-valued
+In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
 and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993}
@@
 However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
-the total spin $\hat{\mathcal{S}}^2$ operator, leading to so-called ``spin-contamination'' in the wave function.
+the total spin $\hat{\mathcal{S}}^2$ operator, leading to ``spin-contamination'' in the wave function.
 
@@
 \end{equation}
-However, in the strongly correlated regime (large $U$), the closed-shell restriction on the orbitals prevents RHF from 
+However, in the strongly correlated regime $U>2t$, the closed-shell restriction on the orbitals prevents RHF from 
 correctly modelling the physics of the system with the two electrons on opposing sites.

### 2020-11-19 Manuscript/EPAWTFT.tex
add fig RadConv

@@
 A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
-The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in \titou{Fig.~\ref{eq:UMP_rc}}.
+The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{fig:RadConv}.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{RadConv}
+	\caption{
+	Evolution of the radius of convergence $r_c$ associated with the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) as functions of the ration $U/t$.
+	\label{fig:RadConv}}
+\end{figure}
 

### 2020-11-19 Manuscript/EPAWTFT.tex
saving work

@@
 The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{fig:RadConv}.
+From it, we clearly see that the UMP series has \titou{always?} a larger radius of convergence than the RMP series \titou{(except maybe at $U/t = 2^+$)}, and that the UMP ground-state series is always convergent as $r_c > 1$ for all $U/t$.
 
@@
 	\caption{
-	Evolution of the radius of convergence $r_c$ associated with the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) as functions of the ration $U/t$.
+	Evolution of the radius of convergence $r_c$ associated with the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) as functions of the ratio $U/t$.
 	\label{fig:RadConv}}

### 2020-11-19 Manuscript/EPAWTFT.tex
Worked through RMP discussion

--- 2020-11-19 Manuscript/EPAWTFT.tex
@@
 \newcommand{\rc}{r_{\text{c}}}
+\newcommand{\lc}{\lambda_{\text{c}}}
+\newcommand{\lep}{\lambda_{\text{EP}}}
 
@@
 
-The HF Hamiltonian \eqref{eq:HFHamiltonian} can be used as the zeroth-order Hamiltonian of Eq.~\eqref{eq:SchrEq-PT}.
-This partitioning of the Hamiltonian leads to the so-called M{\o}ller-Plesset (MP) perturbation theory.
-\cite{Moller_1934}
-The discovery of a partitioning of the Hamiltonian that allowed chemists to recover a large chunck of the correlation energy (\ie, the difference between the exact energy and the Hartree-Fock energy) using perturbation theory has been a major step in the development of post-HF methods.
-This yields
+In electronic structure, the HF Hamiltonian \eqref{eq:HFHamiltonian} is often used as the zeroth-order Hamiltonian
+to define M\o{}ller--Plesset (MP) perturbation theory.\cite{Moller_1934}
+This approach can recover a large proportion of the electron correlation energy,\cite{Lowdin_1955} 
+and provides the foundation for numerous post-HF approximations.
+With the MP partitioning, the parametrised perturbation Hamiltonian becomes
 \begin{multline}\label{eq:MPHamiltonian}
     \hH(\lambda) = 
-    \sum_{i}^{N} \Bigg[ 
+    \sum_{i}^{N} \Bigg( 
     -\frac{\grad_i^2}{2} 
@@
     + \lambda\sum_{i<j}^{N}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
-    \Bigg].
+    \Bigg).
 \end{multline}
-The nature of the HF wave function is up for grabs, and if one considers a RHF or UHF reference wave functions, it leads to the RMP or UMP series, respectively.
-
-As mentioned earlier, in perturbation theory, the energy is a power series of $\lambda$ and the physical energy is obtained at $\lambda = 1$. 
-The MP$n$ energy is defined as 
+Any set of orbitals can be used to define the HF Hamiltonian, although usually either the RHF or UHF orbitals are chosen to 
+define the RMP or UMP series respectively.
+The MP energy at a given order $n$ (\ie, MP$n$) is then defined as
 \begin{equation}
@@
 \end{equation}
-where $E_{\text{MP}}^{(k)}$ is the $k$th-order MP correction, and it is well known that $E_{\text{MP1}} =  E_{\text{MP}}^{(0)} + E_{\text{MP}}^{(1)} = E_\text{HF}$. \cite{SzaboBook}
-The MP2 energy reads
+where $E_{\text{MP}}^{(k)}$ is the $k$th-order MP correction and 
+\begin{equation}
+E_{\text{MP1}} =  E_{\text{MP}}^{(0)} + E_{\text{MP}}^{(1)} = E_\text{HF}.
+\end{equation}
+The second-order MP2 energy is given by
 \begin{equation}\label{eq:EMP2}
@@
 \end{equation}
-with $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$, and where  
-\begin{equation}
-	\braket{pq}{rs} = \iint \dd\vb{x}_1\dd\vb{x}_2\frac{\phi_p(\vb{x}_1)\phi_q(\vb{x}_2)\phi_r(\vb{x}_1)\phi_s(\vb{x}_2)}{\abs{\vb{r}_1 - \vb{r}_2}}
-\end{equation}
-are two-electron integrals in the spin-orbital basis. \cite{Gill_1994}
-
-As mentioned earlier, there is, \textit{a priori}, no guarantee that the MP$n$ series converges to the exact energy as $n \to \infty$. 
-In fact, it is known that when the HF wave function is a poor approximation to the exact wave function, for example in multi-reference systems, the MP method yields deceptive results.
-\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000}
-A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
-By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
-As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
-These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
-The direct computation of the terms of the series is quite manageable up to fourth order in perturbation, while the fifth and sixth order in perturbation can still be obtained but at a rather high cost.
+where $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$ are the anti-symmetrised two-electron integrals
+in the molecular spin-obital basis\cite{Gill_1994}
+\begin{equation}
+	\braket{pq}{rs} 
+    = \iint \dd\vb{x}_1\dd\vb{x}_2
+    \frac{\phi^{*}_p(\vb{x}_1)\phi^{*}_q(\vb{x}_2)\phi^{\vphantom{*}}_r(\vb{x}_1)\phi^{\vphantom{*}}_s(\vb{x}_2)}%
+      {\abs{\vb{r}_1 - \vb{r}_2}}.
+\end{equation}
+
+\hugh{While most practical calculations usually consider only the MP2 or MP3 approximations, higher order terms can 
+easily be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}}
+\textit{A priori}, there is no guarantee that this series will provide the smooth convergence that is desirable for a
+systematically improvable theory.
+\hugh{In fact, when the reference HF wave function is a poor approximation to the exact wave function, 
+for example in multi-configurational systems, MP theory can yield highly oscillitory, 
+slowly convergent, or catastrophically divergent results.\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000}
+Furthermore, the convergence properties of the MP series can depend strongly on the choice of restricted or
+unrestricted reference orbitals.}
+
+% HGAB: I don't think this parapgrah tells us anything we haven't discussed before
+%A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
+%By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, 
+%and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
+%As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
+%These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
+%The direct computation of the terms of the series is quite manageable up to fourth order in perturbation, while the fifth and sixth order in perturbation can still be obtained but at a rather high cost.
 \cite{JensenBook}
-In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
-For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
-If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
-
-Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
-i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
-Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
-ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
-iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
-
-Let us illustrate the behaviour of the RMP and UMP series on the Hubbard dimer (see Fig.~\ref{fig:RMP}).
-Within the RMP partition technique, we have 
+%In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
+%For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
+%If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
+
+To illustrate the behaviour of the RMP and UMP series, we can again consider the Hubbard dimer.
+Using the ground-state RHF reference orbitals leads to the RMP Hamiltonian
 \begin{widetext}
@@
 \label{eq:H_RMP}
-	\bH_\text{RMP} = 
+\bH_\text{RMP}\hugh{\qty(\lambda)} = 
 	\begin{pmatrix}
@@
 \end{equation}
-From this expression, it is easy to identify that the radius of convergence is defined by the EPs at $\lambda_c = \pm i 4t / U$ (which are actually located at the same position than the exact EPs discussed in Sec.~\ref{sec:example}).
-Equation \eqref{eq:E0MP} can be Taylor expanded in terms of $\lambda$ to obtain the $n$th-order MP correction
-\begin{equation}
-	E_\text{MP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2),
-\end{equation}
-with 
-\begin{equation}
-	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
-\end{equation}
-The convergence of the RMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3.5$ (where $r_c > 1$) and $4.5$ (where $r_c < 1$) is illustrated in Fig.~\ref{subfig:RMP_cvg}.
-The Riemann surfaces associated with the exact energy of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$ (see Figs.~\ref{subfig:RMP_3.5} and \ref{subfig:RMP_4.5}).
-From these, one \titou{clearly?} sees that the EP is outside (inside) the (pink) cylinder of unit radius for $U/t = 3.5$ ($4.5$),
-and the centre graph of Fig.~\ref{fig:RMP} evidences the convergent (divergent) nature of the RMP series.
-Interestingly, one can show that the convergent and divergent series start to differ at fourth order.
+From this expression, the EPs can be identified as $\lep = \pm \i 4t / U$,
+giving the radius of convergence
+\begin{equation}
+    \rc^{\text{RMP}} = \qty|\frac{4t}{U}|.
+\end{equation}
+These EPs are identical the the exact EPs discussed in Sec.~\ref{sec:example}.
+The Taylor expansion of the RMP energy can then be evaluated to obtain the $n$th order MP correction
+\begin{equation}
+	E_\text{RMP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2).
+\end{equation}
+%with 
+%\begin{equation}
+%	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
+%\end{equation}
+
+\hugh{The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
+of perturbation in Fig.~\ref{subfig:RMP_cvg}.
+In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
+The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
+\ref{subfig:RMP_4.5} respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
+by the vertical cylinder of unit radius.
+In the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ can bee
+seen outside this cylinder.
+The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
+from the single excitations.\cite{Lepetit_1998}
+This divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting
+the structure of the reference orbitals rather than capturing the correlation energy.
+}
 
@@
 \end{figure*}
+
+\hugh{(\textbf{HGAB}: Lets keep all the MP discussion together and add this note here)}
+Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
+i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
+Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
+ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
+iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
 

### 2020-11-19 Manuscript/EPAWTFT.tex

@@
 A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
-The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in \titou{Fig.~\ref{eq:UMP_rc}}.
+The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{fig:RadConv}.
+From it, we clearly see that the UMP series has \titou{always?} a larger radius of convergence than the RMP series \titou{(except maybe at $U/t = 2^+$)}, and that the UMP ground-state series is always convergent as $r_c > 1$ for all $U/t$.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{RadConv}
+	\caption{
+	Evolution of the radius of convergence $r_c$ associated with the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) as functions of the ratio $U/t$.
+	\label{fig:RadConv}}
+\end{figure}
 

### 2020-11-19 Manuscript/EPAWTFT.tex
another UMP paragraph: about the rad. conv. plot

--- 2020-11-19 Manuscript/EPAWTFT.tex
@@
 \begin{equation}
-    \rc^{\text{RMP}} = \qty|\frac{4t}{U}|.
+    \rc = \qty|\frac{4t}{U}|.
 \end{equation}
@@
 by the vertical cylinder of unit radius.
-In the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ can bee
-seen outside this cylinder.
+For the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
+outside this cylinder.
+In both cases, the EP connects the ground state with the doubly-excited state, and thus the convergence behaviour
+for the two states using the ground state RHF orbitals is identical.
 The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
@@
 
-The behaviour of the UMP series is more subtle as the spin-contamination comes into play and introduces additional coupling between electronic states.
-The UMP partitioning yield the following $\lambda$-dependent Hamiltonian:
+The behaviour of the UMP series is more subtle \hugh{than the RMP series as spin-contamination in the wave function
+must be considered, introducing additional coupling between electronic states.
+Using the ground-state UHF reference orbitals in the Hubbard dimer yields the UMP Hamiltonian}
 \begin{widetext}
@@
 \label{eq:H_UMP}
-	\bH_\text{UMP} = 
+\bH_\text{UMP}\hugh{\qty(\lambda)} = 
 	\begin{pmatrix}
-		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
-		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
-	\end{pmatrix},
+		-2t^2 \lambda/U	&	0									&	0									&	2t^2 \lambda/U		\\
+		0				&	U - 2t^2 \lambda/U 					&	2t^2\lambda/U						&	2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		0				&	2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		2t^2 \lambda/U	&	2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
+	\end{pmatrix}.
 \end{equation}
 \end{widetext}
-A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
-The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in \titou{Fig.~\ref{eq:UMP_rc}}.
-
+While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
+Instead, the radius of convergence of the UMP series can obtained numerically as a function of $U/t$, as shown
+in Fig.~\ref{fig:RadConv}.
+\hugh{These numerical values reveal that the UMP ground state series has $\rc > 1$ for all $U/t$ and must always converge.
+However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
+the corresponding UMP series will become increasingly slow.
+Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
+of $U/t$, reaching the limit value of $1/2$ for $U/t \rightarrow \infty$, and excited-state UMP series will always diverge.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% RADIUS OF CONVERGENCE PLOTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+	\includegraphics[width=\linewidth]{RadConv}
+	\caption{
+	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
+    series as functions of the ratio $U/t$.
+	\label{fig:RadConv}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% DISCUSSION OF UMP RIEMANN SURFACES
 The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.

### 2020-11-19 Manuscript/EPAWTFT.tex
More edits to UMP

@@
 % DISCUSSION OF UMP RIEMANN SURFACES
-The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
-Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
-This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
-For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
-Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
-For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
-We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
-An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
+\hugh{%
+The convergence behaviour can be further elucidated by considering the full structure of the UMP energies 
+in the complex $\lambda$-plane.
+These Riemann surfaces are illustrated for $U = 3t$ and $7t$ alongside the perturbation terms at each order
+in Fig.~\ref{subfig:UMP_cvg}.
+At $U = 3t$, the RMP series is convergent, while RMP becomes divergent for $U=7t$.
+The UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
+for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
+}
+
+% EFFECT OF SYMMETRY BREAKING
+\hugh{%
+Allowing the UHF orbitals to break the molecular symmetry introduces new couplings between electronic states
+and fundamentally changes the structure of the EPs in the complex $\lambda$-plane.
+For example, while the RMP energy shows only one EP between the ground state and 
+the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
+and first-excited open-shell singlet, and the other connecting the open-shell singlet state to the 
+doubly-excited second exciation (Fig.~\ref{fig:UMP}).
+While this symmetry-breaking makes the ground-state UMP series convergent by moving the corresponding
+EP outside the radius of convergence, this process also moves the excited-state EP within the radius of convergence
+and thus causes a deterioration in the convergence of the excited-state UMP series.
+Furthermore, since the UHF ground-state energy is already an improved approximation of the exact energy, the ground-state
+UMP energy surface is relatively flat and the majority of the UMP expansion is concerned with removing 
+spin-contamination from the wave function.
+}
+
+%The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
+%Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
+%This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
+%For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
+%Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
+%For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
+%We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
+%An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
 %On the other hand, there is an EP on the excited energy surface that is well within the radius of convergence.

### 2020-11-19 Manuscript/EPAWTFT.tex
cleanup stuff around and small modifications

@@
 \begin{abstract}
-In this review, we explore the extension of quantum chemistry in the complex plane.
-We observe that the physics of a quantum system is intimately connected to the position of the energy singularities in the complex plane. 
-After a presentation of the fundamental notions of quantum chemistry and perturbation theory in the complex plane, we provide a historical overview of the various research activities that have been performed on the physic of singularities.
+In this review, we explore the extension of quantum chemistry in the complex plane and their intimate link with perturbation theory.
+We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as expectational points.
+After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field approximation and perturbation theory, and their illustration with the ubiquitous Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller-Plesset perturbation theory.
+
 \end{abstract}
@@
 \begin{equation}\label{eq:FockOp}
-    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty( \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ) \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
+    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty[ \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
 \end{equation}
@@
 \begin{equation}
-    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty( \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) )
+    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
 \end{equation}
@@
     \label{eq:E_HF}
-    E_\text{HF} = \hugh{\frac{1}{2} \sum_i^{N} \Big( h_i + f_i \Big)},
-	%E_\text{HF} = \sum_i^{N} h_i + \frac{1}{2} \sum_{ij}^{N} \qty( J_{ij} - K_{ij} ),
+    E_\text{HF} = \frac{1}{2} \sum_i^{N} \qty( h_i + f_i ),
 \end{equation}
@@
 \begin{align}
-	h_i = \mel{\phi_i}{\Hat{h}}{\phi_i}
-    \quad \text{and} \quad
-    \hugh{f_i = \mel{\phi_i}{\Hat{f}}{\phi_i}.}
+	h_i & = \mel{\phi_i}{\Hat{h}}{\phi_i},
+    & 
+    f_i & = \mel{\phi_i}{\Hat{f}}{\phi_i}.
 	%J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
@@
 UHF solution appears with a lower energy than the RHF one.
+Note that the RHF wave function remains a genuine solution of the HF equations for $U \ge 2t$, but corresponds to a saddle point 
+of the HF energy rather than a minimum.
 This critical point is analogous to the infamous Coulson--Fischer point identified in the hydrogen dimer.\cite{Coulson_1949}
@@
 by swapping $\ta^{\text{UHF}}$ and $\tb^{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
-Note that the RHF wave function remains a genuine solution of the HF equations for $U \ge 2t$, but corresponds to a saddle point 
-of the HF energy rather than a minimum.
+This type of symmetry breaking is also called a spin-density wave in the physics community as the system ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
+There also exist symmetry-breaking processes at the RHF level where a charge-density wave is created via the oscillation between the situations where the two electrons are one side or the other.
+\cite{GiulianiBook}
 
@@
 to define M\o{}ller--Plesset (MP) perturbation theory.\cite{Moller_1934}
-This approach can recover a large proportion of the electron correlation energy,\cite{Lowdin_1955} 
+This approach can recover a large proportion of the electron correlation energy,\cite{Lowdin_1955a,Lowdin_1955b,Lowdin_1955c} 
 and provides the foundation for numerous post-HF approximations.
@@
 
-\hugh{While most practical calculations usually consider only the MP2 or MP3 approximations, higher order terms can 
-easily be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}}
+While most practical calculations usually consider only the MP2 or MP3 approximations, higher order terms can 
+easily be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}
 \textit{A priori}, there is no guarantee that this series will provide the smooth convergence that is desirable for a
 systematically improvable theory.
-\hugh{In fact, when the reference HF wave function is a poor approximation to the exact wave function, 
-for example in multi-configurational systems, MP theory can yield highly oscillitory, 
+In fact, when the reference HF wave function is a poor approximation to the exact wave function, 
+for example in multi-configurational systems, MP theory can yield highly oscillatory, 
 slowly convergent, or catastrophically divergent results.\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000}
 Furthermore, the convergence properties of the MP series can depend strongly on the choice of restricted or
-unrestricted reference orbitals.}
+unrestricted reference orbitals.
 
@@
 \label{eq:H_RMP}
-\bH_\text{RMP}\hugh{\qty(\lambda)} = 
+\bH_\text{RMP}\qty(\lambda) = 
 	\begin{pmatrix}
@@
 \begin{equation}
-    \rc = \qty|\frac{4t}{U}|.
+    \rc = \abs{\frac{4t}{U}}.
 \end{equation}
@@
 
-\hugh{The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
+The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
 of perturbation in Fig.~\ref{subfig:RMP_cvg}.
@@
 The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
-from the single excitations.\cite{Lepetit_1998}
+from the single excitations.\cite{Lepetit_1988}
 This divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting
 the structure of the reference orbitals rather than capturing the correlation energy.
-}
 
@@
 
-The behaviour of the UMP series is more subtle \hugh{than the RMP series as spin-contamination in the wave function
+The behaviour of the UMP series is more subtle than the RMP series as spin-contamination in the wave function
 must be considered, introducing additional coupling between electronic states.
-Using the ground-state UHF reference orbitals in the Hubbard dimer yields the UMP Hamiltonian}
+Using the ground-state UHF reference orbitals in the Hubbard dimer yields the UMP Hamiltonian
 \begin{widetext}
@@
 \label{eq:H_UMP}
-\bH_\text{UMP}\hugh{\qty(\lambda)} = 
+\bH_\text{UMP}\qty(\lambda) = 
 	\begin{pmatrix}
@@
 in Fig.~\ref{fig:RadConv}.
-\hugh{These numerical values reveal that the UMP ground state series has $\rc > 1$ for all $U/t$ and must always converge.
+These numerical values reveal that the UMP ground state series has $\rc > 1$ for all $U/t$ and must always converge.
 However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
@@
 Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
-of $U/t$, reaching the limit value of $1/2$ for $U/t \rightarrow \infty$, and excited-state UMP series will always diverge.}
+of $U/t$, reaching the limit value of $1/2$ for $U/t \rightarrow \infty$, and excited-state UMP series will always diverge.
 
@@
 % DISCUSSION OF UMP RIEMANN SURFACES
-\hugh{%
 The convergence behaviour can be further elucidated by considering the full structure of the UMP energies 
@@
 for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
-}
 
 % EFFECT OF SYMMETRY BREAKING
-\hugh{%
 Allowing the UHF orbitals to break the molecular symmetry introduces new couplings between electronic states
@@
 and first-excited open-shell singlet, and the other connecting the open-shell singlet state to the 
-doubly-excited second exciation (Fig.~\ref{fig:UMP}).
+doubly-excited second excitation (Fig.~\ref{fig:UMP}).
 While this symmetry-breaking makes the ground-state UMP series convergent by moving the corresponding
@@
 spin-contamination from the wave function.
-}
 
@@
 
-\hugh{(\textbf{HGAB}: Lets keep all the MP discussion together and add this note here)}
 Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
@@
 
-%%============================================================%
-%\section{The spherium model}
-%\label{sec:spherium}
-%%============================================================%
-%
-%Simple systems that are analytically solvable (or at least quasi-exactly solvable, \ie, models for which it is possible to obtain a finite portion of the exact solutions of the Schr{\"o}dinger equation \cite{Ushveridze_1994}) are of great importance in theoretical chemistry.
-%These systems are very useful to perform benchmark studies in order to test new methods as the mathematics are easier than in realistic systems (such as molecules or solids) but retain much of the key physics.
-%To investigate the physics of EPs we consider one such system named \textit{spherium}. 
-%It consists of two electrons confined to the surface of a sphere interacting through the long-range Coulomb potential. \cite{Thompson_2005, Seidl_2007, Loos_2009b} 
-%Thus, the Hamiltonian is
-%\begin{equation}
-%	\hH = -\frac{\grad_1^2 + \grad_2^2}{2} + \frac{1}{r_{12}},
-%\end{equation}
-%or
-%\begin{equation} \label{eq:H-sph-omega}
-%	\hH = -\frac{1}{R^2} \qty( \pdv[2]{}{\omega} + \cot \omega \pdv{}{\omega}) + \frac{1}{R \sqrt{2 - 2 \cos \omega}},
-%\end{equation}
-%in term of the interelectronic angle $\omega$.
-%The Laplace operators are the kinetic operators for each electron and $r_{12}^{-1} = \abs{\vb{r}_1 - \vb{r}_2}^{-1}$ is the Coulomb operator. 
-%Note that, as readily seen by the definition of the interelectronic distance $r_{12}$, the electrons interact through the sphere.
-%The radius of the sphere $R$ dictates the correlation regime. \cite{Loos_2009}
-%In the weak correlation regime (\ie, small $R$), the kinetic energy (which scales as $R^{-2}$) dominates and the electrons are delocalized over the sphere.
-%For large $R$ (or strong correlation regime), the electron repulsion term (which scales as $R^{-1}$) drives the physics and the electrons localize on opposite side of the sphere to minimize their Coulomb repulsion.
-%This phenomenon is sometimes referred to as a Wigner crystallization. \cite{Wigner_1934}
-%
-%We will use this model in order to rationalize the effects of the parameters that may influence the physics of EPs:
-%i) Partitioning of the Hamiltonian and the actual zeroth-order reference: weak correlation reference (RHF or UHF references, MP or EN partitioning), or strongly correlated reference.
-%ii) Basis set: minimal basis or infinite (\ie, complete) basis.
-%iii) Radius of the sphere that ultimately dictates the correlation regime.
-%
-%In the RHF formalism, the two electrons are restricted to ``live'' in the same spatial orbital.
-%The spatial part of the RHF wave function is then
-%\begin{equation}\label{eq:RHF_WF}
-%	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
-%\end{equation}
-%where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
-%Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
-%
-%The RHF wave function cannot model properly the physics of the system at large $R$ because the spatial orbitals are restricted to be the same, and, \textit{a fortiori}, it cannot represent two electrons on opposite side of the sphere.
-%Within the UHF formalism, there is a critical value of $R$, called Coulson-Fischer point, \cite{Coulson_1949} at which a UHF solution appears and is lower in energy than the RHF one.
-%The UHF solution has broken symmetry because the two electrons tends to localize on opposite sides of the sphere. 
-%The spatial part of the UHF wave function is defined as
-%\begin{equation}\label{eq:UHF_WF}
-%	\Psi_{\text{UHF}}(\theta_1,\theta_2)=\phi_\alpha(\theta_1)\phi_\beta(\theta_2),
-%\end{equation}
-%where $\phi_\sigma(\theta)$ is the spatial orbital associated with the spin-$\sigma$ electrons ($\sigma = \alpha$ for spin-up electrons and $\sigma = \beta$ for spin-down electrons).
-%These one-electron orbitals are expanded in the basis of zonal spherical harmonics
-%\begin{equation}
-%	\phi_\sigma(\theta)=\sum_{\ell=0}^{\infty}C_{\sigma,\ell}Y_{\ell}(\theta).
-%\end{equation}
-%It is possible to obtain the formula for the HF energy in this basis set: \cite{Loos_2009}
-%\begin{equation}
-%	E_{\text{HF}} = T_{\text{HF}} + V_{\text{HF}},
-%\label{eq:EHF}
-%\end{equation}
-%where the kinetic and potential energies are, respectively,
-%\begin{align}
-%	T_{\text{HF}} & = \frac{1}{R^2} \sum_{\sigma=\alpha,\beta} \sum_{\ell=0}^{\infty} C_{\sigma,\ell}^2 \, \ell(\ell+1),
-%	&
-%	V_{\text{HF}} & = \frac{1}{R} \sum_{L=0}^{\infty}
-%	v^\alpha_{L} v^\beta_{L},
-%\end{align}
-%and
-%\begin{equation}
-%	v^\sigma_{L} 
-%	=  \sum_{\ell_1,\ell_2} \sqrt{(2\ell_1+1)(2\ell_2+1)} C_{\sigma,\ell_1}C_{\sigma,\ell_2}
-%	\begin{pmatrix}
-%		\ell_1 & L & \ell_2 
-%		\\
-%		0 & 0 & 0
-%	\end{pmatrix}^2 
-%\end{equation}
-%is expressed in terms of the Wigner 3j-symbols. \cite{AngularBook}
-%
-%The general method is to use a self-consistent field procedure as described in Ref.~\onlinecite{SzaboBook} to get the coefficients of the HF wave function corresponding to stationary solutions with respect to the coefficients $C_{\sigma,\ell}$, \ie,
-%\begin{equation}
-%	\pdv{E_{\text{HF}}}{C_{\sigma,\ell}} = 0.
-%\end{equation}
-%Here, we work in a minimal basis, composed of $Y_{0}$ and $Y_{1}$, or equivalently, a $s$ and $p_{z}$ orbital, to illustrate the difference between the RHF and UHF solutions.
-In this basis there is a shortcut to find the stationary solutions and ensure normalization of the orbitals.
-One can define the one-electron orbitals as
-%\begin{equation}
-%	\phi_\sigma(\theta)= \cos(\chi_\sigma)Y_{0}(\theta) + \sin(\chi_\sigma)Y_{1}(\theta),
-%\end{equation}
-%using a mixing angle $\chi_\sigma$ between the two basis functions for each spin manifold. 
-%Hence, one has just to minimize/maximize the energy with respect to the two mixing angles $\chi_\alpha$ and $\chi_\beta$.
-% 
-%This process provides the three following solutions valid for all value of $R$, which are respectively a minimum, a maximum and a saddle point of the HF equations:
-%i) the two electrons are in the $s$ orbital which is a RHF solution. This solution is associated with the energy $1/R$;
-%ii) the two electrons are in the $p_{z}$ orbital which is a RHF solution. This solution is associated with the energy $2/R^{2}+ 29/(25R)$;
-%iii) one electron is in the $s$ orbital and the other is in the $p_{z}$ orbital which is a UHF solution. This solution is associated with the energy $1/R^{2} + 1/R$.
-%
-%In addition, the minimization process gives also the well-known symmetry-broken UHF (sb-UHF) solution. In this case the Coulson-Fischer point associated to this solution is $R=3/2$. 
-%For $R>3/2$, the sb-UHF solution is the global minimum of the HF equations and the RHF solution presented before is a local minimum.
-This solution corresponds to the configuration with the spin-up electron in an orbital on one side of the sphere and the spin-down electron in a miror-image orbital on the opposite side and the configuration the other way round.
-The electrons can be on opposite sides of the sphere because the choice of $p_{z}$ as a basis function induced a privileged axis on the sphere for the electrons.
-For $R>3/2$, this solution has the energy
-%\begin{equation}\label{eq:EsbUHF}
-%	E_{\text{sb-UHF}}=-\frac{75}{112R^3}+\frac{25}{28R^2}+\frac{59}{84R}.
-%\end{equation}
-%
-%The exact solution for the ground state is a singlet. The spherical harmonics are eigenvectors of $\hS^2$ (the spin operator) and they are associated to different eigenvalues. 
-%Yet, the symmetry-broken orbitals are linear combinations of $Y_0$ and $Y_1$. 
-%Hence, the symmetry-broken orbitals are not eigenvectors of $\hS^2$. 
-%However, this solution gives lower energies than the RHF one at large $R$, even if it does not have the exact spin symmetry. 
-%In fact, at the Coulson-Fischer point, it becomes more effective to minimize the Coulomb repulsion than the kinetic energy in order to minimize the total energy. 
-%Thus, within the HF approximation, the variational principle is allowed to break the spin symmetry because it yields a more effective minimization of the Coulomb repulsion. 
-%This type of symmetry breaking is also called a spin-density wave in the physics community as the system ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
-%
-%There is also another symmetry-broken solution for $R>75/38$ but this one corresponds to a maximum of the HF equations. 
-%This solution is associated with another type of symmetry breaking somewhat less known. 
-%It corresponds to a configuration where both electrons are on the same side of the sphere, in the same spatial orbital. 
-%This solution is called symmetry-broken RHF (sb-RHF). The reasoning is counter-intuitive because the electrons tends to maximize their energy. 
-%The $sp_{z}$ orbital is symmetric with respect to the center of the sphere. 
-%If the orbitals are symmetric, the maximum is when the two electrons are in the $p_{z}$ orbital because it maximizes the kinetic energy. 
-%At the critical value of $R$, placing the two electrons in the same symmetry-broken orbital \ie, on the same side of the sphere gives a superior energy than the $p_{z}^2$ state.
-Adding a s orbital on one side of the $p_{z}$ orbital to form a symmetry-broken orbital reduce the kinetic energy but increase the repulsion energy as the two electrons are more localized on one side of the sphere.
-%It becomes more efficient to maximize the repulsion energy than the kinetic energy for $R>75/38$. 
-%This configuration breaks the spatial symmetry of charge. 
-%Hence this symmetry breaking is associated with a charge-density wave as the system oscillates between the situations where the two electrons are one side or the other. \cite{GiulianiBook}
-%The energy associated with this sb-RHF solution reads
-%\begin{equation}
-%E_{\text{sb-RHF}}=\frac{75}{88R^3}+\frac{25}{22R^2}+\frac{91}{66R}.
-%\end{equation}
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{EsbHF.pdf}
-%    \caption{Energies of the five solutions of the HF equations (multiplied by $R^2$). The dotted curves correspond to the analytic continuation of the symmetry-broken solutions.}
-%    \label{fig:SpheriumNrj}
-%\end{figure}
-%
-%We can also consider negative values of $R$, which corresponds to the situation where one of the electrons is replaced by a positron as readily seen in Eq.~\eqref{eq:H-sph-omega}. 
-%For negative $R$ values, there are also a sb-RHF ($R<-3/2$) and a sb-UHF ($R<-75/38$) solution for negative values of $R$ (see Fig.~\ref{fig:SpheriumNrj}) but in this case the sb-RHF solution is a minimum and the sb-UHF is a maximum of the HF equations.
-%Indeed, the sb-RHF state minimizes the attraction energy by placing the electron and the positron on the same side of the sphere. 
-%And the sb-UHF state maximizes the energy because the two attracting particles are on opposite sides of the sphere.
-%
-%In addition, we can also consider the symmetry-broken solutions beyond their respective Coulson-Fischer points by analytically continuing their respective energies leading to the so-called holomorphic solutions.
-\cite{Hiscock_2014, Burton_2019, Burton_2019a} All those energies are plotted in Fig.~\ref{fig:SpheriumNrj}.
-The dotted curves corresponds to the holomorphic domain of the energies.
-%
-%
-%\section{Radius of convergence and exceptional points}
-%
-%\subsection{Evolution of the radius of convergence}
-%
-%In this subsection, we investigate how the partitioning of $\hH(\lambda)$ influence the radius of convergence of the perturbation series.
-Let us remind the reader that the radius of convergence is equal to the distance of the closest singularity to the origin of $E(\lambda)$.
-Hence, we have to determine the locations of the EPs to obtain information on the convergence properties of the perturbative series.
-To find them we solve simultaneously the following equations: \cite{Cejnar_2007}
-%\begin{subequations}
-%\begin{align}
-%	\label{eq:PolChar}
-%	\det[E\hI-\hH(\lambda)] & = 0,
-%	\\ 
-%	\label{eq:DPolChar}
-%	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
-%\end{align}
-%\end{subequations}
-%where $\hI$ is the identity operator.
-%Equation \eqref{eq:PolChar} is the well-known secular equation providing us with the (eigen)energies of the system.
-If an energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy is, at least, two-fold degenerate.
-In this case the energies obtained are  $\lambda$-dependent.
-%Thus, solving these equations with respect to $E$ and $\lambda$ gives the value of $\lambda$ where two energies are degenerate. 
-%These degeneracies can be conical intersections between two states with different symmetries for real values of $\lambda$ \cite{Yarkony_1996} or EPs between two states with the same symmetry for complex values of $\lambda$.
-%
-%Let us assume that electron 1 is spin-up and electron 2 is spin-down. 
-%Hence, we can forget about the spin part of the spin-orbitals and from now on we will work with spatial orbitals.
-In the restricted formalism the spatial orbitals are the same so the two-electron basis set can be defined as
-%
-%\begin{align}\label{eq:rhfbasis}
-% \psi_1 & =Y_{0}(\theta_1)Y_{0}(\theta_2),
-% & 
-% \psi_2 & =Y_{0}(\theta_1)Y_{1}(\theta_2),\\
-% \psi_3 & =Y_{1}(\theta_1)Y_{0}(\theta_2),
-% & 
-% \psi_4 & =Y_{1}(\theta_1)Y_{1}(\theta_2).
-%\end{align}
-%The Hamiltonian $\hH(\lambda)$ is block diagonal in this basis because of its symmetry, \ie, $\psi_1$ only interacts with $\psi_4$, and $\psi_2$ with $\psi_3$.
-The two singly-excited states yield, after diagonalization, a spatially anti-symmetric singlet $sp_z$ and a spatially symmetric triplet $sp_{z}$ state.
-%Hence those states do not have the same symmetry as the spatially symmetric singlet ground state. 
-%Thus, these states cannot be involved in an avoided crossing with the ground state as can be seen in Fig.~\ref{fig:RHFMiniBas} and, \textit{a fortiori} cannot be involved in an EP with the ground state.
-%However there is an avoided crossing between the $s^{2}$ and $p_{z}^{2}$ states which gives two EPs in the complex plane. 
-%
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{EMP_RHF_R10.pdf}
-%    \caption{Energies $E(\lambda)$ in the restricted basis set \eqref{eq:rhfbasis} with $R=10$.
-%    One can clearly see the avoided crossing between the $s^{2}$ and $p_{z}^{2}$ states around $\lambda = 1$.}
-%    \label{fig:RHFMiniBas}
-%\end{figure}
-%
-%To simplify the problem, it is convenient to only consider basis functions of a given symmetry.
-Such basis functions are called configuration state functions (CSFs).
-It simplifies greatly the problem because, with such a basis set, one only gets the degeneracies of interest associated with the convergence properties, \ie, the EPs between states with the same symmetry as the ground state.
-In the present context, the ground state is a totally symmetric singlet.
-According to angular momentum theory, \cite{AngularBook, SlaterBook, Loos_2009} we expand the exact wave function in the following two-electron basis:
-%\begin{equation}
-%\Phi_\ell(\omega)=\frac{\sqrt{2\ell+1}}{4\pi R^2}P_\ell(\cos\omega),
-%\end{equation}
-%where $P_\ell$ are Legendre polynomials.
-%
-%Then, using this basis set we can compare the different partitioning of Sec.~\ref{sec:AlterPart}.
-Figure \ref{fig:RadiusPartitioning} shows the evolution of the radius of convergence $R_{\text{CV}}$ as a function of $R$ for the MP, the EN, the WC and the SC partitioning in a minimal basis (\ie, consisting of $P_0$ and $P_1$) of size $K = 2$, and in the same basis augmented with $P_2$ ($K = 3$).
-We see that, for the SC partitioning, $R_{\text{CV}}$ increases with $R$ whereas it is decreasing for the three others partitioning.
-This result is expected because the MP, EN, and WC partitioning use a weakly correlated reference so $\hH^{(0)}$ is a good approximation for small $R$.
-On the contrary, the SC partitioning consider naturally a strongly correlated reference so the SC series converges far better when the electron are strongly correlated, \ie, when $R$ is large in the spherium model.
-%
-%Interestingly, the radius of convergence associated with the SC partitioning is greater than one for a greater range of radii for $K = 2$ than $K = 3$. 
-%
-%\begin{figure}
-%    \includegraphics[width=0.49\textwidth]{PartitioningRCV2.pdf}
-%    \includegraphics[width=0.49\textwidth]{PartitioningRCV3.pdf}
-%    \caption{Radius of convergence $R_{\text{CV}}$ for two (left) and three (right) basis functions for various partitionings.}
-%    \label{fig:RadiusPartitioning}
-%\end{figure}
-%
-%The MP partitioning is always better than WC in Fig.~\ref{fig:RadiusPartitioning}.
-In the WC partitioning the powers of $R$ (the zeroth-order scales as $R^{-2}$ while the perturbation scales as $R^{-1}$) are well-separated so each term of the series has a well-defined power of $R$.
-This is not the case for the MP series.
-%Interestingly, it can be proved that the $m$th order energy of the WC series can be obtained as a Taylor series of MP$m$ with respect to $R$. 
-%It seems that the EN is better than MP for very small $R$ in the minimal basis.
-In fact, it is just an artefact of the minimal basis because, for $K = 3$, the MP series has a greater radius of convergence for all values of $R$.
-It holds true for $K>3$.
-%
-%
-%Figure \ref{fig:RadiusBasis} shows that the radius of convergence is not very sensitive to the size of the basis set.
-The CSFs have all the same spin and spatial symmetries so we expect that the singularities obtained within this basis set will be $\alpha$ singularities.
-Table \ref{tab:SingAlpha} shows that the singularities considered in this case are indeed $\alpha$ singularities.
-This is consistent with the observation of Goodson and Sergeev \cite{Goodson_2004} who stated that $\alpha$ singularities are relatively insensitive to the basis set size.
-The discontinuities observed in Fig.~\ref{fig:RadiusBasis} for the MP partitioning are due to changes in dominant singularity.
-We can observe this change in Table \ref{tab:SingAlpha}, the value for $R=1$ and $R=2$ are respectively in the positive and negative planes.
-%
-%\begin{figure}
-%    \includegraphics[width=0.49\textwidth]{MPlargebasis.pdf}
-%    \includegraphics[width=0.49\textwidth]{WCElargebasis.pdf}
-%    \caption{Radius of convergence $R_{\text{CV}}$ in the CSF basis with $K$ basis functions for the MP (left) and WC (right) partitioning.}
-%    \label{fig:RadiusBasis}
-%\end{figure}
-%
-%\begin{table*}
-%\caption{Dominant singularity in the CSF basis set ($K=8$) for various value of $R$ in the MP and WC partitioning.}
-%\begin{ruledtabular}
-%\begin{tabular}{cccccccc}
-%$R$ & 0.1 & 1 & 2 & 3 & 5 & 10 & 100 \\
-%\hline
-%MP & $+14.1-10.9\,i$ & $+2.38-1.47\,i$ & $-0.67-1.30\,i$ & $-0.49-0.89\,i$ & $-0.33-0.55\,i$ & $-0.22-0.31\,i$ & $+0.03-0.05\,i$ \\
-%WC & $-9.6-10.7\,i$ & $-0.96-1.07\,i$ & $-0.48-0.53\,i$ & $-0.32-0.36\,i$ & $-0.19-0.21\,i$ & $-0.10-0.11\,i$ & $-0.01-0.01\,i$ \\
-%\end{tabular}
-%\end{ruledtabular}
-%\label{tab:SingAlpha}
-%\end{table*}
-%
-%\subsection{Exceptional points in the UHF formalism}\label{sec:uhfSing}
-%
-%Now, we investigate the differences in the singularity structure between the RHF and UHF formalism.
-To do so, we use the symmetry-broken orbitals discussed in Sec.~\ref{sec:spherium}.
-Thus, the UHF two-electron basis is
-%\begin{align}\label{eq:uhfbasis}
-% \psi_1 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,1}(\theta_2),
-% & 
-% \psi_2 & =\phi_{\alpha,1}(\theta_1)\phi_{\beta,2}(\theta_2),\\
-% \psi_3 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,1}(\theta_2),
-% & 
-% \psi_4 & =\phi_{\alpha,2}(\theta_1)\phi_{\beta,2}(\theta_2).
-%\end{align}
-%with the symmetry-broken orbitals
-%\begin{subequations}
-%\begin{align}\label{eq:uhforbitals}
-% 	\phi_{\alpha,1}(\theta) 
-% 		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
-% 		+ \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
-% \\ 
-% 	\phi_{\beta,1}(\theta) 
-%		& =\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{0}(\theta)
-%		- \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{1}(\theta),
-% \\
-%	 \phi_{\alpha,2}(\theta) 
-%	 & = - \frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
-%	  + \frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta),
-% \\
-%	 \phi_{\beta,2}(\theta) 
-%	 & =\frac{5\sqrt{-3+2R}}{4\sqrt{7R}} Y_{0}(\theta)
-%	 +\frac{\sqrt{75+62R}}{4\sqrt{7R}} Y_{1}(\theta).
-%\end{align}
-%\end{subequations}
-%
-%In the UHF formalism the Hamiltonian $\hH(\lambda)$ is no more block diagonal, $\psi_4$ can interact with $\psi_2$ and $\psi_3$.
-The matrix elements of the Hamiltonian corresponding to this interaction are
-%\begin{equation}\label{eq:MatrixElem}
-%	H_{24}=H_{34}=H_{42}=H_{43}=\sqrt{R-\frac{3}{2}}\sqrt{R+\frac{75}{62}}\qty(R+\frac{25}{2})\frac{\sqrt{31}}{70R^3}
-%\end{equation}
-%
-%For $R=3/2$ the Hamiltonian is block diagonal because the matrix elements \eqref{eq:MatrixElem} are equal to zero so this is equivalent to the RHF case but for $R>3/2$ the matrix elements become real.
-This interaction corresponds to the spin contamination of the wave function.
-For $R<3/2$ the matrix elements are complex, this corresponds to the holomorphic solution of Fig.~\ref{fig:SpheriumNrj}, the singularities in this case will be treated later.
-The matrix elements become real again for $R<-75/62$, this corresponds to the sb-UHF solution for negative value of $R$ observed in Sec.~\ref{sec:spherium}.
-We will refer to the domain where the matrix elements are complex as the holomorphic domain.
-%
-%The singularity structure in this case is more complex because of the spin contamination of the wave function.
-We can not use CSFs in this case.
-So when one compute all the degeneracies using Eqs.~\eqref{eq:PolChar} and \eqref{eq:DPolChar} some correspond to EPs and some correspond to conical intersections.
-The numerical distinction of those singularities is very difficult.
-We will first look at the energies $E(\lambda)$ obtained with this basis set to attribute a physical signification to the singularities obtained numerically.
-%Figure \ref{fig:UHFMiniBas} is the analog of Fig.~\ref{fig:RHFMiniBas} in the UHF formalism.
-We see that in this case the $sp_{z}$ triplet interacts with the $s^{2}$ and the $p_{z}^{2}$ singlets.
-Those avoided crossings are due to the spin contamination of the wave function.
-%
-%\begin{figure}
-%    \includegraphics[width=\linewidth]{EMP_UHF_R10.pdf}
-%    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} with $R=10$.}
-%    \label{fig:UHFMiniBas}
-%\end{figure}
-%
-%Within the RHF formalism, we have observed only $\alpha$ singularities and large avoided crossings but one can see in Fig.~\ref{fig:UHFMiniBas} that in the UHF case there are sharp avoided crossings which are known to be connected to $\beta$ singularities.
-For example at $R=10$ the pair of singularities connected to the avoided crossing between $s^{2}$ and $sp_{z}$ $^{3}P$ is $0.999\pm0.014\,i$.
-And the one between $sp_{z}$ $^{3}P$ and $p_{z}^{2}$ is connected with the singularities $2.207\pm0.023\,i$.
-However, in spherium, the electrons cannot be ionized so those singularities cannot be the same $\beta$ singularities as the ones highlighted by Sergeev and Goodson.
-\cite{Sergeev_2005} We can see in Fig.~\ref{fig:UHFEP} that the $s^{2}$ singlet and the $sp_{z}$ triplet states are degenerated for $R=3/2$.
-For $R>3/2$, it becomes an avoided crossing on the real axis and the degeneracies are $moved$ in the complex plane.
-The wave function is spin contaminated by $Y_1$ for $R>3/2$ this is why the $s^{2}$ singlet energy cannot cross the $sp_{z}$ triplet curves anymore.
-When $R$ increases this avoided crossing becomes sharper.
-As presented before $\beta$ singularities are linked to quantum phase transition so it seems that this singularity is linked to the spin symmetry breaking of the UHF wave function.
-The fact that a similar pair of $\beta$ singularities appears for $R<-75/62$ confirms this assumption.
-The sharp avoided crossing between $sp_{z}$ $^{3}P$ and $p_{z}^{2}$ is not present on Fig.
-\ref{fig:UHFEP}.
-The second pair of $\beta$ singularities resulting from this avoided crossing appears for $R\gtrsim 2.5$, this is probably due to an excited-state quantum phase transition but this still need to be investigated.
-%
-%\begin{figure}
-%    \includegraphics[width=0.45\textwidth]{UHFCI.pdf}
-%    \includegraphics[width=0.45\textwidth]{UHFEP.pdf}
-%    \caption{Energies $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1.5$ (left) and $R=1.51$ (right).}
-%    \label{fig:UHFEP}
-%\end{figure}
-%
-%As shown before, some matrix elements of the Hamiltonian become complex in the holomorphic domain.
-Therefore the Hamiltonian becomes non-Hermitian for these values of $R$.
-In Ref.~\onlinecite{Burton_2019a}, Burton \textit{et al.}~proved that for the \ce{H_2} molecule the unrestricted Hamiltonian is not \pt -symmetric in the holomorphic domain.
-An analog reasoning can be done with the spherium model to prove the same result.
-The \pt -symmetry (invariance with respect to combined space reflection $\mathcal{P}$ and time reversal $\mathcal{T}$) is a property which ensures that a non-Hermitian Hamiltonian has a real energy spectrum.
-\cite{BenderPTBook} Thus \pt -symmetric Hamiltonians can be seen as an intermediate class between Hermitian and non-Hermitian Hamiltonians.
-%
-%Figure \ref{fig:UHFPT} shows that for the spherium model a part of the energy spectrum becomes complex when $R$ is in the holomorphic domain.
-The domain of values where the energy becomes complex is called the broken \pt-symmetry region.
-This is consistent with the fact that in the holomorphic domain the Hamiltonian is no more \pt -symmetric.
-%
-%For a non-Hermitian Hamiltonian the EPs can lie on the real axis.
-In particular, at the point of {\pt} transition (the point where the energies become complex) the two energies are degenerate resulting in such an EP on the real axis.
-This degeneracy can be seen in Fig.~\ref{fig:UHFPT}.
-%
-%\begin{figure}[h!]
-%    \includegraphics[width=0.45\textwidth]{ReNRJPT.pdf}
-%    \includegraphics[width=0.45\textwidth]{ImNRJPT.pdf}
-%    \caption{Real part (left) and imaginary part (right) of $E(\lambda)$ in the unrestricted basis set \eqref{eq:uhfbasis} for $R=1$.}
-%    \label{fig:UHFPT}
-%\end{figure}
-
+%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
+%%%%%%%%%%%%%%%%%%%%
 
@@
 More preoccupying cases were also reported. 
-For instance, it has been shown that systems considered as well-understood (\eg, \ce{Ne}) can exhibit divergent behavior when the basis set is augmented with diffuse functions. 
-Later, these erratic behaviors of the perturbation series were investigated and rationalized in terms of avoided crossings and singularities in the complex plane.
+For instance, it has been shown that systems considered as well understood (\eg, \ce{Ne}) can exhibit divergent behaviour when the basis set is augmented with diffuse functions. 
+Later, these erratic behaviours of the perturbation series were investigated and rationalised in terms of avoided crossings and singularities in the complex plane.
 It was shown that the singularities can be classified in two families.
 The first family includes $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly-excited states. 
-The $\beta$ singularities, which constitutes the second family, are artifacts generated by the incompleteness of the Hilbert space, and they are directly connected to an ionization phenomenon occurring in the complete Hilbert space.
+The $\beta$ singularities, which constitutes the second family, are artefacts generated by the incompleteness of the Hilbert space, and they are directly connected to an ionisation phenomenon occurring in the complete Hilbert space.
 These singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state. 
-We have found that the $\beta$ singularities modeling the ionization phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
-Indeed, those singularities close to the real axis are connected to quantum phase transition and symmetry breaking, and theoretical physics have demonstrated that the behavior of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).
-
-%In this work, we have shown that $\beta$ singularities are involved in the spin symmetry breaking of the UHF wave function. 
-%This confirms that $\beta$ singularities can occur for other types of transition and symmetry breaking than just the formation of a bound cluster of electrons. 
-%It would be interesting to investigate the difference between the different type of symmetry breaking and how it affects the singularity structure. 
-%Moreover the singularity structure in the non-Hermitian case still need to be investigated. 
-%In the holomorphic domain, some singularities lie on the real axis and it would also be interesting to look at the differences between the different symmetry breaking and their respective holomorphic domain.
-%Furthermore, in this study we have used spherical harmonics (or combination of spherical harmonics) as basis functions which have a delocalized nature.
-It would also be interesting to investigate the use of localized basis functions \cite{Seidl_2018} (for example gaussians) because these functions would be more adapted to describe the strongly correlated regime.
-%More generally, to investigate the effect of the type of basis on the physics of EPs.
-%To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We have found that the $\beta$ singularities modelling the ionisation phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities.
+Indeed, those singularities close to the real axis are connected to quantum phase transitions and symmetry breaking, and theoretical physics have demonstrated that the behaviour of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).
+To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
 HGAB gratefully acknowledges New College, Oxford for funding through the Astor Junior Research Fellowship.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 \end{acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{EPAWTFT}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-11-19 Manuscript/EPAWTFT.tex
correcting typos here and there

@@
 \begin{abstract}
-In this review, we explore the extension of quantum chemistry in the complex plane and their intimate link with perturbation theory.
-We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as expectational points.
-After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field approximation and perturbation theory, and their illustration with the ubiquitous Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+In this review, we explore the extension of quantum chemistry in the complex plane and its link with perturbation theory.
+We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptionnal points.
+After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree-Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
 In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller-Plesset perturbation theory.
@@
 
-Due to the ubiquitous influence of processes involving electronic excited states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
+Due to the ubiquitous influence of processes involving electronic states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
 Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community.
 An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws. 
-The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new excited-state methodologies, their main goal being to get the most accurate excitation energies (and properties) at the lowest possible computational cost in the most general context.
+The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
 
@@
 Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
-Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realized in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
+Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realised in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
 \cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
@@
 Analytically solvable model systems are essential in theoretical chemistry and physics as the simplicity of the
-mathematics compared to realistic systems (e.g.\ atoms and molecules) readily allows concepts to be illustrated and new methods to be tested wile retaining much 
+mathematics compared to realistic systems (e.g., atoms and molecules) readily allows concepts to be illustrated and new methods to be tested wile retaining much 
 of the key physics.
@@
 Exact solutions to Eq.~\eqref{eq:SchrEq} are only possible in the simplest of systems, such as 
-the one-electron hydrogen atom. 
+the one-electron hydrogen atom and some specific two-electron systems with well-defined mathematical properties. \cite{Taut_1993,Loos_2009b,Loos_2010e,Loos_2012}
 In practice, one of the most common approximations involves
@@
 % LAMBDA IN THE COMPLEX PLANE
-From complex-analysis, the radius of convergence for the energy can be obtained by looking for the 
+From complex-analysis, \cite{BenderBook} the radius of convergence for the energy can be obtained by looking for the 
 singularities of $E(\lambda)$ in the complex $\lambda$ plane.
@@
 
-Practically, to locate EPs in a more complicated systems, one must simultaneously solve
+Practically, to locate EPs, one must simultaneously solve
 \begin{subequations}
@@
 However, the application of HF with some level of constraint on the orbital structure is far more common.
-Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, while allowing different for different spins leads to the so-called unrestricted HF (UHF) approach.
+Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, while allowing different orbitals for different spins leads to the so-called unrestricted HF (UHF) approach.
 The advantage of the UHF approximation is its ability to correctly describe strongly correlated systems, 
@@
 \end{equation}
-These EPs are identical the the exact EPs discussed in Sec.~\ref{sec:example}.
-The Taylor expansion of the RMP energy can then be evaluated to obtain the $n$th order MP correction
+These EPs are identical than the exact EPs discussed in Sec.~\ref{sec:example}.
+The Taylor expansion of the RMP energy can then be evaluated to obtain the $n$th-order MP correction
 \begin{equation}
@@
 the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
-and first-excited open-shell singlet, and the other connecting the open-shell singlet state to the 
+first-excited open-shell singlet, and the other connecting the open-shell singlet state to the 
 doubly-excited second excitation (Fig.~\ref{fig:UMP}).
 While this symmetry-breaking makes the ground-state UMP series convergent by moving the corresponding
-EP outside the radius of convergence, this process also moves the excited-state EP within the radius of convergence
+EP outside the unit cylinder, this process also moves the excited-state EP within the unit cylinder
 and thus causes a deterioration in the convergence of the excited-state UMP series.
@@
 One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
-However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behavior that one would wish for.
+However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
 
@@
 \cite{Gill_1988}
-Handy and coworkers reported the same behavior of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
-\cite{Handy_1985} Lepetit \textit{et al.}~analyzed the difference between the MP and EN partitioning for the UHF reference.
+Handy and coworkers reported the same behaviour of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
+\cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
 \cite{Lepetit_1988}
 They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations. 
-Cremer and He analyzed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
 Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
 They highlighted that \cite{Cremer_1996}
-\textit{``Class A systems are characterized by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
 Moreover, they analyzed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
@@
 The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalized use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 
@@
 However, the choice of the functional form of the fit remains a subtle task.
-This technique was first generalized by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
+This technique was first generalised by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
 \begin{equation}
@@
 
-The discovery of this divergent behavior is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
+The discovery of this divergent behaviour is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
 Including diffuse functions is particularly important in the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
 As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence.
-To do so, they analyzed the relation between the dominant singularity (\ie, the closest singularity to the origin) and the convergence behavior of the series.
+To do so, they analysed the relation between the dominant singularity (\ie, the closest singularity to the origin) and the convergence behaviour of the series.
 \cite{Olsen_2000} Their analysis is based on Darboux's theorem:
@@
 Their method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities. 
-Then, by modeling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ matrix
+Then, by modelling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ matrix
 \begin{equation}
@@
 For example, the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly-excited states which results in alternated terms up to 10th order. 
-For higher orders, the series is monotonically convergent. This surprising behavior is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
-
-In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalized to a non-symmetric Hamiltonian 
+For higher orders, the series is monotonically convergent. This surprising behaviour is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
+
+In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalised to a non-symmetric Hamiltonian 
 \begin{equation}
@@
 It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
-Interestingly, they showed that the convergence pattern of a given perturbation method can be characterized by its archetype which defines the overall ``shape'' of the energy convergence.
+Interestingly, they showed that the convergence pattern of a given perturbation method can be characterised by its archetype which defines the overall ``shape'' of the energy convergence. 
 These so-called archetypes can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
 Importantly, they observed that the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
-Other features characterizing the convergence behavior of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern;
+Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern;
 the three remaining archetypes seem to be rarely observed in MP perturbation theory.
@@
 Singularities of type $\alpha$ are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work of Stillinger.
-\cite{Stillinger_2000}
+They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work of Stillinger. \cite{Stillinger_2000}
 
@@
 
-The major difference between these two terms is that the repulsive mean field is localized around the nuclei whereas the interelectronic interaction persist away from the nuclei.
+The major difference between these two terms is that the repulsive mean field is localised around the nuclei whereas the interelectronic interaction persist away from the nuclei. 
 If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the electron-nucleus attraction.
@@
 However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modeled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-This explains that Olsen \textit{et al.}, because they used a simple $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence.
-\cite{Olsen_2000}
+Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+This explains that Olsen \textit{et al.}, because they used a simple $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
 
@@
 Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
-\cite{Heiss_1988,Heiss_2002,Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017} In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter.
+\cite{Heiss_1988,Heiss_2002,Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}
+In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter. 
 In some cases the variation of a parameter can lead to abrupt changes at a critical point. 
 These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
-\cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019} A ground-state QPT is characterized by the derivatives of the ground-state energy with respect to a non-thermal control parameter.
-\cite{Cejnar_2009, Sachdev_2011} The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value.
+\cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019} A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter.
+\cite{Cejnar_2009, Sachdev_2011}
+The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
 Otherwise, it is called continuous and of $m$th order if the $m$th derivative is discontinuous. 
@@
 Hence, the design of specific methods are required to get information on the location of EPs. 
-Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis.
-\cite{Cejnar_2005, Cejnar_2007} More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT.
-\cite{Stransky_2018} In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis.
+Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
+More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT. \cite{Stransky_2018} 
+In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
 They showed that, within the interacting boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases. 
@@
 Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the IBM model from the QPT's point of view \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}. 
-The phase of the ensemble of $s$ and $d$ bosons is characterized by a dynamical symmetry.
-When a parameter is continously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase.
+The phase of the ensemble of $s$ and $d$ bosons is characterised by a dynamical symmetry. 
+When a parameter is continuously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase. 
 They showed that at this critical value of the parameter, the system undergoes a QPT. 
-For example, without interaction the ground state is the spherical phase (a condensate of s bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of s and d bosons states.
-In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wavefunction of the hydrogen molecule when the bond is stretched \cite{SzaboBook}.
+For example, without interaction the ground state is the spherical phase (a condensate of $s$ bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of $s$ and $d$ bosons states.
+In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched \cite{SzaboBook}.
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory. 
 Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT. 
-Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modeling the formation of a bound cluster of electrons are actually a more general class of singularities.
+Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities. 
 The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly. 

### 2020-11-20 Manuscript/EPAWTFT.tex
adding bunch of refs and other stuff

@@
 Additionally, the wave functions pick up a geometric phase in the process, and four complete loops are required to recover their starting forms.\cite{MoiseyevBook}
+
+\titou{The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
+\cite{MoiseyevBook}
+Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
+We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
 
@@
 For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
-In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example here RMP5 is worse than RMP4).
+In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example, in the case of \ce{He2^2+}, RMP5 is worse than RMP4).
 On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
@@
 \cite{Mihalka_2017a}
-Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of the convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
+Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
 In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series taking again as an example the water molecule in a stretched geometry.
-In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent, and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
+In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
 However, the choice of the functional form of the fit remains a subtle task.
@@
 	\label{eq:Cauchy}
-	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(z)}{z - a} = E(a),
-\end{equation}
-which states that the value of the energy can be computed at $z=a$ inside the contour $\gamma$ only by the knowledge of its values on the same contour.
-Their method consists in refining self-consistently the values of $E(z)$ computed on a contour going through the physical point at $z = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
-The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(z)$ is analytic.
-When the values of $E(z)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(z=1)$ which corresponds to the final estimate of the FCI energy.
+	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(\lambda)}{\lambda - a} = E(a),
+\end{equation}
+which states that the value of the energy can be computed at $\lambda=a$ inside the complex contour $\gamma$ only by the knowledge of its values on the same contour.
+Their method consists in refining self-consistently the values of $E(\lambda)$ computed on a contour going through the physical point at $\lambda = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
+The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(\lambda)$ is analytic.
+When the values of $E(\lambda)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(\lambda=1)$ which corresponds to the final estimate of the FCI energy.
 The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
@@
 The exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states were good candidates for being intruder states.
-\titou{For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
-They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.}
+For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
+They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
 
@@
 Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
-\cite{Heiss_1988,Heiss_2002,Cejnar_2005, Cejnar_2007, Cejnar_2009, Borisov_2015, Sindelka_2017}
+\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook}
 In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter. 
@@
 These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
-\cite{Cejnar_2009, Sachdev_2011, Cejnar_2015, Cejnar_2016, Caprio_2008, Macek_2019} A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter.
-\cite{Cejnar_2009, Sachdev_2011}
+\cite{Cejnar_2005,Cejnar_2007,Caprio_2008,Cejnar_2009,Sachdev_2011,Cejnar_2015,Cejnar_2016, Macek_2019,Cejnar_2020}
+A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter. \cite{Cejnar_2009, Sachdev_2011} 
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
@@
 
-Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the IBM model from the QPT's point of view \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}. 
+Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the interaction boson model from a QPT point of view. \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}
 The phase of the ensemble of $s$ and $d$ bosons is characterised by a dynamical symmetry. 
@@
 For example, without interaction the ground state is the spherical phase (a condensate of $s$ bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of $s$ and $d$ bosons states.
-In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched \cite{SzaboBook}.
+In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched.
+\cite{SzaboBook}
 It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory. 

### 2020-11-20 Manuscript/EPAWTFT.tex
adding bunch of refs and other stuff

@@
 singularities of $E(\lambda)$ in the complex $\lambda$ plane.
-This property arises from the following theorem: \cite{Goodson_2012}
+This property arises from the following theorem: \cite{Goodson_2011}
 \begin{quote}
@@
 singularity in $E(\lambda)$ that is closest to the origin.
-Like the exact system in Section~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
+Like the exact system in Sec.~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
 a ``one-to-many'' function with the output elements representing an approximation to both the ground and excited states.
@@
 Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
-In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series taking again as an example the water molecule in a stretched geometry.
+In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
 In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
@@
 
-In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behavior of the MP series.
-\cite{Olsen_1996} They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and \ce{HF}.
+In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behavior of the MP series. \cite{Olsen_1996} 
+They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and the \ce{HF} molecule.
 \cite{Olsen_1996, Christiansen_1996} Cremer and He had already studied these two systems and classified them as \textit{class B} systems.
@@
 To do so, they analysed the relation between the dominant singularity (\ie, the closest singularity to the origin) and the convergence behaviour of the series.
-\cite{Olsen_2000} Their analysis is based on Darboux's theorem:
+\cite{Olsen_2000} Their analysis is based on Darboux's theorem: \cite{Goodson_2011}
 \begin{quote}
-	\textit{``In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin.
-Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.''}
+	\textit{``In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin. ''}
 \end{quote}
-
+Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.
 A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).

### 2020-11-20 Manuscript/EPAWTFT.tex
moving stuff around

@@
 
+\tableofcontents
+
 %%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Background}
 \label{sec:intro}
 %%%%%%%%%%%%%%%%%%%%%%%
-
-%======================%
-\subsection{Background}
-%=======================%
 
@@
 
+\titou{The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
+\cite{MoiseyevBook}
+Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
+We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\section{Exceptional points in electronic structure}
+\label{sec:EPs}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 %===================================%
-\subsection{Illustrative Example}
+\subsection{Exceptional points in the Hubbard dimer}
 \label{sec:example}
@@
 
-\titou{The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
-\cite{MoiseyevBook}
-Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
-We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Perturbation theory}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %============================================================%
@@
 
-%============================================================%
-\subsection{The Hartree-Fock Hamiltonian}
-%============================================================%
+%===========================================%
+\subsection{Hartree-Fock theory}
+%===========================================%
 
@@
 
-%
-%The spatial part of the RHF wave function is then
-%\begin{equation}\label{eq:RHF_WF}
-%	\Psi_{\text{RHF}}(\theta_1,\theta_2) = Y_0(\theta_1) Y_0(\theta_2),
-%\end{equation}
-%where $\theta_i$ is the polar angle of the $i$th electron and $Y_{\ell}(\theta)$ is a zonal spherical harmonic. 
-%Because $Y_0(\theta) = 1/\sqrt{4\pi}$, it is clear that the RHF wave function yields a uniform one-electron density.
-%
+%================================================================%
+\subsection{The Hartree-Fock approximation in the Hubbard dimer}
+%================================================================%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{M{\o}ller-Plesset perturbation theory}
+\label{sec:MP}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %=====================================================%
-\subsection{M{\o}ller-Plesset perturbation theory}
+\subsection{Basics}
 %=====================================================%
@@
     \hH(\lambda) =   
-    \sum_{i}^{N} \Bigg( 
-    -\frac{\grad_i^2}{2} 
-    - \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+     \sum_{i}^{N} \qty[ - \frac{\grad_i^2}{2} - \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} ]
     \\
-    + (1-\lambda) v^{\text{HF}}(\vb{x}_i) 
-    + \lambda\sum_{i<j}^{N}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}} 
-    \Bigg).
+    + (1-\lambda) \sum_{i}^{N} v^{\text{HF}}(\vb{x}_i)
+    + \lambda\sum_{i<j}^{N}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}.
 \end{multline}
@@
 where $\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}$ are the anti-symmetrised two-electron integrals
-in the molecular spin-obital basis\cite{Gill_1994}
+in the molecular spin-orbital basis\cite{Gill_1994}
 \begin{equation}
@@
 %If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
+
+Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
+i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
+Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
+ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
+iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
+
+%=====================================================%
+\subsection{Behavior of the M{\o}ller-Plesset series in molecular systems}
+%=====================================================%
+
+When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
+%In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
+In other words, one would like a monotonic convergence of the MP series.
+Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
+Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
+In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example, in the case of \ce{He2^2+}, RMP5 is worse than RMP4).
+On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
+Thus, one cannot practically use it for systems where only the first terms can be computed.
+
+When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
+Yet the HF wave function is restricted to be a single Slater determinant.
+It is then inappropriate to model (even qualitatively) stretched systems.
+Nevertheless, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
+One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
+However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
+
+In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
+Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination for \ce{H2} in a minimal basis.
+\cite{Gill_1988}
+Handy and coworkers reported the same behaviour of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
+\cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
+\cite{Lepetit_1988}
+They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations. 
+Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
+They highlighted that \cite{Cremer_1996}
+\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+Moreover, they analyzed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation.
+On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
+This observation on the contribution to the MPn energy corroborates the electronic structure discussed above.
+As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+
+%==========================================%
+\subsection{Behavior of the M{\o}ller-Plesset series in the Hubbard dimer}
+%==========================================%
 
@@
 
-Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
-i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
-Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
-ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
-iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Historical overview}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%=====================================================%
-\subsection{Behavior of the M{\o}ller-Plesset series}
-%=====================================================%
-
-When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
-%In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
-In other words, one would like a monotonic convergence of the MP series.
-Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
-Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
-For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
-In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example, in the case of \ce{He2^2+}, RMP5 is worse than RMP4).
-On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
-Thus, one cannot practically use it for systems where only the first terms can be computed.
-
-When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
-Yet the HF wave function is restricted to be a single Slater determinant.
-It is then inappropriate to model (even qualitatively) stretched systems.
-Nevertheless, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
-One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system.
-However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
-
-In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
-Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination for \ce{H2} in a minimal basis.
-\cite{Gill_1988}
-Handy and coworkers reported the same behaviour of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
-\cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
-\cite{Lepetit_1988}
-They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations. 
-Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
-Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets.
-They highlighted that \cite{Cremer_1996}
-\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-Moreover, they analyzed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
-They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation.
-On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
-This observation on the contribution to the MPn energy corroborates the electronic structure discussed above.
-As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
-The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
-
-Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning.
-\cite{Mihalka_2017a}
-Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
-In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
-In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
-However, the choice of the functional form of the fit remains a subtle task.
-This technique was first generalised by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
-\begin{equation}
-	\label{eq:Cauchy}
-	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(\lambda)}{\lambda - a} = E(a),
-\end{equation}
-which states that the value of the energy can be computed at $\lambda=a$ inside the complex contour $\gamma$ only by the knowledge of its values on the same contour.
-Their method consists in refining self-consistently the values of $E(\lambda)$ computed on a contour going through the physical point at $\lambda = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
-The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(\lambda)$ is analytic.
-When the values of $E(\lambda)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(\lambda=1)$ which corresponds to the final estimate of the FCI energy.
-The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
-
 %==========================================%
-\subsection{Insights from a two-state model}
+\subsection{Further insights from a two-state model}
 %==========================================%
@@
 We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, \ie, to the multi-reference nature of the wave function thus to the static part of the correlation energy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Exploiting complex analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%==========================================%
+\subsection{Pad\'e approximant}
+%==========================================%
+
+%==========================================%
+\subsection{Analytic continuation}
+%==========================================%
+
+Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning.
+\cite{Mihalka_2017a}
+Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
+In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
+In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
+However, the choice of the functional form of the fit remains a subtle task.
+This technique was first generalised by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
+\begin{equation}
+	\label{eq:Cauchy}
+	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(\lambda)}{\lambda - a} = E(a),
+\end{equation}
+which states that the value of the energy can be computed at $\lambda=a$ inside the complex contour $\gamma$ only by the knowledge of its values on the same contour.
+Their method consists in refining self-consistently the values of $E(\lambda)$ computed on a contour going through the physical point at $\lambda = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
+The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(\lambda)$ is analytic.
+When the values of $E(\lambda)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(\lambda=1)$ which corresponds to the final estimate of the FCI energy.
+The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
 

### 2020-11-22 Manuscript/EPAWTFT.tex
minor corrections up to MP section

@@
 After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree-Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
-In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller-Plesset perturbation theory.
-
+In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller-Plesset perturbation theory and its apparent link with quantum phase transitions.
 \end{abstract}
@@
 \cite{MoiseyevBook,Heiss_1988,Heiss_1990,Heiss_1999,Berry_2011,Heiss_2012,Heiss_2016,Benda_2018}
-They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photo-chemical mechanisms.
+They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
 In the case of auto-ionising resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
@@
 
-To illustrate the concepts discussed throughout this article, we will consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
+To illustrate the concepts discussed throughout this article, we consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
 Analytically solvable model systems are essential in theoretical chemistry and physics as the simplicity of the
@@
 that complex singularities are essential to fully understand the series convergence on the real axis.\cite{BenderBook}
-
-The radius of convergence for the perturbation series is therefore dictated by the magnitude $\abs{\lambda_0}$ of the
+\titou{Include Antoine's example $\sum_{n=1}^\infty \lambda^n/n$ which is divergent at $\lambda = 1$ but convergent at $\lambda = -1$.}
+
+The radius of convergence for the perturbation series is therefore dictated by the magnitude \titou{$\abs{\lambda_0}$} of the
 singularity in $E(\lambda)$ that is closest to the origin.
@@
 \begin{equation}
+\label{eq:Hcore}
 	\Hat{h}(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
@@
 In the most flexible variant of real HF theory (generalised HF) the one-electron orbitals can be complex-valued
-and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993}
+and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993,Jimenez-Hoyos_2011}
 However, the application of HF with some level of constraint on the orbital structure is far more common.
@@
 There also exist symmetry-breaking processes at the RHF level where a charge-density wave is created via the oscillation between the situations where the two electrons are one side or the other.
-\cite{GiulianiBook}
+\cite{StuberPaldus,Fukutome_1981}
 
@@
 % INTRODUCE PARAMETRISED FOCK HAMILTONIAN
-The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
+The inherent non-linearity in the Fock eigenvalue problem \eqref{eq:FockOp} arises from self-consistency 
 in the HF approximation, and is usually solved through an iterative approach.\cite{SzaboBook}
 Alternatively, the non-linear terms arising from the Coulomb and exchange operators can 
-be considered as a perturbation from the core Hamiltonian by introducing the
+be considered as a perturbation from the core Hamiltonian \eqref{eq:Hcore} by introducing the
 transformation $U \rightarrow \lambda\, U$, giving the parametrised Fock operator 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller-Plesset perturbation theory}
+\section{M{\o}ller-Plesset perturbation theory in the complex plane}
 \label{sec:MP}
@@
 i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
-Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
+%Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
 ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
@@
 On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
-Thus, one cannot practically use it for systems where only the first terms can be computed.
+Thus, one cannot practically use it for systems where only the first terms are computationally accessible.
 

### 2020-11-23 Manuscript/EPAWTFT.tex
modifications in MP section

@@
 \subsection{Hartree-Fock theory}
+\label{sec:HF}
 %===========================================%
@@
 \subsection{The Hartree-Fock approximation in the Hubbard dimer}
+\label{sec:HF_hubbard}
 %================================================================%
@@
 When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
-%In other words, each time a higher-order term is computed, one would like to obtained an overall result closer to the exact energy. 
 In other words, one would like a monotonic convergence of the MP series.
 Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
-Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behavior of the perturbative coefficients are not uncommon.
-For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986, Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
-In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion (for example, in the case of \ce{He2^2+}, RMP5 is worse than RMP4).
-On the other hand, the UMP series is monotonically convergent (except for the first few orders) but very slowly. 
+Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behaviour of the perturbative coefficients are not uncommon.
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
+In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion.
+For example, in the case of the barrier to homolytic fission of \ce{He2^2+} in a minimal basis set, RMP5 is worse than RMP4 (see Fig.~2 in Ref.~\onlinecite{Gill_1986}).
+On the other hand, the UMP series is monotonically convergent after UMP5 but very slowly . 
 Thus, one cannot practically use it for systems where only the first terms are computationally accessible.
@@
 When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
-Yet the HF wave function is restricted to be a single Slater determinant.
+Yet, the HF wave function is restricted to be a single Slater determinant.
 It is then inappropriate to model (even qualitatively) stretched systems. 
-Nevertheless, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see for example the case of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
+Nevertheless, as explained in Sec.~\ref{sec:HF} and illustrated in Sec.~\ref{sec:HF_hubbard}, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see also the pedagogical example of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
 One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system. 
-However, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
+However, as illustrated above, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
+The reasons behind this ambiguous behaviour are further explained below.
 
@@
 \cite{Gill_1988}
-Handy and coworkers reported the same behaviour of the series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
+Handy and coworkers reported the same behaviour of the UMP series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
 \cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
 \cite{Lepetit_1988}
-They concluded that the slow convergence is due to the coupling of the singly- and doubly-excited configurations. 
-Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+They concluded that the slow convergence of the UMP series is due to i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2}) tends to a constant instead of vanishing, and ii) the lack of the singly-excited configurations (which only appears at fourth order) that strongly couple to the doubly-excited configurations.
+
+Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
 Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
@@
 \textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-Moreover, they analyzed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
 They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
 On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
-This observation on the contribution to the MPn energy corroborates the electronic structure discussed above.
+This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
 As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
 Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+\cite{Cremer_1996}
 The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Cremer and He clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 

### 2020-11-23 Manuscript/EPAWTFT.tex
small modifs in MP Hubbard section

@@
 Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behaviour of the perturbative coefficients are not uncommon.
-For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985, Lepetit_1988}).
+For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985,Lepetit_1988}).
 In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion.
@@
 They concluded that the slow convergence of the UMP series is due to i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2}) tends to a constant instead of vanishing, and ii) the lack of the singly-excited configurations (which only appears at fourth order) that strongly couple to the doubly-excited configurations.
+We believe that this divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting the structure of the reference orbitals rather than capturing the correlation energy.
 
@@
 These EPs are identical than the exact EPs discussed in Sec.~\ref{sec:example}.
-The Taylor expansion of the RMP energy can then be evaluated to obtain the $n$th-order MP correction
+The Taylor expansion of the RMP energy can then be evaluated to obtain the $k$th-order MP correction
 \begin{equation}
@@
 The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
-\ref{subfig:RMP_4.5} respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
+\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
 by the vertical cylinder of unit radius.
@@
 from the single excitations.\cite{Lepetit_1988}
-This divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting
-the structure of the reference orbitals rather than capturing the correlation energy.
 
@@
 While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
-Instead, the radius of convergence of the UMP series can obtained numerically as a function of $U/t$, as shown
+Instead, the radius of convergence of the UMP series can be obtained numerically as a function of $U/t$, as shown
 in Fig.~\ref{fig:RadConv}.
@@
 the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
-first-excited open-shell singlet, and the other connecting the open-shell singlet state to the 
+first-excited \titou{open-shell singlet?}, and the other connecting the \titou{open-shell singlet?} to the 
 doubly-excited second excitation (Fig.~\ref{fig:UMP}).
@@
 	The Riemann surfaces associated with the exact energies of the UMP Hamiltonian \eqref{eq:H_UMP} are also represented for these two values of $U/t$ as functions of $\lambda$.
+\titou{Please Hugh, modify central figure.}
 	\label{fig:UMP}}

### 2020-11-23 Manuscript/EPAWTFT.tex
small modifs in Olsen section

@@
 
-In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behavior of the MP series. \cite{Olsen_1996} 
-They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and the \ce{HF} molecule.
-\cite{Olsen_1996, Christiansen_1996} Cremer and He had already studied these two systems and classified them as \textit{class B} systems.
+In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behaviour of the MP series. \cite{Olsen_1996} 
+They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and the \ce{HF} molecule. \cite{Olsen_1996, Christiansen_1996} 
+Cremer and He had already studied these two systems and classified them as \textit{class B} systems. 
 However, the analysis of Olsen and coworkers was performed in larger basis sets containing diffuse functions. 
@@
 The discovery of this divergent behaviour is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
+\cite{Loos_2019d,Giner_2019}
 Including diffuse functions is particularly important in the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
+\cite{Loos_2018a,Loos_2020a}
 As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence. 
@@
 \end{quote}
+\titou{T2: should we move this theorem earlier?}
 Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.
 A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
-Their method consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities. 
+
+Following their observations from Ref.~\onlinecite{Olsen_1996}, Olsen and collaborators later proposed a simple method which consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities.
+\cite{Olsen_2000}
 Then, by modelling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ matrix
 \begin{equation}
+	\label{eq:Olsen_2x2}
 	\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta \\ \delta & - \gamma)}_{\bV},
@@
 
-They first studied molecules with low-lying doubly-excited states of the same spatial and spin symmetry.
-The exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states were good candidates for being intruder states.
-For \ce{CH_2} in a large basis set, the series is convergent up to the 50th order.
+They first studied an example of molecules with low-lying doubly-excited states of the same spatial and spin symmetry as the ground state. \cite{Olsen_2000}
+In such a case, the exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states are good candidates for being intruder states. 
+For \ce{CH_2} in a diffuse yet rather small basis set, the series is convergent at least up to the 50th order. 
 They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
 
-Then they demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state. 
+Then, they demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state. 
 When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back-door intruder state. 
@@
 
-In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} is generalised to a non-symmetric Hamiltonian 
+In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} [see Eq.~\eqref{eq:Olsen_2x2}] is generalised to a non-symmetric Hamiltonian 
 \begin{equation}
@@
 \end{equation}
-allowing an analysis of various choice of perturbation (not only the MP partioning) such as coupled cluster perturbation expansions \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} and other non-Hermitian perturbation methods.
+allowing an analysis of various choice of perturbation (not only the MP partitioning) such as coupled cluster perturbation expansions \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} and other non-Hermitian perturbation methods.
 It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
@@
 These so-called archetypes can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
+Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
 Importantly, they observed that the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
-Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern;
-the three remaining archetypes seem to be rarely observed in MP perturbation theory.
+The three remaining archetypes seem to be rarely observed in MP perturbation theory.
 However, in the non-Hermitian setting of coupled cluster perturbation theory, \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} on can encounter interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric archetypes.

### 2020-11-23 Manuscript/EPAWTFT.tex
small modifs in singularity structure

@@
 In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+\cite{Olsen_1996,Olsen_2000,Olsen_2019}
 They regrouped singularities in two classes: i) $\alpha$ singularities which have ``large'' imaginary parts, and ii) $\beta$ singularities which have very small imaginary parts. 
-Singularities of type $\alpha$ are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work of Stillinger. \cite{Stillinger_2000}
+Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
+They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
 
@@
 The major difference between these two terms is that the repulsive mean field is localised around the nuclei whereas the interelectronic interaction persist away from the nuclei. 
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value of $\lambda$, $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the electron-nucleus attraction.
+If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the electron-nucleus attraction.
 For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei. 
@@
 Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-This explains that Olsen \textit{et al.}, because they used a simple $2\times2$ model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
-
-Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the stretching of the system. 
+This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
+
+Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
 On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
 According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
-This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium geometry and stretched geometry. 
+This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
 To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.

### 2020-11-23 Manuscript/EPAWTFT.tex
Added some references, reorganised some of Section II

@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\section{Background}
+\section{Introduction}
 \label{sec:intro}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\section{Exceptional points in electronic structure}
+\section{Exceptional Points in Electronic Structure}
 \label{sec:EPs}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Time-Independent Schr\"odinger Equation}
+\label{sec:TDSE}
+%%%%%%%%%%%%%%%%%%%%%%%
+Within the Born-Oppenheimer approximation, the exact molecular Hamiltonian with $\Ne$ electrons and 
+$\Nn$ (clamped) nuclei is defined \hugh{for a given nuclear framework} as
+\begin{equation}\label{eq:ExactHamiltonian}
+    \hugh{\hH(\vb{R})} = 
+    - \frac{1}{2} \sum_{i}^{\Ne} \grad_i^2 
+    - \sum_{i}^{\Ne} \sum_{A}^{\Nn} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
+    + \sum_{i<j}^{\Ne}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}},
+\end{equation}
+where $\vb{r}_i$ defines the position of the $i$-th electron, $\vb{R}_{A}$ and $Z_{A}$ are the position
+and charge of the $A$-th nucleus respectively, \hugh{and $\vb{R} = (\vb{R}_{1}, \dots, \vb{R}_{\Nn})$ is a
+collective vector for the nuclear positions.}
+The first term represents the kinetic energy of the electrons, while 
+the two following terms account for the electron-nucleus attraction and the electron-electron repulsion.
+
+% EXACT SCHRODINGER EQUATION
+The exact many-electron wave function \hugh{at a given nuclear geometry} $\Psi(\vb{R})$ corresponds 
+to the solution of the (time-independent) Schr\"{o}dinger equation
+\begin{equation} 
+    \hugh{\hH(\vb{R})\, \Psi(\vb{R}) = E(\vb{R})\, \Psi(\vb{R}),}
+    \label{eq:SchrEq}
+\end{equation} 
+with the eigenvalues $E(\vb{R})$ providing the exact energies.
+\hugh{The energy $E(\vb{R})$ can be considered as a ``one-to-many'' function since each input nuclear geometry
+yields several eigenvalues corresponding to the ground and excited states of the exact spectrum.}
+However, exact solutions to Eq.~\eqref{eq:SchrEq} are only possible in the simplest of systems, such as 
+the one-electron hydrogen atom and some specific two-electron systems with well-defined mathematical 
+properties.\cite{Taut_1993,Loos_2009b,Loos_2010e,Loos_2012}
+\hugh{In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
+the perturbation theories and Hartree--Fock approximation considered in this review
+In what follows, we will drop the parametric dependence on the nuclear geometry and, 
+unless otherwise stated, atomic units will be used throughout.}
+
 %===================================%
-\subsection{Exceptional points in the Hubbard dimer}
+\subsection{Exceptional Points in the Hubbard Dimer}
 \label{sec:example}
@@
 To illustrate the concepts discussed throughout this article, we consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
-Analytically solvable model systems are essential in theoretical chemistry and physics as the simplicity of the
-mathematics compared to realistic systems (e.g., atoms and molecules) readily allows concepts to be illustrated and new methods to be tested wile retaining much 
-of the key physics.
+Analytic\trashHB{ally solvable} model systems are essential in theoretical chemistry and physics as their \hugh{mathematical} simplicity \trashHB{of the
+mathematics} compared to realistic systems (e.g., atoms and molecules) allows new concepts and methods to be 
+easily \trashHB{illustrated and} tested while retaining the key physical phenomena.
+\hugh{(HGAB: This sentence felt too long to me. Feel free to re-instate words if you think they are neccessary)}
 
@@
 In the weak correlation regime (small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
-In the large-$U$ (or strong correlation) regime, the electron repulsion term drives the physics and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
+In the large-$U$ (or strong correlation) regime, the electron repulsion term \hugh{becomes dominant} \trashHB{drives the physics}
+and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
 This phenomenon is often referred to as Wigner crystallisation. \cite{Wigner_1934}
 
-To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$.
+To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$
+\hugh{to give the parameterised Hamiltonian $\hH(\lambda)$.}
 When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) (eigen)energies
@@
 
+% LOCATING EPS
+\hugh{To locate EPs in practice, one must simultaneously solve
+\begin{subequations}
+\begin{align}
+	\label{eq:PolChar}
+	\det[E\hI-\hH(\lambda)] & = 0,
+	\\ 
+	\label{eq:DPolChar}
+	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
+\end{align}
+\end{subequations}
+where $\hI$ is the identity operator.\cite{Cejnar_2007}
+Equation \eqref{eq:PolChar} is the well-known secular equation providing the (eigen)energies of the system. 
+If the energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is at least two-fold degenerate. 
+These degeneracies can be conical intersections between two states with different symmetries 
+for real values of $\lambda$,\cite{Yarkony_1996} or EPs between two states with the 
+same symmetry for complex values of $\lambda$.}
+
 %============================================================%
-\subsection{Rayleigh-Schr\"odinger perturbation theory}
+\subsection{Rayleigh-Schr\"odinger Perturbation Theory}
 %============================================================%
 
-Within the Born-Oppenheimer approximation, the exact molecular Hamiltonian with $\Ne$ electrons and 
-$\Nn$ (clamped) nuclei is defined as
-\begin{equation}\label{eq:ExactHamiltonian}
-    \hH = 
-    - \frac{1}{2} \sum_{i}^{\Ne} \grad_i^2 
-    - \sum_{i}^{\Ne} \sum_{A}^{\Nn} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}} 
-    + \sum_{i<j}^{\Ne}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}},
-\end{equation}
-where $\vb{r}_i$ defines the position of the $i$-th electron, and $\vb{R}_{A}$ and $Z_{A}$ are the position
-and charge of the $A$-th nucleus respectively.
-The first term represents the kinetic energy of the electrons, while 
-the two following terms account for the electron-nucleus attraction and the electron-electron repulsion.
-Atomic units are used unless otherwise stated.
-
-% EXACT SCHRODINGER EQUATION
-The exact many-electron wave function $\Psi$ corresponds to the solution of the (time-independent)
-Schr\"{o}dinger equation
-\begin{equation} 
-	\hH\Psi = E \Psi,
-    \label{eq:SchrEq}
-\end{equation} 
-with the eigenvalue $E$ providing the exact energy.
-Exact solutions to Eq.~\eqref{eq:SchrEq} are only possible in the simplest of systems, such as 
-the one-electron hydrogen atom and some specific two-electron systems with well-defined mathematical properties. \cite{Taut_1993,Loos_2009b,Loos_2010e,Loos_2012}
-In practice, one of the most common approximations involves
-a perturbative expansion of the energy.
+\hugh{One of the most common routes to approximately solving the Schr\"odinger equation
+is to introduce a perturbative expansion of the exact energy.}
 % SUMMARY OF RS-PT
@@
 converge in this domain.
-However, this series diverges $x \ge 1$.
+However, this series diverges for $x \ge 1$.
 This divergence occurs because $f(x)$ has four singularities in the complex 
@@
 
-The radius of convergence for the perturbation series is therefore dictated by the magnitude \titou{$\abs{\lambda_0}$} of the
+The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude \titou{$\abs{\lambda_0}$} of the
 singularity in $E(\lambda)$ that is closest to the origin.
@@
 
-Practically, to locate EPs, one must simultaneously solve
-\begin{subequations}
-\begin{align}
-	\label{eq:PolChar}
-	\det[E\hI-\hH(\lambda)] & = 0,
-	\\ 
-	\label{eq:DPolChar}
-	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
-\end{align}
-\end{subequations}
-where $\hI$ is the identity operator.\cite{Cejnar_2007}
-Equation \eqref{eq:PolChar} is the well-known secular equation providing the (eigen)energies of the system. 
-If the energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is at least two-fold degenerate. 
-These degeneracies can be conical intersections between two states with different symmetries 
-for real values of $\lambda$,\cite{Yarkony_1996} or EPs between two states with the 
-same symmetry for complex values of $\lambda$.
-
 %===========================================%
-\subsection{Hartree-Fock theory}
+\subsection{Hartree-Fock Theory}
 \label{sec:HF}
@@
 \end{equation}
-Here the core Hamiltonian is
+Here the \hugh{(one-electron)} core Hamiltonian is
 \begin{equation}
@@
 However, the application of HF with some level of constraint on the orbital structure is far more common.
-Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, while allowing different orbitals for different spins leads to the so-called unrestricted HF (UHF) approach.
+Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, 
+while allowing different orbitals for different spins leads to the so-called unrestricted HF (UHF) approach.\cite{StuberPaldus}
 The advantage of the UHF approximation is its ability to correctly describe strongly correlated systems, 
-such as the dissociation of the hydrogen dimer.\cite{Coulson_1949}
+such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer,\cite{Coulson_1949}
 However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
@@
 %================================================================%
-\subsection{The Hartree-Fock approximation in the Hubbard dimer}
+\subsection{Hartree-Fock in the Hubbard Dimer}
 \label{sec:HF_hubbard}
@@
     RHF and UHF energies as a function of the correlation strength $U/t$. 
-    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot) known as the Coulson-Fischer point.}
+    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson-Fischer point.}
 \end{figure}
@@
 
-Returning to the Hubbard dimer, the UHF energy can be parametrised in terms of two rotation angles $\ta$ and $\tb$ as
-\begin{equation}
-E_\text{HF}(\ta, \tb) = -t \qty( \sin \ta + \sin \tb ) + \frac{U}{2} \qty( 1 + \cos \ta \cos \tb ),
+In the Hubbard dimer, the UHF energy can be parametrised using two rotation angles $\ta$ and $\tb$ as
+\begin{equation}
+E_\text{HF}(\ta, \tb) = -t\, \qty( \sin \ta + \sin \tb ) + \frac{U}{2} \qty( 1 + \cos \ta \cos \tb ),
 \end{equation}
@@
 \end{equation}
-However, in the strongly correlated regime $U>2t$, the closed-shell restriction on the orbitals prevents RHF from 
-correctly modelling the physics of the system with the two electrons on opposing sites.
+However, in the strongly correlated regime $U>2t$, the closed-shell orbital restriction prevents RHF from 
+modelling the correct physics with the two electrons on opposing sites.
 
@@
     the \textit{quasi}-EP $\lambda_{\text{c}}$ (black dot).
-    The RHF solution is independent of $\lambda$, giving constant plane at $\pi/2$.
+    The RHF solution is independent of $\lambda$, giving the constant plane at $\pi/2$.
     (\subref{subfig:UHF_cplx_energy}) The corresponding HF energy surfaces show a non-analytic 
@@
 by swapping $\ta^{\text{UHF}}$ and $\tb^{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
-This type of symmetry breaking is also called a spin-density wave in the physics community as the system ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
-There also exist symmetry-breaking processes at the RHF level where a charge-density wave is created via the oscillation between the situations where the two electrons are one side or the other.
-\cite{StuberPaldus,Fukutome_1981}
+This type of symmetry breaking is also called a spin-density wave in the physics community as the system
+``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
+\hugh{Symmetry breaking can also occur in RHF theory when a charge-density wave is formed from an oscillation 
+between the two closed-shell configurations with both electrons localised on one site or the other.\cite{StuberPaldus,Fukutome_1981}}
 
 %============================================================%
-\subsection{Self-consistency as a perturbation} %OR {Complex adiabatic connection}
+\subsection{Self-Consistency as a Perturbation} %OR {Complex adiabatic connection}
 %============================================================%
@@
 % INTRODUCE PARAMETRISED FOCK HAMILTONIAN
-The inherent non-linearity in the Fock eigenvalue problem \eqref{eq:FockOp} arises from self-consistency 
-in the HF approximation, and is usually solved through an iterative approach.\cite{SzaboBook}
+The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
+in the HF approximation, and is usually solved through an iterative approach.\cite{Roothaan1951,Hall1951}
 Alternatively, the non-linear terms arising from the Coulomb and exchange operators can 
@@
 \begin{equation}
-    \Hat{f}_{\lambda}(\vb{x}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+    \Hat{f}(\vb{x} \hugh{; \lambda}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
 \end{equation}

### 2020-11-23 Manuscript/EPAWTFT.tex
Added references and personal reading notee

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller-Plesset perturbation theory in the complex plane}
+\section{M{\o}ller-Plesset Perturbation Theory in the Complex Plane}
 \label{sec:MP}
@@
 %=====================================================%
-\subsection{Basics}
+\subsection{Background Theory}
 %=====================================================%
@@
 \end{multline}
-Any set of orbitals can be used to define the HF Hamiltonian, although usually either the RHF or UHF orbitals are chosen to 
+Any set of orbitals can be used to define the HF Hamiltonian, although either the RHF or UHF orbitals are usually chosen to 
 define the RMP or UMP series respectively.
@@
 
-While most practical calculations usually consider only the MP2 or MP3 approximations, higher order terms can 
+While most practical calculations generally consider only the MP2 or MP3 approximations, higher order terms can 
 easily be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}
@@
 \cite{JensenBook}
-%In order to better understand the behavior of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
+%In order to better understand the behaviour of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
 %For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
@@
 
-Obviously, although practically convenient for electronic structure calculations, the MP partitioning is not the only possibility, and alternative partitioning have been proposed in the literature:
+Although practically convenient for electronic structure calculations, the MP partitioning is not 
+the only possibility and alternative partitionings have been considered including: %proposed in the literature:
 i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
@@
 iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
+\hugh{While an in-depth comparison of these different approaches can offer insight into 
+their relative strengths and weaknesses for various situations, we will restrict our current discussion
+to the convergence properties of the MP expansion.}
 
 %=====================================================%
-\subsection{Behavior of the M{\o}ller-Plesset series in molecular systems}
+\subsection{M{\o}ller-Plesset Convergence in Molecular Systems}
 %=====================================================%
@@
 %==========================================%
-\subsection{Behavior of the M{\o}ller-Plesset series in the Hubbard dimer}
+\subsection{M{\o}ller-Plesset Convergence in the Hubbard Dimer}
 %==========================================%

### 2020-11-24 Manuscript/EPAWTFT.tex
minor corrections in QPT

@@
 In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point. 
-In a finite basis set this critical point is model by a cluster of $\beta$ singularities. 
+In a finite basis set, this critical point is model by a cluster of $\beta$ singularities. 
 It is now well known that this phenomenon is a special case of a more general phenomenon. 
@@
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
-Otherwise, it is called continuous and of $m$th order if the $m$th derivative is discontinuous. 
+Otherwise, it is called continuous and of $m$th order (with $m \ge 2$) if the $m$th derivative is discontinuous. 
 A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
@@
 Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
-More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT. \cite{Stransky_2018} 
+More recently Stransky and coworkers proved that the distribution of EPs is characteristic of the QPT order. \cite{Stransky_2018} 
 In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
@@
 Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.
+
 Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities. 

### 2020-11-24 Manuscript/EPAWTFT.tex
add Antoine example and degreenified Hugh comments

@@
 Within the Born-Oppenheimer approximation, the exact molecular Hamiltonian with $\Ne$ electrons and 
-$\Nn$ (clamped) nuclei is defined \hugh{for a given nuclear framework} as
+$\Nn$ (clamped) nuclei is defined for a given nuclear framework as
 \begin{equation}\label{eq:ExactHamiltonian}
-    \hugh{\hH(\vb{R})} = 
+    \hH(\vb{R}) = 
     - \frac{1}{2} \sum_{i}^{\Ne} \grad_i^2 
@@
 where $\vb{r}_i$ defines the position of the $i$-th electron, $\vb{R}_{A}$ and $Z_{A}$ are the position
-and charge of the $A$-th nucleus respectively, \hugh{and $\vb{R} = (\vb{R}_{1}, \dots, \vb{R}_{\Nn})$ is a
-collective vector for the nuclear positions.}
+and charge of the $A$-th nucleus respectively, and $\vb{R} = (\vb{R}_{1}, \dots, \vb{R}_{\Nn})$ is a
+collective vector for the nuclear positions.
 The first term represents the kinetic energy of the electrons, while 
@@
 % EXACT SCHRODINGER EQUATION
-The exact many-electron wave function \hugh{at a given nuclear geometry} $\Psi(\vb{R})$ corresponds 
+The exact many-electron wave function at a given nuclear geometry $\Psi(\vb{R})$ corresponds 
 to the solution of the (time-independent) Schr\"{o}dinger equation
 \begin{equation} 
-    \hugh{\hH(\vb{R})\, \Psi(\vb{R}) = E(\vb{R})\, \Psi(\vb{R}),}
+    \hH(\vb{R})\, \Psi(\vb{R}) = E(\vb{R})\, \Psi(\vb{R}),
     \label{eq:SchrEq}
@@
 with the eigenvalues $E(\vb{R})$ providing the exact energies.
-\hugh{The energy $E(\vb{R})$ can be considered as a ``one-to-many'' function since each input nuclear geometry
-yields several eigenvalues corresponding to the ground and excited states of the exact spectrum.}
+The energy $E(\vb{R})$ can be considered as a ``one-to-many'' function since each input nuclear geometry
+yields several eigenvalues corresponding to the ground and excited states of the exact spectrum.
 However, exact solutions to Eq.~\eqref{eq:SchrEq} are only possible in the simplest of systems, such as 
@@
 properties.\cite{Taut_1993,Loos_2009b,Loos_2010e,Loos_2012}
-\hugh{In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
+In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
 the perturbation theories and Hartree--Fock approximation considered in this review
 In what follows, we will drop the parametric dependence on the nuclear geometry and, 
-unless otherwise stated, atomic units will be used throughout.}
+unless otherwise stated, atomic units will be used throughout.
 
@@
 To illustrate the concepts discussed throughout this article, we consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
-Analytic\trashHB{ally solvable} model systems are essential in theoretical chemistry and physics as their \hugh{mathematical} simplicity \trashHB{of the
-mathematics} compared to realistic systems (e.g., atoms and molecules) allows new concepts and methods to be 
-easily \trashHB{illustrated and} tested while retaining the key physical phenomena.
-\hugh{(HGAB: This sentence felt too long to me. Feel free to re-instate words if you think they are neccessary)}
+Analytically solvable models are essential in theoretical chemistry and physics as their mathematical simplicity compared to realistic systems (e.g., atoms and molecules) allows new concepts and methods to be
+easily tested while retaining the key physical phenomena.
 
@@
 In the weak correlation regime (small $U$), the kinetic energy dominates and the electrons are delocalised over both sites.
-In the large-$U$ (or strong correlation) regime, the electron repulsion term \hugh{becomes dominant} \trashHB{drives the physics}
+In the large-$U$ (or strong correlation) regime, the electron repulsion term becomes dominant 
 and the electrons localise on opposite sites to minimise their Coulomb repulsion. 
@@
 
-To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$
-\hugh{to give the parameterised Hamiltonian $\hH(\lambda)$.}
+To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$ to give the parameterised Hamiltonian $\hH(\lambda)$.
 When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) (eigen)energies
@@
 % LOCATING EPS
-\hugh{To locate EPs in practice, one must simultaneously solve
+To locate EPs in practice, one must simultaneously solve
 \begin{subequations}
@@
 for real values of $\lambda$,\cite{Yarkony_1996} or EPs between two states with the 
-same symmetry for complex values of $\lambda$.}
+same symmetry for complex values of $\lambda$.
 
@@
 
-\hugh{One of the most common routes to approximately solving the Schr\"odinger equation
-is to introduce a perturbative expansion of the exact energy.}
+One of the most common routes to approximately solving the Schr\"odinger equation
+is to introduce a perturbative expansion of the exact energy.
 % SUMMARY OF RS-PT
@@
 that complex singularities are essential to fully understand the series convergence on the real axis.\cite{BenderBook}
-\titou{Include Antoine's example $\sum_{n=1}^\infty \lambda^n/n$ which is divergent at $\lambda = 1$ but convergent at $\lambda = -1$.}
-
-The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude \titou{$\abs{\lambda_0}$} of the
+
+The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude $\abs{\lambda_c}$ of the
 singularity in $E(\lambda)$ that is closest to the origin.
+Note that when $\lambda = \lambda_c$, one cannot \textit{a priori} predict if the series is convergent or not.
+For example, the series $\sum_{k=1}^\infty \lambda^k/k$ diverges at $\lambda = 1$ but converges at $\lambda = -1$.
+
 Like the exact system in Sec.~\ref{sec:example}, the perturbation energy $E(\lambda)$ represents
@@
 \end{equation}
-Here the \hugh{(one-electron)} core Hamiltonian is
+Here the (one-electron) core Hamiltonian is
 \begin{equation}
@@
 ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
-\hugh{Symmetry breaking can also occur in RHF theory when a charge-density wave is formed from an oscillation 
-between the two closed-shell configurations with both electrons localised on one site or the other.\cite{StuberPaldus,Fukutome_1981}}
+Symmetry breaking can also occur in RHF theory when a charge-density wave is formed from an oscillation 
+between the two closed-shell configurations with both electrons localised on one site or the other.\cite{StuberPaldus,Fukutome_1981}
 
@@
 \begin{equation}
-    \Hat{f}(\vb{x} \hugh{; \lambda}) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+    \Hat{f}(\vb{x} ; \lambda) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
 \end{equation}
@@
 iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
-\hugh{While an in-depth comparison of these different approaches can offer insight into 
+While an in-depth comparison of these different approaches can offer insight into 
 their relative strengths and weaknesses for various situations, we will restrict our current discussion
-to the convergence properties of the MP expansion.}
+to the convergence properties of the MP expansion.
 
@@
 \end{quote}
-\titou{T2: should we move this theorem earlier?}
 Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.

### 2020-11-24 Manuscript/EPAWTFT.tex
add Hugh references

@@
 
-\title{Perturbation theory in the complex plane: Exceptional points and where to find them}
+\title{Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them}
 
@@
 The inherent non-linearity in the Fock eigenvalue problem arises from self-consistency 
-in the HF approximation, and is usually solved through an iterative approach.\cite{Roothaan1951,Hall1951}
+in the HF approximation, and is usually solved through an iterative approach.\cite{Roothaan_1951,Hall_1951}
 Alternatively, the non-linear terms arising from the Coulomb and exchange operators can 

### 2020-11-24 Manuscript/EPAWTFT.tex
temp commit

--- 2020-11-24 Manuscript/EPAWTFT.tex
@@
 
+% GENERAL DESIRE FOR WELL-BEHAVED CONVERGENCE AND LOW-ORDER TERMS
+\hugh{Among the most desirable properties of any electronic structure technique is the existence of 
+a systematic route to increasingly accurate energies. 
+In the context of MP theory, one would like a monotonic convergence of the perturbation
+series towards the exact energy such that the accuracy increases as each term in the series is added.
+If such well-behaved convergence can be established, then our ability to compute individual 
+terms in the series becomes the only barrier to computing the exact correlation in a finite basis set.
+Unfortunately, the computational scaling of each term in the MP series increases with the perturbation
+order, and practical calculations rely on fast convergence
+to obtain high-accuracy results using only the lowest order terms.
+}
+
+% INITIAL POSITIVITY AROUND THE CONVERGENCE PROPERTIES
+\hugh{MP theory was first introduced to quantum chemistry through the pioneering
+works of Bartlett \etal{},\cite{Bartlett_1975} and Pople \etal{}.\cite{Pople_1976,Pople_1978}
+The first investigations into the convergence of the MP series followed soon after, and 
+it was quickly realised that this convergence was often very slow, or erratic. 
+}
+Given the
+
+% WORRIES ABOUT ERRATIC OR SLOW CONVERGENCE
+
+% CREMER AND HE
+
 When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
@@
 In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point. 
-In a finite basis set, this critical point is model by a cluster of $\beta$ singularities. 
+In a finite basis set this critical point is model by a cluster of $\beta$ singularities. 
 It is now well known that this phenomenon is a special case of a more general phenomenon. 
@@
 The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
-Otherwise, it is called continuous and of $m$th order (with $m \ge 2$) if the $m$th derivative is discontinuous. 
+Otherwise, it is called continuous and of $m$th order if the $m$th derivative is discontinuous. 
 A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
@@
 Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
-More recently Stransky and coworkers proved that the distribution of EPs is characteristic of the QPT order. \cite{Stransky_2018} 
+More recently Stransky and coworkers proved that the distribution of EPs is characteristic on the order of the QPT. \cite{Stransky_2018} 
 In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
@@
 Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT. 
-
 Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities. 

### 2020-11-24 Manuscript/EPAWTFT.tex
Almost there on Section III B and C...

--- 2020-11-24 Manuscript/EPAWTFT.tex
@@
 \newcommand{\eg}{\latin{e.g.}}
+\newcommand{\etal}{\latin{et.\ al}}
+
 \newcommand{\mc}{\multicolumn}
@@
 %=====================================================%
-\subsection{M{\o}ller-Plesset Convergence in Molecular Systems}
+\subsection{Early Investigations into M{\o}ller-Plesset Convergence} % in Molecular Systems}
 %=====================================================%
 
-When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
-In other words, one would like a monotonic convergence of the MP series.
+% GENERAL DESIRE FOR WELL-BEHAVED CONVERGENCE AND LOW-ORDER TERMS
+\hugh{%
+ Among the most desirable properties of any electronic structure technique is the existence of 
+a systematic route to increasingly accurate energies. 
+In the context of MP theory, one would like a monotonic convergence of the perturbation
+series towards the exact energy such that the accuracy increases as each term in the series is added.
+If such well-behaved convergence can be established, then our ability to compute individual 
+terms in the series becomes the only barrier to computing the exact correlation in a finite basis set.
+Unfortunately, the computational scaling of each term in the MP series increases with the perturbation
+order, and practical calculations must rely on fast convergence
+to obtain high-accuracy results using only the lowest order terms.
+}
+
+% INITIAL POSITIVITY AROUND THE CONVERGENCE PROPERTIES AND EARLY WORK SCOPE
+\hugh{%
+MP theory was first introduced to quantum chemistry through the pioneering
+works of Bartlett \etal\ in the context of many-body perturbation theory,\cite{Bartlett_1975}
+and Pople and co-workers in the context of determinantal expansions.\cite{Pople_1976,Pople_1978}
+Early implementations were restricted to the fourth-order MP4 approach that was considered
+to offer state-of-the-art quantitative accuracy.\cite{Pople_1978,Krishnan_1980}
+However, it was quickly realised that the MP series often demonstrated very slow, oscillatory, 
+or erratic convergence, with the UMP series showing particularly slow convergence.\cite{Laidig_1985,Knowles_1985,Handy_1985}
+For example, RMP5 is worse than RMP4 for predicting the the homolytic barrier fission of \ce{He2^2+} using a minimal basis set, 
+while the UMP series monotonically converges but becomes increasingly slow beyond UMP5.\cite{Gill_1986}
+The first examples of divergent MP series were observed in the heavy-atom \ce{N2} and \ce{F2} 
+diatomics, where low-order RMP and UMP expansions give qualitatively wrong binding curves.\cite{Laidig_1987} 
+}
+
+% SLOW UMP CONVERGENCE AND SPIN CONTAMINATION
+\hugh{%
+The divergence of RMP expansions for stretched bonds can be easily understood from two perspectives.\cite{Gill_1988a}
+Firstly, the exact wave function becomes increasingly multi-configurational as the bond is stretched, and the 
+HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
+Secondly, the energy gap between the bonding and anitbonding orbitals associated with the stretch becomes
+increasingly small at larger bond lengths, leading to a divergence in the Rayleigh--Schr\"odinger perturbation
+expansion Eq.~\eqref{eq:EMP2}.
+In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains
+qualitatively correct at large bond lengths and the orbital degeneracy is avoided.
+Furthermore, this slow convergence can also be observed in molecules with a UHF ground state at the equilibrium
+geometry (\eg, \ce{CN^{-}}), suggesting a more fundamental link with spin-contamination 
+in the reference wave function.\cite{Nobes_1987}
+}
+
+\hugh{%
+Using the UHF framework allows} the singlet ground state wave function to mix with triplet wave functions, 
+leading to \hugh{spin contamination where the wave function is no longer an eigenfunction of the $\Hat{\cS}^2$ operator.}
+\hugh{The link between slow UMP convergence and this spin-contamination was first systematically investigated} 
+by Gill and \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
+\hugh{In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
+and identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
+low-lying double excitation.
+This erroneous description of the double excitation amplitude has the same origin as the spin-contamination in the reference
+UHF wave function, creating the first direct link between spin-contamination and slow UMP convergence.\cite{Gill_1988}
+Lepetit \etal\ later analysed the difference between the unrestricted MP and EN partitionings and argued
+that the slow UMP convergence for stretched molecules arises from (i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2})
+tends to a constant value instead of vanishing, and (ii) the slow convergence of contributions from the 
+singly-excited configurations that strongly couple to the doubly-excited configurations and first
+appear at fourth-order.\cite{Lepetit_1988}
+Drawing these ideas together, we believe that slow UMP convergence occurs because the single excitations must focus on removing
+spin-contamination from the reference wave function rather than fine-tuning the amplitudes of the higher 
+excitations that capture the correlation energy.
+}
+
+%When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
+%In other words, one would like a monotonic convergence of the MP series.
 Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
-Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behaviour of the perturbative coefficients are not uncommon.
-For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985,Lepetit_1988}).
-In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion.
-For example, in the case of the barrier to homolytic fission of \ce{He2^2+} in a minimal basis set, RMP5 is worse than RMP4 (see Fig.~2 in Ref.~\onlinecite{Gill_1986}).
-On the other hand, the UMP series is monotonically convergent after UMP5 but very slowly . 
-Thus, one cannot practically use it for systems where only the first terms are computationally accessible.
-
-When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
-Yet, the HF wave function is restricted to be a single Slater determinant.
-It is then inappropriate to model (even qualitatively) stretched systems. 
-Nevertheless, as explained in Sec.~\ref{sec:HF} and illustrated in Sec.~\ref{sec:HF_hubbard}, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see also the pedagogical example of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
-One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system. 
-However, as illustrated above, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
-The reasons behind this ambiguous behaviour are further explained below.
-
-In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
+%Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behaviour of the perturbative coefficients are not uncommon.
+%For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985,Lepetit_1988}). 
+%In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion.
+%For example, in the case of the barrier to homolytic fission of \ce{He2^2+} in a minimal basis set, RMP5 is worse than RMP4 (see Fig.~2 in Ref.~\onlinecite{Gill_1986}).
+%On the other hand, the UMP series is monotonically convergent after UMP5 but very slowly . 
+%Thus, one cannot practically use it for systems where only the first terms are computationally accessible.
+
+%When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
+%Yet, the HF wave function is restricted to be a single Slater determinant.
+%It is then inappropriate to model (even qualitatively) stretched systems. 
+%Nevertheless, as explained in Sec.~\ref{sec:HF} and illustrated in Sec.~\ref{sec:HF_hubbard}, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see also the pedagogical example of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
+%One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system. 
+%However, as illustrated above, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
+%The reasons behind this ambiguous behaviour are further explained below.
+
+%In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
 Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination for \ce{H2} in a minimal basis.
 \cite{Gill_1988}
-Handy and coworkers reported the same behaviour of the UMP series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
+%Handy and coworkers reported the same behaviour of the UMP series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
 \cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
 \cite{Lepetit_1988}
-They concluded that the slow convergence of the UMP series is due to i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2}) tends to a constant instead of vanishing, and ii) the lack of the singly-excited configurations (which only appears at fourth order) that strongly couple to the doubly-excited configurations.
-We believe that this divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting the structure of the reference orbitals rather than capturing the correlation energy.
-
-Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
-Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
-They highlighted that \cite{Cremer_1996}
-\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
-They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
-On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
-This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
-As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+%They concluded that the slow convergence of the UMP series is due to i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2}) tends to a constant instead of vanishing, and ii) the lack of the singly-excited configurations (which only appears at fourth order) that strongly couple to the doubly-excited configurations.
+%We believe that this divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting the structure of the reference orbitals rather than capturing the correlation energy.
+
+%Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+%Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
+%They highlighted that \cite{Cremer_1996}
+%\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+%Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+%They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
+%On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
+%This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
+%As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+%Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
 \cite{Cremer_1996}
-The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+%The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+%Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 
 %==========================================%
-\subsection{M{\o}ller-Plesset Convergence in the Hubbard Dimer}
+\subsection{Effect of Spin-Contamination in the Hubbard Dimer}
 %==========================================%
-
-To illustrate the behaviour of the RMP and UMP series, we can again consider the Hubbard dimer.
-Using the ground-state RHF reference orbitals leads to the RMP Hamiltonian
-\begin{widetext}
-\begin{equation}
-\label{eq:H_RMP}
-\bH_\text{RMP}\qty(\lambda) = 
-	\begin{pmatrix}
-		-2t + U - \lambda U/2	&	0					&	0					&	\lambda U/2	\\
-		0						&	U - \lambda U/2 	&	\lambda U/2			&	0	\\
-		0						&	\lambda U/2			&	U - \lambda U/2 	&	0	\\
-		\lambda U/2 			&	0 					&	0					&	2t + U - \lambda U/2	\\
-	\end{pmatrix},
-\end{equation}
-\end{widetext}
-which yields the ground-state energy 
-\begin{equation}
-	\label{eq:E0MP}
-	E_{-}(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}.
-\end{equation}
-From this expression, the EPs can be identified as $\lep = \pm \i 4t / U$,
-giving the radius of convergence
-\begin{equation}
-    \rc = \abs{\frac{4t}{U}}.
-\end{equation}
-These EPs are identical than the exact EPs discussed in Sec.~\ref{sec:example}.
-The Taylor expansion of the RMP energy can then be evaluated to obtain the $k$th-order MP correction
-\begin{equation}
-	E_\text{RMP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2).
-\end{equation}
-%with 
-%\begin{equation}
-%	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
-%\end{equation}
-
-The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
-of perturbation in Fig.~\ref{subfig:RMP_cvg}.
-In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
-The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
-\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
-by the vertical cylinder of unit radius.
-For the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
-outside this cylinder.
-In both cases, the EP connects the ground state with the doubly-excited state, and thus the convergence behaviour
-for the two states using the ground state RHF orbitals is identical.
-The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
-from the single excitations.\cite{Lepetit_1988}
 
@@
 
-The behaviour of the UMP series is more subtle than the RMP series as spin-contamination in the wave function
-must be considered, introducing additional coupling between electronic states.
-Using the ground-state UHF reference orbitals in the Hubbard dimer yields the UMP Hamiltonian
+\hugh{The behaviour of the RMP and UMP series observed in \ce{H2} can again be analytically illustrated by considering
+the Hubbard dimer with a complex-valued perturbation strength.
+In this system, the stretching of a chemical bond is directly mirrored by an increase in the on-site repulsion $U$.
+}
+Using the ground-state RHF reference orbitals leads to the \hugh{parametrised} RMP Hamiltonian
+\begin{widetext}
+\begin{equation}
+\label{eq:H_RMP}
+\bH_\text{RMP}\qty(\lambda) = 
+	\begin{pmatrix}
+		-2t + U - \lambda U/2	&	0					&	0					&	\lambda U/2	\\
+		0						&	U - \lambda U/2 	&	\lambda U/2			&	0	\\
+		0						&	\lambda U/2			&	U - \lambda U/2 	&	0	\\
+		\lambda U/2 			&	0 					&	0					&	2t + U - \lambda U/2	\\
+	\end{pmatrix},
+\end{equation}
+\end{widetext}
+which yields the ground-state energy 
+\begin{equation}
+	\label{eq:E0MP}
+	E_{-}(\lambda) = U - \frac{\lambda U}{2} - \frac{1}{2} \sqrt{(4t)^2 + \lambda ^2 U^2}.
+\end{equation}
+From this expression, the EPs can be identified as $\lep = \pm \i 4t / U$,
+giving the radius of convergence
+\begin{equation}
+    \rc = \abs{\frac{4t}{U}}.
+\end{equation}
+Remarkably, these EPs are identical to the exact EPs discussed in Sec.~\ref{sec:example}.
+The Taylor expansion of the RMP energy can then be evaluated to obtain the $k$th-order MP correction
+\begin{equation}
+	E_\text{RMP}^{(k)} = U \delta_{0,k} - \frac{1}{2} \frac{U^k}{(4t)^{k-1}} \mqty( 1/2 \\ k/2).
+\end{equation}
+%with 
+%\begin{equation}
+%	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
+%\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% RADIUS OF CONVERGENCE PLOTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+	\includegraphics[width=\linewidth]{RadConv}
+	\caption{
+	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
+    series as functions of the ratio $U/t$.
+	\label{fig:RadConv}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
+of perturbation in Fig.~\ref{subfig:RMP_cvg}.
+In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
+The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
+\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
+by the vertical cylinder of unit radius.
+For the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
+outside this cylinder.
+In both cases, the EP connects the ground state with the doubly-excited state, and thus the convergence behaviour
+for the two states using the ground-state RHF orbitals is identical.
+% HGAB: This cannot be relevant here as the single-excitations don't couple to either ground or excited state.
+%The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
+%%from the single excitations.\cite{Lepetit_1988}
+
+The behaviour of the UMP series is more subtle than the RMP series as the spin-contamination in the wave function
+\hugh{introduces additional coupling between the singly- and doubly-excited configurations.}
+Using the ground-state UHF reference orbitals in the Hubbard dimer yields the \hugh{parametrised} UMP Hamiltonian
 \begin{widetext}
@@
 However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
-the corresponding UMP series will become increasingly slow.
+the corresponding UMP series becomes increasingly slow.
 Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
-of $U/t$, reaching the limit value of $1/2$ for $U/t \rightarrow \infty$, and excited-state UMP series will always diverge.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% RADIUS OF CONVERGENCE PLOTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=\linewidth]{RadConv}
-	\caption{
-	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
-    series as functions of the ratio $U/t$.
-	\label{fig:RadConv}}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+of $U/t$, reaching the limiting value of $1/2$ for $U/t \rightarrow \infty$, and thus the 
+excited-state UMP series will always diverge.
 
@@
 %==========================================%
-\subsection{Further insights from a two-state model}
+\subsection{Classifying Types of Convergence Behaviour} % Further insights from a two-state model}
 %==========================================%
+
+% CREMER AND HE
+\hugh{Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
+They highlighted that \cite{Cremer_1996}
+\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
+On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
+This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
+As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+\cite{Cremer_1996}
+The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.}
 

### 2020-11-24 Manuscript/EPAWTFT.tex
corrected Moller-Plesset em-dash throughout

@@
 After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree-Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
-In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller-Plesset perturbation theory and its apparent link with quantum phase transitions.
+In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory and its apparent link with quantum phase transitions.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller-Plesset Perturbation Theory in the Complex Plane}
+\section{M{\o}ller--Plesset Perturbation Theory in the Complex Plane}
 \label{sec:MP}
@@
 %=====================================================%
-\subsection{Early Investigations into M{\o}ller-Plesset Convergence} % in Molecular Systems}
+\subsection{Early Investigations into M{\o}ller--Plesset Convergence} % in Molecular Systems}
 %=====================================================%

### 2020-11-24 Manuscript/EPAWTFT.tex
changes to the UMP hubbard dimer convergence

@@
 \newcommand{\eg}{\latin{e.g.}}
-\newcommand{\etal}{\latin{et.\ al}}
+\newcommand{\etal}{\textit{et.\ al}}
 
@@
 or erratic convergence, with the UMP series showing particularly slow convergence.\cite{Laidig_1985,Knowles_1985,Handy_1985}
-For example, RMP5 is worse than RMP4 for predicting the the homolytic barrier fission of \ce{He2^2+} using a minimal basis set, 
+For example, RMP5 is worse than RMP4 for predicting the homolytic barrier fission of \ce{He2^2+} using a minimal basis set, 
 while the UMP series monotonically converges but becomes increasingly slow beyond UMP5.\cite{Gill_1986}
@@
 \hugh{The link between slow UMP convergence and this spin-contamination was first systematically investigated} 
-by Gill and \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
+by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
 \hugh{In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
@@
 UHF wave function, creating the first direct link between spin-contamination and slow UMP convergence.\cite{Gill_1988}
-Lepetit \etal\ later analysed the difference between the unrestricted MP and EN partitionings and argued
-that the slow UMP convergence for stretched molecules arises from (i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2})
+Lepetit \etal\ later analysed the difference between perturbation convergence using the unrestricted MP 
+and EN partitionings.\cite{Lepetit_1988}
+They argued that the slow UMP convergence for stretched molecules arises from 
+(i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2})
 tends to a constant value instead of vanishing, and (ii) the slow convergence of contributions from the 
@@
 Drawing these ideas together, we believe that slow UMP convergence occurs because the single excitations must focus on removing
-spin-contamination from the reference wave function rather than fine-tuning the amplitudes of the higher 
+spin-contamination from the reference wave function, limiting their ability to fine-tune the amplitudes of the higher 
 excitations that capture the correlation energy.
@@
 
-\hugh{The behaviour of the RMP and UMP series observed in \ce{H2} can again be analytically illustrated by considering
-the Hubbard dimer with a complex-valued perturbation strength.
-In this system, the stretching of a chemical bond is directly mirrored by an increase in the on-site repulsion $U$.
+\hugh{The behaviour of the RMP and UMP series observed in \ce{H2} can also be illustrated by considering
+the analytic Hubbard dimer with a complex-valued perturbation strength.
+In this system, the stretching of a chemical bond is directly mirrored by an increase in the electron correlation $U/t$.
 }
@@
 in Fig.~\ref{fig:RadConv}.
-These numerical values reveal that the UMP ground state series has $\rc > 1$ for all $U/t$ and must always converge.
+These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and must always converge.
 However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
@@
 At $U = 3t$, the RMP series is convergent, while RMP becomes divergent for $U=7t$.
-The UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
+The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
 for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
@@
 % EFFECT OF SYMMETRY BREAKING
-Allowing the UHF orbitals to break the molecular symmetry introduces new couplings between electronic states
-and fundamentally changes the structure of the EPs in the complex $\lambda$-plane.
+As the UHF orbitals break the molecular symmetry, new coupling terms emerge between the electronic states that
+cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
 For example, while the RMP energy shows only one EP between the ground state and 
 the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
-first-excited \titou{open-shell singlet?}, and the other connecting the \titou{open-shell singlet?} to the 
+singly-excited open-shell singlet, and the other connecting this single excitation to the 
 doubly-excited second excitation (Fig.~\ref{fig:UMP}).
-While this symmetry-breaking makes the ground-state UMP series convergent by moving the corresponding
-EP outside the unit cylinder, this process also moves the excited-state EP within the unit cylinder
-and thus causes a deterioration in the convergence of the excited-state UMP series.
-Furthermore, since the UHF ground-state energy is already an improved approximation of the exact energy, the ground-state
-UMP energy surface is relatively flat and the majority of the UMP expansion is concerned with removing 
-spin-contamination from the wave function.
+\hugh{%
+This new ground-state EP always appears outside the unit cylinder and guarantees convergence of the ground-state energy.
+However, the excited-state EP is moved within} the unit cylinder and causes the 
+convergence of the excited-state UMP series to deteriorate.
+\hugh{Our interpretation of this effect is that the symmetry-broken orbital optimisation has redistributed the strong 
+coupling between the ground- and doubly-excited states into weaker couplings between all states, and has thus
+sacrificed convergence of the excited-state series so that the chance of ground-state convergence can be maximised.}
+
+Since the UHF ground state already provides a good approximation to the exact energy, the ground-state sheet of
+the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
+\hugh{The slow convergence observed in \ce{H2} can then be seen as this EP moves ever closer to one at larger $U/t$ values.}
+Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
+function \hugh{rather than improving the energy.
+It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
+of highly-excited determinants,\cite{Lowdin_1955c} and thus it is not surprising that this process proceeds 
+very slowly as the perturbation order is increased.
+}
 

### 2020-11-24 Manuscript/EPAWTFT.tex
Updated UMP convergence figure

@@
 the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\hugh{The slow convergence observed in \ce{H2} can then be seen as this EP moves ever closer to one at larger $U/t$ values.}
+\hugh{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+moves closer to one at larger $U/t$ values.}
 Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 

### 2020-11-24 Manuscript/EPAWTFT.tex
Added paragraph on spin-projected MP convergence.

@@
 
+\raggedbottom
 \tableofcontents
@@
 
+% SPIN-PROJECTION SCHEMES
+\hugh{%
+A number of spin-projected extensions have been derived to reduce spin-contamination in the wave function
+and overcome the slow UMP convergence.
+Early versions of these theories, introduced by Schlegel\cite{Schlegel_1986, Schlegel_1988} or 
+Knowles and Handy\cite{Knowles_1988a,Knowles_1988b}, exploited the ``projection-after-variation'' philosophy,
+where the spin-projection is applied directly to the UMP expansion.
+These methods succeeded in accelerating the convergence of the projected MP series and were 
+considered as highly effective methods for capturing the electron correlation at low computational cost.\cite{Knowles_1988b}
+However, the use of projection-after-variation leads to gradient discontinuities in the vicinity of the UHF symmetry-breaking point,
+and can result in spurious minima along a molecular binding curve.\cite{Schlegel_1986,Knowles_1988a}
+More recent formulations of spin-projected perturbations theories have considered the  
+``variation-after-projection'' framework using alternative definitions of the reference 
+Hamiltonian.\cite{Tsuchimochi_2014,Tsuchimochi_2019}
+These methods yield more accurate spin-pure energies without 
+gradient discontinuities or spurious minima.
+}
+
 %When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
@@
 
-The behaviour of the UMP series is more subtle than the RMP series as the spin-contamination in the wave function
-\hugh{introduces additional coupling between the singly- and doubly-excited configurations.}
-Using the ground-state UHF reference orbitals in the Hubbard dimer yields the \hugh{parametrised} UMP Hamiltonian
-\begin{widetext}
-\begin{equation}
-\label{eq:H_UMP}
-\bH_\text{UMP}\qty(\lambda) = 
-	\begin{pmatrix}
-		-2t^2 \lambda/U	&	0									&	0									&	2t^2 \lambda/U		\\
-		0				&	U - 2t^2 \lambda/U 					&	2t^2\lambda/U						&	2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		0				&	2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
-		2t^2 \lambda/U	&	2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
-	\end{pmatrix}.
-\end{equation}
-\end{widetext}
-While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
-Instead, the radius of convergence of the UMP series can be obtained numerically as a function of $U/t$, as shown
-in Fig.~\ref{fig:RadConv}.
-These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and must always converge.
-However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
-the corresponding UMP series becomes increasingly slow.
-Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
-of $U/t$, reaching the limiting value of $1/2$ for $U/t \rightarrow \infty$, and thus the 
-excited-state UMP series will always diverge.
-
-% DISCUSSION OF UMP RIEMANN SURFACES
-The convergence behaviour can be further elucidated by considering the full structure of the UMP energies 
-in the complex $\lambda$-plane.
-These Riemann surfaces are illustrated for $U = 3t$ and $7t$ alongside the perturbation terms at each order
-in Fig.~\ref{subfig:UMP_cvg}.
-At $U = 3t$, the RMP series is convergent, while RMP becomes divergent for $U=7t$.
-The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
-for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
-
-% EFFECT OF SYMMETRY BREAKING
-As the UHF orbitals break the molecular symmetry, new coupling terms emerge between the electronic states that
-cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
-For example, while the RMP energy shows only one EP between the ground state and 
-the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
-singly-excited open-shell singlet, and the other connecting this single excitation to the 
-doubly-excited second excitation (Fig.~\ref{fig:UMP}).
-\hugh{%
-This new ground-state EP always appears outside the unit cylinder and guarantees convergence of the ground-state energy.
-However, the excited-state EP is moved within} the unit cylinder and causes the 
-convergence of the excited-state UMP series to deteriorate.
-\hugh{Our interpretation of this effect is that the symmetry-broken orbital optimisation has redistributed the strong 
-coupling between the ground- and doubly-excited states into weaker couplings between all states, and has thus
-sacrificed convergence of the excited-state series so that the chance of ground-state convergence can be maximised.}
-
-Since the UHF ground state already provides a good approximation to the exact energy, the ground-state sheet of
-the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\hugh{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
-moves closer to one at larger $U/t$ values.}
-Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
-function \hugh{rather than improving the energy.
-It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
-of highly-excited determinants,\cite{Lowdin_1955c} and thus it is not surprising that this process proceeds 
-very slowly as the perturbation order is increased.
-}
-
-%The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
-%Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
-%This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
-%For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
-%Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
-%For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
-%We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
-%An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
-%On the other hand, there is an EP on the excited energy surface that is well within the radius of convergence.
-%We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
-%at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
-%In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
-%the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
-
 %%% FIG 3 %%%
@@
 	The Riemann surfaces associated with the exact energies of the UMP Hamiltonian \eqref{eq:H_UMP} are also represented for these two values of $U/t$ as functions of $\lambda$.
-\titou{Please Hugh, modify central figure.}
 	\label{fig:UMP}}
 \end{figure*}
+
+The behaviour of the UMP series is more subtle than the RMP series as the spin-contamination in the wave function
+\hugh{introduces additional coupling between the singly- and doubly-excited configurations.}
+Using the ground-state UHF reference orbitals in the Hubbard dimer yields the \hugh{parametrised} UMP Hamiltonian
+\begin{widetext}
+\begin{equation}
+\label{eq:H_UMP}
+\bH_\text{UMP}\qty(\lambda) = 
+	\begin{pmatrix}
+		-2t^2 \lambda/U	&	0									&	0									&	2t^2 \lambda/U		\\
+		0				&	U - 2t^2 \lambda/U 					&	2t^2\lambda/U						&	2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		0				&	2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
+		2t^2 \lambda/U	&	2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
+	\end{pmatrix}.
+\end{equation}
+\end{widetext}
+While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
+Instead, the radius of convergence of the UMP series can be obtained numerically as a function of $U/t$, as shown
+in Fig.~\ref{fig:RadConv}.
+These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and must always converge.
+However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
+the corresponding UMP series becomes increasingly slow.
+Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
+of $U/t$, reaching the limiting value of $1/2$ for $U/t \rightarrow \infty$, and thus the 
+excited-state UMP series will always diverge.
+
+% DISCUSSION OF UMP RIEMANN SURFACES
+The convergence behaviour can be further elucidated by considering the full structure of the UMP energies 
+in the complex $\lambda$-plane.
+These Riemann surfaces are illustrated for $U = 3t$ and $7t$ alongside the perturbation terms at each order
+in Fig.~\ref{subfig:UMP_cvg}.
+At $U = 3t$, the RMP series is convergent, while RMP becomes divergent for $U=7t$.
+The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
+for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
+
+% EFFECT OF SYMMETRY BREAKING
+As the UHF orbitals break the molecular symmetry, new coupling terms emerge between the electronic states that
+cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
+For example, while the RMP energy shows only one EP between the ground state and 
+the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
+singly-excited open-shell singlet, and the other connecting this single excitation to the 
+doubly-excited second excitation (Fig.~\ref{fig:UMP}).
+\hugh{%
+This new ground-state EP always appears outside the unit cylinder and guarantees convergence of the ground-state energy.
+However, the excited-state EP is moved within} the unit cylinder and causes the 
+convergence of the excited-state UMP series to deteriorate.
+\hugh{Our interpretation of this effect is that the symmetry-broken orbital optimisation has redistributed the strong 
+coupling between the ground- and doubly-excited states into weaker couplings between all states, and has thus
+sacrificed convergence of the excited-state series so that the ground-state convergence can be maximised.}
+
+Since the UHF ground state already provides a good approximation to the exact energy, the ground-state sheet of
+the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
+\hugh{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+moves closer to one at larger $U/t$ values.}
+Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
+function \hugh{rather than improving the energy.
+It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
+of highly-excited determinants,\cite{Lowdin_1955c} and thus it is not surprising that this process proceeds 
+very slowly as the perturbation order is increased.
+}
+
+%The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
+%Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
+%This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
+%For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
+%Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
+%For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
+%We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
+%An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
+%On the other hand, there is an EP on the excited energy surface that is well within the radius of convergence.
+%We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
+%at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
+%In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
+%the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
 

### 2020-11-24 Manuscript/EPAWTFT.tex
reviewing hugh stuff, good as usual

@@
 \newcommand{\eg}{\latin{e.g.}}
-\newcommand{\etal}{\textit{et.\ al}}
+\newcommand{\etal}{\textit{et al.}}
 
@@
 % GENERAL DESIRE FOR WELL-BEHAVED CONVERGENCE AND LOW-ORDER TERMS
-\hugh{%
  Among the most desirable properties of any electronic structure technique is the existence of 
@@
 to obtain high-accuracy results using only the lowest order terms.
-}
 
 % INITIAL POSITIVITY AROUND THE CONVERGENCE PROPERTIES AND EARLY WORK SCOPE
-\hugh{%
 MP theory was first introduced to quantum chemistry through the pioneering
@@
 while the UMP series monotonically converges but becomes increasingly slow beyond UMP5.\cite{Gill_1986}
-The first examples of divergent MP series were observed in the heavy-atom \ce{N2} and \ce{F2} 
+The first examples of divergent MP series were observed in the \ce{N2} and \ce{F2} 
 diatomics, where low-order RMP and UMP expansions give qualitatively wrong binding curves.\cite{Laidig_1987}
-}
 
 % SLOW UMP CONVERGENCE AND SPIN CONTAMINATION
-\hugh{%
 The divergence of RMP expansions for stretched bonds can be easily understood from two perspectives.\cite{Gill_1988a}
@@
 Furthermore, this slow convergence can also be observed in molecules with a UHF ground state at the equilibrium
-geometry (\eg, \ce{CN^{-}}), suggesting a more fundamental link with spin-contamination 
+geometry (\eg, \ce{CN-}), suggesting a more fundamental link with spin-contamination 
 in the reference wave function.\cite{Nobes_1987}
-}
-
-\hugh{%
-Using the UHF framework allows} the singlet ground state wave function to mix with triplet wave functions, 
-leading to \hugh{spin contamination where the wave function is no longer an eigenfunction of the $\Hat{\cS}^2$ operator.}
-\hugh{The link between slow UMP convergence and this spin-contamination was first systematically investigated} 
+
+Using the UHF framework allows the singlet ground state wave function to mix with triplet wave functions, 
+leading to spin contamination where the wave function is no longer an eigenfunction of the $\Hat{\cS}^2$ operator.
+The link between slow UMP convergence and this spin-contamination was first systematically investigated
 by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
-\hugh{In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
+In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
 and identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
@@
 excitations that capture the correlation energy.
-}
 
 % SPIN-PROJECTION SCHEMES
-\hugh{%
 A number of spin-projected extensions have been derived to reduce spin-contamination in the wave function
 and overcome the slow UMP convergence.
-Early versions of these theories, introduced by Schlegel\cite{Schlegel_1986, Schlegel_1988} or 
-Knowles and Handy\cite{Knowles_1988a,Knowles_1988b}, exploited the ``projection-after-variation'' philosophy,
+Early versions of these theories, introduced by Schlegel \cite{Schlegel_1986, Schlegel_1988} or 
+Knowles and Handy,\cite{Knowles_1988a,Knowles_1988b} exploited the ``projection-after-variation'' philosophy,
 where the spin-projection is applied directly to the UMP expansion.
@@
 gradient discontinuities or spurious minima.
-}
 
@@
 
-\hugh{The behaviour of the RMP and UMP series observed in \ce{H2} can also be illustrated by considering
+The behaviour of the RMP and UMP series observed in \ce{H2} can also be illustrated by considering
 the analytic Hubbard dimer with a complex-valued perturbation strength.
 In this system, the stretching of a chemical bond is directly mirrored by an increase in the electron correlation $U/t$.
-}
-Using the ground-state RHF reference orbitals leads to the \hugh{parametrised} RMP Hamiltonian
+Using the ground-state RHF reference orbitals leads to the parametrised RMP Hamiltonian
 \begin{widetext}
@@
 The behaviour of the UMP series is more subtle than the RMP series as the spin-contamination in the wave function
-\hugh{introduces additional coupling between the singly- and doubly-excited configurations.}
-Using the ground-state UHF reference orbitals in the Hubbard dimer yields the \hugh{parametrised} UMP Hamiltonian
+introduces additional coupling between the singly- and doubly-excited configurations.
+Using the ground-state UHF reference orbitals in the Hubbard dimer yields the parametrised UMP Hamiltonian
 \begin{widetext}
@@
 doubly-excited second excitation (Fig.~\ref{fig:UMP}).
-\hugh{%
 This new ground-state EP always appears outside the unit cylinder and guarantees convergence of the ground-state energy.
-However, the excited-state EP is moved within} the unit cylinder and causes the 
+However, the excited-state EP is moved within the unit cylinder and causes the 
 convergence of the excited-state UMP series to deteriorate.
-\hugh{Our interpretation of this effect is that the symmetry-broken orbital optimisation has redistributed the strong 
+Our interpretation of this effect is that the symmetry-broken orbital optimisation has redistributed the strong 
 coupling between the ground- and doubly-excited states into weaker couplings between all states, and has thus
-sacrificed convergence of the excited-state series so that the ground-state convergence can be maximised.}
+sacrificed convergence of the excited-state series so that the ground-state convergence can be maximised.
 
@@
 the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\hugh{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+\titou{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
 moves closer to one at larger $U/t$ values.}
 Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
-function \hugh{rather than improving the energy.
+function rather than improving the energy.
 It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
@@
 very slowly as the perturbation order is increased.
-}
 
@@
 % CREMER AND HE
-\hugh{Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
 Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
@@
 The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.}
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 

### 2020-11-24 Manuscript/EPAWTFT.tex
starting working on pade and stuff

@@
 %==========================================%
+According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}.
+A $[d_A/d_B]$ Pad\'e approximant is defined as
+\begin{equation}
+	\label{eq:PadeApp}
+	E(\lambda) = \frac{A(\lambda)}{B(\lambda)} = \frac{\sum_{k=0}^{d_A} a_k \lambda^k}{\sum_{k=0}^{d_B} b_k \lambda^k}
+\end{equation}
+with $b_0 = 1$.
+Pad\'e approximants are nice and they can model poles, but they cannot model functions with square-root branch points, and that sucks.
+
+%==========================================%
+\subsection{Quadratic approximant}
+%==========================================%
+In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalized version of the square-root singularity expression
+\begin{equation}
+	\label{eq:QuadApp}
+	E(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ]
+\end{equation}
+where 
+\begin{align}
+	\label{eq:PQR}
+	P(\lambda) & = \sum_{k=0}^{d_P} p_k \lambda^k,
+	&
+	Q(\lambda) & = \sum_{k=0}^{d_Q} q_k \lambda^k, 
+	&
+	R(\lambda) & = \sum_{k=0}^{d_R} r_k \lambda^k 
+\end{align}
+are polynomials, such that $d_P + d_Q + d_R = n - 1$ where $n$ is the highest-order series coefficient known from the Taylor expansion of $E(\lambda)$.
+Recasting Eq.~\eqref{eq:QuadApp} as a second-order expression in $E(\lambda)$, \ie,
+\begin{equation}
+	Q(\lambda) E^2(\lambda) - P(\lambda) E(\lambda) + R(\lambda) \sim \order*{\lambda^{n+1}}
+\end{equation}
+and substituting $E(\lambda$) by its $n$th-order expansion and the polynomials by their respective expressions \eqref{eq:PQR} yields $n+1$ linear equations for the coefficients $p_k$, $q_k$, and $r_k$ (where we are free to assume that $q_0 = 1$).
+A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $\max(2d_p,d_q+d_r)$ branch points.
+The diagonal sequence of quadratic approximant, \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, is of particular interest.
+
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximation, but its $[1/0,1]$ version already model perfectly the RMP energy function by predicting a single pair of EPs at $\lambda_{EP} = \pm i 4t/U$.
+This is expected knowing the form of the RMP energy [see Eq.~\eqref{eq:E0MP}] which perfectly suits the purpose of quadratic approximants.
+
+We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case.
+However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~??.
 

### 2020-11-25 Manuscript/EPAWTFT.tex
saving work on Pade

@@
 Lepetit \etal\ later analysed the difference between perturbation convergence using the unrestricted MP 
-and EN partitionings.\cite{Lepetit_1988}
+and EN partitionings. \cite{Lepetit_1988}
 They argued that the slow UMP convergence for stretched molecules arises from 
@@
 
+The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
+
 %==========================================%
@@
 According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}.
-A $[d_A/d_B]$ Pad\'e approximant is defined as
+A $[d_A/d_B]$ Pad\'e approximant is defined as \cite{Pade}
 \begin{equation}
 	\label{eq:PadeApp}
-	E(\lambda) = \frac{A(\lambda)}{B(\lambda)} = \frac{\sum_{k=0}^{d_A} a_k \lambda^k}{\sum_{k=0}^{d_B} b_k \lambda^k}
-\end{equation}
-with $b_0 = 1$.
-Pad\'e approximants are nice and they can model poles, but they cannot model functions with square-root branch points, and that sucks.
+	E_{[d_A/d_B]}(\lambda) = \frac{A(\lambda)}{B(\lambda)} = \frac{\sum_{k=0}^{d_A} a_k \lambda^k}{\sum_{k=0}^{d_B} b_k \lambda^k}
+\end{equation}
+(with $b_0 = 1$), where the coefficients of the polynomials are determined by collecting terms according to power of $\lambda$.
+Pad\'e approximants are nice and they can model poles (the poles of a $[d_A/d_B]$ Pad\'e approximant appears at the roots of the polynomial $B(\lambda)$), but they cannot model functions with square-root branch points, and that sucks because it is not consistent with the singularity structure of a typical perturbative treatment.
 
@@
 
-Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning.
-\cite{Mihalka_2017a}
+Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning \cite{Mihalka_2017a} (see also Ref.~\onlinecite{Surjan_2000}).
 Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.

### 2020-11-25 Manuscript/EPAWTFT.tex
saving work on Pade

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Exploiting complex analysis}
+\section{Resummation techniques}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As frequently claimed by Carl Bender, the most stupid thing that one can do with a series is to sum it.
+Nonetheless, quantum chemists are basically doing exactly this on a daily basis.
 
@@
 %==========================================%
-According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}.
-A $[d_A/d_B]$ Pad\'e approximant is defined as \cite{Pade}
+According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}. \cite{BakerBook}
+A $[d_A/d_B]$ Pad\'e approximant is defined as \cite{Pade_1892}
 \begin{equation}
@@
 \end{equation}
-(with $b_0 = 1$), where the coefficients of the polynomials are determined by collecting terms according to power of $\lambda$.
-Pad\'e approximants are nice and they can model poles (the poles of a $[d_A/d_B]$ Pad\'e approximant appears at the roots of the polynomial $B(\lambda)$), but they cannot model functions with square-root branch points, and that sucks because it is not consistent with the singularity structure of a typical perturbative treatment.
+(with $b_0 = 1$), where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms according to power of $\lambda$.
+Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Gluzman_2020} as they can model poles [the poles of a Pad\'e approximant appears at the roots of the polynomial $B(\lambda)$].
+However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
 
@@
 %==========================================%
-In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalized version of the square-root singularity expression
+In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalized version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
 \begin{equation}
@@
 \end{align}
-are polynomials, such that $d_P + d_Q + d_R = n - 1$ where $n$ is the highest-order series coefficient known from the Taylor expansion of $E(\lambda)$.
+are polynomials, such that $d_P + d_Q + d_R = n - 1$, where $n$ is the highest-order series coefficient known from the Taylor expansion of $E(\lambda)$.
 Recasting Eq.~\eqref{eq:QuadApp} as a second-order expression in $E(\lambda)$, \ie,

### 2020-11-25 Manuscript/EPAWTFT.tex
saving work on Pade

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Resummation techniques}
+\section{Resummation Methods}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-As frequently claimed by Carl Bender, the most stupid thing that one can do with a series is to sum it.
+As frequently claimed by Carl Bender, \textit{``the most stupid thing that one can do with a series is to sum it.''}
 Nonetheless, quantum chemists are basically doing exactly this on a daily basis.
-
-The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
+Here, we discuss tools that can be used to sum divergent series.
+Resummation techniques is a vast field of research and, below, we provide details for a non-exhaustive list of these techniques.
+We refer the interested reader to more specialised reviews for additional information. \cite{Goodson_2011,Goodson_2019}
 
@@
 %==========================================%
-According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}. \cite{BakerBook}
-A $[d_A/d_B]$ Pad\'e approximant is defined as \cite{Pade_1892}
+The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
+This description can be significantly improved thanks to Pad\'e approximant. \cite{Pade_1892,BakerBook}
+
+According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}. 
+A $[d_A/d_B]$ Pad\'e approximant is defined as 
 \begin{equation}
@@
 (with $b_0 = 1$), where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms according to power of $\lambda$.
-Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Gluzman_2020} as they can model poles [the poles of a Pad\'e approximant appears at the roots of the polynomial $B(\lambda)$].
+Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Gluzman_2020} as they can model poles, which appears at the roots of the polynomial $B(\lambda)$. 
 However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
@@
 and substituting $E(\lambda$) by its $n$th-order expansion and the polynomials by their respective expressions \eqref{eq:PQR} yields $n+1$ linear equations for the coefficients $p_k$, $q_k$, and $r_k$ (where we are free to assume that $q_0 = 1$).
-A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $\max(2d_p,d_q+d_r)$ branch points.
+A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $\max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$.
 The diagonal sequence of quadratic approximant, \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, is of particular interest.
-
-For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximation, but its $[1/0,1]$ version already model perfectly the RMP energy function by predicting a single pair of EPs at $\lambda_{EP} = \pm i 4t/U$.
+Note that, by construction, a quadratic approximant has only two branches which hampers the faithful description of more complicated singularity structures.
+
+As shown in Ref.~\onlinecite{Goodson_2000}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}
+
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximation, but its $[1/0,1]$ version already model perfectly the RMP energy function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
 This is expected knowing the form of the RMP energy [see Eq.~\eqref{eq:E0MP}] which perfectly suits the purpose of quadratic approximants.
 
-We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case.
+We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function which contains three branches.
 However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~??.

### 2020-11-25 Manuscript/EPAWTFT.tex
new fig for Pade

@@
 However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
+Figure \ref{fig:PadeRMP} illustrates the improvement brought by Pad\'e approximants as compared to the usual Taylor expansion in the case of the RMP series of the Hubbard dimer for $U/t = 4.5$.
+
+%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \includegraphics[width=\linewidth]{PadeRMP}
+    \caption{\label{fig:PadeRMP}
+    RMP ground-state energy as a function of $\lambda$ obtained with various approximations for $U/t = 4.5$.}
+\end{figure}
+%%%%%%%%%%%%%%%%%
 

### 2020-11-25 Manuscript/EPAWTFT.tex
Discussion on Cremer

--- 2020-11-25 Manuscript/EPAWTFT.tex
@@
 \newcommand{\lep}{\lambda_{\text{EP}}}
+
+% Some energies
+\newcommand{\Emp}{E_{\text{MP}}}
 
@@
 %==========================================%
-\subsection{Effect of Spin-Contamination in the Hubbard Dimer}
+\subsection{Spin-Contamination in the Hubbard Dimer}
 %==========================================%
@@
 the analytic Hubbard dimer with a complex-valued perturbation strength.
-In this system, the stretching of a chemical bond is directly mirrored by an increase in the electron correlation $U/t$.
+In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the electron correlation $U/t$.
 Using the ground-state RHF reference orbitals leads to the parametrised RMP Hamiltonian
@@
 \end{widetext}
-While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
+While a closed-form expression for the ground-state energy exists, it is cumbersome and we eschew reporting it.
 Instead, the radius of convergence of the UMP series can be obtained numerically as a function of $U/t$, as shown
 in Fig.~\ref{fig:RadConv}.
-These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and must always converge.
+These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and always converges.
 However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
@@
 The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
-for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
+for larger $U/t$ as the radius of convergence becomes increasingly close to one (Fig.~\ref{fig:RadConv}).
 
@@
 the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\titou{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
-moves closer to one at larger $U/t$ values.}
+\hugh{The slow convergence observed in stretched \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+moves increasingly close to the unit cylinder at large $U/t$ and $\rc$ approaches one (from above).}
 Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
@@
 % CREMER AND HE
-Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
-Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
-They highlighted that \cite{Cremer_1996}
-\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
-They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
-On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
-This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
-As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+\hugh{As computational implementations of higher-order MP terms improved, the systematic investigation 
+of convergence behaviour in a broader class of molecules became possible.}
+Cremer and He \hugh{introduced an efficient MP6 approach and used it to analyse the RMP convergence of}
+29 atomic and molecular systems with respect to the FCI energy.\cite{Cremer_1996}
+They established two general classes: ``class A'' systems that exhibit monotonic convergence; 
+and ``class B'' systems for which convergence is erratic after initial oscillations. 
+%Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
+\hugh{By analysing the different cluster contributions to the MP energy terms, they proposed that
+class A systems generally include well-separated and weakly correlated electron pairs, while class B systems
+are characterised by dense electron clustering in one or more spatial regions.}\cite{Cremer_1996}
+%\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+%Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+In class A systems, they showed that the majority of the correlation energy arises from pair correlation, 
+with little contribution from triple excitations.
+On the other hand, triple excitations have an important contribution in class B systems, including providing
+orbital relaxation, and these contributions lead to oscillations of the total correlation energy.
+%This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
+
+\hugh{%
+Using these classifications, Cremer and He then introduced simple extrapolation formulas for estimating the 
+exact correlation energy $\Delta E$ using terms up to MP6\cite{Cremer_1996}
+\begin{align}
+\Delta E_{\text{A}}
+    &= \Emp^{(2)} + \Emp^{(3)} + \Emp^{(4)}
+     + \frac{\Emp^{(5)}}{1 - (\Emp^{(6)} / \Emp^{(5)})}, 
+     \\[5pt]
+\Delta E_{\text{B}} 
+    &= \Emp^{(2)} + \Emp^{(3)} + \qty(\Emp^{(4)} + \Emp^{(5)}) \exp(\Emp^{(6)} / \Emp^{(5)}).
+\end{align}
+%As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+%Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
 \cite{Cremer_1996}
-The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+These class-specific formulas reduced the mean absolute error from the FCI correlation energy by a
+factor of four compared to previous class-independent extrapolations,
+highlighting how one can leverage a deeper understanding of MP convergence to improve estimates of 
+the correlation energy at lower computational costs. 
+In Section~\ref{sec:Resummation}, we consider more advanced extrapolation routines that take account of EPs in the complex $\lambda$-plane.
+}
+%The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+%Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 
@@
 \section{Resummation Methods}
+\label{sec:Resummation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-25 Manuscript/EPAWTFT.tex
minor textual changes to Olsen analysis

@@
 
-In the late 90's, Olsen \textit{et al.}~discovered an even more preoccupying behaviour of the MP series. \cite{Olsen_1996} 
-They showed that the series could be divergent even in systems that they considered as well understood like \ce{Ne} and the \ce{HF} molecule. \cite{Olsen_1996, Christiansen_1996} 
-Cremer and He had already studied these two systems and classified them as \textit{class B} systems. 
-However, the analysis of Olsen and coworkers was performed in larger basis sets containing diffuse functions. 
-In these basis sets, they found that the series become divergent at (very) high order.
-
-The discovery of this divergent behaviour is worrying as in order to get meaningful and accurate energies, calculations must be performed in large basis sets (as close as possible from the complete basis set limit).
-\cite{Loos_2019d,Giner_2019}
-Including diffuse functions is particularly important in the case of anions and/or Rydberg excited states where the wave function is much more diffuse than the ground-state one.
-\cite{Loos_2018a,Loos_2020a}
-As a consequence, they investigated further the causes of these divergences as well as the reasons of the different types of convergence. 
-To do so, they analysed the relation between the dominant singularity (\ie, the closest singularity to the origin) and the convergence behaviour of the series.
-\cite{Olsen_2000} Their analysis is based on Darboux's theorem: \cite{Goodson_2011}
+In the late 90's, Olsen \etal\ discovered an even more concerning behaviour of the MP series. \cite{Olsen_1996} 
+They showed that the series could be divergent even in systems that were considered to be well understood, 
+such as \ce{Ne} or the \ce{HF} molecule. \cite{Olsen_1996, Christiansen_1996} 
+Cremer and He had already studied these two systems and classified them as \textit{class B} systems.\cite{Cremer_1996} 
+However, Olsen and co-workers performed their analysis in larger basis sets containing diffuse functions,
+finding that the correspoding MP series becomes divergent at (very) high order.
+The discovery of this divergent behaviour is particularly worrying as large basis sets \trashHB{(as close to 
+the complete basis set as possible)} are required to get meaningful and accurate energies.\cite{Loos_2019d,Giner_2019}
+Furthermore, diffuse functions are particularly important for anions and/or Rydberg excited states, where the wave function 
+is inherently more diffuse than the ground state.\cite{Loos_2018a,Loos_2020a}
+
+Olsen \etal\ investigated the causes of these divergences and the different types of convergence by
+analysing the relation between the dominant singularity (\ie, the closest singularity to the origin) 
+and the convergence behaviour of the series.\cite{Olsen_2000} 
+Their analysis is based on Darboux's theorem: \cite{Goodson_2011}
 \begin{quote}
@@
 \end{quote}
-Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.
-A singularity in the unit circle is designated as an intruder state, more precisely as a front-door (respectively back-door) intruder state if the real part of the singularity is positive (respectively negative).
-
-Following their observations from Ref.~\onlinecite{Olsen_1996}, Olsen and collaborators later proposed a simple method which consists in performing a scan of the real axis to detect the avoided crossing responsible for the pair of dominant singularities.
-\cite{Olsen_2000}
-Then, by modelling this avoided crossing via a two-state Hamiltonian one can get an approximation of the dominant conjugate pair of singularities by finding the EPs of the following $2\times2$ matrix
+\trashHB{Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.}
+\hugh{Following this theory,} a singularity in the unit circle is designated as an intruder state, 
+with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative).
+
+Using their observations in Ref.~\onlinecite{Olsen_1996}, Olsen and collaborators proposed 
+a simple method that performs a scan of the real axis to detect the avoided crossing responsible 
+for the dominant singularities in the complex plane. \cite{Olsen_2000} 
+By modelling this avoided crossing using a two-state Hamiltonian, one can obtain an approximation for
+the dominant singularities as the EPs of the $2\times2$ matrix
 \begin{equation}
 	\label{eq:Olsen_2x2}
-	\underbrace{\mqty(\alpha & \delta \\ \delta & \beta)}_{\bH} = \underbrace{\mqty(\alpha & 0 \\ 0 & \beta + \gamma )}_{\bH^{(0)}} + \underbrace{\mqty( 0 & \delta \\ \delta & - \gamma)}_{\bV},
-\end{equation}
-where the diagonal matrix is the unperturbed Hamiltonian matrix $\bH^{(0)}$ and the second matrix in the right-hand-side $\bV$ is the perturbation.
-
-They first studied an example of molecules with low-lying doubly-excited states of the same spatial and spin symmetry as the ground state. \cite{Olsen_2000}
-In such a case, the exact wave function has a non-negligible contribution from the doubly-excited states, so these low-lying excited states are good candidates for being intruder states. 
-For \ce{CH_2} in a diffuse yet rather small basis set, the series is convergent at least up to the 50th order. 
-They showed that the dominant singularity lies outside the unit circle but close to it causing the slow convergence.
-
-Then, they demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state. 
-When the basis set is augmented with diffuse functions, the ground state undergo sharp avoided crossings with highly diffuse excited states leading to a back-door intruder state. 
-They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series. 
+    \underbrace{\mqty(\alpha & \delta \\ \delta & \beta )}_{\bH} 
+    = \underbrace{\mqty(\alpha + \alpha_{\text{s}} & 0 \\ 0 & \beta + \beta_{\text{s}} )}_{\bH^{(0)}} 
+    + \underbrace{\mqty( -\alpha_{\text{s}} & \delta \\ \delta & - \beta_{\text{s}})}_{\bV},
+\end{equation}
+where the diagonal matrix is the unperturbed Hamiltonian matrix $\bH^{(0)}$ with level shifts
+$\alpha_{\text{s}}$ and $\beta_{\text{s}}$, \hugh{and $\bV$ represents the perturbation.}
+
+The authors first considered molecules with low-lying doubly-excited states with the same spatial
+and spin symmetry as the ground state. \cite{Olsen_2000}
+In these systems, the exact wave function has a non-negligible contribution from the doubly-excited states, 
+and thus the low-lying excited states are likely to become intruder states. 
+For \ce{CH_2} in a diffuse, yet rather small basis set, the series is convergent at least up to the 50th order, and
+the dominant singularity lies close (but outside) the unit circle, causing slow convergence of the series.
+\hugh{These intruder-state effects are analogous to the EP that dictates the convergence behaviour of 
+the RMP series for the Hubbard dimer (Fig.~\ref{fig:RMP}).}
+Furthermore, the authors demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state
+that arise when the ground state undergos sharp avoided crossings with highly diffuse excited states.
+%They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series. 
 %They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state. 
-
-Moreover they proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} cannot be used for all systems, and that these formulas were not mathematically motivated when looking at the singularity causing the divergence.
-For example, the hydrogen fluoride molecule contains both back-door intruder states and low-lying doubly-excited states which results in alternated terms up to 10th order. 
-For higher orders, the series is monotonically convergent. This surprising behaviour is due to the fact that two pairs of singularities are approximately at the same distance from the origin.
-
-In Ref.~\onlinecite{Olsen_2019}, the simple two-state model proposed by Olsen \textit{et al.} [see Eq.~\eqref{eq:Olsen_2x2}] is generalised to a non-symmetric Hamiltonian 
+\hugh{This divergence is related to a more fundamental critical point in the MP energy surface that we will
+discuss in Section~\ref{sec:MP_critical_point}.}
+
+Finally, Ref.~\onlinecite{Olsen_1996} proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996}
+are not mathematically motivated when considering the complex singularities causing the divergence, and therefore
+cannot be applied for all systems.
+For example, \ce{HF} contains both back-door intruder states and low-lying doubly-excited states that
+result in alternating terms up to 10th order. 
+The series becomes monotonically convergent at higher orders since
+the two pairs of singularities are approximately the same distance from the origin.
+
+More recently, this two-state model has been extended to non-symmetric Hamiltonians as\cite{Olsen_2019}
 \begin{equation}
@@
 \end{equation}
-allowing an analysis of various choice of perturbation (not only the MP partitioning) such as coupled cluster perturbation expansions \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} and other non-Hermitian perturbation methods.
-It is worth noting that only cases where $\text{sgn}(\delta_1) = - \text{sgn}(\delta_2)$ leads to new forms of perturbation expansions.
-Interestingly, they showed that the convergence pattern of a given perturbation method can be characterised by its archetype which defines the overall ``shape'' of the energy convergence. 
-These so-called archetypes can be subdivided in five classes for Hermitian Hamiltonians (zigzag, interspersed zigzag, triadic, ripples, and geometric), while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
-Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
-Importantly, they observed that the geometric archetype is the most common for MP expansions but that the ripples archetype sometimes occurs. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
-The three remaining archetypes seem to be rarely observed in MP perturbation theory.
-However, in the non-Hermitian setting of coupled cluster perturbation theory, \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} on can encounter interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric archetypes.
-One of main take-home messages of Olsen's study is that the primary critical point defines the high-order convergence, irrespective of whether this point is inside or outside the complex unit circle.
-\cite{Handy_1985,Olsen_2000}
+This extension allows various choices of perturbation to be analysed, including coupled cluster 
+perturbation expansions \cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} 
+and other non-Hermitian perturbation methods.
+Note that new forms of perturbation expansions only occur when the sign of $\delta_1$ and $\delta_2$ differ.
+Using these non-Hermitian two-state model, the convergence of a perturbation series can be characterised 
+according to a so-called ``archetype'' that defines the overall ``shape'' of the energy convergence.\cite{Olsen_2019} 
+For Hermitian Hamiltonians, these archetypes can be subdivided into five classes 
+(zigzag, interspersed zigzag, triadic, ripples, and geometric), 
+while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
+%Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
+
+The geometric archetype appears to be the most common for MP expansions,\cite{Olsen_2019} but the 
+ripples archetype corresponds to some of the early examples of MP convergence. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
+The three remaining Hermitian archetypes seem to be rarely observed in MP perturbation theory.
+In contrast, the non-Hermitian coupled cluster perturbation theory,%
+\cite{Pawlowski_2019a,Pawlowski_2019b,Pawlowski_2019c,Pawlowski_2019d,Pawlowski_2019e} exhibits a range of archetypes
+including the interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric forms.
+\hugh{This analysis highlights the importance of the primary critical point in controlling the high-order convergergence, 
+regardless of whether this point is inside or outside the complex unit circle. \cite{Handy_1985,Olsen_2000}}
 
@@
 \subsection{The singularity structure}
+\label{sec:MP_critical_point}
 %=======================================

### 2020-11-25 Manuscript/EPAWTFT.tex
Stuff on quadratic approximant

--- 2020-11-25 Manuscript/EPAWTFT.tex
@@
 \newcommand{\lep}{\lambda_{\text{EP}}}
-
-% Some energies
-\newcommand{\Emp}{E_{\text{MP}}}
 
@@
 %==========================================%
-\subsection{Spin-Contamination in the Hubbard Dimer}
+\subsection{Effect of Spin-Contamination in the Hubbard Dimer}
 %==========================================%
@@
 the analytic Hubbard dimer with a complex-valued perturbation strength.
-In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the electron correlation $U/t$.
+In this system, the stretching of a chemical bond is directly mirrored by an increase in the electron correlation $U/t$.
 Using the ground-state RHF reference orbitals leads to the parametrised RMP Hamiltonian
@@
 \end{widetext}
-While a closed-form expression for the ground-state energy exists, it is cumbersome and we eschew reporting it.
+While there is a closed-form expression for the ground-state energy, it is cumbersome and we eschew reporting it.
 Instead, the radius of convergence of the UMP series can be obtained numerically as a function of $U/t$, as shown
 in Fig.~\ref{fig:RadConv}.
-These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and always converges.
+These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and must always converge.
 However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
@@
 The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
-for larger $U/t$ as the radius of convergence becomes increasingly close to one (Fig.~\ref{fig:RadConv}).
+for larger $U/t$ as the radius of convergence becomes increasingly close to 1 (Fig.~\ref{fig:RadConv}).
 
@@
 the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\hugh{The slow convergence observed in stretched \ce{H2}\cite{Gill_1988} can then be seen as this EP 
-moves increasingly close to the unit cylinder at large $U/t$ and $\rc$ approaches one (from above).}
+\titou{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+moves closer to one at larger $U/t$ values.}
 Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
@@
 % CREMER AND HE
-\hugh{As computational implementations of higher-order MP terms improved, the systematic investigation 
-of convergence behaviour in a broader class of molecules became possible.}
-Cremer and He \hugh{introduced an efficient MP6 approach and used it to analyse the RMP convergence of}
-29 atomic and molecular systems with respect to the FCI energy.\cite{Cremer_1996}
-They established two general classes: ``class A'' systems that exhibit monotonic convergence; 
-and ``class B'' systems for which convergence is erratic after initial oscillations. 
-%Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
-\hugh{By analysing the different cluster contributions to the MP energy terms, they proposed that
-class A systems generally include well-separated and weakly correlated electron pairs, while class B systems
-are characterised by dense electron clustering in one or more spatial regions.}\cite{Cremer_1996}
-%\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-%Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
-In class A systems, they showed that the majority of the correlation energy arises from pair correlation, 
-with little contribution from triple excitations.
-On the other hand, triple excitations have an important contribution in class B systems, including providing
-orbital relaxation, and these contributions lead to oscillations of the total correlation energy.
-%This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
-
-\hugh{%
-Using these classifications, Cremer and He then introduced simple extrapolation formulas for estimating the 
-exact correlation energy $\Delta E$ using terms up to MP6\cite{Cremer_1996}
-\begin{align}
-\Delta E_{\text{A}}
-    &= \Emp^{(2)} + \Emp^{(3)} + \Emp^{(4)}
-     + \frac{\Emp^{(5)}}{1 - (\Emp^{(6)} / \Emp^{(5)})}, 
-     \\[5pt]
-\Delta E_{\text{B}} 
-    &= \Emp^{(2)} + \Emp^{(3)} + \qty(\Emp^{(4)} + \Emp^{(5)}) \exp(\Emp^{(6)} / \Emp^{(5)}).
-\end{align}
-%As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-%Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
+Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
+Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
+They highlighted that \cite{Cremer_1996}
+\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
+Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
+They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
+On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
+This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
+As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
+Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
 \cite{Cremer_1996}
-These class-specific formulas reduced the mean absolute error from the FCI correlation energy by a
-factor of four compared to previous class-independent extrapolations,
-highlighting how one can leverage a deeper understanding of MP convergence to improve estimates of 
-the correlation energy at lower computational costs. 
-In Section~\ref{sec:Resummation}, we consider more advanced extrapolation routines that take account of EPs in the complex $\lambda$-plane.
-}
-%The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-%Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
+Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
 
@@
 \section{Resummation Methods}
-\label{sec:Resummation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained with various approximations for $U/t = 4.5$.}
+    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 4.5$.}
 \end{figure}
@@
 \end{align}
-are polynomials, such that $d_P + d_Q + d_R = n - 1$, where $n$ is the highest-order series coefficient known from the Taylor expansion of $E(\lambda)$.
+are polynomials, such that $d_P + d_Q + d_R = n - 1$, where $n$ is the truncation order of the Taylor of $E(\lambda)$.
 Recasting Eq.~\eqref{eq:QuadApp} as a second-order expression in $E(\lambda)$, \ie,
@@
 and substituting $E(\lambda$) by its $n$th-order expansion and the polynomials by their respective expressions \eqref{eq:PQR} yields $n+1$ linear equations for the coefficients $p_k$, $q_k$, and $r_k$ (where we are free to assume that $q_0 = 1$).
-A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $\max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$.
+A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$.
 The diagonal sequence of quadratic approximant, \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, is of particular interest.
@@
 We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function which contains three branches.
-However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~??.
+However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~\ref{fig:QuadUMP}.
+
+\titou{Here comes a discussion of Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}.}
+
+%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \includegraphics[width=\linewidth]{QuadUMP}
+    \caption{\label{fig:QuadUMP}
+    UMP energies as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3$.}
+\end{figure}
+%%%%%%%%%%%%%%%%%
+
+\begin{table}
+	\caption{Radius of convergence $r_c$ for various resummation techniques at $U/t = 3$ and $7$.
+	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch points $n_\text{bp} = \max(2d_p,d_q+d_r)$ generated by the quadratic approximant are also reported.
+	\label{tab:QuadUMP}}
+	\begin{ruledtabular}
+		\begin{tabular}{llcccc}
+						&			&			&					&	\mc{2}{c}{$r_c$}			\\
+																		\cline{5-6}
+			\mc{2}{c}{Method}		&	$n$		&	$n_\text{bp}$	&	$U/t = 3$	&	$U/t = 7$	\\
+			\hline
+			Pad\'e		&	[2/2]	&	4	&		&	0.97448		&	1.00030	\\
+						&	[3/3]	&	6	&		&	1.14138		&	1.00448	\\
+			Quadratic	&	[2/1,2]	&	6	&	4	&	1.08640		&	1.00310	\\
+						&	[2/2,2]	&	7	&	4	&	1.08193		&	1.00310	\\
+						&	[3/2,2]	&	8	&	6	&	1.08247		&	1.00106	\\
+						&	[3/2,3]	&	9	&	6	&	1.07069		&	1.00239	\\
+						&	[3/3,3]	&	10	&	6	&	1.07064		&	1.00239	\\
+			Exact		&			&		&		&	1.06917		&	1.00239\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 

### 2020-11-25 Manuscript/EPAWTFT.tex
reviewing Hugh stuff. Corrected a few typos

@@
 Using the (localised) site basis, the Hilbert space of the Hubbard dimer comprises the four configurations
-\begin{align}
+\begin{align*}
 & \ket{\Lup \Ldown} &  & \ket{\Lup\Rdown} &  & \ket{\Rup\Ldown} &  & \ket{\Rup\Rdown}
-\end{align}
+\end{align*}
 where $\Lsi$ ($\Rsi$) denotes an electron with spin $\sigma$ on the left (right) site.
@@
 the spin-$\sigma$ electrons as
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 In the weak correlation regime $0 \le U \le 2t$, the angles which minimise the HF energy, 
@@
 For $U \ge 2t$, the optimal orbital rotation angles for the UHF orbitals become
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 with the corresponding UHF ground-state energy (Fig.~\ref{fig:HF_real})
@@
 the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
-\hugh{The slow convergence observed in stretched \ce{H2}\cite{Gill_1988} can then be seen as this EP 
-moves increasingly close to the unit cylinder at large $U/t$ and $\rc$ approaches one (from above).}
+The slow convergence observed in stretched \ce{H2}\cite{Gill_1988} can then be seen as this EP 
+moves increasingly close to the unit cylinder at large $U/t$ and $\rc$ approaches one (from above).
 Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
@@
 % CREMER AND HE
-\hugh{As computational implementations of higher-order MP terms improved, the systematic investigation 
-of convergence behaviour in a broader class of molecules became possible.}
-Cremer and He \hugh{introduced an efficient MP6 approach and used it to analyse the RMP convergence of}
+As computational implementations of higher-order MP terms improved, the systematic investigation 
+of convergence behaviour in a broader class of molecules became possible.
+Cremer and He introduced an efficient MP6 approach and used it to analyse the RMP convergence of
 29 atomic and molecular systems with respect to the FCI energy.\cite{Cremer_1996}
@@
 %Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
-\hugh{By analysing the different cluster contributions to the MP energy terms, they proposed that
+By analysing the different cluster contributions to the MP energy terms, they proposed that
 class A systems generally include well-separated and weakly correlated electron pairs, while class B systems
-are characterised by dense electron clustering in one or more spatial regions.}\cite{Cremer_1996}
+are characterised by dense electron clustering in one or more spatial regions.\cite{Cremer_1996}
 %\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
@@
 
-\hugh{%
 Using these classifications, Cremer and He then introduced simple extrapolation formulas for estimating the 
 exact correlation energy $\Delta E$ using terms up to MP6\cite{Cremer_1996}
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 %As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
@@
 In Section~\ref{sec:Resummation}, we consider more advanced extrapolation routines that take account of EPs in the complex $\lambda$-plane.
-}
 %The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
@@
 However, Olsen and co-workers performed their analysis in larger basis sets containing diffuse functions,
-finding that the correspoding MP series becomes divergent at (very) high order.
-The discovery of this divergent behaviour is particularly worrying as large basis sets \trashHB{(as close to 
-the complete basis set as possible)} are required to get meaningful and accurate energies.\cite{Loos_2019d,Giner_2019}
+finding that the corresponding MP series becomes divergent at (very) high order.
+The discovery of this divergent behaviour is particularly worrying as large basis sets 
+are required to get meaningful and accurate energies.\cite{Loos_2019d,Giner_2019}
 Furthermore, diffuse functions are particularly important for anions and/or Rydberg excited states, where the wave function 
@@
 \end{quote}
-\trashHB{Following the result of this theorem, the convergence patterns of the MP series can be explained by looking at the dominant singularity.}
-\hugh{Following this theory,} a singularity in the unit circle is designated as an intruder state, 
+Following this theory, a singularity in the unit circle is designated as an intruder state, 
 with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative).
@@
 where the diagonal matrix is the unperturbed Hamiltonian matrix $\bH^{(0)}$ with level shifts
-$\alpha_{\text{s}}$ and $\beta_{\text{s}}$, \hugh{and $\bV$ represents the perturbation.}
+$\alpha_{\text{s}}$ and $\beta_{\text{s}}$, and $\bV$ represents the perturbation.
 
@@
 the dominant singularity lies close (but outside) the unit circle, causing slow convergence of the series.
-\hugh{These intruder-state effects are analogous to the EP that dictates the convergence behaviour of 
-the RMP series for the Hubbard dimer (Fig.~\ref{fig:RMP}).}
+These intruder-state effects are analogous to the EP that dictates the convergence behaviour of 
+the RMP series for the Hubbard dimer (Fig.~\ref{fig:RMP}).
 Furthermore, the authors demonstrated that the divergence for \ce{Ne} is due to a back-door intruder state
-that arise when the ground state undergos sharp avoided crossings with highly diffuse excited states.
+that arise when the ground state undergoes sharp avoided crossings with highly diffuse excited states.
 %They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series. 
 %They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state. 
-\hugh{This divergence is related to a more fundamental critical point in the MP energy surface that we will
-discuss in Section~\ref{sec:MP_critical_point}.}
+This divergence is related to a more fundamental critical point in the MP energy surface that we will
+discuss in Section~\ref{sec:MP_critical_point}.
 
@@
 including the interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric forms.
-\hugh{This analysis highlights the importance of the primary critical point in controlling the high-order convergergence, 
-regardless of whether this point is inside or outside the complex unit circle. \cite{Handy_1985,Olsen_2000}}
+This analysis highlights the importance of the primary critical point in controlling the high-order convergence, 
+regardless of whether this point is inside or outside the complex unit circle. \cite{Handy_1985,Olsen_2000}
 
@@
 %=======================================
-In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analyzed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
 \cite{Olsen_1996,Olsen_2000,Olsen_2019}

### 2020-11-25 Manuscript/EPAWTFT.tex
few typos in Pade section

@@
 The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
-This description can be significantly improved thanks to Pad\'e approximant. \cite{Pade_1892,BakerBook}
+A Taylor series just does not have enough flexibility for this job.
+Nonetheless, the description of complex energy functions can be significantly improved thanks to Pad\'e approximant, \cite{Pade_1892} and related techniques. \cite{BakerBook,BenderBook}
 
 According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}. 
-A $[d_A/d_B]$ Pad\'e approximant is defined as 
+More specifically, a $[d_A/d_B]$ Pad\'e approximant is defined as 
 \begin{equation}
@@
 (with $b_0 = 1$), where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms according to power of $\lambda$.
-Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Gluzman_2020} as they can model poles, which appears at the roots of the polynomial $B(\lambda)$. 
+Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, which appears at the roots of the polynomial $B(\lambda)$.
 However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
@@
 %==========================================%
-In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalized version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
+In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalised version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
 \begin{equation}
@@
 \end{align}
-are polynomials, such that $d_P + d_Q + d_R = n - 1$, where $n$ is the truncation order of the Taylor of $E(\lambda)$.
+are polynomials, such that $d_P + d_Q + d_R = n - 1$, and $n$ is the truncation order of the Taylor series of $E(\lambda)$.
 Recasting Eq.~\eqref{eq:QuadApp} as a second-order expression in $E(\lambda)$, \ie,
@@
 
-We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function which contains three branches.
-However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~\ref{fig:QuadUMP}.
+We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function contains three branches.
+However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}.
 

### 2020-11-26 Manuscript/EPAWTFT.tex
new fig with Hugh style
update fig

@@
 However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
-Figure \ref{fig:PadeRMP} illustrates the improvement brought by Pad\'e approximants as compared to the usual Taylor expansion in the case of the RMP series of the Hubbard dimer for $U/t = 4.5$.
+Figure \ref{fig:PadeRMP} illustrates the improvement brought by diagonal (\ie, $d_A = d_B$) Pad\'e approximants as compared to the usual Taylor expansion in the case of the RMP series of the Hubbard dimer for $U/t = 4.5$.
 
@@
 Note that, by construction, a quadratic approximant has only two branches which hampers the faithful description of more complicated singularity structures.
-
 As shown in Ref.~\onlinecite{Goodson_2000}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}

### 2020-11-26 Manuscript/EPAWTFT.tex
35 and 45

@@
 %%%%%%%%%%%%%%%%%
-\begin{figure}
-    \includegraphics[width=\linewidth]{PadeRMP}
+\begin{figure*}
+    \includegraphics[height=0.23\textheight]{PadeRMP35}
+    \includegraphics[height=0.23\textheight]{PadeRMP45}
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 4.5$.}
-\end{figure}
+    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
+\end{figure*}
 %%%%%%%%%%%%%%%%%

### 2020-11-26 Manuscript/EPAWTFT.tex
saving work on RMP pade

@@
 However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
-Figure \ref{fig:PadeRMP} illustrates the improvement brought by diagonal (\ie, $d_A = d_B$) Pad\'e approximants as compared to the usual Taylor expansion in the case of the RMP series of the Hubbard dimer for $U/t = 4.5$.
+Figure \ref{fig:PadeRMP} illustrates the improvement brought by diagonal (\ie, $d_A = d_B$) Pad\'e approximants as compared to the usual Taylor expansion in cases where the RMP series of the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
+
+\begin{table}
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various Taylor expansions and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
+	We also report the estimate of the radius of convergence $r_c$ provided by the diagonal Pad\'e approximants.
+	\label{tab:PadeRMP}}
+	\begin{ruledtabular}
+		\begin{tabular}{lccccc}
+						&			&	\mc{2}{c}{$r_c$}			&	\mc{2}{c}{$E_{-}(\lambda = 1)$}			\\
+																		\cline{3-4} \cline{5-6}
+			Method		&	degree	&	$U/t = 3.5$	&	$U/t = 4.5$	&	$U/t = 3.5$	&	$U/t = 4.5$	\\
+			\hline
+			Taylor		&	2		&		&		&	$-1.01563$	&	$-1.01563$	\\
+						&	3		&		&		&	$-1.01563$	&	$-1.01563$	\\
+						&	4		&		&		&	$-0.86908$	&	$-0.61517$	\\
+						&	5		&		&		&	$-0.86908$	&	$-0.61517$	\\
+						&	6		&		&		&	$-0.92518$	&	$-0.86858$	\\
+			Pad\'e		&	[1/1]	&	$2.29$	&	$1.78$	&	$-1.61111$	&	$-2.64286$	\\
+						&	[2/2]	&	$2.29$	&	$1.78$	&	$-0.82124$	&	$-0.48446$	\\
+						&	[3/3]	&	$1.73$	&	$1.34$	&	$-0.91995$	&	$-0.81929$	\\
+						&	[4/4]	&	$1.47$	&	$1.14$	&	$-0.90579$	&	$-0.74866$	\\
+						&	[5/5]	&	$1.35$	&	$1.05$	&	$-0.90778$	&	$-0.76277$	\\
+			\hline
+			Exact		&			&	$1.14$	&	$0.89$	&	$-0.90754$	&	$-0.76040$	\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 
@@
 \begin{table}
-	\caption{Radius of convergence $r_c$ for various resummation techniques at $U/t = 3$ and $7$.
-	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch points $n_\text{bp} = \max(2d_p,d_q+d_r)$ generated by the quadratic approximant are also reported.
+	\caption{Estimate of the radius of convergence $r_c$ of the UMP energy function provided by various resummation techniques at $U/t = 3$ and $7$.
+	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch points $n_\text{bp} = \max(2d_p,d_q+d_r)$ generated by the quadratic approximants are also reported.
 	\label{tab:QuadUMP}}
 	\begin{ruledtabular}
-		\begin{tabular}{llcccc}
-						&			&			&					&	\mc{2}{c}{$r_c$}			\\
-																		\cline{5-6}
-			\mc{2}{c}{Method}		&	$n$		&	$n_\text{bp}$	&	$U/t = 3$	&	$U/t = 7$	\\
+		\begin{tabular}{lccccccc}
+						&			&			&					&	\mc{2}{c}{$r_c$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
+																		\cline{5-6}\cline{7-8}
+			\mc{2}{c}{Method}		&	$n$		&	$n_\text{bp}$	&	$U/t = 3$	&	$U/t = 7$	&	$U/t = 3$	&	$U/t = 7$	\\
 			\hline
-			Pad\'e		&	[2/2]	&	4	&		&	0.97448		&	1.00030	\\
-						&	[3/3]	&	6	&		&	1.14138		&	1.00448	\\
-			Quadratic	&	[2/1,2]	&	6	&	4	&	1.08640		&	1.00310	\\
-						&	[2/2,2]	&	7	&	4	&	1.08193		&	1.00310	\\
-						&	[3/2,2]	&	8	&	6	&	1.08247		&	1.00106	\\
-						&	[3/2,3]	&	9	&	6	&	1.07069		&	1.00239	\\
-						&	[3/3,3]	&	10	&	6	&	1.07064		&	1.00239	\\
-			Exact		&			&		&		&	1.06917		&	1.00239\\
+			Pad\'e		&	[2/2]	&	4	&		&	0.974		&	1.000	\\
+						&	[3/3]	&	6	&		&	1.141		&	1.004	\\
+						&	[4/4]	&	8	&		&	1.068		&	1.003	\\
+			Quadratic	&	[2/1,2]	&	6	&	4	&	1.086		&	1.003	\\
+						&	[2/2,2]	&	7	&	4	&	1.082		&	1.003	\\
+						&	[3/2,2]	&	8	&	6	&	1.082		&	1.001	\\
+						&	[3/2,3]	&	9	&	6	&	1.071		&	1.002	\\
+						&	[3/3,3]	&	10	&	6	&	1.071		&	1.002	\\
+			Exact		&			&		&		&	1.069		&	1.002	\\
 		\end{tabular}

### 2020-11-26 Manuscript/EPAWTFT.tex
1st complete draft of Pade and Quadratic

@@
 The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
-A Taylor series just does not have enough flexibility for this job.
+A truncated Taylor series just does not have enough flexibility to do the job properly.
 Nonetheless, the description of complex energy functions can be significantly improved thanks to Pad\'e approximant, \cite{Pade_1892} and related techniques. \cite{BakerBook,BenderBook}
@@
 (with $b_0 = 1$), where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms according to power of $\lambda$.
-Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, which appears at the roots of the polynomial $B(\lambda)$.
-However, they are unable to model functions with square-root branch points, which are ubiquitous in the singularity structure of a typical perturbative treatment.
+Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, which appears at the locations of the roots of $B(\lambda)$.
+However, they are unable to model functions with square-root branch points (which are ubiquitous in the singularity structure of a typical perturbative treatment) and more complicated functional forms appearing at critical points (where the nature of the solution undergoes a sudden transition) for example.
+
 Figure \ref{fig:PadeRMP} illustrates the improvement brought by diagonal (\ie, $d_A = d_B$) Pad\'e approximants as compared to the usual Taylor expansion in cases where the RMP series of the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
+More quantitatively, Table \ref{tab:PadeRMP} gathers estimates of the RMP ground-state energy at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e approximants for these two values of the ratio $U/t$.
+While the truncated Taylor series converges laboriously to the exact energy at $U/t = 3.5$ when one increases the truncation degree, the Pad\'e approximants yield much more accurate results with, additionally, a rather good estimate of the radius of convergence of the RMP series.
+For $U/t = 4.5$, the struggles of the truncated Taylor expansions are magnified and the Pad\'e approximants still provide quite accurate energies even outside the radius of convergence of the RMP series.
 
 \begin{table}
-	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various Taylor expansions and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
 	We also report the estimate of the radius of convergence $r_c$ provided by the diagonal Pad\'e approximants.
@@
 
-We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function contains three branches.
-However, by ramping up high enough the degree of the polynomials, one is able to get an accurate estimates of the radius of convergence of the UMP series as shown in Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}.
-
-\titou{Here comes a discussion of Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}.}
+We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function contains three branches (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
+However, by ramping up high enough the degree of the polynomials, one is able to get both, as shown in Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}, accurate estimates of the radius of convergence of the UMP series and of the ground-state energy at $\lambda = 1$, even in cases where the convergence of the UMP series is painfully slow (see Fig.~\ref{subfig:UMP_cvg}).
+Figure \ref{fig:QuadUMP} evidences that the Pad\'e approximants are trying to model the square root singularity by placing a pole on the real axis (for [3/3]) or just off the real axis (for [4/4]).
+Thanks to greater flexibility, the quadratic approximants are able to model nicely the avoided crossing and the location of the singularities. 
+Besides, they provide accurate estimates of the ground-state energy at $\lambda = 1$ (see Table \ref{tab:QuadUMP}).
 
@@
 			\hline
-			Pad\'e		&	[2/2]	&	4	&		&	0.974		&	1.000	\\
-						&	[3/3]	&	6	&		&	1.141		&	1.004	\\
-						&	[4/4]	&	8	&		&	1.068		&	1.003	\\
-			Quadratic	&	[2/1,2]	&	6	&	4	&	1.086		&	1.003	\\
-						&	[2/2,2]	&	7	&	4	&	1.082		&	1.003	\\
-						&	[3/2,2]	&	8	&	6	&	1.082		&	1.001	\\
-						&	[3/2,3]	&	9	&	6	&	1.071		&	1.002	\\
-						&	[3/3,3]	&	10	&	6	&	1.071		&	1.002	\\
-			Exact		&			&		&		&	1.069		&	1.002	\\
+			Pad\'e		&	[3/3]	&	6		&					&	$1.141$		&	$1.004$		&	$-1.10896$	&	$-1.49856$	\\
+						&	[4/4]	&	8		&					&	$1.068$		&	$1.003$		&	$-0.85396$	&	$-0.33596$	\\
+						&	[5/5]	&	10		&					&	$1.122$		&	$1.004$		&	$-0.97254$	&	$-0.35513$	\\
+			Quadratic	&	[2/1,2]	&	6		&	4				&	$1.086$		&	$1.003$		&	$-1.01009$	&	$-0.53472$	\\
+						&	[2/2,2]	&	7		&	4				&	$1.082$		&	$1.003$		&	$-1.00553$	&	$-0.53463$	\\
+						&	[3/2,2]	&	8		&	6				&	$1.082$		&	$1.001$		&	$-1.00568$	&	$-0.52473$	\\
+						&	[3/2,3]	&	9		&	6				&	$1.071$		&	$1.002$		&	$-0.99973$	&	$-0.53102$	\\
+						&	[3/3,3]	&	10		&	6				&	$1.071$		&	$1.002$		&	$-0.99966$	&	$-0.53103$	\\
+			\hline
+			Exact		&			&			&					&	$1.069$		&	$1.002$		&	$-1.00000$	&	$-0.53113$	\\
 		\end{tabular}

### 2020-11-27 Manuscript/EPAWTFT.tex
Modifications to the MP critical point section

@@
 We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptionnal points.
-After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree-Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
 In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory and its apparent link with quantum phase transitions.
@@
 %===========================================%
-\subsection{Hartree-Fock Theory}
+\subsection{Hartree--Fock Theory}
 \label{sec:HF}
@@
 % SUMMARY OF HF
-In the Hartree-Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
+In the Hartree--Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
 This Slater determinant is defined as an antisymmetric combination of $\Ne$ (real-valued) occupied one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
@@
 %================================================================%
-\subsection{Hartree-Fock in the Hubbard Dimer}
+\subsection{Hartree--Fock in the Hubbard Dimer}
 \label{sec:HF_hubbard}
@@
 
-%\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree-Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
+%\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree--Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
 %In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller--Plesset Perturbation Theory in the Complex Plane}
+\section{M{\o}ller--Plesset Theory in the Complex Plane}
 \label{sec:MP}
@@
 %=====================================================%
-\subsection{Early Investigations into M{\o}ller--Plesset Convergence} % in Molecular Systems}
+\subsection{Early Studies of M{\o}ller--Plesset Convergence} % in Molecular Systems}
 %=====================================================%
@@
 %==========================================%
-\subsection{Classifying Types of Convergence Behaviour} % Further insights from a two-state model}
+\subsection{Classifying Types of Convergence} % Behaviour} % Further insights from a two-state model}
 %==========================================%
@@
 %=======================================
-\subsection{The singularity structure}
+\subsection{The M{\o}ller--Plesset Critical Point}
 \label{sec:MP_critical_point}
 %=======================================
-In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
-\cite{Olsen_1996,Olsen_2000,Olsen_2019}
-They regrouped singularities in two classes: i) $\alpha$ singularities which have ``large'' imaginary parts, and ii) $\beta$ singularities which have very small imaginary parts. 
-Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
-
-To understand the convergence properties of the perturbation series at $\lambda=1$, one must look at the whole complex plane, in particular, for negative (\ie, real) values of $\lambda$. 
-If $\lambda$ is negative, the Coulomb interaction becomes attractive but the mean field (which has been computed at $\lambda = 1$) remains repulsive as it is proportional to $(1-\lambda)$:
-
+
+% STILLINGER INTRODUCES THE CRITICAL POINT
+\hugh{%
+In the early 2000's, Stillinger reconsidered the mathematical origin behind the divergent series with odd-even
+sign alternation.\cite{Stillinger_2000} 
+This type of convergence behaviour corresponds to Cremer and He's class B systems with closely spaced
+electron pairs and includes \ce{Ne}, \ce{HF}, \ce{F-}, and \ce{H2O}.\cite{Cremer_1996}
+Stillinger proposed that the divergence of these series occurs arise from a dominant singularity
+on the negative real $\lambda$ axis, corresponding to a multielectron autoionisation threshold.\cite{Stillinger_2000}
+To understand Stillinger's argument, consider the paramterised MP Hamiltonian in the form
 \begin{multline}
@@
     \hH(\lambda) = 
-    \sum_{i}^{n} \Bigg[ 
+    \sum_{i}^{\Ne} \Bigg[ 
     \overbrace{-\frac{1}{2}\grad_i^2 
-    - \sum_{A}^{N} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}^{\text{independent of $\lambda$}}
+    - \sum_{A}^{\Nn} \frac{Z_A}{\abs{\vb{r}_i-\vb{R}_A}}}^{\text{independent of $\lambda$}}
     \\
     + \underbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}_{\text{repulsive for $\lambda < 1$}}
-    + \underbrace{\lambda\sum_{i<j}^{n}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{attractive for $\lambda < 0$}}
+    + \underbrace{\lambda\sum_{i<j}^{\Ne}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{attractive for $\lambda < 0$}}
     \Bigg].
 \end{multline}
-
-The major difference between these two terms is that the repulsive mean field is localised around the nuclei whereas the interelectronic interaction persist away from the nuclei. 
-If $\lambda$ becomes more and more negative the mean field becomes more and more repulsive so there exists a critical (negative) value $\lambda_\text{c}$, for which the Coulombic field created by the nuclei cannot bind the electrons anymore because of the $\lambda$-independent nature of the electron-nucleus attraction.
-For $\lambda = \lambda_c$, the electrons dissociate from the nuclei and form a bound cluster which is infinitely separated from the nuclei. 
-According to Baker, \cite{Baker_1971} this value is a critical point of the system and, by analogy with thermodynamics, the energy $E(\lambda)$ exhibits a singularity at $\lambda_\text{c}$. 
-At this point the system undergo a phase transition and a symmetry breaking. 
-Beyond $\lambda_c$ there is a continuum of eigenstates thanks to which the electrons dissociated from the nuclei.
-
-This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis. 
-However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
-
-Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
-On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
-According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
-This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
-To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
-
-%====================================================
-\subsection{The physics of quantum phase transitions}
-%====================================================
-
-In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point. 
-In a finite basis set, this critical point is model by a cluster of $\beta$ singularities. 
-It is now well known that this phenomenon is a special case of a more general phenomenon. 
-Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
+The mean-field potential $v^{\text{HF}}$ essentially represents a negatively charged field with the spatial extent
+controlled by the extent of the HF orbitals, usually located close to the nuclei.
+When $\lambda$ is negative, the mean-field potential becomes increasingly repulsive, while the explicit two-electron 
+Coulomb interaction becomes attractive.
+There is therefore a critical value $\lc < 0$ where it becomes energetically favourable for the electrons 
+to dissociate and form a bound cluster at an infinite separation from the nuclei.\cite{Stillinger_2000}
+This autoionisation effect is closely related to the critial point for electron binding in two-electron 
+atoms (see Ref.~\onlinecite{Baker_1971}).
+Furthermore, a similar set of critical points exists along the positive real axis, corresponding to single-electron ionisation
+processes.\cite{Sergeev_2005}
+}
+
+% CLASSIFICATIONS BY GOODSOON AND SERGEEV
+\hugh{%
+To further develop the link between the critical point and types of MP convergence, Sergeev and Goodson investigated
+the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}.
+They demonstrated that the dominant singularity in class A corresponds to a dominant EP with a positive real component, 
+with the magnitude of the imaginary component controlling the oscillations in the signs of the MP 
+term.\cite{Goodson_2000a,Goodson200b}
+In contrast, class B systems correspond to a dominant singularity on the negative real $\lambda$ axis representing
+the MP critical point.
+The divergence of class B systems, which contain closely spaced electrons (\eg, \ce{F-}), can then be understood as the 
+HF potential $v^{\text{HF}}$ is relatively localised and the autoionization is favoured at negative 
+$\lambda$ values closer to the origin.
+With these insights, they regrouped the systems into new classes: i) $\alpha$ singularities which have ``large'' imaginary parts, 
+and ii) $\beta$ singularities which have very small imaginary parts.\cite{Goodson_2004,Sergeev_2006} 
+}
+
+% RELATIONSHIP TO BASIS SET SIZE
+\hugh{%
+The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
+and \ce{HF} molecule occured when diffuse basis functions were included.\cite{Olsen_1996}
+Clearly diffuse basis functions are required for the electrons to dissociate from the nuclei, and indeed using
+only compact basis functions causes the critical point to disappear.
+While a finite basis can only predict complex-conjugate branch point singularities, the critical point is modelled
+by a cluster of sharp avoided crossings between the ground state and high-lying excited states.\cite{Sergeev_2005}
+Alternatively, Sergeev \etal\ demonstrated that the inclusion of a ``ghost'' atom also
+allows the formation of the critical point as the electrons form a bound cluster occuping the ghost atom orbitals.\cite{Sergeev_2005}
+This effect explains the origin of the divergence in the \ce{HF} molecule as the \ce{F} valence electrons jump to \ce{H} 
+for a sufficiently negative $\lambda$.\cite{Sergeev_2005}
+Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
+divergences caused by the MP critical point.
+}
+
+% BASIS SET DEPENDENCE (INCLUDE?)
+%Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
+%On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
+%According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
+%This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
+%To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+
+%In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+\cite{Olsen_1996,Olsen_2000,Olsen_2019}
+%Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
+%They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
+
+%This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis. 
+%However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+%Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+%This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
+
+% RELATIONSHIP TO QUANTUM PHASE TRANSITION
+\hugh{%
+When a Hamiltonian is parametrised by a variable such as $\lambda$, the existence of abrupt changes in the 
+eigenstates as a function of $\lambda$ indicate the presence of a zero-temperature quantum phase transition (QPT).%
 \cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
-In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter. 
-In some cases the variation of a parameter can lead to abrupt changes at a critical point. 
-These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
+As an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis.
+The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
+Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
+recognised a QPT within the perturbation theory approximation.
+However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
+basis set limit.\cite{Kais_2006}
+The MP critical point $\beta$ singularity in a finite basis must therefore be modelled by pairs of EPs
+that tend towards the real axis, exactly as described by Sergeev \etal.\cite{Sergeev_2005}
+In contrast, $\alpha$ singularities correspond to large avoided crossings that are indicative of low-lying excited
+states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
+}
+
+%=======================================
+\subsection{Critical Point in the Hubbard Dimer}
+\label{sec:critical_point_hubbard}
+%=======================================
+
+%%====================================================
+%\subsection{The physics of quantum phase transitions}
+%%====================================================
+%
+%In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point. 
+%In a finite basis set, this critical point is model by a cluster of $\beta$ singularities. 
+%It is now well known that this phenomenon is a special case of a more general phenomenon. 
+%Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
+\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook}
+%In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter. 
+%In some cases the variation of a parameter can lead to abrupt changes at a critical point. 
+%These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
 \cite{Cejnar_2005,Cejnar_2007,Caprio_2008,Cejnar_2009,Sachdev_2011,Cejnar_2015,Cejnar_2016, Macek_2019,Cejnar_2020}
-A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter. \cite{Cejnar_2009, Sachdev_2011} 
-The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
-Otherwise, it is called continuous and of $m$th order (with $m \ge 2$) if the $m$th derivative is discontinuous. 
-A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives).
-
-The presence of an EP close to the real axis is characteristic of a sharp avoided crossing. 
-Yet, at such an avoided crossing, eigenstates change abruptly. 
-Although it is now well understood that EPs are closely related to QPTs, the link between the type of QPT (ground state or excited state, first or higher order) and EPs still need to be clarified. 
-One of the major obstacles that one faces in order to achieve this resides in the ability to compute the distribution of EPs. 
-The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions. 
-Hence, the design of specific methods are required to get information on the location of EPs. 
-Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
-More recently Stransky and coworkers proved that the distribution of EPs is characteristic of the QPT order. \cite{Stransky_2018} 
-In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
-They showed that, within the interacting boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases. 
-The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second orders, respectively) with respect to the number of particles.
-
-Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the interaction boson model from a QPT point of view. \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}
-The phase of the ensemble of $s$ and $d$ bosons is characterised by a dynamical symmetry. 
-When a parameter is continuously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase. 
-They showed that at this critical value of the parameter, the system undergoes a QPT. 
-For example, without interaction the ground state is the spherical phase (a condensate of $s$ bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of $s$ and $d$ bosons states.
-In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched.
+%A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter. \cite{Cejnar_2009, Sachdev_2011} 
+%The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
+%Otherwise, it is called continuous and of $m$th order (with $m \ge 2$) if the $m$th derivative is discontinuous. 
+%A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives). 
+%
+%The presence of an EP close to the real axis is characteristic of a sharp avoided crossing. 
+%Yet, at such an avoided crossing, eigenstates change abruptly. 
+%Although it is now well understood that EPs are closely related to QPTs, the link between the type of QPT (ground state or excited state, first or higher order) and EPs still need to be clarified. 
+%One of the major obstacles that one faces in order to achieve this resides in the ability to compute the distribution of EPs. 
+%The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions. 
+%Hence, the design of specific methods are required to get information on the location of EPs. 
+%Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
+%More recently Stransky and coworkers proved that the distribution of EPs is characteristic of the QPT order. \cite{Stransky_2018} 
+%In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
+%They showed that, within the interacting boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases. 
+%The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second orders, respectively) with respect to the number of particles.
+%
+%Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the interaction boson model from a QPT point of view. \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}
+%The phase of the ensemble of $s$ and $d$ bosons is characterised by a dynamical symmetry. 
+%When a parameter is continuously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase. 
+%They showed that at this critical value of the parameter, the system undergoes a QPT. 
+%For example, without interaction the ground state is the spherical phase (a condensate of $s$ bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of $s$ and $d$ bosons states.
+%In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched.
 \cite{SzaboBook}
-It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory. 
-Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT.
-
-Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities. 
-The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly. 
-However, the $\alpha$ singularities arise from large avoided crossings. 
-Thus, they cannot be connected to QPT. 
-The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states. 
-Those excited states have a non-negligible contribution to the exact FCI solution because they have (usually) the same spatial and spin symmetry as the ground state. 
-We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, \ie, to the multi-reference nature of the wave function thus to the static part of the correlation energy.
+%It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory. 
+%Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT. 
+%
+%Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities.
+%The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly. 
+%However, the $\alpha$ singularities arise from large avoided crossings. 
+%Thus, they cannot be connected to QPT. 
+%The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states. 
+%Those excited states have a non-negligible contribution to the exact FCI solution because they have (usually) the same spatial and spin symmetry as the ground state. 
+%We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, \ie, to the multi-reference nature of the wave function thus to the static part of the correlation energy.
 

### 2020-11-27 Manuscript/EPAWTFT.tex
forgotten references

@@
 with the magnitude of the imaginary component controlling the oscillations in the signs of the MP 
-term.\cite{Goodson_2000a,Goodson200b}
+term.\cite{Goodson_2000a,Goodson_2000b}
 In contrast, class B systems correspond to a dominant singularity on the negative real $\lambda$ axis representing
@@
 Note that, by construction, a quadratic approximant has only two branches which hampers the faithful description of more complicated singularity structures.
-As shown in Ref.~\onlinecite{Goodson_2000}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}
+As shown in Ref.~\onlinecite{Goodson_2000a}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}
 

### 2020-11-27 Manuscript/EPAWTFT.tex
review Hugh changes

@@
 % STILLINGER INTRODUCES THE CRITICAL POINT
-\hugh{%
 In the early 2000's, Stillinger reconsidered the mathematical origin behind the divergent series with odd-even
@@
 electron pairs and includes \ce{Ne}, \ce{HF}, \ce{F-}, and \ce{H2O}.\cite{Cremer_1996}
-Stillinger proposed that the divergence of these series occurs arise from a dominant singularity
+Stillinger proposed that the divergence of these series arise from a dominant singularity
 on the negative real $\lambda$ axis, corresponding to a multielectron autoionisation threshold.\cite{Stillinger_2000}
@@
 processes.\cite{Sergeev_2005}
-}
 
 % CLASSIFICATIONS BY GOODSOON AND SERGEEV
-\hugh{%
 To further develop the link between the critical point and types of MP convergence, Sergeev and Goodson investigated
-the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}.
+the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}
 They demonstrated that the dominant singularity in class A corresponds to a dominant EP with a positive real component, 
@@
 and ii) $\beta$ singularities which have very small imaginary parts.\cite{Goodson_2004,Sergeev_2006}
-}
 
 % RELATIONSHIP TO BASIS SET SIZE
-\hugh{%
 The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
@@
 This effect explains the origin of the divergence in the \ce{HF} molecule as the \ce{F} valence electrons jump to \ce{H} 
-for a sufficiently negative $\lambda$.\cite{Sergeev_2005}
+for a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
 Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
 divergences caused by the MP critical point.
-}
 
@@
 % RELATIONSHIP TO QUANTUM PHASE TRANSITION
-\hugh{%
 When a Hamiltonian is parametrised by a variable such as $\lambda$, the existence of abrupt changes in the 
@@
 \cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
-As an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis.
+As an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
 The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
@@
 However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
-basis set limit.\cite{Kais_2006}
+basis set limit in our case.\cite{Kais_2006}
 The MP critical point $\beta$ singularity in a finite basis must therefore be modelled by pairs of EPs
-that tend towards the real axis, exactly as described by Sergeev \etal.\cite{Sergeev_2005}
+that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
 In contrast, $\alpha$ singularities correspond to large avoided crossings that are indicative of low-lying excited
 states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
-}
 

### 2020-11-28 Manuscript/EPAWTFT.tex
some spell-checking

@@
 %=======================================
-\subsection{The M{\o}ller--Plesset Critical Point}
+\subsection{M{\o}ller--Plesset Critical Point}
 \label{sec:MP_critical_point}
@@
 electron pairs and includes \ce{Ne}, \ce{HF}, \ce{F-}, and \ce{H2O}.\cite{Cremer_1996}
-Stillinger proposed that the divergence of these series arise from a dominant singularity
+Stillinger proposed that these series diverge due to a dominant singularity
 on the negative real $\lambda$ axis, corresponding to a multielectron autoionisation threshold.\cite{Stillinger_2000}
-To understand Stillinger's argument, consider the paramterised MP Hamiltonian in the form
+To understand Stillinger's argument, consider the parametrised MP Hamiltonian in the form
 \begin{multline}
@@
 Coulomb interaction becomes attractive.
-There is therefore a critical value $\lc < 0$ where it becomes energetically favourable for the electrons 
+There is therefore a negative critical value $\lc$ where it becomes energetically favourable for the electrons 
 to dissociate and form a bound cluster at an infinite separation from the nuclei.\cite{Stillinger_2000}
@@
 the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}
-They demonstrated that the dominant singularity in class A corresponds to a dominant EP with a positive real component, 
-with the magnitude of the imaginary component controlling the oscillations in the signs of the MP 
-term.\cite{Goodson_2000a,Goodson_2000b}
+They demonstrated that the dominant singularity in class A systems corresponds to a dominant EP with a positive real component, 
+with the magnitude of the imaginary component controlling the oscillations in the signs of successive MP 
+terms.\cite{Goodson_2000a,Goodson_2000b}
 In contrast, class B systems correspond to a dominant singularity on the negative real $\lambda$ axis representing
@@
 The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
-and \ce{HF} molecule occured when diffuse basis functions were included.\cite{Olsen_1996}
+and \ce{HF} molecule occurred when diffuse basis functions were included.\cite{Olsen_1996}
 Clearly diffuse basis functions are required for the electrons to dissociate from the nuclei, and indeed using
@@
 Alternatively, Sergeev \etal\ demonstrated that the inclusion of a ``ghost'' atom also
-allows the formation of the critical point as the electrons form a bound cluster occuping the ghost atom orbitals.\cite{Sergeev_2005}
-This effect explains the origin of the divergence in the \ce{HF} molecule as the \ce{F} valence electrons jump to \ce{H} 
-for a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
+allows the formation of the critical point as the electrons form a bound cluster occupying the ghost atom orbitals.\cite{Sergeev_2005}
+This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to hydrogen at
+ a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
 Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
@@
 \cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
-As an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
+Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
 The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
-recognised a QPT within the perturbation theory approximation.
+recognised as a QPT within the perturbation theory approximation.
 However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
-basis set limit in our case.\cite{Kais_2006}
+basis set limit.\cite{Kais_2006}
 The MP critical point $\beta$ singularity in a finite basis must therefore be modelled by pairs of EPs

### 2020-11-28 Manuscript/EPAWTFT.tex
added small paragraph on singularities

@@
 We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
+
+\titou{Discussion around the different types of singularities in complex analysis.
+At a singular point, a function and/or its derivatives becomes infinite or undefined (hence non analytic).
+One very common type of singularities (belonging to the family of isolated singularities) are poles where the function behaves $1/(\lambda - \lambda_c)^n$ where $n \in \mathbb{N}^*$ is the order of the pole.
+Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts where the function ``jumps'' from one value to another.
+Yet another family of singularities are formed by critical points which lie on the real axis, have more complicated functional forms and where the nature of the function undergoes a sudden transition.
+}
 

### 2020-11-28 Manuscript/EPAWTFT.tex
added small paragraph on singularities

@@
 One very common type of singularities (belonging to the family of isolated singularities) are poles where the function behaves $1/(\lambda - \lambda_c)^n$ where $n \in \mathbb{N}^*$ is the order of the pole.
-Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts where the function ``jumps'' from one value to another.
+Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts which are lines or curves where the function ``jumps'' from one value to another.
 Yet another family of singularities are formed by critical points which lie on the real axis, have more complicated functional forms and where the nature of the function undergoes a sudden transition.

### 2020-11-29 Manuscript/EPAWTFT.tex
spell-checking

--- 2020-11-28 Manuscript/EPAWTFT.tex
@@
-\documentclass[aps,prb,reprint,noshowkeys,linenumbers,superscriptaddress]{revtex4-1}
+\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
 \usepackage{subcaption}
@@
 basis set limit.\cite{Kais_2006}
-The MP critical point $\beta$ singularity in a finite basis must therefore be modelled by pairs of EPs
+The MP critical point and corresponding $\beta$ singularities in a finite basis must therefore be modelled by pairs of EPs
 that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
@@
 %=======================================
-\subsection{Critical Point in the Hubbard Dimer}
-\label{sec:critical_point_hubbard}
+%\subsection{Critical Point in the Hubbard Dimer}
+%\label{sec:critical_point_hubbard}
 %=======================================

### 2020-11-29 Manuscript/EPAWTFT.tex

@@
 We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
+
+\titou{Discussion around the different types of singularities in complex analysis.
+At a singular point, a function and/or its derivatives becomes infinite or undefined (hence non analytic).
+One very common type of singularities (belonging to the family of isolated singularities) are poles where the function behaves $1/(\lambda - \lambda_c)^n$ where $n \in \mathbb{N}^*$ is the order of the pole.
+Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts which are lines or curves where the function ``jumps'' from one value to another.
+Yet another family of singularities are formed by critical points which lie on the real axis, have more complicated functional forms and where the nature of the function undergoes a sudden transition.
+}
 

### 2020-11-29 Manuscript/EPAWTFT.tex
Transferred RMP critical point discussion from notebook as skeleton.

@@
 \newcommand{\hugh}[1]{\textcolor{hughgreen}{#1}}
+\newcommand{\hughDraft}[1]{\textcolor{orange}{#1}}
 \newcommand{\trash}[1]{\textcolor{red}{\sout{#1}}}
@@
 %=======================================
-%\subsection{Critical Point in the Hubbard Dimer}
-%\label{sec:critical_point_hubbard}
+\subsection{Critical Points in the Hubbard Dimer}
+\label{sec:critical_point_hubbard}
 %=======================================
+
+%------------------------------------------------------------------%
+% Figure on the RMP critical point
+%------------------------------------------------------------------%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{rmp_critical_point}
+	\subcaption{\label{subfig:rmp_cp}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{rmp_critical_point_surf}
+	\subcaption{\label{subfig:rmp_cp_surf}}
+    \end{subfigure}
+	\caption{%
+    \hugh{RMP critical point in the Hubbard dimer.}
+	\label{fig:RMP_cp}}
+\end{figure*}
+%------------------------------------------------------------------%
+
+\hughDraft{%
+The simplified site basis of the Hubbard dimer makes explicitly modelling the ionisation continuum 
+impossible.
+To model the auto-ionisation in the Hubbard dimer, we need to turn one of the sites into a ghost atom that will act as
+a destination for ionised electrons. We do this by considering an asymmetric Hubbard dimer where the "atomic" site
+has a negative diagonal term in the one-electron Hamiltonian, representing the nuclear attraction. This term is already
+encoded in the Initialisation section such that the core Hamiltonian is
+To model the doubly-occupied atom, we can define our reference HF state as the configuration with $\theta = 0$ and energy
+\begin{equation}
+    \frac{1}{2} (2 U - 4 \epsilon)
+\end{equation}
+The RMP Hamiltonian then becomes
+...
+}
+
+\hughDraft{%
+Now let's think about the physics of the problem...
+For the ghost site to truly represent ionised electrons, we need the hopping term to vanish (or become very small).
+$U$ controls the strength of the HF repulsive potential. A stronger repulsion will encourage the electrons to be forced
+away from the "atomic" site at a less negative value of $\lambda$.
+$\epsilon$ controls the strength of attraction to the atom. A stronger attraction to the nucleus will mean that the electrons
+are more tightly bound to the atom and a more negative $\lambda$ will be needed for auto-ionisation.
+We therefore expect that the position of the RMP critical point will be controlled by the ratio $\epsilon / U$, with smaller ratios
+making ionisation occur closer to $\lambda$ origin, and making the divergence in these cases more likely.
+}
+
+\hughDraft{%
+Taking the exact case with $t=0$, the RMP energies becomes
+\begin{subequations}
+\begin{align}
+    E_{-} &= 2U - 2 \epsilon - U \lambda
+    \\
+    E_{\text{S}} &= U - \epsilon - U \lambda
+    \\ 
+    E_{+} &= U \lambda 
+\end{align}
+\end{subequations}
+By comparison with Fig.~\ref{fig:RMP_cp}, the critical point can be identified as by solving $E_{-} = E_{+}$,
+giving 
+\begin{equation}
+\lc = 1 - \epsilon / U.
+\end{equation}
+Thus, as expected, the critical point lies on the real axis and moves closer to the origin for larger 
+$U / \epsilon$. 
+}
+
+\hughDraft{%
+The position of the critical point is controlled by the ratio $\epsilon / U$.
+If the magnitude of the ratio becomes greater than one, then the series diverges.
+We can interpret large $U$ as strong electron repulsion effects in electron dense molecules, 
+such as \ce{F-}. A small $\epsilon$ is also likely to correspond to 
+strong nuclear screening by the core and valence electrons. Both of these factors are 
+common in atoms on the right-hand-side of periodic table, 
+\eg\ \ce{F}, \ce{O}, \ce{Ne}, etc, as well as negatively-charged species, and so we recover the
+class $\beta$ system classification.
+}
+
+\hughDraft{%
+In practical calculations, one considers the perturbation energy in a finite basis and the critical point is modelled
+as a cluster of branch points close to the real axis. While we cannot change the size of our basis, we can adjust
+the extent to which the second site behaves as a ghost by making the hopping term larger.
+When $t$ is (slightly) non-zero, our modelled critical point becomes an EP point close to the real axis with a sharp
+associated avoided crossing for real $\lambda$. If $t$ becomes larger, this avoided crossing becomes less sharp and the EPs
+move away from the real axis. This mirrors the discussion of EPs approaching the real axis in the exact basis.
+This effect is shown by the dashed lines in Fig.~\ref{fig:RMP_cp}.
+}
 

### 2020-11-29 Manuscript/EPAWTFT.tex
modif singularities

@@
 Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts which are lines or curves where the function ``jumps'' from one value to another.
-Yet another family of singularities are formed by critical points which lie on the real axis, have more complicated functional forms and where the nature of the function undergoes a sudden transition.
+Critical points are singularities which lie on the real axis and where the nature of the function undergoes a sudden transition. 
+However, these do not clearly belong to a given class of singularities and they cannot be rigorously classified as they have more complicated functional forms.
 }

### 2020-11-30 Manuscript/EPAWTFT.tex
RMP Hamiltonian for Hugh
Added RMP critical point discussion... UMP to come

--- 2020-11-29 Manuscript/EPAWTFT.tex
@@
 \end{align}
+\label{eq:RHF_orbs}
 \end{subequations}
@@
 
+%------------------------------------------------------------------%
+% Figure on the RMP critical point
+%------------------------------------------------------------------%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{rmp_critical_point}
+	\subcaption{\label{subfig:rmp_cp}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{rmp_critical_point_surf}
+	\subcaption{\label{subfig:rmp_cp_surf}}
+    \end{subfigure}
+	\caption{%
+    \hugh{Modelling the RMP critical point using the asymmetric Hubbard dimer.
+        (\subref{subfig:rmp_cp}) Exact critical points with $t=0$ occur on the negative real $\lambda$ axis (dashed).
+        (\subref{subfig:rmp_cp_surf}) Modelling a finite basis using $t=0.1$ yields complex-conjugate EPs close to the
+        real axis, giving a sharp avoided crossing on the real axis (solid).
+    }
+	\label{fig:RMP_cp}}
+\end{figure*}
+%------------------------------------------------------------------%
+
 % RELATIONSHIP TO BASIS SET SIZE
@@
 %=======================================
-%\subsection{Critical Point in the Hubbard Dimer}
-%\label{sec:critical_point_hubbard}
+\subsection{Critical Points in the Hubbard Dimer}
+\label{sec:critical_point_hubbard}
 %=======================================
+
+% INTRODUCING THE MODEL
+\hugh{%
+The simplified site basis of the Hubbard dimer makes explicilty modelling the ionisation continuum impossible.
+Instead, we can use an asymmetric Hubbard dimer to consider one site as a ``ghost atom'' that acts as a 
+destination for ionised electrons.
+In this asymmetric model, we introduce a one-electron potential $-\epsilon$ on the left site to 
+represent the attraction between the electrons and the model ``atomic'' nucleus, where we define $\epsilon > 0$.
+%The exact Hamiltonian [Eq.~\eqref{eq:H_FCI}] then becomes
+%\begin{equation}
+%\label{eq:H_FCI_Asymm}
+%\bH = 
+%\begin{pmatrix}
+%	U-2\epsilon & -t        & -t        &  0 \\
+%   -t           & -\epsilon &  0        & -t \\
+%   -t           &  0        & -\epsilon & -t \\
+%    0           & -t        & -t        &  U \\
+%\end{pmatrix}.
+%\end{equation}
+The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
+orbitals [Eq.~\eqref{eq:RHF_orbs}] with 
+\begin{equation}
+    \theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0.
+\end{equation}
+%and energy
+%\begin{equation}
+%   E_\text{HF}(0, 0) = \frac{1}{2} (2 U - 4 \epsilon).
+%\end{equation}
+With this representation, the parametrised RMP Hamiltonian becomes
+\begin{widetext}
+\begin{equation}
+\label{eq:H_RMP}
+\bH_\text{RMP}\qty(\lambda) = 
+\begin{pmatrix}
+    2(U-\epsilon) - \lambda U &	-\lambda t				 &	-\lambda t	            &	0	        \\
+    -\lambda t				  &	(U-\epsilon) - \lambda U &	0		                &	-\lambda t	\\
+    -\lambda t				  &	0			             &	(U-\epsilon) -\lambda U	&	-\lambda t	\\
+    0 				          &	-\lambda t 	 			 &	-\lambda t              &	\lambda U	\\
+\end{pmatrix}.
+\end{equation}
+\end{widetext}
+}
+
+% DERIVING BEHAVIOUR OF THE CRITICAL SITE
+\hugh{%
+For the ghost site to perfectly represent ionised electrons, the hopping term between the two sites must vanish with $t=0$.
+This limit corresponds to the dissociative regime in the asymmetric Hubbard dimer (see Ref.~\ref{Carrascal_2018}), 
+and the RMP energies become
+\begin{subequations}
+\begin{align}
+    E_{-} &= 2U - 2 \epsilon - U \lambda
+    \\
+    E_{\text{S}} &= U - \epsilon - U \lambda
+    \\ 
+    E_{+} &= U \lambda,
+\end{align}
+\end{subequations}
+as shown in Fig.~\ref{subfig:rmp_cp} (dashed lines).
+The RMP critical point then corresponds to the intersection $E_{-} = E_{+}$, giving the critical $\lambda$ value
+\begin{equation}
+    \lc = 1 - \frac{\epsilon}{U}. 
+\end{equation}
+Clearly the radius of convergence $\rc = \abs{\lc}$ is controlled directly by the ratio $\epsilon / U$, 
+with a convergent RMP series occurring for $\epsilon > 2 U$.
+The on-site repulsion $U$ controls the strength of the HF potential localised around the ``atomic site'', with a
+stronger repulsion encouraging the electrons to be ionised at a less negative value of $\lambda$. 
+Large $U$ can be physically interpreted as strong electron repulsion effects in electron dense molecules. 
+In contrast, smaller $\epsilon$ gives a weaker attraction to the atomic site, 
+representing strong screening of the nuclear attraction by core and valence electrons, 
+and again a less negative $\lambda$ is required for ionisation to occur.
+Both of these factors are common in atoms on the right-hand side of the periodic table, \eg\ \ce{F},
+\ce{O}, \ce{Ne}, and thus molecules containing these atoms are often class $\beta$ systems with
+a divergent RMP series due to the MP critical point.
+}
+
+% EXACT VERSUS APPROXIMATE
+\hugh{%
+The critical point in the exact case $t=0$ lies on the real $\lambda$ axis, mirroring the behaviour of a quantum
+phase transition.\cite{Kais_2006}
+However, in practical calculations performed with a finite basis set, the critical point is modelled as a cluster
+of branch points close to the real axis.
+The use of a finite basis can be modelled in the asymmetric dimer by making the second site a less
+idealised destination for the ionised electrons with a non-zero hopping term $t$.
+Taking the small value $t=0.1$ (Fig.~\ref{subfig:rmp_cp}: solid lines), the critical point becomes a
+sharp avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
+In the limit $t \rightarrow 0$, these EPs approach the real axis, mirroring Sergeev's discussion on finite basis
+set representations of the MP critical point.\cite{Sergeev_2006}
+}
 

### 2020-11-30 Manuscript/EPAWTFT.tex
updated some figures

@@
 UHF wave function, creating the first direct link between spin-contamination and slow UMP convergence.\cite{Gill_1988}
+
+% LEPETIT CHAT
 Lepetit \etal\ later analysed the difference between perturbation convergence using the unrestricted MP 
@@
 
+% RELATIONSHIP TO BASIS SET SIZE
+The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
+and \ce{HF} molecule occurred when diffuse basis functions were included.\cite{Olsen_1996}
+Clearly diffuse basis functions are required for the electrons to dissociate from the nuclei, and indeed using
+only compact basis functions causes the critical point to disappear.
+While a finite basis can only predict complex-conjugate branch point singularities, the critical point is modelled
+by a cluster of sharp avoided crossings between the ground state and high-lying excited states.\cite{Sergeev_2005}
+Alternatively, Sergeev \etal\ demonstrated that the inclusion of a ``ghost'' atom also
+allows the formation of the critical point as the electrons form a bound cluster occupying the ghost atom orbitals.\cite{Sergeev_2005}
+This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to hydrogen at
+ a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
+Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
+divergences caused by the MP critical point.
+
+% BASIS SET DEPENDENCE (INCLUDE?)
+%Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
+%On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
+%According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
+%This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
+%To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
+
+%In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
+\cite{Olsen_1996,Olsen_2000,Olsen_2019}
+%Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
+%They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
+
+%This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis. 
+%However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
+%Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
+%This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
+
+% RELATIONSHIP TO QUANTUM PHASE TRANSITION
+When a Hamiltonian is parametrised by a variable such as $\lambda$, the existence of abrupt changes in the 
+eigenstates as a function of $\lambda$ indicate the presence of a zero-temperature quantum phase transition (QPT).%
+\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
+Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
+The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
+Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
+recognised as a QPT within the perturbation theory approximation.
+However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
+basis set limit.\cite{Kais_2006}
+The MP critical point and corresponding $\beta$ singularities in a finite basis must therefore be modelled by pairs of EPs
+that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
+In contrast, $\alpha$ singularities correspond to large avoided crossings that are indicative of low-lying excited
+states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
+
+%=======================================
+\subsection{Critical Points in the Hubbard Dimer}
+\label{sec:critical_point_hubbard}
+%=======================================
+
 %------------------------------------------------------------------%
@@
 
-% RELATIONSHIP TO BASIS SET SIZE
-The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
-and \ce{HF} molecule occurred when diffuse basis functions were included.\cite{Olsen_1996}
-Clearly diffuse basis functions are required for the electrons to dissociate from the nuclei, and indeed using
-only compact basis functions causes the critical point to disappear.
-While a finite basis can only predict complex-conjugate branch point singularities, the critical point is modelled
-by a cluster of sharp avoided crossings between the ground state and high-lying excited states.\cite{Sergeev_2005}
-Alternatively, Sergeev \etal\ demonstrated that the inclusion of a ``ghost'' atom also
-allows the formation of the critical point as the electrons form a bound cluster occupying the ghost atom orbitals.\cite{Sergeev_2005}
-This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to hydrogen at
- a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
-Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
-divergences caused by the MP critical point.
-
-% BASIS SET DEPENDENCE (INCLUDE?)
-%Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
-%On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
-%According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
-%This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
-%To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
-
-%In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
-\cite{Olsen_1996,Olsen_2000,Olsen_2019}
-%Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-%They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
-
-%This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis. 
-%However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-%Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-%This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
-
-% RELATIONSHIP TO QUANTUM PHASE TRANSITION
-When a Hamiltonian is parametrised by a variable such as $\lambda$, the existence of abrupt changes in the 
-eigenstates as a function of $\lambda$ indicate the presence of a zero-temperature quantum phase transition (QPT).%
-\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
-Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
-The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
-Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
-recognised as a QPT within the perturbation theory approximation.
-However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
-basis set limit.\cite{Kais_2006}
-The MP critical point and corresponding $\beta$ singularities in a finite basis must therefore be modelled by pairs of EPs
-that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
-In contrast, $\alpha$ singularities correspond to large avoided crossings that are indicative of low-lying excited
-states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
-
-%=======================================
-\subsection{Critical Points in the Hubbard Dimer}
-\label{sec:critical_point_hubbard}
-%=======================================
-
 % INTRODUCING THE MODEL
@@
 set representations of the MP critical point.\cite{Sergeev_2006}
+}
+
+%------------------------------------------------------------------%
+% Figure on the UMP critical point
+%------------------------------------------------------------------%
+\begin{figure*}[t]
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{ump_critical_point}
+	\subcaption{\label{subfig:ump_cp}}
+    \end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\includegraphics[height=0.65\textwidth]{ump_ep_to_cp}
+	\subcaption{\label{subfig:ump_ep_to_cp}}
+    \end{subfigure}
+	\caption{%
+    \hugh{Modelling the RMP critical point using the asymmetric Hubbard dimer.
+        (\subref{subfig:rmp_cp}) Exact critical points with $t=0$ occur on the negative real $\lambda$ axis (dashed).
+        (\subref{subfig:rmp_cp_surf}) Modelling a finite basis using $t=0.1$ yields complex-conjugate EPs close to the
+        real axis, giving a sharp avoided crossing on the real axis (solid).
+    }
+	\label{fig:RMP_cp}}
+\end{figure*}
+%------------------------------------------------------------------%
+
+% RELATIONSHIP BETWEEN QPT AND UMP
+\hughDraft{%
+The ground-state EP observed in the UMP series also has a small imaginary part and falls close to the real axis. 
+As the correlation strength increases, this EP moves closer to the real axis and closer to the radius of convergence at 
+$\lambda = 1$. So can we understand this using the arguments related to the critical point?
+Closed-shell case:
+The work by Stillinger builds an argument around the HF potential $v_{\text{HF}}$ which, by itself, 
+is repulsive and concentrated around the 
+occupied orbitals. As $\lambda$ becomes increasingly positive along the real axis, this HF potential 
+becomes attractive for $\lambda > 1$.
+However, the explicit two-electron becomes increasingly repulsive for larger positive $\lambda$, 
+until eventually single electrons are successively expelled from the molecule.
+Effect of symmetry-breaking:
+Things become more subtle for the symmetry-broken case because we must now consider the $\alpha$ and $\beta$ HF potentials.
+When UHF symmetry breaking occurs in the Hubbard dimer, with the $\alpha$ electron localising on the left site, 
+the $\alpha$ HF potential
+will then be a repulsive interaction localised around the $\beta$ electron, so on the right site. 
+The same is true for the $\beta$ HF potential.
+Therefore, as $\lambda$ becomes greater than 1 and the HF potentials become attractive, 
+there is a driving force for the $\alpha$ and $\beta$.
+electrons to swap sites. If both electrons swap at the same time, then we get a double excitation. Therefore, we expect an 
+avoided crossing as $\lambda$ is increased beyond 1. 
+The "sharpness" of this avoided crossing is controlled by the strength of the electron-electron repulsion... see below.
+}
+
+\hughDraft{%
+For small $U/t$, the HF potentials will be weak and the electrons will slowly delocalise over 
+both sites as $\lambda$ increases. The UHF reference itself already has some degree of delocalisation over 
+both sites as we are only just beyond the CFP. This leads to a
+"shallow" avoided crossing, and the corresponding EPs corresponding with have non-zero imaginary parts. 
+At larger $U/t$, the HF potentials will becomes increasingly repulsive and the "swapping" driving force will become stronger. 
+Furthermore, the strong on-site repulsion will make delocalisation over both sites increasingly unfavourable. 
+We therefore see that the electrons swap sites almost instantaneously as $\lambda$ passes through 1, as this is the threshold point 
+where the HF potential becomes attractive. This very rapid change in the nature of the state corresponds to a "sharp" avoided
+crossing, with EPs close to the real axis.
+Note that, although this appears to be an avoided crossing with the first-excited state, 
+by the time we have reached $\lambda \approx 1$,
+we are beyond the excited-state avoided crossing and thus the first-excited state qualitatively corresponds to a double
+excitation from the reference. This matches our expectation of both electrons swapping sites.
+Okay we can't actually do $U/t = \infty$, but we can make it very large. With such a strong attractive HF potential and such strong
+on-site repulsion, the electrons swapping process will occur exactly at $\lambda=1$. In this limit, the change is so sudden that it
+now corresponds to a QPT in the perturbation approximation, and again the EPs fall on the real axis.
+}
+
+\hughDraft{%
+By applying the separation of the Hamiltionian proposed by Stillinger, we have been able to rationalise why the UMP ground-state
+occurs so close to radius of convergence and increasingly close to the real axis for large $U/t$. The key feature here is the fact that the
+HF potential is different for the $\alpha$ and $\beta$ electrons, and by extension the potential felt by 
+an electron is not strictly localised around
+that electrons orbitals. This is completely different to the symmetric structure in the closed-shell case. Because of these different 
+potentials, there can be a large driving force for spatial rearrangement occurring as soon as the HF potential becomes positive 
+(at $\lambda=1$). 
+This sudden change in electron distribution is made more extreme if the HF potential and electron repulsion dominate over the 
+one-electron terms, which also corresponds to the regime of strong wave function symmetry breaking. 
+We have therefore provided a physical motivation behind why this EP can behave like a QPT for strong symmetry breaking. 
+This supports the conclusions in Antoine's report that the symmetry-broken EP behaves as a class $\beta$ singularity.
 }

### 2020-11-30 Manuscript/EPAWTFT.tex
Added discussion on UMP relationship to critical point

--- 2020-11-30 Manuscript/EPAWTFT.tex
@@
 
+% Making life easier
 \newcommand{\Lup}{\mathcal{L}^{\uparrow}}
@@
 \newcommand{\Rsi}{\mathcal{R}^{\sigma}}
+\newcommand{\vhf}{v_{\text{HF}}}
 
@@
 \subsection{Spin-Contamination in the Hubbard Dimer}
+\label{sec:spin_cont}
 %==========================================%
@@
 set representations of the MP critical point.\cite{Sergeev_2006}
+}
+
+%------------------------------------------------------------------%
+% Figure on the UMP critical point
+%------------------------------------------------------------------%
+\begin{figure*}[t]
+\begin{subfigure}{0.49\textwidth}
+\includegraphics[height=0.65\textwidth]{ump_critical_point}
+\subcaption{\label{subfig:ump_cp}}
+\end{subfigure}
+\begin{subfigure}{0.49\textwidth}
+\includegraphics[height=0.65\textwidth]{ump_ep_to_cp}
+\subcaption{\label{subfig:ump_ep_to_cp}}
+\end{subfigure}
+\caption{%
+\hugh{%
+    The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
+    (\subref{subfig:ump_cp}) As the $U/t$ increases, the avoided crossing on the real $\lambda$ axis
+    becomes increasingly sharp.
+    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs onto the real axis for $U/t \rightarrow \infty$
+    mirrors the formation of the RMP critical point and other QPTs in the infinite basis set limit.
+}
+\label{fig:UMP_cp}}
+
+\end{figure*}
+%------------------------------------------------------------------%
+
+% RELATIONSHIP BETWEEN QPT AND UMP
+\hugh{%
+In Section~\ref{sec:spin_cont} we showed that the slow convergence of the UMP series for the strongly correlated
+Hubbard dimer was due to a complex-conjguate pair of  EPs just outside the radius of convergence.
+These EPs have positive real components and small imaginary components (Fig.~\ref{fig:UMP}), suggesting a potential 
+connection to MP critical points and QPTs.
+For $\lambda>1$, the HF potential becomes an attractive component in Stillinger's 
+Hamiltonian [Eq.~\eqref{eq:HamiltonianStillinger}], while the explicit electron-electron interaction
+becomes increasingly repulsive.
+Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
+points were the two-electron repulsion overcomes the attractive HF potential and an electron
+are successively expelled from the molecule.\cite{Sergeev_2006}
+}
+
+\hugh{%
+Symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
+Consider the reference UHF solution where the spin-up and spin-down electrons are localised on the left and
+right sites respectively.  
+The spin-up HF potential will then be a repulsive interaction from the spin-down electron 
+density that is centred around the right site (and vice-versa).
+As $\lambda$ becomes greater than 1 and the HF potentials become attractive, there will be a sudden
+driving force for the electrons to swap sites.
+This swapping process can also be represented as a double excitation, and thus an avoided crossing will occur
+for $\lambda \geq 1$ (Fig.~\ref{subfig:ump_cp}).
+Note that, although this appears to be an avoided crossing between the ground and first-excited state, 
+the earlier excited-state avoided crossing means that the first-excited state qualitatively 
+represents the double excitation for $\lambda > 0.5.$
+}
+
+% SHARPNESS AND QPT
+\hugh{%
+The ``sharpness'' of the avoided crossing is controlled by the correlation strength $U/t$.
+For small $U/t$, the HF potentials will be weak and the electrons will delocalise over the two sites,
+both in the UHF reference and as $\lambda$ increases.
+This delocalisataion dampens the electron swapping process and leads to a ``shallow'' avoided crossing
+that corresponds to EPs with non-zero imaginary components (solid lines in Fig.~\ref{subfig:ump_cp}).
+As $U/t$ becomes larger, the HF potentials become stronger and the on-site repulsion dominates the hopping
+term to make electron delocalisation less favourable.
+These effects create a stronger driving force for the electrons to swap sites until eventually this swapping
+occurs exactly at $\lambda = 1$.
+In this limit, the ground-state EPs approach the real axis (Fig.~\ref{subfig:ump_ep_to_cp}) and the avoided 
+crossing creates a gradient discontinuity in the ground-state energy (dashed lines in Fig.~\ref{subfig:ump_cp}).
+We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes becomes
+a new type of MP critical and represents a QPT in the perturbation approximation. 
+Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
+radius of convergence (see Fig.~\ref{fig:RadConv}).
 }

### 2020-11-30 Manuscript/EPAWTFT.tex
fixed my axisvi EPAWTFT.tex
changed notation to lambda_EP not lambda_c

@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[height=0.65\textwidth]{ump_critical_point}
+    \includegraphics[height=0.65\textwidth,trim={0pt 5pt 0pt 15pt}, clip]{ump_critical_point}
 \subcaption{\label{subfig:ump_cp}}
@@
     becomes increasingly sharp.
-    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs onto the real axis for $U/t \rightarrow \infty$
+    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs at $\lep$ onto the real axis for $U/t \rightarrow \infty$
     mirrors the formation of the RMP critical point and other QPTs in the infinite basis set limit.

### 2020-11-30 Manuscript/EPAWTFT.tex
reviewing Hugh asym Hubbard example

@@
 
-To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t\rightarrow \lambda t$ to give the parameterised Hamiltonian $\hH(\lambda)$.
+To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t \to \lambda t$ to give the parameterised Hamiltonian $\hH(\lambda)$.
 When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) (eigen)energies
@@
 be considered as a perturbation from the core Hamiltonian \eqref{eq:Hcore} by introducing the
-transformation $U \rightarrow \lambda\, U$, giving the parametrised Fock operator 
+transformation $U \to \lambda\, U$, giving the parametrised Fock operator 
 \begin{equation}
@@
 Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
-of $U/t$, reaching the limiting value of $1/2$ for $U/t \rightarrow \infty$, and thus the 
+of $U/t$, reaching the limiting value of $1/2$ for $U/t \to \infty$, and thus the 
 excited-state UMP series will always diverge.
@@
 	\caption{%
-    \hugh{Modelling the RMP critical point using the asymmetric Hubbard dimer.
+		Modelling the RMP critical point using the asymmetric Hubbard dimer.
 		(\subref{subfig:rmp_cp}) Exact critical points with $t=0$ occur on the negative real $\lambda$ axis (dashed).
@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
-    }
 	\label{fig:RMP_cp}}
@@
 % INTRODUCING THE MODEL
-\hugh{%
 The simplified site basis of the Hubbard dimer makes explicilty modelling the ionisation continuum impossible.
-Instead, we can use an asymmetric Hubbard dimer to consider one site as a ``ghost atom'' that acts as a 
+Instead, we can use an asymmetric Hubbard dimer \cite{Carrascal_2015,Carrascal_2018} to consider one site as a ``ghost atom'' that acts as a 
 destination for ionised electrons.
 In this asymmetric model, we introduce a one-electron potential $-\epsilon$ on the left site to 
-represent the attraction between the electrons and the model ``atomic'' nucleus, where we define $\epsilon > 0$.
+represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
 %The exact Hamiltonian [Eq.~\eqref{eq:H_FCI}] then becomes
@@
 The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
-orbitals [Eq.~\eqref{eq:RHF_orbs}] with 
-\begin{equation}
-    \theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0.
-\end{equation}
+orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$.
 %and energy
@@
 \end{widetext}
-}
+\titou{Shall we change the symbol $\bH_\text{RMP}\qty(\lambda)$ to avoid confusion? Maybe $\Tilde{\bH}_\text{RMP}\qty(\lambda)$?}
 
 % DERIVING BEHAVIOUR OF THE CRITICAL SITE
-\hugh{%
 For the ghost site to perfectly represent ionised electrons, the hopping term between the two sites must vanish with $t=0$.
-This limit corresponds to the dissociative regime in the asymmetric Hubbard dimer (see Ref.~\ref{Carrascal_2018}), 
+This limit corresponds to the dissociative regime in the asymmetric Hubbard dimer as discussed in Ref.~\onlinecite{Carrascal_2018}, 
 and the RMP energies become
@@
 \begin{align}
-    E_{-} &= 2U - 2 \epsilon - U \lambda
+    E_{-} &= 2U - 2 \epsilon - U \lambda,
     \\
-    E_{\text{S}} &= U - \epsilon - U \lambda
+    E_{\text{S}} &= U - \epsilon - U \lambda,
     \\ 
@@
 \ce{O}, \ce{Ne}, and thus molecules containing these atoms are often class $\beta$ systems with
-a divergent RMP series due to the MP critical point.
-}
+a divergent RMP series due to the MP critical point. \cite{Goodson_2004,Sergeev_2006}
 
 % EXACT VERSUS APPROXIMATE
-\hugh{%
-The critical point in the exact case $t=0$ lies on the real $\lambda$ axis, mirroring the behaviour of a quantum
-phase transition.\cite{Kais_2006}
+The critical point in the exact case $t=0$ lies on the \titou{negative} real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: dashed lines), 
+mirroring the behaviour of a quantum phase transition.\cite{Kais_2006}
 However, in practical calculations performed with a finite basis set, the critical point is modelled as a cluster
@@
 The use of a finite basis can be modelled in the asymmetric dimer by making the second site a less
-idealised destination for the ionised electrons with a non-zero hopping term $t$.
-Taking the small value $t=0.1$ (Fig.~\ref{subfig:rmp_cp}: solid lines), the critical point becomes a
+idealised destination for the ionised electrons with a non-zero (yet small) hopping term $t$.
+Taking the value $t=0.1$ (Fig.~\ref{subfig:rmp_cp}: solid lines), the critical point becomes a
 sharp avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
-In the limit $t \rightarrow 0$, these EPs approach the real axis, mirroring Sergeev's discussion on finite basis
+In the limit $t \to 0$, these EPs approach the real axis, mirroring Sergeev's discussion on finite basis
 set representations of the MP critical point.\cite{Sergeev_2006}
-}
 
@@
 \caption{%
-\hugh{%
     The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
-    (\subref{subfig:ump_cp}) As the $U/t$ increases, the avoided crossing on the real $\lambda$ axis
+    (\subref{subfig:ump_cp}) As $U/t$ increases, the avoided crossing on the real $\lambda$ axis
     becomes increasingly sharp.
-    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs at $\lep$ onto the real axis for $U/t \rightarrow \infty$
-    mirrors the formation of the RMP critical point and other QPTs in the infinite basis set limit.
-}
+    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs at $\lep$ onto the real axis for $U/t \to \infty$
+    mirrors the formation of the RMP critical point and other QPTs in the complete basis set limit.
 \label{fig:UMP_cp}}
@@
 % RELATIONSHIP BETWEEN QPT AND UMP
-\hugh{%
-In Section~\ref{sec:spin_cont} we showed that the slow convergence of the UMP series for the strongly correlated
-Hubbard dimer was due to a complex-conjguate pair of  EPs just outside the radius of convergence.
+In Sec.~\ref{sec:spin_cont} we showed that the slow convergence of the UMP series for the strongly correlated
+Hubbard dimer was due to a complex-conjugate pair of EPs just outside the radius of convergence.
 These EPs have positive real components and small imaginary components (Fig.~\ref{fig:UMP}), suggesting a potential 
-connection to MP critical points and QPTs.
+connection to MP critical points and QPTs (see Sec.~\ref{sec:MP_critical_point}).
 For $\lambda>1$, the HF potential becomes an attractive component in Stillinger's 
-Hamiltonian [Eq.~\eqref{eq:HamiltonianStillinger}], while the explicit electron-electron interaction
+Hamiltonian displayed in Eq.~\eqref{eq:HamiltonianStillinger}, while the explicit electron-electron interaction
 becomes increasingly repulsive.
 Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
-points were the two-electron repulsion overcomes the attractive HF potential and an electron
+points where the two-electron repulsion overcomes the attractive HF potential and an electron
 are successively expelled from the molecule.\cite{Sergeev_2006}
-}
-
-\hugh{%
+
 Symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
@@
 represents the double excitation for $\lambda > 0.5.$
-}
 
 % SHARPNESS AND QPT
-\hugh{%
 The ``sharpness'' of the avoided crossing is controlled by the correlation strength $U/t$.
@@
 both in the UHF reference and as $\lambda$ increases.
-This delocalisataion dampens the electron swapping process and leads to a ``shallow'' avoided crossing
+This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing
 that corresponds to EPs with non-zero imaginary components (solid lines in Fig.~\ref{subfig:ump_cp}).
@@
 crossing creates a gradient discontinuity in the ground-state energy (dashed lines in Fig.~\ref{subfig:ump_cp}).
-We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes becomes
+We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
 a new type of MP critical and represents a QPT in the perturbation approximation. 
@@
 radius of convergence (see Fig.~\ref{fig:RadConv}).
-}
 

### 2020-11-30 Manuscript/EPAWTFT.tex
minor edits

@@
 %\end{equation}
-With this representation, the parametrised RMP Hamiltonian becomes
+With this representation, the parametrised \hugh{atomic} RMP Hamiltonian becomes
 \begin{widetext}
@@
 \label{eq:H_RMP}
-\bH_\text{RMP}\qty(\lambda) = 
+\hugh{\bH_\text{atom}\qty(\lambda)} = 
 \begin{pmatrix}
@@
 Both of these factors are common in atoms on the right-hand side of the periodic table, \eg\ \ce{F},
-\ce{O}, \ce{Ne}, and thus molecules containing these atoms are often class $\beta$ systems with
+\ce{O}, \ce{Ne}.
+Molecules containing these atoms are therefore often class $\beta$ systems with
 a divergent RMP series due to the MP critical point. \cite{Goodson_2004,Sergeev_2006}
@@
 Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
-points where the two-electron repulsion overcomes the attractive HF potential and an electron
-are successively expelled from the molecule.\cite{Sergeev_2006}
-
-Symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
+points where the two-electron repulsion overcomes the attractive HF potential and a single electron dissociates from the molecule.\cite{Sergeev_2006}
+
+In contrast, symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
 Consider the reference UHF solution where the spin-up and spin-down electrons are localised on the left and
@@
 We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
-a new type of MP critical and represents a QPT in the perturbation approximation. 
+a new type of MP critical point and represents a QPT in the perturbation approximation. 
 Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 

### 2020-11-30 Manuscript/EPAWTFT.tex
comments for Hugh

--- 2020-11-30 Manuscript/EPAWTFT.tex
@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
+		\titou{vertical axe label wrong in b.}
 	\label{fig:RMP_cp}}
@@
 The simplified site basis of the Hubbard dimer makes explicilty modelling the ionisation continuum impossible.
-Instead, we can use an asymmetric Hubbard dimer \cite{Carrascal_2015,Carrascal_2018} to consider one site as a ``ghost atom'' that acts as a 
-destination for ionised electrons.
-In this asymmetric model, we introduce a one-electron potential $-\epsilon$ on the left site to 
+Instead, we can use an asymmetric version of the Hubbard dimer \cite{Carrascal_2015,Carrascal_2018} 
+where we consider one of the sites as a ``ghost atom'' that acts as a 
+destination for ionised electrons being originally localised on the other site.
+To mathematically model this scenario, in this asymmetric Hubbard dimer, we introduce a one-electron potential $-\epsilon$ on the left site to 
 represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
-%The exact Hamiltonian [Eq.~\eqref{eq:H_FCI}] then becomes
-%\begin{equation}
-%\label{eq:H_FCI_Asymm}
-%\bH = 
-%\begin{pmatrix}
-%	U-2\epsilon & -t        & -t        &  0 \\
-%   -t           & -\epsilon &  0        & -t \\
-%   -t           &  0        & -\epsilon & -t \\
-%    0           & -t        & -t        &  U \\
-%\end{pmatrix}.
-%\end{equation}
 The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
-orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$.
+orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$, which corresponds to strictly localise the two electrons on the left site.
 %and energy
@@
 \label{eq:H_RMP}
-\bH_\text{RMP}\qty(\lambda) = 
+\Tilde{\bH}_\text{RMP}\qty(\lambda) = 
 \begin{pmatrix}
@@
 \end{widetext}
-\titou{Shall we change the symbol $\bH_\text{RMP}\qty(\lambda)$ to avoid confusion? Maybe $\Tilde{\bH}_\text{RMP}\qty(\lambda)$?}
 
 % DERIVING BEHAVIOUR OF THE CRITICAL SITE
-For the ghost site to perfectly represent ionised electrons, the hopping term between the two sites must vanish with $t=0$.
+For the ghost site to perfectly represent ionised electrons, the hopping term between the two sites must vanish (\ie, $t=0$).
 This limit corresponds to the dissociative regime in the asymmetric Hubbard dimer as discussed in Ref.~\onlinecite{Carrascal_2018}, 
@@
 \begin{align}
-    E_{-} &= 2U - 2 \epsilon - U \lambda,
+    E_{-} &= 2(U - \epsilon) - \lambda U,
     \\
-    E_{\text{S}} &= U - \epsilon - U \lambda,
+    E_{\text{S}} &= (U - \epsilon) - \lambda U,
     \\ 
@@
 % RELATIONSHIP BETWEEN QPT AND UMP
+\titou{Returning to the symmetric Hubbard dimer?}
 In Sec.~\ref{sec:spin_cont} we showed that the slow convergence of the UMP series for the strongly correlated
 Hubbard dimer was due to a complex-conjugate pair of EPs just outside the radius of convergence.
-These EPs have positive real components and small imaginary components (Fig.~\ref{fig:UMP}), suggesting a potential 
+These EPs have positive real components and small imaginary components (see Fig.~\ref{fig:UMP}), suggesting a potential 
 connection to MP critical points and QPTs (see Sec.~\ref{sec:MP_critical_point}).
@@
 becomes increasingly repulsive.
-Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
+\titou{Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
 points where the two-electron repulsion overcomes the attractive HF potential and an electron
-are successively expelled from the molecule.\cite{Sergeev_2006}
+are successively expelled from the molecule.\cite{Sergeev_2006}}
+\titou{T2: I'd like to discuss that with you.}
 
 Symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
-Consider the reference UHF solution where the spin-up and spin-down electrons are localised on the left and
+Consider one of the two reference UHF solutions where the spin-up and spin-down electrons are localised on the left and
 right sites respectively.  
@@
 for $\lambda \geq 1$ (Fig.~\ref{subfig:ump_cp}).
-Note that, although this appears to be an avoided crossing between the ground and first-excited state, 
+\titou{Note that, although this appears to be an avoided crossing between the ground and first-excited state, 
 the earlier excited-state avoided crossing means that the first-excited state qualitatively 
-represents the double excitation for $\lambda > 0.5.$
+represents the double excitation for $\lambda > 0.5.$}
+\titou{T2: I find it hard to understand. I'd like to discuss this as well.}
 
@@
 term to make electron delocalisation less favourable.
+\titou{In other words, the electron localises on each site forming a so-called Wigner crystal.
+T2: is it worth saying again?}
 These effects create a stronger driving force for the electrons to swap sites until eventually this swapping
@@
 We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
-a new type of MP critical and represents a QPT in the perturbation approximation. 
+a new type of MP critical point \titou{and represents a QPT in the perturbation approximation}.
+\titou{T2: what do you mean by this?} 
 Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 

### 2020-11-30 Manuscript/EPAWTFT.tex

@@
 \label{eq:H_RMP}
-\Tilde{\bH}_\text{RMP}\qty(\lambda) = 
+\hugh{\bH_\text{atom}\qty(\lambda)} = 
 \begin{pmatrix}
@@
 \titou{Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
-points where the two-electron repulsion overcomes the attractive HF potential and an electron
-are successively expelled from the molecule.\cite{Sergeev_2006}}
+points where the two-electron repulsion overcomes the attractive HF potential 
+and a single electron dissociates from the molecule.\cite{Sergeev_2006}}
 \titou{T2: I'd like to discuss that with you.}
 
-Symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
-Consider one of the two reference UHF solutions where the spin-up and spin-down electrons are localised on the left and
-right sites respectively.  
+In contrast, symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
+Consider one of the two reference UHF solutions where the spin-up and spin-down electrons are localised on the left and right sites respectively. 
 The spin-up HF potential will then be a repulsive interaction from the spin-down electron 

### 2020-12-01 Manuscript/EPAWTFT.tex
t2 comment on goodson
added new RMP critical point figures
morning modifications to MP critical points

@@
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
-recognised as a QPT within the perturbation theory approximation.
+recognised as a QPT \hugh{with respect to varying the perturbation parameter $\lambda$}.
 However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
@@
 \begin{figure*}[t]
-	\begin{subfigure}{0.49\textwidth}
-	\includegraphics[height=0.65\textwidth]{rmp_critical_point}
+	\begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{rmp_cp}	
 		\subcaption{\label{subfig:rmp_cp}}
     \end{subfigure}
-	\begin{subfigure}{0.49\textwidth}
-	\includegraphics[height=0.65\textwidth]{rmp_critical_point_surf}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{rmp_cp_surf}
 		\subcaption{\label{subfig:rmp_cp_surf}}
     \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{rmp_ep_to_cp}	
+		\subcaption{\label{subfig:rmp_ep_to_cp}}
+    \end{subfigure}
 	\caption{%
-		Modelling the RMP critical point using the asymmetric Hubbard dimer.
+		RMP critical point using the asymmetric Hubbard dimer with $\epsilon = 2.5 U$.
 		(\subref{subfig:rmp_cp}) Exact critical points with $t=0$ occur on the negative real $\lambda$ axis (dashed).
@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
-		\titou{vertical axe label wrong in b.}
+		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the exact limit $t \rightarrow 0$.
 	\label{fig:RMP_cp}}
@@
 destination for ionised electrons being originally localised on the other site.
-To mathematically model this scenario, in this asymmetric Hubbard dimer, we introduce a one-electron potential $-\epsilon$ on the left site to 
+To mathematically model this scenario in this asymmetric Hubbard dimer, we introduce a one-electron potential $-\epsilon$ on the left site to 
 represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
 The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
-orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$, which corresponds to strictly localise the two electrons on the left site.
+orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$, 
+which corresponds to strictly localising the two electrons on the left site.
 %and energy
@@
 %\end{equation}
-With this representation, the parametrised \hugh{atomic} RMP Hamiltonian becomes
+With this representation, the parametrised \hugh{asymmetric} RMP Hamiltonian becomes
 \begin{widetext}
@@
 \label{eq:H_RMP}
-\hugh{\bH_\text{atom}\qty(\lambda)} = 
+\hugh{\bH_\text{asym}\qty(\lambda)} = 
 \begin{pmatrix}
@@
 % EXACT VERSUS APPROXIMATE
-The critical point in the exact case $t=0$ lies on the \titou{negative} real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: dashed lines), 
+The critical point in the exact case $t=0$ lies on the negative real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: dashed lines), 
 mirroring the behaviour of a quantum phase transition.\cite{Kais_2006}
@@
 sharp avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
-In the limit $t \to 0$, these EPs approach the real axis, mirroring Sergeev's discussion on finite basis
+In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}),
+mirroring Sergeev's discussion on finite basis
 set representations of the MP critical point.\cite{Sergeev_2006}
@@
 \begin{figure*}[t]
-\begin{subfigure}{0.49\textwidth}
-    \includegraphics[height=0.65\textwidth,trim={0pt 5pt 0pt 15pt}, clip]{ump_critical_point}
+	\begin{subfigure}{0.32\textwidth}
+        \includegraphics[height=0.75\textwidth,trim={0pt 5pt -10pt 15pt},clip]{ump_cp}	
 		\subcaption{\label{subfig:ump_cp}}
     \end{subfigure}
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[height=0.65\textwidth]{ump_ep_to_cp}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{ump_cp_surf}
+		\subcaption{\label{subfig:ump_cp_surf}}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.75\textwidth]{ump_ep_to_cp}	
 		\subcaption{\label{subfig:ump_ep_to_cp}}
     \end{subfigure}
+%    \includegraphics[height=0.65\textwidth,trim={0pt 5pt 0pt 15pt}, clip]{ump_critical_point}
 \caption{%
@@
     becomes increasingly sharp.
-    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs at $\lep$ onto the real axis for $U/t \to \infty$
-    mirrors the formation of the RMP critical point and other QPTs in the complete basis set limit.
+    (\subref{subfig:ump_cp_surf}) Complex energy surfaces for $U = 5t$.
+    (\subref{subfig:ump_ep_to_cp}) Convergence of the EPs at $\lep$ onto the real axis for $U/t \to \infty$.
+    %mirrors the formation of the RMP critical point and other QPTs in the complete basis set limit.
 \label{fig:UMP_cp}}
@@
 % RELATIONSHIP BETWEEN QPT AND UMP
-\titou{Returning to the symmetric Hubbard dimer?}
-In Sec.~\ref{sec:spin_cont} we showed that the slow convergence of the UMP series for the strongly correlated
-Hubbard dimer was due to a complex-conjugate pair of EPs just outside the radius of convergence.
+Returning to the symmetric Hubbard dimer, we showed in Sec.~\ref{sec:spin_cont} that the slow
+convergence of the strongly correlated UMP series
+was due to a complex-conjugate pair of EPs just outside the radius of convergence.
 These EPs have positive real components and small imaginary components (see Fig.~\ref{fig:UMP}), suggesting a potential 
@@
 becomes increasingly repulsive.
-\titou{Critical points along the positive real $\lambda$ axis for closed-shell molecules then represent 
+Closed--shell critical points along the positive real $\lambda$ axis then represent 
 points where the two-electron repulsion overcomes the attractive HF potential 
-and a single electron dissociates from the molecule.\cite{Sergeev_2006}}
-\titou{T2: I'd like to discuss that with you.}
+and a single electron dissociates from the molecule (see Ref.~\onlinecite{Sergeev_2006})
 
@@
 for $\lambda \geq 1$ (Fig.~\ref{subfig:ump_cp}).
-\titou{Note that, although this appears to be an avoided crossing between the ground and first-excited state, 
-the earlier excited-state avoided crossing means that the first-excited state qualitatively 
-represents the double excitation for $\lambda > 0.5.$}
-\titou{T2: I find it hard to understand. I'd like to discuss this as well.}
+While this appears to be an avoided crossing between the ground and first-excited state, 
+the presence of an earlier excited-state avoided crossing means that the first-excited state qualitatively 
+represents the reference double excitation for $\lambda > 0.5.$
 
@@
 term to make electron delocalisation less favourable.
-\titou{In other words, the electron localises on each site forming a so-called Wigner crystal.
-T2: is it worth saying again?}
+In other words, the electrons localise on individual sites to form a Wigner crystal.
 These effects create a stronger driving force for the electrons to swap sites until eventually this swapping
@@
 We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
-a new type of MP critical point \titou{and represents a QPT in the perturbation approximation}.
-\titou{T2: what do you mean by this?} 
+a new type of MP critical point and \hugh{represents a QPT as the perturbation parameter $\lambda$ is varied.}
 Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
@@
 
+\titou{T2 will add a comment about Goodson's remark on the failure of low-order approximants when $\alpha$ and $\beta$ singularities are present.}
+
 %%%%%%%%%%%%%%%%%%%%

### 2020-12-01 Manuscript/EPAWTFT.tex
comment on confocal map

@@
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
-recognised as a QPT \hugh{with respect to varying the perturbation parameter $\lambda$}.
+recognised as a QPT with respect to varying the perturbation parameter $\lambda$.
 However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
@@
 %\end{equation}
-With this representation, the parametrised \hugh{asymmetric} RMP Hamiltonian becomes
+With this representation, the parametrised asymmetric RMP Hamiltonian becomes
 \begin{widetext}
 \begin{equation}
-\label{eq:H_RMP}
-\hugh{\bH_\text{asym}\qty(\lambda)} = 
+\label{eq:H_asym}
+\bH_\text{asym}\qty(\lambda) = 
 \begin{pmatrix}
@@
 We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
-a new type of MP critical point and \hugh{represents a QPT as the perturbation parameter $\lambda$ is varied.}
+a new type of MP critical point and represents a QPT as the perturbation parameter $\lambda$ is varied.
 Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
@@
 
+An interesting point raised in Ref.~\onlinecite{Goodson_2019} suggests that low-order quadratic approximants might struggle to model the correct singularity structure when the energy function has poles in both the positive and negative half-planes.
+In such a scenario, the quadratic approximant will have the tendency to place its branch points in-between, potentially introducing singularities quite close to the origin.
+A simple potential cure for this consists in applying a judicious transformation (like a bilinear conformal mapping) which does not affect the points at $\lambda = 0$ and $\lambda = 1$.
+\cite{Feenberg_1956}
+
 %==========================================%
@@
 In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
-In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
+In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\abs{\lambda} < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
 However, the choice of the functional form of the fit remains a subtle task.
@@
 The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
-
-\titou{T2 will add a comment about Goodson's remark on the failure of low-order approximants when $\alpha$ and $\beta$ singularities are present.}
 

### 2020-12-01 Manuscript/EPAWTFT.tex
reviewing Hugh changes

@@
 the presence of an earlier excited-state avoided crossing means that the first-excited state qualitatively 
-represents the reference double excitation for $\lambda > 0.5.$
+represents the reference double excitation for $\lambda > 1/2$ (see Fig.~\ref{subfig:ump_cp}).
 

### 2020-12-01 Manuscript/EPAWTFT.tex
reviewing Hugh changes

@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
-		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the exact limit $t \rightarrow 0$.
+		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the \trash{exact} limit $t \to 0$.
 	\label{fig:RMP_cp}}
@@
 \caption{%
-    The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
+    The UMP ground-state EP \titou{in the symmetric Hubbard dimer} becomes a critical point in the strong correlation limit (\ie, large $U/t$).
     (\subref{subfig:ump_cp}) As $U/t$ increases, the avoided crossing on the real $\lambda$ axis

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIA and IIB

@@
 
+\titou{T2: I THINK THAT IN GENERAL THE AXE LABELS ARE TOO SMALL.}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
-the perturbation theories and Hartree--Fock approximation considered in this review
+perturbation theories and Hartree--Fock approximation considered in this review.
 In what follows, we will drop the parametric dependence on the nuclear geometry and, 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIC

@@
 The energy of the target ``physical'' system is recovered at the point $\lambda = 1$.
-However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
-When $\rc \le 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
+However, like all series expansions, Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
+When $\rc < 1$, the Rayleigh--Schr\"{o}dinger expansion will diverge
 for the physical system.
@@
 
-The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude $\abs{\lambda_c}$ of the
+The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude $r_c = \abs{\lambda_c}$ of the
 singularity in $E(\lambda)$ that is closest to the origin.
-Note that when $\lambda = \lambda_c$, one cannot \textit{a priori} predict if the series is convergent or not.
+Note that when $\abs{\lambda} = r_c$, one cannot \textit{a priori} predict if the series is convergent or not.
 For example, the series $\sum_{k=1}^\infty \lambda^k/k$ diverges at $\lambda = 1$ but converges at $\lambda = -1$.

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IID

@@
     f_i & = \mel{\phi_i}{\Hat{f}}{\phi_i}.
-	%J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
-	%&
-	%K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}.
 \end{align}
@@
 \begin{equation}\label{eq:HFHamiltonian}
-	\hH_{\text{HF}} = \sum_{i} f(\vb{x}_i).
+	\hH_{\text{HF}} = \sum_{i}^{N} f(\vb{x}_i).
 \end{equation}
@@
 However, the application of HF with some level of constraint on the orbital structure is far more common.
-Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, 
+Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) method, 
 while allowing different orbitals for different spins leads to the so-called unrestricted HF (UHF) approach.\cite{StuberPaldus}
 The advantage of the UHF approximation is its ability to correctly describe strongly correlated systems, 
-such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer,\cite{Coulson_1949}
+such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer.\cite{Coulson_1949}
 However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
-the total spin $\hat{\mathcal{S}}^2$ operator, leading to ``spin-contamination'' in the wave function.
+the total spin operator $\hat{\mathcal{S}}^2$, leading to ``spin-contamination'' in the wave function.
 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIE

@@
 
-In the Hubbard dimer, the UHF energy can be parametrised using two rotation angles $\ta$ and $\tb$ as
+In the Hubbard dimer, the HF energy can be parametrised using two rotation angles $\ta$ and $\tb$ as
 \begin{equation}
@@
 However, in the strongly correlated regime $U>2t$, the closed-shell orbital restriction prevents RHF from 
-modelling the correct physics with the two electrons on opposing sites.
+modelling the correct physics with the two electrons on opposite sites.
 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIF

@@
     \caption{\label{fig:HF_real}
-    RHF and UHF energies as a function of the correlation strength $U/t$. 
+    RHF and UHF energies \titou{in the Hubbard dimer} as a function of the correlation strength $U/t$. 
     The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson-Fischer point.}
@@
 	\caption{%
-    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
+    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$ \titou{in the Hubbard dimer for $U/t = ??$}.
     Symmetry-broken solutions correspond to individual sheets and become equivalent at 
@@
 % COMPLEX ADIABATIC CONNECTION
-We have recently shown that the complex scaled Fock operator Eq.~\eqref{eq:scaled_fock}
+We have recently shown that the complex scaled Fock operator \eqref{eq:scaled_fock}
 also allows states of different symmetries to be interconverted by following a well-defined

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIA

@@
 
-%\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree--Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
-%In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
-\cite{Seidl_2018}
-%In such a way, we could obtain a doubly-excited state wave function starting from the ground state wave function, a process which is not as easy as one might think.
-\cite{Gilbert_2008,Thom_2008,Shea_2018}
-%One of the fundamental discovery we made was that Coulson-Fischer points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
-%The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
-%It perfectly illustrates the deeper topology of electronic states revealed using a complex-scaled electron-electron interaction.
-%Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller--Plesset Theory in the Complex Plane}
+\section{M{\o}ller--Plesset Perturbation Theory in the Complex Plane}
 \label{sec:MP}
@@
 
-% HGAB: I don't think this parapgrah tells us anything we haven't discussed before
-%A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
-%By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, 
-%and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
-%As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
-%These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
-%The direct computation of the terms of the series is quite manageable up to fourth order in perturbation, while the fifth and sixth order in perturbation can still be obtained but at a rather high cost.
-\cite{JensenBook}
-%In order to better understand the behaviour of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
-%For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
-%If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
-
 Although practically convenient for electronic structure calculations, the MP partitioning is not 
-the only possibility and alternative partitionings have been considered including: %proposed in the literature:
+the only possibility and alternative partitionings have been considered including: 
 i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
-%Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
 ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIB

@@
 Firstly, the exact wave function becomes increasingly multi-configurational as the bond is stretched, and the 
-HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
-Secondly, the energy gap between the bonding and anitbonding orbitals associated with the stretch becomes
-increasingly small at larger bond lengths, leading to a divergence in the Rayleigh--Schr\"odinger perturbation
-expansion Eq.~\eqref{eq:EMP2}.
+\titou{R}HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
+Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
+increasingly small at larger bond lengths, \titou{leading to a divergence, for example, in the second-order MP correction \eqref{eq:EMP2}.}
 In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains
@@
 by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
-In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
+In this work, the authors compared \titou{the UMP series with the exact RHF- and UHF-based FCI expansions (T2: I don't understand this)}
 and identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
@@
 % LEPETIT CHAT
-Lepetit \etal\ later analysed the difference between perturbation convergence using the unrestricted MP 
+Lepetit \etal\ later analysed the difference between perturbation convergence using the UMP 
 and EN partitionings. \cite{Lepetit_1988}

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIC

@@
 \end{equation}
-where $\vb{r}_i$ defines the position of the $i$-th electron, $\vb{R}_{A}$ and $Z_{A}$ are the position
-and charge of the $A$-th nucleus respectively, and $\vb{R} = (\vb{R}_{1}, \dots, \vb{R}_{\Nn})$ is a
+where $\vb{r}_i$ defines the position of the $i$th electron, $\vb{R}_{A}$ and $Z_{A}$ are the position
+and charge of the $A$th nucleus respectively, and $\vb{R} = (\vb{R}_{1}, \dots, \vb{R}_{\Nn})$ is a
 collective vector for the nuclear positions.
@@
 the analytic Hubbard dimer with a complex-valued perturbation strength.
-In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the electron correlation $U/t$.
+In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the \trash{electron correlation} \titou{ratio} $U/t$.
 Using the ground-state RHF reference orbitals leads to the parametrised RMP Hamiltonian
@@
 These numerical values reveal that the UMP ground-state series has $\rc > 1$ for all $U/t$ and always converges.
-However, in the strong correlation limit (large $U$), this radius of convergence tends to unity, indicating that
-the corresponding UMP series becomes increasingly slow.
+However, in the strong correlation limit (large $U/t$), this radius of convergence tends to unity, indicating that
+the convergence of the corresponding UMP series becomes increasingly slow.
 Furthermore, the doubly-excited state using the ground-state UHF orbitals has $\rc < 1$ for almost any value 
-of $U/t$, reaching the limiting value of $1/2$ for $U/t \to \infty$, and thus the 
+of $U/t$, reaching the limiting value of $1/2$ for $U/t \to \infty$. Hence, the 
 excited-state UMP series will always diverge.
@@
 The convergence behaviour can be further elucidated by considering the full structure of the UMP energies 
-in the complex $\lambda$-plane.
+in the complex $\lambda$-plane (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
 These Riemann surfaces are illustrated for $U = 3t$ and $7t$ alongside the perturbation terms at each order
@@
 % EFFECT OF SYMMETRY BREAKING
-As the UHF orbitals break the molecular symmetry, new coupling terms emerge between the electronic states that
+As the UHF orbitals break the \trash{molecular} \titou{spin} symmetry, new coupling terms emerge between the electronic states that
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIC

@@
 
-%When one relies on MP perturbation theory (and more generally on any perturbative partitioning), it would be reasonable to ask for a systematic improvement of the energy with respect to the perturbative order, \ie, one would expect that the more terms of the perturbative series one can compute, the closer the result from the exact energy.
-%In other words, one would like a monotonic convergence of the MP series.
-Assuming this, the only limiting process to get the exact correlation energy (in a finite basis set) would be our ability to compute the terms of this perturbation series.
-%Unfortunately this is not as easy as one might think because i) the terms of the perturbative series become rapidly computationally cumbersome, and ii) erratic behaviour of the perturbative coefficients are not uncommon.
-%For example, in the late 80's, Gill and Radom reported deceptive and slow convergences in stretched systems \cite{Gill_1986,Gill_1988} (see also Refs.~\onlinecite{Handy_1985,Lepetit_1988}). 
-%In Ref.~\onlinecite{Gill_1986}, the authors showed that the RMP series is convergent, yet oscillatory which is far from being convenient if one is only able to compute the first few terms of the expansion.
-%For example, in the case of the barrier to homolytic fission of \ce{He2^2+} in a minimal basis set, RMP5 is worse than RMP4 (see Fig.~2 in Ref.~\onlinecite{Gill_1986}).
-%On the other hand, the UMP series is monotonically convergent after UMP5 but very slowly . 
-%Thus, one cannot practically use it for systems where only the first terms are computationally accessible.
-
-%When a bond is stretched, in most cases the exact wave function becomes more and more of multi-reference nature. 
-%Yet, the HF wave function is restricted to be a single Slater determinant.
-%It is then inappropriate to model (even qualitatively) stretched systems. 
-%Nevertheless, as explained in Sec.~\ref{sec:HF} and illustrated in Sec.~\ref{sec:HF_hubbard}, the HF wave function can undergo symmetry breaking to lower its energy by sacrificing one of the symmetry of the exact wave function in the process (see also the pedagogical example of \ce{H2} in Ref.~\onlinecite{SzaboBook}).
-%One could then potentially claim that the RMP series exhibits deceptive convergence properties as the RHF Slater determinant is a poor approximation of the exact wave function for stretched system. 
-%However, as illustrated above, even in the unrestricted formalism which clearly represents a better description of a stretched system, the UMP series does not have the smooth and rapidly convergent behaviour that one would wish for.
-%The reasons behind this ambiguous behaviour are further explained below.
-
-%In the unrestricted framework the singlet ground state wave function is allowed to mix with triplet wave functions, leading to the so-called spin contamination issue.
-Gill \textit{et al.}~highlighted the link between slow convergence of the UMP series and spin contamination for \ce{H2} in a minimal basis.
-\cite{Gill_1988}
-%Handy and coworkers reported the same behaviour of the UMP series (oscillatory and slowly monotonically convergent) in stretched \ce{H2O} and \ce{NH2}.
-\cite{Handy_1985} Lepetit \textit{et al.}~analysed the difference between the MP and EN partitioning for the UHF reference.
-\cite{Lepetit_1988}
-%They concluded that the slow convergence of the UMP series is due to i) the fact that the MP denominator (see Eq.~\ref{eq:EMP2}) tends to a constant instead of vanishing, and ii) the lack of the singly-excited configurations (which only appears at fourth order) that strongly couple to the doubly-excited configurations.
-%We believe that this divergent behaviour might therefore be attributed to the need for the single excitations to focus on correcting the structure of the reference orbitals rather than capturing the correlation energy.
-
-%Cremer and He analysed 29 atomic and molecular systems at the FCI level \cite{Cremer_1996} and grouped them in two classes: i) the \textit{class A} systems where one observes a monotonic convergence \titou{of the RMP series?} to the FCI energy, and ii) the \textit{class B} systems for which convergence is erratic after initial oscillations.
-%Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
-%They highlighted that \cite{Cremer_1996}
-%\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-%Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
-%They showed that class A systems have very little contribution from the triple excitations and that most of the correlation energy is due to pair correlation. 
-%On the other hand, class B systems have an important contribution from the triple excitations which alternates in sign resulting in an oscillation of the total correlation energy.
-%This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
-%As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-%Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
-\cite{Cremer_1996}
-%The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-%Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
-
 %==========================================%
@@
 \end{equation}
-%with 
-%\begin{equation}
-%	E_{\text{MP}n}(\lambda) = \sum_{k=0}^n E_\text{MP}^{(k)} \lambda^k.
-%\end{equation}
 
@@
 for the two states using the ground-state RHF orbitals is identical.
-% HGAB: This cannot be relevant here as the single-excitations don't couple to either ground or excited state.
-%The convergent and divergent series start to differ at fourth order, corresponding to the lowest-order contribution
-%%from the single excitations.\cite{Lepetit_1988}
 
@@
 
-%The convergence of the UMP as a function of the ratio $U/t$ is shown in Fig.~\ref{subfig:UMP_cvg} for two specific values: the first ($U = 3t$) is well within the RMP convergence region, while the second ($U = 7t$) falls outside.
-%Note that in the case of UMP, there are now two pairs of EPs as the open-shell singlet now couples strongly with both the ground and doubly-excited states.
-%This has the clear tendency to move away from the origin the EP dictating the convergence of the ground-state energy, while deteriorating the convergence properties of the excited-state energy.
-%For $U = 3t$ (see Fig.~\ref{subfig:UMP_3}), the ground-state energy is remarkably flat since the UHF energy is already a pretty good estimate of the exact energy thanks to the symmetry-breaking process.
-%Most of the UMP expansion is actually correcting the spin-contamination in the wave function.
-%For $U = 7t$ (see Fig.~\ref{subfig:UMP_7}), we are well towards the strong correlation regime, where we see that the UMP series is slowly convergent while RMP diverges.
-%We see a single EP on the ground-state surface which falls just outside (maybe on?) the radius of convergence. 
-%An EP this close to the radius of convergence gives an increasingly slow convergence of the UMP series, but it will converge eventually as observed in Fig.~\ref{subfig:UMP_cvg}.
-%On the other hand, there is an EP on the excited energy surface that is well within the radius of convergence.
-%We can therefore say that the use of a symmetry-broken UHF wave function can retain a convergent ground-state perturbation series
-%at the expense of a divergent excited-state perturbation series. (Note: the orbitals are not optimised for excited-state here).
-%In contrast, the RMP expansion was always convergent for the open-shell excited state (which was a single CSF) while
-%the radius of convergence for the doubly-excited state was identical to the ground-state as this was the only exceptional point.
-
 %==========================================%
@@
 and ``class B'' systems for which convergence is erratic after initial oscillations. 
-%Their system set contains stretched molecules as well as molecules at their equilibrium geometry for various basis sets. 
 By analysing the different cluster contributions to the MP energy terms, they proposed that
@@
 are characterised by dense electron clustering in one or more spatial regions.\cite{Cremer_1996}
-%\textit{``Class A systems are characterised by electronic structures with well-separated electron pairs while class B systems are characterized by electronic structures with electron clustering in one or more regions.''}
-%Moreover, they analysed the contribution of the triple (T) excitations to the MP4, MP5 and MP6 energies next to the single, double and quadruple (SDQ) excitations contribution.
 In class A systems, they showed that the majority of the correlation energy arises from pair correlation, 
@@
 orbital relaxation, and these contributions lead to oscillations of the total correlation energy.
-%This observation on the contribution to the MP$n$ energy corroborates the electronic structure discussed above.
 

### 2020-12-01 Manuscript/EPAWTFT.tex
local changes

--- 2020-12-01 Manuscript/EPAWTFT.tex
@@
 
-\titou{T2: I THINK THAT IN GENERAL THE AXE LABELS ARE TOO SMALL.}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
-perturbation theories and Hartree--Fock approximation considered in this review.
+the perturbation theories and Hartree--Fock approximation considered in this review
 In what follows, we will drop the parametric dependence on the nuclear geometry and, 
@@
 The energy of the target ``physical'' system is recovered at the point $\lambda = 1$.
-However, like all series expansions, Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
-When $\rc < 1$, the Rayleigh--Schr\"{o}dinger expansion will diverge
+However, like all series expansions, the Eq.~\eqref{eq:E_expansion} has a radius of convergence $\rc$. 
+When $\rc \le 1$, the Rayleigh--Sch\"{r}odinger expansion will diverge
 for the physical system.
@@
 
-The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude $r_c = \abs{\lambda_c}$ of the
+The radius of convergence for the perturbation series Eq.~\eqref{eq:E_expansion} is therefore dictated by the magnitude $\abs{\lambda_c}$ of the
 singularity in $E(\lambda)$ that is closest to the origin.
-Note that when $\abs{\lambda} = r_c$, one cannot \textit{a priori} predict if the series is convergent or not.
+Note that when $\lambda = \lambda_c$, one cannot \textit{a priori} predict if the series is convergent or not.
 For example, the series $\sum_{k=1}^\infty \lambda^k/k$ diverges at $\lambda = 1$ but converges at $\lambda = -1$.
@@
     f_i & = \mel{\phi_i}{\Hat{f}}{\phi_i}.
+	%J_{ij} & = \mel{\phi_i}{\Hat{J}_j}{\phi_i},
+	%&
+	%K_{ij} & = \mel{\phi_i}{\Hat{K}_j}{\phi_i}.
 \end{align}
@@
 \begin{equation}\label{eq:HFHamiltonian}
-	\hH_{\text{HF}} = \sum_{i}^{N} f(\vb{x}_i).
+	\hH_{\text{HF}} = \sum_{i} f(\vb{x}_i).
 \end{equation}
@@
 However, the application of HF with some level of constraint on the orbital structure is far more common.
-Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) method, 
+Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) theory, 
 while allowing different orbitals for different spins leads to the so-called unrestricted HF (UHF) approach.\cite{StuberPaldus}
 The advantage of the UHF approximation is its ability to correctly describe strongly correlated systems, 
-such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer.\cite{Coulson_1949}
+such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer,\cite{Coulson_1949}
 However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
-the total spin operator $\hat{\mathcal{S}}^2$, leading to ``spin-contamination'' in the wave function.
+the total spin $\hat{\mathcal{S}}^2$ operator, leading to ``spin-contamination'' in the wave function.
 
@@
     \caption{\label{fig:HF_real}
-    RHF and UHF energies \titou{in the Hubbard dimer} as a function of the correlation strength $U/t$. 
+    RHF and UHF energies as a function of the correlation strength $U/t$. 
     The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson-Fischer point.}
@@
 
-In the Hubbard dimer, the HF energy can be parametrised using two rotation angles $\ta$ and $\tb$ as
+In the Hubbard dimer, the UHF energy can be parametrised using two rotation angles $\ta$ and $\tb$ as
 \begin{equation}
@@
 However, in the strongly correlated regime $U>2t$, the closed-shell orbital restriction prevents RHF from 
-modelling the correct physics with the two electrons on opposite sites.
+modelling the correct physics with the two electrons on opposing sites.
 
@@
 	\caption{%
-    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$ \titou{in the Hubbard dimer for $U/t = ??$}.
+    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$.
     Symmetry-broken solutions correspond to individual sheets and become equivalent at 
@@
 % COMPLEX ADIABATIC CONNECTION
-We have recently shown that the complex scaled Fock operator \eqref{eq:scaled_fock}
+We have recently shown that the complex scaled Fock operator Eq.~\eqref{eq:scaled_fock}
 also allows states of different symmetries to be interconverted by following a well-defined
@@
 
+%\titou{In a recent paper, \cite{Burton_2019} using holomorphic Hartree--Fock (h-HF) \cite{Hiscock_2014,Burton_2018,Burton_2016} as an analytic continuation of conventional HF theory, we have demonstrated, on a simple model, that one can interconvert states of different symmetries and natures by following well-defined contours in the complex $\lambda$-plane, where $\lambda$ is the strength of the electron-electron interaction (see Fig.~\ref{fig:iAC}).
+%In particular, by slowly varying $\lambda$ in a similar (yet different) manner to an adiabatic connection in density-functional theory, \cite{Langreth_1975,Gunnarsson_1976,Zhang_2004} one can ``morph'' a ground-state wave function into an excited-state wave function via a stationary path of HF solutions.
+\cite{Seidl_2018}
+%In such a way, we could obtain a doubly-excited state wave function starting from the ground state wave function, a process which is not as easy as one might think.
+\cite{Gilbert_2008,Thom_2008,Shea_2018}
+%One of the fundamental discovery we made was that Coulson-Fischer points (where multiple symmetry-broken solutions coalesce) play a central role and can be classified as \textit{quasi}-exceptional points, as the wave functions do not become self-orthogonal.
+%The findings reported in Ref.~\onlinecite{Burton_2019} represent the very first study of non-Hermitian quantum mechanics for the exploration of multiple solutions at the HF level. 
+%It perfectly illustrates the deeper topology of electronic states revealed using a complex-scaled electron-electron interaction.
+%Through the introduction of non-Hermiticity, we have provided a more general framework in which the complex and diverse characteristics of multiple solutions can be explored and understood.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{M{\o}ller--Plesset Perturbation Theory in the Complex Plane}
+\section{M{\o}ller--Plesset Theory in the Complex Plane}
 \label{sec:MP}
@@
 
+% HGAB: I don't think this parapgrah tells us anything we haven't discussed before
+%A convenient way to investigate the convergence properties of the MP series is to analytically continue the coupling parameter $\lambda$ into the complex variable. 
+%By doing so, the Hamiltonian and the energy become complex-valued functions of $\lambda$, 
+%and the energy becomes a multivalued function on $K$ Riemann sheets (where $K$ is the number of basis functions).
+%As mentioned above, by searching the singularities of the function $E(\lambda)$, one can get information on the convergence properties of the MP series. 
+%These singularities of the energy function are exactly the EPs connecting the electronic states as mentioned in Sec.~\ref{sec:intro}. 
+%The direct computation of the terms of the series is quite manageable up to fourth order in perturbation, while the fifth and sixth order in perturbation can still be obtained but at a rather high cost.
+\cite{JensenBook}
+%In order to better understand the behaviour of the MP series and how it is connected to the singularity structure, we have to access high-order terms. 
+%For small systems, one can access the whole terms of the series using full configuration interaction (FCI). 
+%If the Hamiltonian $H(\lambda)$ is diagonalized in the FCI space, one gets the exact energies (in this finite Hilbert space) and the Taylor expansion with respect to $\lambda$ allows to access the MP perturbation series at any order.
+
 Although practically convenient for electronic structure calculations, the MP partitioning is not 
-the only possibility and alternative partitionings have been considered including: 
+the only possibility and alternative partitionings have been considered including: %proposed in the literature:
 i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
+%Hence, the off-diagonal elements of $\hH$ are the perturbation operator,
 ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
@@
 Firstly, the exact wave function becomes increasingly multi-configurational as the bond is stretched, and the 
-\titou{R}HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
-Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
-increasingly small at larger bond lengths, \titou{leading to a divergence, for example, in the second-order MP correction \eqref{eq:EMP2}.}
+HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
+Secondly, the energy gap between the bonding and anitbonding orbitals associated with the stretch becomes
+increasingly small at larger bond lengths, leading to a divergence in the Rayleigh--Schr\"odinger perturbation
+expansion Eq.~\eqref{eq:EMP2}.
 In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains
@@
 by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
-In this work, the authors compared \titou{the UMP series with the exact RHF- and UHF-based FCI expansions (T2: I don't understand this)}
+In this work, the authors compared the UMP series with the exact RHF- and UHF-based FCI expansions
 and identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
@@
 % LEPETIT CHAT
-Lepetit \etal\ later analysed the difference between perturbation convergence using the UMP 
+Lepetit \etal\ later analysed the difference between perturbation convergence using the unrestricted MP 
 and EN partitionings. \cite{Lepetit_1988}
@@
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
-recognised as a QPT with respect to varying the perturbation parameter $\lambda$.
+recognised as a QPT \hugh{with respect to varying the perturbation parameter $\lambda$}.
 However, a conventional QPT can only occur in the thermodynamic limit, which here is analogous to the complete 
@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
-		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the \trash{exact} limit $t \to 0$.
+		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the exact limit $t \rightarrow 0$.
 	\label{fig:RMP_cp}}
@@
 To mathematically model this scenario in this asymmetric Hubbard dimer, we introduce a one-electron potential $-\epsilon$ on the left site to 
-represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
+represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], 
+where we define $\epsilon \geq 0$.
 The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
@@
 %\end{equation}
-With this representation, the parametrised asymmetric RMP Hamiltonian becomes
+With this representation, the parametrised \hugh{asymmetric} RMP Hamiltonian becomes
 \begin{widetext}
 \begin{equation}
-\label{eq:H_asym}
-\bH_\text{asym}\qty(\lambda) = 
+\label{eq:H_RMP}
+\hugh{\bH_\text{asym}\qty(\lambda)} = 
 \begin{pmatrix}
@@
 as shown in Fig.~\ref{subfig:rmp_cp} (dashed lines).
-The RMP critical point then corresponds to the intersection $E_{-} = E_{+}$, giving the critical $\lambda$ value
+The RMP critical point then occurs at the intersection $E_{-} = E_{+}$, giving the critical $\lambda$ value
 \begin{equation}
@@
 \caption{%
-    The UMP ground-state EP \titou{in the symmetric Hubbard dimer} becomes a critical point in the strong correlation limit (\ie, large $U/t$).
+    The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
     (\subref{subfig:ump_cp}) As $U/t$ increases, the avoided crossing on the real $\lambda$ axis
@@
 the presence of an earlier excited-state avoided crossing means that the first-excited state qualitatively 
-represents the reference double excitation for $\lambda > 1/2$ (see Fig.~\ref{subfig:ump_cp}).
+represents the reference double excitation for $\lambda > 0.5.$
 
@@
 For small $U/t$, the HF potentials will be weak and the electrons will delocalise over the two sites,
-both in the UHF reference and as $\lambda$ increases.
+both in the UHF reference and as $\lambda$ increases towards the exact solution.
 This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing
@@
 We therefore find that, in the strong correlation limit, the symmetry-broken ground-state EP becomes
-a new type of MP critical point and represents a QPT as the perturbation parameter $\lambda$ is varied.
+a new type of MP critical point and \hugh{represents a QPT as the perturbation parameter $\lambda$ is varied.}
 Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
@@
 
-An interesting point raised in Ref.~\onlinecite{Goodson_2019} suggests that low-order quadratic approximants might struggle to model the correct singularity structure when the energy function has poles in both the positive and negative half-planes.
-In such a scenario, the quadratic approximant will have the tendency to place its branch points in-between, potentially introducing singularities quite close to the origin.
-A simple potential cure for this consists in applying a judicious transformation (like a bilinear conformal mapping) which does not affect the points at $\lambda = 0$ and $\lambda = 1$.
-\cite{Feenberg_1956}
-
 %==========================================%
@@
 In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
-In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\abs{\lambda} < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
+In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\lambda < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
 However, the choice of the functional form of the fit remains a subtle task.
@@
 The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
+
+\titou{T2 will add a comment about Goodson's remark on the failure of low-order approximants when $\alpha$ and $\beta$ singularities are present.}
 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIID

--- 2020-12-01 Manuscript/EPAWTFT.tex
@@
 \end{subequations}
-%As one can only compute the first terms of the MP series, a smart way of getting more accurate results is to use extrapolation formula, \ie, estimating the limit of the series with only few terms. 
-%Cremer and He proved that using specific extrapolation formulas of the MP series for class A and class B systems improves the precision of the results compared to the formula used without resorting to classes.
-\cite{Cremer_1996}
 These class-specific formulas reduced the mean absolute error from the FCI correlation energy by a
@@
 the correlation energy at lower computational costs. 
-In Section~\ref{sec:Resummation}, we consider more advanced extrapolation routines that take account of EPs in the complex $\lambda$-plane.
-%The mean absolute deviation taking the FCI correlation energies as reference is $0.3$ millihartree with the class-specific formula whereas the deviation increases to 12 millihartree using the general formula.
-%Even if there were still shaded areas in their analysis and that their classification was incomplete, the work of Ref.~\onlinecite{Cremer_1996} clearly evidenced that understanding the origin of the different modes of convergence could potentially lead to a more rationalised use of MP perturbation theory and, hence, to more accurate correlation energy estimates.
+In Sec.~\ref{sec:Resummation}, we consider more advanced extrapolation routines that take account of EPs in the complex $\lambda$-plane.
 
@@
 By modelling this avoided crossing using a two-state Hamiltonian, one can obtain an approximation for
-the dominant singularities as the EPs of the $2\times2$ matrix
+the dominant singularities as the EPs of the two-state matrix
 \begin{equation}
@@
 that arise when the ground state undergoes sharp avoided crossings with highly diffuse excited states.
-%They used their two-state model on this avoided crossings and the model was actually predicting the divergence of the series. 
-%They concluded that the divergence of the series was due to the interaction with a highly diffuse excited state. 
 This divergence is related to a more fundamental critical point in the MP energy surface that we will
-discuss in Section~\ref{sec:MP_critical_point}.
+discuss in Sec.~\ref{sec:MP_critical_point}.
 
@@
 while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
-%Other features characterising the convergence behaviour of a perturbation method are its rate of convergence, its length of recurring period, and its sign pattern.
 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIE

@@
 They demonstrated that the dominant singularity in class A systems corresponds to a dominant EP with a positive real component, 
-with the magnitude of the imaginary component controlling the oscillations in the signs of successive MP 
+where the magnitude of the imaginary component controls the oscillations in the signs of successive MP 
 terms.\cite{Goodson_2000a,Goodson_2000b}
@@
  a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
-Furthermore, the two-state model of Olsen \etal{}\cite{Olsen_2000} was simply too minimal to understand the complexity of 
+Furthermore, the two-state model of Olsen and collaborators \cite{Olsen_2000} was simply too minimal to understand the complexity of 
 divergences caused by the MP critical point.
-
-% BASIS SET DEPENDENCE (INCLUDE?)
-%Finally, it was shown that $\beta$ singularities are very sensitive to changes in the basis set but not to the bond stretching. 
-%On the contrary, $\alpha$ singularities are relatively insensitive to the basis sets but very sensitive to bond stretching. 
-%According to Goodson, \cite{Goodson_2004} the singularity structure of stretched molecules is difficult because there is more than one significant singularity. 
-%This is consistent with the observation of Olsen and coworkers \cite{Olsen_2000} on the \ce{HF} molecule at equilibrium and stretched geometries. 
-%To the best of our knowledge, the effect of bond stretching on singularities, its link with spin contamination and symmetry breaking of the wave function has not been as well understood as the ionization phenomenon and its link with diffuse functions.
-
-%In the 2000's, Sergeev and Goodson \cite{Sergeev_2005, Sergeev_2006} analysed this problem from a more mathematical point of view by looking at the whole singularity structure where Olsen and collaborators were trying to find the dominant singularity causing the divergence.
-\cite{Olsen_1996,Olsen_2000,Olsen_2019}
-%Singularities of $\alpha$-type are related to large avoided crossing between the ground and low-lying excited states, whereas $\beta$ singularities come from a sharp avoided crossing between the ground state and a highly diffuse state.
-%They succeeded to explain the divergence of the series caused by $\beta$ singularities following previous work by Stillinger. \cite{Stillinger_2000}
-
-%This reasoning is done on the exact Hamiltonian and energy, \ie, the Hamiltonian in the complete Hilbert space, this is the exact energy which exhibits this singularity on the negative real axis. 
-%However, in a finite basis set which does not span the complete Hilbert space, one can prove that, for a Hermitian Hamiltonian, the singularities of $E(\lambda)$ occurs in complex conjugate pairs with non-zero imaginary parts.
-%Sergeev and Goodson proved, \cite{Sergeev_2005} as predicted by Stillinger, \cite{Stillinger_2000} that in a finite basis set the critical point on the real axis is modelled by a cluster of sharp avoided crossings with diffuse functions, equivalently by a cluster of $\beta$ singularities in the negative half plane.
-%This explains that Olsen \textit{et al.}, because they used a simple two-state model, only observed the first singularity of this cluster of singularities causing the divergence. \cite{Olsen_2000}
 

### 2020-12-01 Manuscript/EPAWTFT.tex
Done with IIIF

@@
 represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
-The reference Slater determinant for a doubly-occupied atom can be represented using the RHF
+The reference Slater determinant for a doubly-occupied atom can be represented using RHF
 orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$, 

### 2020-12-01 Manuscript/EPAWTFT.tex
abstract

@@
 In this review, we explore the extension of quantum chemistry in the complex plane and its link with perturbation theory.
-We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptionnal points.
+We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptional points.
 After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
 In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory and its apparent link with quantum phase transitions.
+Each of these points is further illustrated with the Hubbard dimer.
+Finally, we discuss several resummation techniques (such as Pad\'e and quadratic approximants) alongside concrete examples.
 \end{abstract}

### 2020-12-01 Manuscript/EPAWTFT.tex
adding references in intro and slight modifications

@@
 An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws.
-The fact that none of these methods is successful in every chemical scenario has encouraged chemists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
+\cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
+The fact that none of these methods is successful in every chemical scenario has encouraged chemists and physicists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
+In particular, the design of an affordable, black-box method performing well in both the weak and strong correlation regimes is still elusive.
 
@@
 Within this quantised paradigm, electronic states look completely disconnected from one another.
-Many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.
+For example, many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.\cite{Piecuch_2002,Dreuw_2005,Krylov_2006,Sneskov_2012,Gonzales_2012,Laurent_2013,Adamo_2013,Ghosh_2018,Blase_2020,Loos_2020a}
 However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.

### 2020-12-02 Manuscript/EPAWTFT.tex
local changes

--- 2020-12-01 Manuscript/EPAWTFT.tex
@@
 
-As frequently claimed by Carl Bender, \textit{``the most stupid thing that one can do with a series is to sum it.''}
+%As frequently claimed by Carl Bender, 
+\hugh{It is frequently stated that}
+\textit{``the most stupid thing that one can do with a series is to sum it.''}
 Nonetheless, quantum chemists are basically doing exactly this on a daily basis.
-Here, we discuss tools that can be used to sum divergent series.
-Resummation techniques is a vast field of research and, below, we provide details for a non-exhaustive list of these techniques.
-We refer the interested reader to more specialised reviews for additional information. \cite{Goodson_2011,Goodson_2019}
+\hugh{As we have seen throughout this review, the MP series can often show erratic, 
+slow, or divergent behaviour.
+In these cases, estimating the correlation energy by simply summing successive
+low-order terms is almost guaranteed to fail.}
+Here, we discuss alternative tools that can be used to sum slowly convergent or divergent series.
+\hugh{These so-called ``resummation'' techniques} form a vast field of research and thus we will
+provide details for only the most relevant methods.
+We refer the interested reader to more specialised reviews for additional information.% 
+\cite{Goodson_2011,Goodson_2019}
 
 %==========================================%
-\subsection{Pad\'e approximant}
+\subsection{Pad\'e Approximant}
 %==========================================%
-The inability of Taylor series to model properly the energy function $E(\lambda$) can be simply understood by the fact that one aims at modelling a complicated function with potentially poles and singularities by a simple polynomial of finite order.
+\hugh{The failure of a Taylor series for correctly modelling the MP energy function $E(\lambda)$ 
+arises because one is trying to model a complicated function containing branch points and
+singularities} using a simple polynomial of finite order.
 A truncated Taylor series just does not have enough flexibility to do the job properly.
-Nonetheless, the description of complex energy functions can be significantly improved thanks to Pad\'e approximant, \cite{Pade_1892} and related techniques. \cite{BakerBook,BenderBook}
-
-According to Wikipedia, \textit{``a Pad\'e approximant is the best approximation of a function by a rational function of given order''}. 
+Alternatively, the description of complex energy functions can be significantly improved
+by introducing Pad\'e approximants, \cite{Pade_1892} and related techniques. \cite{BakerBook,BenderBook}
+
+\hugh{A Pad\'e approximant can be considered as the best approximation of a function by a 
+rational function of given order.}
 More specifically, a $[d_A/d_B]$ Pad\'e approximant is defined as 
@@
 	\label{eq:PadeApp}
-	E_{[d_A/d_B]}(\lambda) = \frac{A(\lambda)}{B(\lambda)} = \frac{\sum_{k=0}^{d_A} a_k \lambda^k}{\sum_{k=0}^{d_B} b_k \lambda^k}
-\end{equation}
-(with $b_0 = 1$), where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms according to power of $\lambda$.
+	E_{[d_A/d_B]}(\lambda) = \frac{A(\lambda)}{B(\lambda)} 
+    = \frac{\sum_{k=0}^{d_A} a_k\, \lambda^k}{1 + \sum_{k=1}^{d_B} b_k\, \lambda^k},
+\end{equation}
+where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms for each power of $\lambda$.
 Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, which appears at the locations of the roots of $B(\lambda)$.
-However, they are unable to model functions with square-root branch points (which are ubiquitous in the singularity structure of a typical perturbative treatment) and more complicated functional forms appearing at critical points (where the nature of the solution undergoes a sudden transition) for example.
-
-Figure \ref{fig:PadeRMP} illustrates the improvement brought by diagonal (\ie, $d_A = d_B$) Pad\'e approximants as compared to the usual Taylor expansion in cases where the RMP series of the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
+However, they are unable to model functions with square-root branch points (which are ubiquitous in the singularity structure of a typical perturbative treatment) and more complicated functional forms appearing at critical points (where the nature of the solution undergoes a sudden transition).
+\hugh{Despite this limitation, the successive diagonal Pad\'e approximants (\ie, $d_A = d_B $) 
+often define a convergent perturbation series in cases where the Taylor series expansion diverges.}
+
+Figure \ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e approximants compared to the usual Taylor expansion in cases where the RMP series of the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
 More quantitatively, Table \ref{tab:PadeRMP} gathers estimates of the RMP ground-state energy at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e approximants for these two values of the ratio $U/t$.
-While the truncated Taylor series converges laboriously to the exact energy at $U/t = 3.5$ when one increases the truncation degree, the Pad\'e approximants yield much more accurate results with, additionally, a rather good estimate of the radius of convergence of the RMP series.
-For $U/t = 4.5$, the struggles of the truncated Taylor expansions are magnified and the Pad\'e approximants still provide quite accurate energies even outside the radius of convergence of the RMP series.
+While the truncated Taylor series converges laboriously to the exact energy as the truncation degree increases at $U/t = 3.5$, the Pad\'e approximants yield much more accurate results.
+\hugh{Furthermore, the Pad\'e approximants provide a rather good estimate of the radius of convergence of the RMP series.}
+For $U/t = 4.5$, the Taylor series expansion performs worse (and eventually diverges),
+while the Pad\'e approximants still offer relaitively accurate energies even outside the radius of convergence of the RMP series.
+
+\hugh{%
+We can expect that the singularity structure of the UMP energy will be much more challenging to model properly as the UMP energy function contains three connected branches (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
+Figure~\ref{fig:QuadUMP} and Table~\ref{tab:QuadUMP} indicate that this is indeed the case. 
+However, with sufficiently high degree polynomials, one obtains
+accurate estimates of both the radius of convergence and the ground-state energy at $\lambda = 1$,
+even in cases where the convergence of the UMP series is incredibly slow 
+(see Fig.~\ref{subfig:UMP_cvg}).
+In Figure \ref{fig:QuadUMP}, it becomes clear that the Pad\'e approximants are trying to model
+the square root branch point that lies close to $\lambda = 1$ by placing a pole on the real axis
+(for [3/3]) or with a very small imaginary component (for [4/4]).
+The proximity of these poles to the radius of convergence means that any error in the Pad\'e 
+functional form becomes magnified in the estimate of energy at $\lambda = 1$.
+}
 
@@
 %==========================================%
-\subsection{Quadratic approximant}
+\subsection{Quadratic Approximant}
 %==========================================%
-In a nutshell, the idea behind quadratic approximant is to model the singularity structure of the energy function $E(\lambda)$ via a generalised version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
+Quadratic approximants \hugh{are designed} to model the singularity structure of the energy function $E(\lambda)$ via a generalised version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
 \begin{equation}
@@
 \end{equation}
-where 
+with the polynomials 
 \begin{align}
@@
 \end{align}
-are polynomials, such that $d_P + d_Q + d_R = n - 1$, and $n$ is the truncation order of the Taylor series of $E(\lambda)$.
+defined such that $d_P + d_Q + d_R = n - 1$, and $n$ is the truncation order of the Taylor series of $E(\lambda)$.
 Recasting Eq.~\eqref{eq:QuadApp} as a second-order expression in $E(\lambda)$, \ie,
@@
 The diagonal sequence of quadratic approximant, \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, is of particular interest.
-Note that, by construction, a quadratic approximant has only two branches which hampers the faithful description of more complicated singularity structures.
+However, by construction, a quadratic approximant has only two branches, which hampering the faithful description of more complicated singularity structures.
 As shown in Ref.~\onlinecite{Goodson_2000a}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}
 
-For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximation, but its $[1/0,1]$ version already model perfectly the RMP energy function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
-This is expected knowing the form of the RMP energy [see Eq.~\eqref{eq:E0MP}] which perfectly suits the purpose of quadratic approximants.
-
-We can anticipate that the singularity structure of the UMP energy function is going to be much more challenging to model properly, and this is indeed the case as the UMP energy function contains three branches (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
-However, by ramping up high enough the degree of the polynomials, one is able to get both, as shown in Fig.~\ref{fig:QuadUMP} and Table \ref{tab:QuadUMP}, accurate estimates of the radius of convergence of the UMP series and of the ground-state energy at $\lambda = 1$, even in cases where the convergence of the UMP series is painfully slow (see Fig.~\ref{subfig:UMP_cvg}).
-Figure \ref{fig:QuadUMP} evidences that the Pad\'e approximants are trying to model the square root singularity by placing a pole on the real axis (for [3/3]) or just off the real axis (for [4/4]).
-Thanks to greater flexibility, the quadratic approximants are able to model nicely the avoided crossing and the location of the singularities. 
-Besides, they provide accurate estimates of the ground-state energy at $\lambda = 1$ (see Table \ref{tab:QuadUMP}).
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
+This is expected from the form of the RMP energy [see Eq.~\eqref{eq:E0MP}], which matches the ideal target for quadratic approximants.
 
@@
 			\hline
-			Pad\'e		&	[3/3]	&	6		&					&	$1.141$		&	$1.004$		&	$-1.10896$	&	$-1.49856$	\\
+			Pad\'e		&	[1/1]	&	2		&					&	$9.000$		&	$49.00$		&	$-0.75000$	&	$-0.29167$	\\
+                        &	[2/2]	&	4		&					&	$0.974$		&	$1.003$		&	$\hphantom{-}0.75000$	&	$-17.9375$	\\
+			         	&	[3/3]	&	6		&					&	$1.141$		&	$1.004$		&	$-1.10896$	&	$-1.49856$	\\
 						&	[4/4]	&	8		&					&	$1.068$		&	$1.003$		&	$-0.85396$	&	$-0.33596$	\\
@@
 \end{table}
-
-An interesting point raised in Ref.~\onlinecite{Goodson_2019} suggests that low-order quadratic approximants might struggle to model the correct singularity structure when the energy function has poles in both the positive and negative half-planes.
-In such a scenario, the quadratic approximant will have the tendency to place its branch points in-between, potentially introducing singularities quite close to the origin.
-A simple potential cure for this consists in applying a judicious transformation (like a bilinear conformal mapping) which does not affect the points at $\lambda = 0$ and $\lambda = 1$.
+\hugh{On the other hand, the greater flexibility of the quadratic approximants provides a significantly
+improved model of the UMP energy in comparison to the Pad\' approximants or Taylor series.
+In particular, the quadratic approximants provide an effect model for the avoided crossings 
+(Fig.~\ref{fig:QuadUMP}) and a far better estimate for the location of the branch point singularities.
+Furthermore, they provide remarkably accurate estimates of the ground-state energy at $\lambda = 1$, 
+as shown in Table~\ref{tab:QuadUMP}}
+
+However, as a note of caution, Ref.~\onlinecite{Goodson_2019} suggests that low-order 
+quadratic approximants can struggle to correctly model the singularity structure when 
+the energy function has poles in both the positive and negative half-planes. 
+In such a scenario, the quadratic approximant will tend to place its branch points in-between, potentially introducing singularities quite close to the origin.
+The remedy for this problem involves applying a suitable transformation of the complex plane (such as a bilinear conformal mapping) which leaves the points at $\lambda = 0$ and $\lambda = 1$ unchanged.
 \cite{Feenberg_1956}
+
+%==========================================%
+\subsection{Shanks Transformation}
+%==========================================%
+
+While the Pad\'e and quadratic approximants can yield a convergent series representation
+in cases where the standard MP series diverges, there is no guarantee that the rate of convergence
+will be fast enough for low-order approximations to be useful.
+However, these low-order partial sums or approximants often contain a remarkable amount of information
+that can be used to extract further information about the exact result.
+The Shanks transformation presents one approach for extracting this information
+and accelerating the rate of convergence of a sequence.\cite{Shanks_1955}
+
+Consider the partial sums $S_N$ defined from the truncated summation of an infinite series
+\begin{equation}
+    S_N = \sum_{k=0}^{N} a_k.
+\end{equation}
+If the series converges, then the partial sums will tend to the exact result in the limit $N\rightarrow \infty$.
+The Shanks transformation attempts to generate increasingly accurate estimates of the
+exact result by defining a new series as
+\begin{equation}
+    T(S_N) = \frac{S_{N+1} S_{N-1} - S_{N}^2}{S_{N+1} + S_{N-1} - 2 S_{N}}.
+\end{equation}
+This series can converge faster than the original partial sums and can thus provide greater
+accuracy using only the first few terms in the series.
 

### 2020-12-02 Manuscript/EPAWTFT.tex
comment in conclusion

--- 2020-12-01 Manuscript/EPAWTFT.tex
@@
 
-In order to model accurately chemical systems, one must choose, in a ever growing zoo of methods, which computational protocol is adapted to the system of interest.
+In order to model accurately chemical systems, one must choose, in an ever growing zoo of methods, which computational protocol is adapted to the system of interest.
 This choice can be, moreover, motivated by the type of properties that one is interested in.
@@
 
+\titou{The Hubbard dimer is clearly a very versatile model to understand perturbation theory and could be used for further developments around PT.
+Comment on approximants are requiring higher order MP which is expensive.
+Paragraph  on Paola's stuff.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-02 Manuscript/EPAWTFT.tex
proposition sentenceabout critical points and functional form
conclusion

@@
 radius of convergence (see Fig.~\ref{fig:RadConv}).
-
-%%====================================================
-%\subsection{The physics of quantum phase transitions}
-%%====================================================
-%
-%In the previous section, we saw that a careful analysis of the structure of the Hamiltonian allows us to predict the existence of a critical point. 
-%In a finite basis set, this critical point is model by a cluster of $\beta$ singularities. 
-%It is now well known that this phenomenon is a special case of a more general phenomenon. 
-%Indeed, theoretical physicists proved that EPs close to the real axis are connected to \textit{quantum phase transitions} (QPTs).
-\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook}
-%In quantum mechanics, the Hamiltonian is almost always dependent of, at least, one parameter. 
-%In some cases the variation of a parameter can lead to abrupt changes at a critical point. 
-%These QPTs exist both for ground and excited states as shown by Cejnar and coworkers.
-\cite{Cejnar_2005,Cejnar_2007,Caprio_2008,Cejnar_2009,Sachdev_2011,Cejnar_2015,Cejnar_2016, Macek_2019,Cejnar_2020}
-%A ground-state QPT is characterised by the derivatives of the ground-state energy with respect to a non-thermal control parameter. \cite{Cejnar_2009, Sachdev_2011} 
-%The transition is called discontinuous and of first order if the first derivative is discontinuous at the critical parameter value. 
-%Otherwise, it is called continuous and of $m$th order (with $m \ge 2$) if the $m$th derivative is discontinuous. 
-%A QPT can also be identify by the discontinuity of an appropriate order parameter (or one of its derivatives). 
-%
-%The presence of an EP close to the real axis is characteristic of a sharp avoided crossing. 
-%Yet, at such an avoided crossing, eigenstates change abruptly. 
-%Although it is now well understood that EPs are closely related to QPTs, the link between the type of QPT (ground state or excited state, first or higher order) and EPs still need to be clarified. 
-%One of the major obstacles that one faces in order to achieve this resides in the ability to compute the distribution of EPs. 
-%The numerical assignment of an EP to two energies on the real axis is very difficult in large dimensions. 
-%Hence, the design of specific methods are required to get information on the location of EPs. 
-%Following this idea, Cejnar \textit{et al.}~developed a method based on a Coulomb analogy giving access to the density of EP close to the real axis. \cite{Cejnar_2005, Cejnar_2007} 
-%More recently Stransky and coworkers proved that the distribution of EPs is characteristic of the QPT order. \cite{Stransky_2018} 
-%In the thermodynamic limit, some of the EPs converge towards a critical point $\lambda_\text{c}$ on the real axis. 
-%They showed that, within the interacting boson model, \cite{Lipkin_1965} EPs associated to first- and second-order QPT behave differently when the number of particles increases. 
-%The position of these singularities converge towards the critical point on the real axis at different rates (exponentially and algebraically for the first and second orders, respectively) with respect to the number of particles.
-%
-%Moreover, Cejnar \textit{et al.}~studied the so-called shape-phase transitions of the interaction boson model from a QPT point of view. \cite{Cejnar_2000, Cejnar_2003, Cejnar_2007a, Cejnar_2009}
-%The phase of the ensemble of $s$ and $d$ bosons is characterised by a dynamical symmetry. 
-%When a parameter is continuously modified the dynamical symmetry of the system can change at a critical value of this parameter, leading to a deformed phase. 
-%They showed that at this critical value of the parameter, the system undergoes a QPT. 
-%For example, without interaction the ground state is the spherical phase (a condensate of $s$ bosons) and when the interaction increases it leads to a deformed phase constituted of a mixture of $s$ and $d$ bosons states.
-%In particular, we see that the transition from the spherical phase to the axially symmetric one is analog to the symmetry breaking of the wave function of the hydrogen molecule when the bond is stretched.
-\cite{SzaboBook}
-%It seems like our understanding of the physics of spatial and/or spin symmetry breaking in HF theory can be enlightened by QPT theory. 
-%Indeed, the second derivative of the HF ground-state energy is discontinuous at the point of spin symmetry-breaking which means that the system undergo a second-order QPT. 
-%
-%Moreover, the $\beta$ singularities introduced by Sergeev and coworkers to describe the EPs modelling the formation of a bound cluster of electrons are actually a more general class of singularities.
-%The EPs close to the real axis (the so-called $\beta$ singularities) are connected to QPT because they result from a sharp avoided crossings at which the eigenstates change quickly. 
-%However, the $\alpha$ singularities arise from large avoided crossings. 
-%Thus, they cannot be connected to QPT. 
-%The avoided crossings generating $\alpha$ singularities generally involve the ground state and low-lying doubly-excited states. 
-%Those excited states have a non-negligible contribution to the exact FCI solution because they have (usually) the same spatial and spin symmetry as the ground state. 
-%We believe that $\alpha$ singularities are connected to states with non-negligible contribution in the CI expansion thus to the dynamical part of the correlation energy, while $\beta$ singularities are linked to symmetry breaking and phase transitions of the wave function, \ie, to the multi-reference nature of the wave function thus to the static part of the correlation energy.
 
@@
 That means that one must understand the strengths and weaknesses of each method, \ie, why one method might fail in some cases and work beautifully in others. 
-We have seen that for methods relying on perturbation theory, their successes and failures are directly connected to the position of EPs in the complex plane. 
-Exhaustive studies have been performed on the causes of failure of MP perturbation theory. 
-First, it was understood that, for chemical systems for which the HF Slater determinant is a poor approximation to the exact wave function, MP perturbation theory fails too. 
-Such systems can be, for example, molecules where the exact ground-state wave function is dominated by more than one configuration, \ie, multi-reference systems. 
-More preoccupying cases were also reported. 
-For instance, it has been shown that systems considered as well understood (\eg, \ce{Ne}) can exhibit divergent behaviour when the basis set is augmented with diffuse functions. 
-Later, these erratic behaviours of the perturbation series were investigated and rationalised in terms of avoided crossings and singularities in the complex plane. 
-It was shown that the singularities can be classified in two families. 
-The first family includes $\alpha$ singularities resulting from a large avoided crossing between the ground state and a low-lying doubly-excited states. 
-The $\beta$ singularities, which constitutes the second family, are artefacts generated by the incompleteness of the Hilbert space, and they are directly connected to an ionisation phenomenon occurring in the complete Hilbert space.
-These singularities are close to the real axis and connected with sharp avoided crossing between the ground state and a highly diffuse state. 
-We have found that the $\beta$ singularities modelling the ionisation phenomenon described by Sergeev and Goodson are actually part of a more general class of singularities. 
-Indeed, those singularities close to the real axis are connected to quantum phase transitions and symmetry breaking, and theoretical physics have demonstrated that the behaviour of the EPs depends of the type of transitions from which the EPs result (first or higher orders, ground state or excited state transitions).
-To conclude, this work shows that our understanding of the singularity structure of the energy is still incomplete but we hope that it opens new perspectives for the understanding of the physics of EPs in electronic structure theory.
-
-\titou{The Hubbard dimer is clearly a very versatile model to understand perturbation theory and could be used for further developments around PT.
-Comment on approximants are requiring higher order MP which is expensive.
-Paragraph  on Paola's stuff.}
+We have seen that for methods relying on perturbation theory, their successes and failures are directly connected to the position of singularities in the complex plane, known as exceptional points.
+
+After a short presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we have provided an exhaustive historical overview of the various research activities that have been performed on the physics of singularities with a particular focus on M{\o}ller--Plesset perturbation theory.
+Seminal contributions from various research groups around the world have evidenced highly oscillatory, slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988}
+
+Later, these erratic behaviours were investigated and rationalised in terms of avoided crossings and singularities in the complex plane. 
+In that regard, it is worth highlighting the key contribution of Cremer and He who proposed a classification of the types of convergence: \cite{Cremer_1996} ``class A'' systems that exhibit monotonic convergence, and ``class B'' systems for which convergence is erratic after initial oscillations.
+Further insights were brought thanks to a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employ a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
+Building on the careful mathematical analysis of Stillinger who showed that the mathematical origin behind the divergent series with odd-even sign alternation is due to a dominant singularity on the negative real $\lambda$ axis, \cite{Stillinger_2000} Sergeev and Goodson proposed a more refined singularity classification: $\alpha$ singularities which have ``large'' imaginary parts, and $\beta$ singularities which have very small imaginary parts.
+\cite{Goodson_2000a,Goodson_2000b,Goodson_2004,Sergeev_2005,Sergeev_2006}
+We have further highlighted that these so-called $\beta$ singularities are connected to quantum phase transitions and symmetry breaking.
+
+Finally, we have discussed several resummation techniques, such as Pad\'e and quadratic approximants, that can be used to improve energy estimates for both convergent and divergent series.
+However, it is worth mentioning that the construction of these approximants requires high-order MP coefficients which are quite expensive to compute in practice.
+
+Most of the concepts reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
+Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand perturbation theory as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} and many others.
+We believe that the Hubbard dimer could then be used for further developments around perturbation theory.
+
+As a concluding remark and from a broader point of view, the present work shows that our understanding of the singularity structure of the energy is still incomplete.
+Yet, we hope that the present contribution will open new perspectives for the understanding of the physics of exceptional points in electronic structure theory.
 

### 2020-12-02 Manuscript/EPAWTFT.tex
local changes

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 \newcommand{\lc}{\lambda_{\text{c}}}
+\newcommand{\lp}{\lambda_{\text{p}}}
 \newcommand{\lep}{\lambda_{\text{EP}}}
@@
 \begin{quote}
-	\textit{``In the limit of large order, the series coefficients become equivalent to the Taylor series coefficients of the singularity closest to the origin. ''}
+\textit{``In the limit of large order, the series coefficients become equivalent to 
+    the Taylor series coefficients of the singularity closest to the origin. ''}
 \end{quote}
@@
 where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms for each power of $\lambda$.
-Pad\'e approximants are extremely useful in many areas of physics and chemistry \cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, which appears at the locations of the roots of $B(\lambda)$.
-However, they are unable to model functions with square-root branch points (which are ubiquitous in the singularity structure of a typical perturbative treatment) and more complicated functional forms appearing at critical points (where the nature of the solution undergoes a sudden transition).
+Pad\'e approximants are extremely useful in many areas of physics and 
+chemistry\cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, 
+which appears at the locations of the roots of $B(\lambda)$. 
+However, they are unable to model functions with square-root branch points 
+(which are ubiquitous in the singularity structure of a typical perturbative treatment) 
+and more complicated functional forms appearing at critical points (
+where the nature of the solution undergoes a sudden transition).
 \hugh{Despite this limitation, the successive diagonal Pad\'e approximants (\ie, $d_A = d_B $) 
@@
 
-Figure \ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e approximants compared to the usual Taylor expansion in cases where the RMP series of the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
-More quantitatively, Table \ref{tab:PadeRMP} gathers estimates of the RMP ground-state energy at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e approximants for these two values of the ratio $U/t$.
-While the truncated Taylor series converges laboriously to the exact energy as the truncation degree increases at $U/t = 3.5$, the Pad\'e approximants yield much more accurate results.
-\hugh{Furthermore, the Pad\'e approximants provide a rather good estimate of the radius of convergence of the RMP series.}
-For $U/t = 4.5$, the Taylor series expansion performs worse (and eventually diverges),
-while the Pad\'e approximants still offer relaitively accurate energies even outside the radius of convergence of the RMP series.
+Fig.~\ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e 
+approximants compared to the usual Taylor expansion in cases where the RMP series of 
+the Hubbard dimer converges ($U/t = 3.5$) and diverges ($U/t = 4.5$).
+More quantitatively, Table \ref{tab:PadeRMP} gathers estimates of the RMP ground-state 
+energy at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e 
+approximants for these two values of the ratio $U/t$.
+While the truncated Taylor series converges laboriously to the exact energy as the truncation 
+degree increases at $U/t = 3.5$, the Pad\'e approximants yield much more accurate results.
+\hugh{Furthermore, the position of the closest pole to origin $\lc$ in the Pad\'e approximants 
+indicate that they a relatively good approximation to the true branch point singularity in the RMP energy.
+For $U/t = 4.5$, the Taylor series expansion performs worse and eventually diverges,
+while the Pad\'e approximants still offer relaitively accurate energies and recovers
+a convergent series.}
 
 \hugh{%
-We can expect that the singularity structure of the UMP energy will be much more challenging to model properly as the UMP energy function contains three connected branches (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
-Figure~\ref{fig:QuadUMP} and Table~\ref{tab:QuadUMP} indicate that this is indeed the case. 
+We can expect that the singularity structure of the UMP energy will be much more challenging 
+to model properly as the UMP energy function contains three connected branches 
+(see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
+Fig.~\ref{fig:QuadUMP} and Table~\ref{tab:QuadUMP} indicate that this is indeed the case. 
+In particular, Fig.~\ref{fig:QuadUMP} illustrates that the Pad\'e approximants are trying to model
+the square root branch point that lies close to $\lambda = 1$ by placing a pole on the real axis
+(\eg, [3/3]) or with a very small imaginary component (\eg, [4/4]).
+The proximity of these poles to the physical point $\lambda = 1$ means that any error in the Pad\'e 
+functional form becomes magnified in the estimate of exact energy, as seen for the low-order
+approximants in Table~\ref{tab:QuadUMP}.
 However, with sufficiently high degree polynomials, one obtains
-accurate estimates of both the radius of convergence and the ground-state energy at $\lambda = 1$,
+accurate estimates for the position of the closest singularity and the ground-state energy at $\lambda = 1$,
 even in cases where the convergence of the UMP series is incredibly slow 
 (see Fig.~\ref{subfig:UMP_cvg}).
-In Figure \ref{fig:QuadUMP}, it becomes clear that the Pad\'e approximants are trying to model
-the square root branch point that lies close to $\lambda = 1$ by placing a pole on the real axis
-(for [3/3]) or with a very small imaginary component (for [4/4]).
-The proximity of these poles to the radius of convergence means that any error in the Pad\'e 
-functional form becomes magnified in the estimate of energy at $\lambda = 1$.
 }
@@
 \begin{table}
-	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
-	We also report the estimate of the radius of convergence $r_c$ provided by the diagonal Pad\'e approximants.
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor 
+    series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
+    We also report the \hugh{closest pole to the origin $\lc$} provided by the diagonal Pad\'e approximants.
 	\label{tab:PadeRMP}}
@@
 		\begin{tabular}{lccccc}
-						&			&	\mc{2}{c}{$r_c$}			&	\mc{2}{c}{$E_{-}(\lambda = 1)$}			\\
+						&			&	\mc{2}{c}{$\lc$}	&	\mc{2}{c}{$E_{-}(\lambda = 1)$} \\
 																		\cline{3-4} \cline{5-6}
@@
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
+    RMP ground-state energy as a function of $\lambda$ obtained using various resummation 
+    techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
 \end{figure*}
@@
 %==========================================%
-Quadratic approximants \hugh{are designed} to model the singularity structure of the energy function $E(\lambda)$ via a generalised version of the square-root singularity expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
+Quadratic approximants \hugh{are designed} to model the singularity structure of the energy 
+function $E(\lambda)$ via a generalised version of the square-root singularity 
+expression \cite{Mayer_1985,Goodson_2011,Goodson_2019}
 \begin{equation}
@@
 \end{equation}
-and substituting $E(\lambda$) by its $n$th-order expansion and the polynomials by their respective expressions \eqref{eq:PQR} yields $n+1$ linear equations for the coefficients $p_k$, $q_k$, and $r_k$ (where we are free to assume that $q_0 = 1$).
-A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, $n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$.
-The diagonal sequence of quadratic approximant, \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, is of particular interest.
-However, by construction, a quadratic approximant has only two branches, which hampering the faithful description of more complicated singularity structures.
-As shown in Ref.~\onlinecite{Goodson_2000a}, quadratic approximants provide convergent results in the most divergent cases considered by Olsen and collaborators \cite{Christiansen_1996,Olsen_1996} and Leininger \etal \cite{Leininger_2000}
-
-For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
-This is expected from the form of the RMP energy [see Eq.~\eqref{eq:E0MP}], which matches the ideal target for quadratic approximants.
+and substituting $E(\lambda$) by its $n$th-order expansion and the polynomials by 
+their respective expressions \eqref{eq:PQR} yields $n+1$ linear equations for the coefficients 
+$p_k$, $q_k$, and $r_k$ (where we are free to assume that $q_0 = 1$).
+A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, 
+$n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$ \hugh{and $d_q$ poles at the roots of $Q(\lambda)$}.
+Generally, the diagonal sequence of quadratic approximant, 
+\ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, 
+is of particular interest \hugh{as the order of the corresponding Taylor series increases on each step.
+However, while a quadratic approximant can reproduce multiple branch points, it can only describe 
+a total of two branches.
+Since every branch point must therefore correspond to a degeneracy of the same two branches, this constraint
+can hamper the faithful description of more complicated singularity structures such as the MP energy surface.
+Despite this limitiation,} Ref.~\onlinecite{Goodson_2000a} demonstrates that quadratic approximants 
+provide convergent results in the most divergent cases considered by Olsen and 
+collaborators\cite{Christiansen_1996,Olsen_1996} 
+and Leininger \etal \cite{Leininger_2000}
+
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant 
+are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy
+function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
+This is expected from the form of the RMP energy [see Eq.~\eqref{eq:E0MP}], which matches 
+the ideal target for quadratic approximants.
 
@@
 \begin{table}
-	\caption{Estimate of the radius of convergence $r_c$ of the UMP energy function provided by various resummation techniques at $U/t = 3$ and $7$.
-	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch points $n_\text{bp} = \max(2d_p,d_q+d_r)$ generated by the quadratic approximants are also reported.
+	\caption{Estimate of the radius of convergence $r_c$ of the UMP energy function provided 
+    by various resummation techniques at $U/t = 3$ and $7$.
+	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch 
+    points $n_\text{bp} = \max(2d_p,d_q+d_r)$ generated by the quadratic approximants are also reported.
 	\label{tab:QuadUMP}}
@@
 		\begin{tabular}{lccccccc}
-						&			&			&					&	\mc{2}{c}{$r_c$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
+						&			&			&					&	\mc{2}{c}{$\lp$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
 																		\cline{5-6}\cline{7-8}
@@
 \end{table}
-\hugh{On the other hand, the greater flexibility of the quadratic approximants provides a significantly
-improved model of the UMP energy in comparison to the Pad\' approximants or Taylor series.
-In particular, the quadratic approximants provide an effect model for the avoided crossings 
+
+\hugh{On the other hand, the greater flexibility of the diagonal quadratic approximants provides a significantly
+improved model of the UMP energy in comparison to the Pad\'e approximants or Taylor series.
+In particular, these quadratic approximants provide an effect model for the avoided crossings 
 (Fig.~\ref{fig:QuadUMP}) and a far better estimate for the location of the branch point singularities.

### 2020-12-02 Manuscript/EPAWTFT.tex

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 \newcommand{\trashHB}[1]{\textcolor{orange}{\sout{#1}}}
+\newcommand{\antoine}[1]{\textcolor{cyan}{#1}}
 
@@
 }
+\antoine{However, their complicated functional forms makes it difficult to know if they belong to a given class of singularities.
+Thus it is not clear if critical points can be sorted in one mathematical class of singularities or not.
+To the best of our knowledge, this question is still open.}
 

### 2020-12-02 Manuscript/EPAWTFT.tex
Added more discussion about quadratics...

@@
 
+%%%%%%%%%%%%%%%%%
+\begin{figure*}
+    \includegraphics[height=0.23\textheight]{PadeRMP35}
+    \includegraphics[height=0.23\textheight]{PadeRMP45}
+    \caption{\label{fig:PadeRMP}
+    RMP ground-state energy as a function of $\lambda$ obtained using various resummation 
+    techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
+\end{figure*}
+%%%%%%%%%%%%%%%%%
+
 %As frequently claimed by Carl Bender, 
@@
 %==========================================%
+
 \hugh{The failure of a Taylor series for correctly modelling the MP energy function $E(\lambda)$ 
-arises because one is trying to model a complicated function containing branch points and
+arises because one is trying to model a complicated function containing multiple branches, branch points and
 singularities} using a simple polynomial of finite order.
-A truncated Taylor series just does not have enough flexibility to do the job properly.
+A truncated Taylor series \hugh{can only predict a single sheet and} does not have enough 
+flexibility to adequately describe the MP energy.
 Alternatively, the description of complex energy functions can be significantly improved
@@
 
+\begin{table}[b]
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor 
+    series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
+    We also report the \hugh{closest pole to the origin $\lc$} provided by the diagonal Pad\'e approximants.
+	\label{tab:PadeRMP}}
+	\begin{ruledtabular}
+		\begin{tabular}{lccccc}
+            &			&	\mc{2}{c}{$\abs{\lc}$}	&	\mc{2}{c}{$E_{-}(\lambda = 1)$} \\
+																		\cline{3-4} \cline{5-6}
+			Method		&	degree	&	$U/t = 3.5$	&	$U/t = 4.5$	&	$U/t = 3.5$	&	$U/t = 4.5$	\\
+			\hline
+			Taylor		&	2		&			&			&	$-1.01563$	&	$-1.01563$	\\
+						&	3		&			&			&	$-1.01563$	&	$-1.01563$	\\
+						&	4		&			&			&	$-0.86908$	&	$-0.61517$	\\
+						&	5		&			&			&	$-0.86908$	&	$-0.61517$	\\
+						&	6		&			&			&	$-0.92518$	&	$-0.86858$	\\
+            \hline
+			Pad\'e		&	[1/1]	&	$2.29$	&	$1.78$	&	$-1.61111$	&	$-2.64286$	\\
+						&	[2/2]	&	$2.29$	&	$1.78$	&	$-0.82124$	&	$-0.48446$	\\
+						&	[3/3]	&	$1.73$	&	$1.34$	&	$-0.91995$	&	$-0.81929$	\\
+						&	[4/4]	&	$1.47$	&	$1.14$	&	$-0.90579$	&	$-0.74866$	\\
+						&	[5/5]	&	$1.35$	&	$1.05$	&	$-0.90778$	&	$-0.76277$	\\
+			\hline
+			Exact		&			&	$1.14$	&	$0.89$	&	$-0.90754$	&	$-0.76040$	\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
+
 Fig.~\ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e 
@@
 degree increases at $U/t = 3.5$, the Pad\'e approximants yield much more accurate results.
-\hugh{Furthermore, the position of the closest pole to origin $\lc$ in the Pad\'e approximants 
-indicate that they a relatively good approximation to the true branch point singularity in the RMP energy.
+\hugh{Furthermore, the distance of the closest pole to origin $\abs{\lc}$ in the Pad\'e approximants 
+indicate that they a relatively good approximation to the position of the 
+true branch point singularity in the RMP energy.
 For $U/t = 4.5$, the Taylor series expansion performs worse and eventually diverges,
@@
 
+%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \includegraphics[width=\linewidth]{QuadUMP}
+    \caption{\label{fig:QuadUMP}
+    UMP energies as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3$.}
+\end{figure}
+%%%%%%%%%%%%%%%%%
+
 \hugh{%
-We can expect that the singularity structure of the UMP energy will be much more challenging 
-to model properly as the UMP energy function contains three connected branches 
+We can expect the UMP energy function to be much more challenging 
+to model properly as it contains three connected branches 
 (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
@@
 
-\begin{table}
-	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor 
-    series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
-    We also report the \hugh{closest pole to the origin $\lc$} provided by the diagonal Pad\'e approximants.
-	\label{tab:PadeRMP}}
-	\begin{ruledtabular}
-		\begin{tabular}{lccccc}
-						&			&	\mc{2}{c}{$\lc$}	&	\mc{2}{c}{$E_{-}(\lambda = 1)$} \\
-																		\cline{3-4} \cline{5-6}
-			Method		&	degree	&	$U/t = 3.5$	&	$U/t = 4.5$	&	$U/t = 3.5$	&	$U/t = 4.5$	\\
-			\hline
-			Taylor		&	2		&			&			&	$-1.01563$	&	$-1.01563$	\\
-						&	3		&			&			&	$-1.01563$	&	$-1.01563$	\\
-						&	4		&			&			&	$-0.86908$	&	$-0.61517$	\\
-						&	5		&			&			&	$-0.86908$	&	$-0.61517$	\\
-						&	6		&			&			&	$-0.92518$	&	$-0.86858$	\\
-			Pad\'e		&	[1/1]	&	$2.29$	&	$1.78$	&	$-1.61111$	&	$-2.64286$	\\
-						&	[2/2]	&	$2.29$	&	$1.78$	&	$-0.82124$	&	$-0.48446$	\\
-						&	[3/3]	&	$1.73$	&	$1.34$	&	$-0.91995$	&	$-0.81929$	\\
-						&	[4/4]	&	$1.47$	&	$1.14$	&	$-0.90579$	&	$-0.74866$	\\
-						&	[5/5]	&	$1.35$	&	$1.05$	&	$-0.90778$	&	$-0.76277$	\\
-			\hline
-			Exact		&			&	$1.14$	&	$0.89$	&	$-0.90754$	&	$-0.76040$	\\
-		\end{tabular}
-	\end{ruledtabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%
-\begin{figure*}
-    \includegraphics[height=0.23\textheight]{PadeRMP35}
-    \includegraphics[height=0.23\textheight]{PadeRMP45}
-    \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained using various resummation 
-    techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
-\end{figure*}
-%%%%%%%%%%%%%%%%%
-
 %==========================================%
@@
 $n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$ \hugh{and $d_q$ poles at the roots of $Q(\lambda)$}.
+
 Generally, the diagonal sequence of quadratic approximant, 
@@
 
-For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant 
-are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy
-function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm i 4t/U$.
-This is expected from the form of the RMP energy [see Eq.~\eqref{eq:E0MP}], which matches 
-the ideal target for quadratic approximants.
-
-%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \includegraphics[width=\linewidth]{QuadUMP}
-    \caption{\label{fig:QuadUMP}
-    UMP energies as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3$.}
-\end{figure}
-%%%%%%%%%%%%%%%%%
-
-\begin{table}
-	\caption{Estimate of the radius of convergence $r_c$ of the UMP energy function provided 
+As a note of caution, Ref.~\onlinecite{Goodson_2019} suggests that low-order 
+quadratic approximants can struggle to correctly model the singularity structure when 
+the energy function has poles in both the positive and negative half-planes. 
+In such a scenario, the quadratic approximant will tend to place its branch points in-between, potentially introducing singularities quite close to the origin.
+The remedy for this problem involves applying a suitable transformation of the complex plane (such as a bilinear conformal mapping) which leaves the points at $\lambda = 0$ and $\lambda = 1$ unchanged.
+\cite{Feenberg_1956}
+
+\begin{table}[b]
+    \caption{Estimate \hugh{for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$}
+    in the UMP energy function provided 
     by various resummation techniques at $U/t = 3$ and $7$.
@@
 		\begin{tabular}{lccccccc}
-						&			&			&					&	\mc{2}{c}{$\lp$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
+            &			&			&					&	\mc{2}{c}{$\abs{\lc}$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
 																		\cline{5-6}\cline{7-8}
 			\mc{2}{c}{Method}		&	$n$		&	$n_\text{bp}$	&	$U/t = 3$	&	$U/t = 7$	&	$U/t = 3$	&	$U/t = 7$	\\
+			\hline
+			Taylor		&	     	&	2		&					&	    		&	    		&	$-0.74074$	&	$-0.29155$	\\
+                        &	     	&	3		&					&	    		&	    		&	$-0.78189$	&	$-0.29690$	\\
+			         	&	     	&	4		&					&	    		&	    		&	$-0.82213$	&	$-0.30225$	\\
+						&	     	&	5		&					&	    		&	    		&	$-0.85769$	&	$-0.30758$	\\
+                        &	     	&   6		&					&	    		&	    		&	$-0.88882$	&	$-0.31289$	\\
 			\hline
@@
                         &	[5/5]	&	10		&					&	$1.122$		&	$1.004$		&	$-0.97254$	&	$-0.35513$	\\
+            \hline
 			Quadratic	&	[2/1,2]	&	6		&	4				&	$1.086$		&	$1.003$		&	$-1.01009$	&	$-0.53472$	\\
@@
 						&	[3/2,3]	&	9		&	6				&	$1.071$		&	$1.002$		&	$-0.99973$	&	$-0.53102$	\\
-						&	[3/3,3]	&	10		&	6				&	$1.071$		&	$1.002$		&	$-0.99966$	&	$-0.53103$	\\
+                        &	[3/3,3]	&	10		&	6				&	$1.071$		&	$1.002$		&	$-0.99966$	&	$-0.53103$	\\[0.5ex]
+            (pole-free)	&	[3/0,2]	&	6		&	6				&	$1.059$	    &	$1.003$ 	&	$-1.13712$	&	$-0.57199$	\\
+		                &	[3/0,3]	&	7		&	6				&	$1.073$		&	$1.002$		&	$-1.00335$	&	$-0.53113$	\\
+						&	[3/0,4]	&	8		&	6				&	$1.071$		&	$1.002$		&	$-1.00074$	&	$-0.53116$	\\
+						&	[3/0,5]	&	9		&	6				&	$1.070$		&	$1.002$		&	$-1.00042$	&	$-0.53114$	\\
+						&	[3/0,6]	&	10		&	6				&	$1.070$		&	$1.002$		&	$-1.00039$	&	$-0.53113$	\\
 			\hline
@@
 
-\hugh{On the other hand, the greater flexibility of the diagonal quadratic approximants provides a significantly
+\begin{figure*}
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.85\textwidth]{ump_qa322}	
+    \subcaption{\label{subfig:ump_ep_to_cp} [3/2,2] Quadratic}
+    \end{subfigure}
+    %
+    \begin{subfigure}{0.32\textwidth}
+	\includegraphics[height=0.85\textwidth]{ump_exact}
+		\subcaption{\label{subfig:ump_cp_surf} Exact}
+    \end{subfigure}
+    %
+	\begin{subfigure}{0.32\textwidth}
+        \includegraphics[height=0.85\textwidth]{ump_qa304}	
+    \subcaption{\label{subfig:ump_cp} [3/0,4] Quadratic}
+    \end{subfigure}
+\caption{%
+\hugh{% 
+Comparison of the [3/2,2] and [3/0,4] quadratic approximants with the exact UMP energy surface in the complex $\lambda$ 
+plane with $U/t = 3$. 
+Both quadratic approximants correspond to the same truncation degree of the Taylor series and model the branch points 
+using a radicand polynomial of the same order.
+However, the [3/2,2] approximant introduces poles into the surface that limits it accuracy, while the [3/0,4] approximant
+is free of poles.}
+\label{fig:nopole_quad}}
+\end{figure*}
+
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant 
+are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy
+function by predicting a single pair of EPs at $\lambda_\text{EP} = \pm \i 4t/U$.
+This is expected from the form of the RMP energy [see Eq.~\eqref{eq:E0MP}], which matches 
+the ideal target for quadratic approximants.
+\hugh{%
+Furthermore, the greater flexibility of the diagonal quadratic approximants provides a significantly
 improved model of the UMP energy in comparison to the Pad\'e approximants or Taylor series.
-In particular, these quadratic approximants provide an effect model for the avoided crossings 
-(Fig.~\ref{fig:QuadUMP}) and a far better estimate for the location of the branch point singularities.
-Furthermore, they provide remarkably accurate estimates of the ground-state energy at $\lambda = 1$, 
-as shown in Table~\ref{tab:QuadUMP}}
-
-However, as a note of caution, Ref.~\onlinecite{Goodson_2019} suggests that low-order 
-quadratic approximants can struggle to correctly model the singularity structure when 
-the energy function has poles in both the positive and negative half-planes. 
-In such a scenario, the quadratic approximant will tend to place its branch points in-between, potentially introducing singularities quite close to the origin.
-The remedy for this problem involves applying a suitable transformation of the complex plane (such as a bilinear conformal mapping) which leaves the points at $\lambda = 0$ and $\lambda = 1$ unchanged.
-\cite{Feenberg_1956}
+In particular, these quadratic approximants provide an effective model for the avoided crossings 
+(Fig.~\ref{fig:QuadUMP}) and an improved estimate for the distance of the 
+closest branch point  to the origin.
+Table~\ref{tab:QuadUMP} shows that they provide remarkably accurate 
+estimates of the ground-state energy at $\lambda = 1$.}
+
+\hugh{%
+While the diagonal quadratic approximants provide significanty improved estimates of the 
+ground-state energy, we can use our knowledge of the UMP singularity structure to develop
+even more accurate results.
+We have seen in previous sections that the UMP energy surface
+contains only square-root branch cuts that approach the real axis in the limit $U/t \rightarrow \infty$. 
+Since there are no true poles on this surface, we can obtain more accurate quadratic approximants by
+taking $d_q = 0$ and increasing $d_r$ to retain equivalent accuracy in the square-root term.
+Fig.~\ref{fig:nopole_quad} illustrates this improvement for the pole-free [3/0,4] quadratic
+approximant compared to the [3/2,2] approximant with the same truncation degree in the Taylor
+expansion.
+Clearly modelling the square-root branch point using $d_q = 2$ has the negative effect of
+introducing spurious poles in the energy, while focussing purely on the branch point with $d_q = 0$
+leads to a significantly improved model.
+Table~\ref{tab:QuadUMP} shows that these pole-free quadratic approximants
+provide a rapidly convergent series with essentially exact energies at low order.
+}
+
+\hugh{Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
+or pole-free approximants, we consider the energy and error obtained using only the first 10 terms in the UMP
+in Table~\ref{tab:UMP_order10}.
+The accuracy of these approximants reinforces how our understanding of the MP
+energy surface in the complex plane can be leveraged to significantly improve estimates of the exact
+energy using low-order perturbation expansions.
+}
+
+\begin{table}[h]
+	\caption{
+    \hugh{%
+    Estimate and associated error of the exact UMP energy at $U/t = 7$ for 
+    various approximants using up to ten terms in the Taylor expansion.
+    }
+	\label{tab:UMP_order10}}
+	\begin{ruledtabular}
+		\begin{tabular}{lccc}
+            \mc{2}{c}{Method}	 &	$E_{-}(\lambda)$ & Abs.\ Error \\ 
+			\hline
+            Taylor		         &	 10	         &	$-0.33338$      &  $0.197290$ \\
+            Pad\'e               &   [5/5]       &  $-0.35513$      &  $0.176000$ \\
+            Quadratic (diagonal) &   [3/3,3]     &  $-0.53104$      &  $0.000103$ \\
+            Quadratic (pole-free)&   [3/0,6]     &  $-0.53113$      &  $0.000003$ \\
+			\hline
+            Exact		         &	        	 &	$-0.53113$	     &            \\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 

### 2020-12-02 Manuscript/EPAWTFT.tex
Pade section

@@
 %As frequently claimed by Carl Bender, 
-\hugh{It is frequently stated that}
+It is frequently stated that
 \textit{``the most stupid thing that one can do with a series is to sum it.''}
 Nonetheless, quantum chemists are basically doing exactly this on a daily basis.
-\hugh{As we have seen throughout this review, the MP series can often show erratic, 
+As we have seen throughout this review, the MP series can often show erratic, 
 slow, or divergent behaviour.
 In these cases, estimating the correlation energy by simply summing successive
-low-order terms is almost guaranteed to fail.}
+low-order terms is almost guaranteed to fail.
 Here, we discuss alternative tools that can be used to sum slowly convergent or divergent series.
-\hugh{These so-called ``resummation'' techniques} form a vast field of research and thus we will
+These so-called ``resummation'' techniques form a vast field of research and thus we will
 provide details for only the most relevant methods.
@@
 
-\hugh{The failure of a Taylor series for correctly modelling the MP energy function $E(\lambda)$ 
+The failure of a Taylor series for correctly modelling the MP energy function $E(\lambda)$ 
 arises because one is trying to model a complicated function containing multiple branches, branch points and
-singularities} using a simple polynomial of finite order.
-A truncated Taylor series \hugh{can only predict a single sheet and} does not have enough 
-flexibility to adequately describe the MP energy.
+singularities using a simple polynomial of finite order.
+A truncated Taylor series can only predict a single sheet and does not have enough 
+flexibility to adequately describe, for example, the MP energy.
 Alternatively, the description of complex energy functions can be significantly improved
@@
 
-\hugh{A Pad\'e approximant can be considered as the best approximation of a function by a 
-rational function of given order.}
+A Pad\'e approximant can be considered as the best approximation of a function by a 
+rational function of given order.
 More specifically, a $[d_A/d_B]$ Pad\'e approximant is defined as 
@@
 (which are ubiquitous in the singularity structure of a typical perturbative treatment) 
-and more complicated functional forms appearing at critical points (
-where the nature of the solution undergoes a sudden transition).
-\hugh{Despite this limitation, the successive diagonal Pad\'e approximants (\ie, $d_A = d_B $) 
-often define a convergent perturbation series in cases where the Taylor series expansion diverges.}
+and more complicated functional forms appearing at critical points 
+(where the nature of the solution undergoes a sudden transition).
+Despite this limitation, the successive diagonal Pad\'e approximants (\ie, $d_A = d_B $) 
+often define a convergent perturbation series in cases where the Taylor series expansion diverges.
 
@@
     series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
-    We also report the \hugh{closest pole to the origin $\lc$} provided by the diagonal Pad\'e approximants.
+    We also report the distance of the closest pole to the origin $\abs{\lc}$ provided by the diagonal Pad\'e approximants.
 	\label{tab:PadeRMP}}
@@
 
-Fig.~\ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e 
+Figure~\ref{fig:PadeRMP} illustrates the improvement provided by diagonal Pad\'e 
 approximants compared to the usual Taylor expansion in cases where the RMP series of 
@@
 degree increases at $U/t = 3.5$, the Pad\'e approximants yield much more accurate results.
-\hugh{Furthermore, the distance of the closest pole to origin $\abs{\lc}$ in the Pad\'e approximants 
+Furthermore, the distance of the closest pole to the origin $\abs{\lc}$ in the Pad\'e approximants 
 indicate that they a relatively good approximation to the position of the 
@@
 For $U/t = 4.5$, the Taylor series expansion performs worse and eventually diverges,
-while the Pad\'e approximants still offer relaitively accurate energies and recovers
-a convergent series.}
+while the Pad\'e approximants still offer relatively accurate energies and recovers
+a convergent series.
 
@@
 
-\hugh{%
 We can expect the UMP energy function to be much more challenging 
@@
 (see Figs.~\ref{subfig:UMP_3} and \ref{subfig:UMP_7}).
-Fig.~\ref{fig:QuadUMP} and Table~\ref{tab:QuadUMP} indicate that this is indeed the case. 
+Figure~\ref{fig:QuadUMP} and Table~\ref{tab:QuadUMP} indicate that this is indeed the case. 
 In particular, Fig.~\ref{fig:QuadUMP} illustrates that the Pad\'e approximants are trying to model
@@
 The proximity of these poles to the physical point $\lambda = 1$ means that any error in the Pad\'e 
-functional form becomes magnified in the estimate of exact energy, as seen for the low-order
+functional form becomes magnified in the estimate of the exact energy, as seen for the low-order
 approximants in Table~\ref{tab:QuadUMP}.
@@
 (see Fig.~\ref{subfig:UMP_cvg}).
-}
 
@@
 		\begin{tabular}{lccccccc}
-            &			&			&					&	\mc{2}{c}{$\abs{\lc}$}	&	\mc{2}{c}{$E_{-}(\lambda)$}			\\
+            &			&			&					&	\mc{2}{c}{$\abs{\lc}$}	&	\mc{2}{c}{$E_{-}(\lambda = 1)$}			\\
 																		\cline{5-6}\cline{7-8}
@@
 		\begin{tabular}{lccc}
-            \mc{2}{c}{Method}	 &	$E_{-}(\lambda)$ & Abs.\ Error \\ 
+            \mc{2}{c}{Method}	 &	$E_{-}(\lambda = 1)$ & Abs.\ Error \\ 
 			\hline

### 2020-12-02 Manuscript/EPAWTFT.tex
Quadratic section

@@
 %==========================================%
-Quadratic approximants \hugh{are designed} to model the singularity structure of the energy 
+Quadratic approximants are designed to model the singularity structure of the energy 
 function $E(\lambda)$ via a generalised version of the square-root singularity 
@@
 	\label{eq:QuadApp}
-	E(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ]
+	E(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ],
 \end{equation}
@@
 	&
-	R(\lambda) & = \sum_{k=0}^{d_R} r_k \lambda^k 
+	R(\lambda) & = \sum_{k=0}^{d_R} r_k \lambda^k,
 \end{align}
@@
 \begin{equation}
-	Q(\lambda) E^2(\lambda) - P(\lambda) E(\lambda) + R(\lambda) \sim \order*{\lambda^{n+1}}
+	Q(\lambda) E^2(\lambda) - P(\lambda) E(\lambda) + R(\lambda) \sim \order*{\lambda^{n+1}},
 \end{equation}
@@
 A quadratic approximant, characterised by the label $[d_P/d_Q,d_R]$, generates, by construction, 
-$n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial $P^2(\lambda) - 4 Q(\lambda) R(\lambda)$ \hugh{and $d_q$ poles at the roots of $Q(\lambda)$}.
+$n_\text{bp} = \max(2d_p,d_q+d_r)$ branch points at the roots of the polynomial 
+$P^2(\lambda) - 4 Q(\lambda) R(\lambda)$ and $d_q$ poles at the roots of $Q(\lambda)$.
 
@@
 \ie, $[0/0,0]$, $[1/0,0]$, $[1/0,1]$, $[1/1,1]$, $[2/1,1]$, 
-is of particular interest \hugh{as the order of the corresponding Taylor series increases on each step.
+is of particular interest as the order of the corresponding Taylor series increases on each step.
 However, while a quadratic approximant can reproduce multiple branch points, it can only describe 
 a total of two branches.
-Since every branch point must therefore correspond to a degeneracy of the same two branches, this constraint
+\titou{Since every branch points must therefore correspond to a degeneracy of the same two branches,} this constraint
 can hamper the faithful description of more complicated singularity structures such as the MP energy surface.
-Despite this limitiation,} Ref.~\onlinecite{Goodson_2000a} demonstrates that quadratic approximants 
+Despite this limitation, Ref.~\onlinecite{Goodson_2000a} demonstrates that quadratic approximants 
 provide convergent results in the most divergent cases considered by Olsen and 
@@
 \begin{table}[b]
-    \caption{Estimate \hugh{for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$}
-    in the UMP energy function provided 
-    by various resummation techniques at $U/t = 3$ and $7$.
+    \caption{Estimate for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$
+    in the UMP energy function provided by various resummation techniques at $U/t = 3$ and $7$.
 	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch 
@@
 \caption{%
-\hugh{% 
 Comparison of the [3/2,2] and [3/0,4] quadratic approximants with the exact UMP energy surface in the complex $\lambda$ 
@@
 is free of poles.}
-\label{fig:nopole_quad}}
+\label{fig:nopole_quad}
 \end{figure*}
@@
 the ideal target for quadratic approximants.
-\hugh{%
 Furthermore, the greater flexibility of the diagonal quadratic approximants provides a significantly
@@
 Table~\ref{tab:QuadUMP} shows that they provide remarkably accurate 
-estimates of the ground-state energy at $\lambda = 1$.}
-
-\hugh{%
+estimates of the ground-state energy at $\lambda = 1$.
+
 While the diagonal quadratic approximants provide significanty improved estimates of the 
@@
 We have seen in previous sections that the UMP energy surface
-contains only square-root branch cuts that approach the real axis in the limit $U/t \rightarrow \infty$. 
+contains only \titou{square-root branch cuts} that approach the real axis in the limit $U/t \to \infty$. 
 Since there are no true poles on this surface, we can obtain more accurate quadratic approximants by
-taking $d_q = 0$ and increasing $d_r$ to retain equivalent accuracy in the square-root term.
-Fig.~\ref{fig:nopole_quad} illustrates this improvement for the pole-free [3/0,4] quadratic
+taking $d_q = 0$ and increasing $d_r$ to retain equivalent accuracy in the square-root term [see Eq.\eqref{eq:QuadApp}].
+Figure~\ref{fig:nopole_quad} illustrates this improvement for the pole-free [3/0,4] quadratic
 approximant compared to the [3/2,2] approximant with the same truncation degree in the Taylor
@@
 provide a rapidly convergent series with essentially exact energies at low order.
-}
-
-\hugh{Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
-or pole-free approximants, we consider the energy and error obtained using only the first 10 terms in the UMP
+
+Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
+or pole-free approximants, we consider the energy and error obtained using only the first 10 terms of the UMP series
 in Table~\ref{tab:UMP_order10}.
@@
 energy using low-order perturbation expansions.
-}
 
@@
 	\caption{
-    \hugh{%
     Estimate and associated error of the exact UMP energy at $U/t = 7$ for 
     various approximants using up to ten terms in the Taylor expansion.
-    }
 	\label{tab:UMP_order10}}
@@
 The Shanks transformation presents one approach for extracting this information
-and accelerating the rate of convergence of a sequence.\cite{Shanks_1955}
+and accelerating the rate of convergence of a sequence.\cite{Shanks_1955,BenderBook}
 

### 2020-12-02 Manuscript/EPAWTFT.tex
added shanks results... needs some references

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 																		\cline{3-4} \cline{5-6}
-			Method		&	degree	&	$U/t = 3.5$	&	$U/t = 4.5$	&	$U/t = 3.5$	&	$U/t = 4.5$	\\
+			Method		&	Degree	&	$U/t = 3.5$	&	$U/t = 4.5$	&	$U/t = 3.5$	&	$U/t = 4.5$	\\
 			\hline
@@
 \hugh{Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
-or pole-free approximants, we consider the energy and error obtained using only the first 10 terms in the UMP
-in Table~\ref{tab:UMP_order10}.
+or pole-free quadratic approximants, we consider the energy and error obtained using only the first 10 terms of the UMP
+Taylor series in Table~\ref{tab:UMP_order10}.
 The accuracy of these approximants reinforces how our understanding of the MP
@@
 		\begin{tabular}{lccc}
-            \mc{2}{c}{Method}	 &	$E_{-}(\lambda)$ & Abs.\ Error \\ 
+            \mc{2}{c}{Method}	 &	$E_{-}(\lambda = 1)$ & \% Abs.\ Error \\ 
 			\hline
-            Taylor		         &	 10	         &	$-0.33338$      &  $0.197290$ \\
-            Pad\'e               &   [5/5]       &  $-0.35513$      &  $0.176000$ \\
-            Quadratic (diagonal) &   [3/3,3]     &  $-0.53104$      &  $0.000103$ \\
-            Quadratic (pole-free)&   [3/0,6]     &  $-0.53113$      &  $0.000003$ \\
+            Taylor		         &	 10	         &	$-0.33338$      &  $37.150$ \\
+            Pad\'e               &   [5/5]       &  $-0.35513$      &  $33.140$ \\
+            Quadratic (diagonal) &   [3/3,3]     &  $-0.53103$      &  $\hphantom{0}0.019$ \\
+            Quadratic (pole-free)&   [3/0,6]     &  $-0.53113$      &  $\hphantom{0}0.005$ \\
 			\hline
@@
 
-Consider the partial sums $S_N$ defined from the truncated summation of an infinite series
-\begin{equation}
-    S_N = \sum_{k=0}^{N} a_k.
-\end{equation}
-If the series converges, then the partial sums will tend to the exact result in the limit $N\rightarrow \infty$.
-The Shanks transformation attempts to generate increasingly accurate estimates of the
-exact result by defining a new series as
+\hugh{Consider the partial sums
+$S_N = \sum_{k=0}^{N} a_k$
+defined from the truncated summation of an infinite series 
+$    S = \sum_{k=0}^{\infty} a_k$.
+If the series converges, then the partial sums will tend to the exact result 
+\begin{equation}
+\lim_{N\rightarrow \infty} S_N = S. 
+\end{equation}
+The Shanks transformation attempts to generate increasingly accurate estimates of this
+limt by defining a new series as
 \begin{equation}
@@
 accuracy using only the first few terms in the series.
+However, it is designed to accelerate exponentially converging partial sums with 
+the approximate form
+\begin{equation}
+    S_N \approx S + a\,b^N.
+\end{equation}
+Furthermore, while this transformation can accelerate the convergence of a series, 
+there is no guarantee that this acceleration will be fast enough to significantly
+improve the accuracy of low-order approximations.}
+
+\hugh{To the best of our knowledge, the Shanks transformation has never previously been applied
+to the acceleration of the MP series.
+We have therefore applied it to the convergent Taylor series, Pad\'e approximants, and quadratic
+approximants for RMP and UMP in the symmetric Hubbard dimer. 
+The UMP approximants converge too slowly for the Shanks transformation
+to provide any improvement, even in the case where the quadratic approximants are already 
+very accurate.
+In contrast, acceleration of the diagonal Pad\'e approximants for the RMP cases 
+can significantly improve the estimate of the energy using low-order perturbation terms, 
+as shown in Table~\ref{tab:RMP_shank}.
+Even though the RMP series diverges at $U/t = 4.5$, the combination
+of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error of 
+the best energy estimate to 0.002\,\%.}
+
+\begin{table}[th]
+	\caption{
+    \hugh{%
+    Acceleration of the diagonal Pad\'e approximant sequence for the RMP energy
+    using the Shanks transformation.
+    }
+	\label{tab:RMP_shank}}
+	\begin{ruledtabular}
+		\begin{tabular}{lcccc}
+            &			&	&	\mc{2}{c}{$E_{-}(\lambda = 1)$} \\
+												\cline{4-5} 
+            Method  &   Degree	&  Series Term &   $U/t = 3.5$ & $U/t = 4.5$ \\
+			\hline
+            Pad\'e	&	[1/1]	& $S_1$        &  $-1.61111$   &  $-2.64286$ \\
+                    &   [2/2]   & $S_2$        &  $-0.82124$   &  $-0.48446$ \\
+                    &   [3/3]   & $S_3$        &  $-0.91995$   &  $-0.81929$ \\
+                    &   [4/4]   & $S_4$        &  $-0.90579$   &  $-0.74866$ \\
+                    &   [5/5]   & $S_5$        &  $-0.90778$   &  $-0.76277$ \\
+            \hline
+            Shanks  &	        &  $T(S_2)$    &  $-0.90898$   &  $-0.77432$ \\
+                    &           &  $T(S_3)$    &  $-0.90757$   &  $-0.76096$ \\
+                    &           &  $T(S_4)$    &  $-0.90753$   &  $-0.76042$ \\
+			\hline
+            Exact	&	        & 	           &  $-0.90754$	&  $-0.76040$ \\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 

### 2020-12-02 Manuscript/EPAWTFT.tex

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
-or pole-free approximants, we consider the energy and error obtained using only the first 10 terms of the UMP series
-in Table~\ref{tab:UMP_order10}.
+or pole-free quadratic approximants, we consider the energy and error obtained using only the first 10 terms of the UMP
+Taylor series in Table~\ref{tab:UMP_order10}.
 The accuracy of these approximants reinforces how our understanding of the MP
@@
 		\begin{tabular}{lccc}
-            \mc{2}{c}{Method}	 &	$E_{-}(\lambda = 1)$ & Abs.\ Error \\ 
+            \mc{2}{c}{Method}	 &	$E_{-}(\lambda = 1)$ & \% Abs.\ Error \\ 
 			\hline
-            Taylor		         &	 10	         &	$-0.33338$      &  $0.197290$ \\
-            Pad\'e               &   [5/5]       &  $-0.35513$      &  $0.176000$ \\
-            Quadratic (diagonal) &   [3/3,3]     &  $-0.53104$      &  $0.000103$ \\
-            Quadratic (pole-free)&   [3/0,6]     &  $-0.53113$      &  $0.000003$ \\
+            Taylor		         &	 10	         &	$-0.33338$      &  $37.150$ \\
+            Pad\'e               &   [5/5]       &  $-0.35513$      &  $33.140$ \\
+            Quadratic (diagonal) &   [3/3,3]     &  $-0.53103$      &  $\hphantom{0}0.019$ \\
+            Quadratic (pole-free)&   [3/0,6]     &  $-0.53113$      &  $\hphantom{0}0.005$ \\
 			\hline

### 2020-12-02 Manuscript/EPAWTFT.tex
saving work in Shanks

@@
 We have seen in previous sections that the UMP energy surface
-contains only \titou{square-root branch cuts} that approach the real axis in the limit $U/t \to \infty$. 
+contains only square-root branch cuts that approach the real axis in the limit $U/t \to \infty$. 
 Since there are no true poles on this surface, we can obtain more accurate quadratic approximants by
@@
 
-\hugh{Consider the partial sums
+\titou{T2: $N$ is defined as the number of electrons. Maybe we should use $n$ instead?}
+Consider the partial sums
 $S_N = \sum_{k=0}^{N} a_k$
@@
 The Shanks transformation attempts to generate increasingly accurate estimates of this
-limt by defining a new series as
+limit by defining a new series as
 \begin{equation}
@@
 there is no guarantee that this acceleration will be fast enough to significantly
-improve the accuracy of low-order approximations.}
+improve the accuracy of low-order approximations.
 

### 2020-12-02 Manuscript/EPAWTFT.tex
saving work in Shanks

@@
 
-\titou{T2: $N$ is defined as the number of electrons. Maybe we should use $n$ instead?}
 Consider the partial sums
-$S_N = \sum_{k=0}^{N} a_k$
+$S_n = \sum_{k=0}^{n} s_k$
 defined from the truncated summation of an infinite series 
-$    S = \sum_{k=0}^{\infty} a_k$.
+$S = \sum_{k=0}^{\infty} s_k$.
 If the series converges, then the partial sums will tend to the exact result 
 \begin{equation}
-\lim_{N\rightarrow \infty} S_N = S. 
+	\lim_{n \to \infty} S_n = S. 
 \end{equation}
@@
 \begin{equation}
-    T(S_N) = \frac{S_{N+1} S_{N-1} - S_{N}^2}{S_{N+1} + S_{N-1} - 2 S_{N}}.
+    T(S_n) = \frac{S_{n+1} S_{n-1} - S_{n}^2}{S_{n+1} + S_{n-1} - 2 S_{n}}.
 \end{equation}
@@
 accuracy using only the first few terms in the series.
-However, it is designed to accelerate exponentially converging partial sums with 
+However, it is designed to accelerate \titou{exponentially?} converging partial sums with 
 the approximate form
 \begin{equation}
-    S_N \approx S + a\,b^N.
+    S_n \approx S + \alpha\,\beta^n.
 \end{equation}
@@
 
-\hugh{To the best of our knowledge, the Shanks transformation has never previously been applied
+To the best of our knowledge, the Shanks transformation has never previously been applied
 to the acceleration of the MP series.
@@
 of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error of 
-the best energy estimate to 0.002\,\%.}
+the best energy estimate to 0.002\,\%.
 
@@
 	\caption{
-    \hugh{%
     Acceleration of the diagonal Pad\'e approximant sequence for the RMP energy
     using the Shanks transformation.
-    }
 	\label{tab:RMP_shank}}

### 2020-12-02 Manuscript/EPAWTFT.tex
Shanks done
another little commit

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error of 
-the best energy estimate to 0.002\,\%.}
+the best energy estimate to 0.002\,\% using only the lowest 10 terms in the corresponding 
+Taylor series.}
+This remarkable result indicates just how much information is contained in the first few
+terms of a perturbation series, even if it diverges.
 

### 2020-12-02 Manuscript/EPAWTFT.tex

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error of 
-the best energy estimate to 0.002\,\%.
+the best energy estimate to 0.002\,\% using only the lowest 10 terms in the Taylor series.
+This remarkable result indicates just how much information is contained in the first few
+terms of a perturbation series, even if it diverges.
 

### 2020-12-02 Manuscript/EPAWTFT.tex
ccl

--- 2020-12-02 Manuscript/EPAWTFT.tex
@@
 \subsection{Shanks Transformation}
+\label{sec:Shanks}
 %==========================================%
@@
 In that regard, it is worth highlighting the key contribution of Cremer and He who proposed a classification of the types of convergence: \cite{Cremer_1996} ``class A'' systems that exhibit monotonic convergence, and ``class B'' systems for which convergence is erratic after initial oscillations.
-Further insights were brought thanks to a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employ a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
+Further insights were brought thanks to a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employed a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
 Building on the careful mathematical analysis of Stillinger who showed that the mathematical origin behind the divergent series with odd-even sign alternation is due to a dominant singularity on the negative real $\lambda$ axis, \cite{Stillinger_2000} Sergeev and Goodson proposed a more refined singularity classification: $\alpha$ singularities which have ``large'' imaginary parts, and $\beta$ singularities which have very small imaginary parts.
@@
 However, it is worth mentioning that the construction of these approximants requires high-order MP coefficients which are quite expensive to compute in practice.
-
-Most of the concepts reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
+The Shanks transformation presented in Sec.~\ref{sec:Shanks} can, in some cases, alleviate this issue.
+
+Most of the physical concepts and mathematical tools reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
 Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand perturbation theory as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} and many others.
-We believe that the Hubbard dimer could then be used for further developments around perturbation theory.
+We believe that the Hubbard dimer could then be used for further developments and comprehension around perturbation theory.
 
 As a concluding remark and from a broader point of view, the present work shows that our understanding of the singularity structure of the energy is still incomplete.
-Yet, we hope that the present contribution will open new perspectives for the understanding of the physics of exceptional points in electronic structure theory.
+Yet, we hope that the present contribution will open new perspectives on the physics of exceptional points in electronic structure theory.
 

### 2020-12-02 Manuscript/EPAWTFT.tex
fix bib
add bib

@@
 
-\raggedbottom
-\tableofcontents
+%\raggedbottom
+%\tableofcontents
 
@@
 Most of the physical concepts and mathematical tools reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
-Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand perturbation theory as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} and many others.
+Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand perturbation theory as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018} and many others.
 We believe that the Hubbard dimer could then be used for further developments and comprehension around perturbation theory.

### 2020-12-03 Manuscript/EPAWTFT.tex
edits for analytic continuation

@@
 accuracy using only the first few terms in the series.
-However, it is designed to accelerate \titou{exponentially?} converging partial sums with 
+However, it is only designed to accelerate converging partial sums with 
 the approximate form
@@
 To the best of our knowledge, the Shanks transformation has never previously been applied
-to the acceleration of the MP series.
+to accelerate the convergence of the MP series.
 We have therefore applied it to the convergent Taylor series, Pad\'e approximants, and quadratic
@@
 Even though the RMP series diverges at $U/t = 4.5$, the combination
-of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error of 
-the best energy estimate to 0.002\,\% using only the lowest 10 terms in the Taylor series.
+of diagonal Pad\'e approximants with the Shanks transformation reduces the absolute error in
+the best energy estimate to 0.002\,\% using only the first 10 terms in the Taylor series.
 This remarkable result indicates just how much information is contained in the first few
@@
 
-Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning \cite{Mihalka_2017a} (see also Ref.~\onlinecite{Surjan_2000}).
-Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
-In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent MP series \cite{Goodson_2011} taking again as an example the water molecule in a stretched geometry.
-In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent (\ie, for $\abs{\lambda} < r_c$), and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit.
-However, the choice of the functional form of the fit remains a subtle task.
-This technique was first generalised by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula \cite{Mihalka_2019}
+Recently, Mih\'alka \etal\ have studied the effect of different partitionings, such as MP or EN theory, on the position of 
+branch points and the convergence properties of Rayleigh--Schr\"odinger perturbation theory\cite{Mihalka_2017b} (see also
+Ref.~\onlinecite{Surjan_2000}).
+Taking the equilibrium and stretched water structures as an example, they estimated the radius of convergence using quadratic
+Pad\'e approximants.
+The EN partitioning provided worse convergence properties than the MP partitioning, which is believed to be
+because the EN denominators are generally smaller than the MP denominators.
+To remedy the situation, they showed that introducing a suitably chosen level shift parameter can turn a 
+divergent series into a convergent one by increasing the magnitude of these denominators.\cite{Mihalka_2017b}
+However, like the UMP series in stretched \ce{H2},\cite{Lepetit_1988} 
+the cost of larger denominators is an overall slower rate of convergence.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{rmp_anal_cont}
+    \caption{%
+        Comparison of the scaled RMP10 Taylor expansion with the exact RMP energy as a function
+        of $\lambda$ for the symmetric Hubbard dimer at $U/t = 4$. 
+        The two functions correspond closely within the radius of convergence.
+    }
+    \label{fig:rmp_anal_cont}
+\end{figure}
+
+In a later study by the same group, they used analytic continuation techniques 
+to resum a divergent MP series such as a stretched water molecule.\cite{Mihalka_2017a}
+Any MP series truncated at a given order $n$ can be used to define the scaled function
+\begin{equation}
+   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} E^{(k)}.
+\end{equation}
+Reliable estimates of the energy can be obtained for values of $\lambda$ where the MP series is rapidly
+convergent (\ie, for $\abs{\lambda} < \rc$), as shown in Fig.~\ref{fig:rmp_anal_cont} for the RMP10 series 
+of the symmetric Hubbard dimer with $U/t = 4.5$.
+These values can then be analytically continued using a polynomial- or Pad\'e-based fit to obtain an 
+estimate of the exact energy at $\lambda = 1$.
+However, choosing the functional form for the best fit remains a difficult and subtle challenge.
+
+This technique was first generalised by using complex scaling parameters and constructing an analytic
+continuation by solving the Laplace equations.\cite{Surjan_2018}
+It was then further improved by introducing Cauchy's integral formula\cite{Mihalka_2019}
 \begin{equation}
 	\label{eq:Cauchy}
-	\frac{1}{2\pi i} \oint_{\gamma} \frac{E(\lambda)}{\lambda - a} = E(a),
-\end{equation}
-which states that the value of the energy can be computed at $\lambda=a$ inside the complex contour $\gamma$ only by the knowledge of its values on the same contour.
-Their method consists in refining self-consistently the values of $E(\lambda)$ computed on a contour going through the physical point at $\lambda = 1$ and encloses points of the ``trusted'' region (where the MP series is convergent).
-The shape of this contour is arbitrary but no singularities are allowed inside the contour to ensure $E(\lambda)$ is analytic.
-When the values of $E(\lambda)$ on the so-called contour are converged, Cauchy's integrals formula \eqref{eq:Cauchy} is invoked to compute the values at $E(\lambda=1)$ which corresponds to the final estimate of the FCI energy.
-The authors illustrate this protocol on the dissociation curve of \ce{LiH} and the stretched water molecule showing encouraging results. \cite{Mihalka_2019}
+    \frac{1}{2\pi \i} \oint_{\mathcal{C}} \frac{E(\lambda)}{\lambda - \lambda_1} = E(\lambda_1),
+\end{equation}
+which states that the value of the energy can be computed at $\lambda_1$ inside the complex 
+contour $\mathcal{C}$ using only the values along the same contour.
+Starting from a set of points in a ``trusted'' region where the MP series is convergent, their approach 
+self-consistently refines estimates of the $E(\lambda)$ values on a contour around the physical point 
+$\lambda = 1$.
+The shape of this contour is arbitrary, but there must be no branch points or other singularities inside
+the contour.
+Once the contour values of $E(\lambda)$ are converged, Cauchy's integral formula Eq.~\eqref{eq:Cauchy} can 
+be invoked to compute the value at $E(\lambda=1)$ and obtain a final estimate of the exact energy.
+The authors illustrate this protocol for the dissociation curve of \ce{LiH} and the stretched water 
+molecule to obtain encouragingly accurate results.\cite{Mihalka_2019}
 

### 2020-12-03 Manuscript/EPAWTFT.tex
Unified all figures

@@
 The exact many-electron wave function at a given nuclear geometry $\Psi(\vb{R})$ corresponds 
+of using adjacent partial sums 
 to the solution of the (time-independent) Schr\"{o}dinger equation
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{HF_real.pdf}
+    \includegraphics[width=\linewidth]{fig2}
     \caption{\label{fig:HF_real}
@@
 	\begin{subfigure}{0.49\textwidth}
-    \includegraphics[height=0.65\textwidth,trim={0pt 0pt 0pt -35pt},clip]{HF_cplx_angle}
+    \includegraphics[height=0.65\textwidth,trim={0pt 0pt 0pt -35pt},clip]{fig3a}
 	\subcaption{\label{subfig:UHF_cplx_angle}}
@@
 	\begin{subfigure}{0.49\textwidth}
-	\includegraphics[height=0.65\textwidth]{HF_cplx_energy}
+	\includegraphics[height=0.65\textwidth]{fig3b}
 	\subcaption{\label{subfig:UHF_cplx_energy}}
@@
 	\caption{%
-    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$ \titou{in the Hubbard dimer for $U/t = ??$}.
+    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$ in the Hubbard dimer for $U/t = 2$.
     Symmetry-broken solutions correspond to individual sheets and become equivalent at 
@@
 	\begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig2a}	
+	\includegraphics[height=0.75\textwidth]{fig4a}	
 		\subcaption{\label{subfig:RMP_3.5} $U/t = 3.5$}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig2b}
+	\includegraphics[height=0.75\textwidth]{fig4b}
 		\subcaption{\label{subfig:RMP_cvg}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig2c}	
+	\includegraphics[height=0.75\textwidth]{fig4c}	
 		\subcaption{\label{subfig:RMP_4.5} $U/t = 4.5$}
@@
 \begin{figure}[htb]
-	\includegraphics[width=\linewidth]{RadConv}
+	\includegraphics[width=\linewidth]{fig5}
 	\caption{
@@
 	\begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig3a}	
+	\includegraphics[height=0.75\textwidth]{fig6a}	
 		\subcaption{\label{subfig:UMP_3} $U/t = 3$}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig3b}
+	\includegraphics[height=0.75\textwidth]{fig6b}
 		\subcaption{\label{subfig:UMP_cvg}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{fig3c}	
+	\includegraphics[height=0.75\textwidth]{fig6c}	
 		\subcaption{\label{subfig:UMP_7} $U/t = 7$}
@@
 	\begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{rmp_cp}	
+	\includegraphics[height=0.75\textwidth]{fig7a}	
 		\subcaption{\label{subfig:rmp_cp}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{rmp_cp_surf}
+	\includegraphics[height=0.75\textwidth]{fig7b}
 		\subcaption{\label{subfig:rmp_cp_surf}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{rmp_ep_to_cp}	
+    \includegraphics[height=0.75\textwidth]{fig7c}
 		\subcaption{\label{subfig:rmp_ep_to_cp}}
@@
 	\begin{subfigure}{0.32\textwidth}
-        \includegraphics[height=0.75\textwidth,trim={0pt 5pt -10pt 15pt},clip]{ump_cp}	
+    \includegraphics[height=0.75\textwidth,trim={0pt 5pt -10pt 15pt},clip]{fig8a}
 		\subcaption{\label{subfig:ump_cp}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{ump_cp_surf}
+	\includegraphics[height=0.75\textwidth]{fig8b}
 		\subcaption{\label{subfig:ump_cp_surf}}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.75\textwidth]{ump_ep_to_cp}	
+	\includegraphics[height=0.75\textwidth]{fig8c}	
 		\subcaption{\label{subfig:ump_ep_to_cp}}
@@
 \begin{figure*}
-    \includegraphics[height=0.23\textheight]{PadeRMP35}
-    \includegraphics[height=0.23\textheight]{PadeRMP45}
+    \includegraphics[height=0.23\textheight]{fig9a}
+    \includegraphics[height=0.23\textheight]{fig9b}
     \caption{\label{fig:PadeRMP}
@@
 \begin{figure}[t]
-    \includegraphics[width=\linewidth]{QuadUMP}
+    \includegraphics[width=\linewidth]{fig10}
     \caption{\label{fig:QuadUMP}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.85\textwidth]{ump_qa322}	
-    \subcaption{\label{subfig:ump_ep_to_cp} [3/2,2] Quadratic}
+	\includegraphics[height=0.85\textwidth]{fig11a}	
+    \subcaption{\label{subfig:322quad} [3/2,2] Quadratic}
     \end{subfigure}
@@
     \begin{subfigure}{0.32\textwidth}
-	\includegraphics[height=0.85\textwidth]{ump_exact}
-		\subcaption{\label{subfig:ump_cp_surf} Exact}
+	\includegraphics[height=0.85\textwidth]{fig11b}
+		\subcaption{\label{subfig:exact} Exact}
     \end{subfigure}
@@
 	\begin{subfigure}{0.32\textwidth}
-        \includegraphics[height=0.85\textwidth]{ump_qa304}	
-    \subcaption{\label{subfig:ump_cp} [3/0,4] Quadratic}
+        \includegraphics[height=0.85\textwidth]{fig11c}	
+    \subcaption{\label{subfig:304quad} [3/0,4] Quadratic}
     \end{subfigure}
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{rmp_anal_cont}
+    \includegraphics[width=\linewidth]{fig12}
     \caption{%

### 2020-12-03 Manuscript/EPAWTFT.tex
accepted Titou changes

@@
     \caption{\label{fig:HF_real}
-    RHF and UHF energies \titou{in the Hubbard dimer} as a function of the correlation strength $U/t$. 
+    RHF and UHF energies in the Hubbard dimer as a function of the correlation strength $U/t$. 
     The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson-Fischer point.}
@@
 Firstly, the exact wave function becomes increasingly multi-configurational as the bond is stretched, and the 
-\titou{R}HF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
+RHF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
 Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
-increasingly small at larger bond lengths, \titou{leading to a divergence, for example, in the second-order MP correction \eqref{eq:EMP2}.}
+increasingly small at larger bond lengths, leading to a divergence, for example, in the second-order MP correction \eqref{eq:EMP2}.
 In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains
@@
 by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
-In this work, the authors compared \titou{the UMP series with the exact RHF- and UHF-based FCI expansions (T2: I don't understand this)}
-and identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
+In this work, the authors %compared titou{the UMP series with the exact RHF- and UHF-based FCI expansions (T2: I don't understand this)} and
+identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
 low-lying double excitation.
@@
 the analytic Hubbard dimer with a complex-valued perturbation strength.
-In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the \trash{electron correlation} \titou{ratio} $U/t$.
+In this system, the stretching of the \ce{H\bond{-}H} bond is directly mirrored by an increase in the ratio $U/t$.
 Using the ground-state RHF reference orbitals leads to the parametrised RMP Hamiltonian
@@
 % EFFECT OF SYMMETRY BREAKING
-As the UHF orbitals break the \trash{molecular} \titou{spin} symmetry, new coupling terms emerge between the electronic states that
+As the UHF orbitals break the spin symmetry, new coupling terms emerge between the electronic states that
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
@@
 \caption{%
-    The UMP ground-state EP \titou{in the symmetric Hubbard dimer} becomes a critical point in the strong correlation limit (\ie, large $U/t$).
+    The UMP ground-state EP in the symmetric Hubbard dimer becomes a critical point in the strong correlation limit (\ie, large $U/t$).
     (\subref{subfig:ump_cp}) As $U/t$ increases, the avoided crossing on the real $\lambda$ axis

### 2020-12-03 Manuscript/EPAWTFT.tex
comment on Surjan section

@@
 \begin{equation}
-   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} E^{(k)}.
+   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} \titou{E_\text{MP}^{(k)}}.
 \end{equation}
@@
 Starting from a set of points in a ``trusted'' region where the MP series is convergent, their approach 
-self-consistently refines estimates of the $E(\lambda)$ values on a contour around the physical point 
+self-consistently refines estimates of the $E(\lambda)$ values on a contour \titou{around} the physical point 
 $\lambda = 1$.
+\titou{T2: actually this is not true as the point $\lambda = 1$ is chosen to be on the contour.}
 The shape of this contour is arbitrary, but there must be no branch points or other singularities inside

### 2020-12-03 Manuscript/EPAWTFT.tex
Hugh full review

--- 2020-12-03 Manuscript/EPAWTFT.tex
@@
 The exact many-electron wave function at a given nuclear geometry $\Psi(\vb{R})$ corresponds 
-of using adjacent partial sums 
 to the solution of the (time-independent) Schr\"{o}dinger equation
@@
 In practice, approximations to the exact Schr\"{o}dinger equation must be introduced, including
-perturbation theories and Hartree--Fock approximation considered in this review.
+perturbation theories and the Hartree--Fock approximation considered in this review.
 In what follows, we will drop the parametric dependence on the nuclear geometry and, 
@@
 As a result, completely encircling an EP leads to the interconversion of the two interacting states, while a second complete rotation returns the two states to their original energies.
-Additionally, the wave functions pick up a geometric phase in the process, and four complete loops are required to recover their starting forms.\cite{MoiseyevBook}
+Additionally, the wave functions  can pick up a geometric phase in the process, and four complete loops are required to recover their starting forms.\cite{MoiseyevBook}
 
@@
 Equation \eqref{eq:PolChar} is the well-known secular equation providing the (eigen)energies of the system. 
-If the energy is also solution of Eq.~\eqref{eq:DPolChar}, then this energy value is at least two-fold degenerate. 
+If the energy is also a solution of Eq.~\eqref{eq:DPolChar}, then this energy value is at least two-fold degenerate. 
 These degeneracies can be conical intersections between two states with different symmetries 
@@
 of the reference and perturbation Hamiltonians in Eq.~\eqref{eq:SchrEq-PT}.\cite{Mihalka_2017b}
-
+%
 % LAMBDA IN THE COMPLEX PLANE
@@
 As a result, the radius of convergence for a function is equal to the distance from the origin of the closest singularity
-in the complex plane.
+in the complex plane, \hugh{referred to as the ``dominant'' singularity.
+This singularity may represent a pole of the function, or a branch point (\eg, square-root or logarithmic)
+in a multi-valued function.
+Critical points are singularities that lie on the real axis, where the nature of a function experiences
+a discontinuity in either its value or one of its derivatives.}
+
 For example, the simple function
@@
 However, this series diverges for $x \ge 1$.
-This divergence occurs because $f(x)$ has four singularities in the complex 
+This divergence occurs because $f(x)$ has four \hugh{poles} in the complex 
 ($\e^{\i\pi/4}$, $\e^{-\i\pi/4}$, $\e^{\i3\pi/4}$, and $\e^{-\i3\pi/4}$) with a modulus equal to $1$, demonstrating
@@
 While most practical calculations generally consider only the MP2 or MP3 approximations, higher order terms can 
-easily be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}
+be computed to understand the convergence of the MP$n$ series.\cite{Handy_1985}
 \textit{A priori}, there is no guarantee that this series will provide the smooth convergence that is desirable for a
@@
 UHF wave function, creating the first direct link between spin-contamination and slow UMP convergence.\cite{Gill_1988}
-
+%
 % LEPETIT CHAT
@@
 cannot be applied for all systems.
-For example, \ce{HF} contains both back-door intruder states and low-lying doubly-excited states that
+For example, the \ce{HF} molecule contains both back-door intruder states and low-lying doubly-excited states that
 result in alternating terms up to 10th order. 
@@
 Note that new forms of perturbation expansions only occur when the sign of $\delta_1$ and $\delta_2$ differ.
-Using these non-Hermitian two-state model, the convergence of a perturbation series can be characterised 
+Using this non-Hermitian two-state model, the convergence of a perturbation series can be characterised 
 according to a so-called ``archetype'' that defines the overall ``shape'' of the energy convergence.\cite{Olsen_2019} 
@@
 while two additional archetypes (zigzag-geometric and convex-geometric) are observed in non-Hermitian Hamiltonians.
-
+%
 The geometric archetype appears to be the most common for MP expansions,\cite{Olsen_2019} but the 
@@
 the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}
-They demonstrated that the dominant singularity in class A systems corresponds to a dominant EP with a positive real component, 
+They demonstrated that the dominant singularity in class A systems corresponds to a EP with a positive real component, 
 where the magnitude of the imaginary component controls the oscillations in the signs of successive MP 
@@
 The existence of the MP critical point can also explain why the divergence observed by Olsen \etal\ in the \ce{Ne} atom 
-and \ce{HF} molecule occurred when diffuse basis functions were included.\cite{Olsen_1996}
+and the \ce{HF} molecule occurred when diffuse basis functions were included.\cite{Olsen_1996}
 Clearly diffuse basis functions are required for the electrons to dissociate from the nuclei, and indeed using
@@
 To mathematically model this scenario in this asymmetric Hubbard dimer, we introduce a one-electron potential $-\epsilon$ on the left site to 
-represent the attraction between the electrons and the model ``atomic'' nucleus [see Eq.~\eqref{eq:H_FCI}], where we define $\epsilon > 0$.
+represent the attraction between the electrons and the model ``atomic'' nucleus, where we define $\epsilon > 0$.
 The reference Slater determinant for a doubly-occupied atom can be represented using RHF
@@
 the presence of an earlier excited-state avoided crossing means that the first-excited state qualitatively 
-represents the reference double excitation for $\lambda > 1/2$ (see Fig.~\ref{subfig:ump_cp}).
+represents the reference double excitation for $\lambda > 1/2$.
 
@@
 For small $U/t$, the HF potentials will be weak and the electrons will delocalise over the two sites,
-both in the UHF reference and as $\lambda$ increases.
+both in the UHF reference and \hugh{the exact solution}.
 This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing
@@
 \textit{``the most stupid thing that one can do with a series is to sum it.''}
-Nonetheless, quantum chemists are basically doing exactly this on a daily basis.
+Nonetheless, quantum chemists are basically doing this on a daily basis.
 As we have seen throughout this review, the MP series can often show erratic, 
@@
 A truncated Taylor series can only predict a single sheet and does not have enough 
-flexibility to adequately describe, for example, the MP energy.
+flexibility to adequately describe functions such as the MP energy.
 Alternatively, the description of complex energy functions can be significantly improved
@@
 chemistry\cite{Loos_2013,Pavlyukh_2017,Tarantino_2019,Gluzman_2020} as they can model poles, 
-which appears at the locations of the roots of $B(\lambda)$. 
+which appear at the roots of $B(\lambda)$. 
 However, they are unable to model functions with square-root branch points 
@@
 Furthermore, the distance of the closest pole to the origin $\abs{\lc}$ in the Pad\'e approximants 
-indicate that they a relatively good approximation to the position of the 
+indicate that they provide a relatively good approximation to the position of the 
 true branch point singularity in the RMP energy.
@@
 a total of two branches.
-\titou{Since every branch points must therefore correspond to a degeneracy of the same two branches,} this constraint
+%\titou{Since every branch points must therefore correspond to a degeneracy of the same two branches,} 
+This constraint
 can hamper the faithful description of more complicated singularity structures such as the MP energy surface.
@@
 expansion.
-Clearly modelling the square-root branch point using $d_q = 2$ has the negative effect of
+Clearly, modelling the square-root branch point using $d_q = 2$ has the negative effect of
 introducing spurious poles in the energy, while focussing purely on the branch point with $d_q = 0$
@@
 \begin{equation}
-   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} E^{(k)}.
+   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} E_\text{MP}^{(k)}.
 \end{equation}
@@
 
-This technique was first generalised by using complex scaling parameters and constructing an analytic
+This technique was first generalised using complex scaling parameters to construct an analytic
 continuation by solving the Laplace equations.\cite{Surjan_2018}
@@
 	\label{eq:Cauchy}
-    \frac{1}{2\pi \i} \oint_{\mathcal{C}} \frac{E(\lambda)}{\lambda - \lambda_1} = E(\lambda_1),
+    E(\lambda) = \frac{1}{2\pi \i} \oint_{\mathcal{C}} \frac{E(\lambda')}{\lambda' - \lambda},
 \end{equation}
@@
 Starting from a set of points in a ``trusted'' region where the MP series is convergent, their approach 
-self-consistently refines estimates of the $E(\lambda)$ values on a contour around the physical point 
+self-consistently refines estimates of the $E(\lambda')$ values on a contour that includes the physical point 
 $\lambda = 1$.
@@
 the contour.
-Once the contour values of $E(\lambda)$ are converged, Cauchy's integral formula Eq.~\eqref{eq:Cauchy} can 
+Once the contour values of $E(\lambda')$ are converged, Cauchy's integral formula Eq.~\eqref{eq:Cauchy} can 
 be invoked to compute the value at $E(\lambda=1)$ and obtain a final estimate of the exact energy.

### 2020-12-03 Manuscript/EPAWTFT.tex
Hugh had a go at the introduction

@@
 
-\title{Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them}
+\title{M\o{}ller--Plesset Theory in the Complex Plane: Exceptional Points and Where to Find Them}
 
@@
 
-Due to the ubiquitous influence of processes involving electronic states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
-Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community. 
-An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws.
+% MP THEORY
+\hugh{%
+M\o{}ller--Plesset (MP) perturbation theory remains one of the most popular methods for computing the electron
+correlation energy.\cite{Moller_1934}
+In this approach, the exact electronic energy is estimated by constructing a perturbative correction on top
+of a mean-field Hartree--Fock (HF) approximation.\cite{SzaboBook}
+The popularity of MP theory stems from its black-box nature and relatively low computational scaling, 
+making it easily applied in a broad range of molecular research.
+However, it is now widely understood that the series of MP approximantions (defined for a given perturbation
+order $n$ as MP$n$) can show erratic, slow, or divergent behaviour that limit its systematic improvability.%
+\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988} 
+As a result, practical applications typically employ only the lowest-order MP2 approach, while 
+the successive MP3, MP4, and MP5 (and higher) terms are generally not considered to offer enough improvement
+to justify their increased cost.
+Turning the MP approximations into a convergent and systematically improvable series largely remains an open challenge.
+}
+
+% COMPLEX PLANE
+\hugh{%
+Our conventional view of electronic structure theory is centered around the Hermitian notion of quantised energy levels,
+where the different electronic states of a molecular are discrete and energetically ordered.
+The lowest energy state defines the ground electronic state, while higher energy states
+represent electronic excited states.
+However, an entirely different perspective on quantisation can be found by analytically continuining
+quantum mechanics into the complex domain.
+In this inherently non-Hermitian framework, the energy levels emerge as individual \textit{sheets} of a complex
+multi-valued function and can be connected as one continuous \textit{Riemann surface}.\cite{BenderPTBook}
+This connection is possible because orderability of real numbers is lost when energies are extended to the
+complex domain.
+As a result, our quantised view of conventional quantum mechanics only arises from
+restricting our domain to Hermitian approximations.
+}
+
+% NON-HERMITIAN HAMILTONIANS
+\hugh{%
+Non-Hermitian Hamiltonians already have a long history in quantum chemistry and have been extensively used to 
+describe metastable resonance phenomina.\cite{MoiseyevBook}
+Through the methods of complex-scaling\cite{Moiseyev_1998} and complex absorbing 
+potentials,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonances can be stabilised as square-integrable
+wave functions with a complex energy that allows the resonance energy and lifetime to be computed.
+We refer the interested reader to the excellent book by Moiseyev for a general overview. \cite{MoiseyevBook}
+}
+
+% EXCEPTIONAL POINTS
+\hugh{%
+The Riemann surface for the electronic energy $E(\lambda)$ with a coupling parameter $\lambda$ can be 
+constructed by analytically continuing the function into the complex $\lambda$ domain.
+In the process, the ground and excited states become smoothly connected and form a continuous complex-valued
+energy surface. 
+\textit{Exceptional points} (EPs) can exist on this energy surface, corresponding to branch point 
+singularities where two (or more) states become exactly degenerate.%
+\cite{MoiseyevBook,Heiss_1988,Heiss_1990,Heiss_1999,Berry_2011,Heiss_2012,Heiss_2016,Benda_2018}
+While EPs can be considered as the non-Hermitian analogues of conical intersections,\cite{Yarkony_1996} 
+the behaviour of their eigenvalues near a degeneracy couldn't be more different.
+Incredibly, following the eigenvalues around an EP leads to the interconversion of the degenerate states, 
+and multiple loops around the EP are required to recover the initial energy.\cite{MoiseyevBook,Heiss_2016,Benda_2018}
+In contrast, encircling a conical intersection leaves the states unchanged.
+Furthermore, while the eigenvectors remain orthogonal at a conical intersection, the eigenvectors at an EP
+become identical and result in a \textit{self-orthogonal} state. \cite{MoiseyevBook}
+An EP effectively creates a ``portal'' between ground and excited-states in the complex plane.%
+\cite{Burton_2019,Burton_2019a}
+This transition between states has been experimentally observed in electronics, 
+microwaves, mechanics, acoustics, atomic systems and optics.\cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
+}
+
+% MP THEORY IN THE COMPLEX PLANE
+\hugh{%
+The MP energy correction can be considered as a function of the perturbation parameter $\lambda$.
+When the domain of $\lambda$ is extended to the complex plane, EPs can also occur in the MP energy.
+Although these EPs generally exist in the complex plane, their positions are intimately related to the 
+convergence of the perturbation expansion on the real axis.%
+\cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019,Mihalka_2017a,Mihalka_2017b,Mihalka_2019}
+Furthermore, the existence of an avoided crossing on the real axis is indicative of a nearby EP
+in the complex plane.
+Our aim in this article is to provide a comprehensive review of the fundamental relationship between EPs
+and the convergence properties of the MP series.
+In doing so, we will demonstrate how understanding the MP energy in the complex plane can 
+be harnessed to significantly improve estimates of the exact energy using only the lowest-order terms
+in the MP series.
+}
+
+%Due to the ubiquitous influence of processes involving electronic states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
+%Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community. 
+%An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws.
 \cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
-The fact that none of these methods is successful in every chemical scenario has encouraged chemists and physicists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
-In particular, the design of an affordable, black-box method performing well in both the weak and strong correlation regimes is still elusive.
-
-One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
-Within this quantised paradigm, electronic states look completely disconnected from one another.
-For example, many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.\cite{Piecuch_2002,Dreuw_2005,Krylov_2006,Sneskov_2012,Gonzales_2012,Laurent_2013,Adamo_2013,Ghosh_2018,Blase_2020,Loos_2020a}
-However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
-In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
-In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
+%The fact that none of these methods is successful in every chemical scenario has encouraged chemists and physicists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
+%In particular, the design of an affordable, black-box method performing well in both the weak and strong correlation regimes is still elusive.
+
+%One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
+%Within this quantised paradigm, electronic states look completely disconnected from one another.
+%For example, many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.\cite{Piecuch_2002,Dreuw_2005,Krylov_2006,Sneskov_2012,Gonzales_2012,Laurent_2013,Adamo_2013,Ghosh_2018,Blase_2020,Loos_2020a}
+%However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
+%In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
+%In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
 \cite{MoiseyevBook,BenderPTBook}
-The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
-One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019,Burton_2019a}
-
-By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
-This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
-Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
-Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realised in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
+%The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
+%One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019,Burton_2019a}
+
+%By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
+%This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
+%Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
+%Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realised in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
 \cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
 
-Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate.
+%Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate.
 \cite{MoiseyevBook,Heiss_1988,Heiss_1990,Heiss_1999,Berry_2011,Heiss_2012,Heiss_2016,Benda_2018}
-They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
-In the case of auto-ionising resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
-Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
-For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
+%They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
+%In the case of auto-ionising resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
+%Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
+%For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
 \cite{MoiseyevBook,Heiss_2016,Benda_2018}
-Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
-In contrast, encircling Hermitian degeneracies at conical intersections only introduces a geometric phase while leaving the states unchanged.
-More dramatically, whilst eigenvectors remain orthogonal at conical intersections, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state.
+%Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
+%In contrast, encircling Hermitian degeneracies at conical intersections only introduces a geometric phase while leaving the states unchanged.
+%More dramatically, whilst eigenvectors remain orthogonal at conical intersections, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state.
 \cite{MoiseyevBook}
-More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
+%More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
 \cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019,Mihalka_2017a,Mihalka_2017b,Mihalka_2019}
 
-\titou{The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
+%The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
 \cite{MoiseyevBook}
-Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
-We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}}
-
-\titou{Discussion around the different types of singularities in complex analysis.
+%Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
+%We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}
+
+\hugh{\bf (HGAB: Moved (and condensed) this to end of Section IIC)}.
+\trashHB{Discussion around the different types of singularities in complex analysis.
 At a singular point, a function and/or its derivatives becomes infinite or undefined (hence non analytic).
@@
 }
-\antoine{However, their complicated functional forms makes it difficult to know if they belong to a given class of singularities.
-Thus it is not clear if critical points can be sorted in one mathematical class of singularities or not.
-To the best of our knowledge, this question is still open.}
-
-\titou{T2: I THINK THAT IN GENERAL THE AXE LABELS ARE TOO SMALL.}
 
@@
     The contour followed around the EP in order to interchange states is also represented.
+    \hugh{HUGH TO ADD CONTOUR AGAIN....}
 	\label{fig:FCI}}
@@
 in a multi-valued function.
-Critical points are singularities that lie on the real axis, where the nature of a function experiences
-a discontinuity in either its value or one of its derivatives.}
+}
 
@@
 Coulomb interaction becomes attractive.
-There is therefore a negative critical value $\lc$ where it becomes energetically favourable for the electrons 
+There is therefore a negative critical point $\lc$ where it becomes energetically favourable for the electrons 
 to dissociate and form a bound cluster at an infinite separation from the nuclei.\cite{Stillinger_2000}
@@
 processes.\cite{Sergeev_2005}
+\hugh{While these critical points are singularities on the real axis, their exact mathematical form is difficult 
+to identify and remains an open question.}
 
@@
 After a short presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we have provided an exhaustive historical overview of the various research activities that have been performed on the physics of singularities with a particular focus on M{\o}ller--Plesset perturbation theory.
-Seminal contributions from various research groups around the world have evidenced highly oscillatory, slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988}
+Seminal contributions from various research groups around the world have evidenced highly oscillatory, slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%
+\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988}
 

### 2020-12-03 Manuscript/EPAWTFT.tex
binding Hugh intro

@@
 
-\title{M\o{}ller--Plesset Theory in the Complex Plane: Exceptional Points and Where to Find Them}
+\title{Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them}
 
@@
 
-% MP THEORY
-\hugh{%
+% Good old Schroedinger
+The electronic Schr\"odinger equation,
+\begin{equation}
+	\hH \Psi = E \Psi,
+\end{equation}
+is the starting point for a fundamental understanding of the behaviour of electrons and, thence, of chemical structure, bonding and reactivity. 
+However, as famously stated by Dirac: \cite{Dirac_1929}
+\begin{quote}
+	\textit{``The underlying physical laws necessary for the mathematical theory of a large part of physics and the whole of chemistry are thus completely known, and the difficulty is only that the exact application of these laws leads to equations much too complicated to be soluble.
+	It therefore becomes desirable that approximate practical methods of applying quantum mechanics should be developed, which can lead to an explanation of the main features of complex atomic systems without too much computation.''}
+\end{quote}
+Indeed, as anticipated by Dirac, accurately predicting the energetics of electronic states from first principles has been one of the grand challenges faced by theoretical chemists and physicists since the dawn of quantum mechanics.
+
+% RSPT
+Together with the variational principle, perturbation theory is one of the very few essential tool for describing realistic quantum systems for which it is impossible to find the exact solution of the Schr\"odinger equation.
+In particular, time-independent Rayleigh--Schr\"odinger perturbation theory \cite{RayleighBook,Schrodinger_1926} has cemented itself as an instrument of choice in the armada of theoretical and computational methods that have been developed for this purpose.
+\cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
+
+% Moller-Plesset
 M\o{}ller--Plesset (MP) perturbation theory remains one of the most popular methods for computing the electron
@@
 making it easily applied in a broad range of molecular research.
-However, it is now widely understood that the series of MP approximantions (defined for a given perturbation
+However, it is now widely understood that the series of MP approximations (defined for a given perturbation
 order $n$ as MP$n$) can show erratic, slow, or divergent behaviour that limit its systematic improvability.%
@@
 Turning the MP approximations into a convergent and systematically improvable series largely remains an open challenge.
-}
 
 % COMPLEX PLANE
-\hugh{%
-Our conventional view of electronic structure theory is centered around the Hermitian notion of quantised energy levels,
+Our conventional view of electronic structure theory is centred around the Hermitian notion of quantised energy levels,
 where the different electronic states of a molecular are discrete and energetically ordered.
@@
 represent electronic excited states.
-However, an entirely different perspective on quantisation can be found by analytically continuining
+However, an entirely different perspective on quantisation can be found by analytically continuing
 quantum mechanics into the complex domain.
@@
 restricting our domain to Hermitian approximations.
-}
 
 % NON-HERMITIAN HAMILTONIANS
-\hugh{%
 Non-Hermitian Hamiltonians already have a long history in quantum chemistry and have been extensively used to 
-describe metastable resonance phenomina.\cite{MoiseyevBook}
+describe metastable resonance phenomena.\cite{MoiseyevBook}
 Through the methods of complex-scaling\cite{Moiseyev_1998} and complex absorbing 
@@
 We refer the interested reader to the excellent book by Moiseyev for a general overview. \cite{MoiseyevBook}
-}
 
 % EXCEPTIONAL POINTS
-\hugh{%
 The Riemann surface for the electronic energy $E(\lambda)$ with a coupling parameter $\lambda$ can be 
@@
 While EPs can be considered as the non-Hermitian analogues of conical intersections,\cite{Yarkony_1996} 
-the behaviour of their eigenvalues near a degeneracy couldn't be more different.
+the behaviour of their eigenvalues near a degeneracy could not be more different.
 Incredibly, following the eigenvalues around an EP leads to the interconversion of the degenerate states, 
@@
 microwaves, mechanics, acoustics, atomic systems and optics.\cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
-}
 
 % MP THEORY IN THE COMPLEX PLANE
-\hugh{%
 The MP energy correction can be considered as a function of the perturbation parameter $\lambda$.
@@
 in the MP series.
-}
-
-%Due to the ubiquitous influence of processes involving electronic states in physics, chemistry, and biology, their faithful description from first principles has been one of the grand challenges faced by theoretical chemists since the dawn of computational chemistry.
-%Accurately predicting ground- and excited-state energies (hence excitation energies) is particularly valuable in this context, and it has concentrated most of the efforts within the community. 
-%An armada of theoretical and computational methods have been developed to this end, each of them being plagued by its own flaws.
-\cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
-%The fact that none of these methods is successful in every chemical scenario has encouraged chemists and physicists to carry on the development of new methodologies, their main goal being to get the most accurate energies (and properties) at the lowest possible computational cost in the most general context.
-%In particular, the design of an affordable, black-box method performing well in both the weak and strong correlation regimes is still elusive.
-
-%One common feature of all these methods is that they rely on the notion of quantised energy levels of Hermitian quantum mechanics, in which the different electronic states of a molecule or an atom are energetically ordered, the lowest being the ground state while the higher ones are excited states.
-%Within this quantised paradigm, electronic states look completely disconnected from one another.
-%For example, many current methods study excited states using only ground-state information, creating a ground-state bias that leads to incorrect excitation energies.\cite{Piecuch_2002,Dreuw_2005,Krylov_2006,Sneskov_2012,Gonzales_2012,Laurent_2013,Adamo_2013,Ghosh_2018,Blase_2020,Loos_2020a}
-%However, one can gain a different perspective on quantisation extending quantum chemistry into the complex domain.
-%In a non-Hermitian complex picture, the energy levels are \textit{sheets} of a more complicated topological manifold called \textit{Riemann surface}, and they are smooth and continuous \textit{analytic continuation} of one another.
-%In other words, our view of the quantised nature of conventional Hermitian quantum mechanics arises only from our limited perception of the more complex and profound structure of its non-Hermitian variant.
-\cite{MoiseyevBook,BenderPTBook}
-%The realisation that ground and excited states both emerge from one single mathematical structure with equal importance suggests that excited-state energies can be computed from first principles in their own right.
-%One could then exploit the structure of these Riemann surfaces to develop methods that directly target excited-state energies without needing ground-state information. \cite{Burton_2019,Burton_2019a}
-
-%By analytically continuing the electronic energy $E(\lambda)$ in the complex domain (where $\lambda$ is a coupling parameter), the ground and excited states of a molecule can be smoothly connected.
-%This connection is possible because by extending real numbers to the complex domain, the ordering property of real numbers is lost.
-%Hence, electronic states can be interchanged away from the real axis since the concept of ground and excited states has been lost.
-%Amazingly, this smooth and continuous transition from one state to another has recently been experimentally realised in physical settings such as electronics, microwaves, mechanics, acoustics, atomic systems and optics.
-\cite{Bittner_2012,Chong_2011,Chtchelkatchev_2012,Doppler_2016,Guo_2009,Hang_2013,Liertzer_2012,Longhi_2010,Peng_2014, Peng_2014a,Regensburger_2012,Ruter_2010,Schindler_2011,Szameit_2011,Zhao_2010,Zheng_2013,Choi_2018,El-Ganainy_2018}
-
-%Exceptional points (EPs) are branch point singularities where two (or more) states become exactly degenerate.
-\cite{MoiseyevBook,Heiss_1988,Heiss_1990,Heiss_1999,Berry_2011,Heiss_2012,Heiss_2016,Benda_2018}
-%They are the non-Hermitian analogs of conical intersections, \cite{Yarkony_1996} which are ubiquitous in non-adiabatic processes and play a key role in photochemical mechanisms.
-%In the case of auto-ionising resonances, EPs have a role in deactivation processes similar to conical intersections in the decay of bound excited states. \cite{Benda_2018}
-%Although Hermitian and non-Hermitian Hamiltonians are closely related, the behaviour of their eigenvalues near degeneracies is starkly different.
-%For example, encircling non-Hermitian degeneracies at EPs leads to an interconversion of states, and two loops around the EP are necessary to recover the initial energy.
-\cite{MoiseyevBook,Heiss_2016,Benda_2018}
-%Additionally, the wave function picks up a geometric phase (also known as Berry phase \cite{Berry_1984}) and four loops are required to recover the initial wave function.
-%In contrast, encircling Hermitian degeneracies at conical intersections only introduces a geometric phase while leaving the states unchanged.
-%More dramatically, whilst eigenvectors remain orthogonal at conical intersections, at non-Hermitian EPs the eigenvectors themselves become equivalent, resulting in a \textit{self-orthogonal} state.
-\cite{MoiseyevBook}
-%More importantly here, although EPs usually lie off the real axis, these singular points are intimately related to the convergence properties of perturbative methods and avoided crossing on the real axis are indicative of singularities in the complex plane.
-\cite{BenderBook,Olsen_1996,Olsen_2000,Olsen_2019,Mihalka_2017a,Mihalka_2017b,Mihalka_2019}
-
-%The use of non-Hermitian Hamiltonians in quantum chemistry has a long history; these Hamiltonians have been used extensively as a method for describing metastable resonance phenomena.
-\cite{MoiseyevBook}
-%Through a complex-scaling of the electronic or atomic coordinates,\cite{Moiseyev_1998} or by introducing a complex absorbing potential,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonance states are transformed into square-integrable wave functions that allow the energy and lifetime of the resonance to be computed.
-%We refer the interested reader to the excellent book of Moiseyev for a general overview. \cite{MoiseyevBook}
-
-\hugh{\bf (HGAB: Moved (and condensed) this to end of Section IIC)}.
-\trashHB{Discussion around the different types of singularities in complex analysis.
-At a singular point, a function and/or its derivatives becomes infinite or undefined (hence non analytic).
-One very common type of singularities (belonging to the family of isolated singularities) are poles where the function behaves $1/(\lambda - \lambda_c)^n$ where $n \in \mathbb{N}^*$ is the order of the pole.
-Another class of singularities are branch points resulting from a multi-valued function such as a square root or a logarithm function and usually implying the presence of so-called branch cuts which are lines or curves where the function ``jumps'' from one value to another.
-Critical points are singularities which lie on the real axis and where the nature of the function undergoes a sudden transition. 
-However, these do not clearly belong to a given class of singularities and they cannot be rigorously classified as they have more complicated functional forms.
-}
+
+The present review is organised as follows.
+In Sec.~\ref{sec:EPs}, we introduce key concepts, such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their extension to the complex plane.
+Section \ref{sec:MP} deals with MP perturbation theory and we report an exhaustive historical overview of the various research activities that have been performed on the physics of singularities.
+We discuss several resummation techniques (such as Pad\'e and quadratic approximants) in Sec.~\ref{sec:Resummation}.
+Finally, we draw our conclusions in Sec.~\ref{sec:ccl}.
+For most of the concepts presented in this review, we report concrete illustrative and pedagogical examples based on the ubiquitous Hubbard dimer, showing the amazing versatility of this simple yet powerful model system.
 
@@
 As a result, the radius of convergence for a function is equal to the distance from the origin of the closest singularity
-in the complex plane, \hugh{referred to as the ``dominant'' singularity.
+in the complex plane, referred to as the ``dominant'' singularity.
 This singularity may represent a pole of the function, or a branch point (\eg, square-root or logarithmic)
 in a multi-valued function.
-}
 
@@
 However, this series diverges for $x \ge 1$.
-This divergence occurs because $f(x)$ has four \hugh{poles} in the complex 
+This divergence occurs because $f(x)$ has four poles in the complex 
 ($\e^{\i\pi/4}$, $\e^{-\i\pi/4}$, $\e^{\i3\pi/4}$, and $\e^{-\i3\pi/4}$) with a modulus equal to $1$, demonstrating
@@
 processes.\cite{Sergeev_2005}
-\hugh{While these critical points are singularities on the real axis, their exact mathematical form is difficult 
-to identify and remains an open question.}
+While these critical points are singularities on the real axis, their exact mathematical form is difficult 
+to identify and remains an open question.
 
@@
 For small $U/t$, the HF potentials will be weak and the electrons will delocalise over the two sites,
-both in the UHF reference and \hugh{the exact solution}.
+both in the UHF reference and the exact wave function.
 This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing
@@
 \section{Conclusion}
+\label{sec:ccl}
 %%%%%%%%%%%%%%%%%%%%

### 2020-12-04 Manuscript/EPAWTFT.tex
abstract

@@
 \begin{abstract}
-In this review, we explore the extension of quantum chemistry in the complex plane and its link with perturbation theory.
+We explore the extension of quantum chemistry in the complex plane and its link with perturbation theory.
 We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptional points.
-After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, and their illustration with the ubiquitous (symmetric) Hubbard dimer at half filling, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
 In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory and its apparent link with quantum phase transitions.
-Each of these points is further illustrated with the Hubbard dimer.
-Finally, we discuss several resummation techniques (such as Pad\'e and quadratic approximants) alongside concrete examples.
+We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) able to improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
+Each of these points is further illustrated with the ubiquitous Hubbard dimer at half filling which proves to be a versatile model system in order to understand the subtle concepts of the analytic continuation of perturbation theory in the complex plane.
 \end{abstract}

### 2020-12-04 Manuscript/EPAWTFT.tex
intro

@@
 % Moller-Plesset
-M\o{}ller--Plesset (MP) perturbation theory remains one of the most popular methods for computing the electron
-correlation energy.\cite{Moller_1934}
+The workhorse of time-independent perturbation theory is most certainly M\o{}ller--Plesset (MP) perturbation 
+theory which remains one of the most popular methods for computing the electron correlation energy.\cite{Moller_1934}
 In this approach, the exact electronic energy is estimated by constructing a perturbative correction on top

### 2020-12-04 Manuscript/EPAWTFT.tex
intro

--- 2020-12-04 Manuscript/EPAWTFT.tex
@@
 % Moller-Plesset
-M\o{}ller--Plesset (MP) perturbation theory remains one of the most popular methods for computing the electron
-correlation energy.\cite{Moller_1934}
+The workhorse of time-independent perturbation theory is most certainly M\o{}ller--Plesset (MP) perturbation 
+theory \cite{Moller_1934} which remains one of the most popular methods for computing the electron correlation energy, 
+an old yet important concept, first introduced by Wigner \cite{Wigner_1934} and later defined by L\"owdin. \cite{Lowdin_1958} 
 In this approach, the exact electronic energy is estimated by constructing a perturbative correction on top

### 2020-12-04 Manuscript/EPAWTFT.tex
intro

@@
 We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) able to improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
-Each of these points is further illustrated with the ubiquitous Hubbard dimer at half filling which proves to be a versatile model system in order to understand the subtle concepts of the analytic continuation of perturbation theory in the complex plane.
+Each of these points is further illustrated with the ubiquitous Hubbard dimer at half filling which proves to be a versatile model system in order to understand the subtle concepts of the analytic continuation of perturbation theory into the complex plane.
 \end{abstract}
@@
 The present review is organised as follows.
-In Sec.~\ref{sec:EPs}, we introduce key concepts, such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their extension to the complex plane.
+In Sec.~\ref{sec:EPs}, we introduce key concepts, such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their analytic continuation into the complex plane.
 Section \ref{sec:MP} deals with MP perturbation theory and we report an exhaustive historical overview of the various research activities that have been performed on the physics of singularities.
@@
 Finally, we draw our conclusions in Sec.~\ref{sec:ccl}.
-For most of the concepts presented in this review, we report concrete illustrative and pedagogical examples based on the ubiquitous Hubbard dimer, showing the amazing versatility of this simple yet powerful model system.
+For most of the concepts presented in this review, we report illustrative and pedagogical examples based on the ubiquitous Hubbard dimer, showing the amazing versatility of this simple yet powerful model system.
 

### 2020-12-04 Manuscript/EPAWTFT.tex
intro

@@
 In that regard, it is worth highlighting the key contribution of Cremer and He who proposed a classification of the types of convergence: \cite{Cremer_1996} ``class A'' systems that exhibit monotonic convergence, and ``class B'' systems for which convergence is erratic after initial oscillations.
-Further insights were brought thanks to a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employed a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
-Building on the careful mathematical analysis of Stillinger who showed that the mathematical origin behind the divergent series with odd-even sign alternation is due to a dominant singularity on the negative real $\lambda$ axis, \cite{Stillinger_2000} Sergeev and Goodson proposed a more refined singularity classification: $\alpha$ singularities which have ``large'' imaginary parts, and $\beta$ singularities which have very small imaginary parts.
+Further insights were provided by a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employed a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
+Building on the careful mathematical analysis of Stillinger who showed that the mathematical origin behind the divergent series with odd-even sign alternation is due to a dominant singularity on the negative real axis, \cite{Stillinger_2000} Sergeev and Goodson proposed a singularity classification: $\alpha$ singularities which have ``large'' imaginary parts, and $\beta$ singularities which have very small imaginary parts.
 \cite{Goodson_2000a,Goodson_2000b,Goodson_2004,Sergeev_2005,Sergeev_2006}
@@
 Finally, we have discussed several resummation techniques, such as Pad\'e and quadratic approximants, that can be used to improve energy estimates for both convergent and divergent series.
+As mentioned earlier in this manuscript, turning low-order truncated MP series into convergent and systematically improvable series would be a highly desirable feature that could drastically improve the general applicability of such methods.
 However, it is worth mentioning that the construction of these approximants requires high-order MP coefficients which are quite expensive to compute in practice.
@@
 Most of the physical concepts and mathematical tools reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
-Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand perturbation theory as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018} and many others.
+Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand the subtle notions linked to the extension of perturbation theory into the complex plane, as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018}, correlated methods, \cite{} and many others.
 We believe that the Hubbard dimer could then be used for further developments and comprehension around perturbation theory.

### 2020-12-04 Manuscript/EPAWTFT.tex
conclusion

@@
 Most of the physical concepts and mathematical tools reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
-Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand the subtle notions linked to the extension of perturbation theory into the complex plane, as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017}, DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018}, correlated methods, \cite{} and many others.
+Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand the subtle notions linked to the extension of perturbation theory into the complex plane, as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015,Cohen_2016} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017,Olevano_2019} DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018} coupled cluster theory, \cite{Stein_2014,Henderson_2015,Shepherd_2016} and many others.
 We believe that the Hubbard dimer could then be used for further developments and comprehension around perturbation theory.

### 2020-12-04 Manuscript/EPAWTFT.tex
Hugh added some spice to the opening paragraph

@@
 
+% SPIKE THE READER
+\hugh{Perturbation theory isn't usually considered in the complex plane.
+Normally it is applied using real numbers as one of very few availabe tools for 
+describing realistic quantum systems where exact solutions of the Schr\"odinger equation are impossible.\cite{Dirac_1929}
+In particular, time-independent Rayleigh--Schr\"odinger perturbation theory\cite{RayleighBook,Schrodinger_1926} 
+has emerged as an instrument of choice among the vast array of methods developed for this purpose.%
+\cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
+However, the properties of perturbation theory in the complex plane
+are essential for understanding the quality of perturbative approximations on the real axis.
+}
+
 % Good old Schroedinger
-The electronic Schr\"odinger equation,
-\begin{equation}
-	\hH \Psi = E \Psi,
-\end{equation}
-is the starting point for a fundamental understanding of the behaviour of electrons and, thence, of chemical structure, bonding and reactivity. 
-However, as famously stated by Dirac: \cite{Dirac_1929}
-\begin{quote}
-	\textit{``The underlying physical laws necessary for the mathematical theory of a large part of physics and the whole of chemistry are thus completely known, and the difficulty is only that the exact application of these laws leads to equations much too complicated to be soluble.
-	It therefore becomes desirable that approximate practical methods of applying quantum mechanics should be developed, which can lead to an explanation of the main features of complex atomic systems without too much computation.''}
-\end{quote}
-Indeed, as anticipated by Dirac, accurately predicting the energetics of electronic states from first principles has been one of the grand challenges faced by theoretical chemists and physicists since the dawn of quantum mechanics.
+%The electronic Schr\"odinger equation,
+%\begin{equation}
+%	\hH \Psi = E \Psi,
+%\end{equation}
+%is the starting point for a fundamental understanding of the behaviour of electrons and, thence, of chemical structure, bonding and reactivity. 
+%However, as famously stated by Dirac: \cite{Dirac_1929}
+%\begin{quote}
+%	\textit{``The underlying physical laws necessary for the mathematical theory of a large part of physics and the whole of chemistry are thus completely known, and the difficulty is only that the exact application of these laws leads to equations much too complicated to be soluble.
+%	It therefore becomes desirable that approximate practical methods of applying quantum mechanics should be developed, which can lead to an explanation of the main features of complex atomic systems without too much computation.''}
+%\end{quote}
+%Indeed, as anticipated by Dirac, accurately predicting the energetics of electronic states from first principles has been one of the grand challenges faced by theoretical chemists and physicists since the dawn of quantum mechanics.
 
 % RSPT
-Together with the variational principle, perturbation theory is one of the very few essential tool for describing realistic quantum systems for which it is impossible to find the exact solution of the Schr\"odinger equation.
-In particular, time-independent Rayleigh--Schr\"odinger perturbation theory \cite{RayleighBook,Schrodinger_1926} has cemented itself as an instrument of choice in the armada of theoretical and computational methods that have been developed for this purpose.
+%Together with the variational principle, perturbation theory is one of the very few essential tool for describing realistic quantum systems for which it is impossible to find the exact solution of the Schr\"odinger equation.
+%In particular, time-independent Rayleigh--Schr\"odinger perturbation theory \cite{RayleighBook,Schrodinger_1926} has cemented itself as an instrument of choice in the armada of theoretical and computational methods that have been developed for this purpose.
 \cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
@@
 % Moller-Plesset
-The workhorse of time-independent perturbation theory is most certainly M\o{}ller--Plesset (MP) perturbation 
-theory \cite{Moller_1934} which remains one of the most popular methods for computing the electron correlation energy, 
-an old yet important concept, first introduced by Wigner \cite{Wigner_1934} and later defined by L\"owdin. \cite{Lowdin_1958} 
-In this approach, the exact electronic energy is estimated by constructing a perturbative correction on top
+%\hugh{Accurately predicting the electronic energy is the primary focus of electronic structure theory, in 
+%principle providing a fundamental understanding of chemical structure, bonding, and reactivity.
+\hugh{In electronic structure theory,} the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) %perturbation 
+theory,\cite{Moller_1934} which remains one of the most popular methods for computing the electron 
+correlation energy.\cite{Wigner_1934,Lowdin_1958}
+%\trashHB{an old yet important concept, first introduced by Wigner \cite{Wigner_1934} and later defined by L\"owdin. \cite{Lowdin_1958}}
+This approach estimates the exact electronic energy by constructing a perturbative correction on top
 of a mean-field Hartree--Fock (HF) approximation.\cite{SzaboBook}
-The popularity of MP theory stems from its black-box nature and relatively low computational scaling, 
-making it easily applied in a broad range of molecular research.
-However, it is now widely understood that the series of MP approximations (defined for a given perturbation
+The popularity of MP theory stems from its black-box nature, \hugh{size-extensivity,} and relatively low computational scaling, 
+making it easily applied in a broad range of molecular research.\cite{HelgakerBook}
+However, it is now widely recognised that the series of MP approximations (defined for a given perturbation
 order $n$ as MP$n$) can show erratic, slow, or divergent behaviour that limit its systematic improvability.%
@@
 As a result, practical applications typically employ only the lowest-order MP2 approach, while 
-the successive MP3, MP4, and MP5 (and higher) terms are generally not considered to offer enough improvement
+the successive MP3, MP4, and MP5 (and higher \hugh{order}) terms are generally not considered to offer enough improvement
 to justify their increased cost.
-Turning the MP approximations into a convergent and systematically improvable series largely remains an open challenge.
+Turning the MP approximations into a convergent and 
+systematically improvable series largely remains an open challenge.
 
@@
 multi-valued function and can be connected as one continuous \textit{Riemann surface}.\cite{BenderPTBook}
-This connection is possible because orderability of real numbers is lost when energies are extended to the
+This connection is possible because the orderability of real numbers is lost when energies are extended to the
 complex domain.
@@
 
-The present review is organised as follows.
-In Sec.~\ref{sec:EPs}, we introduce key concepts, such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their analytic continuation into the complex plane.
-Section \ref{sec:MP} deals with MP perturbation theory and we report an exhaustive historical overview of the various research activities that have been performed on the physics of singularities.
-We discuss several resummation techniques (such as Pad\'e and quadratic approximants) in Sec.~\ref{sec:Resummation}.
-Finally, we draw our conclusions in Sec.~\ref{sec:ccl}.
-For most of the concepts presented in this review, we report illustrative and pedagogical examples based on the ubiquitous Hubbard dimer, showing the amazing versatility of this simple yet powerful model system.
+\trashHB{The present review is organised as follows.}
+In Sec.~\ref{sec:EPs}, we introduce the key concepts such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their \hugh{non-Hermitian} analytic continuation into the complex plane.
+Section \ref{sec:MP} presents MP perturbation theory and we report a comprehensive historical overview of the research that
+has been performed on the physics of MP singularities.
+In Sec.~\ref{sec:Resummation}, we discuss several resummation techniques for improving the accuracy
+of low-order MP approximations, including Pad\'e and quadratic approximants.
+Finally, we draw our conclusions in Sec.~\ref{sec:ccl} \hugh{and highlight our perspective on directions for 
+future research}.
+Throughout this review, we present illustrative and pedagogical examples based on the ubiquitous 
+Hubbard dimer, \hugh{reinforcing} the amazing versatility of this powerful simplistic model.
 
@@
         Comparison of the scaled RMP10 Taylor expansion with the exact RMP energy as a function
-        of $\lambda$ for the symmetric Hubbard dimer at $U/t = 4$. 
+        of $\lambda$ for the symmetric Hubbard dimer at $U/t = 4.5$. 
         The two functions correspond closely within the radius of convergence.

### 2020-12-04 Manuscript/EPAWTFT.tex
Hugh added words to conclusions, time for references

@@
 
-In order to model accurately chemical systems, one must choose, in an ever growing zoo of methods, which computational protocol is adapted to the system of interest.
-This choice can be, moreover, motivated by the type of properties that one is interested in.
-That means that one must understand the strengths and weaknesses of each method, \ie, why one method might fail in some cases and work beautifully in others. 
-We have seen that for methods relying on perturbation theory, their successes and failures are directly connected to the position of singularities in the complex plane, known as exceptional points.
-
-After a short presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we have provided an exhaustive historical overview of the various research activities that have been performed on the physics of singularities with a particular focus on M{\o}ller--Plesset perturbation theory.
-Seminal contributions from various research groups around the world have evidenced highly oscillatory, slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%
+% INTRO TO CONC.
+\hugh{To accurately model chemical systems, one must choose a computational protocol from an ever growing 
+collection of theoretical methods.
+Until the Sch\"odinger equation is solved exactly, this choice must make a compromise on the accuracy
+of certain properties depending on the system that is being studied.
+}
+It is therefore essential that we understand the strengths and weaknesses of different methods, 
+and why one might fail in cases where others work beautifully.
+In this review, we have seen that the success and failure of perturbation-based methods are 
+directly connected to the position of exceptional point singularities in the complex plane.
+
+% HISTORICAL OVERVIEW
+We began by presenting the fundamental concepts behind non-Hermitian extensions of quantum chemistry into the complex plane, 
+including the Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory.
+We then provided a comprehensive review of the various research that has been performed 
+around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller--Plesset theory. 
+Seminal contributions from various research groups around the world have revealed highly oscillatory,
+slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%
 \cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988} 
-
-Later, these erratic behaviours were investigated and rationalised in terms of avoided crossings and singularities in the complex plane. 
-In that regard, it is worth highlighting the key contribution of Cremer and He who proposed a classification of the types of convergence: \cite{Cremer_1996} ``class A'' systems that exhibit monotonic convergence, and ``class B'' systems for which convergence is erratic after initial oscillations.
-Further insights were provided by a series of papers by Olsen and coworkers \cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} where they employed a two-state model to dissect the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
-Building on the careful mathematical analysis of Stillinger who showed that the mathematical origin behind the divergent series with odd-even sign alternation is due to a dominant singularity on the negative real axis, \cite{Stillinger_2000} Sergeev and Goodson proposed a singularity classification: $\alpha$ singularities which have ``large'' imaginary parts, and $\beta$ singularities which have very small imaginary parts.
+\hugh{In particular, the spin-symmetry-broken unrestricted MP series is notorious
+for giving incredibly slow convergence.\cite{Gill_1986,Nobes_1987,Gill_1988a,Gill_1988}
+All these behaviours can be rationalised and explained by the position of exceptional points
+and other singularities that arise when perturbation theory is extended across the complex plane.}
+
+% CLASSIFICATIONS
+\hugh{%
+The classifications of different convergence types developed by Cremer and He,\cite{Cremer_1996} 
+Olsen \etal,\cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} 
+or Sergeev and Goodson\cite{Goodson_2000a,Goodson_2000b,Goodson_2004,Sergeev_2005,Sergeev_2006} are particularly
+worth highlighting.
+In Cremer and He's original classification, ``class A'' systems exhibit monotonic convergence and generally
+correspond to weakly correlated electron pairs, while ``class B'' systems show erratic convergence after initial 
+oscillations and generally contain spatially dense electron clusters.\cite{Cremer_1996}
+Further insights were provided by Olsen and coworkers\cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} 
+who employed a two-state model to understand the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
+The careful analysis from Sergeev and Goodson later refined these classes depending on the position of the
+singularity closest to the origin, giving $\alpha$ singularities which have large imaginary component, 
+and $\beta$ singularities which have a very small imaginary component.%
 \cite{Goodson_2000a,Goodson_2000b,Goodson_2004,Sergeev_2005,Sergeev_2006}
-We have further highlighted that these so-called $\beta$ singularities are connected to quantum phase transitions and symmetry breaking.
-
-Finally, we have discussed several resummation techniques, such as Pad\'e and quadratic approximants, that can be used to improve energy estimates for both convergent and divergent series.
-As mentioned earlier in this manuscript, turning low-order truncated MP series into convergent and systematically improvable series would be a highly desirable feature that could drastically improve the general applicability of such methods.
-However, it is worth mentioning that the construction of these approximants requires high-order MP coefficients which are quite expensive to compute in practice.
-The Shanks transformation presented in Sec.~\ref{sec:Shanks} can, in some cases, alleviate this issue.
-
-Most of the physical concepts and mathematical tools reviewed in the present manuscript has been illustrated on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
-Although extremely simple, this clearly illustrates the obvious versatility of the Hubbard model to understand the subtle notions linked to the extension of perturbation theory into the complex plane, as well as other concepts such as Kohn-Sham density-functional theory (DFT), \cite{Carrascal_2015,Cohen_2016} linear-response theory, \cite{Carrascal_2018} many-body perturbation theory, \cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017,Olevano_2019} DFT for ensembles, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT, \cite{Smith_2016,Smith_2018} coupled cluster theory, \cite{Stein_2014,Henderson_2015,Shepherd_2016} and many others.
-We believe that the Hubbard dimer could then be used for further developments and comprehension around perturbation theory.
-
-As a concluding remark and from a broader point of view, the present work shows that our understanding of the singularity structure of the energy is still incomplete.
-Yet, we hope that the present contribution will open new perspectives on the physics of exceptional points in electronic structure theory.
+Remarkably, the position of $\beta$ singularities close to the real axis can be justified as a critical 
+point where one (or more) electrons is ionised from the molecule, creating a quantum phase transition.\cite{Stillinger_2000}
+We have shown that the slow convergence of symmetry-broken MP approximations can also be driven by a $\beta$ 
+singularity and is closely related to these quantum phase transitions.
+}
+
+% RESUMMATION
+We have also discussed several resummation techniques that can be used to improve energy estimates
+for both convergent and divergent series, including Pad\'e and quadratic approximants.
+\hugh{Furthermore, we have provided the first illustration of how the Shanks transformation can accelerate
+convergence of MP approximants to improve the accuracy of low-order approximations.}
+Using these resummation and acceleration methods to turn low-order truncated MP series into convergent and
+systematically improvable series can dramatically improve the accuracy and applicability of these perturbative methods.
+\hugh{However, the application of these approaches requires the evaluation of higher-order MP coefficents 
+(\eg, MP3, MP4, MP5, etc) that are generally expensive to compute in practice.
+There is therefore a strong demand for computationally efficient approaches to evaluate general terms in the MP 
+series, and the development of stochastic, resolution-of-the-identity, or linear-scaling approximations
+may prove fruitful avenues in this direction.
+}
+
+% ORBITAL OPTIMISATION EXCITED STATES
+\hugh{
+The present review has only considered the convergence of the MP series using the RHF or UHF 
+reference orbitals.
+However, numerous recent studies have shown that the use of orbitals optimised in the presence of the MP2 
+correction or using Kohn--Sham density-functional theory (DFT) orbitals 
+can significantly improve the accuracy of the MP3 correction,
+particularly in the presence of symmetry-breaking.
+Beyond intuitive heuristics, it is not clear why these alternative orbitals provide such accurate results, 
+and a detailed investigation of their MP energy function in the complex plane is therefore bound to provide
+fascinating insights.
+Furthermore, the convergence properties of the excited-state MP series using orbital-optimised higher energy 
+HF solutions remains entirely unexplored.
+}
+
+% HUBBARD
+Finally, the physical concepts and mathematical tools presented in this manuscript have been illustrated 
+on the symmetric (or asymmetric in one occasion) Hubbard dimer at half-filling.
+Although extremely simple, these illustrations highlight the incredible versatility of the Hubbard model
+for understanding the subtle features of perturbation theory in the complex plane, alongisde other examples 
+such as Kohn-Sham DFT, \cite{Carrascal_2015,Cohen_2016} linear-response theory,\cite{Carrascal_2018} 
+many-body perturbation theory,\cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017,Olevano_2019} 
+ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 
+coupled cluster theory,\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
+\hugh{In particular, we have shown that the Hubbard dimer contains suifficient flexibility to describe 
+the effects of symmetry breaking, the MP critical point, and resummation techniques, in contrast to the more 
+minimalistic models considered previously.
+We therefore propose that the Hubbard dimer provides the ideal arena for further developing our fundamental understanding
+and applications of perturbation theory.}
+
+% DIRECTIONS
+\hugh{Perturbation theory isn't usually considered in the complex plane. 
+But when it is, we have seen that a lot can be learnt about the performance of perturbation theory on the real axis.
+These insights can allow incredibly accurate results to be obtained using only the lowest-order terms in a perturbation series.
+Yet perturbation theory represents only one method for approximating the exact energy, and few other methods
+have been considered through similar complex non-Hermitian extensions.
+There is therefore much still to be discovered about the existence and consequences of exceptional points
+throughout electronic structure theory.}
 

### 2020-12-04 Manuscript/EPAWTFT.tex
Modified conclusions

@@
 oscillations and generally contain spatially dense electron clusters.\cite{Cremer_1996}
-Further insights were provided by Olsen and coworkers\cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019} 
-who employed a two-state model to understand the various convergence behaviours of Hermitian and non-Hermitian perturbation series.
+Further insights were provided by Olsen and coworkers
+who employed a two-state model to understand the various convergence behaviours of Hermitian and non-Hermitian 
+perturbation series.\cite{Christiansen_1996,Olsen_1996,Olsen_2000,Olsen_2019}
 The careful analysis from Sergeev and Goodson later refined these classes depending on the position of the
@@
 There is therefore a strong demand for computationally efficient approaches to evaluate general terms in the MP 
-series, and the development of stochastic, resolution-of-the-identity, or linear-scaling approximations
+series, and the development of stochastic,\cite{Thom_2007,Neuhauser_2012,Willow_2012,Takeshita_2017,Li_2019}
+or linear-scaling approximations\cite{Rauhut_1998,Schutz_1999}
 may prove fruitful avenues in this direction.
@@
 However, numerous recent studies have shown that the use of orbitals optimised in the presence of the MP2 
-correction or using Kohn--Sham density-functional theory (DFT) orbitals 
-can significantly improve the accuracy of the MP3 correction,
+correction\cite{Bozkaya_2011,Neese_2009,Lee_2018} or Kohn--Sham density-functional theory (DFT) orbitals 
+can significantly improve the accuracy of the MP3 correction,\cite{Bertels_2019,Rettig_2020}
 particularly in the presence of symmetry-breaking.
@@
 Furthermore, the convergence properties of the excited-state MP series using orbital-optimised higher energy 
-HF solutions remains entirely unexplored.
+HF solutions\cite{Gilbert_2008} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}
 }

### 2020-12-04 Manuscript/EPAWTFT.tex
Rename to Concluding Remarks
edits to the abstract

@@
 \begin{abstract}
-We explore the extension of quantum chemistry in the complex plane and its link with perturbation theory.
+We explore the non-Hermitian extension of quantum chemistry in the complex plane and its link with perturbation theory.
 We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptional points.
-After a presentation of the fundamental notions of quantum chemistry in the complex plane, such as the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
-In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory and its apparent link with quantum phase transitions.
-We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) able to improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
-Each of these points is further illustrated with the ubiquitous Hubbard dimer at half filling which proves to be a versatile model system in order to understand the subtle concepts of the analytic continuation of perturbation theory into the complex plane.
+After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
+We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) that can improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
+Each of these points is pedagogically illustrated using the Hubbard dimer at half filling, which proves to be a versatile model for understanding the subtlety of analytically-continued perturbation theory in the complex plane.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
+\section{Concluding Remarks}
 \label{sec:ccl}

### 2020-12-04 Manuscript/EPAWTFT.tex
intro OK

--- 2020-12-04 Manuscript/EPAWTFT.tex
@@
 % SPIKE THE READER
-\hugh{Perturbation theory isn't usually considered in the complex plane.
+Perturbation theory isn't usually considered in the complex plane.
 Normally it is applied using real numbers as one of very few availabe tools for 
@@
 are essential for understanding the quality of perturbative approximations on the real axis.
-}
 
@@
 %principle providing a fundamental understanding of chemical structure, bonding, and reactivity.
-\hugh{In electronic structure theory,} the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) %perturbation 
+In electronic structure theory, the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) %perturbation 
 theory,\cite{Moller_1934} which remains one of the most popular methods for computing the electron 
@@
 of a mean-field Hartree--Fock (HF) approximation.\cite{SzaboBook}
-The popularity of MP theory stems from its black-box nature, \hugh{size-extensivity,} and relatively low computational scaling, 
+The popularity of MP theory stems from its black-box nature, size-extensivity, and relatively low computational scaling, 
 making it easily applied in a broad range of molecular research.\cite{HelgakerBook}
@@
 As a result, practical applications typically employ only the lowest-order MP2 approach, while 
-the successive MP3, MP4, and MP5 (and higher \hugh{order}) terms are generally not considered to offer enough improvement
+the successive MP3, MP4, and MP5 (and higher order) terms are generally not considered to offer enough improvement
 to justify their increased cost.
@@
 
-\trashHB{The present review is organised as follows.}
-In Sec.~\ref{sec:EPs}, we introduce the key concepts such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their \hugh{non-Hermitian} analytic continuation into the complex plane.
+In Sec.~\ref{sec:EPs}, we introduce the key concepts such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their non-Hermitian analytic continuation into the complex plane.
 Section \ref{sec:MP} presents MP perturbation theory and we report a comprehensive historical overview of the research that
@@
 of low-order MP approximations, including Pad\'e and quadratic approximants.
-Finally, we draw our conclusions in Sec.~\ref{sec:ccl} \hugh{and highlight our perspective on directions for 
-future research}.
+Finally, we draw our conclusions in Sec.~\ref{sec:ccl} and highlight our perspective on directions for 
+future research.
 Throughout this review, we present illustrative and pedagogical examples based on the ubiquitous 
-Hubbard dimer, \hugh{reinforcing} the amazing versatility of this powerful simplistic model.
+Hubbard dimer, reinforcing the amazing versatility of this powerful simplistic model.
 

### 2020-12-04 Manuscript/EPAWTFT.tex
OK

@@
 % INTRO TO CONC.
-\hugh{To accurately model chemical systems, one must choose a computational protocol from an ever growing 
+To accurately model chemical systems, one must choose a computational protocol from an ever growing 
 collection of theoretical methods.
@@
 of certain properties depending on the system that is being studied.
-}
 It is therefore essential that we understand the strengths and weaknesses of different methods, 
@@
 \cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988} 
-\hugh{In particular, the spin-symmetry-broken unrestricted MP series is notorious
+In particular, the spin-symmetry-broken unrestricted MP series is notorious
 for giving incredibly slow convergence.\cite{Gill_1986,Nobes_1987,Gill_1988a,Gill_1988}
 All these behaviours can be rationalised and explained by the position of exceptional points
-and other singularities that arise when perturbation theory is extended across the complex plane.}
+and other singularities that arise when perturbation theory is extended across the complex plane.
 
 % CLASSIFICATIONS
-\hugh{%
 The classifications of different convergence types developed by Cremer and He,\cite{Cremer_1996} 
@@
 Remarkably, the position of $\beta$ singularities close to the real axis can be justified as a critical 
-point where one (or more) electrons is ionised from the molecule, creating a quantum phase transition.\cite{Stillinger_2000}
+point where one (or more) electron is ionised from the molecule, creating a quantum phase transition.\cite{Stillinger_2000}
 We have shown that the slow convergence of symmetry-broken MP approximations can also be driven by a $\beta$ 
 singularity and is closely related to these quantum phase transitions.
-}
 
@@
 for both convergent and divergent series, including Pad\'e and quadratic approximants.
-\hugh{Furthermore, we have provided the first illustration of how the Shanks transformation can accelerate
-convergence of MP approximants to improve the accuracy of low-order approximations.}
+Furthermore, we have provided the first illustration of how the Shanks transformation can accelerate
+convergence of MP approximants to improve the accuracy of low-order approximations.
 Using these resummation and acceleration methods to turn low-order truncated MP series into convergent and
 systematically improvable series can dramatically improve the accuracy and applicability of these perturbative methods.
-\hugh{However, the application of these approaches requires the evaluation of higher-order MP coefficents 
+However, the application of these approaches requires the evaluation of higher-order MP coefficients 
 (\eg, MP3, MP4, MP5, etc) that are generally expensive to compute in practice.
@@
 may prove fruitful avenues in this direction.
-}
 
 % ORBITAL OPTIMISATION EXCITED STATES
-\hugh{
 The present review has only considered the convergence of the MP series using the RHF or UHF 
@@
 HF solutions\cite{Gilbert_2008} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}
-}
 
@@
 coupled cluster theory,\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
-\hugh{In particular, we have shown that the Hubbard dimer contains suifficient flexibility to describe 
+In particular, we have shown that the Hubbard dimer contains sufficient flexibility to describe 
 the effects of symmetry breaking, the MP critical point, and resummation techniques, in contrast to the more 
@@
 We therefore propose that the Hubbard dimer provides the ideal arena for further developing our fundamental understanding
-and applications of perturbation theory.}
+and applications of perturbation theory.
 
 % DIRECTIONS
-\hugh{Perturbation theory isn't usually considered in the complex plane. 
+Perturbation theory isn't usually considered in the complex plane. 
 But when it is, we have seen that a lot can be learnt about the performance of perturbation theory on the real axis.
@@
 There is therefore much still to be discovered about the existence and consequences of exceptional points
-throughout electronic structure theory.}
+throughout electronic structure theory.
 

### 2020-12-04 Cover_Letter/CoverLetter.tex
cover letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,mathpazo,ragged2e,url}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of Journal of Physics: Condensed Matter (JPCM)}

\opening{Dear Editors,}

\justifying
Following the recent invitation of Ania Wronski, please find enclosed our manuscript entitled \textit{``Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them''}, which we would like you to consider as a Topical Review in \textit{J. Phys. Cond. Mat.}

The present multidisciplinary review explores the non-Hermitian extension of computational quantum chemistry in the complex plane and its link with perturbation theory.
In particular, we focus on its mathematical roots and its connection with physical phenomena such as quantum phase transitions and exceptional points in the complex plane.
We begin by presenting the fundamental concepts behind non-Hermitian extensions of quantum chemistry into the complex plane, including the Hartree-Fock approximation and
Rayleigh-Schr\"odinger perturbation theory. 
We then provide a comprehensive review of the various research that has been performed around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller?Plesset theory.
Finally, several resummation techniques that can be used to improve energy estimates for both convergent and divergent series (including Pad\'e and quadratic approximants) are discussed. 
Throughout this review, we present illustrative and pedagogical examples based on the ubiquitous Hubbard dimer at half-filling, reinforcing the amazing versatility of this powerful simplistic model.

Due to the genuine interdisciplinary nature of the present article and its pedological aspect, we believe that it will be of interest to a wide audience within the physics and chemistry communities.
We hope that the editors and the reviewers of JPCM will find this topical review enjoyable and educative.

\closing{Sincerely, the authors.}

\end{letter}
\end{document}

### 2020-12-04 Manuscript/EPAWTFT.tex
one more ref to Hirata

@@
 such as Kohn-Sham DFT, \cite{Carrascal_2015,Cohen_2016} linear-response theory,\cite{Carrascal_2018} 
-many-body perturbation theory,\cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Tarantino_2017,Olevano_2019} 
+many-body perturbation theory,\cite{Romaniello_2009,Romaniello_2012,DiSabatino_2015,Hirata_2015,Tarantino_2017,Olevano_2019} 
 ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 

### 2020-12-04 Cover_Letter/CoverLetter.tex
cover letter
Minor edits to cover letter

@@
 \begin{letter}%
-{To the Editors of Journal of Physics: Condensed Matter (JPCM)}
+{To the Editors of the Journal of Physics: Condensed Matter (JPCM)}
 
@@
 
-The present multidisciplinary review explores the non-Hermitian extension of computational quantum chemistry in the complex plane and its link with perturbation theory.
-In particular, we focus on its mathematical roots and its connection with physical phenomena such as quantum phase transitions and exceptional points in the complex plane.
-We begin by presenting the fundamental concepts behind non-Hermitian extensions of quantum chemistry into the complex plane, including the Hartree-Fock approximation and
-Rayleigh-Schr\"odinger perturbation theory. 
-We then provide a comprehensive review of the various research that has been performed around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller?Plesset theory.
-Finally, several resummation techniques that can be used to improve energy estimates for both convergent and divergent series (including Pad\'e and quadratic approximants) are discussed. 
+This multidisciplinary review explores the non-Hermitian extension of computational quantum chemistry to the complex plane and its link with perturbation theory.
+In particular, we focus on its mathematical roots and connections with physical phenomena such as quantum phase transitions and exceptional points in the complex plane.
+We begin by presenting the fundamental concepts behind non-Hermitian extensions of quantum chemistry into the complex plane, including the Hartree--Fock approximation and
+Rayleigh--Schr\"odinger perturbation theory. 
+We then provide a comprehensive review of the various research that has been performed around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller--Plesset theory.
+Finally, several resummation techniques are discussedthat can improve energy estimates for both convergent and divergent series, including Pad\'e and quadratic approximants.
 Throughout this review, we present illustrative and pedagogical examples based on the ubiquitous Hubbard dimer at half-filling, reinforcing the amazing versatility of this powerful simplistic model.
 
-Due to the genuine interdisciplinary nature of the present article and its pedological aspect, we believe that it will be of interest to a wide audience within the physics and chemistry communities.
-We hope that the editors and the reviewers of JPCM will find this topical review enjoyable and educative.
+Due to the genuine interdisciplinary nature of the present article and its pedagogical aspect, we believe that it will be of interest to a wide audience within the physics and chemistry communities.
+We hope that the editors and the reviewers of \textit{JPCM} will find this topical review enjoyable and educative.
+
+We suggest Paola Gori-Giorgi, Jeppe Olsen, So Hirata, Peter Knowles, and Kieron Burke as potential referees.
+We look forward to hearing from you soon.
 

### 2020-12-04 Manuscript/EPAWTFT.tex
Minor edits to cover letter
Re-added contour to fig1b

--- 2020-12-04 Manuscript/EPAWTFT.tex
@@
     The contour followed around the EP in order to interchange states is also represented.
-    \hugh{HUGH TO ADD CONTOUR AGAIN....}
 	\label{fig:FCI}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb]
-	\includegraphics[width=\linewidth]{fig5}
-	\caption{
-	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
-    series as functions of the ratio $U/t$.
-	\label{fig:RadConv}}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
@@
 for the two states using the ground-state RHF orbitals is identical.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% RADIUS OF CONVERGENCE PLOTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+	\includegraphics[width=\linewidth]{fig5}
+	\caption{
+	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
+    series as functions of the ratio $U/t$.
+	\label{fig:RadConv}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 		real axis, giving a sharp avoided crossing on the real axis (solid).
-		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the \trash{exact} limit $t \to 0$.
+		(\subref{subfig:rmp_ep_to_cp}) Convergence of the ground-state EP onto the real axis in the limit $t \to 0$.
 	\label{fig:RMP_cp}}
@@
 Perturbation theory isn't usually considered in the complex plane. 
-But when it is, we have seen that a lot can be learnt about the performance of perturbation theory on the real axis.
+But when it is, a lot can be learnt about the performance of perturbation theory on the real axis.
 These insights can allow incredibly accurate results to be obtained using only the lowest-order terms in a perturbation series.

### 2020-12-05 Cover_Letter/CoverLetter.tex
OK with abstract and intro

@@
 We then provide a comprehensive review of the various research that has been performed around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller--Plesset theory.
-Finally, several resummation techniques are discussedthat can improve energy estimates for both convergent and divergent series, including Pad\'e and quadratic approximants.
+Finally, several resummation techniques are discussed that can improve energy estimates for both convergent and divergent series, including Pad\'e and quadratic approximants.
 Throughout this review, we present illustrative and pedagogical examples based on the ubiquitous Hubbard dimer at half-filling, reinforcing the amazing versatility of this powerful simplistic model.

### 2020-12-05 Manuscript/EPAWTFT.tex
OK with abstract and intro

@@
 Normally it is applied using real numbers as one of very few availabe tools for 
-describing realistic quantum systems where exact solutions of the Schr\"odinger equation are impossible.\cite{Dirac_1929}
+describing realistic quantum systems where exact solutions of the Schr\"odinger equation are impossible \titou{to find?}.\cite{Dirac_1929}
 In particular, time-independent Rayleigh--Schr\"odinger perturbation theory\cite{RayleighBook,Schrodinger_1926} 

### 2020-12-05 Manuscript/EPAWTFT.tex
OK with abstract and intro

@@
 
-% Good old Schroedinger
-%The electronic Schr\"odinger equation,
-%\begin{equation}
-%	\hH \Psi = E \Psi,
-%\end{equation}
-%is the starting point for a fundamental understanding of the behaviour of electrons and, thence, of chemical structure, bonding and reactivity. 
-%However, as famously stated by Dirac: \cite{Dirac_1929}
-%\begin{quote}
-%	\textit{``The underlying physical laws necessary for the mathematical theory of a large part of physics and the whole of chemistry are thus completely known, and the difficulty is only that the exact application of these laws leads to equations much too complicated to be soluble.
-%	It therefore becomes desirable that approximate practical methods of applying quantum mechanics should be developed, which can lead to an explanation of the main features of complex atomic systems without too much computation.''}
-%\end{quote}
-%Indeed, as anticipated by Dirac, accurately predicting the energetics of electronic states from first principles has been one of the grand challenges faced by theoretical chemists and physicists since the dawn of quantum mechanics.
-
-% RSPT
-%Together with the variational principle, perturbation theory is one of the very few essential tool for describing realistic quantum systems for which it is impossible to find the exact solution of the Schr\"odinger equation.
-%In particular, time-independent Rayleigh--Schr\"odinger perturbation theory \cite{RayleighBook,Schrodinger_1926} has cemented itself as an instrument of choice in the armada of theoretical and computational methods that have been developed for this purpose.
-\cite{SzaboBook,JensenBook,CramerBook,HelgakerBook,ParrBook,FetterBook,ReiningBook}
-
 % Moller-Plesset
-%\hugh{Accurately predicting the electronic energy is the primary focus of electronic structure theory, in 
-%principle providing a fundamental understanding of chemical structure, bonding, and reactivity.
 In electronic structure theory, the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) %perturbation 
@@
 correlation energy.\cite{Wigner_1934,Lowdin_1958}
-%\trashHB{an old yet important concept, first introduced by Wigner \cite{Wigner_1934} and later defined by L\"owdin. \cite{Lowdin_1958}}
 This approach estimates the exact electronic energy by constructing a perturbative correction on top

### 2020-12-05 Manuscript/EPAWTFT.tex
OK with abstract and intro
OK with Sec II

@@
 
-\newcommand{\updot}{%
-  \mathrel{\ooalign{\hfil$\vcenter{
-    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\uparrow$\cr}
-  }%
-}
-\newcommand{\dwdot}{%
-  \mathrel{\ooalign{\hfil$\vcenter{
-    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\downarrow$\cr}
-  }%
-}
-\newcommand{\vac}{%
-  \mathrel{\ooalign{\hfil$\vcenter{
-    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$ $\cr}
-  }%
-}
-
-\newcommand{\uddot}{%
-  \mathrel{\ooalign{\hfil$\vcenter{
-    \hbox{$\scriptscriptstyle\bullet$}}$\hfil\cr$\uparrow\downarrow$\cr}
-  }%
-}
-
 % Center tabularx columns
@@
 We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptional points.
-After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh-Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
+After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
 In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
@@
 
-In Sec.~\ref{sec:EPs}, we introduce the key concepts such as Rayleigh-Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their non-Hermitian analytic continuation into the complex plane.
+In Sec.~\ref{sec:EPs}, we introduce the key concepts such as Rayleigh--Schr\"odinger perturbation theory and the mean-field HF approximation, and discuss their non-Hermitian analytic continuation into the complex plane.
 Section \ref{sec:MP} presents MP perturbation theory and we report a comprehensive historical overview of the research that
@@
 	\includegraphics[height=0.65\textwidth]{fig1a}
-	\subcaption{\label{subfig:FCI_real}}
+	\subcaption{\titou{Real axis} \label{subfig:FCI_real}}
     \end{subfigure}
@@
 	\includegraphics[height=0.65\textwidth]{fig1b}
-	\subcaption{\label{subfig:FCI_cplx}}
+	\subcaption{\titou{Complex plane} \label{subfig:FCI_cplx}}
     \end{subfigure}
@@
 \begin{align*}
-& \ket{\Lup \Ldown} &  & \ket{\Lup\Rdown} &  & \ket{\Rup\Ldown} &  & \ket{\Rup\Rdown}
+& \ket{\Lup \Ldown}, &  & \ket{\Lup\Rdown}, &  & \ket{\Rup\Ldown}, &  & \ket{\Rup\Rdown},
 \end{align*}
@@
 	\label{eq:PolChar}
-	\det[E\hI-\hH(\lambda)] & = 0,
+	\det[\hH(\lambda) - E \hI] & = 0,
 	\\ 
 	\label{eq:DPolChar}
-	\pdv{E}\det[E\hI-\hH(\lambda)] & = 0,
+	\pdv{E}\det[\hH(\lambda) - E \hI] & = 0,
 \end{align}
@@
 %============================================================%
-\subsection{Rayleigh-Schr\"odinger Perturbation Theory}
+\subsection{Rayleigh--Schr\"odinger Perturbation Theory}
 %============================================================%
@@
 % SUMMARY OF RS-PT
-Within Rayleigh-Schr\"odinger perturbation theory, the time-independent Schr\"odinger equation 
+Within Rayleigh--Schr\"odinger perturbation theory, the time-independent Schr\"odinger equation 
 is recast as 
@@
 \begin{align}
-    \Psi(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,\Psi^{(k)} 
+    \Psi(\lambda) &= \sum_{k=0}^{\infty} \lambda^{k}\,\Psi^{(k)},
     \label{eq:psi_expansion}
@@
 \end{subequations}
-solving the corresponding perturbation equations up to a given order $k$, and
+solving the corresponding perturbation equations up to a given order \titou{$n$}, and
 setting $\lambda = 1$ then yields approximate solutions to Eq.~\eqref{eq:SchrEq}.
@@
 % LAMBDA IN THE COMPLEX PLANE
-From complex-analysis, \cite{BenderBook} the radius of convergence for the energy can be obtained by looking for the 
+From complex analysis, \cite{BenderBook} the radius of convergence for the energy can be obtained by looking for the 
 singularities of $E(\lambda)$ in the complex $\lambda$ plane.
@@
 % SUMMARY OF HF
-In the Hartree--Fock (HF) approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_N)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
+In the \trash{Hartree--Fock (HF)} \titou{HF} approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_\Ne)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
 This Slater determinant is defined as an antisymmetric combination of $\Ne$ (real-valued) occupied one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
@@
 \label{eq:Hcore}
-	\Hat{h}(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{M} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
+	\Hat{h}(\vb{x}) = -\frac{\grad^2}{2} + \sum_{A}^{\Nn} \frac{Z_A}{\abs{\vb{r}-\vb{R}_A}}
 \end{equation}
@@
 \begin{equation}
-    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{N} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
+    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{\Ne} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
 \end{equation}
@@
     \label{eq:E_HF}
-    E_\text{HF} = \frac{1}{2} \sum_i^{N} \qty( h_i + f_i ),
+    E_\text{HF} = \frac{1}{2} \sum_i^{\Ne} \qty( h_i + f_i ),
 \end{equation}
@@
 \begin{equation}\label{eq:HFHamiltonian}
-	\hH_{\text{HF}} = \sum_{i}^{N} f(\vb{x}_i).
+	\hH_{\text{HF}} = \sum_{i}^{\Ne} f(\vb{x}_i).
 \end{equation}
@@
 and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993,Jimenez-Hoyos_2011}
-However, the application of HF with some level of constraint on the orbital structure is far more common.
+However, the application of HF \titou{theory} with some level of constraint on the orbital structure is far more common.
 Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) method, 
@@
     RHF and UHF energies in the Hubbard dimer as a function of the correlation strength $U/t$. 
-    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson-Fischer point.}
+    The symmetry-broken UHF solution emerges at the coalescence point $U=2t$ (black dot), often known as the Coulson--Fischer point.}
 \end{figure}
@@
 \begin{equation}
-	E_\text{RHF} \equiv E_\text{HF}(\ta^\text{RHF}, \tb^\text{RHF}) = -2t + \frac{U}{2}
+	E_\text{RHF} \equiv E_\text{HF}(\ta^\text{RHF}, \tb^\text{RHF}) = -2t + \frac{U}{2}.
 \end{equation}
@@
 \end{equation}
-Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped pair, obtained 
+Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped \titou{pair?}, obtained 
 by swapping $\ta^{\text{UHF}}$ and $\tb^{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.

### 2020-12-05 Manuscript/EPAWTFT.tex
OK up to Sec IIIc

@@
 
-To illustrate the concepts discussed throughout this article, we consider the symmetric Hubbard dimer at half filling, \ie\ with two opposite-spin fermions.
+To illustrate the concepts discussed throughout this article, we consider the symmetric Hubbard dimer at half filling, \ie, with two opposite-spin fermions.
 Analytically solvable models are essential in theoretical chemistry and physics as their mathematical simplicity compared to realistic systems (e.g., atoms and molecules) allows new concepts and methods to be
@@
 the only possibility and alternative partitionings have been considered including: 
-i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian. \cite{Nesbet_1955,Epstein_1926} 
+i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian, \cite{Nesbet_1955,Epstein_1926} 
 ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
@@
 Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
-increasingly small at larger bond lengths, leading to a divergence, for example, in the second-order MP correction \eqref{eq:EMP2}.
+increasingly small at larger bond lengths, leading to a divergence, for example, in the \trash{second-order MP} \titou{MP2} correction \eqref{eq:EMP2}.
 In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains

### 2020-12-05 Manuscript/EPAWTFT.tex
OK up to Sec IIIE

@@
 On the other hand, triple excitations have an important contribution in class B systems, including providing
-orbital relaxation, and these contributions lead to oscillations of the total correlation energy.
+orbital relaxation \titou{to doubly-excited states}, and these contributions lead to oscillations of the total correlation energy.
 
@@
 \begin{align}
+	\label{eq:CrHeA}
 \Delta E_{\text{A}}
@@
      + \frac{\Emp^{(5)}}{1 - (\Emp^{(6)} / \Emp^{(5)})}, 
-     \\[5pt]
+     \\
+	\label{eq:CrHeB}
 \Delta E_{\text{B}} 
@@
 Finally, Ref.~\onlinecite{Olsen_1996} proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} 
-are not mathematically motivated when considering the complex singularities causing the divergence, and therefore
-cannot be applied for all systems.
+\titou{[see Eqs.~\eqref{eq:CrHeA} and \eqref{eq:CrHeB}]} are not mathematically motivated when considering the complex 
+singularities causing the divergence, and therefore cannot be applied for all systems.
 For example, the \ce{HF} molecule contains both back-door intruder states and low-lying doubly-excited states that

### 2020-12-05 Manuscript/EPAWTFT.tex
OK up to Sec IIIF

@@
 the relationship with the location of the dominant singularity that controls the radius of convergence.\cite{Goodson_2004}
-They demonstrated that the dominant singularity in class A systems corresponds to a EP with a positive real component, 
+They demonstrated that the dominant singularity in class A systems corresponds to an EP with a positive real component, 
 where the magnitude of the imaginary component controls the oscillations in the signs of successive MP 
@@
 allows the formation of the critical point as the electrons form a bound cluster occupying the ghost atom orbitals.\cite{Sergeev_2005}
-This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to hydrogen at
+This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to \titou{the} hydrogen at
  a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
@@
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained using various resummation 
-    techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
+    RMP ground-state energy as a function of $\lambda$ obtained using various \titou{truncated Taylor series and approximants} 
+    at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
 \end{figure*}
@@
     \caption{\label{fig:QuadUMP}
-    UMP energies as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3$.}
+    UMP energies as a function of $\lambda$ obtained using various \titou{approximants} at $U/t = 3$.}
 \end{figure}
@@
     \caption{Estimate for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$
-    in the UMP energy function provided by various resummation techniques at $U/t = 3$ and $7$.
+    in the UMP energy function provided by various \titou{truncated Taylor series and approximants} at $U/t = 3$ and $7$.
 	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch 
@@
         The two functions correspond closely within the radius of convergence.
+        \titou{T2: are we keeping this?}
     }

### 2020-12-05 Manuscript/EPAWTFT.tex
OK with III

@@
 and again a less negative $\lambda$ is required for ionisation to occur.
-Both of these factors are common in atoms on the right-hand side of the periodic table, \eg\ \ce{F},
+Both of these factors are common in atoms on the right-hand side of the periodic table, \eg, \ce{F},
 \ce{O}, \ce{Ne}.
@@
 becomes increasingly repulsive.
-Closed--shell critical points along the positive real $\lambda$ axis then represent 
+Closed-shell critical points along the positive real $\lambda$ axis then represent 
 points where the two-electron repulsion overcomes the attractive HF potential 
-and a single electron dissociates from the molecule (see Ref.~\onlinecite{Sergeev_2006})
+and a single electron dissociates from the molecule (see Ref.~\onlinecite{Sergeev_2006}).
 

### 2020-12-05 Manuscript/EPAWTFT.tex
OK with IV

@@
 	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
-    series as functions of the ratio $U/t$.
+    series \titou{of the Hubbard dimer} as functions of the ratio $U/t$.
 	\label{fig:RadConv}}
@@
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ obtained using various \titou{truncated Taylor series and approximants} 
+    RMP ground-state energy as a function of $\lambda$ \titou{in the Hubbard dimer} obtained using various \titou{truncated Taylor series and approximants} 
     at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
@@
 \begin{table}[b]
-	\caption{RMP ground-state energy estimate at $\lambda = 1$ provided by various truncated Taylor 
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ \titou{of the Hubbard dimer} provided by various truncated Taylor 
     series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
@@
     \caption{\label{fig:QuadUMP}
-    UMP energies as a function of $\lambda$ obtained using various \titou{approximants} at $U/t = 3$.}
+    UMP energies \titou{in the Hubbard dimer} as a function of $\lambda$ obtained using various \titou{approximants} at $U/t = 3$.}
 \end{figure}
@@
 	\label{eq:QuadApp}
-	E(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ],
+	\titou{E_{[d_P/d_Q,d_R]}}(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ],
 \end{equation}
@@
     \caption{Estimate for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$
-    in the UMP energy function provided by various \titou{truncated Taylor series and approximants} at $U/t = 3$ and $7$.
+    in the UMP energy function \titou{of the Hubbard dimer} provided by various \titou{truncated Taylor series and approximants} at $U/t = 3$ and $7$.
 	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch 
@@
 Comparison of the [3/2,2] and [3/0,4] quadratic approximants with the exact UMP energy surface in the complex $\lambda$ 
-plane with $U/t = 3$. 
+plane \titou{in the Hubbard dimer} with $U/t = 3$. 
 Both quadratic approximants correspond to the same truncation degree of the Taylor series and model the branch points 
@@
 	\caption{
-    Estimate and associated error of the exact UMP energy at $U/t = 7$ for 
+    Estimate and associated error of the exact UMP energy \titou{of the Hubbard dimer} at $U/t = 7$ for 
     various approximants using up to ten terms in the Taylor expansion.
@@
 \begin{equation}
-    T(S_n) = \frac{S_{n+1} S_{n-1} - S_{n}^2}{S_{n+1} + S_{n-1} - 2 S_{n}}.
+    T(S_n) = \frac{S_{n+1} S_{n-1} - S_{n}^2}{S_{n+1} - 2 S_{n} + S_{n-1}}.
 \end{equation}
@@
 However, it is only designed to accelerate converging partial sums with 
-the approximate form
-\begin{equation}
-    S_n \approx S + \alpha\,\beta^n.
-\end{equation}
+the approximate form $S_n \approx S + \alpha\,\beta^n$.
 Furthermore, while this transformation can accelerate the convergence of a series, 
@@
     Acceleration of the diagonal Pad\'e approximant sequence for the RMP energy
-    using the Shanks transformation.
+    \titou{of the Hubbard dimer at $U/t = 3.5$ and $4.5$} using the Shanks transformation.
 	\label{tab:RMP_shank}}
@@
         Comparison of the scaled RMP10 Taylor expansion with the exact RMP energy as a function
-        of $\lambda$ for the symmetric Hubbard dimer at $U/t = 4.5$. 
+        of $\lambda$ for the \trash{symmetric} Hubbard dimer at $U/t = 4.5$. 
         The two functions correspond closely within the radius of convergence.
@@
 The authors illustrate this protocol for the dissociation curve of \ce{LiH} and the stretched water 
-molecule to obtain encouragingly accurate results.\cite{Mihalka_2019}
+molecule \trash{to obtain} \titou{and obtained?} encouragingly accurate results.\cite{Mihalka_2019}
 

### 2020-12-05 Manuscript/EPAWTFT.tex
DONE

@@
 Furthermore, the convergence properties of the excited-state MP series using orbital-optimised higher energy 
-HF solutions\cite{Gilbert_2008} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}
+HF solutions\cite{Gilbert_2008,Barca_2014,Barca_2018a,Barca_2018b} remains entirely unexplored.\cite{Lee_2019,CarterFenk_2020}
 
@@
 ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 
-coupled cluster theory,\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
+\titou{wave function methods},\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
 In particular, we have shown that the Hubbard dimer contains sufficient flexibility to describe 

### 2020-12-05 Manuscript/EPAWTFT.tex
one more Paola ref

@@
 \usepackage{subcaption}
-\usepackage{bm,graphicx,tabularx,array,booktabs,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx,mhchem}
+\usepackage{bm,graphicx,tabularx,array,booktabs,dcolumn,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,siunitx}
+\usepackage[version=4]{mhchem}
 \usepackage[utf8]{inputenc}
@@
 ii) the weak correlation partitioning in which the one-electron part is consider as the unperturbed Hamiltonian $\hH^{(0)}$ and the two-electron part is the perturbation operator $\hV$, and 
-iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018}
+iii) the strong coupling partitioning where the two operators are inverted compared to the weak correlation partitioning. \cite{Seidl_2018,Daas_2020}
 While an in-depth comparison of these different approaches can offer insight into 

### 2020-12-05 Manuscript/EPAWTFT.tex
keywords

@@
-\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
+\documentclass[aps,prb,reprint,showkeys,superscriptaddress]{revtex4-1}
 \usepackage{subcaption}
@@
 \newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France.}
-\newcommand{\UCAM}{Department of Chemistry, University of Cambridge, Lensfield Road, Cambridge, CB2 1EW, U.K.}
 \newcommand{\UOX}{Physical and Theoretical Chemical Laboratory, Department of Chemistry, University of Oxford, Oxford, OX1 3QZ, U.K.}
@@
 
+\keywords{perturbation theory, complex plane, exceptional point, divergent series, resummation}
+
 \maketitle
-
 %\raggedbottom

### 2020-12-06 Manuscript/EPAWTFT.tex
antoine's full read

@@
 \newcommand{\antoine}[1]{\textcolor{cyan}{#1}}
+\newcommand{\trashantoine}[1]{\textcolor{cyan}{\sout{#1}}}
 
@@
 Perturbation theory isn't usually considered in the complex plane.
-Normally it is applied using real numbers as one of very few availabe tools for 
+Normally it is applied using real numbers as one of very few available tools for 
 describing realistic quantum systems where exact solutions of the Schr\"odinger equation are impossible \titou{to find?}.\cite{Dirac_1929}
@@
 Our conventional view of electronic structure theory is centred around the Hermitian notion of quantised energy levels,
-where the different electronic states of a molecular are discrete and energetically ordered.
+where the different electronic states of a molecular \antoine{molecule or molecular system?} are discrete and energetically ordered.
 The lowest energy state defines the ground electronic state, while higher energy states
@@
 \begin{equation}\label{eq:FockOp}
-    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty[ \Hat{h}(\vb{x}) + \Hat{v}_\text{HF}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
+    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty[ \Hat{h}(\vb{x}) + \Hat{v}^{\antoine{\text{HF}}}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
 \end{equation}
@@
 \begin{equation}
-    \Hat{f}(\vb{x} ; \lambda) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}_\text{HF}(\vb{x}).
+    \Hat{f}(\vb{x} ; \lambda) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}^{\antoine{\text{HF}}}(\vb{x}).
 \end{equation}
@@
 by the vertical cylinder of unit radius.
-For the divergent case, the $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
+For the divergent case, the $\lep$ \antoine{(\sout{the} $\lep$)} lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
 outside this cylinder.
@@
 For example, while the RMP energy shows only one EP between the ground state and 
-the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two EPs: one connecting the ground state with the
+the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
 singly-excited open-shell singlet, and the other connecting this single excitation to the 

### 2020-12-06 Manuscript/EPAWTFT.tex
added changes

@@
 \newcommand{\trash}[1]{\textcolor{red}{\sout{#1}}}
-\newcommand{\trashHB}[1]{\textcolor{orange}{\sout{#1}}}
+\newcommand{\trashHB}[1]{\textcolor{hughgreen}{\sout{#1}}}
 \newcommand{\antoine}[1]{\textcolor{cyan}{#1}}
@@
 % HF rotation angles
-\newcommand{\ta}{\theta_{\alpha}}
-\newcommand{\tb}{\theta_{\beta}}
+\newcommand{\ta}{\theta^{\,\alpha}}
+\newcommand{\tb}{\theta^{\,\beta}}
+\newcommand{\ts}{\theta^{\sigma}}
 
@@
 \newcommand{\Rsi}{\mathcal{R}^{\sigma}}
-\newcommand{\vhf}{v_{\text{HF}}}
+\newcommand{\vhf}{\Hat{v}_{\text{HF}}}
+\newcommand{\whf}{\Psi_{\text{HF}}}
 
@@
 We explore the non-Hermitian extension of quantum chemistry in the complex plane and its link with perturbation theory.
-We observe that the physics of a quantum system is intimately connected to the position of energy singularities in the complex plane, known as exceptional points.
+We observe that the physics of a quantum system is intimately connected to the position of \hugh{complex-valued} energy singularities
+\trashHB{in the complex plane}, known as exceptional points.
 After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
-In particular, we highlight the seminal work of several research groups on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
+In particular, we highlight the seminal work \trashHB{of several research groups} on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
 We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) that can improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
-Each of these points is pedagogically illustrated using the Hubbard dimer at half filling, which proves to be a versatile model for understanding the subtlety of analytically-continued perturbation theory in the complex plane.
+Each of these points is \trashHB{pedagogically} illustrated using the Hubbard dimer at half filling, which proves to be a versatile model for understanding the subtlety of analytically-continued perturbation theory in the complex plane.
 \end{abstract}
@@
 Normally it is applied using real numbers as one of very few available tools for 
-describing realistic quantum systems where exact solutions of the Schr\"odinger equation are impossible \titou{to find?}.\cite{Dirac_1929}
+describing realistic quantum systems \trashHB{where exact solutions of the Schr\"odinger equation are impossible \titou{to find?}}.\cite{Dirac_1929}
 In particular, time-independent Rayleigh--Schr\"odinger perturbation theory\cite{RayleighBook,Schrodinger_1926} 
@@
 Our conventional view of electronic structure theory is centred around the Hermitian notion of quantised energy levels,
-where the different electronic states of a molecular \antoine{molecule or molecular system?} are discrete and energetically ordered.
+where the different electronic states of a \hugh{molecule} are discrete and energetically ordered.
 The lowest energy state defines the ground electronic state, while higher energy states
@@
 When the domain of $\lambda$ is extended to the complex plane, EPs can also occur in the MP energy.
-Although these EPs generally exist in the complex plane, their positions are intimately related to the 
+Although these EPs \hugh{are generally complex-valued} \trashHB{exist in the complex plane}, 
+their positions are intimately related to the 
 convergence of the perturbation expansion on the real axis.%
@@
 To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t \to \lambda t$ to give the parameterised Hamiltonian $\hH(\lambda)$.
-When $\lambda$ is real, the Hamiltonian~\eqref{eq:H_FCI} is Hermitian with the distinct (real-valued) (eigen)energies
+When $\lambda$ is real, the Hamiltonian \trashHB{\eqref{eq:H_FCI}} is Hermitian with the distinct (real-valued) (eigen)energies
 \begin{subequations}
@@
 From complex analysis, \cite{BenderBook} the radius of convergence for the energy can be obtained by looking for the 
-singularities of $E(\lambda)$ in the complex $\lambda$ plane.
+\hugh{non-analytic} singularities of $E(\lambda)$ in the complex $\lambda$ plane.
 This property arises from the following theorem: \cite{Goodson_2011}
@@
 $\lambda$ plane where two states become degenerate.
-Later we will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
+Later we will demonstrate how the choice of reference \hugh{wave function} \trashHB{Hamiltonian} controls the position of these EPs, and 
 ultimately determines the convergence properties of the perturbation series.
@@
 % SUMMARY OF HF
-In the \trash{Hartree--Fock (HF)} \titou{HF} approximation, the many-electron wave function is approximated as a single Slater determinant $\Psi^{\text{HF}}(\vb{x}_1,\ldots,\vb{x}_\Ne)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
+In the \trash{Hartree--Fock (HF)} \titou{HF} approximation, the many-electron wave function is approximated as a single Slater determinant $\whf(\vb{x}_1,\ldots,\vb{x}_\Ne)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
 This Slater determinant is defined as an antisymmetric combination of $\Ne$ (real-valued) occupied one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
 \begin{equation}\label{eq:FockOp}
-    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty[ \Hat{h}(\vb{x}) + \Hat{v}^{\antoine{\text{HF}}}(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
+    \Hat{f}(\vb{x}) \phi_p(\vb{x}) = \qty[ \Hat{h}(\vb{x}) + \vhf(\vb{x}) ] \phi_p(\vb{x}) = \epsilon_p \phi_p(\vb{x}).
 \end{equation}
@@
 \begin{equation}
-    \Hat{v}_\text{HF}(\vb{x}) = \sum_i^{\Ne} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
+    \vhf(\vb{x}) = \sum_i^{\Ne} \qty[ \Hat{J}_i(\vb{x}) - \Hat{K}_i(\vb{x}) ]
 \end{equation}
@@
 such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer.\cite{Coulson_1949}
-However, by allowing different orbitals for different spins, the UHF is no longer required to be an eigenfunction of 
-the total spin operator $\hat{\mathcal{S}}^2$, leading to ``spin-contamination'' in the wave function.
+However, by allowing different orbitals for different spins, the UHF \hugh{wave function} is no longer required to be an eigenfunction of 
+the total spin operator $\hat{\mathcal{S}}^2$, leading to ``spin-contamination''.
 
@@
 \begin{align}
-    \mathcal{B}^{\sigma} & = \hphantom{-} \cos(\frac{\theta_\sigma}{2}) \Lsi + \sin(\frac{\theta_\sigma}{2}) \Rsi,
+    \mathcal{B}^{\sigma} & = \hphantom{-} \cos(\frac{\ts}{2}) \Lsi + \sin(\frac{\ts}{2}) \Rsi,
 	\\
-	\mathcal{A}^{\sigma} & = - \sin(\frac{\theta_\sigma}{2}) \Lsi + \cos(\frac{\theta_\sigma}{2}) \Rsi
+	\mathcal{A}^{\sigma} & = - \sin(\frac{\ts}{2}) \Lsi + \cos(\frac{\ts}{2}) \Rsi
 \end{align}
@@
 In the weak correlation regime $0 \le U \le 2t$, the angles which minimise the HF energy, 
-\ie, $\pdv*{E_\text{HF}}{\theta_\sigma} = 0$, are 
-\begin{equation}
-	\ta^\text{RHF} = \tb^\text{RHF} = \pi/2,
+\ie, $\pdv*{E_\text{HF}}{\ts} = 0$, are 
+\begin{equation}
+	\ta_\text{RHF} = \tb_\text{RHF} = \pi/2,
 \end{equation}
@@
 \begin{equation}
-	E_\text{RHF} \equiv E_\text{HF}(\ta^\text{RHF}, \tb^\text{RHF}) = -2t + \frac{U}{2}.
+	E_\text{RHF} \equiv E_\text{HF}(\ta_\text{RHF}, \tb_\text{RHF}) = -2t + \frac{U}{2}.
 \end{equation}
@@
 	\caption{%
-    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta^{\text{UHF}}$ for $\lambda \in \bbC$ in the Hubbard dimer for $U/t = 2$.
+    (\subref{subfig:UHF_cplx_angle}) Real component of the UHF angle $\ta_{\text{UHF}}$ for $\lambda \in \bbC$ in the Hubbard dimer for $U/t = 2$.
     Symmetry-broken solutions correspond to individual sheets and become equivalent at 
@@
 \begin{align}
-    \ta^\text{UHF} & = \arctan (-\frac{2t}{\sqrt{U^2 - 4t^2}}),
+    \ta_\text{UHF} & = \arctan (-\frac{2t}{\sqrt{U^2 - 4t^2}}),
     \label{eq:ta_uhf}
 	\\
-    \tb^\text{UHF} & = \arctan (+\frac{2t}{\sqrt{U^2 - 4t^2}}),
+    \tb_\text{UHF} & = \arctan (+\frac{2t}{\sqrt{U^2 - 4t^2}}),
     \label{eq:tb_uhf}
@@
 \begin{equation}
-	E_\text{UHF} \equiv E_\text{HF}(\ta^\text{UHF}, \tb^\text{UHF}) = - \frac{2t^2}{U}.
+    E_\text{UHF} \equiv E_\text{HF}(\ta_\text{UHF}, \tb_\text{UHF}) = - \frac{2t^2}{U}.
 \end{equation}
 Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped \titou{pair?}, obtained 
-by swapping $\ta^{\text{UHF}}$ and $\tb^{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
+by swapping $\ta_{\text{UHF}}$ and $\tb_{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
 This type of symmetry breaking is also called a spin-density wave in the physics community as the system
@@
 \begin{equation}
-    \Hat{f}(\vb{x} ; \lambda) = \Hat{h}(\vb{x}) + \lambda\, \Hat{v}^{\antoine{\text{HF}}}(\vb{x}).
+    \Hat{f}(\vb{x} ; \lambda) = \Hat{h}(\vb{x}) + \lambda\, \vhf(\vb{x}).
 \end{equation}
@@
 In contrast, when $\lambda$ becomes complex, the HF equations become non-Hermitian and 
-each HF solutions can be analytically continued for all $\lambda$ values using
+each HF solution can be analytically continued for all $\lambda$ values using
 the holomorphic HF approach.\cite{Hiscock_2014,Burton_2016,Burton_2018}
@@
 role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.
+\hugh{Furthermore, the complex-scaled Fock operator can be used routinely construct analytic
+continuations of HF solutions beyond the points where real HF solutions
+coalesce and vanish.\cite{Burton_2019b}}
 
@@
     \\
-    + (1-\lambda) \sum_{i}^{N} v^{\text{HF}}(\vb{x}_i)
+    + (1-\lambda) \sum_{i}^{N} \vhf(\vb{x}_i)
     + \lambda\sum_{i<j}^{N}\frac{1}{\abs{\vb{r}_i-\vb{r}_j}}.
@@
 \end{equation}
-The second-order MP2 energy is given by
+The second-order MP2 energy correction is given by
 \begin{equation}\label{eq:EMP2}
-	E_{\text{MP2}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
+    \hugh{E_{\text{MP}}^{(2)}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
 \end{equation}
@@
 	Convergence of the RMP series as a function of the perturbation order $n$ for the Hubbard dimer at $U/t = 3.5$ (where $r_c > 1$) and $4.5$ (where $r_c < 1$).
-	The Riemann surfaces associated with the exact energies of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$ as functions of $\lambda$. 
+	The Riemann surfaces associated with the exact energies of the RMP Hamiltonian \eqref{eq:H_RMP} are also represented for these two values of $U/t$ as functions of complex $\lambda$. 
 	\label{fig:RMP}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each order
-of perturbation in Fig.~\ref{subfig:RMP_cvg}.
+The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each 
+\hugh{perturbation} order in Fig.~\ref{subfig:RMP_cvg}.
 In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
@@
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
-For example, while the RMP energy shows only one EP between the ground state and 
-the doubly-excited state (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
+For example, while the RMP energy shows only one EP between the ground \trashHB{state} and 
+\trashHB{the} doubly-excited states (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
 singly-excited open-shell singlet, and the other connecting this single excitation to the 
@@
 Cremer and He introduced an efficient MP6 approach and used it to analyse the RMP convergence of
-29 atomic and molecular systems with respect to the FCI energy.\cite{Cremer_1996}
+29 atomic and molecular systems \trashHB{with respect to the FCI energy}.\cite{Cremer_1996}
 They established two general classes: ``class A'' systems that exhibit monotonic convergence; 
@@
     \\
-    + \underbrace{(1-\lambda)v^{\text{HF}}(\vb{x}_i)}_{\text{repulsive for $\lambda < 1$}}
+    + \underbrace{(1-\lambda)\vhf(\vb{x}_i)}_{\text{repulsive for $\lambda < 1$}}
     + \underbrace{\lambda\sum_{i<j}^{\Ne}\frac{1}{|\vb{r}_i-\vb{r}_j|}}_{\text{attractive for $\lambda < 0$}}
@@
 \end{multline}
-The mean-field potential $v^{\text{HF}}$ essentially represents a negatively charged field with the spatial extent
+The mean-field potential $\vhf$ essentially represents a negatively charged field with the spatial extent
 controlled by the extent of the HF orbitals, usually located close to the nuclei.
@@
 The divergence of class B systems, which contain closely spaced electrons (\eg, \ce{F-}), can then be understood as the 
-HF potential $v^{\text{HF}}$ is relatively localised and the autoionization is favoured at negative 
+HF potential $\vhf$ is relatively localised and the autoionization is favoured at negative 
 $\lambda$ values closer to the origin.
@@
 The reference Slater determinant for a doubly-occupied atom can be represented using RHF
-orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\theta_{\alpha}^{\text{RHF}} = \theta_{\beta}^{\text{RHF}} = 0$, 
+orbitals [see Eq.~\eqref{eq:RHF_orbs}] with $\ta_{\text{RHF}} = \tb_{\text{RHF}} = 0$, 
 which corresponds to strictly localising the two electrons on the left site.
@@
 It is frequently stated that
-\textit{``the most stupid thing that one can do with a series is to sum it.''}
+\textit{``the most stupid thing \hugh{to} \trashHB{that one can} do with a series is to sum it.''}
 Nonetheless, quantum chemists are basically doing this on a daily basis.
@@
 The failure of a Taylor series for correctly modelling the MP energy function $E(\lambda)$ 
-arises because one is trying to model a complicated function containing multiple branches, branch points and
+arises because one is trying to model a complicated function containing multiple branches, branch points, and
 singularities using a simple polynomial of finite order.
@@
 However, they are unable to model functions with square-root branch points 
-(which are ubiquitous in the singularity structure of a typical perturbative treatment) 
+(which are ubiquitous in the singularity structure of \trashHB{a typical} perturbative \hugh{methods} \trashHB{treatment}) 
 and more complicated functional forms appearing at critical points 
@@
 
-For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximant 
+For the RMP series of the Hubbard dimer, the $[0/0,0]$ and $[1/0,0]$ quadratic approximants 
 are quite poor approximations, but the $[1/0,1]$ version perfectly models the RMP energy
@@
 Finally, to emphasise the improvement that can be gained by using either Pad\'e, diagonal quadratic,
-or pole-free quadratic approximants, we consider the energy and error obtained using only the first 10 terms of the UMP
+or pole-free quadratic approximants, we collect the energy and error obtained using only the first 10 terms of the UMP
 Taylor series in Table~\ref{tab:UMP_order10}.
@@
 %==========================================%
-\subsection{Analytic continuation}
+\subsection{Analytic Continuation}
 %==========================================%
@@
 \end{equation}
-which states that the value of the energy can be computed at $\lambda_1$ inside the complex 
+which states that the value of the energy can be computed at $\lambda$ inside the complex 
 contour $\mathcal{C}$ using only the values along the same contour.
@@
 around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller--Plesset theory. 
-Seminal contributions from various research groups around the world have revealed highly oscillatory,
+Seminal contributions from various research groups \trashHB{around the world} have revealed highly oscillatory,
 slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%

### 2020-12-06 Manuscript/EPAWTFT.tex
remove easy corrections

@@
 We explore the non-Hermitian extension of quantum chemistry in the complex plane and its link with perturbation theory.
-We observe that the physics of a quantum system is intimately connected to the position of \hugh{complex-valued} energy singularities
-\trashHB{in the complex plane}, known as exceptional points.
+We observe that the physics of a quantum system is intimately connected to the position of complex-valued energy singularities, known as exceptional points.
 After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
@@
 We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) that can improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
-Each of these points is \trashHB{pedagogically} illustrated using the Hubbard dimer at half filling, which proves to be a versatile model for understanding the subtlety of analytically-continued perturbation theory in the complex plane.
+Each of these points is illustrated using the Hubbard dimer at half filling, which proves to be a versatile model for understanding the subtlety of analytically-continued perturbation theory in the complex plane.
 \end{abstract}
@@
 \maketitle
-%\raggedbottom
-%\tableofcontents
 
@@
 Our conventional view of electronic structure theory is centred around the Hermitian notion of quantised energy levels,
-where the different electronic states of a \hugh{molecule} are discrete and energetically ordered.
+where the different electronic states of a molecule are discrete and energetically ordered.
 The lowest energy state defines the ground electronic state, while higher energy states
@@
 When the domain of $\lambda$ is extended to the complex plane, EPs can also occur in the MP energy.
-Although these EPs \hugh{are generally complex-valued} \trashHB{exist in the complex plane}, 
+Although these EPs are generally complex-valued, 
 their positions are intimately related to the 
@@
 	\includegraphics[height=0.65\textwidth]{fig1a}
-	\subcaption{\titou{Real axis} \label{subfig:FCI_real}}
+	\subcaption{Real axis \label{subfig:FCI_real}}
     \end{subfigure}
@@
 	\includegraphics[height=0.65\textwidth]{fig1b}
-	\subcaption{\titou{Complex plane} \label{subfig:FCI_cplx}}
+	\subcaption{Complex plane \label{subfig:FCI_cplx}}
     \end{subfigure}
@@
 To illustrate the formation of an EP, we scale the off-diagonal coupling strength by introducing the complex parameter $\lambda$ through the transformation $t \to \lambda t$ to give the parameterised Hamiltonian $\hH(\lambda)$.
-When $\lambda$ is real, the Hamiltonian \trashHB{\eqref{eq:H_FCI}} is Hermitian with the distinct (real-valued) (eigen)energies
+When $\lambda$ is real, the Hamiltonian is Hermitian with the distinct (real-valued) (eigen)energies
 \begin{subequations}
@@
 From complex analysis, \cite{BenderBook} the radius of convergence for the energy can be obtained by looking for the 
-\hugh{non-analytic} singularities of $E(\lambda)$ in the complex $\lambda$ plane.
+non-analytic singularities of $E(\lambda)$ in the complex $\lambda$ plane.
 This property arises from the following theorem: \cite{Goodson_2011}
@@
 % SUMMARY OF HF
-In the \trash{Hartree--Fock (HF)} \titou{HF} approximation, the many-electron wave function is approximated as a single Slater determinant $\whf(\vb{x}_1,\ldots,\vb{x}_\Ne)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
+In the HF approximation, the many-electron wave function is approximated as a single Slater determinant $\whf(\vb{x}_1,\ldots,\vb{x}_\Ne)$, where $\vb{x} = (\sigma,\vb{r})$ is a composite vector gathering spin and spatial coordinates.
 This Slater determinant is defined as an antisymmetric combination of $\Ne$ (real-valued) occupied one-electron spin-orbitals $\phi_p(\vb{x})$, which are, by definition, eigenfunctions of the one-electron Fock operator
@@
 and contain a mixture of spin-up and spin-down components.\cite{Mayer_1993,Jimenez-Hoyos_2011}
-However, the application of HF \titou{theory} with some level of constraint on the orbital structure is far more common.
+However, the application of HF theory with some level of constraint on the orbital structure is far more common.
 Forcing the spatial part of the orbitals to be the same for spin-up and spin-down electrons leads to restricted HF (RHF) method, 
@@
 such as antiferromagnetic phases\cite{Slater_1951} or the dissociation of the hydrogen dimer.\cite{Coulson_1949}
-However, by allowing different orbitals for different spins, the UHF \hugh{wave function} is no longer required to be an eigenfunction of 
+However, by allowing different orbitals for different spins, the UHF wave function is no longer required to be an eigenfunction of 
 the total spin operator $\hat{\mathcal{S}}^2$, leading to ``spin-contamination''.
@@
 role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.
-\hugh{Furthermore, the complex-scaled Fock operator can be used routinely construct analytic
+Furthermore, the complex-scaled Fock operator can be used routinely \titou{to} construct analytic
 continuations of HF solutions beyond the points where real HF solutions
-coalesce and vanish.\cite{Burton_2019b}}
+coalesce and vanish.\cite{Burton_2019b}
 
@@
 \begin{equation}\label{eq:EMP2}
-    \hugh{E_{\text{MP}}^{(2)}} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
+    E_{\text{MP}}^{(2)} = \frac{1}{4} \sum_{ij} \sum_{ab} \frac{\abs{\mel{ij}{}{ab}}^2}{\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b},
 \end{equation}
@@
 Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
-increasingly small at larger bond lengths, leading to a divergence, for example, in the \trash{second-order MP} \titou{MP2} correction \eqref{eq:EMP2}.
+increasingly small at larger bond lengths, leading to a divergence, for example, in the MP2 correction \eqref{eq:EMP2}.
 In contrast, the origin of slow UMP convergence is less obvious as the reference UHF energy remains
@@
 by Gill \etal\ using the minimal basis \ce{H2} model.\cite{Gill_1988}
-In this work, the authors %compared titou{the UMP series with the exact RHF- and UHF-based FCI expansions (T2: I don't understand this)} and
+In this work, the authors 
 identified that the slow UMP convergence arises from its failure to correctly predict the amplitude of the
@@
 The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each 
-\hugh{perturbation} order in Fig.~\ref{subfig:RMP_cvg}.
+perturbation order in Fig.~\ref{subfig:RMP_cvg}.
 In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
@@
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
-For example, while the RMP energy shows only one EP between the ground \trashHB{state} and 
-\trashHB{the} doubly-excited states (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
+For example, while the RMP energy shows only one EP between the ground and 
+doubly-excited states (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
 singly-excited open-shell singlet, and the other connecting this single excitation to the 
@@
 Cremer and He introduced an efficient MP6 approach and used it to analyse the RMP convergence of
-29 atomic and molecular systems \trashHB{with respect to the FCI energy}.\cite{Cremer_1996}
+29 atomic and molecular systems.\cite{Cremer_1996}
 They established two general classes: ``class A'' systems that exhibit monotonic convergence; 
@@
 Finally, Ref.~\onlinecite{Olsen_1996} proved that the extrapolation formulas of Cremer and He \cite{Cremer_1996} 
-\titou{[see Eqs.~\eqref{eq:CrHeA} and \eqref{eq:CrHeB}]} are not mathematically motivated when considering the complex 
+[see Eqs.~\eqref{eq:CrHeA} and \eqref{eq:CrHeB}] are not mathematically motivated when considering the complex 
 singularities causing the divergence, and therefore cannot be applied for all systems.
@@
 It is frequently stated that
-\textit{``the most stupid thing \hugh{to} \trashHB{that one can} do with a series is to sum it.''}
+\textit{``the most stupid thing to do with a series is to sum it.''}
 Nonetheless, quantum chemists are basically doing this on a daily basis.
@@
 However, they are unable to model functions with square-root branch points 
-(which are ubiquitous in the singularity structure of \trashHB{a typical} perturbative \hugh{methods} \trashHB{treatment}) 
+(which are ubiquitous in the singularity structure of perturbative methods) 
 and more complicated functional forms appearing at critical points 
@@
 a total of two branches.
-%\titou{Since every branch points must therefore correspond to a degeneracy of the same two branches,} 
-This constraint
-can hamper the faithful description of more complicated singularity structures such as the MP energy surface.
+This constraint can hamper the faithful description of more complicated singularity structures such as the MP energy surface.
 Despite this limitation, Ref.~\onlinecite{Goodson_2000a} demonstrates that quadratic approximants 
@@
 around the physics of complex singularities in perturbation theory, with a particular focus on M{\o}ller--Plesset theory. 
-Seminal contributions from various research groups \trashHB{around the world} have revealed highly oscillatory,
+Seminal contributions from various research groups have revealed highly oscillatory,
 slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%
@@
 ensemble DFT, \cite{Deur_2017,Deur_2018,Senjean_2018,Sagredo_2018,Fromager_2020} thermal DFT,\cite{Smith_2016,Smith_2018} 
-\titou{wave function methods},\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
+wave function methods,\cite{Stein_2014,Henderson_2015,Shepherd_2016} and many more.
 In particular, we have shown that the Hubbard dimer contains sufficient flexibility to describe 

### 2020-12-07 Manuscript/EPAWTFT.tex
for hugh

@@
 After presenting the fundamental concepts of non-Hermitian quantum chemistry in the complex plane, including the mean-field Hartree--Fock approximation and Rayleigh--Schr\"odinger perturbation theory, we provide a historical overview of the various research activities that have been performed on the physics of singularities.
-In particular, we highlight the seminal work \trashHB{of several research groups} on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
+In particular, we highlight seminal work on the convergence behaviour of perturbative series obtained within M{\o}ller--Plesset perturbation theory, and its links with quantum phase transitions.
 We also discuss several resummation techniques (such as Pad\'e and quadratic approximants) that can improve the overall accuracy of the M{\o}ller--Plesset perturbative series in both convergent and divergent cases.
@@
 Normally it is applied using real numbers as one of very few available tools for 
-describing realistic quantum systems \trashHB{where exact solutions of the Schr\"odinger equation are impossible \titou{to find?}}.\cite{Dirac_1929}
+describing realistic quantum systems.
 In particular, time-independent Rayleigh--Schr\"odinger perturbation theory\cite{RayleighBook,Schrodinger_1926} 
@@
 \end{subequations}
-solving the corresponding perturbation equations up to a given order \titou{$n$}, and
+solving the corresponding perturbation equations up to a given order $n$, and
 setting $\lambda = 1$ then yields approximate solutions to Eq.~\eqref{eq:SchrEq}.
@@
 $\lambda$ plane where two states become degenerate.
-Later we will demonstrate how the choice of reference \hugh{wave function} \trashHB{Hamiltonian} controls the position of these EPs, and 
+Later we will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
 ultimately determines the convergence properties of the perturbation series.
@@
 \end{equation}
-Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped \titou{pair?}, obtained 
+Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped counterpart, obtained 
 by swapping $\ta_{\text{UHF}}$ and $\tb_{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
@@
 role of \textit{quasi}-EPs in determining the behaviour of the HF approximation.
-Furthermore, the complex-scaled Fock operator can be used routinely \titou{to} construct analytic
+Furthermore, the complex-scaled Fock operator can be used routinely to construct analytic
 continuations of HF solutions beyond the points where real HF solutions
@@
 by the vertical cylinder of unit radius.
-For the divergent case, the $\lep$ \antoine{(\sout{the} $\lep$)} lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
+For the divergent case, $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
 outside this cylinder.
@@
 	Radius of convergence $r_c$ for the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) 
-    series \titou{of the Hubbard dimer} as functions of the ratio $U/t$.
+    series of the Hubbard dimer as functions of the ratio $U/t$.
 	\label{fig:RadConv}}
@@
 For example, while the RMP energy shows only one EP between the ground and 
-doubly-excited states (Fig.~\ref{fig:RMP}), the UMP energy has two (\antoine{pairs of}) EPs: one connecting the ground state with the
+doubly-excited states (Fig.~\ref{fig:RMP}), the UMP energy has two pairs of complex-conjugate EPs: one connecting the ground state with the
 singly-excited open-shell singlet, and the other connecting this single excitation to the 
@@
 with little contribution from triple excitations.
-On the other hand, triple excitations have an important contribution in class B systems, including providing
-orbital relaxation \titou{to doubly-excited states}, and these contributions lead to oscillations of the total correlation energy.
+On the other hand, triple excitations have an important contribution in class B systems, including
+orbital relaxation to doubly-excited configurations, and these contributions lead to oscillations of the total correlation energy.
 
@@
 including the interspersed zigzag, triadic, ripple, geometric, and zigzag-geometric forms.
-This analysis highlights the importance of the primary critical point in controlling the high-order convergence, 
+This analysis highlights the importance of the primary singularity in controlling the high-order convergence, 
 regardless of whether this point is inside or outside the complex unit circle. \cite{Handy_1985,Olsen_2000}
@@
 allows the formation of the critical point as the electrons form a bound cluster occupying the ghost atom orbitals.\cite{Sergeev_2005}
-This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to \titou{the} hydrogen at
+This effect explains the origin of the divergence in the \ce{HF} molecule as the fluorine valence electrons jump to the hydrogen at
  a sufficiently negative $\lambda$ value.\cite{Sergeev_2005}
@@
 Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
-The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
+\hugh{The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}}
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
@@
     \caption{\label{fig:PadeRMP}
-    RMP ground-state energy as a function of $\lambda$ \titou{in the Hubbard dimer} obtained using various \titou{truncated Taylor series and approximants} 
+    RMP ground-state energy as a function of $\lambda$ in the Hubbard dimer obtained using various truncated Taylor series and approximants
     at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
@@
 \begin{table}[b]
-	\caption{RMP ground-state energy estimate at $\lambda = 1$ \titou{of the Hubbard dimer} provided by various truncated Taylor 
+	\caption{RMP ground-state energy estimate at $\lambda = 1$ of the Hubbard dimer provided by various truncated Taylor 
     series and Pad\'e approximants at $U/t = 3.5$ and $4.5$.
@@
     \caption{\label{fig:QuadUMP}
-    UMP energies \titou{in the Hubbard dimer} as a function of $\lambda$ obtained using various \titou{approximants} at $U/t = 3$.}
+    UMP energies in the Hubbard dimer as a function of $\lambda$ obtained using various approximants at $U/t = 3$.}
 \end{figure}
@@
 	\label{eq:QuadApp}
-	\titou{E_{[d_P/d_Q,d_R]}}(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ],
+	E_{[d_P/d_Q,d_R]}(\lambda) = \frac{1}{2 Q(\lambda)} \qty[ P(\lambda) \pm \sqrt{P^2(\lambda) - 4 Q(\lambda) R(\lambda)} ],
 \end{equation}
@@
     \caption{Estimate for the distance of the closest singularity (pole or branch point) to the origin $\abs{\lc}$
-    in the UMP energy function \titou{of the Hubbard dimer} provided by various \titou{truncated Taylor series and approximants} at $U/t = 3$ and $7$.
+    in the UMP energy function of the Hubbard dimer provided by various truncated Taylor series and approximants at $U/t = 3$ and $7$.
 	The truncation degree of the Taylor expansion $n$ of $E(\lambda)$ and the number of branch 
@@
 Comparison of the [3/2,2] and [3/0,4] quadratic approximants with the exact UMP energy surface in the complex $\lambda$ 
-plane \titou{in the Hubbard dimer} with $U/t = 3$. 
+plane in the Hubbard dimer with $U/t = 3$. 
 Both quadratic approximants correspond to the same truncation degree of the Taylor series and model the branch points 
@@
 	\caption{
-    Estimate and associated error of the exact UMP energy \titou{of the Hubbard dimer} at $U/t = 7$ for 
+    Estimate and associated error of the exact UMP energy of the Hubbard dimer at $U/t = 7$ for 
     various approximants using up to ten terms in the Taylor expansion.
@@
     Acceleration of the diagonal Pad\'e approximant sequence for the RMP energy
-    \titou{of the Hubbard dimer at $U/t = 3.5$ and $4.5$} using the Shanks transformation.
+    of the Hubbard dimer at $U/t = 3.5$ and $4.5$ using the Shanks transformation.
 	\label{tab:RMP_shank}}
@@
         Comparison of the scaled RMP10 Taylor expansion with the exact RMP energy as a function
-        of $\lambda$ for the \trash{symmetric} Hubbard dimer at $U/t = 4.5$. 
+        of $\lambda$ for the Hubbard dimer at $U/t = 4.5$. 
         The two functions correspond closely within the radius of convergence.
-        \titou{T2: are we keeping this?}
     }
@@
 The authors illustrate this protocol for the dissociation curve of \ce{LiH} and the stretched water 
-molecule \trash{to obtain} \titou{and obtained?} encouragingly accurate results.\cite{Mihalka_2019}
+molecule and obtained encouragingly accurate results.\cite{Mihalka_2019}
 

### 2020-12-07 Manuscript/EPAWTFT.tex
Altered fig1b. Added comment about EPs converging on real axis.

@@
 	Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
-    Only the interacting closed-shell singlets are plotted in the complex plane, becoming degenerate at the EP (black dot).
-    The contour followed around the EP in order to interchange states is also represented.
+    Only the interacting closed-shell singlets are shown in the complex plane, becoming degenerate at the EP (black dot).
+    Following a contour around the EP (black solid) interchanges the states, while a second rotation (black dashed)
+    returns the states to their original energies.
 	\label{fig:FCI}}
@@
 The ``shape'' of this avoided crossing is related to the magnitude of $\Im(\lambda_{\text{EP}})$, with smaller values giving a ``sharper'' interaction.
+\hugh{In the limit $U/t \to 0$, the two EPs converge at $\lep \to 0$ to create a conical intersection with 
+a gradient discontinuity on the real axis.}
 
@@
 \cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook} 
-Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis, eventually forming a critical point.
-\hugh{The existence of an EP \emph{on} the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}}
+Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis.
+\hugh{When these points converge on the real axis, they effectively ``annihilate'' each other and no longer behave as EPs.
+Instead, they form a ``critical point'' singularity that resembles a conical intersection, and 
+the convergence of a pair of complex-conjugate EPs on the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}}
+
 Since the MP critical point corresponds to a singularity on the real $\lambda$ axis, it can immediately be
@@
 basis set limit.\cite{Kais_2006}
-The MP critical point and corresponding $\beta$ singularities in a finite basis must therefore be modelled by pairs of EPs
-that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
+The MP critical point and corresponding $\beta$ singularities in a finite basis must therefore be modelled by pairs of
+complex-conjugate EPs that tend towards the real axis, exactly as described by Sergeev \etal\cite{Sergeev_2005}
 In contrast, $\alpha$ singularities correspond to large avoided crossings that are indicative of low-lying excited
 states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
+\hugh{Notably, since the exact MP critical point corresponds to the interaction between a bound state
+and the continuum, its functional form is more complicated than a conical intersection and remains an open question.}
 

### 2020-12-07 Manuscript/EPAWTFT.tex
review Hugh last changes and crushed a few typos

@@
 \author{Hugh G.~A.~\surname{Burton}}
-\email{hugh.burton@chem.ox.ac.uk}
+\email[Corresponding author: ]{hugh.burton@chem.ox.ac.uk}
 \affiliation{\UOX}
 \author{Pierre-Fran\c{c}ois \surname{Loos}}
-\email{loos@irsamc.ups-tlse.fr}
+\email[Corresponding author: ]{loos@irsamc.ups-tlse.fr}
 \affiliation{\LCPQ}
@@
 % Moller-Plesset
-In electronic structure theory, the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) %perturbation 
+In electronic structure theory, the workhorse of time-independent perturbation theory is M\o{}ller--Plesset (MP) 
 theory,\cite{Moller_1934} which remains one of the most popular methods for computing the electron 
@@
 The ``shape'' of this avoided crossing is related to the magnitude of $\Im(\lambda_{\text{EP}})$, with smaller values giving a ``sharper'' interaction.
-\hugh{In the limit $U/t \to 0$, the two EPs converge at $\lep \to 0$ to create a conical intersection with 
-a gradient discontinuity on the real axis.}
+In the limit $U/t \to 0$, the two EPs converge at $\lep = 0$ to create a conical intersection with 
+a gradient discontinuity on the real axis.
 
@@
 \end{equation}
-where we have introduced bonding $\mathcal{B}^{\sigma}$ and anti-bonding $\mathcal{A}^{\sigma}$ molecular orbitals for 
+where we have introduced bonding $\mathcal{B}^{\sigma}$ and antibonding $\mathcal{A}^{\sigma}$ molecular orbitals for 
 the spin-$\sigma$ electrons as
@@
 
-%============================================================%
-\subsection{Self-Consistency as a Perturbation} %OR {Complex adiabatic connection}
-%============================================================%
+%===============================================%
+\subsection{Self-Consistency as a Perturbation} 
+%===============================================%
 
@@
 RHF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
-Secondly, the energy gap between the bonding and antibonding orbitals associated with the stretch becomes
+Secondly, the energy gap between the bonding and anti-bonding orbitals associated with the stretch becomes
 increasingly small at larger bond lengths, leading to a divergence, for example, in the MP2 correction \eqref{eq:EMP2}.
@@
 %==========================================%
-\subsection{Classifying Types of Convergence} % Behaviour} % Further insights from a two-state model}
+\subsection{Classifying Types of Convergence} 
 %==========================================%
@@
 to dissociate and form a bound cluster at an infinite separation from the nuclei.\cite{Stillinger_2000}
-This autoionisation effect is closely related to the critial point for electron binding in two-electron 
+This autoionisation effect is closely related to the critical point for electron binding in two-electron 
 atoms (see Ref.~\onlinecite{Baker_1971}).
@@
 Meanwhile, as an avoided crossing becomes increasingly sharp, the corresponding EPs move increasingly close to the real axis.
-\hugh{When these points converge on the real axis, they effectively ``annihilate'' each other and no longer behave as EPs.
+When these points converge on the real axis, they effectively ``annihilate'' each other and no longer behave as EPs.
 Instead, they form a ``critical point'' singularity that resembles a conical intersection, and 
-the convergence of a pair of complex-conjugate EPs on the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}}
+the convergence of a pair of complex-conjugate EPs on the real axis is therefore diagnostic of a QPT.\cite{Cejnar_2005, Cejnar_2007a}
 
@@
 states which share the symmetry of the ground state,\cite{Goodson_2004} and are thus not manifestations of a QPT.
-\hugh{Notably, since the exact MP critical point corresponds to the interaction between a bound state
-and the continuum, its functional form is more complicated than a conical intersection and remains an open question.}
+Notably, since the exact MP critical point corresponds to the interaction between a bound state
+and the continuum, its functional form is more complicated than a conical intersection and remains an open question.
 
@@
 % INTRODUCING THE MODEL
-The simplified site basis of the Hubbard dimer makes explicilty modelling the ionisation continuum impossible.
+The simplified site basis of the Hubbard dimer makes explicitly modelling the ionisation continuum impossible.
 Instead, we can use an asymmetric version of the Hubbard dimer \cite{Carrascal_2015,Carrascal_2018} 
@@
 
-While the diagonal quadratic approximants provide significanty improved estimates of the 
+While the diagonal quadratic approximants provide significantly improved estimates of the 
 ground-state energy, we can use our knowledge of the UMP singularity structure to develop
@@
 collection of theoretical methods.
-Until the Sch\"odinger equation is solved exactly, this choice must make a compromise on the accuracy
+Until the Schr\"odinger equation is solved exactly, this choice must make a compromise on the accuracy
 of certain properties depending on the system that is being studied.

### 2021-01-28 Response_Letter/Response_Letter.tex
response letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,mathpazo,ragged2e,hyperref}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of the \textit{Journal of Physics: Condensed Matter}}

\opening{Dear Editors,}

\justifying
Please find attached a revised version of the manuscript entitled 
\begin{quote}
	\textit{``Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them''}.
\end{quote}
We thank the reviewers for their constructive comments.
Our detailed responses to their comments can be found below.
For convenience, changes are highlighted in red in the revised version of the manuscript.

We look forward to hearing from you.

\closing{Sincerely, the authors.}

%%% REVIEWER 1 %%%
\noindent \textbf{\large Authors' answer to Reviewer \#1}

\begin{itemize}

	\item 
	{In this manuscript, the authors provide a comprehensive and thorough discussion of the role of exceptional point singularities in determining the performance of perturbation methods of electronic structure theory. The main subject  considered is the well-known Moller-Plesset (MP) theory to calculate the electronic correlation energy, and various resummation techniques aimed to improve the convergence of the MP series. The system used to illustrate the application of MP theory is the Hubbard dimer. The authors suggest how the combination of resummation methods and acceleration techniques, such as the Shanks transformation, can significantly improve the accuracy of pertubative approaches. The manuscript is well written and has the format of a very useful and informative review of the progress done in the field. For that reason, I was worried that it could not fit the audience of the Journal of Physics Condensed Matter journal, and it might be better placed in a different journal, focusing on reviews. Besides that point, I found some merit in the application of the Shanks transformation to different approximants for both the restricted and unrestricted versions of the theory, which focus on the corresponding set of orbitals. Thus, I am glad to recommend publication.}
	\\
	\alert{bla bla bla}

\end{itemize}

%%% REVIEWER 2 %%%
\noindent \textbf{\large Authors' answer to Reviewer \#2}

\begin{itemize}

	\item 
	{The topical review "Perturbation theory in the complex plane: Exceptional points and where to find them" reviews the origin and meaning of exceptional points in quantum chemistry. The Hubbard dimer is used throughout as an illustrative example for the restricted and unrestricted cases, exact solution (FCI), Hartree-Fock, and Rayleigh-Schrodinger perturbation theory. The authors review the ways that MP series in common quantum chemical applications can behave, using the classification schemes developed in the literature. Finally, they discuss alternative methods to approximate the Taylor series of RS theory by other functions which may have better, faster, or otherwise more robust convergence properties, including their own calculations based on the Shanks transformation.

This topical review is very well done and I recommend it for publication as is. I list my comments below for the authors to address if they choose. Because this manuscript is meant as a review and to have instructional value, my comments are a bit more pedagogical or curiousity driven than may be expected for a normal review. I am not an expert in this exact area, so my questions are meant to represent those a typical reader might have. My questions do not need to all be addressed before the manuscript is published.}
	\\
	\alert{bla bla bla}

\item 
{I
How am I to actually interpret the electronic energy E of such a non-Hermitian Hamiltonian? Is the energy associated with just the real part of the Riemann surface $E(\lambda)$ at every point, is it computable from some combination of Re and Im parts, or is the ordinary meaning of the energy lost completely? Is there a lifetime interpretation for the imaginary part of this non-Hermitian Hamiltonian in the wave function problem as in Green's function theory? Maybe something can be said about this because I suspect the imaginary part is somehow related to losses. This is hinted at in the introduction but was the first question that entered my mind.}
	\\
	\alert{bla bla bla}

\item 
{IIe
Could the authors make it very clear what is meant here by ``symmetry broken"? This term is seen and used very frequently but can be kind of ambiguous and rarely explained completely. What is the symmetry that is broken? Also, what exactly is meant by ``symmetry-pure" when referring to the molecular orbitals? This refers to equal composition of left and right sites, but maybe this can be said explicitly. A useful counterexample would be a mixing angle of zero, in which case the orbitals are either definitely left or definitely right.}
	\\
	\alert{bla bla bla}

\item 
{I personally can get confused because both spatial and spin symmetries are in play (or so I think). At high U/t, left and right sites are both open shell with one electron each. Am I to think of this as a broken spatial symmetry, broken spin symmetry, or both?}
	\\
	\alert{bla bla bla}

\item 
{It could be emphasized that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases, which is why these equations lack an RHF or UHF subscript. Also, in the general case (either RHF or UHF), the bonding orbitals for the two sigma values are occupied and the two antibonding orbitals are unoccupied. Bonding and antibonding notation is not so common in the condensed matter literature and it may be missed that these correspond to occupied and empty single-particle states.}
	\\
	\alert{bla bla bla}

\item 
{IIf
What am I to think of values of $\lambda$ where $|\lambda|>1$? I guess this is mathematically well defined and useful for understanding $r_c$, but the physical system always corresponds to $|\lambda|=1$, even in the complex case. I suppose one needs to understand the singularities at other values of $\lambda$ in order to know the convergence of the series at the value we want, $\lambda = 1$. Some discussion could already be made that these values are not necessarily physical but determine the behavior of the physical series. Certain values away from $\lambda=1$ can also have physical meaning, like the autoionization process discussed later.}
	\\
	\alert{bla bla bla}

\item 
{IIIc
To be extra careful, should it be said that the RMP series is either convergent or divergent at the physical coupling value $|\lambda|=1$? I guess for either value of U, the series is convergent if you are close enough to the origin.}

The language describing the cylinder with unit radius could be improved from: "the radius of convergence indicated by the vertical cylinder of unit radius" I first thought the cylinder was marking the radius of convergence. It is meant to show the position of the EPs and indicate if the radius of convergence is $>1$ or $<1$. The language could be improved.
	\\
	\alert{bla bla bla}

IIId
\item 
{The classification of front-door and back-door intruder states is not totally clear. I raise this point because the journal is JPCM, and these terms are not common in condensed matter literature. Are intruder states equivalent to states creating exceptional points that ruin the series convergence?}
	\\
	\alert{bla bla bla}

\item 
{IIIe
Has "critical point" been defined yet?}
	\\
	\alert{bla bla bla}

\item 
{IIIf
The explanation of the critical point as the occurrence of the autoionization process is great and makes sense to me. I must say, though, I have trouble visualizing this in Figs. 7 and 8. I can trace any one curve continuously along the $\lambda$ axis, and even their ordering does not change. How does the critical point appear in these figures? Presumably, it is because the curves exactly intersect at the CP, but this does not on the surface appear so different than the avoided crossings related to the EPs discussed in earlier sections.

So what exactly in these figures indicates the suddent and abrupt change in the eigenstates that makes it a CP? Is it the derivative discontinuity in the energy on the real $\lambda$ axis, whereas the derivative on the real axis for an avoided crossing due to an exceptional point is continuous? Can this gradient discontinuity be used to define the CP? How do I see something like the autoionization in this figure? If this is correct, it could be emphasized a bit more by a comment referring specifically to that figure.

Is it possible to circle the CP as one does for an EP? Is there any meaning to this?}
	\\
	\alert{bla bla bla}

\item 
{IV
Can something more be said about how these methods are fitted (briefly, and in a general way)? For example, how does one fit the Pade coefficients? Presumably, the exact function is known to some order and/or inside of some radius of convergence. The approximant is fitted in this region to match the exact function and then only the approximant is used beyond the original radius of convergence or at higher order.}
	\\
	\alert{bla bla bla}

\item 
{Throughout the manuscript, the figures are excellent and really help the understanding. The authors have clearly taken time to prepare the manuscript and it can be published immediately.}
	\\
	\alert{bla bla bla}

\end{itemize}

\end{letter}
\end{document}

### 2021-01-29 Response_Letter/Response_Letter.tex
starting working on response letter

@@
 	The system used to illustrate the application of MP theory is the Hubbard dimer. 
-The authors suggest how the combination of resummation methods and acceleration techniques, such as the Shanks transformation, can significantly improve the accuracy of pertubative approaches.
+	The authors suggest how the combination of resummation methods and acceleration techniques, such as the Shanks transformation, can significantly improve the accuracy of perturbative approaches. 
 	The manuscript is well written and has the format of a very useful and informative review of the progress done in the field. 
@@
 	\\
-	\alert{bla bla bla}
+	\alert{We thank Reviewer \#1 for recommending publication of the present review.}
 
@@
 	I list my comments below for the authors to address if they choose. 
-Because this manuscript is meant as a review and to have instructional value, my comments are a bit more pedagogical or curiousity driven than may be expected for a normal review.
+	Because this manuscript is meant as a review and to have instructional value, my comments are a bit more pedagogical or curiosity driven than may be expected for a normal review. 
 	I am not an expert in this exact area, so my questions are meant to represent those a typical reader might have. 
@@
 	\\
-	\alert{bla bla bla}
+	\alert{Again, we thank Reviewer \#2 for recommending publication and for his/her constructive comments.
+	Below, we address these comments.}
 
 \item 
-{I
-How am I to actually interpret the electronic energy E of such a non-Hermitian Hamiltonian?
+	{I.\\
+	How am I to actually interpret the electronic energy $E$ of such a non-Hermitian Hamiltonian? 
 	Is the energy associated with just the real part of the Riemann surface $E(\lambda)$ at every point, is it computable from some combination of Re and Im parts, or is the ordinary meaning of the energy lost completely?
@@
 	\\
-	\alert{bla bla bla}
+	\alert{In most figures, we indeed plot the real component of the energy.
+	By going complex, the energies lost their meaning as there's no relation of order for complex numbers.
+	In non-Hermitian processes like resonances or scattering, the imaginary part of the energy is indeed linked to lifetimes [see the book of Moiseyev].
+	However, the meaning  of the imaginary part of the energy in the present context is unclear and we prefer not to speculate on this.}
 
 \item 
-{IIe
+	{IIe.\\
 	Could the authors make it very clear what is meant here by ``symmetry broken"? 
@@
 	What is the symmetry that is broken? 
-Also, what exactly is meant by ``symmetry-pure" when referring to the molecular orbitals?
-This refers to equal composition of left and right sites, but maybe this can be said explicitly.
-A useful counterexample would be a mixing angle of zero, in which case the orbitals are either definitely left or definitely right.}
-	\\
-	\alert{bla bla bla}
-
-\item 
-{I personally can get confused because both spatial and spin symmetries are in play (or so I think).
-At high U/t, left and right sites are both open shell with one electron each.
+	Also, what exactly is meant by ``symmetry-pure" when referring to the molecular orbitals? This refers to equal composition of left and right sites, but maybe this can be said explicitly. 
+	A useful counterexample would be a mixing angle of zero, in which case the orbitals are either definitely left or definitely right.
+	I personally can get confused because both spatial and spin symmetries are in play (or so I think). 
+	At high $U/t$, left and right sites are both open shell with one electron each. 
 	Am I to think of this as a broken spatial symmetry, broken spin symmetry, or both?}
@@
 \item 
-{It could be emphasized that Eqs.
-20, 21a, and 21b are valid for both the RHF and UHF cases, which is why these equations lack an RHF or UHF subscript.
+	{It could be emphasized that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases, which is why these equations lack an RHF or UHF subscript. 
 	Also, in the general case (either RHF or UHF), the bonding orbitals for the two sigma values are occupied and the two antibonding orbitals are unoccupied. 
@@
 	\\
-	\alert{bla bla bla}
+	\alert{We now mention that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases.
+	We have also changed the notations for the occupied and empty single-particle states.}
 
 \item 
-{IIf
+	{IIf.\\
 	What am I to think of values of $\lambda$ where $|\lambda|>1$? 
@@
 	\\
-	\alert{bla bla bla}
+	\alert{Only the $\lambda = 0$ (non-interacting system in some cases) and $\lambda = 1$ (fully interacting system) are physical systems  as mentioned in the manuscript.
+	However, it can be useful to study the systems at different $\lambda$ values.}
 
 \item 
-{IIIc
+	{IIIc.\\
 	To be extra careful, should it be said that the RMP series is either convergent or divergent at the physical coupling value $|\lambda|=1$? 
-I guess for either value of U, the series is convergent if you are close enough to the origin.}
+	I guess for either value of $U$, the series is convergent if you are close enough to the origin.
+	The language describing the cylinder with unit radius could be improved from: "the radius of convergence indicated by the vertical cylinder of unit radius".
+	I first thought the cylinder was marking the radius of convergence. It is meant to show the position of the EPs and indicate if the radius of convergence is $>1$ or $<1$. 
+	The language could be improved.}
+	\\
+	\alert{The language has been improved.}
 
-The language describing the cylinder with unit radius could be improved from: "the radius of convergence indicated by the vertical cylinder of unit radius" I first thought the cylinder was marking the radius of convergence.
-It is meant to show the position of the EPs and indicate if the radius of convergence is $>1$ or $<1$.
-The language could be improved.
-	\\
-	\alert{bla bla bla}
-
-IIId
 \item 
-{The classification of front-door and back-door intruder states is not totally clear.
+	{IIId.\\
+	The classification of front-door and back-door intruder states is not totally clear. 
 	I raise this point because the journal is JPCM, and these terms are not common in condensed matter literature. 
 	Are intruder states equivalent to states creating exceptional points that ruin the series convergence?}
+	\\
+	\alert{The classification of front-door and back-door intruder states have been clarified.}
+
+\item 
+	{IIIe.\\
+	Has "critical point" been defined yet?}
+	\\
+	\alert{Thank you for spotting this. 
+	"Critical point" is now defined in due place.}
+
+\item 
+	{IIIf
+	The explanation of the critical point as the occurrence of the autoionization process is great and makes sense to me. 
+	I must say, though, I have trouble visualizing this in Figs. 7 and 8. 
+	I can trace any one curve continuously along the $\lambda$ axis, and even their ordering does not change. 
+	How does the critical point appear in these figures? 
+	Presumably, it is because the curves exactly intersect at the CP, but this does not on the surface appear so different than the avoided crossings related to the EPs discussed in earlier sections.
+	So what exactly in these figures indicates the sudden and abrupt change in the eigenstates that makes it a CP? 
+	Is it the derivative discontinuity in the energy on the real $\lambda$ axis, whereas the derivative on the real axis for an avoided crossing due to an exceptional point is continuous? 
+	Can this gradient discontinuity be used to define the CP? 
+	How do I see something like the autoionization in this figure? 
+	If this is correct, it could be emphasized a bit more by a comment referring specifically to that figure.
+	Is it possible to circle the CP as one does for an EP? 
+	Is there any meaning to this?}
 	\\
@@
 \item 
-{IIIe
-Has "critical point" been defined yet?}
-	\\
-	\alert{bla bla bla}
-
-\item 
-{IIIf
-The explanation of the critical point as the occurrence of the autoionization process is great and makes sense to me.
-I must say, though, I have trouble visualizing this in Figs.
-7 and 8.
-I can trace any one curve continuously along the $\lambda$ axis, and even their ordering does not change.
-How does the critical point appear in these figures?
-Presumably, it is because the curves exactly intersect at the CP, but this does not on the surface appear so different than the avoided crossings related to the EPs discussed in earlier sections.
-
-So what exactly in these figures indicates the suddent and abrupt change in the eigenstates that makes it a CP?
-Is it the derivative discontinuity in the energy on the real $\lambda$ axis, whereas the derivative on the real axis for an avoided crossing due to an exceptional point is continuous?
-Can this gradient discontinuity be used to define the CP?
-How do I see something like the autoionization in this figure?
-If this is correct, it could be emphasized a bit more by a comment referring specifically to that figure.
-
-Is it possible to circle the CP as one does for an EP? Is there any meaning to this?}
-	\\
-	\alert{bla bla bla}
-
-\item 
-{IV
+	{IV.
 	Can something more be said about how these methods are fitted (briefly, and in a general way)? 
-For example, how does one fit the Pade coefficients?
+	For example, how does one fit the Pad\'e coefficients? 
 	Presumably, the exact function is known to some order and/or inside of some radius of convergence. 
@@
 	\\
-	\alert{bla bla bla}
+	\alert{As mentioned in the manuscript, the Pad\'e coefficients are determined by solving a set of linear equations involving the coefficients of the Taylor series.
+	This is the  only knowledge required to compute these.}
 
 \item 
-{Throughout the manuscript, the figures are excellent and really help the understanding. The authors have clearly taken time to prepare the manuscript and it can be published immediately.}
+	{Throughout the manuscript, the figures are excellent and really help the understanding. 
+	The authors have clearly taken time to prepare the manuscript and it can be published immediately.}
 	\\
-	\alert{bla bla bla}
+	\alert{Thank you for these kind comments.}
 

### 2021-01-29 Response_Letter/Response_Letter.tex
starting working on response letter

@@
 	\\
-	\alert{The classification of front-door and back-door intruder states have been clarified.}
+	\alert{The classification of front-door and back-door intruder states have been clarified.
+	"Following this theory, a singularity in the unit circle is designated as an intruder state, with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative)."}
 

### 2021-01-29 Manuscript/EPAWTFT.tex
starting working on response letter

@@
 order $n$ as MP$n$) can show erratic, slow, or divergent behaviour that limit its systematic improvability.%
-\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988} 
+\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988,Malrieu_2003} 
 As a result, practical applications typically employ only the lowest-order MP2 approach, while 
@@
 in a multi-valued function.
+\titou{T2: define here critical point.}
 
@@
 \begin{equation}
+\label{eq:EHF}
 E_\text{HF}(\ta, \tb) = -t\, \qty( \sin \ta + \sin \tb ) + \frac{U}{2} \qty( 1 + \cos \ta \cos \tb ),
 \end{equation}
-where we have introduced bonding $\mathcal{B}^{\sigma}$ and antibonding $\mathcal{A}^{\sigma}$ molecular orbitals for 
+where we have introduced \titou{occupied $\psi_1^{\sigma}$} and \titou{unoccupied $\psi_2^{\sigma}$} molecular orbitals for 
 the spin-$\sigma$ electrons as
@@
 \begin{align}
-    \mathcal{B}^{\sigma} & = \hphantom{-} \cos(\frac{\ts}{2}) \Lsi + \sin(\frac{\ts}{2}) \Rsi,
+	\label{eq:psi1}
+    \titou{\psi_1^{\sigma}} & = \hphantom{-} \cos(\frac{\ts}{2}) \Lsi + \sin(\frac{\ts}{2}) \Rsi,
 	\\
-	\mathcal{A}^{\sigma} & = - \sin(\frac{\ts}{2}) \Lsi + \cos(\frac{\ts}{2}) \Rsi
+	\label{eq:psi2}
+	\titou{\psi_2^{\sigma}} & = - \sin(\frac{\ts}{2}) \Lsi + \cos(\frac{\ts}{2}) \Rsi
 \end{align}
@@
 \end{subequations}
+\titou{Equations \eqref{eq:EHF}, \eqref{eq:psi1}, and \eqref{eq:psi2} are valid for both RHF and UHF.}
 In the weak correlation regime $0 \le U \le 2t$, the angles which minimise the HF energy, 
@@
 \begin{align}
-	\mathcal{B}_\text{RHF}^{\sigma} & = \frac{\Lsi + \Rsi}{\sqrt{2}},
+	\titou{\psi_{1,\text{RHF}}^{\sigma}} & = \frac{\Lsi + \Rsi}{\sqrt{2}},
 	&
-	\mathcal{A}_\text{RHF}^{\sigma} & = \frac{\Lsi - \Rsi}{\sqrt{2}},
+	\titou{\psi_{2,\text{RHF}}^{\sigma}} & = \frac{\Lsi - \Rsi}{\sqrt{2}},
 \end{align}
@@
 for example in multi-configurational systems, MP theory can yield highly oscillatory, 
-slowly convergent, or catastrophically divergent results.\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000}
+slowly convergent, or catastrophically divergent results.\cite{Gill_1986,Gill_1988,Handy_1985,Lepetit_1988,Leininger_2000,Malrieu_2003}
 Furthermore, the convergence properties of the MP series can depend strongly on the choice of restricted or
@@
 Although practically convenient for electronic structure calculations, the MP partitioning is not 
-the only possibility and alternative partitionings have been considered including: 
+the only possibility and alternative partitionings have been considered \cite{Surjan_2004} including: 
 i) the Epstein-Nesbet (EN) partitioning which consists in taking the diagonal elements of $\hH$ as the zeroth-order Hamiltonian, \cite{Nesbet_1955,Epstein_1926} 
@@
 \end{quote}
-Following this theory, a singularity in the unit circle is designated as an intruder state, 
-with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative).
+\titou{Following this theory, a singularity in the unit circle is designated as an intruder state, 
+with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative).}
 
@@
 The geometric archetype appears to be the most common for MP expansions,\cite{Olsen_2019} but the 
-ripples archetype corresponds to some of the early examples of MP convergence. \cite{Handy_1985,Lepetit_1988,Leininger_2000}
+ripples archetype corresponds to some of the early examples of MP convergence. \cite{Handy_1985,Lepetit_1988,Leininger_2000,Malrieu_2003}
 The three remaining Hermitian archetypes seem to be rarely observed in MP perturbation theory.
@@
 branch points and the convergence properties of Rayleigh--Schr\"odinger perturbation theory\cite{Mihalka_2017b} (see also
-Ref.~\onlinecite{Surjan_2000}).
+Refs.~\onlinecite{Szabados_1999,Surjan_2000,Szabados_2003}).
 Taking the equilibrium and stretched water structures as an example, they estimated the radius of convergence using quadratic
@@
 slowly convergent, or catastrophically divergent behaviour of the restricted and/or unrestricted MP perturbation series.%
-\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988} 
+\cite{Laidig_1985,Knowles_1985,Handy_1985,Gill_1986,Laidig_1987,Nobes_1987,Gill_1988,Gill_1988a,Lepetit_1988,Malrieu_2003} 
 In particular, the spin-symmetry-broken unrestricted MP series is notorious

### 2021-01-30 Response_Letter/Response_Letter.tex
quick revision and letter

--- 2021-01-29 Response_Letter/Response_Letter.tex
@@
 	\alert{In most figures, we indeed plot the real component of the energy.
-	By going complex, the energies lost their meaning as there's no relation of order for complex numbers.
+	By going complex, the energies lost their meaning as there is no relation of order for complex numbers.
 	In non-Hermitian processes like resonances or scattering, the imaginary part of the energy is indeed linked to lifetimes [see the book of Moiseyev].
-	However, the meaning  of the imaginary part of the energy in the present context is unclear and we prefer not to speculate on this.}
+	This is mention in the introduction section.
+	However, the meaning  of the imaginary part of the energy in the present context is unclear and we prefer not to speculate on this.
+	We have added a comment on this point in the revised version of the manuscript.}
 
@@
 	\\
-	\alert{We now mention that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases.
+	\alert{We now mention that Eqs. 20, 21a, and 21b are valid for both RHF and UHF.
 	We have also changed the notations for the occupied and empty single-particle states.}
@@
 	\alert{Only the $\lambda = 0$ (non-interacting system in some cases) and $\lambda = 1$ (fully interacting system) are physical systems  as mentioned in the manuscript.
-	However, it can be useful to study the systems at different $\lambda$ values.}
+	However, it can be useful to study the systems at different $\lambda$ values as we do in Sec.~II.F.}
 
@@
 	\\
-	\alert{The language has been improved.}
+	\alert{The language has been improved and we have mentioned in several places that we are talking about a convergent/divergent MP series at $\lambda = 1$.}
 
@@
 	\\
-	\alert{The classification of front-door and back-door intruder states have been clarified.}
+	\alert{We believe that the classification of front-door and back-door intruder states has been clearly defined in the original manuscript: 
+	"Following this theory, a singularity in the unit circle is designated as an intruder state, with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative)."}
 

### 2021-01-30 Manuscript/EPAWTFT.tex
quick revision and letter

@@
 same symmetry for complex values of $\lambda$.
+
+\titou{Although the complex component of the energy is linked to lifetime in non-Hermitian quantum mechanics, \cite{MoiseyevBook} its meaning is unclear to us in the present context.}
 
@@
 RHF wave function no longer provides a qualitatively correct reference for the perturbation expansion.
-Secondly, the energy gap between the bonding and anti-bonding orbitals associated with the stretch becomes
+Secondly, the energy gap between the \titou{occupied and unoccupied} orbitals associated with the stretch becomes
 increasingly small at larger bond lengths, leading to a divergence, for example, in the MP2 correction \eqref{eq:EMP2}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The RMP series is convergent for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each 
+The RMP series is convergent \titou{at $\lambda = 1$} for $U = 3.5\,t$ with $\rc > 1$, as illustrated for the individual terms at each 
 perturbation order in Fig.~\ref{subfig:RMP_cvg}.
-In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent.
+In contrast, for $U = 4.5t$ one finds $\rc < 1$, and the RMP series becomes divergent \titou{at $\lambda = 1$}.
 The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
-\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and the radius of convergence indicated
-by the vertical cylinder of unit radius.
+\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and \titou{the radius of convergence indicated
+by the vertical cylinder of unit radius (TODO)}.
 For the divergent case, $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
@@
 in Fig.~\ref{subfig:UMP_cvg}.
-At $U = 3t$, the RMP series is convergent, while RMP becomes divergent for $U=7t$.
+At $U = 3t$, the RMP series is convergent \titou{at $\lambda = 1$}, while RMP becomes divergent \titou{at $\lambda = 1$} for $U=7t$.
 The ground-state UMP expansion is convergent in both cases, although the rate of convergence is significantly slower 
@@
 and thus the low-lying excited states are likely to become intruder states. 
-For \ce{CH_2} in a diffuse, yet rather small basis set, the series is convergent at least up to the 50th order, and
+For \ce{CH_2} in a diffuse, yet rather small basis set, the series is convergent \titou{at $\lambda = 1$} at least up to the 50th order, and
 the dominant singularity lies close (but outside) the unit circle, causing slow convergence of the series.
@@
 Clearly the radius of convergence $\rc = \abs{\lc}$ is controlled directly by the ratio $\epsilon / U$, 
-with a convergent RMP series occurring for $\epsilon > 2 U$.
+with a convergent RMP series \titou{at $\lambda = 1$} occurring for $\epsilon > 2 U$.
 The on-site repulsion $U$ controls the strength of the HF potential localised around the ``atomic site'', with a

### 2021-02-01 Response_Letter/Response_Letter.tex
added new figures, manuscript revisions, and updated response letter

--- 2021-01-29 Response_Letter/Response_Letter.tex
@@
 \definecolor{darkgreen}{HTML}{009900}
+
+\usepackage[strict]{changepage}
+% for formal definitions
+\usepackage{framed}
+\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
+\renewenvironment{quote}
+{\begin{quotation}\noindent\it``\ignorespaces}
+{\ignorespaces''\end{quotation}}
+
+\newcommand{\sic}{[\textit{sic}]}
+% environment derived from framed.sty: see leftbar environment definition
+\definecolor{formalshade}{rgb}{0.95,0.95,1}
+
+\newenvironment{formal}{%
+  \def\FrameCommand{%
+    \hspace{1pt}%
+    {\color{darkblue}\vrule width 2pt}%
+    {\color{formalshade}\vrule width 4pt}%
+    \colorbox{formalshade}%
+  }%
+  \MakeFramed{\advance\hsize-\width\FrameRestore}%
+  \noindent\hspace{-4.55pt}% disable indenting first paragraph
+  \begin{adjustwidth}{}{7pt}%
+  \vspace{2pt}\vspace{2pt}%
+}
+{%
+  \vspace{2pt}\end{adjustwidth}\endMakeFramed%
+}
 
@@
 %%% REVIEWER 1 %%%
+\newpage
 \noindent \textbf{\large Authors' answer to Reviewer \#1}
 
-\begin{itemize}
-
-	\item 
-	{In this manuscript, the authors provide a comprehensive and thorough discussion of the role of exceptional point singularities in determining the performance of perturbation methods of electronic structure theory.
+\begin{formal}
+In this manuscript, the authors provide a comprehensive and thorough discussion of the role of exceptional point singularities in determining the performance of perturbation methods of electronic structure theory.
 The main subject considered is the well-known Moller-Plesset (MP) theory to calculate the electronic correlation energy, and various resummation techniques aimed to improve the convergence of the MP series.
@@
 Besides that point, I found some merit in the application of the Shanks transformation to different approximants for both the restricted and unrestricted versions of the theory, which focus on the corresponding set of orbitals.
-	Thus, I am glad to recommend publication.}
-	\\
-	\alert{We thank Reviewer \#1 for recommending publication of the present review.}
+Thus, I am glad to recommend publication.
+\end{formal}
 
-\end{itemize}
+\noindent{We thank Reviewer \#1 for their  support of our manuscript and for recommending publication.}
 
@@
 
-\begin{itemize}
-
-	\item 
-	{The topical review "Perturbation theory in the complex plane: Exceptional points and where to find them" reviews the origin and meaning of exceptional points in quantum chemistry. 
+\begin{formal}
+The topical review "Perturbation theory in the complex plane: Exceptional points and where to find them" reviews the origin and meaning of exceptional points in quantum chemistry. 
 The Hubbard dimer is used throughout as an illustrative example for the restricted and unrestricted cases, exact solution (FCI), Hartree-Fock, and Rayleigh-Schrodinger perturbation theory. 
@@
 
-	This topical review is very well done and I recommend it for publication as is. 
+\noindent This topical review is very well done and I recommend it for publication as is. 
 I list my comments below for the authors to address if they choose. 
@@
 I am not an expert in this exact area, so my questions are meant to represent those a typical reader might have. 
-	My questions do not need to all be addressed before the manuscript is published.}
-	\\
-	\alert{Again, we thank Reviewer \#2 for recommending publication and for his/her constructive comments.
-	Below, we address these comments.}
+My questions do not need to all be addressed before the manuscript is published.
+\end{formal}
 
-\item 
-	{I.\\
+\noindent {Again, we thank Reviewer \#2 for recommending publication and for their constructive comments.
+Below, we address these comments:}
+
+\begin{formal}
 How am I to actually interpret the electronic energy $E$ of such a non-Hermitian Hamiltonian? 
@@
 	Maybe something can be said about this because I suspect the imaginary part is somehow related to losses. 
-	This is hinted at in the introduction but was the first question that entered my mind.}
-	\\
-	\alert{In most figures, we indeed plot the real component of the energy.
-	By going complex, the energies lost their meaning as there's no relation of order for complex numbers.
-	In non-Hermitian processes like resonances or scattering, the imaginary part of the energy is indeed linked to lifetimes [see the book of Moiseyev].
-	However, the meaning  of the imaginary part of the energy in the present context is unclear and we prefer not to speculate on this.}
+	This is hinted at in the introduction but was the first question that entered my mind.
+\end{formal}
 
-\item 
-	{IIe.\\
+\noindent{In most figures, we indeed plot the real component of the energy, as shown on the relevant
+figure axes.
+By going complex, the energies lose their meaning as there is no ordering relationship for complex numbers.
+In non-Hermitian processes that consider resonances or scattering, the imaginary part of the energy is indeed linked to lifetimes [see the book of Moiseyev].
+We mention this in the Introduction section.
+However, the meaning  of the imaginary part of the energy in the present context is unclear and we prefer not to speculate on this.
+We have added a comment on this point in Section II.B of the revised manuscript.}
+
+\begin{formal}
 Could the authors make it very clear what is meant here by ``symmetry broken"? 
@@
 At high $U/t$, left and right sites are both open shell with one electron each. 
-	Am I to think of this as a broken spatial symmetry, broken spin symmetry, or both?}
-	\\
-	\alert{bla bla bla}
+Am I to think of this as a broken spatial symmetry, broken spin symmetry, or both?
+\end{formal}
 
-\item 
-	{It could be emphasized that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases, which is why these equations lack an RHF or UHF subscript. 
+\noindent{The Reviewer is correct that both spatial and spin symmetries are being broken.
+We consider spatial symmetry breaking to occur when the orbitals do not transform as an 
+irreducible transformation of the relevant point group ($D_{\infty\text{h}}$ in the case of 
+the symmetric Hubbard dimer). 
+Similarly, we consider spin symmetry breaking to occur when the wave function is not an 
+eigenfunction of the $\mathcal{S}^2$ operator. 
+We have clarified these definitions in the discussion of the symmetry-broken UHF wave functions.}
+
+\begin{formal}
+It could be emphasized that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases, which is why these equations lack an RHF or UHF subscript. 
 Also, in the general case (either RHF or UHF), the bonding orbitals for the two sigma values are occupied and the two antibonding orbitals are unoccupied. 
-	Bonding and antibonding notation is not so common in the condensed matter literature and it may be missed that these correspond to occupied and empty single-particle states.}
-	\\
-	\alert{We now mention that Eqs. 20, 21a, and 21b are valid for both the RHF and UHF cases.
-	We have also changed the notations for the occupied and empty single-particle states.}
+Bonding and antibonding notation is not so common in the condensed matter literature and it may be missed that these correspond to occupied and empty single-particle states.
+\end{formal}
 
-\item 
-	{IIf.\\
+\noindent{We now mention that Eqs. 20, 21a, and 21b are valid for both RHF and UHF.	We have also changed the notations for the occupied and empty single-particle states.}
+
+\begin{formal}
 What am I to think of values of $\lambda$ where $|\lambda|>1$? 
@@
 Some discussion could already be made that these values are not necessarily physical but determine the behavior of the physical series. 
-	Certain values away from $\lambda=1$ can also have physical meaning, like the autoionization process discussed later.}
-	\\
-	\alert{Only the $\lambda = 0$ (non-interacting system in some cases) and $\lambda = 1$ (fully interacting system) are physical systems  as mentioned in the manuscript.
-	However, it can be useful to study the systems at different $\lambda$ values.}
+Certain values away from $\lambda=1$ can also have physical meaning, like the autoionization process discussed later.
+\end{formal}
 
-\item 
-	{IIIc.\\
+\noindent{Only the $\lambda = 0$ (non-interacting system in some cases) and $\lambda = 1$ (fully interacting system) are physical systems, as mentioned in the manuscript.
+However, it can be useful to study the systems at different $\lambda$ values, as we do in Sec.~II.F.}
+
+\begin{formal}
 To be extra careful, should it be said that the RMP series is either convergent or divergent at the physical coupling value $|\lambda|=1$? 
@@
 I first thought the cylinder was marking the radius of convergence. It is meant to show the position of the EPs and indicate if the radius of convergence is $>1$ or $<1$. 
-	The language could be improved.}
-	\\
-	\alert{The language has been improved.}
+The language could be improved.
+\end{formal}
 
-\item 
-	{IIId.\\
+\noindent{The language has been improved and we have mentioned in several places that we are talking about a convergent/divergent MP series at $\lambda = 1$.}
+
+\begin{formal}
 The classification of front-door and back-door intruder states is not totally clear. 
 I raise this point because the journal is JPCM, and these terms are not common in condensed matter literature. 
-	Are intruder states equivalent to states creating exceptional points that ruin the series convergence?}
-	\\
-	\alert{The classification of front-door and back-door intruder states have been clarified.}
+Are intruder states equivalent to states creating exceptional points that ruin the series convergence?
+\end{formal}
 
-\item 
-	{IIIe.\\
-	Has "critical point" been defined yet?}
-	\\
-	\alert{Thank you for spotting this. 
-	"Critical point" is now defined in due place.}
+\noindent{We believe that the classification of front-door and back-door intruder states has been clearly defined in the original manuscript: 
+	\textit{``Following this theory, a singularity in the unit circle is designated as an intruder state, with a front-door (or back-door) intruder state if the real part of the singularity is positive (or negative).''}}
+\
+\begin{formal}%
+Has "critical point" been defined yet?
+\end{formal}
+\noindent{Thank you for spotting this. We have now defined ``critical point'' in the relevant locations.}
 
-\item 
-	{IIIf
+\begin{formal}
 The explanation of the critical point as the occurrence of the autoionization process is great and makes sense to me. 
@@
 Is it possible to circle the CP as one does for an EP? 
-	Is there any meaning to this?}
-	\\
-	\alert{bla bla bla}
+Is there any meaning to this?
+\end{formal}
 
-\item 
-	{IV.
+\noindent
+We thank the Reviewer for this useful piece of feedback, and attempt to answer some of their questions here.
+It is correct to say that the exact critical points correspond to points where the ground-state
+energy has a gradient discontinuity. 
+These points correspond to the intersection of two surfaces rather than an avoided crossing,
+leading to the sudden change in the eigenstates.
+It is possible to encircle the CP in the complex plane, but unlike an EP, this will leave the eigenstates unchanged.
+We have included a new plot of the ``atomic'' site  electron density as a function of $\lambda$ to illustrate
+the sudden autoionisation process at the critical point.
+We have also improved our discussion regarding these features using more explicit references to Figs.~7 and 8.
+Finally, we have endeavoured to illustrate the UMP critical point by considering the difference in electron densities on the left and right sites, as shown in an additional figure.
+
+\begin{formal}
 	Can something more be said about how these methods are fitted (briefly, and in a general way)? 
@@
 	Presumably, the exact function is known to some order and/or inside of some radius of convergence. 
-	The approximant is fitted in this region to match the exact function and then only the approximant is used beyond the original radius of convergence or at higher order.}
-	\\
-	\alert{As mentioned in the manuscript, the Pad\'e coefficients are determined by solving a set of linear equations involving the coefficients of the Taylor series.
+	The approximant is fitted in this region to match the exact function and then only the approximant is used beyond the original radius of convergence or at higher order.
+\end{formal} 
+\noindent	{As mentioned in the manuscript, the Pad\'e coefficients are determined by solving a set of linear equations that relate these coefficients with the low-order terms in the Taylor series.
 	This is the only knowledge required to compute these.}
 
-\item 
-	{Throughout the manuscript, the figures are excellent and really help the understanding. 
-	The authors have clearly taken time to prepare the manuscript and it can be published immediately.}
-	\\
-	\alert{Thank you for these kind comments.}
+\begin{formal}
+Throughout the manuscript, the figures are excellent and really help the understanding. 
+The authors have clearly taken time to prepare the manuscript and it can be published immediately.
+\end{formal}
 
-\end{itemize}
+\noindent{Thank you for these kind comments.}
 

### 2021-02-01 Manuscript/EPAWTFT.tex
added new figures, manuscript revisions, and updated response letter

@@
 potentials,\cite{Riss_1993,Ernzerhof_2006,Benda_2018} outgoing resonances can be stabilised as square-integrable
-wave functions with a complex energy that allows the resonance energy and lifetime to be computed.
+wave functions.
+\hugh{In these situations, the energy becomes complex-valued, with the real and imaginary components allowing
+the resonance energy and lifetime to be computed respectively.}
 We refer the interested reader to the excellent book by Moiseyev for a general overview. \cite{MoiseyevBook}
@@
 	Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
-    Only the interacting closed-shell singlets are shown in the complex plane, becoming degenerate at the EP (black dot).
+    Only the \hugh{real component of the}  interacting closed-shell singlet \hugh{energies} are shown in the complex plane, 
+    becoming degenerate at the EP (black dot).
     Following a contour around the EP (black solid) interchanges the states, while a second rotation (black dashed)
@@
 While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Fig.~\ref{subfig:FCI_real}).
+\hugh{In contrast, when $\lambda$ is complex, the energies may become complex-valued, with the real components shown in 
+Fig.~\ref{subfig:FCI_cplx}.
+Although the imaginary component of the energy is linked to resonance lifetimes elsewhere in non-Hermitian 
+quantum mechanics, \cite{MoiseyevBook} its physical interpretation in the current context is unclear.
+Throughout this work, we will generally consider and plot only the real component of any complex-valued energies.
+}
 
@@
 These $\lambda$ values correspond to so-called EPs and connect the ground and excited states in the complex plane.
-Crucially, the energy surface becomes non-analytic at $\lambda_{\text{EP}}$ and a square-root singularity forms with two branch cuts running along the imaginary axis from $\lambda_{\text{EP}}$  to $\pm \i \infty$ (see Fig.~\ref{subfig:FCI_cplx}).
+\hugh{Crucially, the ground- and excited-state wave functions at an EP become \emph{identical} rather than just degenerate.} 
+Furthermore, the energy surface becomes non-analytic at $\lambda_{\text{EP}}$ and a square-root singularity forms with two branch cuts running along the imaginary axis from $\lambda_{\text{EP}}$  to $\pm \i \infty$ (see Fig.~\ref{subfig:FCI_cplx}).
+\hugh{Along these branch cuts, the real components of the energies are equivalent and appear to give a seam 
+of intersection, but a strict degeneracy is avoided because the imaginary components are different.}
+
 On the real $\lambda$ axis, these EPs lead to the singlet avoided crossing at $\lambda = \Re(\lambda_{\text{EP}})$.
@@
 a gradient discontinuity on the real axis.
+\hugh{This gradient discontinuity defines a critical point in the ground-state energy,
+where a sudden change occurs in the electronic wave function, and can be considered as a zero-temperature quantum phase transition.} 
+\cite{Heiss_1988,Heiss_2002,Borisov_2015,Sindelka_2017,CarrBook,Vojta_2003,SachdevBook,GilmoreBook}
 
@@
 same symmetry for complex values of $\lambda$.
-
-\titou{Although the complex component of the energy is linked to lifetime in non-Hermitian quantum mechanics, \cite{MoiseyevBook} its meaning is unclear to us in the present context.}
 
@@
 in a multi-valued function.
-\titou{T2: define here critical point.}
 
@@
 $\lambda$ plane where two states become degenerate.
+\hugh{Additional singularities can also arise at critical points of the energy.
+A critical point corresponds to the intersection of two energy surfaces
+where the eigenstates remain distinct but a gradient discontinuity occurs in 
+the ground-state energy.
+In contrast, at a square-root branch point, both the energies and the associated wave functions
+of the intersecting surfaces become identical.}
 Later we will demonstrate how the choice of reference Hamiltonian controls the position of these EPs, and 
@@
 \end{equation}
-giving the symmetry-pure molecular orbitals
+giving the molecular orbitals
 \begin{align}
@@
 \end{equation}
+\hugh{Here, the molecular orbitals respectively transform 
+according to the $\Sigma_\text{g}^{+}$ and $\Sigma_\text{u}^{+}$ irreducible representations of 
+the $D_{\infty \text{h}}$ point group that represents the symmetric Hubbard dimer.
+We can therefore consider these as symmetry-pure molecular orbitals.} 
 However, in the strongly correlated regime $U>2t$, the closed-shell orbital restriction prevents RHF from 
@@
 
-As the on-site repulsion is increased from 0, the HF approximation reaches a critical value at $U=2t$ where a symmetry-broken 
+As the on-site repulsion is increased from 0, the HF approximation reaches a critical value at $U=2t$ where an alternative
 UHF solution appears with a lower energy than the RHF one.
@@
 \end{equation}
-Time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped counterpart, obtained 
+
+\hugh{The molecular orbitals of the lower-energy UHF solution do not transform as an irreducible
+representation of the $D_{\infty \text{h}}$ point group and therefore break spatial symmetry.
+Allowing different orbitals for the different spins also means that the
+overall wave function is no longer an eigenfunction of the  $\cS^2$ operator and can be considered to break spin symmetry.
+This combined spatial and spin symmetry-breaking occurs for all $U \ge 2t$.}
+Furthermore, time-reversal symmetry dictates that this UHF wave function must be degenerate with its spin-flipped counterpart, obtained 
 by swapping $\ta_{\text{UHF}}$ and $\tb_{\text{UHF}}$ in Eqs.~\eqref{eq:ta_uhf} and \eqref{eq:tb_uhf}.
@@
 ``oscillates'' between the two symmetry-broken configurations. \cite{GiulianiBook}
-Symmetry breaking can also occur in RHF theory when a charge-density wave is formed from an oscillation 
+Spatial symmetry breaking can also occur in RHF theory when a charge-density wave is formed from an oscillation 
 between the two closed-shell configurations with both electrons localised on one site or the other.\cite{StuberPaldus,Fukutome_1981}
@@
 The corresponding Riemann surfaces for $U = 3.5\,t$ and $4.5\,t$ are shown in Figs.~\ref{subfig:RMP_3.5} and 
-\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot) and \titou{the radius of convergence indicated
-by the vertical cylinder of unit radius (TODO)}.
-For the divergent case, $\lep$ lies inside this cylinder of convergence, while in the convergent case $\lep$ lies
+\ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot).
+\hugh{We illustrate the surface $\abs{\lambda} = 1$ using a vertical cylinder of unit radius to provide
+a visual aid for determining if the series will converge at the physical case $\lambda =1$.} 
+For the divergent case, $\lep$ lies inside this \hugh{unit} cylinder, while in the convergent case $\lep$ lies
 outside this cylinder.
@@
 for the two states using the ground-state RHF orbitals is identical.
+\hugh{Note that, when $\lep$ lies \emph{on} the unit cylinder, we cannot \textit{a priori} determine 
+whether the perturbation series will converge or not.}
 
@@
 % EFFECT OF SYMMETRY BREAKING
-As the UHF orbitals break the spin symmetry, new coupling terms emerge between the electronic states that
+As the UHF orbitals break the \hugh{spatial and} spin symmetry, new coupling terms emerge between the electronic states that
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% RMP critical point density
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b]
+	\includegraphics[width=\linewidth]{rmp_crit_density}
+	\caption{
+\hugh{Electron density $\rho_\text{atom}$ on the ``atomic'' site of the asymmetric Hubbard dimer with 
+$\epsilon = 2.5 U$. 
+The autoionsation process associated with the critical point is represented by the sudden drop on the negative $\lambda$ axis.
+In the idealised limit $t=0$, this process becomes increasingly sharp and represents a zero-temperature QPT.} 
+	\label{fig:rmp_dens}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % EXACT VERSUS APPROXIMATE
-The critical point in the exact case $t=0$ lies on the negative real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: dashed lines), 
+The critical point in the exact case $t=0$ \hugh{is represented by the gradient discontinuity in the 
+ground-state energy} on the negative real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: solid lines), 
 mirroring the behaviour of a quantum phase transition.\cite{Kais_2006}
+\hugh{The autoionisation process is manifested by a sudden drop in the ``atomic site'' 
+electron density $\rho_\text{atom}$ (Fig.~\ref{fig:rmp_dens}).} 
 However, in practical calculations performed with a finite basis set, the critical point is modelled as a cluster
@@
 idealised destination for the ionised electrons with a non-zero (yet small) hopping term $t$.
-Taking the value $t=0.1$ (Fig.~\ref{subfig:rmp_cp}: solid lines), the critical point becomes a
-sharp avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
-In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}),
+Taking the value $t=0.1$ (Fig.~\ref{subfig:rmp_cp}: dashed lines), the critical point becomes  
+an avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
+\hugh{In contrast to the exact critical point with $t=0$, the ground-state energy remains
+smooth through this avoided crossing.}
+In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}) \hugh{and the 
+avoided crossing becomes a gradient discontinuity},
 mirroring Sergeev's discussion on finite basis
@@
     becomes increasingly sharp.
-    (\subref{subfig:ump_cp_surf}) Complex energy surfaces for $U = 5t$.
+    (\subref{subfig:ump_cp_surf}) \hugh{The avoided crossing at $U=5t$ corresponds to EPs with a non-zero imaginary component.}
     (\subref{subfig:ump_ep_to_cp}) Convergence of the EPs at $\lep$ onto the real axis for $U/t \to \infty$.
@@
 becomes increasingly repulsive.
-Closed-shell critical points along the positive real $\lambda$ axis then represent 
+Closed-shell critical points along the positive real $\lambda$ axis may then represent 
 points where the two-electron repulsion overcomes the attractive HF potential 
@@
 
-In contrast, symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% UMP critical point density
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b]
+	\includegraphics[width=\linewidth]{ump_crit_density}
+	\caption{
+\hugh{    Difference in the electron densities on the left and right sites for the UMP ground-state in the symmetric Hubbard dimer
+(see Eq.~\eqref{eq:ump_dens}). 
+    At $\lambda = 1$, the spin-up electron transfers from the right site to the left site, while the spin-down
+electron transfers in the opposite direction. 
+In the strong correlation limit (large $U/t$), this process becomes increasingly sharp and represents a
+zero-temperature QPT.}
+	\label{fig:ump_dens}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In contrast, spin symmetry-breaking in the UMP reference creates different HF potentials for the spin-up and spin-down electrons.
 Consider one of the two reference UHF solutions where the spin-up and spin-down electrons are localised on the left and right sites respectively. 
@@
 represents the reference double excitation for $\lambda > 1/2$.
+\hugh{We can visualise this swapping process by considering the difference in the
+electron density on the left and right sites, defined for each spin as
+\begin{equation}
+\Delta \rho^{\sigma} = \rho_\mathcal{R}^{\sigma} - \rho_\mathcal{L}^{\sigma},
+\label{eq:ump_dens}
+\end{equation}
+where $\rho_{\mathcal{L}}^{\sigma}$ ($\rho_{\mathcal{R}}^{\sigma}$) is the spin-$\sigma$ electron density
+on the left (right) site. 
+This density difference is shown for the UMP ground-state at $U = 5 t$ in Fig.~\ref{fig:ump_dens} (solid lines).
+Here, the transfer of the high-spin electron from the right site to the left site can be seen as $\lambda$ passes through 1
+(and similarly for the low-spin electron).}
 
@@
 both in the UHF reference and the exact wave function.
-This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing
-that corresponds to EPs with non-zero imaginary components (solid lines in Fig.~\ref{subfig:ump_cp}).
+This delocalisation dampens the electron swapping process and leads to a ``shallow'' avoided crossing (solid lines in Fig.~\ref{subfig:ump_cp})
+that corresponds to EPs with non-zero imaginary components (Fig.~\ref{subfig:ump_cp_surf}).
 As $U/t$ becomes larger, the HF potentials become stronger and the on-site repulsion dominates the hopping
@@
 In other words, the electrons localise on individual sites to form a Wigner crystal.
-These effects create a stronger driving force for the electrons to swap sites until eventually this swapping
-occurs exactly at $\lambda = 1$.
+These effects create a stronger driving force for the electrons to swap sites until, eventually, this swapping
+occurs suddenly at $\lambda = 1$, \hugh{as shown for $U= 50 t$ in Fig.~\ref{fig:ump_dens} (dashed lines).}
 In this limit, the ground-state EPs approach the real axis (Fig.~\ref{subfig:ump_ep_to_cp}) and the avoided 
@@
 a new type of MP critical point and represents a QPT as the perturbation parameter $\lambda$ is varied.
-Furthermore, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
+Remarkably, this argument explains why the dominant UMP singularity lies so close, but always outside, the 
 radius of convergence (see Fig.~\ref{fig:RadConv}).
@@
 \end{equation}
-where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting terms for each power of $\lambda$.
+where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting 
+\hugh{and comparing terms for each power of $\lambda$ with the low-order terms in the Taylor series expansion}.
 Pad\'e approximants are extremely useful in many areas of physics and 

### 2021-02-01 Response_Letter/Response_Letter.tex
minor modifications

@@
 \begin{quote}
-	\textit{``Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them''}.
+	\textit{Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them.}
 \end{quote}
@@
 \noindent	{As mentioned in the manuscript, the Pad\'e coefficients are determined by solving a set of linear equations that relate these coefficients with the low-order terms in the Taylor series.
-	This is the only knowledge required to compute these.}
+	This is the only knowledge required to compute these.
+	A minor modification has been performed to clarify this.}
 

### 2021-02-01 Manuscript/EPAWTFT.tex
minor modifications

@@
 wave functions.
-\hugh{In these situations, the energy becomes complex-valued, with the real and imaginary components allowing
+\titou{In these situations, the energy becomes complex-valued, with the real and imaginary components allowing
 the resonance energy and lifetime to be computed respectively.}
@@
 	Exact energies for the Hubbard dimer ($U=4t$) as functions of $\lambda$ on the real axis (\subref{subfig:FCI_real}) and in the complex plane (\subref{subfig:FCI_cplx}).
-    Only the \hugh{real component of the}  interacting closed-shell singlet \hugh{energies} are shown in the complex plane, 
+    Only the \titou{real component of the}  interacting closed-shell singlet \titou{energies} are shown in the complex plane, 
     becoming degenerate at the EP (black dot).
@@
 While the open-shell triplet ($E_{\text{T}}$) and singlet ($E_{\text{S}}$) are independent of $\lambda$, the closed-shell singlet ground state ($E_{-}$) and doubly-excited state ($E_{+}$) couple strongly to form an avoided crossing at $\lambda=0$ (see Fig.~\ref{subfig:FCI_real}).
-\hugh{In contrast, when $\lambda$ is complex, the energies may become complex-valued, with the real components shown in 
+\titou{In contrast, when $\lambda$ is complex, the energies may become complex-valued, with the real components shown in 
 Fig.~\ref{subfig:FCI_cplx}.
@@
 These $\lambda$ values correspond to so-called EPs and connect the ground and excited states in the complex plane.
-\hugh{Crucially, the ground- and excited-state wave functions at an EP become \emph{identical} rather than just degenerate.} 
+\titou{Crucially, the ground- and excited-state wave functions at an EP become \emph{identical} rather than just degenerate.} 
 Furthermore, the energy surface becomes non-analytic at $\lambda_{\text{EP}}$ and a square-root singularity forms with two branch cuts running along the imaginary axis from $\lambda_{\text{EP}}$  to $\pm \i \infty$ (see Fig.~\ref{subfig:FCI_cplx}).
-\hugh{Along these branch cuts, the real components of the energies are equivalent and appear to give a seam 
+\titou{Along these branch cuts, the real components of the energies are equivalent and appear to give a seam 
 of intersection, but a strict degeneracy is avoided because the imaginary components are different.}
@@
 a gradient discontinuity on the real axis.
-\hugh{This gradient discontinuity defines a critical point in the ground-state energy,
+\titou{This gradient discontinuity defines a critical point in the ground-state energy,
 where a sudden change occurs in the electronic wave function, and can be considered as a zero-temperature quantum phase transition.} 
@@
 $\lambda$ plane where two states become degenerate.
-\hugh{Additional singularities can also arise at critical points of the energy.
+\titou{Additional singularities can also arise at critical points of the energy.
 A critical point corresponds to the intersection of two energy surfaces
@@
 \end{equation}
-\hugh{Here, the molecular orbitals respectively transform 
+\titou{Here, the molecular orbitals respectively transform 
 according to the $\Sigma_\text{g}^{+}$ and $\Sigma_\text{u}^{+}$ irreducible representations of 
@@
 
-\hugh{The molecular orbitals of the lower-energy UHF solution do not transform as an irreducible
+\titou{The molecular orbitals of the lower-energy UHF solution do not transform as an irreducible
 representation of the $D_{\infty \text{h}}$ point group and therefore break spatial symmetry.
@@
 \ref{subfig:RMP_4.5}, respectively, with the single EP at $\lep$ (black dot).
-\hugh{We illustrate the surface $\abs{\lambda} = 1$ using a vertical cylinder of unit radius to provide
+\titou{We illustrate the surface $\abs{\lambda} = 1$ using a vertical cylinder of unit radius to provide
 a visual aid for determining if the series will converge at the physical case $\lambda =1$.} 
-For the divergent case, $\lep$ lies inside this \hugh{unit} cylinder, while in the convergent case $\lep$ lies
+For the divergent case, $\lep$ lies inside this \titou{unit} cylinder, while in the convergent case $\lep$ lies
 outside this cylinder.
@@
 for the two states using the ground-state RHF orbitals is identical.
-\hugh{Note that, when $\lep$ lies \emph{on} the unit cylinder, we cannot \textit{a priori} determine 
+\titou{Note that, when $\lep$ lies \emph{on} the unit cylinder, we cannot \textit{a priori} determine 
 whether the perturbation series will converge or not.}
@@
 % EFFECT OF SYMMETRY BREAKING
-As the UHF orbitals break the \hugh{spatial and} spin symmetry, new coupling terms emerge between the electronic states that
+As the UHF orbitals break the \titou{spatial and} spin symmetry, new coupling terms emerge between the electronic states that
 cause fundamental changes to the structure of EPs in the complex $\lambda$-plane.
@@
 	\caption{
-\hugh{Electron density $\rho_\text{atom}$ on the ``atomic'' site of the asymmetric Hubbard dimer with 
+\titou{Electron density $\rho_\text{atom}$ on the ``atomic'' site of the asymmetric Hubbard dimer with 
 $\epsilon = 2.5 U$. 
-The autoionsation process associated with the critical point is represented by the sudden drop on the negative $\lambda$ axis.
+The autoionisation process associated with the critical point is represented by the sudden drop on the negative $\lambda$ axis.
 In the idealised limit $t=0$, this process becomes increasingly sharp and represents a zero-temperature QPT.} 
@@
 % EXACT VERSUS APPROXIMATE
-The critical point in the exact case $t=0$ \hugh{is represented by the gradient discontinuity in the 
+The critical point in the exact case $t=0$ \titou{is represented by the gradient discontinuity in the 
 ground-state energy} on the negative real $\lambda$ axis (Fig.~\ref{subfig:rmp_cp}: solid lines), 
 mirroring the behaviour of a quantum phase transition.\cite{Kais_2006}
-\hugh{The autoionisation process is manifested by a sudden drop in the ``atomic site'' 
+\titou{The autoionisation process is manifested by a sudden drop in the ``atomic site'' 
 electron density $\rho_\text{atom}$ (Fig.~\ref{fig:rmp_dens}).} 
@@
 an avoided crossing with a complex-conjugate pair of EPs close to the real axis (Fig.~\ref{subfig:rmp_cp_surf}).
-\hugh{In contrast to the exact critical point with $t=0$, the ground-state energy remains
+\titou{In contrast to the exact critical point with $t=0$, the ground-state energy remains
 smooth through this avoided crossing.}
-In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}) \hugh{and the 
+In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}) \titou{and the 
 avoided crossing becomes a gradient discontinuity},
@@
     becomes increasingly sharp.
-    (\subref{subfig:ump_cp_surf}) \hugh{The avoided crossing at $U=5t$ corresponds to EPs with a non-zero imaginary component.}
+    (\subref{subfig:ump_cp_surf}) \titou{The avoided crossing at $U=5t$ corresponds to EPs with non-zero imaginary components.}
     (\subref{subfig:ump_ep_to_cp}) Convergence of the EPs at $\lep$ onto the real axis for $U/t \to \infty$.
@@
 	\caption{
-\hugh{    Difference in the electron densities on the left and right sites for the UMP ground-state in the symmetric Hubbard dimer
-(see Eq.~\eqref{eq:ump_dens}). 
+\titou{Difference in the electron densities on the left and right sites for the UMP ground state in the symmetric Hubbard dimer
+[see Eq.~\eqref{eq:ump_dens}]. 
     At $\lambda = 1$, the spin-up electron transfers from the right site to the left site, while the spin-down
@@
 represents the reference double excitation for $\lambda > 1/2$.
-\hugh{We can visualise this swapping process by considering the difference in the
+\titou{We can visualise this swapping process by considering the difference in the
 electron density on the left and right sites, defined for each spin as
@@
 These effects create a stronger driving force for the electrons to swap sites until, eventually, this swapping
-occurs suddenly at $\lambda = 1$, \hugh{as shown for $U= 50 t$ in Fig.~\ref{fig:ump_dens} (dashed lines).}
+occurs suddenly at $\lambda = 1$, \titou{as shown for $U= 50 t$ in Fig.~\ref{fig:ump_dens} (dashed lines).}
 In this limit, the ground-state EPs approach the real axis (Fig.~\ref{subfig:ump_ep_to_cp}) and the avoided 
@@
 where the coefficients of the polynomials $A(\lambda)$ and $B(\lambda)$ are determined by collecting 
-\hugh{and comparing terms for each power of $\lambda$ with the low-order terms in the Taylor series expansion}.
+\titou{and comparing terms for each power of $\lambda$ with the low-order terms in the Taylor series expansion}.
 Pad\'e approximants are extremely useful in many areas of physics and 

### 2021-02-02 Response_Letter/Response_Letter.tex
minor edits

@@
 We have included a new plot of the ``atomic'' site  electron density as a function of $\lambda$ to illustrate
-the sudden autoionisation process at the critical point.
+the sudden autoionisation process at the RMP critical point.
 We have also improved our discussion regarding these features using more explicit references to Figs.~7 and 8.
@@
 \end{formal} 
-\noindent	{As mentioned in the manuscript, the Pad\'e coefficients are determined by solving a set of linear equations that relate these coefficients with the low-order terms in the Taylor series.
-	This is the only knowledge required to compute these.
+\noindent	{As mentioned in the manuscript, the Pad\'e (or quadratic) coefficients are determined by solving a set of linear equations that relate these coefficients with the low-order terms in the Taylor series.
+	This is the only knowledge required to compute these approximants.
 	A minor modification has been performed to clarify this.}

### 2021-02-02 Manuscript/EPAWTFT.tex
minor edits

@@
 Perturbation theory isn't usually considered in the complex plane.
-Normally it is applied using real numbers as one of very few available tools for 
+Normally, it is applied using real numbers as one of very few available tools for 
 describing realistic quantum systems.
@@
 Mathematically, Eq.~\eqref{eq:E_expansion} corresponds to a Taylor series expansion of the exact energy
-around the reference system $\lambda = 0$.
+around the reference system $\lambda~=~0$.
 The energy of the target ``physical'' system is recovered at the point $\lambda = 1$.
@@
 \end{equation}
-where we have introduced \titou{occupied $\psi_1^{\sigma}$} and \titou{unoccupied $\psi_2^{\sigma}$} molecular orbitals for 
+where we have introduced \titou{occupied $\phi_1^{\sigma}$} and \titou{unoccupied $\phi_2^{\sigma}$} molecular orbitals for 
 the spin-$\sigma$ electrons as
@@
 	\label{eq:psi1}
-    \titou{\psi_1^{\sigma}} & = \hphantom{-} \cos(\frac{\ts}{2}) \Lsi + \sin(\frac{\ts}{2}) \Rsi,
+    \titou{\phi_1^{\sigma}} & = \hphantom{-} \cos(\frac{\ts}{2}) \Lsi + \sin(\frac{\ts}{2}) \Rsi,
 	\\
 	\label{eq:psi2}
-	\titou{\psi_2^{\sigma}} & = - \sin(\frac{\ts}{2}) \Lsi + \cos(\frac{\ts}{2}) \Rsi
+	\titou{\phi_2^{\sigma}} & = - \sin(\frac{\ts}{2}) \Lsi + \cos(\frac{\ts}{2}) \Rsi
 \end{align}
@@
 \begin{align}
-	\titou{\psi_{1,\text{RHF}}^{\sigma}} & = \frac{\Lsi + \Rsi}{\sqrt{2}},
+	\titou{\phi_{1,\text{RHF}}^{\sigma}} & = \frac{\Lsi + \Rsi}{\sqrt{2}},
 	&
-	\titou{\psi_{2,\text{RHF}}^{\sigma}} & = \frac{\Lsi - \Rsi}{\sqrt{2}},
+	\titou{\phi_{2,\text{RHF}}^{\sigma}} & = \frac{\Lsi - \Rsi}{\sqrt{2}},
 \end{align}
@@
 \titou{In contrast to the exact critical point with $t=0$, the ground-state energy remains
-smooth through this avoided crossing.}
+smooth through this avoided crossing, with a more gradual drop in the atomic site density.}
 In the limit $t \to 0$, these EPs approach the real axis (Fig.~\ref{subfig:rmp_ep_to_cp}) \titou{and the 
@@
 This density difference is shown for the UMP ground-state at $U = 5 t$ in Fig.~\ref{fig:ump_dens} (solid lines).
-Here, the transfer of the high-spin electron from the right site to the left site can be seen as $\lambda$ passes through 1
-(and similarly for the low-spin electron).}
+Here, the transfer of the spin-up electron from the right site to the left site can be seen as $\lambda$ passes through 1
+(and similarly for the spin-down electron).}
 
